### 2024-07-12 ARS/Rewriting.tex
well-founded, ARS tex file

\documentclass{scrartcl}

\begin{document}

\section{Relations, ARS}

\begin{enumerate}
  \item Define logical and structurual operations on relations, proving laws about them.
  \item Define closure operations on realtions, proving laws about them
  \item Define properties such as transtivity etc.
\end{enumerate}

\subsection{Well-foundedness}

Four notions:
\begin{itemize}
  \item Based on every element being accessible
  \item Every inductive relation is universally true
  \item Every non-empty set has a minimal element
  \item No infinite sequence is decreasing
\end{itemize}

\section{Open research questions}
\begin{enumerate}
  \item Sufficient conditions for reversing the implications between notions of
  well-foundedness?
  \item Knaster-Tarski Lemma: Most general form? Alternative formulations?
  \item Syntax for closure operators allowing to prove the needed properties
  uniformly/generically
\end{enumerate}

\section{To Do}
\begin{enumerate}
  \item Clean up the current development
  \item More laws about closure operations: Monotonicity, idempotency
  \item Refactor the ARS formalized results with the new development
  \item Knaster--Tarski in a well-founded setting: what additional
  hypotheses are necessary?
\end{enumerate}

\subsection{Questions about well-foundedness}

\begin{enumerate}
  \item For a given element $x$, is the property of
  being accessible $\lnot\lnot$-closed? I.E.,
  Does $x$ being $\lnot\lnot$-accessible imply that $x$ is accessible?
  (Conjecture: No.)

  \item As a special case, does being weakly (accessible) well-founded imply being $\lnot\lnot$-wellfounded?
  (Conjecture: No.)

  Also: Same question about inductive notion of well-foundedness.

  \item ($\star$) Given a well-founded relation, does every non-empty subset
  have a minimal element?

  \emph{Problem.} Need to decide whether, for a given $x \in U$,
   the set $\{y | Ryx\}$ is empty.

   \item IF every non-empty subset has a minimal element, does this imply
   either of the weak forms of well-foundedness: $\mathtt{isWFacc-}$ or
   $\mathtt{isWFind-}$ ?

   \item Does $\mathtt{isWFmin-}$ imply $\mathtt{isWFacc-}$ or $\mathtt{isWFind-}$?

   \emph{Problem.} Need to go from $\lnot (\forall y. R y d \to \phi y)$
   and $\forall y. R y d \to \lnot \lnot \phi y$ to $\bot$.

   In terms of accessibility, it should suffices to assume accessibility is
   $\lnot\lnot$-closed, since being related to y is not relevant for that. (?)

   \item Does sequential well-foundedness (no decreasing sequence) imply
   any of the other notions, e.g., \texttt{WFmin-} ?

   \emph{Note.}  This seems to require the most classical assumptions:
   $\lnot\lnot$-closure of $\phi$, relativized De Morgan law,
   Markov's principle, etc.
\end{enumerate}

\textsc{Remark.}
$\lnot\lnot$-closure of accessibility should solve problems 1 and 4.

\end{document}

### 2024-08-15 QADT/notes.tex
Quotients of Algebraic Datatypes added

\documentclass[letterpaper,numbers=enddot]{scrartcl}

\usepackage{amsmath}
\usepackage{amssymb}

\title{Isomorphisms between algebraic datatypes}
\author{Andrew Polonsky, Ben Lenox}

\newcommand{\cat}{\mathbb{C}}
\newcommand{\op}{{op}}

\newcommand{\bone}{\boldsymbol{1}}
\newcommand{\then}{\quad\mathrel{\Longrightarrow}\quad}

\newcommand{\ints}{\mathbb{Z}}

\begin{document}

\maketitle

\section{2024.07.10}

Notes on ``Objects of categories as complex numbers''.

\subsection{Prop.2}

Can Proposition 2 be generalized as follows.

Let $p(x) = p_1(x)- p_2(x)$, $q(x) = q_1(x)-q_2(x)$ be elements of $\ints[x]$.

If the content of $p$ divides the content of $q$, and
the roots of $p$ are a submultiset of the roots of $q$, then
\[ \forall x. p(x)=0 \then q(x) = 0 \]

\newpage

\section*{TODO}

\begin{enumerate}
  \item Actually prove that
  \[ X=(X+1)^2 \then X \simeq X^2 \]
\end{enumerate}

\newpage
\section{Questions to be investigated}

\begin{enumerate}
  \item What is a strong isomorphism between ADTs?
  \item What does it mean for a functor to be a factor of another functor?
  \item A conception of a negative set in these terms.
  \begin{itemize}
    \item Universal $U$, and an ``integer set'' is a function from $U$ to $\mathbb{Z}$.
    \item A contravariant functor $- : \cat \to \cat^\op$ that splits the identity
    ($- \circ -^\op = id$)
    \item A solution to $E(X)=X$, obtained by taking $X = Y + 1$ for some type $Y$.
  \end{itemize}
  \item All polynomials functors with degree at least two will have linear factors.
  Can it solve arbitrary linear equation?
  Are all linear datatypes isomorphic to each other?  Are they generated by $S = -1$?
  \item Retractions between datatypes!
  \item Isomorphisms induced by initial algebra maps.
  \item Let $H(X) = 1 + X + X^3$, then $X$ contains sixth roots of unity as well as
  a square root of unity.  $M(X) = 1 + X + X^2$ contains fourth roots of unity;
  does this explain why we can ``divide $H(X)$ by $M(X)$''?

  Is this the reason why a solution to $M(X)=X$, when squared, yields a solution to $H(X)$?
  Why does this happen more generally?
  \item Can any equation $X=P(X)$, with $P(X)$ be an \emph{arbitrary}
  polynomial --- containing both positive and negative coefficients ---
  be solved by substitution $X = (Y+k)$, for some $k \ge 0$.

  Can various solutions be compared?

  \item Generalize all of the above to \emph{systems of equations} of the form
  \begin{align*}
    P_1(X_1,\dots,X_k) &= Q_1(X_1,\dots,X_k)\\
    P_2(X_1,\dots,X_k) &= Q_2(X_1,\dots,X_k)\\
     &\quad \vdots \\
    P_k(X_1,\dots,X_k) &= Q_k(X_1,\dots,X_k)
  \end{align*}
\end{enumerate}

\section{To do:}
\begin{enumerate}
  \item Define an ADT.
  \item Define R(A?)DT: \emph{Rational (Algebraic?) Datatypes}
  \item Is every RADT an ADT?
\end{enumerate}

\section{Discussion}
Let $F$ be a functor, $X$ be the initial $F$-algebra.

By Lambek's Theorem, $F(X) \simeq X$.

For any polynomial $P(X)$ in $X$, we get $P(F(X)) \simeq P(X)$.

Relate this to the notion of strong isomorphism.

\section{2023.08.10}

\subsection*{Functors}
Let $H(X) = 1 + X + X^3$.

Let $N$ be the initial algebra of $H$, so that $N \simeq H(N)$.

Let $B(X) = 1 + 2X$.

Let $S$ be the initial algebra of $B$, so that $S \simeq B(S)$.

Is $B$ a ``factor'' of $H$?

To compare the them, try to put an $B$-algebra on... $N$? Doesn't work.

But on $N^3$ works!

\section{2023.08.16}

\subsection{Main conjecture}

\subsection{Conjecture}

The algebraic datatype $X = P(X)$ includes infinite trees only if it does NOT contain
a positive integer root.

\textbf{Example.}
$F(X) = X^2-4X+1$.  To have $F(X)=X$, we expect the roots to be $X = 4$ and $X = 1$.

Applying the substitution $X = Y+1$, we get
\begin{align*}
  Y+1
  &= Y^2 + 2Y + 1 - 4Y-4 + 4\\
  Y &= Y^2-2Y
\end{align*}

The initial algebra for $Y \mapsto Y^2-2Y$ is $Y=\emptyset$,
which suggests the initial algebra for $F(X)$ is also $X = \bone$.

Setting instead $X = Z + 4$, we get
\[ Z+4 = \cdots = Z^2 + 4Z \]

Generally, whenever we set $X = Y + k$,
where $k$ is a root of the polynomial $F(X)$, then this will cancel out the constants,
leaving out a functor whose initial algebra is the empty set.

\subsection{Observation about $B(X) = 2X+1$}

\begin{align*}
  X &= 2X + 1\\
  X - 1 &= 2X\\
  X &= Y+1\\
  Y+1-1 &= 2Y + 2\\
  Y &= 2Y + 2
\end{align*}

\subsection{Key Question}

What is the notion of a \emph{least} fixed point/\emph{initial} algebra for
a (system of) equation(s) in which \emph{both sides} are polynomials.

(This is equivalent to admitting negative coefficients.)

\subsection{Another example}
\begin{align*}
  X &= X^2 - 4X + 4\\
  X &= 5 + P\\
  5+P &= \cdots \\
  P &= P^2 + 6P + 4
\end{align*}

\subsection{Open questions}

\begin{enumerate}
  \item The following rule is obviously sound:
  \[ X+1 = Y+1 \then X=Y \]
  How constructive is this principle?
  Do we need to decide equality on both $X$ and $Y$ to exhibit the
  isomorphism on the right in terms of the one on the left?

  \textbf{Answer.}
  Always solvable.  Given $i : X+1 \to Y+1$, define $i^! :X \to Y$ as follows.
  Given $x$, consider $X \mapsto X+1 \mapsto Y+1$, can check whether the output is in $1$, and if so,
  apply $i$ to $()$.  Same in the other direction.

  \item What does it mean for an isomorphism from $X$ to $P(X)$, where $P(X)$
  is a polynomial, to describe an ADT, when $P(X)$ has a specific root,
  e.g., $i$, $-i$, $1$, $-1$, $0$, $2$, $-\pi^2$, $\frac{1}{2}$, $\sqrt(2)$, etc.

  What properties does possession of a particular root imply for a given ADT?

  \item Generalize all of the above to having arbitrary ADTs as coefficients
  in the polynomial (defining the functor).

\end{enumerate}

\section{2023.09.07}
\begin{enumerate}
  \item If $X = P(X) + X$, then $X = n \cdot P(X) + X$ for all $n \in \mathbb{Z}$.

  \textsc{Proof.} Induction for non-negative $n$, symmetry for all $n$.

  \item If $X = P(X) + X$, then $X = X \cdot P(X) + X$.

  \item If $X = P(X) + X$, then $X = (X+n)\cdot P(X) + X$ for all $n \in \mathbb{Z}$.

  \textsc{Proof.} Distribute, and use the previous two facts.
\end{enumerate}

Everything reduces to the second case, so we analyze that.
\begin{itemize}
  \item If $P(x)=0$, it's trivially true.
  \item If $P(x) = k$, then $X = X + k$, $X \cdot P(X) + X = X (1 + k)$
\end{itemize}
\end{document}

### 2024-08-15 QADT/adts.hs

@@ -1,0 +1,49 @@
+-- given an ordered list, and a new element, output a sorted list with
+-- the new element added
+insert :: (Ord a) => a -> [a] -> [a]
+insert x [] = [x]
+insert x (y:ys) = if x > y then y : insert x ys else x : (y : ys)
+
+fold :: t -> (a -> t -> t) -> [a] -> t
+fold t0 f [] = t0
+fold t0 f (x:xs) = f x (fold t0 f xs)
+
+mapFromFold :: (a -> b) -> [a] -> [b]
+mapFromFold f = fold [] (\x y -> f x : y)
+
+insertAtEnd :: a -> [a] -> [a]
+insertAtEnd x0 = fold [x0] (:)
+
+addList :: [Integer] -> Integer
+addList = fold (0) (+)
+
+concatLists :: [a] -> [a] -> [a]
+concatLists xs ys = fold (ys) (:) xs
+
+insertFromFold :: (Ord a) => a -> [a] -> [a]
+insertFromFold x ys = fold [x] (\y zs -> if x > y then y : zs else x : y : zs) ys
+
+data Nat = Z | S Nat deriving Show
+
+iter :: a -> (a -> a) -> Nat -> a
+iter z f Z = z
+iter z f (S n) = f (iter z f n)
+
+addFromIter :: Nat -> Nat -> Nat
+addFromIter m = iter m S
+
+mulFromIter :: Nat -> Nat -> Nat
+mulFromIter m = iter (Z) (addFromIter m)
+
+fac :: Nat -> Nat
+fac Z = S Z
+fac (S n) = mulFromIter (S n) (fac n)
+
+
+fact :: Nat -> Nat
+fact Z = S Z
+fact (S n) = iter (S Z) (\k -> mulFromIter (S n) k) n
+
+nat2int :: Nat -> Integer
+nat2int Z = 0
+nat2int (S n) = 1 + nat2int n

### 2024-08-15 QADT/iso_research_more_general.py

@@ -1,0 +1,40 @@
+import re
+def main():
+    diff = [1, 1, 1, 0]
+    poly = [0, 1, 0, 0, 0]
+    # diff = [1, 0, 0, 0, 0, 1]
+    # poly = [1, 1, 0, 0, 0, 1]
+    # poly = [0, 0, 1, 1, 0, 0, 0, 1]
+    last = poly
+    with open("poly_log.txt", "w") as log:
+        while True:
+            if poly != last: log.write(" | ".join(map(lambda x: f"{x:3d}", poly)) + "\n")
+            print(" | ".join(map(lambda x: f"{x:3d}", range(len(poly)))))
+            print(" | ".join(map(lambda x: f"{x:3d}", poly)))
+            last = poly[:]
+            if str(step(diff, poly, 1, 1)) == "break":
+                break
+
+def step(diff, poly, start_x=1,lim=1):
+    n = "~"
+    neg = False
+    while re.match("-?\d+$", n) is None:
+        n = input(": ")
+        if n.lower() in ('q', 'quit'): return "break"
+    n = int(n)
+    if n < 0:
+        neg = True
+        n = abs(n)
+    if n < start_x or poly[n] < lim:
+        return
+    while len(poly) < n + len(diff) + 1:
+        poly.append(0)
+    if neg and all((poly[n+i-start_x] >= diff[i]) or diff[i] <= 0 for i in range(len(diff))):
+        for i in range(len(diff)):
+            poly[n + i - start_x] -= diff[i]
+    elif not neg:
+        for i in range(len(diff)):
+            poly[n + i - start_x] += diff[i]
+
+
+main()

### 2024-08-16 UTA/notes.tex
Added folder: UTA

\documentclass{scrartcl}

\title{Intersection Type Algebras}
\author{Aaron Frye, Andrew Polonsky}

\begin{document}

\section{2024.08.16}

A given set of equations can lead to multiple SR.  These are all equivalent.
\end{document}

### 2024-08-16 UTA/notes.tex
notes updates

@@
 \documentclass{scrartcl}
+
+\usepackage{amsmath}
+\usepackage{amssymb}
 
@@
 \author{Aaron Frye, Andrew Polonsky}
+
+\newcommand{\types}{\mathbb{T}}
 
@@
 A given set of equations can lead to multiple SR.  These are all equivalent.
+
+The \emph{recursive type entailment problem} is as follows.
+Given a set of equations between types $E$ and two types $A$ and $B$,
+determine whether $E \vdash A = B$.
+
+The \emph{unification problem} is: Given two types $A$ and $B$,
+determine whether there exists a substitution $\sigma$
+so that $\vdash A[\sigma] = B[\sigma]$.
+
+The \emph{unification problem up to constraints} is: Given a set of equations $E$,
+and two types $A$ and $B$, determine whether there exists a substitution $\sigma$
+so that $E \vdash A[\sigma] = B[\sigma]$.
+
+The \emph{general satisfiability problem} is as follows.
+
+Given sets of equations $E_1$, $E_2$, determine whether there exists
+a type algebra morphism $h : \types/E_1 \to \types/E_2$.
+
 \end{document}

### 2024-08-21 Relations/Report.tex
Report tex file uploaded. WIP

\documentclass{scrartcl}
% Packages
\usepackage{hyperref}
\usepackage{tikz}
\usepackage{amsmath}
\usepackage{pifont}
\usepackage{mathrsfs}
\usetikzlibrary{arrows.meta, positioning}

\definecolor{darkgreen}{rgb}{0.0, 0.5, 0.0}

\title{Summer 2024 Report}
\author{Sam Arkle}
\date{\today}

\begin{document}

\maketitle

\section{Introduction}
This is a report on the progress I have made during the summer of 2024 working with Dr. Polonsky \footnote{Assisstant Professor, Department of Computer Science, Appalachian State University.}. I have been writing on the topic of relations, working primarily from Term Rewriting Systems (TeReSe) \footnote{(Term Rewriting Systems. (2003). United Kingdom: Cambridge University Press.)}. 
The objective of this work has been to both develop a formal understanding of relations and to build a library in Agda \footnote{\href{https://github.com/DrPolonsky/LAM/tree/main/Relations}{Github repository for this project's code}} that will be used as a foundation to further work in theoretical computer science.
\\
I have been focussed on Chapter 1 of TeReSe which covers abstract reduction systems (ARS) as well as the appendix (sections 1-3) which provides the necessary mathematical background for the rest of the book (e.g. relations, ordinals, inductive definitions and the Knaster-Tarski lemma). Where the book has made use of classical logic I have investigated the possibility of using constructive alternatives.

\section{Relations}

\subsection{Well-foundedness}
\textcolor{red}{Talk about the different types of wellfoundedness, starting with the one given in the book, the reason for thinking it is classical and not constructive, and provide an image showing the relation between the notions of wellfoundedness we have. Talk about future work in this area.}
\\
We have worked with four different notions of well-foundedness in order to explore the connections between them. These four notions each depend on one of the following four definitions:
\begin{enumerate}
    \item accessible \textcolor{red}{For these definitinos is it best to just use the code from agda which is clear, or should we be trying to provide a more 'human' definition to accompany the code?}
    \item inductive predicate
    \item minimal element
    \item non-decreasing index
\end{enumerate}
The four main notions of a relation \textit{R} being well-founded a set \textit{S} we have worked with are:
\begin{enumerate}
    \item \textit{R} is well-founded if every element is \textit{R}-accessible (where an element \textit{x} is \textit{R}-accessible if all elements \textit{R}-below \textit{x}  are themselves \textit{R}-accessible).
    \item \textit{R} is well-founded if every inductive predicate is universally true (where a predicate $\varphi$ is inductive if $\varphi\,x$ is true whenever $\varphi\,y$ is true for all elements $y$ $R$-below $x$).
    \item \textit{R} is well-founded if every non-empty subset of $S$ has a minimal element with respect to $R$.
    \item \textit{R} is well-founded if every sequence contains a non-decreasing index.
\end{enumerate}
Further, we explored weaker variants of these notions of well-foundedness by defining well-foundedness using double negation:
\begin{enumerate}
    \item \textit{R} is well-founded if every element is $\lnot \lnot$  \textit{R}-accessible.
    \item \textit{R} is well-founded if for every inductive predicate $\varphi \; \lnot \lnot \varphi \; x$.
    \item \textit{R} is well-founded if for every non-empty subset of $S$ there is $\lnot \lnot$ a minimal element with respect to $R$.
    \item \textit{R} is well-founded if there is no infinite $R$-decreasing sequence in $S$ (this is the definition of well-foundedness found in TeReSe).
\end{enumerate}

The following graphic illustrates the connections we have found between these definitions and those we are still seeking to find. Green arrows indicate that a definition can be translated into another, red arrows indicate that we believe a translation should be possible but we have not yet found it.

\begin{tikzpicture}[node distance=2cm, auto]
    % Standard definitions
    \node (std1) [draw] {isWFacc};
    \node (std2) [below of=std1, draw] {isWFind};
    \node (std3) [below of=std2, draw] {isWFmin};
    \node (std4) [below of=std3, draw] {isWFseq};

    % Weaker definitions
    \node (weak1) [right of=std1, xshift=4cm, draw] {isWFacc-};
    \node (weak2) [below of=weak1, draw] {isWFind-};
    \node (weak3) [below of=weak2, draw] {isWFmin-};
    \node (weak4) [below of=weak3, draw] {isWFseq-};

    % Arrows
    \draw[->, thick, darkgreen] (std1) -- (weak1);
    \draw[<->, thick, darkgreen] (std1) -- (std2);
    \draw[<->, thick, darkgreen] (weak1) -- (weak2);
    \draw[->, thick, darkgreen] (std2) -- (weak2);
    \draw[->, thick, red] (std2) -- (std3) node[pos=0.5, right, red] {?};
    \draw[->, thick, darkgreen] (weak2) -- (weak3);
    \draw[->, thick, darkgreen] (std3) -- (weak3);
    \draw[->, thick, darkgreen, bend left] (std3) to (std4);
    \draw[->, thick, darkgreen, bend left] (weak3) to (weak4);
    \draw[->, thick, darkgreen] (std4) to (weak4);
    \draw[->, thick, red, bend left] (std4) -- (std3) node[pos=0.5, left, red] {?};
    \draw[->, thick, red, bend left] (weak4) -- (weak3) node[pos=0.5, left, red] {?};
\end{tikzpicture}

As future work we want to know whether the missing reductions can be defined, or what the minimal additional requirements are for making those reductions.

\subsection{Definitions}
\textcolor{red}{Go through some of the main definitions formalised from Terese, focussing on where we have used constructive alternatives to the classically given definitions
Could talk here about omega bounded stuff too!}
\\
One aspect of the project has been working through the definitions, propositions, and theorems in TeReSe and formalising them in Agda. 
For example, in TeReSe the diamond property is defined:
\begin{center}
    $a \in A$ has the \textit{diamond property} if $\forall b, c \in A (c \leftarrow a \rightarrow b \implies \exists d \in A c \rightarrow d \leftarrow b)$. The reduction relation $\rightarrow$ has the \textit{diamond property} if every $a \in A$ has the \textit{diamond property}.
\end{center}
In Agda we have defined the diamond property as:
\begin{flushleft}
    \texttt{\ding{117} : Set}\\
    \texttt{\ding{117} = $\forall a, b, c \rightarrow R_{\alpha} a b \rightarrow R_{\alpha} a c \rightarrow \Sigma[ d \in A ] (R_{\alpha} b d \times R_{\alpha} c d)$}
\end{flushleft}
In formalising the propostions and theorems we also provided solutions to them. \\
The remainder of this section highlights definitions or proofs we hae expressed differently to TeReSe along with an explanation of why we have done so.

\subsubsection{Strongly Normalizing}
\begin{center}
    In TeReSe: $a \in A$ is \textit{strongly normalizing} if every reduction sequence starting from $a$ is finite. The reduciton relation $\rightarrow$ is \textit{strongly normalizing} (SN) if every $a \in A$ is strongly normalizing. 
\end{center}
In Agda we have defined strongly normalizing as:

\begin{flushleft}
    \texttt{data is\_-accessible\_ : $\mathscr{P} A$ where}\\
    \texttt{\ \ \ \ acc : $\forall$ \{x : A\} $\rightarrow$ ($\forall$ y $\rightarrow$ R y x $\rightarrow$ is\_-accessible\_ y) $\rightarrow$ \quad is\_-accessible\_ x}\\
    \texttt{is\_SNacc\_ : $\mathscr{P} A$}\\
    \texttt{is\_SNacc\_ x = is (\textasciitilde R R) -accessible x}\\
    \texttt{is\_SN\_ : $\mathscr{P} A$}\\
    \texttt{is\_SN\_ = is\_SNacc\_}
\end{flushleft}

\subsection{Knaster Tarski}
Go through different proofs Here

\subsection{Newmans lemma}
What it is and the different definitions again

\subsection{}

\end{document}

### 2024-09-05 Relations/Report.tex
recurrence
ARS stuff

@@
 
+\section{Notes from 08.29}
+
+\begin{enumerate}
+  \item Try to ``fix'' CP by changing $R$ into $R^r$
+  \item Finish formulating the ``compactness property".  Two candidates:
+  \begin{itemize}
+    \item ``Every cocone for a given infinite sequence loops back to some point in the sequence"
+    \item ``If an $R^*$-sequence has a cocone then it's constant after some point on.''
+  \end{itemize}
+  \item Add the definition of "recurrent element"
+\end{enumerate}
+
+\section{09.05}
+\begin{enumerate}
+  \item done: WN, UN, RP imply SN (classical)
+  \item need: omega bounded and RP implies SN (classical)
+  \item need: omega bounded and RP implies SN (constructive)
+  \item do we need $s_0 \to^* s_c$ in the proof?
+  \item is $\omega$-bounded implied by WN and the following confluence property:
+  $a \to^* n \in NF$, and $a \to b$ then $b \to^* n $.
+  \item Remark before 1.2? (Exercise 1.3.21)
+  \item Make the first argument to "being a normal form" implicit?
+\end{enumerate}
 \end{document}

### 2024-09-06 Relations/Report.tex
ars

@@
 \end{enumerate}
+
+\newcommand{\RP}{\mathsf{RP}}
+\newcommand{\NF}{\mathsf{NF}}
+\newcommand{\UN}{\mathsf{UN}}
+\newcommand{\UNto}{\mathsf{UN}{\to}}
+\newcommand{\SN}{\mathsf{SN}}
+\newcommand{\WN}{\mathsf{WN}}
+\newcommand{\from}{\leftarrow}
+
+\subsection*{Additional remarks about Theorem 1.2.3.}
+\begin{itemize}
+  \item It seems that part (i) of the theorem can be strengthened to only
+  assume $\UNto(R)$ instead of $\UN(R)$:
+  \[ \WN(R) \land \UNto(R) \to \omega{-}\text{bounded}(R) \tag{i} \]
+  \item The analogue of part (ii) of the theorem is unprovable, namely
+  \[ \omega{-}\text{bounded}(R) \land \RP(R) \to \SN(R) \tag{ii}\]
+  For a countermodel, take the one-element loop $a \to a$.
+
+  (It is both $\omega${-}bounded and satisfies RP.)
+
+  Our hypothesis RP is indeed weaker than ``Inc'' from Terese.
+  \item The goal \texttt{iii-lemma :  $WN(R) \to WCR(R) \to \omega{-}\text{bounded}(R)$}
+  seems either very difficult or impossible.
+
+  Yet, constructing the bound of a given $R$-increasing sequence is key to the proof of
+  (our interpretation of) Theorem 1.2.3(iii), namely that
+  \[ WN(R) \land WCR(R) \land RP(R) \to SN(R) \tag{iii} \]
+  \item Here is a classical proof of this implication.
+
+  Let $R \subseteq A \times A$, and suppose $R$ satisfies WN, WCR, and RP.
+
+  Suppose $R$ is not SN.  Let $a \in A$ be not SN.  By WN, let $n \in \NF$ be
+  such that $a \to^* n$.  By induction on the length of this reduction, the finite sequence
+  of terms comprising it must contain a final term with the property that
+  it is not SN.  (For $n$ is SN, being a normal form, while $a$ is not.)
+
+  $(\star)$ Let this last non-SN term be denoted $b_0$.
+
+  If each single-step $R$-reduct of $b_0$ is SN (so that $b_0 \to x$ implies $x\in \SN$),
+  then $b_0$ would itself be SN --- which it is not, by how it was chosen.
+
+  Thus there exists a $c_0$ with $b_0 \to c_0$, and $c_0 \notin \SN$.
+
+  So we have $c_0 \from b_0 \to m_0$ for some $m_0 \in \SN$. ($m_0$ is the next term after $b_0$ in the reduction $a \to^* n$.)
+
+  By WCR, there exists another element $d_0 \in A$ with $c_0 \to^* d_0 \from^* m_0$.
+
+  Since $m_0 \in \SN$ and this set of terms is closed under reduction, $d_0 \in \SN$ as well.
+
+  Thus $b_0 \to c_0 \to^* d_0$, with $d_0 \in \SN$, and $c_0 \notin \SN$.
+
+  Again, the reduction $c_0 \to^* d_0$ contains a last term that is not in SN.
+
+  Let this term be denoted by $b_1$, and let the next term in the reduction sequence
+  to $d_0$ be denoted $m_1$.
+
+  Now repeat the above process starting at $(\star)$, incrementing all subscripts by 1.
+
+  This generates an infinite reduction sequence
+
+  \[b_0 \to c_0 \to^* b_1 \to c_1 \to^* b_2 \to \cdots \]
+
+  Note that infinitely many terms in this sequence are one reduction step
+  away from a term in $\SN$.
+
+  Moreover, notice that the normal forms of $m_0$, $d_0$, and $m_1$ are the same
+  and equal to $n$, whence the same is true for $m_1$, $d_1$, and $m_2$, etc.
+
+  It follows that, for infinitely many terms in the sequence
+  (namely, all the terms $b_i$), we have $b_i \to^* n$.
+
+  Thus, all terms in the sequence reduce to $n$ and so $n$ is an $\omega$-bound
+  of the sequence.
+
+  By RP, some term $r$ in the sequence is recurrent.
+
+  Since $r \to^* n$ and $r$ is recurrent, also $n \to^* r$.
+
+  But $n$ is a normal form.  So this sequence is empty and $r=n$.
+
+  But $r$ is a term in an infinite reduction sequence, and reduces to its successor.
+
+  This yields a contradiction.
+\end{itemize}
 \end{document}

### 2024-09-11 Relations/Report.tex
Report updated, outline of classical proof in ARS.agda for W N (R) ∧ W CR(R) ∧ RP (R) → SN (R)
Report updates, definitions being added, well founded polished.

@@
 \usepackage{mathrsfs}
+\usepackage{amssymb}
 \usetikzlibrary{arrows.meta, positioning}
@@
 \definecolor{darkgreen}{rgb}{0.0, 0.5, 0.0}
+
+\newcommand{\tto}{\twoheadrightarrow}
 
@@
 \\
-We have worked with four different notions of well-foundedness in order to explore the connections between them. These four notions each depend on one of the following four definitions:
+To date we have investigated the differences between four distinct notions of well-foundedness.
+The make clear the difference between these distinct notions of well-foundedness we first present the following defintiions for a given relation $R$.
 \begin{enumerate}
-    \item accessible \textcolor{red}{For these definitinos is it best to just use the code from agda which is clear, or should we be trying to provide a more 'human' definition to accompany the code?}
-    \item inductive predicate
-    \item minimal element
-    \item non-decreasing index
+    \item \textit{Accessible:} An element $x$ is \textit{R-accessible} if all elements that have an $R$ reduction to $x$ are themselves \textit{R-accessible}.  
+    \item \textit{Inductive predicate:} A predicate $\varphi$ is an inductive predicate if $\varphi \, x$ is true whenever $\varphi$ is true for all elements that have an $R$ reduction to $x$.
+    \item \textit{Minimal element:} An element $x$ is minimal for a given predicate $\varphi$ if $\varphi \, x$ is true and no other element for which $\varphi$ holds has an $R$ reduction to $x$. 
+    \item \textit{Decreasing:} A sequence $s$ is decreasing if every $R$ reduction decreases the size of $n$ (where $n \in \mathbb{N}$).   \textcolor{red}{bad defn. Improve.}
 \end{enumerate}
-The four main notions of a relation \textit{R} being well-founded a set \textit{S} we have worked with are:
+With the above definitions established we define the notions of well-foundedness we have been investigating. For a given relation $R$:
 \begin{enumerate}
-    \item \textit{R} is well-founded if every element is \textit{R}-accessible (where an element \textit{x} is \textit{R}-accessible if all elements \textit{R}-below \textit{x}  are themselves \textit{R}-accessible).
-    \item \textit{R} is well-founded if every inductive predicate is universally true (where a predicate $\varphi$ is inductive if $\varphi\,x$ is true whenever $\varphi\,y$ is true for all elements $y$ $R$-below $x$).
-    \item \textit{R} is well-founded if every non-empty subset of $S$ has a minimal element with respect to $R$.
+    \item \textit{R} is well-founded if every element is \textit{R}-accessible.
+    \item \textit{R} is well-founded if every inductive predicate is universally true.
+    \item \textit{R} is well-founded if every non-empty predicate has a minimal element with respect to $R$.
     \item \textit{R} is well-founded if every sequence contains a non-decreasing index.
 \end{enumerate}
-Further, we explored weaker variants of these notions of well-foundedness by defining well-foundedness using double negation:
+Further, we explored weaker variants of these notions of well-foundedness:
 \begin{enumerate}
     \item \textit{R} is well-founded if every element is $\lnot \lnot$  \textit{R}-accessible.
-    \item \textit{R} is well-founded if for every inductive predicate $\varphi \; \lnot \lnot \varphi \; x$.
-    \item \textit{R} is well-founded if for every non-empty subset of $S$ there is $\lnot \lnot$ a minimal element with respect to $R$.
-    \item \textit{R} is well-founded if there is no infinite $R$-decreasing sequence in $S$ (this is the definition of well-foundedness found in TeReSe).
+    \item \textit{R} is well-founded if for every inductive predicate $\varphi$, $\lnot \lnot \varphi$ is universally true.
+    \item \textit{R} is well-founded if it is not not the case that every non-empty predicate has a minimal element with respect to $R$.
+\textcolor{red}{is there a better way to express this double negation in english?}
+    \item \textit{R} is well-founded if there is no infinite $R$-decreasing sequence (this is the definition of well-foundedness found in TeReSe).
 \end{enumerate}
 
-The following graphic illustrates the connections we have found between these definitions and those we are still seeking to find.
-Green arrows indicate that a definition can be translated into another, red arrows indicate that we believe a translation should be possible but we have not yet found it.
+The following graphic illustrates the implications we have found between these definitions and those we are still seeking to find.
+Green arrows indicate that one definition implies another, red arrows indicate that we believe an implication should be possible but we have not yet found it.
 
+\begin{center}
   \begin{tikzpicture}[node distance=2cm, auto]
@@
 
+    % Double negation definitions
+    \node (dn1) [right of=std1, xshift=2cm, draw] {$\lnot \lnot$ isWFacc};
+    \node (dn2) [right of=std2, xshift=2cm, draw] {$\lnot \lnot$ isWFind};
+    \node (dn3) [right of=std3, xshift=2cm, draw] {$\lnot \lnot$ isWFmin};
+    \node (dn4) [right of=std4, xshift=2cm, draw] {$\lnot \lnot$ isWFseq};
+
     % Weaker definitions
-    \node (weak1) [right of=std1, xshift=4cm, draw] {isWFacc-};
-    \node (weak2) [below of=weak1, draw] {isWFind-};
-    \node (weak3) [below of=weak2, draw] {isWFmin-};
-    \node (weak4) [below of=weak3, draw] {isWFseq-};
+    \node (weak1) [right of=dn1, xshift=2cm, draw] {isWFacc-};
+    \node (weak2) [right of=dn2, xshift=2cm, draw] {isWFind-};
+    \node (weak3) [right of=dn3, xshift=2cm, draw] {isWFmin-};
+    \node (weak4) [right of=dn4, xshift=2cm, draw] {isWFseq-};
 
     % Arrows
-    \draw[->, thick, darkgreen] (std1) -- (weak1);
+    \draw[->, thick, darkgreen] (std1) -- (dn1);
+    \draw[->, thick, darkgreen] (dn1) -- (weak1);
     \draw[<->, thick, darkgreen] (std1) -- (std2);
+    \draw[->, thick, darkgreen] (std2) -- (dn2);
+    \draw[->, thick, darkgreen] (dn2) -- (weak2);
     \draw[<->, thick, darkgreen] (weak1) -- (weak2);
-    \draw[->, thick, darkgreen] (std2) -- (weak2);
     \draw[->, thick, red] (std2) -- (std3) node[pos=0.5, right, red] {?};
+    \draw[->, thick, darkgreen] (std3) -- (dn3);
+    \draw[->, thick, darkgreen] (dn3) -- (weak3);
     \draw[->, thick, darkgreen] (weak2) -- (weak3);
-    \draw[->, thick, darkgreen] (std3) -- (weak3);
     \draw[->, thick, darkgreen, bend left] (std3) to (std4);
     \draw[->, thick, darkgreen, bend left] (weak3) to (weak4);
-    \draw[->, thick, darkgreen] (std4) to (weak4);
+    \draw[->, thick, darkgreen] (std4) -- (dn4);
+    \draw[->, thick, darkgreen] (dn4) -- (weak4);
     \draw[->, thick, red, bend left] (std4) -- (std3) node[pos=0.5, left, red] {?};
@@
   \end{tikzpicture}
+\end{center}
 
-As future work we want to know whether the missing reductions can be defined, or what the minimal additional requirements are for making those reductions.
+  As future work we want to know whether the missing implications can be found, or what the minimal additional requirements are for making those implications.
 
@@
 Could talk here about omega bounded stuff too!}
-\\
-One aspect of the project has been working through the definitions, propositions, and theorems in TeReSe and formalising them in Agda.
-For example, in TeReSe the diamond property is defined:
+
+The most interesting work we have carried out in investigating Chapter 1 of TeReSe has resulted from trying to provide constructive proofs for Newman's lemma, the Knaster-Tarski lemma, Theorem 1.2.2 and Theorem 1.2.3.
+Before exploring those proofs the following definitions are essential.
+\begin{itemize}
+  \item \textit{ARS:} An abstract reduction system (ARS) is a framework which we use to explore reduction relations on a set of objects.  
+\end{itemize}
+Throughout these definitions we use $A$ to denote the set which contains all the objects that can be reduced and $\to$ to denote a binary relation on $A$.
+This relation represents the reduction process.
+For example, if we let $\to$ be the relation of being 'less than' ($<$) then $4 \to 2$.
+\textcolor{red}{Right?}
+
+We use $\to$ for a single-step reduction and $\tto$ for a multi-step reduction.
+
+\begin{itemize}
+  \item \textit{Weakly confluent:} A reduction relation is weakly confluent (AKA weakly Church-Rosser (WCR)) if all single-step reductions from a given element can always converge via multi-step reductions to some common reduct.
+\end{itemize}
 \begin{center}
-    $a \in A$ has the \textit{diamond property} if $\forall b, c \in A (c \leftarrow a \rightarrow b \implies \exists d \in A c \rightarrow d \leftarrow b)$.
-The reduction relation $\rightarrow$ has the \textit{diamond property} if every $a \in A$ has the \textit{diamond property}.
+  \begin{tikzpicture}[node distance=2cm, auto]
+    % Nodes
+    \node (top) {a};
+    \node (left) [below left of=top] {b};
+    \node (right) [below right of=top] {c};
+    \node (bottom) [below of=top, yshift=-1cm] {d};
+
+    % Arrows
+    \draw[->] (top) -- (left);
+    \draw[->] (top) -- (right);
+    \draw[->>] (left) -- (bottom);
+    \draw[->>] (right) -- (bottom);
+\end{tikzpicture}
 \end{center}
-In Agda we have defined the diamond property as:
-\begin{flushleft}
-    \texttt{\ding{117} : Set}\\
-    \texttt{\ding{117} = $\forall a, b, c \rightarrow R_{\alpha} a b \rightarrow R_{\alpha} a c \rightarrow \Sigma[ d \in A ] (R_{\alpha} b d \times R_{\alpha} c d)$}
-\end{flushleft}
-In formalising the propostions and theorems we also provided solutions to them. \\
-The remainder of this section highlights definitions or proofs we hae expressed differently to TeReSe along with an explanation of why we have done so.
+
+\begin{itemize}
+  \item \textit{Confluent} A reduction relation is confluent (AKA Church-Rosser (CR)) if all multi-step redctions from a given element can always converge via multi-step reductions to some common reduct.
+\end{itemize}
+\begin{center}
+  \begin{tikzpicture}[node distance=2cm, auto]
+    % Nodes
+    \node (top) {a};
+    \node (left) [below left of=top] {b};
+    \node (right) [below right of=top] {c};
+    \node (bottom) [below of=top, yshift=-1cm] {d};
+
+    % Arrows
+    \draw[->>] (top) -- (left);
+    \draw[->>] (top) -- (right);
+    \draw[->>] (left) -- (bottom);
+    \draw[->>] (right) -- (bottom);
+\end{tikzpicture}
+\end{center}
 
@@
 \end{center}
-In Agda we have defined strongly normalizing as:
-
-\begin{flushleft}
-    \texttt{data is\_-accessible\_ : $\mathscr{P} A$ where}\\
-    \texttt{\ \ \ \ acc : $\forall$ \{x : A\} $\rightarrow$ ($\forall$ y $\rightarrow$ R y x $\rightarrow$ is\_-accessible\_ y) $\rightarrow$ \quad is\_-accessible\_ x}\\
-    \texttt{is\_SNacc\_ : $\mathscr{P} A$}\\
-    \texttt{is\_SNacc\_ x = is (\textasciitilde R R) -accessible x}\\
-    \texttt{is\_SN\_ : $\mathscr{P} A$}\\
-    \texttt{is\_SN\_ = is\_SNacc\_}
-\end{flushleft}
-
-\subsection{Knaster Tarski}
 Go through different proofs Here
@@
   \[ \WN(R) \land \UNto(R) \to \omega{-}\text{bounded}(R) \tag{i} \]
+  \textcolor{red}{(See ARS.agda i+)}
   \item The analogue of part (ii) of the theorem is unprovable, namely
@@
   This yields a contradiction.
+
 \end{itemize}
+\subsection{09.10 (midweek updata)}
+Is it possible to weaken RP? A possible suggestion:
+
+$RP- :: \omega-bounded \to  \exists i. b \to^* f i$
+
+Does:
+
+$RP \to RP-$
+
+Does:
+
+$RP- \land \; WCR \to RP$
+
+(what other property with $RP-$ would give us $RP$?).
+
 \end{document}

### 2024-09-12 Relations/Report.tex
ARS

@@
 \newcommand{\tto}{\twoheadrightarrow}
+\newcommand{\sse}{\subseteq}
+\newcommand{\bset}{\mathbf{Set}}
+
+\newcommand{\sacomment}[1]{\textcolor{red}{#1}}
+\newcommand{\apcomment}[1]{\textcolor{blue}{#1}}
+
+\usepackage{amsthm}
+
+\newtheorem{thm}{Theorem}
+\newtheorem{dfn}[thm]{Definition}
+\newtheorem{prop}[thm]{Proposition}
+\newtheorem{cor}[thm]{Corollary}
+\newtheorem{lemma}[thm]{Lemma}
+\newtheorem{rmk}[thm]{Remark}
+\newtheorem{expl}[thm]{Example}
+\newtheorem{notn}[thm]{Notation}
+%\theoremstyle{nonumberplain}
+%\theoremsymbol{\Box}
+% \newtheorem{proof}{Proof}
 
@@
 \subsection{Well-foundedness}
-\textcolor{red}{Talk about the different types of wellfoundedness, starting with the one given in the book, the reason for thinking it is classical and not constructive, and provide an image showing the relation between the notions of wellfoundedness we have.
+\sacomment{Talk about the different types of wellfoundedness, starting with the one given in the book, the reason for thinking it is classical and not constructive, and provide an image showing the relation between the notions of wellfoundedness we have.
 Talk about future work in this area.}
-\\
-To date we have investigated the differences between four distinct notions of well-foundedness.
-The make clear the difference between these distinct notions of well-foundedness we first present the following defintiions for a given relation $R$.
+
+\apcomment{Mention that, for a set $A$, we will use "subset of $A$" and "predicate on $A$" interchangeably,
+with subsets being represented in the Agda code using predicates, which are in turn formalized as
+dependent types over $A$, i.e. maps $\varphi : A \to \bset$ }
+
+Working in constructive logic introduces subtle differences between notions of well-foundedness of relations
+which are not present in classical logic.
+In our investigation, we have focused on four distinct definitions of well-foundedness, with minor variations of each.
+To spell these out, we first define some preliminary notions.
+% The make clear the difference between these distinct notions of well-foundedness we first present the following defintiions for a given relation $R$.
+
+\begin{dfn} Let $A$ be a set and $R \sse A \times A$ be a relation.
 \begin{enumerate}
-    \item \textit{Accessible:} An element $x$ is \textit{R-accessible} if all elements that have an $R$ reduction to $x$ are themselves \textit{R-accessible}.  
-    \item \textit{Inductive predicate:} A predicate $\varphi$ is an inductive predicate if $\varphi \, x$ is true whenever $\varphi$ is true for all elements that have an $R$ reduction to $x$.
-    \item \textit{Minimal element:} An element $x$ is minimal for a given predicate $\varphi$ if $\varphi \, x$ is true and no other element for which $\varphi$ holds has an $R$ reduction to $x$. 
-    \item \textit{Decreasing:} A sequence $s$ is decreasing if every $R$ reduction decreases the size of $n$ (where $n \in \mathbb{N}$).   \textcolor{red}{bad defn. Improve.}
+  \item Let $\phi \sse A$.  An element $x$ is $R$-minimal for $\varphi$ if $\varphi(x)$ is true and no other element for which $\varphi$ holds is $R$-related to $x$.
+  \item An element $x \in A$ is \textit{$R$-accessible} if every element $R$-related to $x$ is \textit{$R$-accessible}.
+(This should be understood as an inductive definition, with base case consisting of $R$-minimal elements for the whole of $A$.)
+    \item A predicate $\varphi$ on $A$ is \emph{inductive} if it holds on a given element $x \in A$ whenever it holds on all elements $R$-related to $x$:
+    \[ (\forall y. Ryx \to \phi(y)) \to \phi(x) \]
+    \item A sequence $s = (s_0,s_1,\dots)$ of elements of $A$ is $R$-decreasing
+    if every element is related to its predecessor.  That is, $Rs_{n+1}s_n$ for all $n$.
 \end{enumerate}
+\end{dfn}
 With the above definitions established we define the notions of well-foundedness we have been investigating. For a given relation $R$:

### 2024-09-19 Relations/RewritingQs.tex
ARS

--- 2024-07-12 ARS/Rewriting.tex
@@
 \begin{document}
+
+\section{2024.09.12}
+\begin{itemize}
+  \item Investigate \texttt{iii-lemma}.  (Is it false, or is there a classical proof?)
+  (No constructive proof?)
+  \item Look at variations of RP.
+  \item What happens if properties involving sequences are reformulated for
+  $R^r$? (Cannot decide whether the given sequence is finite or infinite.)
+  \item Look at RP- and WCR implies RP!
+  \item Can "sequential" properties like RP, RP-, isWFseq, isWFseq-, $\omega$-bounded, etc.,
+  be related to the cofinality property.
+\end{itemize}
 

### 2024-09-20 Relations/Report.tex

@@
 with subsets being represented in the Agda code using predicates, which are in turn formalized as
-dependent types over $A$, i.e. maps $\varphi : A \to \bset$ }
+dependent types over $A$, i.e. maps $\phi : A \to \bset$ }
 
@@
 \begin{enumerate}
-  \item Let $\phi \sse A$.  An element $x$ is $R$-minimal for $\varphi$ if $\varphi(x)$ is true and no other element for which $\varphi$ holds is $R$-related to $x$.
+  \item Let $\phi$ be a predicate on $A$. An element $x \in A$ is $R$-minimal for $\phi$ if $\phi(x)$ is true and no other element for which $\phi$ holds is $R$-related to $x$.
   \item An element $x \in A$ is \textit{$R$-accessible} if every element $R$-related to $x$ is \textit{$R$-accessible}.
 (This should be understood as an inductive definition, with base case consisting of $R$-minimal elements for the whole of $A$.)
-    \item A predicate $\varphi$ on $A$ is \emph{inductive} if it holds on a given element $x \in A$ whenever it holds on all elements $R$-related to $x$:
+    \item A predicate $\phi$ on $A$ is \emph{inductive} if it holds on a given element $x \in A$ whenever it holds on all elements $R$-related to $x$:
     \[ (\forall y. Ryx \to \phi(y)) \to \phi(x) \]
@@
 \end{dfn}
-With the above definitions established we define the notions of well-foundedness we have been investigating. For a given relation $R$:
+With the above definitions established we define the notions of well-foundedness we have been investigating. 
+\begin{dfn} \hfil
   \begin{enumerate}
@@
   \end{enumerate}
-Further, we explored weaker variants of these notions of well-foundedness:
+\end{dfn}
+  Further, we explored weaker variants of these notions of well-foundedness.
+  \begin{dfn} \hfil
     \begin{enumerate}
       \item \textit{R} is well-founded if every element is $\lnot \lnot$  \textit{R}-accessible.
-    \item \textit{R} is well-founded if for every inductive predicate $\varphi$, $\lnot \lnot \varphi$ is universally true.
+      \item \textit{R} is well-founded if for every inductive predicate $\phi$, $\lnot \lnot \phi$ is universally true.
       \item \textit{R} is well-founded if it is not not the case that every non-empty predicate has a minimal element with respect to $R$.
@@
 
+\end{dfn}
 The following graphic illustrates the implications we have found between these definitions and those we are still seeking to find.
@@
 
-The most interesting work we have carried out in investigating Chapter 1 of TeReSe has resulted from trying to provide constructive proofs for Newman's lemma, the Knaster-Tarski lemma, Theorem 1.2.2 and Theorem 1.2.3.
+The most interesting work we have carried out in investigating Chapter 1 of TeReSe has resulted from trying to provide constructive proofs for Newman's lemma, the Knaster-Tarski lemma, theorem 1.2.2 and theorem 1.2.3.
 Before exploring those proofs the following definitions are essential.
-\begin{itemize}
-  \item \textit{ARS:} An abstract reduction system (ARS) is a framework which we use to explore reduction relations on a set of objects.
-\end{itemize}
-Throughout these definitions we use $A$ to denote the set which contains all the objects that can be reduced and $\to$ to denote a binary relation on $A$.
+\begin{dfn}
+  An abstract reduction system (\emph{ARS}) is a framework which we use to explore reduction relations on a set of objects.
+\end{dfn}
+Throughout these definitions we use $A$ to denote the set and $\to$ to denote a binary relation on $A$.
 This relation represents the reduction process.
-For example, if we let $\to$ be the relation of being 'less than' ($<$) then $4 \to 2$.
+For example, if we specify $\to$ as the relation of being 'less than' ($<$) then $4 \to 2$.
 \textcolor{red}{Right?}
@@
 
-\begin{itemize}
-  \item \textit{Weakly confluent:} A reduction relation is weakly confluent (AKA weakly Church-Rosser (WCR)) if all single-step reductions from a given element can always converge via multi-step reductions to some common reduct.
-\end{itemize}
+\begin{dfn}
+    A reduction relation is \emph{weakly confluent} (AKA weakly Church-Rosser (WCR)) if all single-step reductions from a given element can always converge via multi-step reductions to some common reduct.
+\end{dfn}
 \begin{center}
@@
 
-\begin{itemize}
-  \item \textit{Confluent} A reduction relation is confluent (AKA Church-Rosser (CR)) if all multi-step redctions from a given element can always converge via multi-step reductions to some common reduct.
-\end{itemize}
+\begin{dfn}
+    A reduction relation is \emph{confluent} (AKA Church-Rosser (CR)) if all multi-step redctions from a given element can always converge via multi-step reductions to some common reduct.
+\end{dfn}
 \begin{center}
@@
 \end{center}
+
+\begin{dfn}
+
+\end{dfn}
 

### 2024-09-24 Relations/CounterExamples.tex
Added a counterexamples file

\documentclass{article}
\usepackage{tikz-cd}

\title{Counterexamples in Mathematical Relations}
\author{}
\date{}

\begin{document}

\maketitle

\section{Introduction}
This document contains diagrams of counterexamples commonly encountered when exploring the properties of mathematical relations.

\section{Counterexamples}

\subsection{Counterexample 1}
\begin{center}

    \begin{tikzcd}[node distance=2cm, auto]
        % Nodes
        \node (a) {a};
        \node (b) [right of=a, xshift=1cm] {b};
        \node (c) [right of=b, xshift=1cm] {c};
        \node (d) [right of=c, xshift=1cm] {d};

        % Arrows
        \draw[->] (b) to [bend left] (c);
        \draw[->] (c) to [bend left] (b);
        \draw[->] (b) -- (a);
        \draw[->] (c) -- (d);
    \end{tikzcd}

\end{center}
Counterexample to:
\begin{itemize}
    \item WCR $\to$ CR
    \item \mbox{WCR R $\to$ $\forall$ a b $\to$ is R -NF b $\to$ (R *) a b $\to$ $\forall$ c $\to$ (R *) a c $\to$ (R *) c b}
\end{itemize}

\subsection{Counterexample 2}
\begin{center}
    \begin{tikzcd}
        % Nodes
        \node (x) {x};
        \node (n) [below left of=x, xshift=-1cm, yshift=-1cm] {n \in NF};
        \node (y) [below right of=x, xshift=1cm, yshift=-1cm] {y};
        \node (z) [below of=y, yshift=-1cm] {z};

        % Arrows
        \draw[->>] (x) -- (n);
        \draw[->>] (x) -- (y);
        \draw[->] (y) to [bend left] (z);
        \draw[->] (z) to [bend left] (y);
    \end{tikzcd}
\end{center}

Counterexample to:
\begin{itemize}
    \item  $\forall$ x $\to$ is R-WN x $\to$ $\forall$ y $\to$ (R *) x y $\to$ is R-WN y

\end{itemize}

\end{document}

### 2024-09-25 UTA/notes.tex

@@
 \begin{document}
+
+\section{2024.09.12}
+
+Questions we still need to figure out:
+\begin{itemize}
+  \item What to do about reflexive constraints?
+  \item What if the list of types equal to the variable is empty?
+  Should its solution be $\top$?
+  \item If $e = e \to e$ is the "terminal" type algebra
+  (any algebra can be mapped to it), admitting solution of any equation,
+  does having a constraint like that in a given system mean we can simulate
+  $\top = e$?
+  \item If we have $e = e \to e$, and we also have a constraint $c = e \to c$,
+  this is like saying $c = \top \to c$.  And $d = d \to e$ is "equivalent" to
+   $d = d \to \top$?  Does this imply that every term can be typed as $d$ as well?
+   (Probably the answer is no.)
+   \item Supposing we substitute every variable that we can,
+   being left with a system in which every type a variable is constrained to,
+   contains that variable.  This might not yet be the proper SR, because we
+   might still need to equate individual types in the list for each variable.
+\end{itemize}
 

### 2024-10-10 Relations/CounterExamples.tex
counterexamples

@@
 
+\subsection{ARS in Agda}
+Important counterexamples:
+\begin{enumerate}
+  \item $a,b,c,d$ with sinks $a$ and $d$ and a 2-cycle between $b$ and $c$.
+  Counterexample to:
+  \begin{itemize}
+      \item WCR and WN implies CR.
+  \end{itemize}
+  \item Loop $a \to a$.
+  Counterexample to:
+  \begin{itemize}
+    \item $\omega$-bounded and RP implies SN
+    \item $\omega$-bounded and RP implies WN
+  \end{itemize}
+  \item Infinite sequence $a_0 \to a_1 \to \cdots$. Falsifies:
+  \begin{itemize}
+    \item $WN$
+    \item $\omega$-bounded
+    \item $WCR \to WN$
+    \item $CR \to WN$
+    \item $CR, CP \to WN$
+    \item $CR, CP \to \omega$-bounded
+  \end{itemize}
+  \item Infinite sequence $a_0 \to a_1 \to \cdots$ with a colimit $a_\infty$,
+  with each $a_n \to a_\infty$ and $a_\infty$ a normal form.
+  \item Infinite sequence $a_0 \to a_1 \to \cdots$, together with links
+  $a_n \to a_0$, for each $n$.
+  \item The combination of the last two.
+  Counterexample to
+  \begin{itemize}
+    \item RP
+  \end{itemize}
+  \item An ``infinite haircomb''. Infinite sequence $a_0 \to a_1 \to \cdots$, together with
+  a disjoint, discrete set $b_0, b_1, \dots$, and links $a_n \to b_n$.
+  Counterexample to:
+  \begin{itemize}
+    \item $WN\to WCR$
+    \item $WN \to SN$
+  \end{itemize}
+  \item A variation of the above with backlinks $a_n \to a_0$ for all $n$.
+\end{enumerate}
+
 \end{document}

### 2024-10-10 Relations/RewritingQs.tex
ARS progress

@@
 
+\usepackage{xcolor}
+
 \begin{document}
+
+\section{2024.10.10}
+
+\begin{itemize}
+  \item Look at restricting WFmin to $\lnot\lnot$-closed predicates
+  \item Status of important hypotheses:
+    \begin{itemize}
+      \item Deciding whether a given element $x$ reduces to a given element $y$
+      (Is $R$ itself decidable?)
+      \item Deciding whether a given element $x$ reduces to some element $y$
+      (Is being an $R$-normal form decidable?)
+
+      {\textcolor{red}{This is needed to show that SN $\Rightarrow$ WN.}}
+
+      \item If a given element $x$ is \emph{not} a normal form,
+      exhibiting some element $y$ that it reduces to.
+      (This is related to DeMorgan/Markov/etc. properties that came up in WF file.)
+
+      \item Does UN-lemma \emph{require} the decidability assumption?
+    \end{itemize}
+  \item META questions: Which of the ARS theorems can be made ``local/pointwise'',
+  for example,
+  \begin{itemize}
+    \item NL+: $WCR(R) \land SN(x) \to CR(x)$?  (Yes?)
+    \item NL++: $WCR(x) \land SN(x) \to CR(x)$? (No.)
+  \end{itemize}
+  \item When time permits, uniformize the notation (variable names, etc.) to the extent possible.
+\end{itemize}
+
+\section{2024.09.19}
+
+TODO item: Compile a list of counterexamples
 
@@
    Markov's principle, etc.
+
+   \item (2024.10.10) Is being $R$-WN inductive?
+   \item (2024.10.10) Does $R$ being finitely branching imply
+   that, for an inductive $\phi$, if $\lnot \phi(x)$ then
+   $\exists y. Rxy \land \lnot \phi(y)$?
+
 \end{enumerate}

### 2024-10-23 Relations/CounterExamples.tex
New counterexample added and expanded on which proofs are relevant for each counterexample.

@@
 \usepackage{tikz-cd}
+\usepackage{amsmath}
+\usepackage{mathrsfs}
+
+\usetikzlibrary{positioning,shapes.geometric,fit}
 
@@
 \begin{itemize}
-    \item  $\forall$ x $\to$ is R-WN x $\to$ $\forall$ y $\to$ (R *) x y $\to$ is R-WN y
+    \item WN$\downarrow\subseteq$WN :  $\forall$ x $\to$ is R-WN x $\to$ $\forall$ y $\to$ (R *) x y $\to$ is R-WN y
+    \item WN$\downarrow$UN$\rightarrow\subseteq$WN :
+
+    UN$\rightarrow\,$R $\to \forall$ x $\to$ is R-WN x $\to$ $\forall$ y $\to$ (R *) x y $\to$ is R-WN y
+
+    \textcolor{red}{SA: The above is a bit messy, can we make it cleaner?}
+    \item $\forall$ (R : $\mathscr{R}$ A) $\to$ $\forall$ is R -WN x $\to$ is R -UN x $\to$ is R -CR x
 
@@
 
+\subsection{Counterexample 3}
+\begin{center}
+  \begin{tikzpicture}
+      % Define the nodes inside the region f
+      \node (f0) at (0, 0) {$f_0$};
+      \node (f1) at (1, 0) {$f_1$};
+      \node (fi) at (3, 0) {$f_i$};
+      \node (fi+1) at (4, 0) {$f_{i+1}$};
+      \node (dots) at (2, 0) {$...$};
+      \node (dots2) at (5, 0) {$...$};
+
+      % Draw the arrows between the nodes inside the region f
+      \draw[->] (f0) -- (f1);
+      \draw[->] (f1) -- (dots);
+      \draw[->] (dots) -- (fi);
+      \draw[->] (fi) -- (fi+1);
+      \draw[->] (fi+1) -- (dots2);
+
+      % Define the region f
+      \node[draw, ellipse, fit=(f0) (dots2), label=left:$f$] {};
+
+      % Define the nodes outside the region f
+      \node (a) [below=of fi, yshift=-.5cm] {\parbox{2cm}{\centering $a$ \\ $\omega-bound$}};
+      \node (y) [above right=of fi, yshift=.5cm] {$y$};
+
+      % Draw the arrows between the nodes inside and outside the region f
+      \draw[->>] (fi) -- (a);
+      \draw[->>] (fi+1) -- (a);
+      \draw[->>] (dots2) -- (a);
+      \draw[->>] (y) -- (fi);
+  \end{tikzpicture}
+\end{center}
+Counterexample to: 
+\begin{itemize}
+  \item RP-$\to$RP
+  \item RP-$\land$WCR$\to$RP
+\end{itemize}
 \subsection{ARS in Agda}

### 2024-10-23 Relations/Report.tex
wf-stuff
Updated WF graph

@@
 \newcommand{\bset}{\mathbf{Set}}
+\newcommand{\nat}{\mathbb{N}}
 
@@
     \draw[->, thick, darkgreen] (std1) -- (dn1);
+    \draw[->, thick, darkgreen] (std1.west) to[out=180, in=90, bend right] (std4);
     \draw[->, thick, darkgreen] (dn1) -- (weak1);
@@
 
+\section{Classical Principles}
+Principles we are considering
+\begin{itemize}
+  \item Decidability of equality on $A$
+  \item Decidability of the relation $R$
+  \item When relevant, decidability of the given precicate $P$
+  \item Not-not-closure of being accessible
+  \item Not-not-closure of $R$
+  \item Not-not-closure of $P$
+  \item Decidability of whether a given element is an $R$-normal form
+  \item When relevant, local/element-wise versions of the above
+  \item Markov's principle:
+  \begin{itemize}
+    \item In $wfMin_0 \to wfSeq$.
+
+    Given a sequence $s : \nat \to A$, let $E(a) = \exists n \in \nat. s n \equiv a$.
+
+    Need: $\forall a. \lnot\lnot E(a) \to E(a)$, i.e.,
+    \[\lnot\lnot \big(\exists n \in \nat. s n \equiv a\big)
+          \to \big(\exists n \in \nat. s n \equiv a\big)\]
+
+  \end{itemize}
+\end{itemize}
+
 \end{document}

### 2024-10-31 Relations/RewritingQs.tex
ARS-stuff
ARSwork

@@
 
+\usepackage{amssymb}
+\usepackage{mathrsfs}
 \usepackage{xcolor}
@@
 \begin{document}
+
+\textbf{Primary Goal: A technical report that focuses on
+Abstract Rewriting in Constructive Setting }
+
+\section{2024.10.31}
+
+Rewriting properties.
+Elementwise
+\begin{itemize}
+  \item NF
+  \item WN
+  \item SN
+  \item WCR
+  \item CR
+  \item NFP
+  \item UN$\to$
+  \item UN
+  \item RP
+  \item RP$-$
+  \item $\omega$-bound
+  \item Recurrent
+  \item CP (Cofinality property)
+  \item FB (Finite branching of rewrite steps)
+  \item DominatedByWF (Needed?)
+  \item Define WNFP to be:
+  \[\forall a b c \to b \in NF \to a R^* b \to a R^* c \to c R^* b \]
+  \item Does WNFP and WN imply CR?  Looks like it!
+  \item Another interesting one? $WN^*$: hereditarily $WN$ ($WN$ for the reduction graph starting from a given element $x$.)
+
+  Could even consider $SN^*$, $CR^*$ etc.
+\end{itemize}
+Most of these properties $P$ have a ``global'' version $P^\forall$, asserting that $\forall x. P(x)$ holds.
+
+Other properties that show up in classical ARS theory:
+\begin{itemize}
+  \item Inc
+  \item Ind
+  \item $\mathrm{CR}^{\le 1}$
+\end{itemize}
+Want to discuss these, and why we may or may not include them in our
+development.
+
+Outline of the document:
+\begin{enumerate}
+  \item Create a diagram with implications between these, and
+  combinations of these, similar to the one in TeReSe.
+  \item Formalization of valid implications
+  \item Counterexamples: Compile a list/chart/graph of those relationships
+  which can be disproved. (A big part!!)
+  \item A list of classical properties, and elaboration of their meaning
+  and whether it's reasonable to assume them in a rewriting context.
+  (Discuss each, and its role in ARS theory.)
+  \item Well-foundedness: different constructive formulations, and relationships between them
+  \item ``Guide'' to the formalization code, GitHub repo
+  \item Discussion of open problems (Add a subsection of these at the end of each section?)
+  \item Conclusion
+\end{enumerate}
+
+\section{Established implications:}
+
+\begin{itemize}
+  \item SN implies $\omega$-bounded
+\end{itemize}
 
@@
 
+\section{Open problems}
+
+\begin{itemize}
+  \item The infinite haircomb refutes $WN \land RP \to \omega$-bounded.  But it is not WCR.
+
+  So, does $WN, RP, WCR$ imply $\omega$-bounded?
+  Answer: yes, that is what we have proved classically.
+
+  \item Wait, does RP- actually imply RP????
+
+  \item RP- and $\omega$-bounded implies RP?
+  \item RP- and WCR imply RP?
+  \item
+  \[ WNg \land UN \to CRelem :
+  \forall (R : \mathscr{R} A) \to WN R \to \forall x \to is R -UN x \to is R -CR x \]
+  \item $WN R \to UN R \to \omega-bdd R \to SN R$ (1.2.3.ii-)
+\end{itemize}
+
 \end{document}

### 2024-11-07 Relations/notes.tex
created notes.tex to merge various scattered bullet points

--- 2024-10-31 Relations/RewritingQs.tex
@@
 
-\usepackage{amssymb}
-\usepackage{mathrsfs}
-\usepackage{xcolor}
+\input{macros}
 
@@
 
-\textbf{Primary Goal: A technical report that focuses on
-Abstract Rewriting in Constructive Setting }
+This document aims to bring together the various notes from report, rewriting qs, and counterexamples.
 
-\section{2024.10.31}
-
+\section{Definitions and implications}
 Rewriting properties.
@@
 development.
-
-Outline of the document:
-\begin{enumerate}
-  \item Create a diagram with implications between these, and
-  combinations of these, similar to the one in TeReSe.
-  \item Formalization of valid implications
-  \item Counterexamples: Compile a list/chart/graph of those relationships
-  which can be disproved. (A big part!!)
-  \item A list of classical properties, and elaboration of their meaning
-  and whether it's reasonable to assume them in a rewriting context.
-  (Discuss each, and its role in ARS theory.)
-  \item Well-foundedness: different constructive formulations, and relationships between them
-  \item ``Guide'' to the formalization code, GitHub repo
-  \item Discussion of open problems (Add a subsection of these at the end of each section?)
-  \item Conclusion
-\end{enumerate}
-
+\newpage
+\section{Formalization of implications}
 \section{Established implications:}
@@
 
-\section{2024.10.10}
+\newpage
+\section{Counterexamples}
+\subsection{Counterexample 1}
+\begin{center}
 
+    \begin{tikzcd}[node distance=2cm, auto]
+        % Nodes
+        \node (a) {a};
+        \node (b) [right of=a, xshift=1cm] {b};
+        \node (c) [right of=b, xshift=1cm] {c};
+        \node (d) [right of=c, xshift=1cm] {d};
+
+        % Arrows
+        \draw[->] (b) to [bend left] (c);
+        \draw[->] (c) to [bend left] (b);
+        \draw[->] (b) -- (a);
+        \draw[->] (c) -- (d);
+    \end{tikzcd}
+
+\end{center}
+Counterexample to:
 \begin{itemize}
-  \item Look at restricting WFmin to $\lnot\lnot$-closed predicates
-  \item Status of important hypotheses:
-    \begin{itemize}
-      \item Deciding whether a given element $x$ reduces to a given element $y$
-      (Is $R$ itself decidable?)
-      \item Deciding whether a given element $x$ reduces to some element $y$
-      (Is being an $R$-normal form decidable?)
-
-      {\textcolor{red}{This is needed to show that SN $\Rightarrow$ WN.}}
-
-      \item If a given element $x$ is \emph{not} a normal form,
-      exhibiting some element $y$ that it reduces to.
-      (This is related to DeMorgan/Markov/etc. properties that came up in WF file.)
-
-      \item Does UN-lemma \emph{require} the decidability assumption?
-    \end{itemize}
-  \item META questions: Which of the ARS theorems can be made ``local/pointwise'',
-  for example,
-  \begin{itemize}
-    \item NL+: $WCR(R) \land SN(x) \to CR(x)$?  (Yes?)
-    \item NL++: $WCR(x) \land SN(x) \to CR(x)$? (No.)
-  \end{itemize}
-  \item When time permits, uniformize the notation (variable names, etc.) to the extent possible.
+    \item WCR $\to$ CR
+    \item WCR and WN $\to$ CR
+    \item WCR and WN $\to$ SN
+    \item \mbox{WCR R $\to$ $\forall$ a b $\to$ is R -NF b $\to$ (R *) a b $\to$ $\forall$ c $\to$ (R *) a c $\to$ (R *) c b}
+    \item IOW, WCR $\to$ WNFP
 \end{itemize}
 
-\section{2024.09.19}
+\subsection{Counterexample 2}
+\begin{center}
+    \begin{tikzcd}
+        % Nodes
+        \node (x) {x};
+        \node (n) [below left of=x, xshift=-1cm, yshift=-1cm] {n \in NF};
+        \node (y) [below right of=x, xshift=1cm, yshift=-1cm] {y};
+        \node (z) [below of=y, yshift=-1cm] {z};
 
-TODO item: Compile a list of counterexamples
+        % Arrows
+        \draw[->>] (x) -- (n);
+        \draw[->>] (x) -- (y);
+        \draw[->] (y) to [bend left] (z);
+        \draw[->] (z) to [bend left] (y);
+    \end{tikzcd}
+\end{center}
 
-\section{2024.09.12}
+Counterexample to:
 \begin{itemize}
-  \item Investigate \texttt{iii-lemma}.  (Is it false, or is there a classical proof?)
-  (No constructive proof?)
-  \item Look at variations of RP.
-  \item What happens if properties involving sequences are reformulated for
-  $R^r$? (Cannot decide whether the given sequence is finite or infinite.)
-  \item Look at RP- and WCR implies RP!
-  \item Can "sequential" properties like RP, RP-, isWFseq, isWFseq-, $\omega$-bounded, etc.,
-  be related to the cofinality property.
+    \item WN$\downarrow\subseteq$WN :  $\forall$ x $\to$ is R-WN x $\to$ $\forall$ y $\to$ (R *) x y $\to$ is R-WN y
+    \item WN$\downarrow$UN$\rightarrow\subseteq$WN :
+
+    UN$\rightarrow\,$R $\to \forall$ x $\to$ is R-WN x $\to$ $\forall$ y $\to$ (R *) x y $\to$ is R-WN y
+
+    \textcolor{red}{SA: The above is a bit messy, can we make it cleaner?}
+    \item $\forall$ (R : $\mathscr{R}$ A) $\to$ $\forall$ is R -WN x $\to$ is R -UN x $\to$ is R -CR x
+
 \end{itemize}
 
-\section{Relations, ARS}
+\subsection{Counterexample 3}
+\begin{center}
+  \begin{tikzpicture}
+      % Define the nodes inside the region f
+      \node (f0) at (0, 0) {$f_0$};
+      \node (f1) at (1, 0) {$f_1$};
+      \node (fi) at (3, 0) {$f_i$};
+      \node (fi+1) at (4, 0) {$f_{i+1}$};
+      \node (dots) at (2, 0) {$...$};
+      \node (dots2) at (5, 0) {$...$};
 
-\begin{enumerate}
-  \item Define logical and structurual operations on relations, proving laws about them.
-  \item Define closure operations on realtions, proving laws about them
-  \item Define properties such as transtivity etc.
-\end{enumerate}
+      % Draw the arrows between the nodes inside the region f
+      \draw[->] (f0) -- (f1);
+      \draw[->] (f1) -- (dots);
+      \draw[->] (dots) -- (fi);
+      \draw[->] (fi) -- (fi+1);
+      \draw[->] (fi+1) -- (dots2);
 
-\subsection{Well-foundedness}
+      % Define the region f
+      \node[draw, ellipse, fit=(f0) (dots2), label=left:$f$] {};
 
-Four notions:
+      % Define the nodes outside the region f
+      \node (a) [below=of fi, yshift=-.5cm] {\parbox{2cm}{\centering $a$ \\ $\omega-bound$}};
+      \node (y) [above right=of fi, yshift=.5cm] {$y$};
+
+          % Draw the arrows between the nodes inside and outside the region f
+          \draw[->>] (fi) to [bend right=15] (a);
+          \draw[->>] (a) to [bend right=15] (fi);
+          \draw[->>] (fi+1) -- (a);
+          \draw[->>] (dots2) -- (a);
+          \draw[->>] (fi) -- (y);   
+      \end{tikzpicture}
+    \end{center}
+    Counterexample to:
     \begin{itemize}
-  \item Based on every element being accessible
-  \item Every inductive relation is universally true
-  \item Every non-empty set has a minimal element
-  \item No infinite sequence is decreasing
+      \item ***** DOES NOT WORK ******
+      \item RP-$\to$RP 
+      \item RP-$\land$WCR$\to$RP \textcolor{red}{NO< NEEDS A NEW CE}
 \end{itemize}
 
-\section{Open research questions}
+\subsection{Other questions}
 \begin{enumerate}
-  \item Sufficient conditions for reversing the implications between notions of
-  well-foundedness?
-  \item Knaster-Tarski Lemma: Most general form? Alternative formulations?
-  \item Syntax for closure operators allowing to prove the needed properties
-  uniformly/generically
+  \item If WCR holds, is WN$\downarrow\subseteq$WN ?
+  \item Same question for next bullet in 2.2
+  \item Same for bullet 3 in 2.2 (but pointwise!)
+  \item Do RP- $\land$ WCR imply RP?
 \end{enumerate}
+\subsection{ARS in Agda}
 
-\section{To Do}
+Important counterexamples:
 \begin{enumerate}
-  \item Clean up the current development
-  \item More laws about closure operations: Monotonicity, idempotency
-  \item Refactor the ARS formalized results with the new development
-  \item Knaster--Tarski in a well-founded setting: what additional
-  hypotheses are necessary?
+  \item $a,b,c,d$ with sinks $a$ and $d$ and a 2-cycle between $b$ and $c$.
+  Counterexample to:
+  \begin{itemize}
+      \item WCR and WN implies CR.
+  \end{itemize}
+  \item Loop $a \to a$.
+  Counterexample to:
+  \begin{itemize}
+    \item $\omega$-bounded and RP implies SN
+    \item $\omega$-bounded and RP implies WN
+  \end{itemize}
+  \item Infinite sequence $a_0 \to a_1 \to \cdots$. Falsifies:
+  \begin{itemize}
+    \item $WN$
+    \item $\omega$-bounded
+    \item RP $\to$ $\omega$-bounded
+    \item $WCR \to WN$
+    \item $CR \to WN$
+    \item $CR, CP \to WN$
+    \item $CR, CP \to \omega$-bounded
+  \end{itemize}
+  \item Infinite sequence $a_0 \to a_1 \to \cdots$ with a colimit $a_\infty$,
+  with each $a_n \to a_\infty$ and $a_\infty$ a normal form.
+
+  Counterexample to:
+  \begin{itemize}
+    \item WN $\to$ SN
+    \item WN, CR $\to$ SN
+    \item WN, CR, $\omega$-bounded $\to$ SN
+  \end{itemize}
+
+  \item Infinite sequence $a_0 \to a_1 \to \cdots$, together with links
+  $a_n \to a_0$, for each $n$.
+  \item The combination of the last two.
+  Counterexample to
+  \begin{itemize}
+    \item RP
+  \end{itemize}
+  \item An ``infinite haircomb''. Infinite sequence $a_0 \to a_1 \to \cdots$, together with
+  a disjoint, discrete set $b_0, b_1, \dots$, and links $a_n \to b_n$.
+  Counterexample to:
+  \begin{itemize}
+    \item $WN\to WCR$
+    \item $WN\to \omega-bounded$
+    \item $WN \to SN$
+    \item $WN,RP \to SN$
+  \end{itemize}
+  \item A variation of the above with backlinks $a_n \to a_0$ for all $n$.
 \end{enumerate}
+\newpage
+\newpage
+\section{Classical properties}
+Principles we are considering
+\begin{itemize}
+  \item Decidability of equality on $A$
+  \item Decidability of the relation $R$
+  \item When relevant, decidability of the given precicate $P$
+  \item Not-not-closure of being accessible
+  \item Not-not-closure of $R$
+  \item Not-not-closure of $P$
+  \item Decidability of whether a given element is an $R$-normal form
+  \item When relevant, local/element-wise versions of the above
+  \item Markov's principle:
+  \begin{itemize}
+    \item In $wfMin_0 \to wfSeq$.
 
-\subsection{Questions about well-foundedness}
+    Given a sequence $s : \nat \to A$, let $E(a) = \exists n \in \nat. s n \equiv a$.
 
+    Need: $\forall a. \lnot\lnot E(a) \to E(a)$, i.e.,
+    \[\lnot\lnot \big(\exists n \in \nat. s n \equiv a\big)
+          \to \big(\exists n \in \nat. s n \equiv a\big)\]
+
+  \end{itemize}
+\end{itemize}
+\newpage
+\section{Well foundedness }
 \begin{enumerate}
@@
 
+  \end{enumerate}
+
+  \textsc{Remark.}
+  $\lnot\lnot$-closure of accessibility should solve problems 1 and 4.
+
+\newpage
+\section{Guide to the code}
+\section{Open problems}
+\begin{itemize}
+    \item Look at restricting WFmin to $\lnot\lnot$-closed predicates
+    \item Status of important hypotheses:
+      \begin{itemize}
+        \item Deciding whether a given element $x$ reduces to a given element $y$
+        (Is $R$ itself decidable?)
+        \item Deciding whether a given element $x$ reduces to some element $y$
+        (Is being an $R$-normal form decidable?)
+
+        {\textcolor{red}{This is needed to show that SN $\Rightarrow$ WN.}}
+
+        \item If a given element $x$ is \emph{not} a normal form,
+        exhibiting some element $y$ that it reduces to.
+        (This is related to DeMorgan/Markov/etc. properties that came up in WF file.)
+
+        \item Does UN-lemma \emph{require} the decidability assumption?
+      \end{itemize}
+    \item META questions: Which of the ARS theorems can be made ``local/pointwise'',
+    for example,
+    \begin{itemize}
+      \item NL+: $WCR(R) \land SN(x) \to CR(x)$?  (Yes?)
+      \item NL++: $WCR(x) \land SN(x) \to CR(x)$? (No.)
+    \end{itemize}
+    \item When time permits, uniformize the notation (variable names, etc.) to the extent possible.
+    \item Can "sequential" properties like RP, RP-, isWFseq, isWFseq-, $\omega$-bounded, etc.,
+    be related to the cofinality property.
+    \item What happens if properties involving sequences are reformulated for
+  $R^r$? (Cannot decide whether the given sequence is finite or infinite.)
+  \item Knaster-Tarski Lemma: Most general form? Alternative formulations?
+  \item Syntax for closure operators allowing to prove the needed properties
+  uniformly/generically
+  \item More laws about closure operations: Monotonicity, idempotency
+  \item \item Knaster--Tarski in a well-founded setting: what additional
+  hypotheses are necessary?
   \item (2024.10.10) Is being $R$-WN inductive?
@@
 
-\end{enumerate}
-
-\textsc{Remark.}
-$\lnot\lnot$-closure of accessibility should solve problems 1 and 4.
-
-\section{Open problems}
-
-\begin{itemize}
      \item The infinite haircomb refutes $WN \land RP \to \omega$-bounded.  But it is not WCR.
@@
      \item $WN R \to UN R \to \omega-bdd R \to SN R$ (1.2.3.ii-)
+      \item Finish formulating the ``compactness property".  Two candidates:
+       \item ``Every cocone for a given infinite sequence loops back to some point in the sequence"
+       \item ``If an $R^*$-sequence has a cocone then it's constant after some point on.''
+       \item is $\omega$-bounded implied by WN and the following confluence property:
+       $a \to^* n \in NF$, and $a \to b$ then $b \to^* n $.
+    \item  Make the first argument to "being a normal form" implicit?
+    \item Write up the classical proof to theorem 1-2-3 iii
+
 \end{itemize}
+\section{Conclusions}
 

### 2024-11-07 Relations/Report.tex
Added macros
multiple definitions added

@@
 \documentclass{scrartcl}
-% Packages
-\usepackage{hyperref}
-\usepackage{tikz}
-\usepackage{amsmath}
-\usepackage{pifont}
-\usepackage{mathrsfs}
-\usepackage{amssymb}
-\usetikzlibrary{arrows.meta, positioning}
-
-\definecolor{darkgreen}{rgb}{0.0, 0.5, 0.0}
-
-\newcommand{\tto}{\twoheadrightarrow}
-\newcommand{\sse}{\subseteq}
-\newcommand{\bset}{\mathbf{Set}}
-\newcommand{\nat}{\mathbb{N}}
-
-\newcommand{\sacomment}[1]{\textcolor{red}{#1}}
-\newcommand{\apcomment}[1]{\textcolor{blue}{#1}}
-
-\usepackage{amsthm}
-
-\newtheorem{thm}{Theorem}
-\newtheorem{dfn}[thm]{Definition}
-\newtheorem{prop}[thm]{Proposition}
-\newtheorem{cor}[thm]{Corollary}
-\newtheorem{lemma}[thm]{Lemma}
-\newtheorem{rmk}[thm]{Remark}
-\newtheorem{expl}[thm]{Example}
-\newtheorem{notn}[thm]{Notation}
-%\theoremstyle{nonumberplain}
-%\theoremsymbol{\Box}
-% \newtheorem{proof}{Proof}
+% \input{packages}
+\input{macros}
 
@@
 \end{dfn}
-The following graphic illustrates the implications we have found between these definitions and those we are still seeking to find.
-Green arrows indicate that one definition implies another, red arrows indicate that we believe an implication should be possible but we have not yet found it.
 
-\begin{center}
+\begin{figure}[h]
+  \centering
   \begin{tikzpicture}[node distance=2cm, auto]
@@
   \end{tikzpicture}
-\end{center}
+  \caption{A graphic illustrating the implications we have found between the above 
+  definitions and those we are still seeking to find. Green arrows indicate that one 
+  definition implies another, red arrows indicate that we believe an implication should 
+  be possible but we have not yet found it.
+  }
+\end{figure}
 
@@
 \begin{dfn}
-  An abstract reduction system (\emph{ARS}) is a framework which we use to explore reduction relations on a set of objects.
+  An abstract reduction system (\emph{ARS}) is a structure $\mathcal{A} = (A, \to_\alpha)$ where $A$ is a set and $\to_\alpha$ is a set of binary relations.    
 \end{dfn}
-Throughout these definitions we use $A$ to denote the set and $\to$ to denote a binary relation on $A$.
-This relation represents the reduction process.
+A relation $\to$ from the set $\to_\alpha$ is refered to as a reduction (or rewrite) relation.
 For example, if we specify $\to$ as the relation of being 'less than' ($<$) then $4 \to 2$.
@@
 \end{dfn}
-\begin{center}
-  \begin{tikzpicture}[node distance=2cm, auto]
+\begin{figure}[h]
+  \centering
+  \begin{tikzpicture}[node distance=1.5cm, auto]
     % Nodes
@@
     \node (right) [below right of=top] {c};
-    \node (bottom) [below of=top, yshift=-1cm] {d};
+    \node (bottom) [below of=top] {d};
 
@@
 \end{tikzpicture}
-\end{center}
+\caption{An example of a weakly confluent relation.}
+\end{figure}
 
@@
 \end{dfn}
-\begin{center}
-  \begin{tikzpicture}[node distance=2cm, auto]
+    \begin{figure}
+      \centering
+      \begin{tikzpicture}[node distance=1.5cm, auto]
         % Nodes
@@
         \node (right) [below right of=top] {c};
-    \node (bottom) [below of=top, yshift=-1cm] {d};
+        \node (bottom) [below of=top] {d};
 
@@
       \end{tikzpicture}
-\end{center}
+    \caption{An example of a confluent relation.}
+    \end{figure}
 
 \begin{dfn}
-
+  \emph An element $a \in A$ is a {normal form} if there exists no reduction relation to any other element in $A$.
 \end{dfn}
 
-\subsubsection{Strongly Normalizing}
-\begin{center}
-    In TeReSe: $a \in A$ is \textit{strongly normalizing} if every reduction sequence starting from $a$ is finite.
-The reduciton relation $\rightarrow$ is \textit{strongly normalizing} (SN) if every $a \in A$ is strongly normalizing.
-\end{center}
-Go through different proofs Here
+\begin{dfn}
+  $a \in A$ is \emph{weakly normalizing} if $a \tto b$ for some normal form $b \in A$. 
+  $\to$ is weakly normalizing (WN) if every $a \in A$ is weakly normalizing.  
+\end{dfn}
+\sacomment{A lot of these are near word for word from TeReSe, is that okay?}
+
+\begin{dfn}
+  $a \in A$ is \emph{strongly normalizing} if every reduction sequence starting from $a$ is finite. $\to$ is strongly normalizing (SN) if every 
+  $a \in A$ is strongly normalizing. 
+\end{dfn}
+
+The above definition of SN is taken from TeReSe. We make use of the alternative definition presented in TeReSe ($\leftarrow$ is accessibly well founded) when working in Agda.
+
+If $\to$ is a reflexive, transitive and symmetric relation we denote it $\to^=$.
+
+\begin{dfn}
+  A reduction relation $\to$ has the \emph{normal form property} (NFP) if 
+ $a \to^= b$  $\implies$
+ $a \tto b$, for all $a \in A$ and any normal form $b \in A$. 
+\end{dfn}
+
+$a, b \in A$ being equivalent is denoted $a \equiv b$.
+
+\begin{dfn}
+  $\to$ has the \emph{unique normal form property} (UN) if 
+  $a \to^= b$  $\implies$
+  $a \equiv b$, for all $a \in A$ and any normal form $b \in A$. 
+\end{dfn}
+
+\begin{dfn}
+  $\to$ has the \emph{unique normal form property with respect to reduction} (UN$^ \to$) if 
+  $a \twoheadleftarrow  \cdot  \tto b$  $\implies$ $a \equiv b$, for all normal forms $a,b \in A$. 
+\end{dfn}
+
+\begin{dfn}
+  A \emph{sequence} is a relation from the natural numbers onto a set: $\nat \to A$.
+\end{dfn}
+
+\begin{dfn}
+  A sequence is \emph{increasing} if every term is greater than (\sacomment{or equal to?}) its previous term.
+\end{dfn}
+
+\begin{dfn}
+  A sequence is \emph{$\omega$-bounded} if there exists an element $a$ to which all elements of the sequence 
+  reduce. 
+\end{dfn}
+
+\begin{figure}[h]
+  \centering 
+  \begin{tikzpicture}
+      % Define the nodes inside the region f
+      \node (f0) at (0, 0) {$f_0$};
+      \node (f1) at (1, 0) {$f_1$};
+      \node (dots) at (2, 0) {$...$};
+
+      % Draw the arrows between the nodes inside the region f
+      \draw[->] (f0) -- (f1);
+      \draw[->] (f1) -- (dots);
+      \draw[->] (f1) -- (dots);
+
+      % Define the nodes outside the region f
+      \node (a) [below=of dots, yshift=-.25cm] {\parbox{2cm}{\centering $a$ }};
+
+          % Draw the arrows between the nodes inside and outside the region f sds
+
+          \draw[->>] (f0) -- (a);
+          \draw[->>] (f1) -- (a);
+          \draw[->>] (dots) -- (a);
+      \end{tikzpicture}
+      \caption{An example of an $\omega$-bounded sequence.}
+
+    \end{figure}
+
+\begin{dfn}
+  $a \in A$ has the \emph{recurrence property} if $a \tto b \implies b \tto a$ for all $b \in A$. 
+\end{dfn}
+\sacomment{I've been using $\tto$ as interchangable with $R *$ (as in the above definition). 
+Is that okay or am I going to have to clarify why they are interchangable (are they not interchangable?)?}
+
+\begin{dfn}
+  $\to$ has the \emph{recurrence property} (RP) if there is an increasing sequence $f$ in $A$ with an $\omega$-bound and 
+  there is an element of the sequence that has the recurrence property. 
+\end{dfn}
+
+    \begin{figure}[h]
+      \centering 
+      \begin{tikzpicture}
+          % Define the nodes inside the region f
+          \node (f0) at (0, 0) {$f_0$};
+          \node (f1) at (1, 0) {$f_1$};
+          \node (dots) at (2, 0) {$...$};
+          \node (fi) at (3, 0) {$f_i$};
+          \node (fi+1) at (4, 0) {$f_{i+1}$};
+          \node (dots2) at (5,0) {$...$};
+
+          % Draw the arrows between the nodes inside the region f
+          \draw[->] (f0) -- (f1);
+          \draw[->] (f1) -- (dots);
+          \draw[->] (dots) -- (fi);
+          \draw[->] (fi) -- (fi+1);
+          \draw[->] (fi+1) -- (dots2);
+
+          % Define the nodes outside the region f
+          \node (a) [below=of dots, yshift=-.25cm] {\parbox{1cm}{\centering $a$ }};
+
+              % Draw the arrows between the nodes inside and outside the region f sds
+
+              \draw[->>] (f0) to [bend right] (a);
+              \draw[->>] (f1) to [bend right] (a);
+              \draw[->>] (dots) -- (a);
+              \draw[->>] (fi) to [bend left=10] (a);
+              \draw[->>] (fi+1) to [bend left] (a);
+              \draw[->>] (dots2) to [bend left] (a); 
+              \draw[->>] (a) to [bend left=10] (fi);
+
+          \end{tikzpicture}
+          \caption{An example of a relation with the recurrence property.}
+
+        \end{figure}
+\begin{dfn}
+  $\to$ has the \emph{recurrence property -} (RP-)  if there is an increasing sequence $f$ in $A$ with an $\omega$-bound $a$ and 
+  there is an element $i$ of the sequence such that $a \tto f (i)$.
+\end{dfn}
+
+\begin{dfn}
+  \emph{Cofinality property}
+\end{dfn}
+\sacomment{Still not sure on how to define cofinality.}
+
+\begin{dfn}
+  $\to$ is \emph{finitely branching} (FB) if, for all $a \in A$, the set of one step reducts of $a$ is finite. 
+\end{dfn}
 

### 2024-11-07 Relations/Report.tex
RP-iffRP

@@
 Before exploring those proofs the following definitions are essential.
+
+The following definitions are taken from [TeReSe], Chapter 1,
+with minimal adaptations for consistency.
+
 \begin{dfn}
@@
 \textcolor{red}{Right?}
+\apcomment{Yes, but move this to a(n eventual) list of examples.}
 
 We use $\to$ for a single-step reduction and $\tto$ for a multi-step reduction.
+
+\apcomment{Thus, when $(a,b) \in \to_{(\alpha)}$, we say that there is a
+\emph{$(\alpha-)$reduction} from $a$ to $b$.
+When $(a,b) \in \tto_\alpha$, we say that there is a multi-step $\alpha$-reduction
+from $a$ to $b$.}
 
@@
   \centering
-  \begin{tikzpicture}[node distance=1.5cm, auto]
+\[  \begin{tikzpicture}[node distance=1.5cm, auto]
     % Nodes
@@
     \node (right) [below right of=top] {c};
-    \node (bottom) [below of=top] {d};
+    \node (bottom) [below right of=left] {d};
 
@@
 \end{tikzpicture}
+\hspace{3cm}
+\begin{tikzpicture}[node distance=1.5cm, auto]
+  % Nodes
+  \node (top) {a};
+  \node (left) [below left of=top] {b};
+  \node (right) [below right of=top] {c};
+  \node (bottom) [below right of=left] {d};
+
+  % Arrows
+  \draw[->>] (top) -- (left);
+  \draw[->>] (top) -- (right);
+  \draw[->>] (left) -- (bottom);
+  \draw[->>] (right) -- (bottom);
+\end{tikzpicture}
+\]
 \caption{An example of a weakly confluent relation.}
@@
 \begin{dfn}
-  A reduction relation is \emph{confluent} (AKA Church-Rosser (CR)) if all multi-step redctions from a given element can always converge via multi-step reductions to some common reduct.
+  A reduction relation is \emph{confluent} (AKA Church-Rosser (CR)) if all multi-step reductions from a given element can always converge via multi-step reductions to some common reduct.
 \end{dfn}
@@
         \node (right) [below right of=top] {c};
-        \node (bottom) [below of=top] {d};
+        \node (bottom) [below right of=left] {d};
 
@@
 \begin{dfn}
-  \emph An element $a \in A$ is a {normal form} if there exists no reduction relation to any other element in $A$.
+  \emph An element $a \in A$ is a {normal form} if there exists no reduction to any other element in $A$.
 \end{dfn}
@@
 \begin{dfn}
-  $a \in A$ is \emph{weakly normalizing} if $a \tto b$ for some normal form $b \in A$. 
-  $\to$ is weakly normalizing (WN) if every $a \in A$ is weakly normalizing.  
+  An element $a \in A$ is \emph{$R$-weakly normalizing} ($WN_{R}$)if $a \tto b$ for some normal form $b \in A$.
+
+  A relation $\to$ is weakly normalizing (WN) if every $a \in A$ is $R$- weakly normalizing.
 \end{dfn}
@@
 \begin{dfn}
-  $a \in A$ is \emph{strongly normalizing} if every reduction sequence starting from $a$ is finite. $\to$ is strongly normalizing (SN) if every 
-  $a \in A$ is strongly normalizing. 
+  An element $a \in A$ is \emph{$R$-strongly normalizing} ($SN_R$) if every reduction sequence starting from $a$ is finite.
+
+  A relation $\to$ is strongly normalizing (SN) if every
+  $a \in A$ is $\to$-strongly normalizing.
 \end{dfn}
 
-The above definition of SN is taken from TeReSe. We make use of the alternative definition presented in TeReSe ($\leftarrow$ is accessibly well founded) when working in Agda.
+The above definition of SN is taken from TeReSe. We make use of the alternative definition presented in TeReSe ($\leftarrow$ is accessibly well-founded) when working in Agda.
 
 If $\to$ is a reflexive, transitive and symmetric relation we denote it $\to^=$.
+
+\apcomment{This is not quite right; rather, $\to^=$ is the reflexive-symmetric-transitive closure of $\to$, i.e., it is the \emph{equivalence relation generated by $\to$}, the NFP refers to this latter relation.}
+
+\apcomment{Add a subsection/definition listing the closure operations on relations.}
 
@@
 
+Let $A$ be a set.
 \begin{dfn}
-  A \emph{sequence} is a relation from the natural numbers onto a set: $\nat \to A$.
+  A \emph{sequence (in $A$)} is a function from the natural numbers to $A$:
+  \begin{align*}
+    &s : \nat \to A \\
+    &s = (s_0,s_1,s_2,\dots)
+  \end{align*}
 \end{dfn}
@@
 \begin{dfn}
-  A sequence is \emph{increasing} if every term is greater than (\sacomment{or equal to?}) its previous term.
+  A sequence is \emph{$R$-increasing} if every term is $R$-related to its preceding term.
 \end{dfn}
@@
 \begin{dfn}
-  A sequence is \emph{$\omega$-bounded} if there exists an element $a$ to which all elements of the sequence 
-  reduce. 
+  A sequence is \emph{bounded} if there exists an element $a$ to which all elements of the sequence reduce.
 \end{dfn}
@@
 Is that okay or am I going to have to clarify why they are interchangable (are they not interchangable?)?}
+\apcomment{It's okay, but later we will need to make sure we are using them consistently.  Say that in Agda code, $\to$ is denoted by $R$.}
 
 \begin{dfn}
-  $\to$ has the \emph{recurrence property} (RP) if there is an increasing sequence $f$ in $A$ with an $\omega$-bound and 
-  there is an element of the sequence that has the recurrence property. 
+  $\to$ has the \emph{recurrence property} (RP) if every
+  bounded, increasing sequence has a recurrent element.
 \end{dfn}
@@
 \begin{dfn}
-  $\to$ has the \emph{recurrence property -} (RP-)  if there is an increasing sequence $f$ in $A$ with an $\omega$-bound $a$ and 
+  $\to$ has the \emph{weak recurrence property} (RP-) if
+  for every increasing sequence with bound $a$,
   there is an element $i$ of the sequence such that $a \tto f (i)$.

### 2024-11-07 Relations/notes.tex
RP-iffRP

@@
 This document aims to bring together the various notes from report, rewriting qs, and counterexamples.
+
+\section{Todo}
+\begin{enumerate}
+  \item In the report, give a classical proof that the $Inc$ Property
+  implies that no $R$-increasing sequence is bounded.
+
+  Conclude that every relation satisfying $Inc$ also satisfies $RP$.
+
+  Therefore, the proof of Theorem 1.2.3(iii) using $RP$ instead of $Inc$
+  is generalizing the claim of the theorem (as stated in [TeReSe]).
+\end{enumerate}
 

### 2024-11-14 Relations/Report.tex
Updates for meeting 14th Nov

@@
 
+\tableofcontents
+
 \section{Introduction}
@@
 
-\section{Relations}
+\section{Definitions}
+The most interesting work we have carried out in investigating Chapter 1 of TeReSe has resulted from trying to provide constructive proofs for Newman's lemma, the Knaster-Tarski lemma, theorem 1.2.2 and theorem 1.2.3.
+Before exploring those proofs the following definitions are essential.
 
+The following definitions are taken from [TeReSe], Chapter 1,
+with minimal adaptations for consistency.
+
+\begin{dfn}
+  An abstract reduction system (\emph{ARS}) is a structure $\mathcal{A} = (A, R_\alpha)$ where $A$ is a set and $R_\alpha$ is a set of binary relations.
+\end{dfn}
+A relation $R$ from the set $R_\alpha$ is refered to as a reduction (or rewrite) relation.
+For example, if we specify $R$ as the relation of being 'less than' ($<$) then $R\, 4\, 2$.
+\textcolor{red}{Right?}
+\apcomment{Yes, but move this to a(n eventual) list of examples.}
+
+We use $R$ or $\to$ for a single-step reduction and $R^*$ or $\tto$ for a multi-step reduction.
+
+\sacomment{Should we be using $R^+$ rather than $R^*$?}
+
+\apcomment{Thus, when $(a,b) \in \to_{(\alpha)}$, we say that there is a
+\emph{$(\alpha-)$reduction} from $a$ to $b$.
+When $(a,b) \in \tto_\alpha$, we say that there is a multi-step $\alpha$-reduction
+from $a$ to $b$.}
+
+\begin{dfn}
+  An element $a \in A$ is \emph{R-weakly confluent} ($WCR_R$) if all single step reductions from $a$ can always converge 
+  via multi-step reductions to some common reduct.  
+  A relation $R$ is \emph{weakly confluent} (AKA weakly Church-Rosser (WCR)) if every $a \in A$ is R-weakly confluent.
+\end{dfn}
+
+\begin{dfn}
+  An element $a \in A$ is \emph{R-confluent} ($CR_R$) if all multi-step reductions from $a$ can always converge 
+  via multi-step reductions to some common reduct.  
+  A relation $R$ is \emph{confluent} (AKA Church-Rosser (CR)) if every $a \in A$ is R-confluent.
+\end{dfn}
+
+\begin{figure}[h]
+  \centering
+\[  \begin{tikzpicture}[node distance=1.5cm, auto]
+    % Nodes
+    \node (top) {a};
+    \node (left) [below left of=top] {b};
+    \node (right) [below right of=top] {c};
+    \node (bottom) [below right of=left] {d};
+
+    % Arrows
+    \draw[->] (top) -- (left);
+    \draw[->] (top) -- (right);
+    \draw[->>] (left) -- (bottom);
+    \draw[->>] (right) -- (bottom);
+\end{tikzpicture}
+\hspace{3cm}
+\begin{tikzpicture}[node distance=1.5cm, auto]
+  % Nodes
+  \node (top) {a};
+  \node (left) [below left of=top] {b};
+  \node (right) [below right of=top] {c};
+  \node (bottom) [below right of=left] {d};
+
+  % Arrows
+  \draw[->>] (top) -- (left);
+  \draw[->>] (top) -- (right);
+  \draw[->>] (left) -- (bottom);
+  \draw[->>] (right) -- (bottom);
+\end{tikzpicture}
+\] 
+\caption{On the left is an example of a weakly confluent relation. On the right is an example of a confluent relation.}
+\end{figure}
+
+\begin{dfn}
+  \emph An element $a \in A$ is a {normal form} if there exists no reduction to any other element in $A$.
+\end{dfn}
+
+\begin{dfn}
+  An element $a \in A$ is \emph{$R$-weakly normalizing} ($WN_{R}$)if $a \tto b$ for some normal form $b \in A$.
+
+  A relation $R$ is weakly normalizing (WN) if every $a \in A$ is $R$- weakly normalizing.
+\end{dfn}
+
+\begin{dfn}
+  An element $a \in A$ is \emph{$R$-strongly normalizing} ($SN_R$) if every reduction sequence starting from $a$ is finite.
+
+  A relation $R$ is strongly normalizing (SN) if every
+  $a \in A$ is $R$-strongly normalizing.
+\end{dfn}
+
+The above definition of SN is taken from [TeReSe]. When working in Agda, we make use of the alternative definition presented in [TeReSe] ($\leftarrow$ is accessibly well-founded).
+
+\subsection{Closure operations on relations}
+
+A relation $R$ has the following properties when the stated conditions are met:
+\begin{dfn}
+  \emph{reflexive} {- $\forall x \in A : x \to x $}    
+\end{dfn}
+\begin{dfn}
+  \emph{transitive} {- $\forall x, y, z \in A : ( x \to y \land y \to z ) \implies x \to z $}    
+\end{dfn}
+\begin{dfn}
+  \emph{symmetric} {- $\forall x, y \in A : x \to y \implies y \to x$}    
+\end{dfn}
+
+\begin{dfn}
+  The \emph{closure} of $R$ is the smallest relation that contains $\to$ and satisfies a given property. 
+\end{dfn}
+
+\begin{dfn}
+  The \emph{reflexive closure} of $R$ is the smallest relation $\to^r$ that contains $\to$ and is reflexive.
+\end{dfn}
+\begin{dfn}
+  The \emph{symmetric closure} of $R$ is the smallest relation $R^s$ that contains $R$ and is symmetric.
+\end{dfn}
+\begin{dfn}
+  The \emph{transitive closure} of $R$ is the smallest relation $R^+$ that contains $R$ and is transitive. 
+\end{dfn}
+\begin{dfn}
+  The \emph{reflexive transitive closure} of $R$ is the smallest relation $R^*$ that contains $R$ and is both reflexive and transitive. 
+\end{dfn}
+\begin{dfn}
+  The \emph{equivalence relation} of $R$ is the smallest relation $R^=$ that contains $R$ and is reflexive, transitive, and symmetric.
+\end{dfn}
+
+\begin{dfn}
+  A relation $R$ has the \emph{normal form property} (NFP) if
+ $a \to^= b$  $\implies$
+ $a \tto b$, for all $a \in A$ and any normal form $b \in A$.
+\end{dfn}
+
+Two elements $a, b \in A$ being equivalent is denoted $a \equiv b$.
+
+\begin{dfn}
+  A relation $R$ has the \emph{unique normal form property} (UN) if
+  $a \to^= b$  $\implies$
+  $a \equiv b$, for all $a \in A$ and any normal form $b \in A$.
+\end{dfn}
+
+\begin{dfn}
+  A relation $R$ has the \emph{unique normal form property with respect to reduction} (UN$^ \to$) if
+  $a \twoheadleftarrow  \cdot  \tto b$  $\implies$ $a \equiv b$, for all normal forms $a,b \in A$.
+\end{dfn}
+
+Let $A$ be a set.
+\begin{dfn}
+  A \emph{sequence (in $A$)} is a function from the natural numbers to $A$:
+  \begin{align*}
+    &s : \nat \to A \\
+    &s = (s_0,s_1,s_2,\dots)
+  \end{align*}
+\end{dfn}
+
+\begin{dfn}
+  A sequence is \emph{$R$-increasing} if every term is $R$-related to its preceding term.
+\end{dfn}
+
+\begin{dfn}
+  A sequence is \emph{bounded} if there exists an element $a$ to which all elements of the sequence reduce.
+\end{dfn}
+
+\begin{figure}[h]
+  \centering
+  \begin{tikzpicture}
+      % Define the nodes inside the region f
+      \node (f0) at (0, 0) {$f_0$};
+      \node (f1) at (1, 0) {$f_1$};
+      \node (dots) at (2, 0) {$...$};
+
+      % Draw the arrows between the nodes inside the region f
+      \draw[->] (f0) -- (f1);
+      \draw[->] (f1) -- (dots);
+      \draw[->] (f1) -- (dots);
+
+      % Define the nodes outside the region f
+      \node (a) [below=of dots, yshift=-.25cm] {\parbox{2cm}{\centering $a$ }};
+
+          % Draw the arrows between the nodes inside and outside the region f sds
+
+          \draw[->>] (f0) -- (a);
+          \draw[->>] (f1) -- (a);
+          \draw[->>] (dots) -- (a);
+      \end{tikzpicture}
+      \caption{An example of an bounded sequence.}
+
+    \end{figure}
+
+\begin{dfn}
+  An element $a \in A$ has the \emph{recurrence property} if $a \tto b \implies b \tto a$ for all $b \in A$.
+\end{dfn}
+\sacomment{I've been using $\tto$ as interchangable with $R *$ (as in the above definition).
+Is that okay or am I going to have to clarify why they are interchangable (are they not interchangable?)?}
+\apcomment{It's okay, but later we will need to make sure we are using them consistently.  Say that in Agda code, $\to$ is denoted by $R$.}
+
+\begin{dfn}
+  A relation $R$ has the \emph{recurrence property} (RP) if every
+  bounded, increasing sequence has a recurrent element.
+\end{dfn}
+
+    \begin{figure}[h]
+      \centering
+      \begin{tikzpicture}
+          % Define the nodes inside the region f
+          \node (f0) at (0, 0) {$f_0$};
+          \node (f1) at (1, 0) {$f_1$};
+          \node (dots) at (2, 0) {$...$};
+          \node (fi) at (3, 0) {$f_i$};
+          \node (fi+1) at (4, 0) {$f_{i+1}$};
+          \node (dots2) at (5,0) {$...$};
+
+          % Draw the arrows between the nodes inside the region f
+          \draw[->] (f0) -- (f1);
+          \draw[->] (f1) -- (dots);
+          \draw[->] (dots) -- (fi);
+          \draw[->] (fi) -- (fi+1);
+          \draw[->] (fi+1) -- (dots2);
+
+          % Define the nodes outside the region f
+          \node (a) [below=of dots, yshift=-.25cm] {\parbox{1cm}{\centering $a$ }};
+
+              % Draw the arrows between the nodes inside and outside the region f sds
+
+              \draw[->>] (f0) to [bend right] (a);
+              \draw[->>] (f1) to [bend right] (a);
+              \draw[->>] (dots) -- (a);
+              \draw[->>] (fi) to [bend left=10] (a);
+              \draw[->>] (fi+1) to [bend left] (a);
+              \draw[->>] (dots2) to [bend left] (a);
+              \draw[->>] (a) to [bend left=10] (fi);
+
+          \end{tikzpicture}
+          \caption{An example of a relation with the recurrence property.}
+
+        \end{figure}
+\begin{dfn}
+  A relation $R$ has the \emph{weak recurrence property} (RP-) if
+  for every increasing sequence with bound $a$,
+  there is an element $i$ of the sequence such that $a \tto f (i)$.
+\end{dfn}
+
+\begin{dfn}
+  \emph{Cofinality property}
+\end{dfn}
+\sacomment{Still not sure on how to define cofinality.}
+
+\begin{dfn}
+  A relation $R$ is \emph{finitely branching} (FB) if, for all $a \in A$, the set of one step reducts of $a$ is finite.
+\end{dfn}
+
+\section{Classical Principles}
+Principles we are considering
+\begin{itemize}
+  \item Decidability of equality on $A$
+  \item Decidability of the relation $R$
+  \item When relevant, decidability of the given precicate $P$
+  \item Not-not-closure of being accessible
+  \item Not-not-closure of $R$
+  \item Not-not-closure of $P$
+  \item Decidability of whether a given element is an $R$-normal form
+  \item When relevant, local/element-wise versions of the above
+  \item Markov's principle:
+  \begin{itemize}
+    \item In $wfMin_0 \to wfSeq$.
+
+    Given a sequence $s : \nat \to A$, let $E(a) = \exists n \in \nat. s n \equiv a$.
+
+    Need: $\forall a. \lnot\lnot E(a) \to E(a)$, i.e.,
+    \[\lnot\lnot \big(\exists n \in \nat. s n \equiv a\big)
+          \to \big(\exists n \in \nat. s n \equiv a\big)\]
+
+  \end{itemize}
+\end{itemize}
+
+\section{Implications}
+We now look into the interrelation of the various properties defined in Section 2. Our aim is to expand on the 
+connections made in Figure 1.8 of [TeReSe] (p.19).
+
+\section{Counterexamples}
+The following counterexamples are used to rule out certain implications between properties from holding. 
+\sacomment{How should we present this section. Is it enough to have diagrams and a list of what they are a counter to?}
+\subsection*{Counterexample 1}
+\begin{center}
+
+  \begin{tikzcd}[node distance=2cm, auto]
+      % Nodes
+      \node (a) {a};
+      \node (b) [right of=a, xshift=1cm] {b};
+      \node (c) [right of=b, xshift=1cm] {c};
+      \node (d) [right of=c, xshift=1cm] {d};
+
+      % Arrows
+      \draw[->] (b) to [bend left] (c);
+      \draw[->] (c) to [bend left] (b);
+      \draw[->] (b) -- (a);
+      \draw[->] (c) -- (d);
+  \end{tikzcd}
+
+\end{center}
+Counterexample to:
+\begin{itemize}
+  \item WCR $\implies$ CR
+  \item WCR and WN $\implies$ CR
+  \item WCR and WN $\implies$ SN
+  \item \mbox{WCR R $\to$ $\forall$ a b $\to$ is R -NF b $\to$ (R *) a b $\to$ $\forall$ c $\to$ (R *) a c $\to$ (R *) c b}
+  \item IOW and WCR $\implies$ WNFP \sacomment{We need to define these still (IOW and WNFP)}
+\end{itemize}
+\subsection*{Counterexample 2}
+\begin{center}
+  \begin{tikzcd}
+      % Nodes
+      \node (x) {x};
+      \node (n) [left of=x, xshift=-1cm] {n \in NF};
+      \node (y) [right of=x, xshift=1cm] {y};
+      \node (z) [right of=y] {z};
+
+      % Arrows
+      \draw[->>] (x) -- (n);
+      \draw[->>] (x) -- (y);
+      \draw[->] (y) to [bend left] (z);
+      \draw[->] (z) to [bend left] (y);
+  \end{tikzcd}
+\end{center}
+
+Counterexample to:
+\begin{itemize}
+  \item WN$\downarrow\subseteq$WN (WN is not closed under reduction) \sacomment{Is this the right way to express that elementwise WN doesn't imply global WN?}
+  \item WN$\downarrow$UN$\rightarrow\subseteq$WN :
+
+  UN$\rightarrow\,$R $\to \forall$ x $\to$ is R-WN x $\to$ $\forall$ y $\to$ (R *) x y $\to$ is R-WN y
+
+  \textcolor{red}{SA: The above is a bit messy, can we make it cleaner?}
+  \item $\forall$ (R : $\mathscr{R}$ A) $\to$ $\forall$ is R -WN x $\to$ is R -UN x $\to$ is R -CR x
+  \item $WN_R$ and $UN_R$ $\implies$ $CR_R$
+
+\end{itemize}
+
+\subsection*{Counterexample 3}
+
+\begin{center}
+  \begin{tikzcd}
+      % Nodes
+      \node (x) {x};
+
+      % Arrows
+      \draw[->, loop] (x) to (x);
+  \end{tikzcd}
+\end{center}
+Counterexample to:
+\begin{itemize}
+  \item bounded and RP implies SN
+  \item bounded and RP implies WN
+\end{itemize}
+
+\subsection*{Counterexample 4}
+  \begin{center}
+      \begin{tikzpicture}
+      % Define the nodes 
+      \node (a) at (0, 0) {$a$};
+      \node (b) at (1, 0) {$b$};
+      \node (dots) at (2, 0) {$...$};
+
+      % Draw the arrows
+      \draw[->] (a) -- (b);
+      \draw[->] (b) -- (dots);
+
+      \end{tikzpicture}
+    \end{center}
+Counterexample to:
+
+\section{Well-foundedness}
 \subsection{Well-foundedness}
@@
 
-\subsection{Definitions}
-\textcolor{red}{Go through some of the main definitions formalised from Terese, focussing on where we have used constructive alternatives to the classically given definitions
-Could talk here about omega bounded stuff too!}
-
-The most interesting work we have carried out in investigating Chapter 1 of TeReSe has resulted from trying to provide constructive proofs for Newman's lemma, the Knaster-Tarski lemma, theorem 1.2.2 and theorem 1.2.3.
-Before exploring those proofs the following definitions are essential.
-
-The following definitions are taken from [TeReSe], Chapter 1,
-with minimal adaptations for consistency.
-
-\begin{dfn}
-  An abstract reduction system (\emph{ARS}) is a structure $\mathcal{A} = (A, \to_\alpha)$ where $A$ is a set and $\to_\alpha$ is a set of binary relations.
-\end{dfn}
-A relation $\to$ from the set $\to_\alpha$ is refered to as a reduction (or rewrite) relation.
-For example, if we specify $\to$ as the relation of being 'less than' ($<$) then $4 \to 2$.
-\textcolor{red}{Right?}
-\apcomment{Yes, but move this to a(n eventual) list of examples.}
-
-We use $\to$ for a single-step reduction and $\tto$ for a multi-step reduction.
-
-\apcomment{Thus, when $(a,b) \in \to_{(\alpha)}$, we say that there is a
-\emph{$(\alpha-)$reduction} from $a$ to $b$.
-When $(a,b) \in \tto_\alpha$, we say that there is a multi-step $\alpha$-reduction
-from $a$ to $b$.}
-
-\begin{dfn}
-    A reduction relation is \emph{weakly confluent} (AKA weakly Church-Rosser (WCR)) if all single-step reductions from a given element can always converge via multi-step reductions to some common reduct.
-\end{dfn}
-\begin{figure}[h]
-  \centering
-\[  \begin{tikzpicture}[node distance=1.5cm, auto]
-    % Nodes
-    \node (top) {a};
-    \node (left) [below left of=top] {b};
-    \node (right) [below right of=top] {c};
-    \node (bottom) [below right of=left] {d};
-
-    % Arrows
-    \draw[->] (top) -- (left);
-    \draw[->] (top) -- (right);
-    \draw[->>] (left) -- (bottom);
-    \draw[->>] (right) -- (bottom);
-\end{tikzpicture}
-\hspace{3cm}
-\begin{tikzpicture}[node distance=1.5cm, auto]
-  % Nodes
-  \node (top) {a};
-  \node (left) [below left of=top] {b};
-  \node (right) [below right of=top] {c};
-  \node (bottom) [below right of=left] {d};
-
-  % Arrows
-  \draw[->>] (top) -- (left);
-  \draw[->>] (top) -- (right);
-  \draw[->>] (left) -- (bottom);
-  \draw[->>] (right) -- (bottom);
-\end{tikzpicture}
-\]
-\caption{An example of a weakly confluent relation.}
-\end{figure}
-
-\begin{dfn}
-  A reduction relation is \emph{confluent} (AKA Church-Rosser (CR)) if all multi-step reductions from a given element can always converge via multi-step reductions to some common reduct.
-\end{dfn}
-    \begin{figure}
-      \centering
-      \begin{tikzpicture}[node distance=1.5cm, auto]
-        % Nodes
-        \node (top) {a};
-        \node (left) [below left of=top] {b};
-        \node (right) [below right of=top] {c};
-        \node (bottom) [below right of=left] {d};
-
-        % Arrows
-        \draw[->>] (top) -- (left);
-        \draw[->>] (top) -- (right);
-        \draw[->>] (left) -- (bottom);
-        \draw[->>] (right) -- (bottom);
-      \end{tikzpicture}
-    \caption{An example of a confluent relation.}
-    \end{figure}
-
-\begin{dfn}
-  \emph An element $a \in A$ is a {normal form} if there exists no reduction to any other element in $A$.
-\end{dfn}
-
-\begin{dfn}
-  An element $a \in A$ is \emph{$R$-weakly normalizing} ($WN_{R}$)if $a \tto b$ for some normal form $b \in A$.
-
-  A relation $\to$ is weakly normalizing (WN) if every $a \in A$ is $R$- weakly normalizing.
-\end{dfn}
-\sacomment{A lot of these are near word for word from TeReSe, is that okay?}
-
-\begin{dfn}
-  An element $a \in A$ is \emph{$R$-strongly normalizing} ($SN_R$) if every reduction sequence starting from $a$ is finite.
-
-  A relation $\to$ is strongly normalizing (SN) if every
-  $a \in A$ is $\to$-strongly normalizing.
-\end{dfn}
-
-The above definition of SN is taken from TeReSe. We make use of the alternative definition presented in TeReSe ($\leftarrow$ is accessibly well-founded) when working in Agda.
-
-If $\to$ is a reflexive, transitive and symmetric relation we denote it $\to^=$.
-
-\apcomment{This is not quite right; rather, $\to^=$ is the reflexive-symmetric-transitive closure of $\to$, i.e., it is the \emph{equivalence relation generated by $\to$}, the NFP refers to this latter relation.}
-
-\apcomment{Add a subsection/definition listing the closure operations on relations.}
-
-\begin{dfn}
-  A reduction relation $\to$ has the \emph{normal form property} (NFP) if
- $a \to^= b$  $\implies$
- $a \tto b$, for all $a \in A$ and any normal form $b \in A$.
-\end{dfn}
-
-$a, b \in A$ being equivalent is denoted $a \equiv b$.
-
-\begin{dfn}
-  $\to$ has the \emph{unique normal form property} (UN) if
-  $a \to^= b$  $\implies$
-  $a \equiv b$, for all $a \in A$ and any normal form $b \in A$.
-\end{dfn}
-
-\begin{dfn}
-  $\to$ has the \emph{unique normal form property with respect to reduction} (UN$^ \to$) if
-  $a \twoheadleftarrow  \cdot  \tto b$  $\implies$ $a \equiv b$, for all normal forms $a,b \in A$.
-\end{dfn}
-
-Let $A$ be a set.
-\begin{dfn}
-  A \emph{sequence (in $A$)} is a function from the natural numbers to $A$:
-  \begin{align*}
-    &s : \nat \to A \\
-    &s = (s_0,s_1,s_2,\dots)
-  \end{align*}
-\end{dfn}
-
-\begin{dfn}
-  A sequence is \emph{$R$-increasing} if every term is $R$-related to its preceding term.
-\end{dfn}
-
-\begin{dfn}
-  A sequence is \emph{bounded} if there exists an element $a$ to which all elements of the sequence reduce.
-\end{dfn}
-
-\begin{figure}[h]
-  \centering
-  \begin{tikzpicture}
-      % Define the nodes inside the region f
-      \node (f0) at (0, 0) {$f_0$};
-      \node (f1) at (1, 0) {$f_1$};
-      \node (dots) at (2, 0) {$...$};
-
-      % Draw the arrows between the nodes inside the region f
-      \draw[->] (f0) -- (f1);
-      \draw[->] (f1) -- (dots);
-      \draw[->] (f1) -- (dots);
-
-      % Define the nodes outside the region f
-      \node (a) [below=of dots, yshift=-.25cm] {\parbox{2cm}{\centering $a$ }};
-
-          % Draw the arrows between the nodes inside and outside the region f sds
-
-          \draw[->>] (f0) -- (a);
-          \draw[->>] (f1) -- (a);
-          \draw[->>] (dots) -- (a);
-      \end{tikzpicture}
-      \caption{An example of an $\omega$-bounded sequence.}
-
-    \end{figure}
-
-\begin{dfn}
-  $a \in A$ has the \emph{recurrence property} if $a \tto b \implies b \tto a$ for all $b \in A$.
-\end{dfn}
-\sacomment{I've been using $\tto$ as interchangable with $R *$ (as in the above definition).
-Is that okay or am I going to have to clarify why they are interchangable (are they not interchangable?)?}
-\apcomment{It's okay, but later we will need to make sure we are using them consistently.  Say that in Agda code, $\to$ is denoted by $R$.}
-
-\begin{dfn}
-  $\to$ has the \emph{recurrence property} (RP) if every
-  bounded, increasing sequence has a recurrent element.
-\end{dfn}
-
-    \begin{figure}[h]
-      \centering
-      \begin{tikzpicture}
-          % Define the nodes inside the region f
-          \node (f0) at (0, 0) {$f_0$};
-          \node (f1) at (1, 0) {$f_1$};
-          \node (dots) at (2, 0) {$...$};
-          \node (fi) at (3, 0) {$f_i$};
-          \node (fi+1) at (4, 0) {$f_{i+1}$};
-          \node (dots2) at (5,0) {$...$};
-
-          % Draw the arrows between the nodes inside the region f
-          \draw[->] (f0) -- (f1);
-          \draw[->] (f1) -- (dots);
-          \draw[->] (dots) -- (fi);
-          \draw[->] (fi) -- (fi+1);
-          \draw[->] (fi+1) -- (dots2);
-
-          % Define the nodes outside the region f
-          \node (a) [below=of dots, yshift=-.25cm] {\parbox{1cm}{\centering $a$ }};
-
-              % Draw the arrows between the nodes inside and outside the region f sds
-
-              \draw[->>] (f0) to [bend right] (a);
-              \draw[->>] (f1) to [bend right] (a);
-              \draw[->>] (dots) -- (a);
-              \draw[->>] (fi) to [bend left=10] (a);
-              \draw[->>] (fi+1) to [bend left] (a);
-              \draw[->>] (dots2) to [bend left] (a);
-              \draw[->>] (a) to [bend left=10] (fi);
-
-          \end{tikzpicture}
-          \caption{An example of a relation with the recurrence property.}
-
-        \end{figure}
-\begin{dfn}
-  $\to$ has the \emph{weak recurrence property} (RP-) if
-  for every increasing sequence with bound $a$,
-  there is an element $i$ of the sequence such that $a \tto f (i)$.
-\end{dfn}
-
-\begin{dfn}
-  \emph{Cofinality property}
-\end{dfn}
-\sacomment{Still not sure on how to define cofinality.}
-
-\begin{dfn}
-  $\to$ is \emph{finitely branching} (FB) if, for all $a \in A$, the set of one step reducts of $a$ is finite.
-\end{dfn}
-
-\subsection{Newmans lemma}
-What it is and the different definitions again
-
-\subsection{}
-
-\section{Notes from 08.29}
+\section{Notes}
+\subsection{Notes from 08.29}
 
@@
 
-\section{09.05}
+\subsection{09.05}
 \begin{enumerate}
@@
 
-\section{Classical Principles}
-Principles we are considering
-\begin{itemize}
-  \item Decidability of equality on $A$
-  \item Decidability of the relation $R$
-  \item When relevant, decidability of the given precicate $P$
-  \item Not-not-closure of being accessible
-  \item Not-not-closure of $R$
-  \item Not-not-closure of $P$
-  \item Decidability of whether a given element is an $R$-normal form
-  \item When relevant, local/element-wise versions of the above
-  \item Markov's principle:
-  \begin{itemize}
-    \item In $wfMin_0 \to wfSeq$.
-
-    Given a sequence $s : \nat \to A$, let $E(a) = \exists n \in \nat. s n \equiv a$.
-
-    Need: $\forall a. \lnot\lnot E(a) \to E(a)$, i.e.,
-    \[\lnot\lnot \big(\exists n \in \nat. s n \equiv a\big)
-          \to \big(\exists n \in \nat. s n \equiv a\big)\]
-
-  \end{itemize}
-\end{itemize}
-
 \end{document}

### 2024-11-14 Relations/notes.tex
Updates for meeting 14th Nov

--- 2024-10-31 Relations/RewritingQs.tex
@@
 
-\textbf{Primary Goal: A technical report that focuses on
-Abstract Rewriting in Constructive Setting }
+This document aims to bring together the various notes from report, rewriting qs, and counterexamples.
 
-\section{2024.10.31}
+\section{Todo}
+\subsection*{Week starting 11th November}
+\begin{enumerate}
+  \item In the report, give a classical proof that the $Inc$ Property
+  implies that no $R$-increasing sequence is bounded.
 
-Rewriting properties.
-Elementwise
-\begin{itemize}
-  \item NF
-  \item WN
-  \item SN
-  \item WCR
-  \item CR
-  \item NFP
-  \item UN$\to$
-  \item UN
-  \item RP
-  \item RP$-$
-  \item $\omega$-bound
-  \item Recurrent
-  \item CP (Cofinality property)
-  \item FB (Finite branching of rewrite steps)
-  \item DominatedByWF (Needed?)
+  Conclude that every relation satisfying $Inc$ also satisfies $RP$.
+
+  Therefore, the proof of Theorem 1.2.3(iii) using $RP$ instead of $Inc$
+  is generalizing the claim of the theorem (as stated in [TeReSe]).
+  \item Complete the proof in ARS.agda of Theorem 1.2.3.(iii)
+  \item Organize notes.tex into three sections: TODO, Open Qs, What we've proved. Make sure all notes from the other
+  tex files are sorted here correctly.
+  \item Tidy up and standardize the notation used in ars.agda and other agda files 
+  \item Carry on working through report.tex.  
+  \item 
+\end{enumerate}
+\subsection*{General todo}
+\begin{enumerate}
+
+  \item  Make the first argument to "being a normal form" implicit?
   \item Define WNFP to be:
@@
   Could even consider $SN^*$, $CR^*$ etc.
+  \item Define: Inc
+  \item Define: Ind
+  \item Define: $\mathrm{CR}^{\le 1}$
+  \item capture all classical properties/asssumptions we might want to use and justify their use. 
+  \item Principles we are considering
+  \begin{itemize}
+    \item Decidability of equality on $A$
+    \item Decidability of the relation $R$
+    \item When relevant, decidability of the given precicate $P$
+    \item Not-not-closure of being accessible
+    \item Not-not-closure of $R$
+    \item Not-not-closure of $P$
+    \item Decidability of whether a given element is an $R$-normal form
+    \item When relevant, local/element-wise versions of the above
+    \item Markov's principle:
+    \begin{itemize}
+      \item In $wfMin_0 \to wfSeq$.
+
+      Given a sequence $s : \nat \to A$, let $E(a) = \exists n \in \nat. s n \equiv a$.
+
+      Need: $\forall a. \lnot\lnot E(a) \to E(a)$, i.e.,
+      \[\lnot\lnot \big(\exists n \in \nat. s n \equiv a\big)
+            \to \big(\exists n \in \nat. s n \equiv a\big)\]
+
     \end{itemize}
-Most of these properties $P$ have a ``global'' version $P^\forall$, asserting that $\forall x. P(x)$ holds.
+  \end{itemize}
+  \item Write a guide to the code
+  \item More laws about closure operations: Monotonicity, idempotency
 
-Other properties that show up in classical ARS theory:
-\begin{itemize}
-  \item Inc
-  \item Ind
-  \item $\mathrm{CR}^{\le 1}$
-\end{itemize}
-Want to discuss these, and why we may or may not include them in our
-development.
+\end{enumerate}
+\newpage
+\section{Open Questions }
+\begin{enumerate}
+  \item
+     \[ WNg \land UN \to CRelem :
+     \forall (R : \mathscr{R} A) \to WN R \to \forall x \to is R -UN x \to is R -CR x \]
+     \item $WN R \to UN R \to \omega-bdd R \to SN R$ (1.2.3.ii-)
+      \item Finish formulating the ``compactness property".  Two candidates:
+       \item ``Every cocone for a given infinite sequence loops back to some point in the sequence"
+       \item ``If an $R^*$-sequence has a cocone then it's constant after some point on.''
+       \item is $\omega$-bounded implied by WN and the following confluence property:
+       $a \to^* n \in NF$, and $a \to b$ then $b \to^* n $.
+  \item (2024.10.10) Is being $R$-WN inductive?
+  \item (2024.10.10) Does $R$ being finitely branching imply
+   that, for an inductive $\phi$, if $\lnot \phi(x)$ then
+   $\exists y. Rxy \land \lnot \phi(y)$?
 
-Outline of the document:
-\begin{enumerate}
-  \item Create a diagram with implications between these, and
-  combinations of these, similar to the one in TeReSe.
-  \item Formalization of valid implications
-  \item Counterexamples: Compile a list/chart/graph of those relationships
-  which can be disproved. (A big part!!)
-  \item A list of classical properties, and elaboration of their meaning
-  and whether it's reasonable to assume them in a rewriting context.
-  (Discuss each, and its role in ARS theory.)
-  \item Well-foundedness: different constructive formulations, and relationships between them
-  \item ``Guide'' to the formalization code, GitHub repo
-  \item Discussion of open problems (Add a subsection of these at the end of each section?)
-  \item Conclusion
-\end{enumerate}
-
-\section{Established implications:}
-
-\begin{itemize}
-  \item SN implies $\omega$-bounded
-\end{itemize}
-
-\section{2024.10.10}
-
-\begin{itemize}
-  \item Look at restricting WFmin to $\lnot\lnot$-closed predicates
+  \item If WCR holds, is WN$\downarrow\subseteq$WN ?
+  \item Same question for next bullet in 2.2
+  \item Same for bullet 3 in 2.2 (but pointwise!)
+  \item \item Look at restricting WFmin to $\lnot\lnot$-closed predicates
   \item Status of important hypotheses:
@@
   \end{itemize}
-  \item When time permits, uniformize the notation (variable names, etc.) to the extent possible.
-\end{itemize}
-
-\section{2024.09.19}
-
-TODO item: Compile a list of counterexamples
-
-\section{2024.09.12}
-\begin{itemize}
-  \item Investigate \texttt{iii-lemma}.  (Is it false, or is there a classical proof?)
-  (No constructive proof?)
-  \item Look at variations of RP.
+  \item Can "sequential" properties like RP, RP-, isWFseq, isWFseq-, $\omega$-bounded, etc.,
+    be related to the cofinality property.
     \item What happens if properties involving sequences are reformulated for
   $R^r$? (Cannot decide whether the given sequence is finite or infinite.)
-  \item Look at RP- and WCR implies RP!
-  \item Can "sequential" properties like RP, RP-, isWFseq, isWFseq-, $\omega$-bounded, etc.,
-  be related to the cofinality property.
-\end{itemize}
-
-\section{Relations, ARS}
-
-\begin{enumerate}
-  \item Define logical and structurual operations on relations, proving laws about them.
-  \item Define closure operations on realtions, proving laws about them
-  \item Define properties such as transtivity etc.
-\end{enumerate}
-
-\subsection{Well-foundedness}
-
-Four notions:
-\begin{itemize}
-  \item Based on every element being accessible
-  \item Every inductive relation is universally true
-  \item Every non-empty set has a minimal element
-  \item No infinite sequence is decreasing
-\end{itemize}
-
-\section{Open research questions}
-\begin{enumerate}
-  \item Sufficient conditions for reversing the implications between notions of
-  well-foundedness?
   \item Knaster-Tarski Lemma: Most general form? Alternative formulations?
-  \item Syntax for closure operators allowing to prove the needed properties
-  uniformly/generically
-\end{enumerate}
-
-\section{To Do}
-\begin{enumerate}
-  \item Clean up the current development
-  \item More laws about closure operations: Monotonicity, idempotency
-  \item Refactor the ARS formalized results with the new development
   \item Knaster--Tarski in a well-founded setting: what additional
@@
 \end{enumerate}
-
-\subsection{Questions about well-foundedness}
-
+\subsection*{well-foundedness}
 \begin{enumerate}
@@
    Markov's principle, etc.
-
-   \item (2024.10.10) Is being $R$-WN inductive?
-   \item (2024.10.10) Does $R$ being finitely branching imply
-   that, for an inductive $\phi$, if $\lnot \phi(x)$ then
-   $\exists y. Rxy \land \lnot \phi(y)$?
+   \textsc{Remark.}
+   $\lnot\lnot$-closure of accessibility should solve problems 1 and 4.
 
@@
 
-\textsc{Remark.}
-$\lnot\lnot$-closure of accessibility should solve problems 1 and 4.
-
-\section{Open problems}
-
+\newpage 
+\section{What has been proven}
 \begin{itemize}
+  \item \sacomment{List all the constructive proofs we've put together!}
+  \item SN implies bounded
+  \item RP- implies RP
   \item The infinite haircomb refutes $WN \land RP \to \omega$-bounded.  But it is not WCR.
+  \item We have formalized proposition 1.1.9, 1.1.10, 1.1.11 from [TeReSe]. 
+  \item We have a proof for Theorem 1.2.1 (Newlman's Lemma) (though we have just one proof of multiple possible proofs).
+  \item We have a proof for all parts of Theorem 1.2.2
+  \item We have a proof for Theorem 1.2.3 i, iv. 
+  \item Reduction closure properties for SN, NF, UN, recurrent property.
 
@@
   Answer: yes, that is what we have proved classically.
-
-  \item Wait, does RP- actually imply RP????
-
-  \item RP- and $\omega$-bounded implies RP?
-  \item RP- and WCR imply RP?
-  \item
-  \[ WNg \land UN \to CRelem :
-  \forall (R : \mathscr{R} A) \to WN R \to \forall x \to is R -UN x \to is R -CR x \]
-  \item $WN R \to UN R \to \omega-bdd R \to SN R$ (1.2.3.ii-)
 \end{itemize}
 
+\newpage
+
 \end{document}

### 2024-11-14 Relations/Report.tex
Theorem 1.2.3 progress

@@
 \end{dfn}
+
+\subsection{Recurrence property and increasing relations}
+
+In [TeReSe], a relation $R \sse A \times A$ is called \emph{increasing} if there
+exists a ``size function'' $|-| : A \to \nat$ satisfying, for all $x, y \in A$,
+ \[ Rxy \to |x| < |y| \]
+
+\begin{prop}
+  If $R$ is increasing, then no infinite $R$-increasing sequence is bounded.
+\end{prop}
+\begin{proof}
+  Let $(a_i) = a_0 \to a_1 \to a_2 \to \cdots$ be an $R$-increasing sequence
+  and suppose that $(a_i)$ is bounded.  Let $b$ be the bound, so that $a_i \to b$ for all $i$.
+
+  If $m = |b|$ then we have
+  \[ 0 \le |a_0| < |a_1| < |a_2| < \cdots < |a_m| < |b| = m \]
+  % \[ m > |a_m| > |a_{m-1}| > \cdots > |a_0| \ge 0 \]
+  which is a contradiction, since there are only $m-1$ integers strictly less than $m$.
+\end{proof}
+
+It follows that every relation that is increasing in the sense of [TeReSe]
+vacuously satisfies the RP condition.
+
+\begin{cor}
+  If $R$ is increasing, then $R$ has the recurrence property.
+\end{cor}
 

### 2024-11-21 Relations/Report.tex
report: counterexamples fleshed out. implications progress

@@
 
-\section{Definitions}
+\section{Definitions} \label{section:Definitions}
 The most interesting work we have carried out in investigating Chapter 1 of TeReSe has resulted from trying to provide constructive proofs for Newman's lemma, the Knaster-Tarski lemma, theorem 1.2.2 and theorem 1.2.3.
@@
       \end{tikzpicture}
-      \caption{An example of an bounded sequence.}
+      \caption{An example of a bounded sequence.}
 
@@
 \section{Implications}
-We now look into the interrelation of the various properties defined in Section 2. Our aim is to expand on the
+We now look into the interrelation of the various properties defined in Section~\ref{section:Definitions}. Our aim is to expand on the
 connections made in Figure 1.8 of [TeReSe] (p.19).
 
+The following are the implications we have proven in Agda, along with a reference to the name of the proof in Agda. Where appropriate we indicate
+which classical assumptions were used as part of the proof.
+
+\begin{itemize}
+  \item SN and WCR $\implies$ CR
+
+\texttt{NewmansLemma : $\mathnormal{\forall}$ \{R : $\mathbb{R}$ A\} $\to$ SN R $\to$ weakly-confluent R $\to$ confluent R}
+
+We have also provided a proof elementwise making use of the classical principal 
+about the decidability of $R$ being minimal.
+
+\texttt{SN$\land$UN$\to$CRelem :\newline $\forall$ (R : $\mathbb{R}$ A) $\to$ decMin (~R R) $\to$ $\forall$ x $\to$ is R -SN x $\to$ is R -UN x$\to$ is R -CR x}
+
+\sacomment{How to one line this consistently and in a pretty way?}
+
+\item{CP $\implies$ CR}
+
+\texttt{iv : CP R $\to$ confluent R}
+
+This is theorem 1-2-3 iv in [TeReSe]
+
+\item{WN and UN $\implies$ CR}
+
+\texttt{ii : WN R $\times$ UN R $\to$ confluent R}
+
+This is theorem 1-2-2 ii in [TeReSe]
+
+\item{WN and UN $\implies$ bounded}
+
+\texttt{i : WN R → UN R → bounded R}
+
+\sacomment{Going to have to find a way to neatly represent the implications}
+
+\sacomment{note to self, tidy up below with references to agda code}
+
+\item{WN and UN$\to$ $\implies$ bounded}
+
+\item{WN and UN and RP $\implies$ wfSeq - (~ R)}
+\item {CR $\implies$ WCR}
+\item {NF $implies$ UN}
+\item {SN and WCR $\implies$ UN and WN}
+\item {Ind and Inc $\implies$ SN} \sacomment{I don't think we have 
+a proof of this, should we include it, include it with a note that we're taking [TeReSe]'s word on it?}
+\item {WCR, WN, and, Inc $\implies$ SN}
+\item {WCR, WN, and RP $\implies$} 
+\item {CR and NF $\implies$ UN}
+\item {CR $^{\leq1} \implies$ CR}
+
+\end{itemize}
+
+\newpage
 \section{Counterexamples}
@@
       % Nodes
-      \node (x) {x};
+      \node (x) {a};
       \node (n) [left of=x, xshift=-1cm] {n \in NF};
-      \node (y) [right of=x, xshift=1cm] {y};
-      \node (z) [right of=y] {z};
+      \node (y) [right of=x, xshift=1cm] {b};
+      \node (z) [right of=y] {c};
 
@@
       % Nodes
-      \node (x) {x};
+      \node (x) {a};
 
@@
 \begin{itemize}
-  \item bounded and RP implies SN
-  \item bounded and RP implies WN
+  \item bounded and RP $\implies$ SN
+  \item bounded and RP $\implies$ WN 
 \end{itemize}
@@
 \subsection*{Counterexample 4}
+An infinite sequence
   \begin{center}
@@
       % Define the nodes
-      \node (a) at (0, 0) {$a$};
-      \node (b) at (1, 0) {$b$};
+      \node (a) at (0, 0) {$f_0$};
+      \node (b) at (1, 0) {$f_1$};
       \node (dots) at (2, 0) {$...$};
@@
       \draw[->] (b) -- (dots);
-
       \end{tikzpicture}
@@
 Counterexample to:
+\begin{itemize}
+  \item WN
+  \item bounded
+  \item RP $\implies$ bounded
+  \item WCR $\implies$ WN
+  \item CR $\implies$ WN
+  \item CR and CP $\implies$ WN
+  \item CR and CP $\implies$ bounded
+\end{itemize}
 
+\subsection*{Counterexample 5}
+An infinite sequence with a bound that is a normal form.
+\begin{center}
+
+  \begin{tikzpicture}
+      % Define the nodes inside the region f
+      \node (f0) at (0, 0) {$f_0$};
+      \node (f1) at (1, 0) {$f_1$};
+      \node (dots) at (2, 0) {$...$};
+
+      % Draw the arrows between the nodes inside the region f
+      \draw[->] (f0) -- (f1);
+      \draw[->] (f1) -- (dots);
+      \draw[->] (f1) -- (dots);
+
+      % Define the nodes outside the region f
+      \node (a) [below=of dots, yshift=-.25cm] {\parbox{2cm}{\centering $n\in NF$ }};
+
+          % Draw the arrows between the nodes inside and outside the region f sds
+
+          \draw[->>] (f0) -- (a);
+          \draw[->>] (f1) -- (a);
+          \draw[->>] (dots) -- (a);
+      \end{tikzpicture}
+
+    \end{center}
+Counterexample to:
+\begin{itemize}
+  \item WN $\implies$ SN
+  \item WN and CR $\implies$ SN
+  \item WN, CR and, bounded $\implies$ SN
+\end{itemize}
+
+\subsection*{Counterexample 6}
+An infinite sequence with a bound that is a normal form where each element
+of the sequence has a single step relation to the initial element of the sequence.
+\begin{center}
+  \begin{tikzpicture}
+      % Define the nodes inside the region f
+      \node (f0) at (0, 0) {$f_0$};
+      \node (f1) at (1, 0) {$f_1$};
+      \node (dots) at (2, 0) {$...$};
+
+      % Draw the arrows between the nodes inside the region f
+      \draw[->] (f0) -- (f1);
+      \draw[->] (f1) -- (dots);
+      \draw[->] (f1) -- (dots);
+      \draw[->] (f1) to [bend right=20] (f0);
+      \draw[->] (dots) to [bend right=50] (f0);
+
+      % Define the nodes outside the region f
+      \node (a) [below=of dots, yshift=-.25cm] {\parbox{2cm}{\centering $n\in NF$ }};
+
+          % Draw the arrows between the nodes inside and outside the region f sds
+
+          \draw[->>] (f0) -- (a);
+          \draw[->>] (f1) -- (a);
+          \draw[->>] (dots) -- (a);
+      \end{tikzpicture}
+
+    \end{center}
+Counterexample to:
+\begin{itemize}
+  \item RP
+\end{itemize}
+
+\subsection*{Counterexample 7}
+An "infinite haircomb"
+\begin{center}
+  \begin{tikzpicture}
+      % Define the nodes inside the region f
+      \node (f0) at (0, 0) {$f_0$};
+      \node (f1) at (1, 0) {$f_1$};
+      \node (f2) at (2, 0) {$f_2$};
+      \node (dots) at (3, 0) {$...$};
+
+      \node (n0) at (0, -1) {$n_0$};
+      \node (n1) at (1, -1) {$n_1$};
+      \node (n2) at (2, -1) {$n_2$};
+      \node (dots2) at (3, -1) {$...$};
+
+      \draw[->] (f0) -- (f1);
+      \draw[->] (f1) -- (f2);
+      \draw[->] (f2) -- (dots);
+
+      \draw[->] (f0) -- (n0);
+      \draw[->] (f1) -- (n1);
+      \draw[->] (f2) -- (n2);
+      \draw[->] (dots) -- (dots2);
+
+      \end{tikzpicture}
+
+    \end{center}
+Counterexample to:
+\begin{itemize}
+  \item WN $\implies$ WCR
+  \item WN $\implies$ bounded
+  \item WN $\implies$ SN
+  \item WN and RP $\implies$ SN
+\end{itemize}
 \section{Well-foundedness}

### 2024-11-21 Relations/Report.tex
ars

@@
 % \input{packages}
+
+\usepackage{booktabs}
+
 \input{macros}
@@
 \begin{document}
+\renewcommand{\arraystretch}{1.3}
 
@@
 \section{Implications}
+{\small
 We now look into the interrelation of the various properties defined in Section~\ref{section:Definitions}. Our aim is to expand on the
@@
 
-\texttt{i : WN R → UN R → bounded R}
+\texttt{i : WN R $\to$ UN R $\to$ bounded R}
 
@@
 \end{itemize}
+}
+
+\subsection{Summary table}
+BP = boundedness property
+
+Table listing highest "confluence" property implied
+by the conjunction of row and column.
+\begin{tabular}{@{}l@{\quad}l@{\quad}l@{\quad}l@{\quad}l@{}}
+  \toprule
+  CP & CR & WCR & WNFP & WUN \\
+  \midrule
+  SN  & & & & \\
+  WN  & & & & \\
+  WN*  & & & & \\
+  BP $\land$ CP   & & & & \\
+  BP  & & & & \\
+  CP  & & & & \\
+  \bottomrule
+\end{tabular}
+
+Table listing highest "normalization" property implied 
+by the conjunction of row and column.
+\begin{tabular}{@{}l@{\quad}l@{\quad}l@{\quad}l@{\quad}l@{}}
+  \toprule
+  CP & CR & WCR & WNFP & WUN \\
+  \midrule
+  SN  & & & & \\
+  WN  & & & & \\
+  WN*  & & & & \\
+  BP $\land$ CP   & & & & \\
+  BP  & & & & \\
+  CP  & & & & \\
+  \bottomrule
+\end{tabular}
 

### 2024-11-26 Relations/Report.tex
Updates to implication table

@@
   The \emph{equivalence relation} of $R$ is the smallest relation $R^=$ that contains $R$ and is reflexive, transitive, and symmetric.
+\end{dfn}
+
+\begin{dfn}
+  A relation $R$ has the \emph{weak normal form property} (WNFP) if
+ $a \tto b$ and $a \tto c$  $\implies$
+ $c \tto b$, for all $a,c \in A$ and all normal form $b \in A$.
 \end{dfn}
@@
 
-\item{WN and UN and RP $\implies$ wfSeq - (~ R)}
+\texttt{i+ : WN R $\to$ UN$\to$ R $\to$ bounded R}
+
+\item{WN and UN and RP $\implies$ wfSeq - ($\sim$ R)}
+
+\texttt{ii3- :  WN R $\to$ UN R $\to$ RP R $\to$ isWFseq- ($\sim$R R)}
+
 \item {CR $\implies$ WCR}
+
+\texttt{CR$\to$WCR : CR R $\to$ WCR R }
+
 \item {NF $implies$ UN}
+\sacomment{Need to prove}
+
 \item {SN and WCR $\implies$ UN and WN}
+\sacomment{Need to proove}
+\texttt{}
+
 \item {Ind and Inc $\implies$ SN} \sacomment{I don't think we have
 a proof of this, should we include it, include it with a note that we're taking [TeReSe]'s word on it?}
+
 \item {WCR, WN, and, Inc $\implies$ SN}
-\item {WCR, WN, and RP $\implies$}
-\item {CR and NF $\implies$ UN}
+
+\item {WCR, WN, and RP $\implies$ SN}
+
+\item {CR $\implies$ NF $\implies$ UN}
+
+\texttt{i-4 : confluent R $\to$ NFP R $\to$ UN R}
+
 \item {CR $^{\leq1} \implies$ CR}
+
+\texttt{iv : CP R $\to$ confluent R}
 
@@
 by the conjunction of row and column.
-\begin{tabular}{@{}l@{\quad}l@{\quad}l@{\quad}l@{\quad}l@{}}
+
+\begin{tabular}{@{}l@{\quad}l@{\quad}l@{\quad}l@{\quad}l@{\quad}l@{}}
   \toprule
-  CP & CR & WCR & WNFP & WUN \\
+  & CP & CR & WCR & WNFP & WUN  \\
   \midrule
-  SN  & & & & \\
-  WN  & & & & \\
-  WN*  & & & & \\
-  BP $\land$ CP   & & & & \\
-  BP  & & & & \\
-  CP  & & & & \\
+  SN  & ? & CR & CR & (Should be CR?)  & ?  \\
+  WN  & ? & CR & (Not CR) & ? & ? \\
+  WN* & ? & CR & ? & ? & ? \\
+  BP $\land$ CP & ? & CR & ? & ? & ? \\
+  BP  & ? & CR & ? & ? & ? \\ 
+  CP  & ? & CR & ? & ? & ? \\
   \bottomrule
@@
 by the conjunction of row and column.
-\begin{tabular}{@{}l@{\quad}l@{\quad}l@{\quad}l@{\quad}l@{}}
+
+\begin{tabular}{@{}l@{\quad}l@{\quad}l@{\quad}l@{\quad}l@{\quad}l@{}}
   \toprule
-  CP & CR & WCR & WNFP & WUN \\
+  & CP & CR & WCR & WNFP & WUN \\
   \midrule
-  SN  & & & & \\
-  WN  & & & & \\
-  WN*  & & & & \\
-  BP $\land$ CP   & & & & \\
-  BP  & & & & \\
-  CP  & & & & \\
+  SN  &?& SN & SN & SN & SN \\
+  WN  &?& (Not SN) & (Not SN) & ? & ? \\
+  WN*  &?& ? & ? & ? & ? \\
+  BP $\land$ CP   &?& ? & ? & ? & ? \\
+  BP  &?& ? & ? & ? & ? \\
+  CP  &?& (not CP or BP) & ? & ? & ? \\
   \bottomrule

### 2024-12-04 Relations/CounterExamples.tex
ARS-stuff
fixed counterexample 3
ARSwork
created notes.tex to merge various scattered bullet points

@@
 \documentclass{article}
-\usepackage{tikz-cd}
-\usepackage{amsmath}
-\usepackage{mathrsfs}
 
-\usetikzlibrary{positioning,shapes.geometric,fit}
+\input{macros}
 
@@
     \item WCR $\to$ CR
+    \item WCR and WN $\to$ CR
+    \item WCR and WN $\to$ SN
     \item \mbox{WCR R $\to$ $\forall$ a b $\to$ is R -NF b $\to$ (R *) a b $\to$ $\forall$ c $\to$ (R *) a c $\to$ (R *) c b}
+    \item IOW, WCR $\to$ WNFP
 \end{itemize}
@@
 
-\subsection{Counterexample 3}
+\subsection{Counterexample 3} \sacomment{This counterexample doesn't work. Keeping it as a useful reminder.}
 \begin{center}
@@
           % Draw the arrows between the nodes inside and outside the region f
-      \draw[->>] (fi) -- (a);
+          \draw[->>] (fi) to [bend right=15] (a);
+          \draw[->>] (a) to [bend right=15] (fi);
           \draw[->>] (fi+1) -- (a);
           \draw[->>] (dots2) -- (a);
-      \draw[->>] (y) -- (fi);
+          \draw[->>] (fi) -- (y);   
       \end{tikzpicture}
@@
     \begin{itemize}
+      \item ***** DOES NOT WORK ******
       \item RP-$\to$RP 
-  \item RP-$\land$WCR$\to$RP
+      \item RP-$\land$WCR$\to$RP \textcolor{red}{NO< NEEDS A NEW CE}
 \end{itemize}
+
+\subsection{Other questions}
+\begin{enumerate}
+  \item If WCR holds, is WN$\downarrow\subseteq$WN ?
+  \item Same question for next bullet in 2.2
+  \item Same for bullet 3 in 2.2 (but pointwise!)
+  \item Do RP- $\land$ WCR imply RP?
+\end{enumerate}
 \subsection{ARS in Agda}
@@
     \item $\omega$-bounded
+    \item RP $\to$ $\omega$-bounded
     \item $WCR \to WN$
@@
   with each $a_n \to a_\infty$ and $a_\infty$ a normal form.
+
+  Counterexample to:
+  \begin{itemize}
+    \item WN $\to$ SN
+    \item WN, CR $\to$ SN
+    \item WN, CR, $\omega$-bounded $\to$ SN
+  \end{itemize}
+
   \item Infinite sequence $a_0 \to a_1 \to \cdots$, together with links
@@
     \item $WN\to WCR$
+    \item $WN\to \omega-bounded$
     \item $WN \to SN$
+    \item $WN,RP \to SN$
   \end{itemize}
@@
 
+\section{Taken from other files and needs sorting into the above}
+\sacomment{Check the tex file for the notes below which have been commented out.}
+% -- Move to counterexamples; delete
+%   -- Not provable: n <- x -> z
+%   -- WN∧UN→CRelem : ∀ x → is R -WN x → is R -UN x → is R -CR x
+%   -- WN∧UN→CRelem x x∈WN x∈UN  = Newmans-Lemma.CR→CRelem R (ii ({! x∈WN  !} , {!   !})) x -- Can we do this or am I being too bullheaded in comparing x∈UN and UN etc?
+
 \end{document}

### 2024-12-04 Relations/notes.tex
Theorem 1.2.3 progress
report: counterexamples fleshed out. implications progress

@@
 \input{macros}
+
+\usepackage{pifont}% http://ctan.org/pkg/pifont
+\newcommand{\cmark}{\quad\ding{51}}%
+\newcommand{\xmark}{\quad\ding{55}}%
+
+\newcommand{\thra}{\twoheadrightarrow}
+\newcommand{\thla}{\twoheadleftarrow}
+\newcommand{\thlra}{{\thla\!\!\thra}}
 
@@
 
+\subsection*{November 21}
+
+Four local ``normal form properties'':
+\begin{enumerate}
+  \item $WNFP(a) : \forall n \in NF. (a \tto n) \to \forall b. (a \tto b) \to (b \tto n)$
+    "$a$ all reducts of $a$ reduce to $a$'s normal form, if it exists``
+  \item $NFP(a) : \forall n \in NF. (a \tto n) \to \forall b. (a \thlra b) \to (b \tto n)$
+    "$a$ all converta of $a$ reduce to $a$'s normal form, if it exists``
+  \item $WUN(a) : \forall n m \in NF. (a \tto n) \to (a \tto m) \to n \equiv m$
+    "$a$ is reducible to at most one normal form"
+  \item $UN(a) : \forall n m \in NF. (a \thlra n) \to (a \thlra m) \to n \equiv m$
+    "$a$ is convertible to at most one normal form''
+\end{enumerate}
+
 \section{Todo}
+
+Look at Exercise 1.3.22
+
 \subsection*{Week starting 11th November}
 \begin{enumerate}
-  \item In the report, give a classical proof that the $Inc$ Property
+  \item[\cmark] In the report, give a classical proof that the $Inc$ Property
   implies that no $R$-increasing sequence is bounded.

### 2024-12-05 Relations/Report.tex
report_update

@@
 \date{\today}
+
+\usepackage{pifont}% http://ctan.org/pkg/pifont
+\newcommand{\cmark}{\quad\ding{51}}%
+\newcommand{\xmark}{\quad\ding{55}}%
+
+\newcommand{\thra}{\twoheadrightarrow}
+\newcommand{\thla}{\twoheadleftarrow}
+\newcommand{\thlra}{{\thla\!\!\thra}}
 
@@
 
+\subsection{Double-check: What has been proven}
+\begin{itemize}
+  \item \sacomment{List all the constructive proofs we've put together!}
+  \item SN implies bounded
+  \item RP- implies RP
+  \item The infinite haircomb refutes $WN \land RP \to \omega$-bounded.  But it is not WCR.
+  \item We have formalized proposition 1.1.9, 1.1.10, 1.1.11 from [TeReSe].
+  \item We have a proof for Theorem 1.2.1 (Newlman's Lemma) (though we have just one proof of multiple possible proofs).
+  \item We have a proof for all parts of Theorem 1.2.2
+  \item We have a proof for Theorem 1.2.3 i, iv.
+  \item Reduction closure properties for SN, NF, UN, recurrent property.
+
+  So, does $WN, RP, WCR$ imply $\omega$-bounded?
+  Answer: yes, that is what we have proved classically.
+\end{itemize}
+
 \newpage
@@
 \end{itemize}
+
 \section{Well-foundedness}
@@
     \end{enumerate}
-
 \end{dfn}
@@
 
-\section{Notes}
+  \section{Open Questions }
+  \begin{enumerate}
+    \item Complete the Wellfoundedness implications:
+       \[ WNg \land UN \to CRelem :
+       \forall (R : \mathscr{R} A) \to WN R \to \forall x \to is R -UN x \to is R -CR x \]
+       \item $WN R \to UN R \to \omega-bdd R \to SN R$ (1.2.3.ii-)
+        \item Finish formulating the ``compactness property".  Two candidates:
+         \item ``Every cocone for a given infinite sequence loops back to some point in the sequence"
+         \item ``If an $R^*$-sequence has a cocone then it's constant after some point on.''
+         \item is $\omega$-bounded implied by WN and the following confluence property:
+         $a \to^* n \in NF$, and $a \to b$ then $b \to^* n $.
+    \item (2024.10.10) Is being $R$-WN inductive?
+    \item (2024.10.10) Does $R$ being finitely branching imply
+     that, for an inductive $\phi$, if $\lnot \phi(x)$ then
+     $\exists y. Rxy \land \lnot \phi(y)$?
+
+    \item If WCR holds, is WN$\downarrow\subseteq$WN ?
+    \item Same question for next bullet in 2.2
+    \item Same for bullet 3 in 2.2 (but pointwise!)
+    \item \item Look at restricting WFmin to $\lnot\lnot$-closed predicates
+    \item Status of important hypotheses:
+      \begin{itemize}
+        \item Deciding whether a given element $x$ reduces to a given element $y$
+        (Is $R$ itself decidable?)
+        \item Deciding whether a given element $x$ reduces to some element $y$
+        (Is being an $R$-normal form decidable?)
+
+        {\textcolor{red}{This is needed to show that SN $\Rightarrow$ WN.}}
+
+        \item If a given element $x$ is \emph{not} a normal form,
+        exhibiting some element $y$ that it reduces to.
+        (This is related to DeMorgan/Markov/etc. properties that came up in WF file.)
+
+        \item Does UN-lemma \emph{require} the decidability assumption?
+      \end{itemize}
+    \item META questions: Which of the ARS theorems can be made ``local/pointwise'',
+    for example,
+    \begin{itemize}
+      \item NL+: $WCR(R) \land SN(x) \to CR(x)$?  (Yes?)
+      \item NL++: $WCR(x) \land SN(x) \to CR(x)$? (No.)
+    \end{itemize}
+    \item Can "sequential" properties like RP, RP-, isWFseq, isWFseq-, $\omega$-bounded, etc.,
+      be related to the cofinality property.
+      \item What happens if properties involving sequences are reformulated for
+    $R^r$? (Cannot decide whether the given sequence is finite or infinite.)
+    \item Knaster-Tarski Lemma: Most general form? Alternative formulations?
+    \item Knaster--Tarski in a well-founded setting: what additional
+    hypotheses are necessary?
+  \end{enumerate}
+
+  \subsection*{Questions about Well-foundedness}
+  \begin{enumerate}
+    \item For a given element $x$, is the property of
+    being accessible $\lnot\lnot$-closed? I.E.,
+    Does $x$ being $\lnot\lnot$-accessible imply that $x$ is accessible?
+    (Conjecture: No.)
+
+    \item As a special case, does being weakly (accessible) well-founded imply being $\lnot\lnot$-wellfounded?
+    (Conjecture: No.)
+
+    Also: Same question about inductive notion of well-foundedness.
+
+    \item ($\star$) Given a well-founded relation, does every non-empty subset
+    have a minimal element?
+
+    \emph{Problem.} Need to decide whether, for a given $x \in U$,
+     the set $\{y | Ryx\}$ is empty.
+
+     \item IF every non-empty subset has a minimal element, does this imply
+     either of the weak forms of well-foundedness: $\mathtt{isWFacc-}$ or
+     $\mathtt{isWFind-}$ ?
+
+     \item Does $\mathtt{isWFmin-}$ imply $\mathtt{isWFacc-}$ or $\mathtt{isWFind-}$?
+
+     \emph{Problem.} Need to go from $\lnot (\forall y. R y d \to \phi y)$
+     and $\forall y. R y d \to \lnot \lnot \phi y$ to $\bot$.
+
+     In terms of accessibility, it should suffices to assume accessibility is
+     $\lnot\lnot$-closed, since being related to y is not relevant for that. (?)
+
+     \item Does sequential well-foundedness (no decreasing sequence) imply
+     any of the other notions, e.g., \texttt{WFmin-} ?
+
+     \emph{Note.}  This seems to require the most classical assumptions:
+     $\lnot\lnot$-closure of $\phi$, relativized De Morgan law,
+     Markov's principle, etc.
+     \textsc{Remark.}
+     $\lnot\lnot$-closure of accessibility should solve problems 1 and 4.
+  \end{enumerate}
+  \newpage
+
+\section{Todo}
+
+\subsection{Main themes}
+\begin{enumerate}
+  \item Clean up the implications around recurrence properties:
+  \begin{itemize}
+    \item RP iff cofinality and Boundedness?
+    \item What is the ``recurrent'' generalization of WN?
+    \item What is the ``recurrent'' generalization of SN?
+    \item The role of WCR in the proof of our generalization of Thm. 1.2.3(iii)
+  \end{itemize}
+  \item Complete the ``design'' of the chart(s) with implications?
+  \item Complete the proof of Theorem 1.2.3
+  \item Address outstanding questions about wellfoundness implications.
+  \begin{itemize}
+    \item WFseq implies WFmin? (Assuming decMin)
+    \item WFacc implies $WFmin_0$? (Assuming decMin)
+    \item DecMin suffices for $SN\to WN$, but what is the optimal \emph{necessary} condition?
+    \item Relationship between these, and De Morgan's laws.
+  \end{itemize}
+\end{enumerate}
+
+\subsection{General todo list}
+\begin{enumerate}
+  \item Look at Exercise 1.3.22
+  \item  Make the first argument to "being a normal form" implicit?
+  \item Define WNFP to be:
+  \[\forall a b c \to b \in NF \to a R^* b \to a R^* c \to c R^* b \]
+  \item Does WNFP and WN imply CR?  Looks like it!
+  \item  Another interesting one? $WN^*$: hereditarily $WN$ ($WN$ for the reduction graph starting from a given element $x$.)
+
+  Could even consider $SN^*$, $CR^*$ etc.
+  \item Define: Inc
+  \item Define: Ind
+  \item Define: $\mathrm{CR}^{\le 1}$
+  \item capture all classical properties/asssumptions we might want to use and justify their use.
+  \item Principles we are considering
+  \begin{itemize}
+    \item Decidability of equality on $A$
+    \item Decidability of the relation $R$
+    \item When relevant, decidability of the given precicate $P$
+    \item Not-not-closure of being accessible
+    \item Not-not-closure of $R$
+    \item Not-not-closure of $P$
+    \item Decidability of whether a given element is an $R$-normal form
+    \item When relevant, local/element-wise versions of the above
+    \item Markov's principle:
+    \begin{itemize}
+      \item In $wfMin_0 \to wfSeq$.
+
+      Given a sequence $s : \nat \to A$, let $E(a) = \exists n \in \nat. s n \equiv a$.
+
+      Need: $\forall a. \lnot\lnot E(a) \to E(a)$, i.e.,
+      \[\lnot\lnot \big(\exists n \in \nat. s n \equiv a\big)
+            \to \big(\exists n \in \nat. s n \equiv a\big)\]
+
+    \end{itemize}
+  \end{itemize}
+  \item Write a guide to the code
+  \item More laws about closure operations: Monotonicity, idempotency
+\end{enumerate}
+
+\subsection*{Week starting 11th November}
+\begin{enumerate}
+  \item[\cmark] In the report, give a classical proof that the $Inc$ Property
+  implies that no $R$-increasing sequence is bounded.
+
+  Conclude that every relation satisfying $Inc$ also satisfies $RP$.
+
+  Therefore, the proof of Theorem 1.2.3(iii) using $RP$ instead of $Inc$
+  is generalizing the claim of the theorem (as stated in [TeReSe]).
+  \item Complete the proof in ARS.agda of Theorem 1.2.3.(iii)
+  \item Organize notes.tex into three sections: TODO, Open Qs, What we've proved. Make sure all notes from the other
+  tex files are sorted here correctly.
+  \item Tidy up and standardize the notation used in ars.agda and other agda files
+  \item Carry on working through report.tex.
+\end{enumerate}
+
+\newpage
+
+\section{Misc. Notes}
+
+\subsection*{November 21}
+Four local ``normal form properties'':
+\begin{enumerate}
+  \item $WNFP(a) : \forall n \in NF. (a \tto n) \to \forall b. (a \tto b) \to (b \tto n)$
+    "$a$ all reducts of $a$ reduce to $a$'s normal form, if it exists``
+  \item $NFP(a) : \forall n \in NF. (a \tto n) \to \forall b. (a \thlra b) \to (b \tto n)$
+    "$a$ all converta of $a$ reduce to $a$'s normal form, if it exists``
+  \item $WUN(a) : \forall n m \in NF. (a \tto n) \to (a \tto m) \to n \equiv m$
+    "$a$ is reducible to at most one normal form"
+  \item $UN(a) : \forall n m \in NF. (a \thlra n) \to (a \thlra m) \to n \equiv m$
+    "$a$ is convertible to at most one normal form''
+\end{enumerate}
+
 \subsection{Notes from 08.29}
-
 \begin{enumerate}

### 2024-12-12 Relations/Report.tex
Report updated, other tex files now redundant

@@
     hypotheses are necessary?
+    \item Show SN and WNFP $\to$ CR : SN R $to$ WNFP R $to$ CR R (or, what combination of properties with WNFP gets us to CR)
+    \item Major: Find a classical or constructive solution to theorem 1-2-3 ii. Note, we have a counterexample showing that we 
+    cannot solve this whilst using recurrence property and boundedness rather than ind(uctive) and inc(reasing). The counterexample is the self loop on an element. 
+    \item is $\omega$-bounded implied by WN and the following confluence property:
+    $a \to^* n \in NF$, and $a \to b$ then $b \to^* n $. (This is a weaker form of WNFP)
   \end{enumerate}
@@
   \item Complete the ``design'' of the chart(s) with implications?
+  \begin{itemize}
+    \item   Look at Exercise 1.3.22 (Show UN $\to$ UN$^\to$ but not conversely. Show a counterexample to WCR and UN$^\to$ $\to$ UN. Find a counter example to WCR and WN $\to$ Ind)
+  \end{itemize}
   \item Complete the proof of Theorem 1.2.3
@@
   \end{itemize}
+  \item Complete the classical properties section
+  \item Complete the guide to the code section
+  \item Miscellaneous
+  \begin{itemize}
+    \item   Make the first argument to "being a normal form" implicit?
+    \item   Define: Inc in report
+    \item   Define: Ind in report 
+    \item   Define: $\mathrm{CR}^{\le 1}$ in report
+    \item   More laws about closure operations: Monotonicity, idempotency
+    \item   Tidy up and standardize the notation used in ars.agda and other agda files
+
+  \end{itemize}
 \end{enumerate}
@@
 \begin{enumerate}
-  \item Look at Exercise 1.3.22
-  \item  Make the first argument to "being a normal form" implicit?
-  \item Define WNFP to be:
-  \[\forall a b c \to b \in NF \to a R^* b \to a R^* c \to c R^* b \]
-  \item Does WNFP and WN imply CR?  Looks like it!
-  \item  Another interesting one? $WN^*$: hereditarily $WN$ ($WN$ for the reduction graph starting from a given element $x$.)
-
+  \item  Another interesting one?
+$WN^*$: hereditarily $WN$ ($WN$ for the reduction graph starting from a given element $x$).
 Could even consider $SN^*$, $CR^*$ etc.
-  \item Define: Inc
-  \item Define: Ind
-  \item Define: $\mathrm{CR}^{\le 1}$
-  \item capture all classical properties/asssumptions we might want to use and justify their use.
-  \item Principles we are considering
-  \begin{itemize}
-    \item Decidability of equality on $A$
-    \item Decidability of the relation $R$
-    \item When relevant, decidability of the given precicate $P$
-    \item Not-not-closure of being accessible
-    \item Not-not-closure of $R$
-    \item Not-not-closure of $P$
-    \item Decidability of whether a given element is an $R$-normal form
-    \item When relevant, local/element-wise versions of the above
-    \item Markov's principle:
-    \begin{itemize}
-      \item In $wfMin_0 \to wfSeq$.
-
-      Given a sequence $s : \nat \to A$, let $E(a) = \exists n \in \nat. s n \equiv a$.
-
-      Need: $\forall a. \lnot\lnot E(a) \to E(a)$, i.e.,
-      \[\lnot\lnot \big(\exists n \in \nat. s n \equiv a\big)
-            \to \big(\exists n \in \nat. s n \equiv a\big)\]
-
-    \end{itemize}
-  \end{itemize}
-  \item Write a guide to the code
-  \item More laws about closure operations: Monotonicity, idempotency
-\end{enumerate}
-
-\subsection*{Week starting 11th November}
-\begin{enumerate}
-  \item[\cmark] In the report, give a classical proof that the $Inc$ Property
-  implies that no $R$-increasing sequence is bounded.
-
-  Conclude that every relation satisfying $Inc$ also satisfies $RP$.
-
-  Therefore, the proof of Theorem 1.2.3(iii) using $RP$ instead of $Inc$
-  is generalizing the claim of the theorem (as stated in [TeReSe]).
-  \item Complete the proof in ARS.agda of Theorem 1.2.3.(iii)
-  \item Organize notes.tex into three sections: TODO, Open Qs, What we've proved. Make sure all notes from the other
-  tex files are sorted here correctly.
-  \item Tidy up and standardize the notation used in ars.agda and other agda files
-  \item Carry on working through report.tex.
+\sacomment{Is this what we have already shown
+  in the reduction closure properties? If so we can delete this. If not it should be moved to open questions}
 \end{enumerate}
@@
 \begin{enumerate}
-  \item Try to ``fix'' CP by changing $R$ into $R^r$
   \item Finish formulating the ``compactness property".  Two candidates:
@@
   \end{itemize}
-  \item Add the definition of "recurrent element"
-\end{enumerate}
-
-\subsection{09.05}
-\begin{enumerate}
-  \item done: WN, UN, RP imply SN (classical)
-  \item need: omega bounded and RP implies SN (classical)
-  \item need: omega bounded and RP implies SN (constructive)
-  \item do we need $s_0 \to^* s_c$ in the proof?
-  \item is $\omega$-bounded implied by WN and the following confluence property:
-  $a \to^* n \in NF$, and $a \to b$ then $b \to^* n $.
-  \item Remark before 1.2? (Exercise 1.3.21)
-  \item Make the first argument to "being a normal form" implicit?
-\end{enumerate}
-
-\newcommand{\RP}{\mathsf{RP}}
-\newcommand{\NF}{\mathsf{NF}}
-\newcommand{\UN}{\mathsf{UN}}
-\newcommand{\UNto}{\mathsf{UN}{\to}}
-\newcommand{\SN}{\mathsf{SN}}
-\newcommand{\WN}{\mathsf{WN}}
-\newcommand{\from}{\leftarrow}
+\end{enumerate} \sacomment{This is our recurrence property right? If so, we can just delete this.}
 
@@
 \begin{itemize}
-  \item It seems that part (i) of the theorem can be strengthened to only
-  assume $\UNto(R)$ instead of $\UN(R)$:
-  \[ \WN(R) \land \UNto(R) \to \omega{-}\text{bounded}(R) \tag{i} \]
-  \textcolor{red}{(See ARS.agda i+)}
-  \item The analogue of part (ii) of the theorem is unprovable, namely
-  \[ \omega{-}\text{bounded}(R) \land \RP(R) \to \SN(R) \tag{ii}\]
-  For a countermodel, take the one-element loop $a \to a$.
-
-  (It is both $\omega${-}bounded and satisfies RP.)
-
-  Our hypothesis RP is indeed weaker than ``Inc'' from Terese.
+
   \item The goal \texttt{iii-lemma :  $WN(R) \to WCR(R) \to \omega{-}\text{bounded}(R)$}
@@
 \end{itemize}
-\subsection{09.10 (midweek updata)}
-Is it possible to weaken RP? A possible suggestion:
-
-$RP- :: \omega-bounded \to  \exists i. b \to^* f i$
-
-Does:
-
-$RP \to RP-$
-
-Does:
-
-$RP- \land \; WCR \to RP$
-
-(what other property with $RP-$ would give us $RP$?).
 

### 2024-12-12 Relations/Report.tex
Minor tidying of ars
Cleaning up the useful dead ends section

@@
   \item WCR $\implies$ CR
+  \item WCR  $\implies$ WNFP
+  \item \mbox{WCR R $\to$ $\forall$ a b $\to$ is R -NF b $\to$ (R *) a b $\to$ $\forall$ c $\to$ R a c $\to$ (R *) c b }
   \item WCR and WN $\implies$ CR
   \item WCR and WN $\implies$ SN
-  \item \mbox{WCR R $\to$ $\forall$ a b $\to$ is R -NF b $\to$ (R *) a b $\to$ $\forall$ c $\to$ (R *) a c $\to$ (R *) c b}
-  \item IOW and WCR $\implies$ WNFP \sacomment{We need to define these still (IOW and WNFP)}
-\end{itemize}
+  \item IOW and WCR $\implies$ WNFP \sacomment{We need to define these still (IOW and WNFP) in the report}
+\end{itemize}
+
 \subsection*{Counterexample 2}
@@
       % Arrows
+      \draw[->] (x) -- (n);
+      \draw[->] (x) -- (y);
+      \draw[->] (y) to [bend left] (z);
+      \draw[->] (z) to [bend left] (y);
+  \end{tikzcd}
+\end{center}
+
+Counterexample to:
+\begin{itemize}
+  \item WCR and an increasing sequence where the first elelement of the sequence reduces to an element in normal form $\to$ 
+  the sequence is bounded.
+\end{itemize}
+
+\subsection*{Counterexample 3}
+\begin{center}
+  \begin{tikzcd}
+      % Nodes
+      \node (x) {a};
+      \node (n) [left of=x, xshift=-1cm] {n \in NF};
+      \node (y) [right of=x, xshift=1cm] {b};
+      \node (z) [right of=y] {c};
+
+      % Arrows
       \draw[->>] (x) -- (n);
@@
 
-\subsection*{Counterexample 3}
+\subsection*{Counterexample 4}
 
@@
 
-\subsection*{Counterexample 4}
+\subsection*{Counterexample 5}
 An infinite sequence
@@
 
-\subsection*{Counterexample 5}
+\subsection*{Counterexample 6}
 An infinite sequence with a bound that is a normal form.
@@
   \item WN and CR $\implies$ SN
-  \item WN, CR and, bounded $\implies$ SN
-\end{itemize}
-
-\subsection*{Counterexample 6}
+  \item WN, CR, and bounded $\implies$ SN
+  \item WN, UN, and bounded $implies$ SN 
+\end{itemize}
+
+\subsection*{Counterexample 7}
 An infinite sequence with a bound that is a normal form where each element
@@
 
-\subsection*{Counterexample 7}
+\subsection*{Counterexample 8}
 An "infinite haircomb"
@@
     $a \to^* n \in NF$, and $a \to b$ then $b \to^* n $. (This is a weaker form of WNFP)
+    \item WN and WCR $\to$ bounded. We reached a dead end trying to show this before. Check github history in the ARS file for iii-lemma 
+    if you'd like to see the previous direction.
   \end{enumerate}

### 2024-12-12 Relations/Report.tex
Minor tidying

@@
 The following counterexamples are used to rule out certain implications between properties from holding.
-\sacomment{How should we present this section. Is it enough to have diagrams and a list of what they are a counter to?}
 \subsection*{Counterexample 1}
@@
   \item WCR and WN $\implies$ SN
-  \item IOW and WCR $\implies$ WNFP \sacomment{We need to define these still (IOW and WNFP) in the report}
+  \item IOW and WCR $\implies$ WNFP \sacomment{We need to define IOW in the report}
 \end{itemize}
@@
 
-  \textcolor{red}{SA: The above is a bit messy, can we make it cleaner?}
   \item $\forall$ (R : $\mathscr{R}$ A) $\to$ $\forall$ is R -WN x $\to$ is R -UN x $\to$ is R -CR x

### 2024-12-16 QADT/notes.tex
QADT clean-up phase 1
QADT notes

@@
 \newcommand{\ints}{\mathbb{Z}}
+\newcommand{\nat}{\mathbb{N}}
 
@@
 \maketitle
+
+\section{Standard ADTs}
+\begin{itemize}
+  \item $s(X) = 1 + 2\cdot X$, $S = \mu X. s(x)$
+  \item $t(X) = 1 + X^2$, $T = \mu X. t(x)$
+  \item $m(X) = 1 + X + X^2$, $M = \mu X. m(x)$
+  \item $j(X) = 1 + 2X + X^2$, $J = \mu X. j(x)$
+  \item $h(X) = 1 + X + X^3$, $H = \mu X. h(x)$
+  \item $h(X) = 1 + X^2 + X^4$
+\end{itemize}
+
+\section{Research problems}
+\subsection{Relating different ``roots'' of a single ADT}
+
+Enumerate/define the polynomials that leave the given ADT unchanged
+
+Examples:
+\begin{enumerate}
+  \item $T = T^5$
+  \item $M = M^3$
+  \item $J = J^2$
+\end{enumerate}
+
+\subsection{Relating different ADTs in terms of their roots}
+\begin{enumerate}
+  \item $T^3 = M^2$
+  \item $T^3$ and $M^2$ vs. $S$?
+  \item
+\end{enumerate}
+
+\subsection{A type theory defining equality without triple equality}
+
+\section{Definitions}
+
+\begin{itemize}
+  \item Let $\nat[x]$ be the set of all polynomials in variable $x$ with coefficients in $\nat$
+  \item This is the free rig over ${x}$
+  \item Consider the left action of $\nat[x]$ on itself: $\_\cdot\_ : \nat[x] \times \nat[x] \to \nat[x]$ and $(p(x) , q(x)) \mapsto p(x) \cdot q(x)$
+  \item If we now consider the quotient $\nat[x] / ((1) x=2x+1 , (2) x+x^2=1+x)$, we find that the induced action satisfies \[(x\cdot) \circ (x\cdot) = id\]
+  \item With (2), every $p(x)$ is equivalent to $a+bx$
+  \item With (1), every $a+b\cdot x$ is equivalent to one of: \[\begin{cases}
+    a & a \ge 0 \\
+    a + x & a                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                     \ge 0 \\
+    bx & b \ge 1
+  \end{cases}\]
+\end{itemize}
+
+\section{2024.08.23}
+
+\begin{itemize}
+  \item Can we define LFP in a way that is positive?
+\end{itemize}
 

### 2024-12-16 Relations/Report.tex
ARS

@@
 
+\newcommand{\down}[1]{{#1}{\downarrow}}
 \begin{document}
@@
 
+\apcomment{For a property $P(x)$, let $\down{P}(x) := \forall y. x \thra y \implies P(y)$}
+
+Note that $\down{P} \subseteq P$.
+
+If the converse inclusion holds, we will say that $P$ is \emph{closed under reduction}.
+
 \newpage
@@
 \subsection*{November 21}
+\apcomment{These may be addressed by the implications table}
 Four local ``normal form properties'':
@@
 
-\subsection{Notes from 08.29}
-\begin{enumerate}
-  \item Finish formulating the ``compactness property".  Two candidates:
-  \begin{itemize}
-    \item ``Every cocone for a given infinite sequence loops back to some point in the sequence"
-    \item ``If an $R^*$-sequence has a cocone then it's constant after some point on.''
-  \end{itemize}
-\end{enumerate} \sacomment{This is our recurrence property right? If so, we can just delete this.}
-
 \subsection*{Additional remarks about Theorem 1.2.3.}
@@
   seems either very difficult or impossible.
+
+  \apcomment{This implication should be either proved or refuted.}
 

### 2024-12-19 QADT/OpenProblems.tex

\documentclass{scrartcl}
\begin{document}

\begin{enumerate}
  \item{Commutativity of interpretations of EnvIso and Iso for ADTS}
  \item{A type theory defining equality without triple equality}
  \begin{itemize}
    \item{Isomorphisms without triple equality}
    \item{}
  \end{itemize}
  \item{}
\end{enumerate}

\end{document}

### 2025-01-17 UTA/notes.tex
uta

@@
 
-\newcommand{\types}{\mathbb{T}}
+\input{lambdamacs}
+
+% \newcommand{\types}{\mathbb{T}}
+\newcommand{\mcS}{\mathcal{S}}
+\newcommand{\mcF}{\mathcal{F}}
+\newcommand{\semof}[1]{{[\![{#1}]\!]}}
+\newcommand{\ita}{\mathpzc{Ita}}
+\newcommand{\msl}{\mathpzc{Msl}}
 
 \begin{document}
+
+\section*{01.17}
+TODO:
+\begin{itemize}
+  \item Need to start writing the paper!
+  \item Need a pretty-printer/helper functions for using the Agda code.
+  \item Need to refactor/cleanup the code
+  \item Work on the conjecture
+  \begin{enumerate}
+    \item One direction should be easy
+    \item Is the other direction even true?
+  \end{enumerate}
+  \item Generalizing the code to preorders/intersection types
+  \item Verify correctness of the code: prove it computes the most general unifier
+  equivalent to the starting list of constraints
+  \item Implementing the decision algorithm for the generated recursive type algebra
+  \item How to implement/define the ``free'' ita/meet semilattices in type theory
+  --- related to: How to define strict order between types.
+  \item Implement/verify the decider for the subtyping relation between trees.
+\end{itemize}
+
+\section{Notes from jan. 2025}
+Intersection type algebras are the simultaneous free algebra for the
+monoid functor (whose free algebras are list algebras) and
+icmonoid functor (whose free algebras are free semilattices).
+
+Specifically, given a type $A$, let $\mathcal{P}_f(A)$ denote the final
+powerset of $A$.  Define
+\begin{align}
+  \label{e:msl}
+  \msl(A) &= \mathcal{P}_f(A) \\
+  \label{e:ita}
+  \ita(A) &= \mu X. A \times \msl(X)^*
+\end{align}
+
+That is, for any type $A$, $\ita(A)$ is the initial type satisfying
+$\ita(A) = \msl(\ita(A))^* \times A$.
+
+The distributivity is implicit in this representation, since the
+type $\msl(\ita(A))$ forms an intersection type algebra in the sense of
+BCD, which involves two binary operations, $\to$ and $\cap$.
+Specifically, given $S_1,S_2 \sse_f (\ita(A)$, we
+define
+\begin{align*}
+  (S_1 \cap S_2) &= S_1 \cup S_2 \\
+  (S_1 \to S_2) &= \setof{((s:ts),a) \mid s \in S_1, (ts,a) \in S_2}
+\end{align*}
+This translation validates the distributivity rule, since
+\begin{align*}
+  S_1 \to (S_2 \cap S_3)
+  &= S_1 \to (S_2 \cup S_3) \\
+  &= \setof{(s:ts,a) \mid s \in S_1, (ts,a) \in S_2 \cup S_3}\\
+  &= \setof{(s:ts,a) \mid s \in S_1, (ts,a) \in S_2}
+  \cup \setof{(s:ts,a) \mid s \in S_1, (ts,a) \in S_3}\\
+  &= (S_1 \to S_2) \cup (S_1 \to S_3) \\
+  &= (S_1 \to S_2) \cap (S_1 \to S_3)
+\end{align*}
+
+With the monadic unit $\eta_A = \lam a{:}A. (\emptyset,a): A \to \msl(\ita(A))$,
+and the initiality of the algebra of BCD types $\types_{\to,\cap}(A)$,
+we obtain a map $dnf_A : \types_{\to,\cap)(A) \to \msl(\ita(A))}$.
+
+The converse map $bcd_A : \msl(\ita(A)) \to \types_{\to,\cap}(A)$
+is given recursively by
+\begin{align*}
+  bcd_A(\setof{T_1,\dots,T_m}) &= bcd'_A(T_1) \cap (bcd'_A(T_2) \cap
+    \cdots (bcd'_A(T_{m-1}) \cap bcd'_A(T_m)) \cdots)\\
+  bcd'(A)([S_1,\dots,S_n],a) &= bcd_A(S_1) \to (bcd_A(S_2) \to \cdots (bcd_A(S_n)\to a)
+  \cdots)
+\end{align*}
+
+It is easy to verify by induction that $bcd_A$ is injective.
+It therefore splits the map $dnf_A$, computing the canonical representative
+for the BCD-equivalence class of every type in $\types_{\to,\times}(A)$ .
+
+\emph{Need to choose an ordering in representation of subsets!}
 

### 2025-01-20 Relations/Report.tex
ARS
Local implications table work

@@
 \begin{dfn}
+  A relation $R$ has the \emph{recurrence property} (RP) if
+ $a \tto b$ and $a \tto c$  $\implies$
+ $c \tto b$, for all $a,c \in A$ and all $b \in A$ with the recurrence property.
+\end{dfn}
+\sacomment{This mirrors our Weak normal form property but for recurrence. Which would be a suitable name?}
+
+\begin{dfn}
+  An element $a \in A$ is \emph{$R$-weakly recurrent} ($WR_{R}$)if $a \tto b$ for some recurrent element $b \in A$.
+
+  A relation $R$ is weakly recurrent (WR) if every $a \in A$ is $R$- weakly recurrent.
+\end{dfn}
+
+\begin{dfn}
+  An element $a \in A$ is \emph{$R$-strongly recurrent} ($SR_R$) if every reduction sequence starting from $a$ reaches a recurrent element in a finite number of reductions.
+
+  A relation $R$ is strongly recurrent (SR) if every
+  $a \in A$ is $R$-strongly recurrent.
+\end{dfn}
+\sacomment{Not sure on this defn. Is it right to state it requires a finite number of steps}
+
+\begin{dfn}
   \emph{Cofinality property}
@@
 
+\subsection{Hierarchy}
+The properties of strong normality and confluence are the two properties of greatest interest. As such, there is 
+value in determining which other properties combine to imply one these properties. This motivated the development of the 
+following hierarchies.
+
+\subsubsection{Confluence hierarchy}
+
+Unique Normal Form Property $<$ Weak Normal Form Property $<$ Recurrence Property $<$ Confluent
+
+\subsubsection{Normalization hierarchy}
+
+Weakly Recurrent $<$ Weakly Normal $<$ Strongly Recurrent $<$ Weakly Normal and Strongly Recurrent $<$ Strongly Normal
+
+The property of being strongly recurrent implies the property of being weakly normal only when there is also the classical property 
+of decidability of minimality for a given element.
+
+\begin{table}[h!]
+  \centering
+  \caption{Local implications}
+  \begin{tabular}{|l|c|c|c|c|c|}     
+  \hline
+  \textbf{CR} & CR, WR  & CR, SR  &   &   &   \\
+  \hline
+  \textbf{RP} & CR, WR  & CR, SR  &   &   &   \\
+  \hline
+  \textbf{NP} & NP, WR  & CR, WN  &   &   &   \\
+  \hline
+  \textbf{UN} & UN, WR  & UN, WN  &   &   &   \\
+  \hline
+  & \textbf{WR} & \textbf{WN} & \textbf{SR} & \textbf{WN}$\boldsymbol{\land}$\textbf{SR} & \textbf{SN} \\
+  \hline  
+  \end{tabular}
+\end{table}
+
+\begin{table}[h!]
+  \centering
+  \caption{Local implications - Counterexamples}
+  \begin{tabular}{|l|c|c|c|c|c|}     
+  \hline
+  \textbf{CR} & CR, CE-9  & CR, CE-6  & WIP , CE-9  &   &   \\
+  \hline
+  \textbf{RP} & CR, CE-9  & CR, CE-6  & WIP , CE-9 &   &   \\
+  \hline
+  \textbf{NP} & CE-10, CE-9  & CR, CE-6  & CE-11 , CE-9 &   &   \\
+  \hline
+  \textbf{UN} & CE-3, CE-9  & CE-3, CE-6  & CE-3, CE-9  &   &   \\
+  \hline
+  & \textbf{WR} & \textbf{WN} & \textbf{SR} & \textbf{WN}$\boldsymbol{\land}$\textbf{SR} & \textbf{SN} \\
+  \hline  
+  \end{tabular}
+\end{table} 
+\sacomment{We can potentially merge the two tables.
+Is it the case that we never move one step up the hierarchy?
+Is it always a case that if we move one step we move up all the steps, if that is the case then we just need to either express the relevant counterexample, or express the property attained.}
+
 \newpage
@@
   \item $WN_R$ and $UN_R$ $\implies$ $CR_R$
+  \item (Local) WR and UN $\implies$ NP 
+  \item (Local) WN and UN $\implies$ SR
 
@@
   \item WN, UN, and bounded $implies$ SN
+  \item (Local) WN and UN $\implies$ SR
+  \item (Local) WN and NP $\implies$ SR
+  \item (Local) WN and RP $\implies$ SR
+  \item (Local) WN and CR $\implies$ SR
 \end{itemize}
@@
   \item WN and RP $\implies$ SN
+\end{itemize}
+
+\subsection*{Counterexample 9}
+\begin{center}
+
+  \begin{tikzcd}[node distance=2cm, auto]
+      % Nodes
+      \node (a) {a};
+      \node (b) [right of=a, xshift=1cm] {b};
+
+      % Arrows
+      \draw[->] (a) to [bend left] (b);
+      \draw[->] (b) to [bend left] (a);
+  \end{tikzcd}
+
+\end{center}
+Counterexample to:
+\begin{itemize}
+  \item (Local) WR and UN $\implies$ WN 
+  \item (Local) SR and UN $\implies$ WN 
+  \item (Local) SR and NP $\implies$ WN 
+  \item (Local) SR and RP $\implies$ WN 
+  \item (Local) SR and CR $\implies$ WN 
+\end{itemize}
+
+\subsection*{Counterexample 10}
+\begin{center}
+  \begin{tikzpicture}
+      % Nodes
+      \node (a) {a};
+      \node (b) [left of=a, xshift=-1cm, yshift=-1cm] {b};
+      \node (c) [left of=b] {c};
+      \node (f0) [right of=a, xshift=1cm, yshift=-1cm] {$f_0$};
+      \node (f1) [right of=f0, xshift=1cm] {$f_1$};
+      \node (f2) [right of=f1, xshift=1cm] {$f_2$};
+      \node (dots) [right of=f2, xshift=1cm] {...};
+
+      % Arrows
+      \draw[->] (a) -- (b);
+      \draw[->] (b) to [bend left] (c);
+      \draw[->] (c) to [bend left] (b);
+      \draw[->] (a) -- (f0);
+      \draw[->] (f0) -- (f1);
+      \draw[->] (f1) -- (f2);
+      \draw[->] (f2) -- (dots);
+  \end{tikzpicture}
+\end{center}
+
+Counterexample to:
+\begin{itemize}
+  \item (Local) WR and NP $\implies$ RP 
+\end{itemize}
+
+\subsection*{Counterexample 11}
+\begin{center}
+  \begin{tikzpicture}
+      % Nodes
+      \node (a) {a};
+      \node (b) [left of=a, xshift=-1cm, yshift=-1cm] {b};
+      \node (c) [left of=b] {c};
+      \node (d) [right of=a, xshift=1cm, yshift=-1cm] {d};
+      \node (e) [right of=d] {e};
+
+      % Arrows
+      \draw[->] (a) -- (b);
+      \draw[->] (b) to [bend left] (c);
+      \draw[->] (c) to [bend left] (b);
+      \draw[->] (a) -- (d);
+      \draw[->] (d) to [bend left] (e);
+      \draw[->] (e) to [bend left] (d);
+
+  \end{tikzpicture}
+\end{center}
+
+Counterexample to:
+\begin{itemize}
+  \item (Local) SR and NP $\implies$ RP 
 \end{itemize}
@@
 
+\subsection{Additional Remarks}
+
+\texttt{isWFmin} is only provably when restricted to \emph{decidable} predicates, and this
+restriction is also necessary: in general, WFmin for all P implies all predicates are decidable.
+
   \section{Open Questions }
@@
     \item   Tidy up and standardize the notation used in ars.agda and other agda files
-
-  \end{itemize}
+  \end{itemize}
+\end{enumerate}
+
+\subsection{12.23}
+\begin{enumerate}
+  \item Prove isWFseq implies isWFmin1
 \end{enumerate}

### 2025-01-22 UTA/UTA_Writeup.tex
Writeup added

\documentclass{article}
\usepackage{graphicx} % Required for inserting images

\title{Formalizing Unification over Extensions of Simple Types}
\author{Aaron Frye}
\date{January 2025}

\begin{document}

\maketitle

\section{Abstract}
We use Agda to implement and verify type inference algorithms for extensions of simple types. We first treat recursive types and simple types, then subtyping.

\section{Formalization and Agda}
It is well known that the Curry-Howard correspondence draws an equivalence between proofs in constructive propositional logic and well typed programs with simple types. Agda leverages this fact to serve as both a functional programming language
and a way of writing formally verified mathematical proofs. It takes the idea a step further by incorporating dependent types, which allows the typing system to admit programs representing proofs in predicate logic.

Due to Agdas innate properties as a proof assistant, our results serve as both executable implementations of the listed algorithms and proofs of their correctness.

\section{Unification}
Unification in computer science refers to the problem of finding a substitution that solves a given set of equations. In our case we focus on unifying equations over types.

\section{Unification of recursive types}

\section{Rough ideas}
\begin{itemize}
    \item{unification}
    \item{Type Algebras}
    \item{Syntactic Algebras, notions of equivalence between algebras}
    \item{Free Algebras, invertibility}
    \item{Unification of Simple Types}
    \item{Deciding equivalence}
    \item{Recursive types}
    \item{The subtyping relation}
    \item{Intersection Types}
\end{itemize}

\end{document}

### 2025-01-22 Relations/Report.tex

@@
   \hline
-  \textbf{CR} & CR, WR  & CR, SR  &   &   &   \\
+  \textbf{CR} & CR, WR  & CR, SR  & CR?, SR  &   &   \\
   \hline
-  \textbf{RP} & CR, WR  & CR, SR  &   &   &   \\
+  \textbf{RP} & CR, WR  & CR, SR  & CR?, SR &   &   \\
   \hline
-  \textbf{NP} & NP, WR  & CR, WN  &   &   &   \\
+  \textbf{NP} & NP, WR  & CR, WN  & NP, SR  &   &   \\
   \hline
-  \textbf{UN} & UN, WR  & UN, WN  &   &   &   \\
+  \textbf{UN} & UN, WR  & UN, WN  & UN, SR  & UN, WN$\land$SR  &   \\
   \hline
@@
   \hline
-  \textbf{UN} & CE-3, CE-9  & CE-3, CE-6  & CE-3, CE-9  &   &   \\
+  \textbf{UN} & CE-3, CE-9  & CE-3, CE-6  & CE-3, CE-9  & CE-3, CE-3  &   \\
   \hline

### 2025-01-24 Relations/Report.tex
Further work on tables

--- 2025-01-20 Relations/Report.tex
@@
 \begin{dfn}
-  An element $a \in A$ is \emph{$R$-strongly recurrent} ($SR_R$) if every reduction sequence starting from $a$ reaches a recurrent element in a finite number of reductions.
+  An element $a \in A$ is \emph{$R$-strongly recurrent} ($SR_R$) if every reduction sequence starting from $a$ reaches a recurrent element in a finite number of steps.
 
@@
 
+In the following table red text indicates that classical properties are required for the implication to hold. Blue indicates we are currently unsure.
+
 \begin{table}[h!]
@@
   \hline
-  \textbf{CR} & CR, WR  & CR, SR  &   &   &   \\
-  \hline
-  \textbf{RP} & CR, WR  & CR, SR  &   &   &   \\
-  \hline
-  \textbf{NP} & NP, WR  & CR, WN  &   &   &   \\
-  \hline
-  \textbf{UN} & UN, WR  & UN, WN  &   &   &   \\
+  \textbf{CR} & CR, CE-9  & CR, CE-6  & CR , CE-9  & CR, CE-6  & CR , SN \\
+  \hline
+  \textbf{RP} & CR, CE-9  & CR, CE-6  & \red{CR} , CE-9 & CR, CE-6   & \red{CR} , SN \\
+  \hline
+  \textbf{WNFP} & CE-10, CE-9  & CR, CE-6  & CE-11 , CE-9 & CR, CE-6   & \red{CR} , SN \\
+  \hline
+  \textbf{UN} & CE-3, CE-9  & CE-3, CE-6  & CE-3, CE-9  & CE-3, CE-3  & \red{CR} , SN \\
   \hline
@@
   \centering
-  \caption{Local implications - Counterexamples}
+  \caption{Local implications - WCR }
   \begin{tabular}{|l|c|c|c|c|c|}     
   \hline
-  \textbf{CR} & CR, CE-9  & CR, CE-6  & WIP , CE-9  &   &   \\
-  \hline
-  \textbf{RP} & CR, CE-9  & CR, CE-6  & WIP , CE-9 &   &   \\
-  \hline
-  \textbf{NP} & CE-10, CE-9  & CR, CE-6  & CE-11 , CE-9 &   &   \\
-  \hline
-  \textbf{UN} & CE-3, CE-9  & CE-3, CE-6  & CE-3, CE-9  &   &   \\
+  \textbf{CR} & CR, CE-9  & CR, \blue{CE-6}  & CR , \blue{CE-9}  & CR, \blue{CE-6}  & CR , SN \\
+  \hline
+  \textbf{RP} & CR, CE-9  & CR, \blue{CE-6}  & \red{CR} , \blue{CE-9} & CR, \blue{CE-6}   & \red{CR} , SN \\
+  \hline
+  \textbf{WNFP} & CE-10, CE-9  & CR, \blue{CE-6}  & \blue{CE-11} , \blue{CE-9} & CR, \blue{CE-6}   & \red{CR} , SN \\
+  \hline
+  \textbf{UN} & CE-3, CE-9  & \blue{CE-3}, \blue{CE-6}  & \blue{CE-3}, \blue{CE-9}  & \blue{CE-3}, \blue{CE-3}  & \red{CR} , SN \\
   \hline
@@
 \end{table}
-\sacomment{We can potentially merge the two tables.
-Is it the case that we never move one step up the hierarchy?
-Is it always a case that if we move one step we move up all the steps, if that is the case then we just need to either express the relevant counterexample, or express the property attained.}
+
+\begin{table}[h!]
+  \centering
+  \caption{Global implications}
+  \begin{tabular}{|l|c|c|c|c|c|}     
+  \hline
+  \textbf{CR} & CR, \blue{CE-9}  & CR, \blue{CE-6}  & CR , \blue{CE-9}  & CR, \blue{CE-6}  & CR , SN \\
+  \hline
+  \textbf{RP} & CR, \blue{CE-9}  & CR, \blue{CE-6}  & \red{CR} , \blue{CE-9} & CR, \blue{CE-6}   & \blue{CR} , SN \\
+  \hline
+  \textbf{WNFP} & \blue{CE-10}, \blue{CE-9}  & CR, \blue{CE-6}  & \red{CR} , \blue{CE-9} & CR, \blue{CE-6}   & \blue{CR} , SN \\
+  \hline
+  \textbf{UN} & \blue{CE-3}, \blue{CE-9}  & CR, \blue{CE-6}  & \red{CR}, \blue{CE-9}  & \blue{CE-3}, \blue{CE-3}  & \blue{CR} , SN \\
+  \hline
+  & \textbf{WR} & \textbf{WN} & \textbf{SR} & \textbf{WN}$\boldsymbol{\land}$\textbf{SR} & \textbf{SN} \\
+  \hline  
+  \end{tabular}
+\end{table}
+
+\begin{table}[h!]
+  \centering
+  \caption{Global implications - WCR}
+  \begin{tabular}{|l|c|c|c|c|c|}     
+  \hline
+  \textbf{CR} & CR, \blue{CE-9}  & CR, \blue{CE-6}  & CR , \blue{CE-9}  & CR, \blue{CE-6}  & CR , SN \\
+  \hline
+  \textbf{RP} & CR, \blue{CE-9}  & CR, \blue{CE-6}  & \red{CR} , \blue{CE-9} & CR, \blue{CE-6}   & CR , SN \\
+  \hline
+  \textbf{WNFP} & \blue{CE-10}, \blue{CE-9}  & CR, \blue{CE-6}  & \red{CR} , \blue{CE-9} & CR, \blue{CE-6}   & CR , SN \\
+  \hline
+  \textbf{UN} & \blue{CE-3}, \blue{CE-9}  & CR, \blue{CE-6}  & \red{CR}, \blue{CE-9}  & \blue{CE-3}, \blue{CE-3}  & CR , SN \\
+  \hline
+  & \textbf{WR} & \textbf{WN} & \textbf{SR} & \textbf{WN}$\boldsymbol{\land}$\textbf{SR} & \textbf{SN} \\
+  \hline  
+  \end{tabular}
+\end{table}
 
@@
   \item $WN_R$ and $UN_R$ $\implies$ $CR_R$
-  \item (Local) WR and UN $\implies$ NP 
-  \item (Local) WN and UN $\implies$ SR
+  \item (Local) WCR, WR and UN $\implies$ NP 
+  \item (Local) WCR, WN and UN $\implies$ SR
 
@@
   \item (Local) WN and CR $\implies$ SR
+  \item (Local) WN, SR, and NP $\implies$ SN
+  \item (Local) WN, SR, and RP $\implies$ SN
+  \item (Local) WN, SR, and CR $\implies$ SN
 \end{itemize}
@@
 \begin{itemize}
-  \item (Local) WR and UN $\implies$ WN 
-  \item (Local) SR and UN $\implies$ WN 
-  \item (Local) SR and NP $\implies$ WN 
-  \item (Local) SR and RP $\implies$ WN 
+  \item (Local) WCR, WR, and UN $\implies$ WN 
   \item (Local) SR and CR $\implies$ WN 
@@
 \begin{itemize}
-  \item (Local) WR and NP $\implies$ RP 
+  \item (Local) WCR, WR, and NP $\implies$ RP 
 \end{itemize}

### 2025-01-24 QADT/T^2+2T+1.hs
J^2 isomoprhism

@@ -1,0 +1,68 @@
+data FX = BNode FX FX | UNode1 FX | UNode2 FX | Leaf
+  deriving (Eq, Show)
+
+type FX2 = (FX, FX)
+
+f :: Maybe (Either (FX2, FX2) (FX2, Bool)) -> FX2
+f Nothing = (Leaf, Leaf)
+f (Just (Right ((Leaf, fx), False))) = (Leaf, UNode1 fx)
+f (Just (Right ((UNode1 fx1, fx2), False))) = (Leaf, BNode fx1 fx2)
+f (Just (Right ((UNode2 fx1, fx2), False))) = (BNode fx1 fx2, Leaf)
+f (Just (Right ((BNode fx1 fx2, fx3), False))) = (BNode fx1 fx2, UNode1 fx3)
+f (Just (Right ((fx, Leaf), True))) = (Leaf, UNode2 fx)
+f (Just (Right ((fx1, UNode1 fx2), True))) = (UNode1 fx1, fx2)
+f (Just (Right ((fx1, UNode2 fx2), True))) = (UNode2 fx1, fx2)
+f (Just (Right ((fx1, BNode fx2 fx3), True))) = (BNode fx1 fx3, UNode2 fx2)
+f (Just (Left ((fx1, fx2), (fx3, fx4)))) = (BNode fx1 fx3, BNode fx2 fx4)
+
+foldF :: FX -> FX2
+foldF (Leaf) = f Nothing
+foldF (UNode1 fx) = f (Just (Right (foldF fx, False)))
+foldF (UNode2 fx) = f (Just (Right (foldF fx, True)))
+foldF (BNode fx1 fx2) = f (Just (Left (foldF fx1, foldF fx2)))
+
+g :: FX2 -> Maybe (Either (FX2, FX2) (FX2, Bool))
+g (Leaf, Leaf) = Nothing
+g (Leaf, UNode1 fx) = Just (Right ((Leaf, fx), False))
+g (Leaf, BNode fx1 fx2) = (Just (Right ((UNode1 fx1, fx2), False)))
+g (BNode fx1 fx2, Leaf) = (Just (Right ((UNode2 fx1, fx2), False)))
+g (BNode fx1 fx2, UNode1 fx3) = (Just (Right ((BNode fx1 fx2, fx3), False)))
+g (Leaf, UNode2 fx) = Just (Right((fx, Leaf), True))
[…]

### 2025-01-24 QADT/T^2+2T+1.hs
stuff

@@ -64,5 +64,18 @@ allFX2 = lazyProd allFX allFX
 list1 = [x == test1 x | x <- take 10000 allFX]
 list2 = [x == test2 x | x <- take 10000 allFX2]
 
+swap :: (a,b) -> (b,a)
+swap (x,y) = (y,x)
+
+mapj :: (a -> b) -> Maybe (Either (a, a) (a, Bool)) -> Maybe (Either (b, b) (b, Bool))
+mapj f Nothing = Nothing
+mapj f (Just (Left (x , y))) = Just (Left (f x, f y))
+mapj f (Just (Right (x,c))) = Just (Right (f x, c))
+
+jswap :: Maybe (Either (FX2, FX2) (FX2, Bool)) -> Maybe (Either (FX2, FX2) (FX2, Bool))
+jswap = mapj swap
+
+list3 = [((g . swap) x , (jswap . g) x) | x <- (take 10000 allFX2) ]
+
 check :: [Bool] -> Bool
 check = all id

### 2025-01-28 Relations/Report.tex
defn of SR updated, table updated, counterexamples updated.

@@
 \begin{dfn}
-  An element $a \in A$ is \emph{$R$-strongly recurrent} ($SR_R$) if every reduction sequence starting from $a$ reaches a recurrent element in a finite number of steps.
+  An element $a \in A$ is \emph{$R$-strongly recurrent} ($SR_R$) if either $a$ itself is recurrent or every element one $R$ step 
+  from $a$ is also strongly recurrent.
 
@@
 \end{dfn}
-\sacomment{Not sure on this defn. Is it right to state it requires a finite number of steps}
+
+\begin{dfn}
+  An element $a \in A$ is \emph{$R$-strongly recurrent} ($SR_R$) if every reduction sequence starting from $a$ reaches a recurrent element in a finite number of steps.
+
+  A relation $R$ is strongly recurrent (SR) if every
+  $a \in A$ is $R$-strongly recurrent.
+\end{dfn}
+\sacomment{We have the two contender definitions for SR above.}
 
@@
 
-\subsection{Summary table}
-BP = boundedness property
-
-Table listing highest "confluence" property implied
-by the conjunction of row and column.
-
-\begin{tabular}{@{}l@{\quad}l@{\quad}l@{\quad}l@{\quad}l@{\quad}l@{}}
-  \toprule
-  & CP & CR & WCR & WNFP & WUN  \\
-  \midrule
-  SN  & ? & CR & CR & (Should be CR?)  & ?  \\
-  WN  & ? & CR & (Not CR) & ? & ? \\
-  WN* & ? & CR & ? & ? & ? \\
-  BP $\land$ CP & ? & CR & ? & ? & ? \\
-  BP  & ? & CR & ? & ? & ? \\
-  CP  & ? & CR & ? & ? & ? \\
-  \bottomrule
-\end{tabular}
-
-Table listing highest "normalization" property implied
-by the conjunction of row and column.
-
-\begin{tabular}{@{}l@{\quad}l@{\quad}l@{\quad}l@{\quad}l@{\quad}l@{}}
-  \toprule
-  & CP & CR & WCR & WNFP & WUN \\
-  \midrule
-  SN  &?& SN & SN & SN & SN \\
-  WN  &?& (Not SN) & (Not SN) & ? & ? \\
-  WN*  &?& ? & ? & ? & ? \\
-  BP $\land$ CP   &?& ? & ? & ? & ? \\
-  BP  &?& ? & ? & ? & ? \\
-  CP  &?& (not CP or BP) & ? & ? & ? \\
-  \bottomrule
-\end{tabular}
-
 \subsection{Double-check: What has been proven}
@@
 
-Unique Normal Form Property $<$ Weak Normal Form Property $<$ Recurrence Property $<$ Confluent
+\begin{center}
+
+  \begin{tikzpicture}[auto,
+    arrowstyle/.style={->, line width=1pt, >={Latex[length=3mm, width=2mm]}, shorten >=2pt}]
+    % A box style
+    \tikzstyle{boxnode} = [draw, rectangle, minimum width=3cm, minimum height=1cm, text centered]
+
+    % Place the nodes vertically (top to bottom)
+    \node (Confluent) [boxnode] at (0,0) {Confluent};
+    \node (RP)        [boxnode, below=2cm of Confluent] {Recurrence Property};
+    \node (WN)        [boxnode, below=2cm of RP] {Weak Normal Form Property};
+    \node (UN)        [boxnode, below=2cm of WN] {Unique Normal Form Property};
+
+    % Draw arrows downwards
+    \draw[arrowstyle] (Confluent) -- (RP);
+    \draw[arrowstyle] (RP) -- (WN);
+    \draw[arrowstyle] (WN) -- (UN);
+  \end{tikzpicture}
+\end{center}
 
@@
 
-Weakly Recurrent $<$ Weakly Normal $<$ Strongly Recurrent $<$ Weakly Normal and Strongly Recurrent $<$ Strongly Normal
-
-The property of being strongly recurrent implies the property of being weakly normal only when there is also the classical property 
+\begin{tikzpicture}[node distance=2cm, auto,
+  % Define a thicker arrow with larger arrowhead and some shortening
+  arrowstyle/.style = {->, line width=1pt, >={Latex[length=3mm, width=2mm]}, shorten >=2pt}
+]
+% Define a box style
+\tikzstyle{boxnode} = [draw, rectangle, minimum width=3cm, minimum height=1cm, text centered]
+
+% Define the nodes
+\node (SN) [boxnode] at (0,0) {Strongly Normal};
+\node (WN) [boxnode, below left=2cm and 2cm of SN] {Weakly Normal};
+\node (SR) [boxnode, below right=2cm and 2cm of SN] {Strongly Recurrent};
+\node (WR) [boxnode, below of=SN, yshift=-4cm] {Weakly Recurrent};
+
+% Draw the arrows to form a diamond
+\draw [arrowstyle] (SN) -- (WN);
+\draw [arrowstyle] (SN) -- (SR);
+\draw [arrowstyle] (WN) -- (WR);
+\draw [arrowstyle] (SR) -- (WR);
+\end{tikzpicture}
+
+The property of being strongly recurrent implies the property of being weakly recurrent only when there is also the classical property 
 of decidability of minimality for a given element.
@@
   \hline
-  \textbf{CR} & CR, CE-9  & CR, CE-6  & CR , CE-9  & CR, CE-6  & CR , SN \\
-  \hline
-  \textbf{RP} & CR, CE-9  & CR, CE-6  & \red{CR} , CE-9 & CR, CE-6   & \red{CR} , SN \\
-  \hline
-  \textbf{WNFP} & CE-10, CE-9  & CR, CE-6  & CE-11 , CE-9 & CR, CE-6   & \red{CR} , SN \\
-  \hline
-  \textbf{UN} & CE-3, CE-9  & CE-3, CE-6  & CE-3, CE-9  & CE-3, CE-3  & \red{CR} , SN \\
+  \textbf{CR} & CR, CE-9  & CR, CE-6  & CR , CE-9  & CR, ?  & CR , SN \\
+  \hline
+  \textbf{RP} & CR, CE-9  & CR, CE-6  & \red{CR} , CE-9 & CR, ?   & \red{CR} , SN \\
+  \hline
+  \textbf{WNFP} & CE-10, CE-9  & CR, CE-6  & CE-11 , CE-9 & CR, ?   & \red{CR} , SN \\
+  \hline
+  \textbf{UN} & CE-3, CE-12  & CE-3, CE-6  & CE-3, CE-9  & CE-3, CE-3  & \red{CR} , SN \\
   \hline
@@
   \hline
-  \textbf{CR} & CR, CE-9  & CR, \blue{CE-6}  & CR , \blue{CE-9}  & CR, \blue{CE-6}  & CR , SN \\
-  \hline
-  \textbf{RP} & CR, CE-9  & CR, \blue{CE-6}  & \red{CR} , \blue{CE-9} & CR, \blue{CE-6}   & \red{CR} , SN \\
-  \hline
-  \textbf{WNFP} & CE-10, CE-9  & CR, \blue{CE-6}  & \blue{CE-11} , \blue{CE-9} & CR, \blue{CE-6}   & \red{CR} , SN \\
-  \hline
-  \textbf{UN} & CE-3, CE-9  & \blue{CE-3}, \blue{CE-6}  & \blue{CE-3}, \blue{CE-9}  & \blue{CE-3}, \blue{CE-3}  & \red{CR} , SN \\
+  \textbf{CR} & CR, CE-9  & CR, {CE-6}  & CR , {CE-9}  & CR, ?  & CR , SN \\
+  \hline
+  \textbf{RP} & CR, CE-9  & CR, {CE-6}  & \red{CR} , {CE-9} & CR, ?   & \red{CR} , SN \\
+  \hline
+  \textbf{WNFP} & CE-10.1, CE-9  & CR, {CE-6}  & {CE-11} , {CE-9} & CR, ?  & \red{CR} , SN \\
+  \hline
+  \textbf{UN} & CE-3.1, CE-12  & {CE-3.1}, {CE-6}  & {CE-3.1}, {CE-9}  & {CE-3.1}, {CE-3.1}  & \red{CR} , SN \\
   \hline
@@
   \hline
-  \textbf{CR} & CR, \blue{CE-9}  & CR, \blue{CE-6}  & CR , \blue{CE-9}  & CR, \blue{CE-6}  & CR , SN \\
-  \hline
-  \textbf{RP} & CR, \blue{CE-9}  & CR, \blue{CE-6}  & \red{CR} , \blue{CE-9} & CR, \blue{CE-6}   & \blue{CR} , SN \\
-  \hline
-  \textbf{WNFP} & \blue{CE-10}, \blue{CE-9}  & CR, \blue{CE-6}  & \red{CR} , \blue{CE-9} & CR, \blue{CE-6}   & \blue{CR} , SN \\
-  \hline
-  \textbf{UN} & \blue{CE-3}, \blue{CE-9}  & CR, \blue{CE-6}  & \red{CR}, \blue{CE-9}  & \blue{CE-3}, \blue{CE-3}  & \blue{CR} , SN \\
+  \textbf{CR} & CR, {CE-9}  & CR, {CE-6}  & CR , {CE-9}  & CR, ?  & CR , SN \\
+  \hline
+  \textbf{RP} & CR, {CE-9}  & CR, {CE-6}  & \red{CR} , {CE-9} & CR, ?   & \red{CR} , SN \\
+  \hline
+  \textbf{WNFP} & {CE-11}, {CE-9}  & CR, {CE-6}  & CE-11 , {CE-9} & CR, ?   & \red{CR} , SN \\
+  \hline
+  \textbf{UN} & {CE-3}, {CE-12}  & CR, {CE-6}  & CE-3, {CE-9}  & CR, {CE-3}  & \red{CR} , SN \\
   \hline
@@
   \hline
-  \textbf{CR} & CR, \blue{CE-9}  & CR, \blue{CE-6}  & CR , \blue{CE-9}  & CR, \blue{CE-6}  & CR , SN \\
-  \hline
-  \textbf{RP} & CR, \blue{CE-9}  & CR, \blue{CE-6}  & \red{CR} , \blue{CE-9} & CR, \blue{CE-6}   & CR , SN \\
-  \hline
-  \textbf{WNFP} & \blue{CE-10}, \blue{CE-9}  & CR, \blue{CE-6}  & \red{CR} , \blue{CE-9} & CR, \blue{CE-6}   & CR , SN \\
-  \hline
-  \textbf{UN} & \blue{CE-3}, \blue{CE-9}  & CR, \blue{CE-6}  & \red{CR}, \blue{CE-9}  & \blue{CE-3}, \blue{CE-3}  & CR , SN \\
+  \textbf{CR} & CR, {CE-9}  & CR, {CE-6}  & CR , {CE-9}  & CR, ?  & CR , SN \\
+  \hline
+  \textbf{RP} & CR, {CE-9}  & CR, {CE-6}  & \red{CR} , {CE-9} & CR, ?   & CR , SN \\
+  \hline
+  \textbf{WNFP} & ?, {CE-9}  & CR, {CE-6}  & \red{CR} , {CE-9} & CR, ?   & CR , SN \\
+  \hline
+  \textbf{UN} & ?, {CE-9}  & CR, {CE-6}  & \red{CR}, {CE-9}  & CR, ?  & CR , SN \\
   \hline
@@
   \item $WN_R$ and $UN_R$ $\implies$ $CR_R$
-  \item (Local) WCR, WR and UN $\implies$ NP 
+  \item (Local) WR and UN $\implies$ NP 
+  \item (Local) WN and UN $\implies$ SR
+
+\end{itemize}
+
+\subsection*{Counterexample 3.1}
+\begin{center}
+  \begin{tikzcd}
+      % Nodes
+      \node (x) {a};
+      \node (a') [above of=x] {a'};
+      \node (n) [left of=x, xshift=-1cm] {n \in NF};
+      \node (y) [right of=x, xshift=1cm] {b};
+      \node (z) [right of=y] {c};
+
+      % Arrows
+      \draw[->>] (x) -- (n);
+      \draw[->] (a') -- (x);
+      \draw[->] (a') -- (n);
+      \draw[->>] (x) -- (y);
+      \draw[->] (y) to [bend left] (z);
+      \draw[->] (z) to [bend left] (y);
+  \end{tikzcd}
+\end{center}
+
+Counterexample to:
+\begin{itemize}
+  \item (Local) WCR, WR, and UN $\implies$ NP 
   \item (Local) WCR, WN and UN $\implies$ SR
@@
 
-          \draw[->>] (f0) -- (a);
-          \draw[->>] (f1) -- (a);
-          \draw[->>] (dots) -- (a);
+          \draw[->] (f0) -- (a);
+          \draw[->] (f1) -- (a);
+          \draw[->] (dots) -- (a);
       \end{tikzpicture}
@@
 \begin{itemize}
+  \item (Local) WR, and NP $\implies$ RP 
+\end{itemize}
+
+\subsection*{Counterexample 10.1}
+\begin{center}
+  \begin{tikzpicture}
+      % Nodes
+      \node (a) {a};
+      \node (a') [above of=a] {a'};
+      \node (b) [left of=a, xshift=-1cm, yshift=-1cm] {b};
+      \node (c) [left of=b] {c};
+      \node (f0) [right of=a, xshift=1cm, yshift=-1cm] {$f_0$};
+      \node (f1) [right of=f0, xshift=1cm] {$f_1$};
+      \node (f2) [right of=f1, xshift=1cm] {$f_2$};
+      \node (dots) [right of=f2, xshift=1cm] {...};
+
+      % Arrows
+      \draw[->] (a) -- (b);
+      \draw[->] (a') -- (a);
+      \draw[->] (a') -- (b);
+      \draw[->] (b) to [bend left] (c);
+      \draw[->] (c) to [bend left] (b);
+      \draw[->] (a) -- (f0);
+      \draw[->] (f0) -- (f1);
+      \draw[->] (f1) -- (f2);
+      \draw[->] (f2) -- (dots);
+  \end{tikzpicture}
+\end{center}
+
+Counterexample to:
+\begin{itemize}
   \item (Local) WCR, WR, and NP $\implies$ RP 
@@
   \item (Local) SR and NP $\implies$ RP 
+\end{itemize}
+
+\subsection*{Counterexample 12}
+\begin{center}
+
+  \begin{tikzcd}[node distance=2cm, auto]
+      % Nodes
+      \node (a) {a};
+      \node (b) [right of=a, xshift=1cm] {b};
+      \node (n) [below of=a, xshift=1cm] {n};
+
+      % Arrows
+      \draw[->] (a) to [bend left] (b);
+      \draw[->] (b) to [bend left] (a);
+      \draw[->] (a) -- (n);
+  \end{tikzcd}
+
+\end{center}
+Counterexample to:
+\begin{itemize}
+    \item (gloabl) WCR, WR, and UN $implies$ WN or SR or SN
 \end{itemize}

### 2025-01-31 Relations/Report.tex
Report update on implications and CEs

@@
   \hline
-  \textbf{UN} & {CE-3}, {CE-12}  & CR, {CE-6}  & CE-3, {CE-9}  & CR, {CE-3}  & \red{CR} , SN \\
+  \textbf{UN} & {CE-3}, {CE-12} and CE-9  & CR, {CE-6}  & CE-3, {CE-9}  & CR, ?  & \red{CR} , SN \\
   \hline
@@
   \hline
-  \textbf{RP} & CR, {CE-9}  & CR, {CE-6}  & \red{CR} , {CE-9} & CR, ?   & CR , SN \\
-  \hline
-  \textbf{WNFP} & ?, {CE-9}  & CR, {CE-6}  & \red{CR} , {CE-9} & CR, ?   & CR , SN \\
-  \hline
-  \textbf{UN} & ?, {CE-9}  & CR, {CE-6}  & \red{CR}, {CE-9}  & CR, ?  & CR , SN \\
+  \textbf{RP} & CR, {CE-9}  & CR, {CE-6}  & {CR} , {CE-9} & CR, ?   & CR , SN \\
+  \hline
+  \textbf{WNFP} & CE-1.2, {CE-9}  & CR, {CE-6}  & {CR} , {CE-9} & CR, ?   & CR , SN \\
+  \hline
+  \textbf{UN} & CE-1.1, {CE-9}  & CR, {CE-6}  & {CR}, {CE-9}  & CR, ?  & CR , SN \\
   \hline
@@
   \item IOW and WCR $\implies$ WNFP \sacomment{We need to define IOW in the report}
+\end{itemize}
+
+\subsection*{Counterexample 1.1}
+\begin{center}
+
+  \begin{tikzcd}[node distance=2cm, auto]
+      % Nodes
+      \node (a) {a};
+      \node (b) [right of=a, xshift=1cm] {b};
+      \node (c) [right of=b, xshift=1cm] {c};
+      \node (d) [right of=c, xshift=1cm] {d};
+
+      % Arrows
+      \draw[->] (b) to [bend left] (c);
+      \draw[->] (c) to [bend left] (b);
+      \draw[->] (b) -- (a);
+      \draw[->] (c) -- (d);
+      \draw[->, loop] (d) to (d);
+
+  \end{tikzcd}
+
+\end{center}
+Counterexample to:
+\begin{itemize}
+  \item (Global) WCR, UN, and WR $\implies$ WNFP
+\end{itemize}
+
+\subsection*{Counterexample 1.2}
+\begin{center}
+
+  \begin{tikzcd}[node distance=2cm, auto]
+      % Nodes
+      \node (a) {a};
+      \node (b) [right of=a, xshift=1cm] {b};
+      \node (c) [right of=b, xshift=1cm] {c};
+      \node (d) [right of=c, xshift=1cm] {d};
+
+      % Arrows
+      \draw[->] (b) to [bend left] (c);
+      \draw[->] (c) to [bend left] (b);
+      \draw[->] (b) -- (a);
+      \draw[->] (c) -- (d);
+      \draw[->, loop] (d) to (d);
+      \draw[->, loop] (a) to (a);
+
+  \end{tikzcd}
+
+\end{center}
+Counterexample to:
+\begin{itemize}
+  \item (Global) WCR, WNFP, and WR $\implies$ RP
 \end{itemize}

### 2025-02-03 QADT/iso_research_more_general.py
Some Examples QADT

@@ -1,7 +1,7 @@
 import re
 def main():
-    diff = [1, 1, 1, 0]
-    poly = [0, 1, 0, 0, 0]
+    diff = [1, 0, 1]
+    poly = [0, 0, 0, 1, 0, 0, 0]
     # diff = [1, 0, 0, 0, 0, 1]
     # poly = [1, 1, 0, 0, 0, 1]
     # poly = [0, 0, 1, 1, 0, 0, 0, 1]
@@ -22,14 +22,14 @@ def step(diff, poly, start_x=1,lim=1):
         n = input(": ")
         if n.lower() in ('q', 'quit'): return "break"
     n = int(n)
+    while len(poly) < n + len(diff) + 1:
+        poly.append(0)
     if n < 0:
         neg = True
         n = abs(n)
-    if n < start_x or poly[n] < lim:
+    if abs(n) < start_x or (poly[n] < lim and not neg):
         return
-    while len(poly) < n + len(diff) + 1:
-        poly.append(0)
-    if neg and all((poly[n+i-start_x] >= diff[i]) or diff[i] <= 0 for i in range(len(diff))):
+    if neg and all((poly[n+i-start_x] >= diff[i]) or diff[i] <= 0 for i in range(len(diff))) and (poly[n] > diff[1] if diff[1] >= 0 else True):
         for i in range(len(diff)):
             poly[n + i - start_x] -= diff[i]
     elif not neg:

### 2025-02-03 Relations/Report.tex

@@
   \hline
-  \textbf{CR} & CR, CE-9  & CR, CE-6  & CR , CE-9  & CR, ?  & CR , SN \\
-  \hline
-  \textbf{RP} & CR, CE-9  & CR, CE-6  & \red{CR} , CE-9 & CR, ?   & \red{CR} , SN \\
-  \hline
-  \textbf{WNFP} & CE-10, CE-9  & CR, CE-6  & CE-11 , CE-9 & CR, ?   & \red{CR} , SN \\
+  \textbf{CR} & CR, CE-9  & CR, CE-6  & CR , CE-9  & CR, SN  & CR , SN \\
+  \hline
+  \textbf{RP} & CR, CE-9  & CR, CE-6  & \red{CR} , CE-9 & CR, SN   & \red{CR} , SN \\
+  \hline
+  \textbf{WNFP} & CE-10, CE-9  & CR, CE-6  & CE-11 , CE-9 & CR, SN   & \red{CR} , SN \\
   \hline
@@
   \hline
-  \textbf{CR} & CR, CE-9  & CR, {CE-6}  & CR , {CE-9}  & CR, ?  & CR , SN \\
-  \hline
-  \textbf{RP} & CR, CE-9  & CR, {CE-6}  & \red{CR} , {CE-9} & CR, ?   & \red{CR} , SN \\
-  \hline
-  \textbf{WNFP} & CE-10.1, CE-9  & CR, {CE-6}  & {CE-11} , {CE-9} & CR, ?  & \red{CR} , SN \\
+  \textbf{CR} & CR, CE-9  & CR, {CE-6}  & CR , {CE-9}  & CR, SN  & CR , SN \\
+  \hline
+  \textbf{RP} & CR, CE-9  & CR, {CE-6}  & \red{CR} , {CE-9} & CR, SN   & \red{CR} , SN \\
+  \hline
+  \textbf{WNFP} & CE-10.1, CE-9  & CR, {CE-6}  & {CE-11} , {CE-9} & CR, SN  & \red{CR} , SN \\
   \hline
@@
   \hline
-  \textbf{CR} & CR, {CE-9}  & CR, {CE-6}  & CR , {CE-9}  & CR, ?  & CR , SN \\
-  \hline
-  \textbf{RP} & CR, {CE-9}  & CR, {CE-6}  & \red{CR} , {CE-9} & CR, ?   & \red{CR} , SN \\
-  \hline
-  \textbf{WNFP} & {CE-11}, {CE-9}  & CR, {CE-6}  & CE-11 , {CE-9} & CR, ?   & \red{CR} , SN \\
-  \hline
-  \textbf{UN} & {CE-3}, {CE-12} and CE-9  & CR, {CE-6}  & CE-3, {CE-9}  & CR, ?  & \red{CR} , SN \\
+  \textbf{CR} & CR, {CE-9}  & CR, {CE-6}  & CR , {CE-9}  & CR, SN  & CR , SN \\
+  \hline
+  \textbf{RP} & CR, {CE-9}  & CR, {CE-6}  & \red{CR} , {CE-9} & CR, SN   & \red{CR} , SN \\
+  \hline
+  \textbf{WNFP} & {CE-11}, {CE-9}  & CR, {CE-6}  & CE-11 , {CE-9} & CR, SN   & \red{CR} , SN \\
+  \hline
+  \textbf{UN} & {CE-3}, {CE-12} and CE-9  & CR, {CE-6}  & CE-3, {CE-9}  & CR, SN  & \red{CR} , SN \\
   \hline
@@
   \hline
-  \textbf{CR} & CR, {CE-9}  & CR, {CE-6}  & CR , {CE-9}  & CR, ?  & CR , SN \\
-  \hline
-  \textbf{RP} & CR, {CE-9}  & CR, {CE-6}  & {CR} , {CE-9} & CR, ?   & CR , SN \\
-  \hline
-  \textbf{WNFP} & CE-1.2, {CE-9}  & CR, {CE-6}  & {CR} , {CE-9} & CR, ?   & CR , SN \\
-  \hline
-  \textbf{UN} & CE-1.1, {CE-9}  & CR, {CE-6}  & {CR}, {CE-9}  & CR, ?  & CR , SN \\
+  \textbf{CR} & CR, {CE-9}  & CR, {CE-6}  & CR , {CE-9}  & CR, SN  & CR , SN \\
+  \hline
+  \textbf{RP} & CR, {CE-9}  & CR, {CE-6}  & {CR} , {CE-9} & CR, SN   & CR , SN \\
+  \hline
+  \textbf{WNFP} & CE-1.2, {CE-9}  & CR, {CE-6}  & {CR} , {CE-9} & CR, SN   & CR , SN \\
+  \hline
+  \textbf{UN} & CE-1.1, {CE-9}  & CR, {CE-6}  & {CR}, {CE-9}  & CR, SN  & CR , SN \\
   \hline

### 2025-02-09 Relations/Report.tex
abstract for FSCD

@@
 
-\title{Summer 2024 Report}
+\title{Formalizing Abstract Rewriting}
+% \title{Abstract Rewriting from a Constructive Viewpoint}
+% \title{A Constructive View on Abstact Rewriting}
 \author{Sam Arkle}
@@
 \newcommand{\down}[1]{{#1}{\downarrow}}
+
 \begin{document}
+
 \renewcommand{\arraystretch}{1.3}
@@
 \maketitle
+\begin{abstract}
+We formalize in the Agda proof assistant the main results about Abstract Reduction Systems (ARS) given in the standard reference [Terese].
+% Our contribution can be viewed as a development of abstract rewriting using constructive logic.
+% , and is part of a larger project aiming to develop a library of programming language theory in Agda.
+This application leads us to give special focus to concepts related to termination and confluence.
+We define a taxonomy of concepts related to termination and confluence and investigate their relationships between each other and their classical counterparts.
+We identify, and eliminate where possible, the use of classical logic in the proofs of standard ARS results.
+% For example, the study of strong normalization leads us to multiple inequivalent
+% formalizations of the notion of a well-founded relations, with subtle distinctions.
+Our analysis leads to refinements and mild generalizations of classical termination and confluence criteria.
+\end{abstract}
 
@@
           \to \big(\exists n \in \nat. s n \equiv a\big)\]
-
-  \end{itemize}
+  \end{itemize}
+  \item When an element is not SN, it transitions to one which is not SN either.
+  (Use in the proof of Theorem 1.2.3)
 \end{itemize}

### 2025-02-11 Relations/Paper/Counterexamples.tex
New structure for the paper

--- 2024-10-10 Relations/CounterExamples.tex
@@
-\documentclass{article}
-\usepackage{tikz-cd}
-
-\title{Counterexamples in Mathematical Relations}
-\author{}
-\date{}
-
-\begin{document}
-
-\maketitle
-
-\section{Introduction}
-This document contains diagrams of counterexamples commonly encountered when exploring the properties of mathematical relations.
-
 \section{Counterexamples}
-
-\subsection{Counterexample 1}
-\begin{center}
-
-    \begin{tikzcd}[node distance=2cm, auto]
-        % Nodes
-        \node (a) {a};
-        \node (b) [right of=a, xshift=1cm] {b};
-        \node (c) [right of=b, xshift=1cm] {c};
-        \node (d) [right of=c, xshift=1cm] {d};
-
-        % Arrows
-        \draw[->] (b) to [bend left] (c);
-        \draw[->] (c) to [bend left] (b);
-        \draw[->] (b) -- (a);
-        \draw[->] (c) -- (d);
-    \end{tikzcd}
-
-\end{center}
-Counterexample to:
-\begin{itemize}
-    \item WCR $\to$ CR
-    \item \mbox{WCR R $\to$ $\forall$ a b $\to$ is R -NF b $\to$ (R *) a b $\to$ $\forall$ c $\to$ (R *) a c $\to$ (R *) c b}
-\end{itemize}
-
-\subsection{Counterexample 2}
-\begin{center}
-    \begin{tikzcd}
-        % Nodes
-        \node (x) {x};
-        \node (n) [below left of=x, xshift=-1cm, yshift=-1cm] {n \in NF};
-        \node (y) [below right of=x, xshift=1cm, yshift=-1cm] {y};
-        \node (z) [below of=y, yshift=-1cm] {z};
-
-        % Arrows
-        \draw[->>] (x) -- (n);
-        \draw[->>] (x) -- (y);
-        \draw[->] (y) to [bend left] (z);
-        \draw[->] (z) to [bend left] (y);
-    \end{tikzcd}
-\end{center}
-
-Counterexample to:
-\begin{itemize}
-    \item  $\forall$ x $\to$ is R-WN x $\to$ $\forall$ y $\to$ (R *) x y $\to$ is R-WN y
-
-\end{itemize}
-
-\subsection{ARS in Agda}
-Important counterexamples:
-\begin{enumerate}
-  \item $a,b,c,d$ with sinks $a$ and $d$ and a 2-cycle between $b$ and $c$.
-  Counterexample to:
-  \begin{itemize}
-      \item WCR and WN implies CR.
-  \end{itemize}
-  \item Loop $a \to a$.
-  Counterexample to:
-  \begin{itemize}
-    \item $\omega$-bounded and RP implies SN
-    \item $\omega$-bounded and RP implies WN
-  \end{itemize}
-  \item Infinite sequence $a_0 \to a_1 \to \cdots$. Falsifies:
-  \begin{itemize}
-    \item $WN$
-    \item $\omega$-bounded
-    \item $WCR \to WN$
-    \item $CR \to WN$
-    \item $CR, CP \to WN$
-    \item $CR, CP \to \omega$-bounded
-  \end{itemize}
-  \item Infinite sequence $a_0 \to a_1 \to \cdots$ with a colimit $a_\infty$,
-  with each $a_n \to a_\infty$ and $a_\infty$ a normal form.
-  \item Infinite sequence $a_0 \to a_1 \to \cdots$, together with links
-  $a_n \to a_0$, for each $n$.
-  \item The combination of the last two.
-  Counterexample to
-  \begin{itemize}
-    \item RP
-  \end{itemize}
-  \item An ``infinite haircomb''. Infinite sequence $a_0 \to a_1 \to \cdots$, together with
-  a disjoint, discrete set $b_0, b_1, \dots$, and links $a_n \to b_n$.
-  Counterexample to:
-  \begin{itemize}
-    \item $WN\to WCR$
-    \item $WN \to SN$
-  \end{itemize}
-  \item A variation of the above with backlinks $a_n \to a_0$ for all $n$.
-\end{enumerate}
-
-\end{document}
+\label{sec:Counterexamples}

### 2025-02-11 Relations/Paper/Introduction.tex
New structure for the paper

\section{Introduction}
\label{sec:Introduction}

The text for the introduction will go here.

### 2025-02-11 Relations/Paper/Main.tex
New structure for the paper

\documentclass[letterpaper,USenglish,cleveref, autoref, thm-restate]{lipics-v2021}

\input{macros}

\bibliographystyle{plainurl}% the mandatory bibstyle

\title{Formalization of Abstract Rewriting}

\author{Andrew Polonsky}{Appalachian State University, USA}
{polonskya@appstate.edu} 
{} 
{}%TODO mandatory, 
% please use full name; only 1 author per \author macro; 
% first two parameters are mandatory, other parameters can be empty. 
% Please provide at least the name of the affiliation and the country. 
% The full address is optional. Use additional curly braces to indicate the correct
%  name splitting when the last name consists of multiple name parts.
\author{Samuel Arkle}{Appalachian State University, USA (Recent graduate)}
{arklesd@appstate.edu}{}{}

\Copyright{Andrew Polonsky and Samuel Arkle}

\ccsdesc[100]{\textcolor{red}{Replace ccsdesc macro with valid one}} %TODO mandatory: Please choose ACM 2012 classifications from https://dl.acm.org/ccs/ccs_flat.cfm

\keywords{Dummy keyword} %TODO mandatory; please add comma-separated list of keywords

\supplement{https://github.com/DrPolonsky/LAM/tree/main/Relations}% TODO: set a repo just for this submissionoptional, e.g. related research data, source code, ... hosted on a repository like zenodo, figshare, GitHub, ...

\begin{document}
\maketitle

\begin{abstract}
    We present a constructive formalization of Abstract Reduction Systems (ARS)
     in the Agda proof assistant, focusing on the results given in Term Rewriting 
     Systems (Terese). We define a taxonomy of concepts related to termination and 
     confluence and investigate their relationships between each other and their 
     classical counterparts. We identify, and eliminate where possible, the use of classical 
     logic in the proofs of standard ARS results. Our analysis leads to refinements and mild
      generalizations of classical termination and confluence criteria.
\end{abstract}
\input{Introduction.tex}
\input{Definitions.tex}
\input{Implications.tex}
\input{Counterexamples.tex}
\input{Well-foundedness.tex}

\end{document}

### 2025-02-11 Relations/Paper/Well-foundedness.tex
New structure for the paper

--- 2025-01-31 Relations/Report.tex
@@
-\documentclass{scrartcl}
-% \input{packages}
-
-\usepackage{booktabs}
-
-\input{macros}
-
-\title{Summer 2024 Report}
-\author{Sam Arkle}
-\date{\today}
-
-\usepackage{pifont}% http://ctan.org/pkg/pifont
-\newcommand{\cmark}{\quad\ding{51}}%
-\newcommand{\xmark}{\quad\ding{55}}%
-
-\newcommand{\thra}{\twoheadrightarrow}
-\newcommand{\thla}{\twoheadleftarrow}
-\newcommand{\thlra}{{\thla\!\!\thra}}
-
-\newcommand{\down}[1]{{#1}{\downarrow}}
-\begin{document}
-\renewcommand{\arraystretch}{1.3}
-
-\maketitle
-
-\tableofcontents
-
-\section{Introduction}
-This is a report on the progress I have made during the summer of 2024 working with Dr.
-Polonsky \footnote{Assisstant Professor, Department of Computer Science, Appalachian State University.}.
-I have been writing on the topic of relations, working primarily from Term Rewriting Systems (TeReSe) \footnote{(Term Rewriting Systems. (2003). United Kingdom: Cambridge University Press.)}.
-The objective of this work has been to both develop a formal understanding of relations and to build a library in Agda \footnote{\href{https://github.com/DrPolonsky/LAM/tree/main/Relations}{Github repository for this project's code}} that will be used as a foundation to further work in theoretical computer science.
-\\
-I have been focussed on Chapter 1 of TeReSe which covers abstract reduction systems (ARS) as well as the appendix (sections 1-3) which provides the necessary mathematical background for the rest of the book (e.g.
-relations, ordinals, inductive definitions and the Knaster-Tarski lemma).
-Where the book has made use of classical logic I have investigated the possibility of using constructive alternatives.
-
-\section{Definitions} \label{section:Definitions}
-The most interesting work we have carried out in investigating Chapter 1 of TeReSe has resulted from trying to provide constructive proofs for Newman's lemma, the Knaster-Tarski lemma, theorem 1.2.2 and theorem 1.2.3.
-Before exploring those proofs the following definitions are essential.
-
-The following definitions are taken from [TeReSe], Chapter 1,
-with minimal adaptations for consistency.
-
-\begin{dfn}
-  An abstract reduction system (\emph{ARS}) is a structure $\mathcal{A} = (A, R_\alpha)$ where $A$ is a set and $R_\alpha$ is a set of binary relations.
-\end{dfn}
-A relation $R$ from the set $R_\alpha$ is refered to as a reduction (or rewrite) relation.
-For example, if we specify $R$ as the relation of being 'less than' ($<$) then $R\, 4\, 2$.
-\textcolor{red}{Right?}
-\apcomment{Yes, but move this to a(n eventual) list of examples.}
-
-We use $R$ or $\to$ for a single-step reduction and $R^*$ or $\tto$ for a multi-step reduction.
-
-\sacomment{Should we be using $R^+$ rather than $R^*$?}
-
-\apcomment{Thus, when $(a,b) \in \to_{(\alpha)}$, we say that there is a
-\emph{$(\alpha-)$reduction} from $a$ to $b$.
-When $(a,b) \in \tto_\alpha$, we say that there is a multi-step $\alpha$-reduction
-from $a$ to $b$.}
-
-\begin{dfn}
-  An element $a \in A$ is \emph{R-weakly confluent} ($WCR_R$) if all single step reductions from $a$ can always converge
-  via multi-step reductions to some common reduct.
-  A relation $R$ is \emph{weakly confluent} (AKA weakly Church-Rosser (WCR)) if every $a \in A$ is R-weakly confluent.
-\end{dfn}
-
-\begin{dfn}
-  An element $a \in A$ is \emph{R-confluent} ($CR_R$) if all multi-step reductions from $a$ can always converge
-  via multi-step reductions to some common reduct.
-  A relation $R$ is \emph{confluent} (AKA Church-Rosser (CR)) if every $a \in A$ is R-confluent.
-\end{dfn}
-
-\begin{figure}[h]
-  \centering
-\[  \begin{tikzpicture}[node distance=1.5cm, auto]
-    % Nodes
-    \node (top) {a};
-    \node (left) [below left of=top] {b};
-    \node (right) [below right of=top] {c};
-    \node (bottom) [below right of=left] {d};
-
-    % Arrows
-    \draw[->] (top) -- (left);
-    \draw[->] (top) -- (right);
-    \draw[->>] (left) -- (bottom);
-    \draw[->>] (right) -- (bottom);
-\end{tikzpicture}
-\hspace{3cm}
-\begin{tikzpicture}[node distance=1.5cm, auto]
-  % Nodes
-  \node (top) {a};
-  \node (left) [below left of=top] {b};
-  \node (right) [below right of=top] {c};
-  \node (bottom) [below right of=left] {d};
-
-  % Arrows
-  \draw[->>] (top) -- (left);
-  \draw[->>] (top) -- (right);
-  \draw[->>] (left) -- (bottom);
-  \draw[->>] (right) -- (bottom);
-\end{tikzpicture}
-\]
-\caption{On the left is an example of a weakly confluent relation. On the right is an example of a confluent relation.}
-\end{figure}
-
-\begin{dfn}
-  \emph An element $a \in A$ is a {normal form} if there exists no reduction to any other element in $A$.
-\end{dfn}
-
-\begin{dfn}
-  An element $a \in A$ is \emph{$R$-weakly normalizing} ($WN_{R}$)if $a \tto b$ for some normal form $b \in A$.
-
-  A relation $R$ is weakly normalizing (WN) if every $a \in A$ is $R$- weakly normalizing.
-\end{dfn}
-
-\begin{dfn}
-  An element $a \in A$ is \emph{$R$-strongly normalizing} ($SN_R$) if every reduction sequence starting from $a$ is finite.
-
-  A relation $R$ is strongly normalizing (SN) if every
-  $a \in A$ is $R$-strongly normalizing.
-\end{dfn}
-
-The above definition of SN is taken from [TeReSe]. When working in Agda, we make use of the alternative definition presented in [TeReSe] ($\leftarrow$ is accessibly well-founded).
-
-\subsection{Closure operations on relations}
-
-A relation $R$ has the following properties when the stated conditions are met:
-\begin{dfn}
-  \emph{reflexive} {- $\forall x \in A : x \to x $}
-\end{dfn}
-\begin{dfn}
-  \emph{transitive} {- $\forall x, y, z \in A : ( x \to y \land y \to z ) \implies x \to z $}
-\end{dfn}
-\begin{dfn}
-  \emph{symmetric} {- $\forall x, y \in A : x \to y \implies y \to x$}
-\end{dfn}
-
-\begin{dfn}
-  The \emph{closure} of $R$ is the smallest relation that contains $\to$ and satisfies a given property.
-\end{dfn}
-
-\begin{dfn}
-  The \emph{reflexive closure} of $R$ is the smallest relation $\to^r$ that contains $\to$ and is reflexive.
-\end{dfn}
-\begin{dfn}
-  The \emph{symmetric closure} of $R$ is the smallest relation $R^s$ that contains $R$ and is symmetric.
-\end{dfn}
-\begin{dfn}
-  The \emph{transitive closure} of $R$ is the smallest relation $R^+$ that contains $R$ and is transitive.
-\end{dfn}
-\begin{dfn}
-  The \emph{reflexive transitive closure} of $R$ is the smallest relation $R^*$ that contains $R$ and is both reflexive and transitive.
-\end{dfn}
-\begin{dfn}
-  The \emph{equivalence relation} of $R$ is the smallest relation $R^=$ that contains $R$ and is reflexive, transitive, and symmetric.
-\end{dfn}
-
-\begin{dfn}
-  A relation $R$ has the \emph{weak normal form property} (WNFP) if
- $a \tto b$ and $a \tto c$  $\implies$
- $c \tto b$, for all $a,c \in A$ and all normal form $b \in A$.
-\end{dfn}
-
-\begin{dfn}
-  A relation $R$ has the \emph{normal form property} (NFP) if
- $a \to^= b$  $\implies$
- $a \tto b$, for all $a \in A$ and any normal form $b \in A$.
-\end{dfn}
-
-Two elements $a, b \in A$ being equivalent is denoted $a \equiv b$.
-
-\begin{dfn}
-  A relation $R$ has the \emph{unique normal form property} (UN) if
-  $a \to^= b$  $\implies$
-  $a \equiv b$, for all $a \in A$ and any normal form $b \in A$.
-\end{dfn}
-
-\begin{dfn}
-  A relation $R$ has the \emph{unique normal form property with respect to reduction} (UN$^ \to$) if
-  $a \twoheadleftarrow  \cdot  \tto b$  $\implies$ $a \equiv b$, for all normal forms $a,b \in A$.
-\end{dfn}
-
-Let $A$ be a set.
-\begin{dfn}
-  A \emph{sequence (in $A$)} is a function from the natural numbers to $A$:
-  \begin{align*}
-    &s : \nat \to A \\
-    &s = (s_0,s_1,s_2,\dots)
-  \end{align*}
-\end{dfn}
-
-\begin{dfn}
-  A sequence is \emph{$R$-increasing} if every term is $R$-related to its preceding term.
-\end{dfn}
-
-\begin{dfn}
-  A sequence is \emph{bounded} if there exists an element $a$ to which all elements of the sequence reduce.
-\end{dfn}
-
-\begin{figure}[h]
-  \centering
-  \begin{tikzpicture}
-      % Define the nodes inside the region f
-      \node (f0) at (0, 0) {$f_0$};
-      \node (f1) at (1, 0) {$f_1$};
-      \node (dots) at (2, 0) {$...$};
-
-      % Draw the arrows between the nodes inside the region f
-      \draw[->] (f0) -- (f1);
-      \draw[->] (f1) -- (dots);
-      \draw[->] (f1) -- (dots);
-
-      % Define the nodes outside the region f
-      \node (a) [below=of dots, yshift=-.25cm] {\parbox{2cm}{\centering $a$ }};
-
-          % Draw the arrows between the nodes inside and outside the region f sds
-
-          \draw[->>] (f0) -- (a);
-          \draw[->>] (f1) -- (a);
-          \draw[->>] (dots) -- (a);
-      \end{tikzpicture}
-      \caption{An example of a bounded sequence.}
-
-    \end{figure}
-
-\begin{dfn}
-  An element $a \in A$ has the \emph{recurrence property} if $a \tto b \implies b \tto a$ for all $b \in A$.
-\end{dfn}
-\sacomment{I've been using $\tto$ as interchangable with $R *$ (as in the above definition).
-Is that okay or am I going to have to clarify why they are interchangable (are they not interchangable?)?}
-\apcomment{It's okay, but later we will need to make sure we are using them consistently.  Say that in Agda code, $\to$ is denoted by $R$.}
-
-\begin{dfn}
-  A relation $R$ has the \emph{recurrence property} (RP) if every
-  bounded, increasing sequence has a recurrent element.
-\end{dfn}
-
-    \begin{figure}[h]
-      \centering
-      \begin{tikzpicture}
-          % Define the nodes inside the region f
-          \node (f0) at (0, 0) {$f_0$};
-          \node (f1) at (1, 0) {$f_1$};
-          \node (dots) at (2, 0) {$...$};
-          \node (fi) at (3, 0) {$f_i$};
-          \node (fi+1) at (4, 0) {$f_{i+1}$};
-          \node (dots2) at (5,0) {$...$};
-
-          % Draw the arrows between the nodes inside the region f
-          \draw[->] (f0) -- (f1);
-          \draw[->] (f1) -- (dots);
-          \draw[->] (dots) -- (fi);
-          \draw[->] (fi) -- (fi+1);
-          \draw[->] (fi+1) -- (dots2);
-
-          % Define the nodes outside the region f
-          \node (a) [below=of dots, yshift=-.25cm] {\parbox{1cm}{\centering $a$ }};
-
-              % Draw the arrows between the nodes inside and outside the region f sds
-
-              \draw[->>] (f0) to [bend right] (a);
-              \draw[->>] (f1) to [bend right] (a);
-              \draw[->>] (dots) -- (a);
-              \draw[->>] (fi) to [bend left=10] (a);
-              \draw[->>] (fi+1) to [bend left] (a);
-              \draw[->>] (dots2) to [bend left] (a);
-              \draw[->>] (a) to [bend left=10] (fi);
-
-          \end{tikzpicture}
-          \caption{An example of a relation with the recurrence property.}
-
-        \end{figure}
-\begin{dfn}
-  A relation $R$ has the \emph{weak recurrence property} (RP-) if
-  for every increasing sequence with bound $a$,
-  there is an element $i$ of the sequence such that $a \tto f (i)$.
-\end{dfn}
-
-\begin{dfn}
-  A relation $R$ has the \emph{recurrence property} (RP) if
- $a \tto b$ and $a \tto c$  $\implies$
- $c \tto b$, for all $a,c \in A$ and all $b \in A$ with the recurrence property.
-\end{dfn}
-\sacomment{This mirrors our Weak normal form property but for recurrence. Which would be a suitable name?}
-
-\begin{dfn}
-  An element $a \in A$ is \emph{$R$-weakly recurrent} ($WR_{R}$)if $a \tto b$ for some recurrent element $b \in A$.
-
-  A relation $R$ is weakly recurrent (WR) if every $a \in A$ is $R$- weakly recurrent.
-\end{dfn}
-
-\begin{dfn}
-  An element $a \in A$ is \emph{$R$-strongly recurrent} ($SR_R$) if either $a$ itself is recurrent or every element one $R$ step 
-  from $a$ is also strongly recurrent.
-
-  A relation $R$ is strongly recurrent (SR) if every
-  $a \in A$ is $R$-strongly recurrent.
-\end{dfn}
-
-\begin{dfn}
-  An element $a \in A$ is \emph{$R$-strongly recurrent} ($SR_R$) if every reduction sequence starting from $a$ reaches a recurrent element in a finite number of steps.
-
-  A relation $R$ is strongly recurrent (SR) if every
-  $a \in A$ is $R$-strongly recurrent.
-\end{dfn}
-\sacomment{We have the two contender definitions for SR above.}
-
-\begin{dfn}
-  \emph{Cofinality property}
-\end{dfn}
-\sacomment{Still not sure on how to define cofinality.}
-
-\begin{dfn}
-  A relation $R$ is \emph{finitely branching} (FB) if, for all $a \in A$, the set of one step reducts of $a$ is finite.
-\end{dfn}
-
-\subsection{Recurrence property and increasing relations}
-
-In [TeReSe], a relation $R \sse A \times A$ is called \emph{increasing} if there
-exists a ``size function'' $|-| : A \to \nat$ satisfying, for all $x, y \in A$,
- \[ Rxy \to |x| < |y| \]
-
-\begin{prop}
-  If $R$ is increasing, then no infinite $R$-increasing sequence is bounded.
-\end{prop}
-\begin{proof}
-  Let $(a_i) = a_0 \to a_1 \to a_2 \to \cdots$ be an $R$-increasing sequence
-  and suppose that $(a_i)$ is bounded.  Let $b$ be the bound, so that $a_i \to b$ for all $i$.
-
-  If $m = |b|$ then we have
-  \[ 0 \le |a_0| < |a_1| < |a_2| < \cdots < |a_m| < |b| = m \]
-  % \[ m > |a_m| > |a_{m-1}| > \cdots > |a_0| \ge 0 \]
-  which is a contradiction, since there are only $m-1$ integers strictly less than $m$.
-\end{proof}
-
-It follows that every relation that is increasing in the sense of [TeReSe]
-vacuously satisfies the RP condition.
-
-\begin{cor}
-  If $R$ is increasing, then $R$ has the recurrence property.
-\end{cor}
-
-\section{Classical Principles}
-Principles we are considering
-\begin{itemize}
-  \item Decidability of equality on $A$
-  \item Decidability of the relation $R$
-  \item When relevant, decidability of the given precicate $P$
-  \item Not-not-closure of being accessible
-  \item Not-not-closure of $R$
-  \item Not-not-closure of $P$
-  \item Decidability of whether a given element is an $R$-normal form
-  \item When relevant, local/element-wise versions of the above
-  \item Markov's principle:
-  \begin{itemize}
-    \item In $wfMin_0 \to wfSeq$.
-
-    Given a sequence $s : \nat \to A$, let $E(a) = \exists n \in \nat. s n \equiv a$.
-
-    Need: $\forall a. \lnot\lnot E(a) \to E(a)$, i.e.,
-    \[\lnot\lnot \big(\exists n \in \nat. s n \equiv a\big)
-          \to \big(\exists n \in \nat. s n \equiv a\big)\]
-
-  \end{itemize}
-\end{itemize}
-
-\section{Implications}
-{\small
-We now look into the interrelation of the various properties defined in Section~\ref{section:Definitions}. Our aim is to expand on the
-connections made in Figure 1.8 of [TeReSe] (p.19).
-
-The following are the implications we have proven in Agda, along with a reference to the name of the proof in Agda. Where appropriate we indicate
-which classical assumptions were used as part of the proof.
-
-\begin{itemize}
-  \item SN and WCR $\implies$ CR
-
-\texttt{NewmansLemma : $\mathnormal{\forall}$ \{R : $\mathbb{R}$ A\} $\to$ SN R $\to$ weakly-confluent R $\to$ confluent R}
-
-We have also provided a proof elementwise making use of the classical principal
-about the decidability of $R$ being minimal.
-
-\texttt{SN$\land$UN$\to$CRelem :\newline $\forall$ (R : $\mathbb{R}$ A) $\to$ decMin (~R R) $\to$ $\forall$ x $\to$ is R -SN x $\to$ is R -UN x$\to$ is R -CR x}
-
-\sacomment{How to one line this consistently and in a pretty way?}
-
-\item{CP $\implies$ CR}
-
-\texttt{iv : CP R $\to$ confluent R}
-
-This is theorem 1-2-3 iv in [TeReSe]
-
-\item{WN and UN $\implies$ CR}
-
-\texttt{ii : WN R $\times$ UN R $\to$ confluent R}
-
-This is theorem 1-2-2 ii in [TeReSe]
-
-\item{WN and UN $\implies$ bounded}
-
-\texttt{i : WN R $\to$ UN R $\to$ bounded R}
-
-\sacomment{Going to have to find a way to neatly represent the implications}
-
-\sacomment{note to self, tidy up below with references to agda code}
-
-\item{WN and UN$\to$ $\implies$ bounded}
-
-\texttt{i+ : WN R $\to$ UN$\to$ R $\to$ bounded R}
-
-\item{WN and UN and RP $\implies$ wfSeq - ($\sim$ R)}
-
-\texttt{ii3- :  WN R $\to$ UN R $\to$ RP R $\to$ isWFseq- ($\sim$R R)}
-
-\item {CR $\implies$ WCR}
-
-\texttt{CR$\to$WCR : CR R $\to$ WCR R }
-
-\item {NF $implies$ UN}
-\sacomment{Need to prove}
-
-\item {SN and WCR $\implies$ UN and WN}
-\sacomment{Need to proove}
-\texttt{}
-
-\item {Ind and Inc $\implies$ SN} \sacomment{I don't think we have
-a proof of this, should we include it, include it with a note that we're taking [TeReSe]'s word on it?}
-
-\item {WCR, WN, and, Inc $\implies$ SN}
-
-\item {WCR, WN, and RP $\implies$ SN}
-
-\item {CR $\implies$ NF $\implies$ UN}
-
-\texttt{i-4 : confluent R $\to$ NFP R $\to$ UN R}
-
-\item {CR $^{\leq1} \implies$ CR}
-
-\texttt{iv : CP R $\to$ confluent R}
-
-\end{itemize}
-}
-
-\subsection{Double-check: What has been proven}
-\begin{itemize}
-  \item \sacomment{List all the constructive proofs we've put together!}
-  \item SN implies bounded
-  \item RP- implies RP
-  \item The infinite haircomb refutes $WN \land RP \to \omega$-bounded.  But it is not WCR.
-  \item We have formalized proposition 1.1.9, 1.1.10, 1.1.11 from [TeReSe].
-  \item We have a proof for Theorem 1.2.1 (Newlman's Lemma) (though we have just one proof of multiple possible proofs).
-  \item We have a proof for all parts of Theorem 1.2.2
-  \item We have a proof for Theorem 1.2.3 i, iv.
-  \item Reduction closure properties for SN, NF, UN, recurrent property.
-
-  So, does $WN, RP, WCR$ imply $\omega$-bounded?
-  Answer: yes, that is what we have proved classically.
-\end{itemize}
-
-\subsection{Hierarchy}
-The properties of strong normality and confluence are the two properties of greatest interest. As such, there is 
-value in determining which other properties combine to imply one these properties. This motivated the development of the 
-following hierarchies.
-
-\subsubsection{Confluence hierarchy}
-
-\begin{center}
-
-  \begin{tikzpicture}[auto,
-    arrowstyle/.style={->, line width=1pt, >={Latex[length=3mm, width=2mm]}, shorten >=2pt}]
-    % A box style
-    \tikzstyle{boxnode} = [draw, rectangle, minimum width=3cm, minimum height=1cm, text centered]
-
-    % Place the nodes vertically (top to bottom)
-    \node (Confluent) [boxnode] at (0,0) {Confluent};
-    \node (RP)        [boxnode, below=2cm of Confluent] {Recurrence Property};
-    \node (WN)        [boxnode, below=2cm of RP] {Weak Normal Form Property};
-    \node (UN)        [boxnode, below=2cm of WN] {Unique Normal Form Property};
-
-    % Draw arrows downwards
-    \draw[arrowstyle] (Confluent) -- (RP);
-    \draw[arrowstyle] (RP) -- (WN);
-    \draw[arrowstyle] (WN) -- (UN);
-  \end{tikzpicture}
-\end{center}
-
-\subsubsection{Normalization hierarchy}
-
-\begin{tikzpicture}[node distance=2cm, auto,
-  % Define a thicker arrow with larger arrowhead and some shortening
-  arrowstyle/.style = {->, line width=1pt, >={Latex[length=3mm, width=2mm]}, shorten >=2pt}
-]
-% Define a box style
-\tikzstyle{boxnode} = [draw, rectangle, minimum width=3cm, minimum height=1cm, text centered]
-
-% Define the nodes
-\node (SN) [boxnode] at (0,0) {Strongly Normal};
-\node (WN) [boxnode, below left=2cm and 2cm of SN] {Weakly Normal};
-\node (SR) [boxnode, below right=2cm and 2cm of SN] {Strongly Recurrent};
-\node (WR) [boxnode, below of=SN, yshift=-4cm] {Weakly Recurrent};
-
-% Draw the arrows to form a diamond
-\draw [arrowstyle] (SN) -- (WN);
-\draw [arrowstyle] (SN) -- (SR);
-\draw [arrowstyle] (WN) -- (WR);
-\draw [arrowstyle] (SR) -- (WR);
-\end{tikzpicture}
-
-The property of being strongly recurrent implies the property of being weakly recurrent only when there is also the classical property 
-of decidability of minimality for a given element.
-
-In the following table red text indicates that classical properties are required for the implication to hold. Blue indicates we are currently unsure.
-
-\begin{table}[h!]
-  \centering
-  \caption{Local implications}
-  \begin{tabular}{|l|c|c|c|c|c|}     
-  \hline
-  \textbf{CR} & CR, CE-9  & CR, CE-6  & CR , CE-9  & CR, ?  & CR , SN \\
-  \hline
-  \textbf{RP} & CR, CE-9  & CR, CE-6  & \red{CR} , CE-9 & CR, ?   & \red{CR} , SN \\
-  \hline
-  \textbf{WNFP} & CE-10, CE-9  & CR, CE-6  & CE-11 , CE-9 & CR, ?   & \red{CR} , SN \\
-  \hline
-  \textbf{UN} & CE-3, CE-12  & CE-3, CE-6  & CE-3, CE-9  & CE-3, CE-3  & \red{CR} , SN \\
-  \hline
-  & \textbf{WR} & \textbf{WN} & \textbf{SR} & \textbf{WN}$\boldsymbol{\land}$\textbf{SR} & \textbf{SN} \\
-  \hline  
-  \end{tabular}
-\end{table}
-
-\begin{table}[h!]
-  \centering
-  \caption{Local implications - WCR }
-  \begin{tabular}{|l|c|c|c|c|c|}     
-  \hline
-  \textbf{CR} & CR, CE-9  & CR, {CE-6}  & CR , {CE-9}  & CR, ?  & CR , SN \\
-  \hline
-  \textbf{RP} & CR, CE-9  & CR, {CE-6}  & \red{CR} , {CE-9} & CR, ?   & \red{CR} , SN \\
-  \hline
-  \textbf{WNFP} & CE-10.1, CE-9  & CR, {CE-6}  & {CE-11} , {CE-9} & CR, ?  & \red{CR} , SN \\
-  \hline
-  \textbf{UN} & CE-3.1, CE-12  & {CE-3.1}, {CE-6}  & {CE-3.1}, {CE-9}  & {CE-3.1}, {CE-3.1}  & \red{CR} , SN \\
-  \hline
-  & \textbf{WR} & \textbf{WN} & \textbf{SR} & \textbf{WN}$\boldsymbol{\land}$\textbf{SR} & \textbf{SN} \\
-  \hline  
-  \end{tabular}
-\end{table}
-
-\begin{table}[h!]
-  \centering
-  \caption{Global implications}
-  \begin{tabular}{|l|c|c|c|c|c|}     
-  \hline
-  \textbf{CR} & CR, {CE-9}  & CR, {CE-6}  & CR , {CE-9}  & CR, ?  & CR , SN \\
-  \hline
-  \textbf{RP} & CR, {CE-9}  & CR, {CE-6}  & \red{CR} , {CE-9} & CR, ?   & \red{CR} , SN \\
-  \hline
-  \textbf{WNFP} & {CE-11}, {CE-9}  & CR, {CE-6}  & CE-11 , {CE-9} & CR, ?   & \red{CR} , SN \\
-  \hline
-  \textbf{UN} & {CE-3}, {CE-12} and CE-9  & CR, {CE-6}  & CE-3, {CE-9}  & CR, ?  & \red{CR} , SN \\
-  \hline
-  & \textbf{WR} & \textbf{WN} & \textbf{SR} & \textbf{WN}$\boldsymbol{\land}$\textbf{SR} & \textbf{SN} \\
-  \hline  
-  \end{tabular}
-\end{table}
-
-\begin{table}[h!]
-  \centering
-  \caption{Global implications - WCR}
-  \begin{tabular}{|l|c|c|c|c|c|}     
-  \hline
-  \textbf{CR} & CR, {CE-9}  & CR, {CE-6}  & CR , {CE-9}  & CR, ?  & CR , SN \\
-  \hline
-  \textbf{RP} & CR, {CE-9}  & CR, {CE-6}  & {CR} , {CE-9} & CR, ?   & CR , SN \\
-  \hline
-  \textbf{WNFP} & CE-1.2, {CE-9}  & CR, {CE-6}  & {CR} , {CE-9} & CR, ?   & CR , SN \\
-  \hline
-  \textbf{UN} & CE-1.1, {CE-9}  & CR, {CE-6}  & {CR}, {CE-9}  & CR, ?  & CR , SN \\
-  \hline
-  & \textbf{WR} & \textbf{WN} & \textbf{SR} & \textbf{WN}$\boldsymbol{\land}$\textbf{SR} & \textbf{SN} \\
-  \hline  
-  \end{tabular}
-\end{table}
-
-\newpage
-\section{Counterexamples}
-The following counterexamples are used to rule out certain implications between properties from holding.
-\subsection*{Counterexample 1}
-\begin{center}
-
-  \begin{tikzcd}[node distance=2cm, auto]
-      % Nodes
-      \node (a) {a};
-      \node (b) [right of=a, xshift=1cm] {b};
-      \node (c) [right of=b, xshift=1cm] {c};
-      \node (d) [right of=c, xshift=1cm] {d};
-
-      % Arrows
-      \draw[->] (b) to [bend left] (c);
-      \draw[->] (c) to [bend left] (b);
-      \draw[->] (b) -- (a);
-      \draw[->] (c) -- (d);
-  \end{tikzcd}
-
-\end{center}
-Counterexample to:
-\begin{itemize}
-  \item WCR $\implies$ CR
-  \item WCR  $\implies$ WNFP
-  \item \mbox{WCR R $\to$ $\forall$ a b $\to$ is R -NF b $\to$ (R *) a b $\to$ $\forall$ c $\to$ R a c $\to$ (R *) c b }
-  \item WCR and WN $\implies$ CR
-  \item WCR and WN $\implies$ SN
-  \item IOW and WCR $\implies$ WNFP \sacomment{We need to define IOW in the report}
-\end{itemize}
-
-\subsection*{Counterexample 1.1}
-\begin{center}
-
-  \begin{tikzcd}[node distance=2cm, auto]
-      % Nodes
-      \node (a) {a};
-      \node (b) [right of=a, xshift=1cm] {b};
-      \node (c) [right of=b, xshift=1cm] {c};
-      \node (d) [right of=c, xshift=1cm] {d};
-
-      % Arrows
-      \draw[->] (b) to [bend left] (c);
-      \draw[->] (c) to [bend left] (b);
-      \draw[->] (b) -- (a);
-      \draw[->] (c) -- (d);
-      \draw[->, loop] (d) to (d);
-
-  \end{tikzcd}
-
-\end{center}
-Counterexample to:
-\begin{itemize}
-  \item (Global) WCR, UN, and WR $\implies$ WNFP
-\end{itemize}
-
-\subsection*{Counterexample 1.2}
-\begin{center}
-
-  \begin{tikzcd}[node distance=2cm, auto]
-      % Nodes
-      \node (a) {a};
-      \node (b) [right of=a, xshift=1cm] {b};
-      \node (c) [right of=b, xshift=1cm] {c};
-      \node (d) [right of=c, xshift=1cm] {d};
-
-      % Arrows
-      \draw[->] (b) to [bend left] (c);
-      \draw[->] (c) to [bend left] (b);
-      \draw[->] (b) -- (a);
-      \draw[->] (c) -- (d);
-      \draw[->, loop] (d) to (d);
-      \draw[->, loop] (a) to (a);
-
-  \end{tikzcd}
-
-\end{center}
-Counterexample to:
-\begin{itemize}
-  \item (Global) WCR, WNFP, and WR $\implies$ RP
-\end{itemize}
-
-\subsection*{Counterexample 2}
-\begin{center}
-  \begin{tikzcd}
-      % Nodes
-      \node (x) {a};
-      \node (n) [left of=x, xshift=-1cm] {n \in NF};
-      \node (y) [right of=x, xshift=1cm] {b};
-      \node (z) [right of=y] {c};
-
-      % Arrows
-      \draw[->] (x) -- (n);
-      \draw[->] (x) -- (y);
-      \draw[->] (y) to [bend left] (z);
-      \draw[->] (z) to [bend left] (y);
-  \end{tikzcd}
-\end{center}
-
-Counterexample to:
-\begin{itemize}
-  \item WCR and an increasing sequence where the first elelement of the sequence reduces to an element in normal form $\to$
-  the sequence is bounded.
-\end{itemize}
-
-\subsection*{Counterexample 3}
-\begin{center}
-  \begin{tikzcd}
-      % Nodes
-      \node (x) {a};
-      \node (n) [left of=x, xshift=-1cm] {n \in NF};
-      \node (y) [right of=x, xshift=1cm] {b};
-      \node (z) [right of=y] {c};
-
-      % Arrows
-      \draw[->>] (x) -- (n);
-      \draw[->>] (x) -- (y);
-      \draw[->] (y) to [bend left] (z);
-      \draw[->] (z) to [bend left] (y);
-  \end{tikzcd}
-\end{center}
-
-Counterexample to:
-\begin{itemize}
-  \item WN$\downarrow\subseteq$WN (WN is not closed under reduction) \sacomment{Is this the right way to express that elementwise WN doesn't imply global WN?}
-  \item WN$\downarrow$UN$\rightarrow\subseteq$WN :
-
-  UN$\rightarrow\,$R $\to \forall$ x $\to$ is R-WN x $\to$ $\forall$ y $\to$ (R *) x y $\to$ is R-WN y
-
-  \item $\forall$ (R : $\mathscr{R}$ A) $\to$ $\forall$ is R -WN x $\to$ is R -UN x $\to$ is R -CR x
-  \item $WN_R$ and $UN_R$ $\implies$ $CR_R$
-  \item (Local) WR and UN $\implies$ NP 
-  \item (Local) WN and UN $\implies$ SR
-
-\end{itemize}
-
-\subsection*{Counterexample 3.1}
-\begin{center}
-  \begin{tikzcd}
-      % Nodes
-      \node (x) {a};
-      \node (a') [above of=x] {a'};
-      \node (n) [left of=x, xshift=-1cm] {n \in NF};
-      \node (y) [right of=x, xshift=1cm] {b};
-      \node (z) [right of=y] {c};
-
-      % Arrows
-      \draw[->>] (x) -- (n);
-      \draw[->] (a') -- (x);
-      \draw[->] (a') -- (n);
-      \draw[->>] (x) -- (y);
-      \draw[->] (y) to [bend left] (z);
-      \draw[->] (z) to [bend left] (y);
-  \end{tikzcd}
-\end{center}
-
-Counterexample to:
-\begin{itemize}
-  \item (Local) WCR, WR, and UN $\implies$ NP 
-  \item (Local) WCR, WN and UN $\implies$ SR
-
-\end{itemize}
-
-\subsection*{Counterexample 4}
-
-\begin{center}
-  \begin{tikzcd}
-      % Nodes
-      \node (x) {a};
-
-      % Arrows
-      \draw[->, loop] (x) to (x);
-  \end{tikzcd}
-\end{center}
-Counterexample to:
-\begin{itemize}
-  \item bounded and RP $\implies$ SN
-  \item bounded and RP $\implies$ WN
-\end{itemize}
-
-\subsection*{Counterexample 5}
-An infinite sequence
-  \begin{center}
-      \begin{tikzpicture}
-      % Define the nodes
-      \node (a) at (0, 0) {$f_0$};
-      \node (b) at (1, 0) {$f_1$};
-      \node (dots) at (2, 0) {$...$};
-
-      % Draw the arrows
-      \draw[->] (a) -- (b);
-      \draw[->] (b) -- (dots);
-      \end{tikzpicture}
-    \end{center}
-Counterexample to:
-\begin{itemize}
-  \item WN
-  \item bounded
-  \item RP $\implies$ bounded
-  \item WCR $\implies$ WN
-  \item CR $\implies$ WN
-  \item CR and CP $\implies$ WN
-  \item CR and CP $\implies$ bounded
-\end{itemize}
-
-\subsection*{Counterexample 6}
-An infinite sequence with a bound that is a normal form.
-\begin{center}
-
-  \begin{tikzpicture}
-      % Define the nodes inside the region f
-      \node (f0) at (0, 0) {$f_0$};
-      \node (f1) at (1, 0) {$f_1$};
-      \node (dots) at (2, 0) {$...$};
-
-      % Draw the arrows between the nodes inside the region f
-      \draw[->] (f0) -- (f1);
-      \draw[->] (f1) -- (dots);
-      \draw[->] (f1) -- (dots);
-
-      % Define the nodes outside the region f
-      \node (a) [below=of dots, yshift=-.25cm] {\parbox{2cm}{\centering $n\in NF$ }};
-
-          % Draw the arrows between the nodes inside and outside the region f sds
-
-          \draw[->] (f0) -- (a);
-          \draw[->] (f1) -- (a);
-          \draw[->] (dots) -- (a);
-      \end{tikzpicture}
-
-    \end{center}
-Counterexample to:
-\begin{itemize}
-  \item WN $\implies$ SN
-  \item WN and CR $\implies$ SN
-  \item WN, CR, and bounded $\implies$ SN
-  \item WN, UN, and bounded $implies$ SN
-  \item (Local) WN and UN $\implies$ SR
-  \item (Local) WN and NP $\implies$ SR
-  \item (Local) WN and RP $\implies$ SR
-  \item (Local) WN and CR $\implies$ SR
-  \item (Local) WN, SR, and NP $\implies$ SN
-  \item (Local) WN, SR, and RP $\implies$ SN
-  \item (Local) WN, SR, and CR $\implies$ SN
-\end{itemize}
-
-\subsection*{Counterexample 7}
-An infinite sequence with a bound that is a normal form where each element
-of the sequence has a single step relation to the initial element of the sequence.
-\begin{center}
-  \begin{tikzpicture}
-      % Define the nodes inside the region f
-      \node (f0) at (0, 0) {$f_0$};
-      \node (f1) at (1, 0) {$f_1$};
-      \node (dots) at (2, 0) {$...$};
-
-      % Draw the arrows between the nodes inside the region f
-      \draw[->] (f0) -- (f1);
-      \draw[->] (f1) -- (dots);
-      \draw[->] (f1) -- (dots);
-      \draw[->] (f1) to [bend right=20] (f0);
-      \draw[->] (dots) to [bend right=50] (f0);
-
-      % Define the nodes outside the region f
-      \node (a) [below=of dots, yshift=-.25cm] {\parbox{2cm}{\centering $n\in NF$ }};
-
-          % Draw the arrows between the nodes inside and outside the region f sds
-
-          \draw[->>] (f0) -- (a);
-          \draw[->>] (f1) -- (a);
-          \draw[->>] (dots) -- (a);
-      \end{tikzpicture}
-
-    \end{center}
-Counterexample to:
-\begin{itemize}
-  \item RP
-\end{itemize}
-
-\subsection*{Counterexample 8}
-An "infinite haircomb"
-\begin{center}
-  \begin{tikzpicture}
-      % Define the nodes inside the region f
-      \node (f0) at (0, 0) {$f_0$};
-      \node (f1) at (1, 0) {$f_1$};
-      \node (f2) at (2, 0) {$f_2$};
-      \node (dots) at (3, 0) {$...$};
-
-      \node (n0) at (0, -1) {$n_0$};
-      \node (n1) at (1, -1) {$n_1$};
-      \node (n2) at (2, -1) {$n_2$};
-      \node (dots2) at (3, -1) {$...$};
-
-      \draw[->] (f0) -- (f1);
-      \draw[->] (f1) -- (f2);
-      \draw[->] (f2) -- (dots);
-
-      \draw[->] (f0) -- (n0);
-      \draw[->] (f1) -- (n1);
-      \draw[->] (f2) -- (n2);
-      \draw[->] (dots) -- (dots2);
-
-      \end{tikzpicture}
-
-    \end{center}
-Counterexample to:
-\begin{itemize}
-  \item WN $\implies$ WCR
-  \item WN $\implies$ bounded
-  \item WN $\implies$ SN
-  \item WN and RP $\implies$ SN
-\end{itemize}
-
-\subsection*{Counterexample 9}
-\begin{center}
-
-  \begin{tikzcd}[node distance=2cm, auto]
-      % Nodes
-      \node (a) {a};
-      \node (b) [right of=a, xshift=1cm] {b};
-
-      % Arrows
-      \draw[->] (a) to [bend left] (b);
-      \draw[->] (b) to [bend left] (a);
-  \end{tikzcd}
-
-\end{center}
-Counterexample to:
-\begin{itemize}
-  \item (Local) WCR, WR, and UN $\implies$ WN 
-  \item (Local) SR and CR $\implies$ WN 
-\end{itemize}
-
-\subsection*{Counterexample 10}
-\begin{center}
-  \begin{tikzpicture}
-      % Nodes
-      \node (a) {a};
-      \node (b) [left of=a, xshift=-1cm, yshift=-1cm] {b};
-      \node (c) [left of=b] {c};
-      \node (f0) [right of=a, xshift=1cm, yshift=-1cm] {$f_0$};
-      \node (f1) [right of=f0, xshift=1cm] {$f_1$};
-      \node (f2) [right of=f1, xshift=1cm] {$f_2$};
-      \node (dots) [right of=f2, xshift=1cm] {...};
-
-      % Arrows
-      \draw[->] (a) -- (b);
-      \draw[->] (b) to [bend left] (c);
-      \draw[->] (c) to [bend left] (b);
-      \draw[->] (a) -- (f0);
-      \draw[->] (f0) -- (f1);
-      \draw[->] (f1) -- (f2);
-      \draw[->] (f2) -- (dots);
-  \end{tikzpicture}
-\end{center}
-
-Counterexample to:
-\begin{itemize}
-  \item (Local) WR, and NP $\implies$ RP 
-\end{itemize}
-
-\subsection*{Counterexample 10.1}
-\begin{center}
-  \begin{tikzpicture}
-      % Nodes
-      \node (a) {a};
-      \node (a') [above of=a] {a'};
-      \node (b) [left of=a, xshift=-1cm, yshift=-1cm] {b};
-      \node (c) [left of=b] {c};
-      \node (f0) [right of=a, xshift=1cm, yshift=-1cm] {$f_0$};
-      \node (f1) [right of=f0, xshift=1cm] {$f_1$};
-      \node (f2) [right of=f1, xshift=1cm] {$f_2$};
-      \node (dots) [right of=f2, xshift=1cm] {...};
-
-      % Arrows
-      \draw[->] (a) -- (b);
-      \draw[->] (a') -- (a);
-      \draw[->] (a') -- (b);
-      \draw[->] (b) to [bend left] (c);
-      \draw[->] (c) to [bend left] (b);
-      \draw[->] (a) -- (f0);
-      \draw[->] (f0) -- (f1);
-      \draw[->] (f1) -- (f2);
-      \draw[->] (f2) -- (dots);
-  \end{tikzpicture}
-\end{center}
-
-Counterexample to:
-\begin{itemize}
-  \item (Local) WCR, WR, and NP $\implies$ RP 
-\end{itemize}
-
-\subsection*{Counterexample 11}
-\begin{center}
-  \begin{tikzpicture}
-      % Nodes
-      \node (a) {a};
-      \node (b) [left of=a, xshift=-1cm, yshift=-1cm] {b};
-      \node (c) [left of=b] {c};
-      \node (d) [right of=a, xshift=1cm, yshift=-1cm] {d};
-      \node (e) [right of=d] {e};
-
-      % Arrows
-      \draw[->] (a) -- (b);
-      \draw[->] (b) to [bend left] (c);
-      \draw[->] (c) to [bend left] (b);
-      \draw[->] (a) -- (d);
-      \draw[->] (d) to [bend left] (e);
-      \draw[->] (e) to [bend left] (d);
-
-  \end{tikzpicture}
-\end{center}
-
-Counterexample to:
-\begin{itemize}
-  \item (Local) SR and NP $\implies$ RP 
-\end{itemize}
-
-\subsection*{Counterexample 12}
-\begin{center}
-
-  \begin{tikzcd}[node distance=2cm, auto]
-      % Nodes
-      \node (a) {a};
-      \node (b) [right of=a, xshift=1cm] {b};
-      \node (n) [below of=a, xshift=1cm] {n};
-
-      % Arrows
-      \draw[->] (a) to [bend left] (b);
-      \draw[->] (b) to [bend left] (a);
-      \draw[->] (a) -- (n);
-  \end{tikzcd}
-
-\end{center}
-Counterexample to:
-\begin{itemize}
-    \item (gloabl) WCR, WR, and UN $implies$ WN or SR or SN
-\end{itemize}
-
 \section{Well-foundedness}
-\subsection{Well-foundedness}
-\sacomment{Talk about the different types of wellfoundedness, starting with the one given in the book, the reason for thinking it is classical and not constructive, and provide an image showing the relation between the notions of wellfoundedness we have.
-Talk about future work in this area.}
-
-\apcomment{Mention that, for a set $A$, we will use "subset of $A$" and "predicate on $A$" interchangeably,
-with subsets being represented in the Agda code using predicates, which are in turn formalized as
-dependent types over $A$, i.e. maps $\phi : A \to \bset$ }
-
-Working in constructive logic introduces subtle differences between notions of well-foundedness of relations
-which are not present in classical logic.
-In our investigation, we have focused on four distinct definitions of well-foundedness, with minor variations of each.
-To spell these out, we first define some preliminary notions.
-% The make clear the difference between these distinct notions of well-foundedness we first present the following defintiions for a given relation $R$.
-
-\begin{dfn} Let $A$ be a set and $R \sse A \times A$ be a relation.
-\begin{enumerate}
-  \item Let $\phi$ be a predicate on $A$. An element $x \in A$ is $R$-minimal for $\phi$ if $\phi(x)$ is true and no other element for which $\phi$ holds is $R$-related to $x$.
-  \item An element $x \in A$ is \textit{$R$-accessible} if every element $R$-related to $x$ is \textit{$R$-accessible}.
-(This should be understood as an inductive definition, with base case consisting of $R$-minimal elements for the whole of $A$.)
-    \item A predicate $\phi$ on $A$ is \emph{inductive} if it holds on a given element $x \in A$ whenever it holds on all elements $R$-related to $x$:
-    \[ (\forall y. Ryx \to \phi(y)) \to \phi(x) \]
-    \item A sequence $s = (s_0,s_1,\dots)$ of elements of $A$ is $R$-decreasing
-    if every element is related to its predecessor.  That is, $Rs_{n+1}s_n$ for all $n$.
-\end{enumerate}
-\end{dfn}
-With the above definitions established we define the notions of well-foundedness we have been investigating.
-\begin{dfn} \hfil
-  \begin{enumerate}
-    \item \textit{R} is well-founded if every element is \textit{R}-accessible.
-    \item \textit{R} is well-founded if every inductive predicate is universally true.
-    \item \textit{R} is well-founded if every non-empty predicate has a minimal element with respect to $R$.
-    \item \textit{R} is well-founded if every sequence contains a non-decreasing index.
-  \end{enumerate}
-\end{dfn}
-  Further, we explored weaker variants of these notions of well-foundedness.
-  \begin{dfn} \hfil
-    \begin{enumerate}
-      \item \textit{R} is well-founded if every element is $\lnot \lnot$  \textit{R}-accessible.
-      \item \textit{R} is well-founded if for every inductive predicate $\phi$, $\lnot \lnot \phi$ is universally true.
-      \item \textit{R} is well-founded if it is not not the case that every non-empty predicate has a minimal element with respect to $R$.
-\textcolor{red}{is there a better way to express this double negation in english?}
-      \item \textit{R} is well-founded if there is no infinite $R$-decreasing sequence (this is the definition of well-foundedness found in TeReSe).
-    \end{enumerate}
-\end{dfn}
-
-\begin{figure}[h]
-  \centering
-  \begin{tikzpicture}[node distance=2cm, auto]
-    % Standard definitions
-    \node (std1) [draw] {isWFacc};
-    \node (std2) [below of=std1, draw] {isWFind};
-    \node (std3) [below of=std2, draw] {isWFmin};
-    \node (std4) [below of=std3, draw] {isWFseq};
-
-    % Double negation definitions
-    \node (dn1) [right of=std1, xshift=2cm, draw] {$\lnot \lnot$ isWFacc};
-    \node (dn2) [right of=std2, xshift=2cm, draw] {$\lnot \lnot$ isWFind};
-    \node (dn3) [right of=std3, xshift=2cm, draw] {$\lnot \lnot$ isWFmin};
-    \node (dn4) [right of=std4, xshift=2cm, draw] {$\lnot \lnot$ isWFseq};
-
-    % Weaker definitions
-    \node (weak1) [right of=dn1, xshift=2cm, draw] {isWFacc-};
-    \node (weak2) [right of=dn2, xshift=2cm, draw] {isWFind-};
-    \node (weak3) [right of=dn3, xshift=2cm, draw] {isWFmin-};
-    \node (weak4) [right of=dn4, xshift=2cm, draw] {isWFseq-};
-
-    % Arrows
-    \draw[->, thick, darkgreen] (std1) -- (dn1);
-    \draw[->, thick, darkgreen] (std1.west) to[out=180, in=90, bend right] (std4);
-    \draw[->, thick, darkgreen] (dn1) -- (weak1);
-    \draw[<->, thick, darkgreen] (std1) -- (std2);
-    \draw[->, thick, darkgreen] (std2) -- (dn2);
-    \draw[->, thick, darkgreen] (dn2) -- (weak2);
-    \draw[<->, thick, darkgreen] (weak1) -- (weak2);
-    \draw[->, thick, red] (std2) -- (std3) node[pos=0.5, right, red] {?};
-    \draw[->, thick, darkgreen] (std3) -- (dn3);
-    \draw[->, thick, darkgreen] (dn3) -- (weak3);
-    \draw[->, thick, darkgreen] (weak2) -- (weak3);
-    \draw[->, thick, darkgreen, bend left] (std3) to (std4);
-    \draw[->, thick, darkgreen, bend left] (weak3) to (weak4);
-    \draw[->, thick, darkgreen] (std4) -- (dn4);
-    \draw[->, thick, darkgreen] (dn4) -- (weak4);
-    \draw[->, thick, red, bend left] (std4) -- (std3) node[pos=0.5, left, red] {?};
-    \draw[->, thick, red, bend left] (weak4) -- (weak3) node[pos=0.5, left, red] {?};
-  \end{tikzpicture}
-  \caption{A graphic illustrating the implications we have found between the above
-  definitions and those we are still seeking to find. Green arrows indicate that one
-  definition implies another, red arrows indicate that we believe an implication should
-  be possible but we have not yet found it.
-  }
-\end{figure}
-
-  As future work we want to know whether the missing implications can be found, or what the minimal additional requirements are for making those implications.
-
-\subsection{Additional Remarks}
-
-\texttt{isWFmin} is only provably when restricted to \emph{decidable} predicates, and this
-restriction is also necessary: in general, WFmin for all P implies all predicates are decidable.
-
-  \section{Open Questions }
-  \begin{enumerate}
-    \item Complete the Wellfoundedness implications:
-       \[ WNg \land UN \to CRelem :
-       \forall (R : \mathscr{R} A) \to WN R \to \forall x \to is R -UN x \to is R -CR x \]
-       \item $WN R \to UN R \to \omega-bdd R \to SN R$ (1.2.3.ii-)
-        \item Finish formulating the ``compactness property".  Two candidates:
-         \item ``Every cocone for a given infinite sequence loops back to some point in the sequence"
-         \item ``If an $R^*$-sequence has a cocone then it's constant after some point on.''
-         \item is $\omega$-bounded implied by WN and the following confluence property:
-         $a \to^* n \in NF$, and $a \to b$ then $b \to^* n $.
-    \item (2024.10.10) Is being $R$-WN inductive?
-    \item (2024.10.10) Does $R$ being finitely branching imply
-     that, for an inductive $\phi$, if $\lnot \phi(x)$ then
-     $\exists y. Rxy \land \lnot \phi(y)$?
-
-    \item If WCR holds, is WN$\downarrow\subseteq$WN ?
-    \item Same question for next bullet in 2.2
-    \item Same for bullet 3 in 2.2 (but pointwise!)
-    \item \item Look at restricting WFmin to $\lnot\lnot$-closed predicates
-    \item Status of important hypotheses:
-      \begin{itemize}
-        \item Deciding whether a given element $x$ reduces to a given element $y$
-        (Is $R$ itself decidable?)
-        \item Deciding whether a given element $x$ reduces to some element $y$
-        (Is being an $R$-normal form decidable?)
-
-        {\textcolor{red}{This is needed to show that SN $\Rightarrow$ WN.}}
-
-        \item If a given element $x$ is \emph{not} a normal form,
-        exhibiting some element $y$ that it reduces to.
-        (This is related to DeMorgan/Markov/etc. properties that came up in WF file.)
-
-        \item Does UN-lemma \emph{require} the decidability assumption?
-      \end{itemize}
-    \item META questions: Which of the ARS theorems can be made ``local/pointwise'',
-    for example,
-    \begin{itemize}
-      \item NL+: $WCR(R) \land SN(x) \to CR(x)$?  (Yes?)
-      \item NL++: $WCR(x) \land SN(x) \to CR(x)$? (No.)
-    \end{itemize}
-    \item Can "sequential" properties like RP, RP-, isWFseq, isWFseq-, $\omega$-bounded, etc.,
-      be related to the cofinality property.
-      \item What happens if properties involving sequences are reformulated for
-    $R^r$? (Cannot decide whether the given sequence is finite or infinite.)
-    \item Knaster-Tarski Lemma: Most general form? Alternative formulations?
-    \item Knaster--Tarski in a well-founded setting: what additional
-    hypotheses are necessary?
-    \item Show SN and WNFP $\to$ CR : SN R $to$ WNFP R $to$ CR R (or, what combination of properties with WNFP gets us to CR)
-    \item Major: Find a classical or constructive solution to theorem 1-2-3 ii. Note, we have a counterexample showing that we
-    cannot solve this whilst using recurrence property and boundedness rather than ind(uctive) and inc(reasing). The counterexample is the self loop on an element.
-    \item is $\omega$-bounded implied by WN and the following confluence property:
-    $a \to^* n \in NF$, and $a \to b$ then $b \to^* n $. (This is a weaker form of WNFP)
-    \item WN and WCR $\to$ bounded. We reached a dead end trying to show this before. Check github history in the ARS file for iii-lemma
-    if you'd like to see the previous direction.
-  \end{enumerate}
-
-  \subsection*{Questions about Well-foundedness}
-  \begin{enumerate}
-    \item For a given element $x$, is the property of
-    being accessible $\lnot\lnot$-closed? I.E.,
-    Does $x$ being $\lnot\lnot$-accessible imply that $x$ is accessible?
-    (Conjecture: No.)
-
-    \item As a special case, does being weakly (accessible) well-founded imply being $\lnot\lnot$-wellfounded?
-    (Conjecture: No.)
-
-    Also: Same question about inductive notion of well-foundedness.
-
-    \item ($\star$) Given a well-founded relation, does every non-empty subset
-    have a minimal element?
-
-    \emph{Problem.} Need to decide whether, for a given $x \in U$,
-     the set $\{y | Ryx\}$ is empty.
-
-     \item IF every non-empty subset has a minimal element, does this imply
-     either of the weak forms of well-foundedness: $\mathtt{isWFacc-}$ or
-     $\mathtt{isWFind-}$ ?
-
-     \item Does $\mathtt{isWFmin-}$ imply $\mathtt{isWFacc-}$ or $\mathtt{isWFind-}$?
-
-     \emph{Problem.} Need to go from $\lnot (\forall y. R y d \to \phi y)$
-     and $\forall y. R y d \to \lnot \lnot \phi y$ to $\bot$.
-
-     In terms of accessibility, it should suffices to assume accessibility is
-     $\lnot\lnot$-closed, since being related to y is not relevant for that. (?)
-
-     \item Does sequential well-foundedness (no decreasing sequence) imply
-     any of the other notions, e.g., \texttt{WFmin-} ?
-
-     \emph{Note.}  This seems to require the most classical assumptions:
-     $\lnot\lnot$-closure of $\phi$, relativized De Morgan law,
-     Markov's principle, etc.
-     \textsc{Remark.}
-     $\lnot\lnot$-closure of accessibility should solve problems 1 and 4.
-  \end{enumerate}
-  \newpage
-
-\section{Todo}
-
-\subsection{Main themes}
-\begin{enumerate}
-  \item Clean up the implications around recurrence properties:
-  \begin{itemize}
-    \item RP iff cofinality and Boundedness?
-    \item What is the ``recurrent'' generalization of WN?
-    \item What is the ``recurrent'' generalization of SN?
-    \item The role of WCR in the proof of our generalization of Thm. 1.2.3(iii)
-  \end{itemize}
-  \item Complete the ``design'' of the chart(s) with implications?
-  \begin{itemize}
-    \item   Look at Exercise 1.3.22 (Show UN $\to$ UN$^\to$ but not conversely. Show a counterexample to WCR and UN$^\to$ $\to$ UN. Find a counter example to WCR and WN $\to$ Ind)
-  \end{itemize}
-  \item Complete the proof of Theorem 1.2.3
-  \item Address outstanding questions about wellfoundness implications.
-  \begin{itemize}
-    \item WFseq implies WFmin? (Assuming decMin)
-    \item WFacc implies $WFmin_0$? (Assuming decMin)
-    \item DecMin suffices for $SN\to WN$, but what is the optimal \emph{necessary} condition?
-    \item Relationship between these, and De Morgan's laws.
-  \end{itemize}
-  \item Complete the classical properties section
-  \item Complete the guide to the code section
-  \item Miscellaneous
-  \begin{itemize}
-    \item   Make the first argument to "being a normal form" implicit?
-    \item   Define: Inc in report
-    \item   Define: Ind in report
-    \item   Define: $\mathrm{CR}^{\le 1}$ in report
-    \item   More laws about closure operations: Monotonicity, idempotency
-    \item   Tidy up and standardize the notation used in ars.agda and other agda files
-  \end{itemize}
-\end{enumerate}
-
-\subsection{12.23}
-\begin{enumerate}
-  \item Prove isWFseq implies isWFmin1
-\end{enumerate}
-
-\subsection{General todo list}
-\begin{enumerate}
-  \item  Another interesting one?
-$WN^*$: hereditarily $WN$ ($WN$ for the reduction graph starting from a given element $x$).
-Could even consider $SN^*$, $CR^*$ etc.
-\sacomment{Is this what we have already shown
-  in the reduction closure properties? If so we can delete this. If not it should be moved to open questions}
-\end{enumerate}
-
-\apcomment{For a property $P(x)$, let $\down{P}(x) := \forall y. x \thra y \implies P(y)$}
-
-Note that $\down{P} \subseteq P$.
-
-If the converse inclusion holds, we will say that $P$ is \emph{closed under reduction}.
-
-\newpage
-
-\section{Misc. Notes}
-
-\subsection*{November 21}
-\apcomment{These may be addressed by the implications table}
-Four local ``normal form properties'':
-\begin{enumerate}
-  \item $WNFP(a) : \forall n \in NF. (a \tto n) \to \forall b. (a \tto b) \to (b \tto n)$
-    "$a$ all reducts of $a$ reduce to $a$'s normal form, if it exists``
-  \item $NFP(a) : \forall n \in NF. (a \tto n) \to \forall b. (a \thlra b) \to (b \tto n)$
-    "$a$ all converta of $a$ reduce to $a$'s normal form, if it exists``
-  \item $WUN(a) : \forall n m \in NF. (a \tto n) \to (a \tto m) \to n \equiv m$
-    "$a$ is reducible to at most one normal form"
-  \item $UN(a) : \forall n m \in NF. (a \thlra n) \to (a \thlra m) \to n \equiv m$
-    "$a$ is convertible to at most one normal form''
-\end{enumerate}
-
-\subsection*{Additional remarks about Theorem 1.2.3.}
-\begin{itemize}
-
-  \item The goal \texttt{iii-lemma :  $WN(R) \to WCR(R) \to \omega{-}\text{bounded}(R)$}
-  seems either very difficult or impossible.
-
-  \apcomment{This implication should be either proved or refuted.}
-
-  Yet, constructing the bound of a given $R$-increasing sequence is key to the proof of
-  (our interpretation of) Theorem 1.2.3(iii), namely that
-  \[ WN(R) \land WCR(R) \land RP(R) \to SN(R) \tag{iii} \]
-  \item Here is a classical proof of this implication.
-
-  Let $R \subseteq A \times A$, and suppose $R$ satisfies WN, WCR, and RP.
-
-  Suppose $R$ is not SN.  Let $a \in A$ be not SN.  By WN, let $n \in \NF$ be
-  such that $a \to^* n$.  By induction on the length of this reduction, the finite sequence
-  of terms comprising it must contain a final term with the property that
-  it is not SN.  (For $n$ is SN, being a normal form, while $a$ is not.)
-
-  $(\star)$ Let this last non-SN term be denoted $b_0$.
-
-  If each single-step $R$-reduct of $b_0$ is SN (so that $b_0 \to x$ implies $x\in \SN$),
-  then $b_0$ would itself be SN --- which it is not, by how it was chosen.
-
-  Thus there exists a $c_0$ with $b_0 \to c_0$, and $c_0 \notin \SN$.
-
-  So we have $c_0 \from b_0 \to m_0$ for some $m_0 \in \SN$. ($m_0$ is the next term after $b_0$ in the reduction $a \to^* n$.)
-
-  By WCR, there exists another element $d_0 \in A$ with $c_0 \to^* d_0 \from^* m_0$.
-
-  Since $m_0 \in \SN$ and this set of terms is closed under reduction, $d_0 \in \SN$ as well.
-
-  Thus $b_0 \to c_0 \to^* d_0$, with $d_0 \in \SN$, and $c_0 \notin \SN$.
-
-  Again, the reduction $c_0 \to^* d_0$ contains a last term that is not in SN.
-
-  Let this term be denoted by $b_1$, and let the next term in the reduction sequence
-  to $d_0$ be denoted $m_1$.
-
-  Now repeat the above process starting at $(\star)$, incrementing all subscripts by 1.
-
-  This generates an infinite reduction sequence
-
-  \[b_0 \to c_0 \to^* b_1 \to c_1 \to^* b_2 \to \cdots \]
-
-  Note that infinitely many terms in this sequence are one reduction step
-  away from a term in $\SN$.
-
-  Moreover, notice that the normal forms of $m_0$, $d_0$, and $m_1$ are the same
-  and equal to $n$, whence the same is true for $m_1$, $d_1$, and $m_2$, etc.
-
-  It follows that, for infinitely many terms in the sequence
-  (namely, all the terms $b_i$), we have $b_i \to^* n$.
-
-  Thus, all terms in the sequence reduce to $n$ and so $n$ is an $\omega$-bound
-  of the sequence.
-
-  By RP, some term $r$ in the sequence is recurrent.
-
-  Since $r \to^* n$ and $r$ is recurrent, also $n \to^* r$.
-
-  But $n$ is a normal form.  So this sequence is empty and $r=n$.
-
-  But $r$ is a term in an infinite reduction sequence, and reduces to its successor.
-
-  This yields a contradiction.
-
-\end{itemize}
-
-\end{document}
+\label{sec:Well-foundedness}

### 2025-02-11 Relations/Paper/FinalTODO.tex
Added todo file.

\section{TODO}

I thought it would be useful to have a final todo in which we can list missing work or questions for this final report.

\begin{enumerate}
    \item Wording question. I'm trying to avoid stating "reduction" when talking about relations. However, can I still refer to a reduct and make sense? See for example the defintion of WCR.
    \item We have shown SN implies SMseq, can we show SN implies SM?
    \item Need to fill in ACM subject classifications
    \item Need to fill in keywords and phrases
    \item Need to check what other mandatory information is required in the file 
    \item Need to fill in Digital object identifier 
    \item Need to sort out a repository for the code and add it to the supplementary material section. 
    \item FINAL Remove this TODO section from the report 
\end{enumerate}

There will also be work we can do once we have submitted the file. We can jot that down here so we don't forget:

\begin{enumerate}
    \item Tidy up the code (fill in or remove goals. Remove unneeded comments. Make sure still compiles after moving it. Make sure it is consistent).
    \item We should create a good clear section of future work so we can pass this project on to future students.
\end{enumerate}

### 2025-02-12 Relations/Paper/Definitions.tex
definitions rough, macros update

\section{Definitions}
\label{sec:Definitions}

The following definitions are provided to ensure clarity and precision 
in our discussion. When useful, we also include the name and type of
definition as we have implemented it in Agda, allowing the report to guide the code
and vice versa.

\begin{definition}
    An abstract rewrite system (\emph{ARS}) is a structure $\mathcal{A} = (A, R_\alpha)$ where
     $A$ is a set of elements and $R_\alpha$ is a set of binary relations on $A$.
\end{definition}

We denote a relation $R$ (from the set $R_\alpha$) from an element $a \in A$ to an element $b \in A$ as $a\rstep b$.
A multi-step relation is denoted $a \mstep b$.

\begin{definition}
    An element $a \in A$ is \emph{R-weakly confluent} ($WCR_R$) if all single step relations from $a$ can always converge
    via multi-step relations to some common reduct.

    A relation $R$ is \emph{weakly confluent} (AKA weakly Church-Rosser (WCR)) if every $a \in A$ is R-weakly confluent.
\end{definition}

\begin{definition}
    An element $a \in A$ is \emph{R-confluent} ($CR_R$) if all multi-step relations from $a$ can always converge
    via multi-step relations to some common reduct.
    A relation $R$ is \emph{confluent} (AKA Church-Rosser (CR)) if every $a \in A$ is R-confluent.
\end{definition}

\begin{definition}
    \emph An element $a \in A$ is a {normal form} if there exists no relation to any other element in $A$.
\end{definition}

\begin{definition}
    An element $a \in A$ is \emph{$R$-weakly normalizing} ($WN_{R}$)if $a \mstep b$ for some normal form $b \in A$.

    A relation $R$ is weakly normalizing (WN) if every $a \in A$ is $R$- weakly normalizing.
\end{definition}

\begin{definition}
    An element $a \in A$ is \emph{$R$-strongly normalizing} ($SN_R$) if every sequence of relations starting from $a$ is finite.

    A relation $R$ is strongly normalizing (SN) if every
    $a \in A$ is $R$-strongly normalizing.
\end{definition}

The above definition of SN is taken from [TeReSe]. 
When working in Agda, we make use of the alternative definition presented in [TeReSe] ($\leftarrow$ is accessibly well-founded). 
The \ref{sec:Well-foundedness} section clarifies this definition.

\begin{definition}
    An element $a \in A$ has the \emph{$R$-weak normal form property} ($WNFP_{R}$) if $a \mstep b$ and 
    $a \mstep c \implies c \mstep b$, for all $c \in A$ and all normal form $b \in A$.

    A relation $R$ has the \emph{weak normal form property} (WNFP) if every $a \in A$ has the $R$-weak normal form property.    
\end{definition}

\begin{definition}
    The \emph{equivalence relation} of $R$ is the smallest relation $\estep$ that contains $R$ and is reflexive, transitive, and symmetric.
\end{definition}

\begin{definition}
An element $a \in A$ has the \emph{$R$-normal form property} ($NFP_{R}$) if
$a \estep b$  $\implies$
$a \mstep b$, for any normal form $b \in A$.

A relation $R$ has the \emph{normal form property} (NFP) if every $a \in A$ has the $R$-normal form property.
\end{definition}

In ARS-Implications.agda we show the equivalence of WNFP and NFP when applied globally in the function $\mathtt{NP \leftrightarrow WNFP}$.

In the next definition we deonte two elements $a, b \in A$ being equivalent with $a \equiv b$.
\begin{definition}
An element $a \in A$ has the \emph{{R}-unique normal form property} ($UN_{R}$) if
$a \estep b$  $\implies$
$a \equiv b$, for any normal form $b \in A$.

A relation $R$ has the \emph{unique normal form property} ($UN$) if every $a \in A$ has the $R$-unique normal form property.
\end{definition}

\begin{definition}
An element $a \in A$ has the \emph{${R}$-unique normal form property with respect to reduction} ($UN^ \to _{R}$) if
$b \bmstep  \cdot  \mstep c$  $\implies$ $b \equiv c$, for all normal forms $b,c \in A$.

A relation $R$ has the \emph{unique normal form property with respect to reduction} ($UN^\to$) if every $a \in A$ has the
$R$-unique normal form property with respect to reduction.
\end{definition}
In ARS-Implications.agda we show that $UN$ implies $UN\to$ but the inverse implication doesn't hold, as seen 
in counterexample (\sacomment{TODO: put counterexample here when section is complete}).

\begin{definition}
    A \emph{sequence (in $A$)} is a function from the natural numbers to $A$:
    \begin{align*}
      &s : \nat \to A \\
      &s = (s_0,s_1,s_2,\dots)
    \end{align*}
\end{definition}

\begin{definition}
    A sequence is \emph{$R$-increasing} if every term is $R$-related to its preceding term.
\end{definition}

\begin{definition}
    A sequence is \emph{bounded} if there exists an element $a \in A$ to which all elements of the sequence reduce.
\end{definition}

\begin{definition}
    An element $a \in A$ has the \emph{minimal form property} ($MF$) if $a \mstep b \implies b \mstep a$ for all $b \in A$.
\end{definition}

Note that being a normal form is a trivial case of the minimal form property (as we prove in ARS-implications.agda 
function $\mathtt{NF\subseteq MF : \forall {x} \to NF x \to MF x}$).

\begin{definition}
    An element $a \in A$ is \emph{$R$-weakly recurrent} ($WR_{R}$)if $a \mstep b$ for some recurrent element $b \in A$.

    A relation $R$ is weakly recurrent (WR) if every $a \in A$ is $R$-weakly recurrent.
\end{definition}

\begin{definition}
    An element $a \in A$ is \emph{$R$-strongly recurrent} ($SR_R$) if either $a$ itself is recurrent or every element one $R$ step
    from $a$ is also strongly recurrent.

    A relation $R$ is strongly recurrent (SR) if every
    $a \in A$ is $R$-strongly recurrent.
\end{definition}

\begin{definition}
   An element $a \in A$ has the \emph{${R}$-weak minimal form property} ($WMFP_R$) if
   $a \mstep b$ and $a \mstep c$  $\implies$
   $c \mstep b$, for all $c \in A$ and all $b \in A$ with the minimal form property.

   A relation $R$ has the \emph{weak minimal form property} (WMFP) if every $a \in A$ has the $R$-weak minimal form property.
\end{definition}

### 2025-02-12 Relations/Paper/Definitions.tex
update to defns

@@
 \begin{definition}
-    An element $a \in A$ is \emph{$R$-weakly recurrent} ($WR_{R}$)if $a \mstep b$ for some recurrent element $b \in A$.
+    An element $a \in A$ is \emph{$R$-weakly minimal} ($WM_{R}$)if $a \mstep b$ for some minimal form $b \in A$.
 
-    A relation $R$ is weakly recurrent (WR) if every $a \in A$ is $R$-weakly recurrent.
+    A relation $R$ is weakly minimal (WM) if every $a \in A$ is $R$-weakly minimal.
 \end{definition}
@@
 \begin{definition}
-    An element $a \in A$ is \emph{$R$-strongly recurrent} ($SR_R$) if either $a$ itself is recurrent or every element one $R$ step
-    from $a$ is also strongly recurrent.
+    An element $a \in A$ is \emph{$R$-strongly minimal} ($SM_R$) if either $a$ itself is a minimal form or every element one $R$ step
+    from $a$ is also strongly minimal.
 
-    A relation $R$ is strongly recurrent (SR) if every
-    $a \in A$ is $R$-strongly recurrent.
+    A relation $R$ is strongly minimal (SM) if every
+    $a \in A$ is $R$-strongly minimal.
 \end{definition}
@@
 \end{definition}
+
+Definitions to add:
+\begin{enumerate}
+    \item Finite branching
+    \item Any other terms from well foundedness
+    \item The other terms we have for strongly 
+\end{enumerate}

### 2025-02-12 Relations/Paper/Definitions.tex
updates...

@@
 The following definitions are provided to ensure clarity and precision
-in our discussion. When useful, we also include the name and type of
+in our discussion.
+ When useful, we also include the name and type of
 definition as we have implemented it in Agda, allowing the report to guide the code
@@
 
-We denote a relation $R$ (from the set $R_\alpha$) from an element $a \in A$ to an element $b \in A$ as $a\rstep b$.
-A multi-step relation is denoted $a \mstep b$.
+For the rest of this section, let $A$ be a fixed set, and $R$ be a relation on $A$.
+(In the Agda code supplement, this is represented by a type $A : \bset$,
+and a binary type family $R : A \to A \to \bset$.)
 
-\begin{definition}
+\greyout{We denote by $\tilde R$ the relational converse of $R$ ($(x,y) \in \tilde R \iff (y,x) \in R$),
+and by $R;R'$ the relational composition of $R$ and $R'$.}
+
+\begin{notation}
+  The following notions are standard.  For precise definitions,
+  see \texttt{ClosureOperators.agda}.
+  \begin{enumerate}
+    \item $R^r$ denotes the \emph{reflexive closure} of $R$.
+    \item $R^s$ denotes the \emph{symmetric closure} of $R$.
+    \item $R^+$ denotes the \emph{transitive closure} of $R$.
+    \item $R^* = (R^r)^+$ denotes the \emph{reflexive-transitive closure} of $R$.
+    \item $R^= = (R^s)^*$ denotes the \emph{equivalence relation generated by} $R$.
+  \end{enumerate}
+\end{notation}
+
+In the context of abstract rewriting, we will often write $a \rstep_R b$
+in place of $(a,b) \in R$.  Similarly, we will write $a \mstep b$ for $(a,b) \in R^*$,
+$a \bstep b$ for $(b,a) \in R$.  When the relation $R$ is clear from the context,
+we may drop the corresponding subscript.
+
+We first define rewriting-theoretic concepts like confluence and normalization relative to a fixed element of $A$; global versions of these properties are obtained by universal quantification.
+
+\begin{definition}  Let $A$ and $R$ be as above, and let $a \in A$.
+  \begin{description}
+    \item[$a \in \NF_R$] \emph{$a$ is a normal form} if $(a,b) \notin R$ for any $b \in A$.
+    \item[$a \in \WN_R$] \emph{$a$ is weakly normalizing} if $a \mstep b$ for some $b \in \NF_R$.
+    \item[$a \in SN_R$]  \emph{$a$ is $R$-accessible}, see Definition \ref{d:WFacc}.
+  \end{description}
+
     An element $a \in A$ is \emph{R-weakly confluent} ($WCR_R$) if all single step relations from $a$ can always converge
@@
 \begin{definition}
-    \emph An element $a \in A$ is a {normal form} if there exists no relation to any other element in $A$.
+  \label{d:WFacc}
+  An element is \emph{accessible} if ...
 \end{definition}

### 2025-02-14 Relations/Paper/Main.tex
Added todo file.
added authorrunning
ARS paper plan

@@
 {arklesd@appstate.edu}{}{}
+
+\authorrunning{A. Polonsky and S. Arkle}
 
@@
 \input{Well-foundedness.tex}
+\input{FinalTODO.tex}
 
 \end{document}
+
+Plan of the paper:
+
+1. Introduction: 2 pages.
+2. Definitions/setup: 2 pages. [WIP]
+3. Formalization of Chapter 1 Terese, including Newman's Lemma: 2 pages [Still needs to be done]
+- Statements (not proofs!) of key propositions and theorems in Agda code
+4. Implications, hierachies, figures, and counterexamples: 4-5 [draft in report]
+5. Classical principles and well-foundedness: 3 pages
+6. Miscellaneous facts: 1 page
+7. Related and future work: 1 page

### 2025-02-20 Relations/Paper/Formalization.tex
Progress on report

\section{Formalization of Terese}
\label{sec:Formalization}
The original ambition of this project was to formalize the contents of the \emph{abstract reduction 
systems} chapter in Term Rewriting Systems [TeReSe], a standard text in rewriting. 
The motivation for the project was to provide construvtive proofs in Agda 
of the propositions and theorems in the chapter. This in turn provides a foundation for 
future work in programming languages theory.

In order to formalize the chapter we have aimed to provide constructive counterparts to the 
classical proofs found in the text, and to make explicit any classical properties we depend 
on when a constructive proof could not be found. It is from this formalization that our 
original work has emerged. We have gone beyond \terese in fleshing out the interrelationship 
of the properties most interesting from the perspective of programming languages theory (namely 
being confluent and strongly normalizing). 
For some properties we suggest alternatives which are more conducive to a constructive project. 
We look into many notions of well-foundedness and again explore their interrelationship.

This section explains the deviations we took from \terese and lays the groundwork for the original work 
that we have carried out.

\sacomment{Maybe mention where we have stayed true to the book, but I don't think this is key}

Our first deviation from \terese is in defining strong normalization. The book defines 
an element as strongly normalizing if every reduction sequence starting from it is finite. 
We wanted to avoid introducing the notion of finiteness to our definition and so we 
followed the alternative definition given in \terese : a relation is strongly normalizing when its 
converse is well founded. In \terese a particular definition of well-foundedness is given but 
it is one with which we were not satisfied and so we explored different definitions of 
well-foundedness. This exploration is detailed in section \ref{sec:Well-foundedness}.

Another deviation we have taken from \terese relates to the use of the definition of an 
increasing relation (see dfn:\ref{d:inc}). This property was one we found particularly difficult 
to make use of in a constructive setting (for example showing that it along with the properties 
of being WCR and WN implies SN) and so we suggest an alternative property, $\RP$.
(dfn:\ref{d:RP}).

\begin{proposition}
    If $R$ is increasing, then no infinite $R$-increasing sequence is bounded.
\end{proposition}
\begin{proof}
    Let $(a_i) = a_0 \to a_1 \to a_2 \to \cdots$ be an $R$-increasing sequence
    and suppose that $(a_i)$ is bounded.  Let $b$ be the bound, so that $a_i \to b$ for all $i$.

    If $m = |b|$ then we have
    \[ 0 \le |a_0| < |a_1| < |a_2| < \cdots < |a_m| < |b| = m \]
    % \[ m > |a_m| > |a_{m-1}| > \cdots > |a_0| \ge 0 \]
    which is a contradiction, since there are only $m-1$ integers strictly less than $m$.
\end{proof}
It follows that every relation that is increasing in the sense of \terese
vacuously satisfies the RP condition.

\begin{corollary}
    If $R$ is increasing, then $R$ has the recurrence property.
\end{corollary}

We investigated $\RP$ and thought that with $\RPm$ we had a candidate for a weaker definition that 
did not rely on the notion of $\MF$. We were able to proove that this weaker definition is 
in fact an equivalent definition in the following proof in Agda:

\verb|RP-↔RP : R is RP- ↔ R is RP| \footnote{ARS-implications.agda}

Three proofs are given in \terese of Newman's Lemma (Theorem 1.2.1). The first and third of 
these proofs we found to rely on classical principles. The second proof was amenablbe to a 
constructive formalization which we carried out in the function

\verb|NewmansLemma : R isSN → R isWCR → R isCR| \footnote{ARS-NewmansLemma.agda}

We show in section \ref{sec:Implications} that $\SN$ implies $\SM$, and it is from this implication 
that we produce a new generalization of Newman's lemma. Every relation with the properties 
$\SM$ and $\WCR$ has the property of $\CR$. This holds true both locally and globally as we show in:

\verb|LocalNewmansLemmaRecurrent : R isWCR → SM ⊆ CR| \footnote{ARS-NewmansLemma.agda}

and \verb|GlobalNewmansLemmaRecurrent : R isWCR → R isSM → R isCR| \footnote{ARS-NewmansLemma.agda}

The formalization of the proof that $\WCR \land \WN \land \Inc \implies \SN$ proved particularly difficult. 
As already mentioned, we substituted out the property $\Inc$ for the property $\RP$ however 
we found that we still require a classical principle in order for the proof to hold (as can be seen in the type of our proof):
\verb|iii : R isWN → R isWCR → R isRP- → dec (SN) → R isSN| \footnote{ARS-Theorems.agda}
The classical property $\decSN$ is a property that states it is decidable whether a given 
element has the property of being $\SN$. \sacomment{Should say more on this proof.}

In the next section we take a closer look at the properties we found most crucial for termination and confluence, and the interrelationship between them.

### 2025-02-20 Relations/Paper/Implications.tex
Progress on report

\section{Implications}
\label{sec:Implications}

From the perspective of programming language theory, the two properties of abstract rewriting 
systems that are most interesting are $\SN$ and $\CR$. The following hierarchies 
show chains of implications starting from these properties.

\begin{center}

    \begin{tikzpicture}[auto,
      arrowstyle/.style={->, line width=1pt, >={Latex[length=3mm, width=2mm]}, shorten >=2pt}]
      % A box style
      \tikzstyle{boxnode} = [draw, rectangle, text centered]

      % Place the nodes vertically (top to bottom)
      \node (Confluent) [boxnode] at (-4,0) {$\CR$};
      \node (RP)        [boxnode, right=.5cm of Confluent] {$\WMFP$};
      \node (WN)        [boxnode, right=.5cm of RP] {$\WNFP$};
      \node (UN)        [boxnode, right=.5cm of WN] {$\UNto$};

      % Draw arrows downwards
      \draw[arrowstyle] (Confluent) -- (RP);
      \draw[arrowstyle] (RP) -- (WN);
      \draw[arrowstyle] (WN) -- (UN);

        % Define the nodes
        \node (SN) [boxnode] at (4,0) {$\SN$};
        \node (WN) [boxnode, above right=0.5cm and 0.5cm of SN] {$\WN$};
        \node (SR) [boxnode, below right=0.5cm and 0.5cm of SN] {$\SM$};
        \node (WR) [boxnode, right of=SN, xshift=2cm] {$\WM$};

        % Draw the arrows to form a diamond
        \draw [arrowstyle] (SN) -- (WN);
        \draw [arrowstyle] (SN) -- (SR);
        \draw [arrowstyle] (WN) -- (WR);
        \draw [arrowstyle] (SR) -- (WR);
      \end{tikzpicture}
\end{center}

The classical property of being minimally decidable is required to complete the implcation 
from $\SN$ to $\WN$, as can be seen in our formalization

\verb|SNdec→WN : (~R R) isMinDec → SN ⊆ WN| \footnote{ARS-Implications.agda}

\sacomment{Are we going to define this property here or elsewhere?}

The isMinDec property states that all elements either have a relation to some other element, or 
there is no other element to which they have a relation. If the element relates to no other element then it is terminating 
and so trivially $\WN$. If the element does relate to some other element $y \in A$, then we recursively apply our claim to 
$y$ and because we know that we have the property of $\SN$ we must eventually reach a terminating element.

Similarly, the property of being minimally decidable is required in order to show that $\SM$ implies $\WM$.

The following tables show which combination of these properties implies a property higher in the hierarchy. Where a combination 
does not imply a higher property a explanatory counterexample is given. The counterexamples referenced are in section \ref{sec:Counterexamples}.

The first table explores where the properties hold locally, the second explores where the properties hold globally, and the third 
table is global and includes the $\WCR$ property. An property being red indicates that classical assumptions are required for the implication 
to hold.

\sacomment{UPDATE COUNTEREXAMPLES WHEN CE SECTION FINISHED}
\begin{table}[h!]
    \centering
    \caption{Local implications}
    \begin{tabular}{|>{\columncolor{gray!30}}l|c|c|c|c|c|}
    \hline
    \rowcolor{gray!30}     & $\WM$         & $\WN$         & $\SM$             & $\SMandWN$        & $\SN$ \\
    \hline
    $\UNto$ &  CE-, CE-     & CE, CE-       & CE , CE-          & CE, CE            & \red{$\CR$} , $\SN$ \\
    \hline
    $\WNFP$ & CE-, CE-      & $\CR$, CE-    & CE , CE-          & $\CR$, $\SN$      & \red{$\CR$} , $\SN$ \\
    \hline
    $\WMFP$ & $\CR$ , CE-    & $\CR$, CE-    & \red{$\CR$} , CE- & $\CR$, $\SN$      & \red{$\CR$} , $\SN$ \\
    \hline
    $\CR$   & $\CR$, CE-     & $\CR$, CE-     & $\CR$, CE-        & $\CR$, $\SN$     & $\CR$ , $\SN$ \\
    \hline

    \end{tabular}
\end{table}

\begin{table}[h!]
    \centering
    \caption{Global implications}
    \begin{tabular}{|l|c|c|c|c|c|}
    \hline
            & $\WM$         & $\WN$         & $\SM$             & $\SMandWN$        & $\SN$ \\
    \hline
    $\UNto$ &  CE-, CE-     & $\CR$, CE-    & CE , CE-          & $\CR$, $\SN$      & \red{$\CR$} , $\SN$ \\
    \hline
    $\WNFP$ & CE-, CE-      & $\CR$, CE-    & CE , CE-          & $\CR$, $\SN$      & \red{$\CR$} , $\SN$ \\
    \hline
    $\WMFP$ & $\CR$ , CE    & $\CR$, CE-    & \red{$\CR$} , CE- & $\CR$, $\SN$      & \red{$\CR$} , $\SN$ \\
    \hline
    $\CR$   & $\CR$, CE     & $\CR$, CE     & $\CR$, CE-        & $\CR$, $\SN$      & $\CR$ , $\SN$ \\
    \hline

    \end{tabular}
\end{table}

\begin{table}[h!]
    \centering
    \caption{Global implications with global $\WCR$}
    \begin{tabular}{|l|c|c|c|c|c|}
    \hline
            & $\WM$         & $\WN$         & $\SM$             & $\SMandWN$        & $\SN$ \\
    \hline
    $\UNto$ &  CE-, CE-     & $\CR$, CE-    &  $\CR$ , CE-      & $\CR$, $\SN$      &  $\CR$ , $\SN$ \\
    \hline
    $\WNFP$ & CE-, CE-      & $\CR$, CE-    &  $\CR$ , CE-      & $\CR$, $\SN$      &  $\CR$ , $\SN$ \\
    \hline
    $\WMFP$ & $\CR$ , CE    & $\CR$, CE-    &  $\CR$ , CE-      & $\CR$, $\SN$      &  $\CR$ , $\SN$ \\
    \hline
    $\CR$   & $\CR$, CE     & $\CR$, CE     &  $\CR$, CE-       & $\CR$, $\SN$      & $\CR$ , $\SN$ \\
    \hline

    \end{tabular}
\end{table}

\sacomment{Need to update the tables with appropriate symbols for global and local. Colour for first row and column?}

The tables show that there are two changes when moving from properties holding locally and globally. 
Globally $\WN \land \UNto \implies \CR$ whereas it does not locally.

### 2025-02-21 Relations/Paper/Implications.tex
Update from WNFP to NP etc
WN and SM gets SN

@@
       % A box style
-      \tikzstyle{boxnode} = [draw, rectangle, text centered]
+      \tikzstyle{boxnode} = [draw, rectangle, text centered,minimum width=1.2cm, inner sep=3pt]
 
@@
       \node (Confluent) [boxnode] at (-4,0) {$\CR$};
-      \node (RP)        [boxnode, right=.5cm of Confluent] {$\WMFP$};
-      \node (WN)        [boxnode, right=.5cm of RP] {$\WNFP$};
+      \node (RP)        [boxnode, right=.5cm of Confluent] {$\MP$};
+      \node (WN)        [boxnode, right=.5cm of RP] {$\NP$};
       \node (UN)        [boxnode, right=.5cm of WN] {$\UNto$};
@@
         \node (SR) [boxnode, below right=0.5cm and 0.5cm of SN] {$\SM$};
-        \node (WR) [boxnode, right of=SN, xshift=2cm] {$\WM$};
+        \node (WR) [boxnode, below right=0.5cm and 0.5cm of WN] {$\WM$};
 
@@
 
-\verb|SNdec→WN : (~R R) isMinDec → SN ⊆ WN| \footnote{ARS-Implications.agda}
+\verb|SNdec→WN : (~R R) isMinDec → SN ⊆ WN| \footnotemark[1]
 
@@
 The following tables show which combination of these properties implies a property higher in the hierarchy. Where a combination 
-does not imply a higher property a explanatory counterexample is given. The counterexamples referenced are in section \ref{sec:Counterexamples}.
+does not imply a higher property an explanatory counterexample is given. The counterexamples referenced are in section \ref{sec:Counterexamples}.
 
-The first table explores where the properties hold locally, the second explores where the properties hold globally, and the third 
-table is global and includes the $\WCR$ property. An property being red indicates that classical assumptions are required for the implication 
-to hold.
+The first table explores where the properties hold locally, the second explores where the properties hold globally. The proofs that the 
+following implications hold are primarily found in \texttt{ARS-implications.agda} unless they have been proven as part of the formalization 
+of \terese, in which case they will be found in either \texttt{ARS-thoerems.agda} or \texttt{ARS-NewmansLemma.agda}.
 
 \sacomment{UPDATE COUNTEREXAMPLES WHEN CE SECTION FINISHED}
+\renewcommand*{\thefootnote}{\fnsymbol{footnote}}
 \begin{table}[h!]
@@
     \hline
-    $\UNto$ &  CE-, CE-     & CE, CE-       & CE , CE-          & CE, CE            & \red{$\CR$} , $\SN$ \\
+    $\UNto$ &  CE-, CE-     & CE, CE-       & $\CR$\footnotemark[1] , CE-          & $\CR$\footnotemark[1], CE            & $\CR$\footnotemark[2] , $\SN$ \\
     \hline
-    $\WNFP$ & CE-, CE-      & $\CR$, CE-    & CE , CE-          & $\CR$, $\SN$      & \red{$\CR$} , $\SN$ \\
+    $\NP$ & CE-, CE-      & $\CR$, CE-    & $\CR$\footnotemark[1] , CE-          & $\CR$, $\SN$      & $\CR$\footnotemark[2] , $\SN$ \\
     \hline
-    $\WMFP$ & $\CR$ , CE-    & $\CR$, CE-    & \red{$\CR$} , CE- & $\CR$, $\SN$      & \red{$\CR$} , $\SN$ \\
+    $\MP$ & $\CR$ , CE-    & $\CR$, CE-    & $\CR$\footnotemark[2] , CE- & $\CR$, $\SN$      & $\CR$\footnotemark[2] , $\SN$ \\
     \hline
@@
 \end{table}
-
 \begin{table}[h!]
@@
     \caption{Global implications}
-    \begin{tabular}{|l|c|c|c|c|c|}
+    \begin{tabular}{|>{\columncolor{gray!30}}l|c|c|c|c|c|}
     \hline
-            & $\WM$         & $\WN$         & $\SM$             & $\SMandWN$        & $\SN$ \\
+    \rowcolor{gray!30}     & $\WM$         & $\WN$         & $\SM$             & $\SMandWN$        & $\SN$ \\
     \hline
-    $\UNto$ &  CE-, CE-     & $\CR$, CE-    & CE , CE-          & $\CR$, $\SN$      & \red{$\CR$} , $\SN$ \\
+    $\UNto$ &  CE-, CE-     & $\CR$, CE-    & $\CR$\footnotemark[1] , CE-          & $\CR$, $\SN$      & $\CR$\footnotemark[2] , $\SN$ \\
     \hline
-    $\WNFP$ & CE-, CE-      & $\CR$, CE-    & CE , CE-          & $\CR$, $\SN$      & \red{$\CR$} , $\SN$ \\
+    $\NP$ & CE-, CE-      & $\CR$, CE-    & $\CR$\footnotemark[1] , CE-          & $\CR$, $\SN$      & $\CR$\footnotemark[2] , $\SN$ \\
     \hline
-    $\WMFP$ & $\CR$ , CE    & $\CR$, CE-    & \red{$\CR$} , CE- & $\CR$, $\SN$      & \red{$\CR$} , $\SN$ \\
+    $\MP$ & $\CR$ , CE    & $\CR$, CE-    & $\CR$\footnotemark[2] , CE- & $\CR$, $\SN$      & $\CR$\footnotemark[2] , $\SN$ \\
     \hline
@@
 \end{table}
-
-\begin{table}[h!]
-    \centering
-    \caption{Global implications with global $\WCR$}
-    \begin{tabular}{|l|c|c|c|c|c|}
-    \hline
-            & $\WM$         & $\WN$         & $\SM$             & $\SMandWN$        & $\SN$ \\
-    \hline
-    $\UNto$ &  CE-, CE-     & $\CR$, CE-    &  $\CR$ , CE-      & $\CR$, $\SN$      &  $\CR$ , $\SN$ \\
-    \hline
-    $\WNFP$ & CE-, CE-      & $\CR$, CE-    &  $\CR$ , CE-      & $\CR$, $\SN$      &  $\CR$ , $\SN$ \\
-    \hline
-    $\WMFP$ & $\CR$ , CE    & $\CR$, CE-    &  $\CR$ , CE-      & $\CR$, $\SN$      &  $\CR$ , $\SN$ \\
-    \hline
-    $\CR$   & $\CR$, CE     & $\CR$, CE     &  $\CR$, CE-       & $\CR$, $\SN$      & $\CR$ , $\SN$ \\
-    \hline
-
-    \end{tabular}
-\end{table}
+\footnotetext[1]{This implication also requires global $\WCR$.}
+\footnotetext[2]{This implication also requires either global $\WCR$ or the classical property required to go from 
+$\SN \to \WN$ or $\SM \to \WM$.}
+\renewcommand*{\thefootnote}{\arabic{footnote}}
 
@@
 
-The tables show that there are two changes when moving from properties holding locally and globally. 
-Globally $\WN \land \UNto \implies \CR$ whereas it does not locally.
+The tables show that there are two changes when moving from properties holding locally to globally. 
+Globally $\WN \land \UNto \implies \CR$ holds whereas it does not locally. Similarly, $\SM \land \WN \implies \SN$ holds 
+globally but not locally.
+
+Theorem 1.2.2 ii in \terese is the claim that $\WN \land \UN \implies \CR$ holds, and we formalize this in
+
+\verb|ii : R isWN × R isUN → R isCR| \footnotemark[3]
+
+We have modestly generalized this theorem by showing that $\WN \land \UNto \implies \CR$ holds (and indeed this is the basis for our proof of the theorem). 
+Counterexample \sacomment{REF HERE} shows why this implication cannot hold when the properties are only local. Our proof is in the function:
+
+\verb|UN→∧WN→CR : R isUN→ → R isWN → R isCR| \footnotemark[1]
+
+To show that $\SM \land \WN \implies \SN$ we built on our proof that locally $\SM \land \WN \land \NP \implies \SN$. If $\WN$ applies 
+globally then our proof no longer requires the property $\NP$. This progression of proofs can be seen in the functions:
+
+\verb|WN∧NP∧SM→SN : ∀ {x} → WN x → NP x → SM x → SN x|
+
+\verb|isWN∧SM→SN : R isWN → ∀ {x} → SM x → SN x|
+
+\verb|isWN∧isSM→isSN : R isWN → R isSM → R isSN| \footnotemark[1]

### 2025-02-21 Relations/Paper/Counterexamples.tex
Start on CE

@@
 \label{sec:Counterexamples}
+
+% Setting up the ce counter 
+\newcounter{CEcounter}
+\renewcommand{\theCEcounter}{\arabic{CEcounter}}
+
+\newenvironment{counterexample}[1][]{%
+    \refstepcounter{CEcounter} % Increment the counter
+    \noindent \scriptsize\textbf{{Counterexample \theCEcounter.}} #1\par
+}
+
+This section collects the useful counterexamples we have encountered whilst undertaking this project. 
+The counterexamples rule out certain implications between properties.
+
+\begin{center}
+\begin{tabular}{ccc}  % Three columns per row
+    % First Counterexample
+    \begin{minipage}{0.3\textwidth}
+        \centering
+        \begin{counterexample}\label{CE:1}
+        \begin{tikzcd}[row sep=small, column sep=small]
+            a & b \arrow[l] \arrow[r, bend left] & c \arrow[l, bend left] \arrow[r] & d
+        \end{tikzcd} \\
+    \end{counterexample}
+    \end{minipage}
+    &
+    % Second Counterexample
+    \begin{minipage}{0.3\textwidth}
+        \centering
+        \begin{counterexample}\label{CE:2}
+        \begin{tikzcd}[row sep=small, column sep=small]
+            a & b \arrow[l] \arrow[r, bend left] & c \arrow[l, bend left] \arrow[r] & d \arrow[loop right]
+        \end{tikzcd} \\
+        \end{counterexample}
+    \end{minipage}
+    &
+    % Third Counterexample
+    \begin{minipage}{0.3\textwidth}
+        \centering
+        \begin{counterexample}\label{CE:e}
+        \begin{tikzcd}[row sep=small, column sep=small]
+            a \arrow[loop left] & b \arrow[l] \arrow[r, bend left] & c \arrow[l, bend left] \arrow[r] & d \arrow[loop right]
+        \end{tikzcd} \\
+    \end{counterexample}
+    \end{minipage}
+    \\  % New row
+    \\
+
+    % Fourth Counterexample
+    \begin{minipage}{0.3\textwidth}
+        \centering
+        \begin{counterexample}\label{CE:4}
+        \begin{tikzcd}[row sep=small, column sep=small]
+            n \in NF & a \arrow[l] \arrow[r] & b \arrow[r, bend left] & c \arrow[l, bend left]
+        \end{tikzcd} \\
+    \end{counterexample}
+    \end{minipage}
+    &
+    % Fifth Counterexample
+    \begin{minipage}{0.3\textwidth}
+        \centering
+        \begin{counterexample}\label{CE:5}
+        \begin{tikzcd}[row sep=small, column sep=small]
+            n \in NF & a \arrow[l, two heads] \arrow[r, two heads] & b \arrow[r, bend left] & c \arrow[l, bend left]
+        \end{tikzcd} \\
+    \end{counterexample}
+    \end{minipage}
+    &
+    % Sixth Counterexample
+    \begin{minipage}{0.3\textwidth}
+        \centering
+        \begin{counterexample}\label{CE:6}
+        \begin{tikzcd}[row sep=small, column sep=small]
+            a \arrow[r, bend left] & b \arrow[l, bend left]
+        \end{tikzcd} \\
+        \end{counterexample}
+    \end{minipage}
+    \\ % New row
+    \\
+    \begin{minipage}{0.3\textwidth}
+        \centering
+        \begin{counterexample}\label{CE:7}
+        \begin{tikzcd}[row sep=small, column sep=small]
+            f_0 \arrow[r] \arrow[dr] & f_1 \arrow[r] \arrow[d] & \dots \arrow[dl] \\
+            & n \in NF 
+        \end{tikzcd} \\
+        \end{counterexample}
+    \end{minipage}
+    &
+    \begin{minipage}{0.3\textwidth}
+        \centering
+        \begin{counterexample}\label{CE:8}
+        \begin{tikzcd}[row sep=small, column sep=small]
+            f_0 \arrow[r] \arrow[d] & f_1 \arrow[r] \arrow[d] & f_2 \arrow[r] \arrow[d] & \dots \arrow[d] \\
+            n_0  & n_1  & n_2 & \dots 
+        \end{tikzcd} \\
+        \end{counterexample}
+    \end{minipage}
+
+    &
+    \begin{minipage}{0.3\textwidth}
+        \centering
+        \begin{counterexample}\label{CE:9}
+        \begin{tikzcd}[row sep=small, column sep=small]
+            a \arrow[r, bend left] & b \arrow[l, bend left]
+        \end{tikzcd} \\
+        \end{counterexample}
+    \end{minipage}
+
+\end{tabular}
+\end{center}

### 2025-02-22 Relations/notes.tex
AP notes

--- 2024-11-14 Relations/notes.tex
@@
 
-\input{macros}
+\usepackage{xcolor}
+
+\newcommand{\hired}[1]{{\color{red}{#1}}}
 
@@
 
-This document aims to bring together the various notes from report, rewriting qs, and counterexamples.
+\section*{Notes}
 
-\section{Todo}
-\subsection*{Week starting 11th November}
-\begin{enumerate}
-  \item In the report, give a classical proof that the $Inc$ Property
-  implies that no $R$-increasing sequence is bounded.
-
-  Conclude that every relation satisfying $Inc$ also satisfies $RP$.
-
-  Therefore, the proof of Theorem 1.2.3(iii) using $RP$ instead of $Inc$
-  is generalizing the claim of the theorem (as stated in [TeReSe]).
-  \item Complete the proof in ARS.agda of Theorem 1.2.3.(iii)
-  \item Organize notes.tex into three sections: TODO, Open Qs, What we've proved. Make sure all notes from the other
-  tex files are sorted here correctly.
-  \item Tidy up and standardize the notation used in ars.agda and other agda files 
-  \item Carry on working through report.tex.  
-  \item 
-\end{enumerate}
-\subsection*{General todo}
-\begin{enumerate}
-
-  \item  Make the first argument to "being a normal form" implicit?
-  \item Define WNFP to be:
-  \[\forall a b c \to b \in NF \to a R^* b \to a R^* c \to c R^* b \]
-  \item Does WNFP and WN imply CR?  Looks like it!
-  \item  Another interesting one? $WN^*$: hereditarily $WN$ ($WN$ for the reduction graph starting from a given element $x$.)
-
-  Could even consider $SN^*$, $CR^*$ etc.
-  \item Define: Inc
-  \item Define: Ind
-  \item Define: $\mathrm{CR}^{\le 1}$
-  \item capture all classical properties/asssumptions we might want to use and justify their use. 
-  \item Principles we are considering
+\section{Plan}
 \begin{itemize}
-    \item Decidability of equality on $A$
-    \item Decidability of the relation $R$
-    \item When relevant, decidability of the given precicate $P$
-    \item Not-not-closure of being accessible
-    \item Not-not-closure of $R$
-    \item Not-not-closure of $P$
-    \item Decidability of whether a given element is an $R$-normal form
-    \item When relevant, local/element-wise versions of the above
-    \item Markov's principle:
-    \begin{itemize}
-      \item In $wfMin_0 \to wfSeq$.
-
-      Given a sequence $s : \nat \to A$, let $E(a) = \exists n \in \nat. s n \equiv a$.
-
-      Need: $\forall a. \lnot\lnot E(a) \to E(a)$, i.e.,
-      \[\lnot\lnot \big(\exists n \in \nat. s n \equiv a\big)
-            \to \big(\exists n \in \nat. s n \equiv a\big)\]
-
-    \end{itemize}
-  \end{itemize}
-  \item Write a guide to the code
-  \item More laws about closure operations: Monotonicity, idempotency
-
-\end{enumerate}
-\newpage
-\section{Open Questions }
-\begin{enumerate}
-  \item
-     \[ WNg \land UN \to CRelem :
-     \forall (R : \mathscr{R} A) \to WN R \to \forall x \to is R -UN x \to is R -CR x \]
-     \item $WN R \to UN R \to \omega-bdd R \to SN R$ (1.2.3.ii-)
-      \item Finish formulating the ``compactness property".  Two candidates:
-       \item ``Every cocone for a given infinite sequence loops back to some point in the sequence"
-       \item ``If an $R^*$-sequence has a cocone then it's constant after some point on.''
-       \item is $\omega$-bounded implied by WN and the following confluence property:
-       $a \to^* n \in NF$, and $a \to b$ then $b \to^* n $.
-  \item (2024.10.10) Is being $R$-WN inductive?
-  \item (2024.10.10) Does $R$ being finitely branching imply
-   that, for an inductive $\phi$, if $\lnot \phi(x)$ then
-   $\exists y. Rxy \land \lnot \phi(y)$?
-
-  \item If WCR holds, is WN$\downarrow\subseteq$WN ?
-  \item Same question for next bullet in 2.2
-  \item Same for bullet 3 in 2.2 (but pointwise!)
-  \item \item Look at restricting WFmin to $\lnot\lnot$-closed predicates
-  \item Status of important hypotheses:
-    \begin{itemize}
-      \item Deciding whether a given element $x$ reduces to a given element $y$
-      (Is $R$ itself decidable?)
-      \item Deciding whether a given element $x$ reduces to some element $y$
-      (Is being an $R$-normal form decidable?)
-
-      {\textcolor{red}{This is needed to show that SN $\Rightarrow$ WN.}}
-
-      \item If a given element $x$ is \emph{not} a normal form,
-      exhibiting some element $y$ that it reduces to.
-      (This is related to DeMorgan/Markov/etc. properties that came up in WF file.)
-
-      \item Does UN-lemma \emph{require} the decidability assumption?
-    \end{itemize}
-  \item META questions: Which of the ARS theorems can be made ``local/pointwise'',
-  for example,
-  \begin{itemize}
-    \item NL+: $WCR(R) \land SN(x) \to CR(x)$?  (Yes?)
-    \item NL++: $WCR(x) \land SN(x) \to CR(x)$? (No.)
-  \end{itemize}
-  \item Can "sequential" properties like RP, RP-, isWFseq, isWFseq-, $\omega$-bounded, etc.,
-    be related to the cofinality property.
-    \item What happens if properties involving sequences are reformulated for
-  $R^r$? (Cannot decide whether the given sequence is finite or infinite.)
-  \item Knaster-Tarski Lemma: Most general form? Alternative formulations?
-  \item Knaster--Tarski in a well-founded setting: what additional
-  hypotheses are necessary?
-\end{enumerate}
-\subsection*{well-foundedness}
-\begin{enumerate}
-  \item For a given element $x$, is the property of
-  being accessible $\lnot\lnot$-closed? I.E.,
-  Does $x$ being $\lnot\lnot$-accessible imply that $x$ is accessible?
-  (Conjecture: No.)
-
-  \item As a special case, does being weakly (accessible) well-founded imply being $\lnot\lnot$-wellfounded?
-  (Conjecture: No.)
-
-  Also: Same question about inductive notion of well-foundedness.
-
-  \item ($\star$) Given a well-founded relation, does every non-empty subset
-  have a minimal element?
-
-  \emph{Problem.} Need to decide whether, for a given $x \in U$,
-   the set $\{y | Ryx\}$ is empty.
-
-   \item IF every non-empty subset has a minimal element, does this imply
-   either of the weak forms of well-foundedness: $\mathtt{isWFacc-}$ or
-   $\mathtt{isWFind-}$ ?
-
-   \item Does $\mathtt{isWFmin-}$ imply $\mathtt{isWFacc-}$ or $\mathtt{isWFind-}$?
-
-   \emph{Problem.} Need to go from $\lnot (\forall y. R y d \to \phi y)$
-   and $\forall y. R y d \to \lnot \lnot \phi y$ to $\bot$.
-
-   In terms of accessibility, it should suffices to assume accessibility is
-   $\lnot\lnot$-closed, since being related to y is not relevant for that. (?)
-
-   \item Does sequential well-foundedness (no decreasing sequence) imply
-   any of the other notions, e.g., \texttt{WFmin-} ?
-
-   \emph{Note.}  This seems to require the most classical assumptions:
-   $\lnot\lnot$-closure of $\phi$, relativized De Morgan law,
-   Markov's principle, etc.
-   \textsc{Remark.}
-   $\lnot\lnot$-closure of accessibility should solve problems 1 and 4.
-
-\end{enumerate}
-
-\newpage 
-\section{What has been proven}
-\begin{itemize}
-  \item \sacomment{List all the constructive proofs we've put together!}
-  \item SN implies bounded
-  \item RP- implies RP
-  \item The infinite haircomb refutes $WN \land RP \to \omega$-bounded.  But it is not WCR.
-  \item We have formalized proposition 1.1.9, 1.1.10, 1.1.11 from [TeReSe]. 
-  \item We have a proof for Theorem 1.2.1 (Newlman's Lemma) (though we have just one proof of multiple possible proofs).
-  \item We have a proof for all parts of Theorem 1.2.2
-  \item We have a proof for Theorem 1.2.3 i, iv. 
-  \item Reduction closure properties for SN, NF, UN, recurrent property.
-
-  So, does $WN, RP, WCR$ imply $\omega$-bounded?
-  Answer: yes, that is what we have proved classically.
+  \item Start by discussing motivation
+  \item Then contributions
+  \item Plan of the paper
+  \item At some point, there should be like a summary of what's been done and what are some interesting discoveries
 \end{itemize}
 
-\newpage
+In the conclusion, we should recap the main takeaways from each piece.
+The key role of finitely branching condition in making many results effective.
+That it also collapses many well-foundedness properties.
+The ``sufficiency frontier'' for completeness (termination and confluence).
+
+Also discuss open problems, unprovable implications, etc.
+Maybe mention the Kleene tree idea, or at least include the reference to the Bezem-Coquand paper.
+
+\section{Motivation}
+
+The standard presentation in Terese makes liberal use of classical logic.
+Should stress effectivity of type-theoretic formalization.
+\section{Contributions}
+
+\begin{itemize}
+  \item Formalization of ``elementary ARS theory'' as presented in
+  Chapter 1 of [TeReSe].
+  \item An ontology of termination and confluence properties, and a detailed analysis of logical relations between them.
+  \item Defining several new ARS concepts that serve to streamline and generalize a number of relationships.
+  \item With the above, obtain marginal improvements to classical confluence and termination criteria
+  \item Collecting implications between constructive notions of well-foundedness
+\end{itemize}
+
+\section{Formalization principles}
+
+\begin{itemize}
+  \item No function extensionality
+  \item No univalence, uniqueness of identity proofs, cubical, or any other
+  assumptions related to equality
+  \item Minimize the use of classical logic; every place where it was necessary,
+  make decidability hypotheses explicit in every place where it could not be avoided.
+  \item The vast majority of results are completely constructive and therefore,
+  they compute.
+  \item The goal is to have the results of basic abstract rewriting
+  formalized in a canonical way, so that they can be used in building
+  libraries of formalized programming language theory
+  \item Since this application ....
+  \item In other words, we wanted to stay as close as possible to the spirit of type theory based on the Curry--Howard isomorphism, so that in every explicitly given situation, our proofs will compute.
+\end{itemize}
+
+One big item in this development was studying various incaranations of the concept of well-foundedness in constructive context.
+(Strong normalization is well-foundedness of the converse relation.)
+The ``standard'' constructive definition does not even allow one to show that SN implies WN, see Example \ref{ex:undec}.
+We therefore looked at a number of variations of this notion, their classical counterparts all being logically equivalent.
+This gave rise to a rich set of concepts, see Figure \ref{f:wf}.
+
+Along the way, we found marginal improvements to a number of standard theorems.
+For example, the termination assumption of the famous Newman's Lemma can be slightly weakened....
+
+There are also large classes of ARSs where some needed classical principles are simply valid.
+For example, finitely branching relations encompass most ARSs resulting from first-order term rewrite systems.
+For such relations, the implication SN to WN requires nothing else beyond plain decidability of
+the relation itself $Rxy \lor \lnot Rxy$.
+
+The main conclusion of our work is that most of basic ARS results can be made completely effective, at least for the most basic instance of first-order TRSs.
+(This also includes the usual lambda calculus.)
+
+For more exotic rewrite systems, like $\lambda \bot$ or coinductive rewriting,
+these decidability assumptions no longer hold, and the utility of ARS results diminishes proportionally.
+
+Finally, our Agda implementation provides a standard ``entry point'' for using these results in formal language development.
 
 \end{document}
+
+META
+This is a report about the work that was completed.
+Putting ARS on a constructive foundation -- stress that.

### 2025-02-22 Relations/Paper/Definitions.tex

@@
 
+\begin{definition}\label{d:RP}
+    A relation $R$ has the \emph{recurrence property} (RP) if every bounded, increasing sequence 
+    has an element $a \in MF$.
+\end{definition}
+
+\begin{definition}\label{d:RP-}
+    A relation $R$ has the \emph{weak recurrence property} (RP-) if for every increasing 
+    sequence with bound $a$, there is an element $i$ of the sequence such that 
+    $a \mstep f(i)$.
+\end{definition}
+
 \begin{definition}
@@
 \end{definition}
+\begin{definition}
+    \label{d:inc}
+    A relation $R \sse A \times A$ is called \emph{increasing} if there
+    exists a ``size function'' $|-| : A \to \nat$ satisfying, for all $x, y \in A$,
+    \[ Rxy \to |x| < |y| \]
+\end{definition}
 

### 2025-02-22 Relations/Paper/Introduction.tex
intro first draft

@@
 
-The text for the introduction will go here.
+% \section{Plan}
+% \begin{itemize}
+%   \item Start by discussing motivation
+%   \item Then contributions
+%   \item Plan of the paper
+%   \item At some point, there should be like a summary of what's been done and what are some interesting discoveries
+% \end{itemize}
+%
+
+We present a formalization of the basic Abstract Rewriting Systems (ARS) theory in the Agda proof assistant.
+This is part of a larger effort to develop a library of formalized programming language theory (PL)
+at Appalachian State University.
+Since Term Rewriting Systems (TRS) play a foundational role in programming languages,
+while ARS encompass the basic facts about rewriting relations in general,
+establishing these facts is part of the necessary infrastructure required to
+pursue the broader project.  The present contribution can therefore be seen as
+``bootstrapping'' Appstate's new formalized PL repository.
+
+This broader goal also drives the main design choices in our approach.
+Since rewriting theory is concerned with a fine-grained analysis of computation,
+the most natural vehicle for formalizing it is type theory based on the
+Curry--Howard isomorphism, which Agda implements.  Proofs in this language
+are automatically effective, and implicitly carry the code implementing the
+transformations from the hypotheses to the conclusion.  For example,
+a proof that a given TRS is terminating automatically renders a function that
+computes a normal form of any term in its domain.
+
+Staying within this paradigm requires the proofs to be constructive.
+Moreover, it requires us to avoid any axioms or postulates, such as function
+extensionality, uniqueness of identity proofs, univalence, etc.
+While most of ARS results are indeed constructive, standard presentations,
+ including \hired{[Terese]}, make liberal use of classical logic.
+Our paper can thus be read as a thoroughly constructive
+development of elementary ARS theory.
+
+Before we proceed further, let us consider two formalization scenarios where
+our contribution can be useful.
+
+\subsection*{Example 1. Formalization of typed lambda calculus.}
+
+Suppose one is formalizing the standard metatheory of
+a typed lambda calculus.  To show confluence, one possible approach is to
+first establish the Church--Rosser theorem for the untyped lambda calculus,
+then invoke the Subject Reduction Theorem.
+However, suppose one has already independently verified Strong Normalization.
+Invoking Newman's lemma, one can then conclude confluence from the weak
+diamond property, which is generally a much simpler fact to prove.
+
+\subsection*{Example 2. Quotients of types.}
+Suppose one wishes to construct the initial model of an algebraic theory.
+The classical definition involves the quotient of a free algebra by
+the equivalence relation induced by the theory.
+The quotient is problematic operation in type theory.
+While there are various solutions, such as Higher Inductive Types,
+or Quotient Inductive--Inductive Types, these require one to extend the
+basic type theory with new constructs.
+
+However, if the algebraic theory in question admits a convergent presentation,
+by a confluent and terminating relation $R : A \to A \to Set$, one can define the type of
+$R$-normal forms as
+\[  (\Sigma n : A) (\Pi x : A) \lnot P n x \]
+In many applications, this type can substitute the true quotient satisfactorily.
+(In univalent or cubical type theories, one can moreover show this type to be
+a set, provided the domain $A$ is.)
+
+As these examples illustrate, a fully effective implementation of basic ARS results
+can be very helpful in many settings arising in programming language theory.
+
+\subsection{Contributions}
+Our contributions
+\begin{itemize}
+  \item Formalization of ``elementary ARS theory'' as presented in
+  Chapter 1 of [TeReSe].
+  \item An ontology of termination and confluence properties, and a detailed analysis of logical relations between them.
+  \item Defining several new ARS concepts that serve to streamline and generalize a number of relationships.
+  \item With the above, obtain marginal improvements to classical confluence and termination criteria
+  \item Collecting implications between constructive notions of well-foundedness
+\end{itemize}
+
+\subsection{Formalization principles}
+\hired{One of our design goals is to stay within pure type theory as much as possible,
+therefore we adopt the following principles.}
+
+\begin{itemize}
+  \item No function extensionality
+  \item No univalence, uniqueness of identity proofs, cubical, or any other
+  assumptions related to equality
+  \item Minimize the use of classical logic; every place where it was necessary,
+  make decidability hypotheses explicit in every place where it could not be avoided.
+  \item The vast majority of results are completely constructive and therefore,
+  they compute.
+  \item The goal is to have the results of basic abstract rewriting
+  formalized in a canonical way, so that they can be used in building
+  libraries of formalized programming language theory
+  \item Since this application ....
+  \item In other words, we wanted to stay as close as possible to the spirit of type theory based on the Curry--Howard isomorphism, so that in every explicitly given situation, our proofs will compute.
+\end{itemize}
+
+\subsection{Misc.}
+One big item in this development was studying various incaranations of the concept of well-foundedness in constructive context.
+(Strong normalization is well-foundedness of the converse relation.)
+The ``standard'' constructive definition does not even allow one to show that SN implies WN, see Example \ref{ex:undec}.
+We therefore looked at a number of variations of this notion, their classical counterparts all being logically equivalent.
+This gave rise to a rich set of concepts, see Figure \ref{f:wf}.
+
+Along the way, we found marginal improvements to a number of standard theorems.
+For example, the termination assumption of the famous Newman's Lemma can be slightly weakened....
+
+There are also large classes of ARSs where some needed classical principles are simply valid.
+For example, finitely branching relations encompass most ARSs resulting from first-order term rewrite systems.
+For such relations, the implication SN to WN requires nothing else beyond plain decidability of
+the relation itself $Rxy \lor \lnot Rxy$.
+
+The main conclusion of our work is that most of basic ARS results can be made completely effective, at least for the most basic instance of first-order TRSs.
+(This also includes the usual lambda calculus.)
+
+For more exotic rewrite systems, like $\lambda \bot$ or coinductive rewriting,
+these decidability assumptions no longer hold, and the utility of ARS results diminishes proportionally.
+
+Finally, our Agda implementation provides a standard ``entry point'' for using these results in formal language development.
+
+{ \color{gray}
+In the conclusion, we should recap the main takeaways from each piece.
+\begin{itemize}
+  \item ARS results are effective for finitely branching and decidable relations
+  --- covers first-order TRSs and the lambda calculus.
+  \item Identification of ``sufficiency frontier'' for completeness (termination and confluence).
+  It also collapses many well-foundedness properties.
+  \item Also discuss open problems, unprovable implications, etc.
+  Maybe mention the Kleene tree idea, or at least include the reference to the Bezem--Coquand paper.
+\end{itemize}
+}
+
+\subsection{OLD>DELETE}
+
+Term Rewriting Systems (TRS) play a foundational role in the theory of
+programming languages.
+
+- Operational semantics
+- Reduction strategies
+
+At Appalachian State University, we are building a library of formalized theory,
+lambda calculus, and type theory. This is a first contribution in this effort.
+
+ARS is Establishing those properties of relations relevant for rewriting theory.
+
+Quotients.
+
+As a motivating example, consider the problem of representing quotients in type theory.
+
+Solutions relying on homotopy type theory require computational interpretation
+of univalence, which is a high price to pay for a basic structural operation
+undergirding many concepts in mathematics.
+Satisfactory solution is provided by cubical type theory, but this solution
+is very complex for something so basic.
+
+However
+
+Term rewriting systems allow to present an algebraic theory with a
+set of generators and relations from which decidability of equality
+follows immediately.
+Moreover, the fact that one can always find canonical representatives
+allows to efficiently work with them.
+
+- Formalization of "Abstract Rewriting" content from TeReSe,
+including background on logic, relations, etc.
+- Identifying constructive formulations of classical concepts and proofs
+- Studying implications between notions related to confluence and termination
+- Isolating classical principles from proofs and eliminating them where possible.
+-

### 2025-02-22 Relations/Paper/Definitions.tex
Progress throughout report

@@
 \label{sec:Definitions}
-
+\sacomment{Need to update move from WNFP to NP, WMFP to MP, NP to NP\_0}
+\sacomment{Need to update to refer to macros for properties}
 The following definitions are provided to ensure clarity and precision
@@
 
-In the context of abstract rewriting, we will often write $a \rstep_R b$
+In the context of abstract rewriting, we will often write $a \rstep b$
 in place of $(a,b) \in R$.  Similarly, we will write $a \mstep b$ for $(a,b) \in R^*$,
@@
 
-We first define rewriting-theoretic concepts like confluence and normalization relative to a fixed element of $A$; global versions of these properties are obtained by universal quantification.
+We next define rewriting-theoretic concepts like confluence and normalization relative to a fixed element of $A$; global versions of these properties are obtained by universal quantification.
+For equivalent definitions, see \texttt{ARS-Properties.agda}.
 
-\begin{definition}  Let $A$ and $R$ be as above, and let $a \in A$.
+\begin{definition} The following definitions relate to normalization. Let $A$ and $R$ be as above, and let $a \in A$.
   \begin{description}
-    \item[$a \in \NF_R$] \emph{$a$ is a normal form} if $(a,b) \notin R$ for any $b \in A$.
+    \item[$a \in \NF_R$] \emph{$a$ is a normal form} if $(a,b) \notin R$ for any $b \in A$ 
     \item[$a \in \WN_R$] \emph{$a$ is weakly normalizing} if $a \mstep b$ for some $b \in \NF_R$.
-    \item[$a \in SN_R$]  \emph{$a$ is $R$-accessible}, see Definition \ref{d:WFacc}.
+    \item[$a \in \SN_R$]  \emph{$a$ is $R$-accessible}, see Definition \ref{d:WFacc}.
   \end{description}
-
-    An element $a \in A$ is \emph{R-weakly confluent} ($WCR_R$) if all single step relations from $a$ can always converge
-    via multi-step relations to some common reduct.
-
-    A relation $R$ is \emph{weakly confluent} (AKA weakly Church-Rosser (WCR)) if every $a \in A$ is R-weakly confluent.
 \end{definition}
 
-\begin{definition}
-    An element $a \in A$ is \emph{R-confluent} ($CR_R$) if all multi-step relations from $a$ can always converge
-    via multi-step relations to some common reduct.
-    A relation $R$ is \emph{confluent} (AKA Church-Rosser (CR)) if every $a \in A$ is R-confluent.
+\begin{definition} The folowing definitions relate to being minimal. Let $A$ and $R$ be as above, and let $a \in A$.
+    \begin{description}
+        \item[$a \in \MF_R$] \emph{$a$ is a minimal form} if $a \mstep b \implies b \mstep a$ for any $b \in A$.
+        \item[$a \in \WM_R$] \emph{$a$ is weakly minimalizing} if $a \mstep b$ for some $b \in \MF_R$.
+        \item[$a \in \SM_R$]  \emph{$a$ is strongly minimalizing} if either $a \in MF_R$ or every element one $R$ step from $a$ is also strongly minimalizing.
+    \end{description}
 \end{definition}
+We found that there was a strong interrelationship between the normalizing properties and the minimal properties. This relationship is 
+captured in Figure \ref{fig:norm-hierarchy}.
+
+\begin{figure}[h]   
+    \centering
+        \begin{tikzpicture}[auto,
+            arrowstyle/.style={->, line width=1pt, >={Latex[length=3mm, width=2mm]}, shorten >=2pt}]
+            % A box style
+            \tikzstyle{boxnode} = [draw, rectangle, text centered,minimum width=1.2cm, inner sep=3pt]   
+            % Define the nodes
+            \node (SN) [boxnode] at (4,0) {$\SN$};
+            \node (WN) [boxnode, above right=0.5cm and 0.5cm of SN] {$\WN$};
+            \node (SR) [boxnode, below right=0.5cm and 0.5cm of SN] {$\SM$};
+            \node (WR) [boxnode, below right=0.5cm and 0.5cm of WN] {$\WM$};
+
+            % Draw the arrows to form a diamond
+            \draw [arrowstyle] (SN) -- (WN);
+            \draw [arrowstyle] (SN) -- (SR);
+            \draw [arrowstyle] (WN) -- (WR);
+            \draw [arrowstyle] (SR) -- (WR);
+        \end{tikzpicture}
+        \caption{A hierarchy of normalizing and minimal properties.}
+        \label{fig:norm-hierarchy}
+\end{figure}
+
+The implications will be explored in detail in Section \ref{sec:Implications}.
+
+A trivial implication not captured in the above figure is covered in Proposition \ref{prop:nftomf}. 
+\begin{proposition}\label{prop:nftomf}
+    $a\in NF_R \implies a \in MF_R$ 
+\end{proposition}    
+\begin{proof}
+    See, \verb|NF ⊆ MF : ∀x → NFx → MFx| in \texttt{ARS-Implications.agda}.
+\end{proof}
+
+\begin{definition} The following definitions relate to confluence. Let $A$ and $R$ be as above, and let $a \in A$.
+    \begin{description}
+        \item[$a \in \WCR_R$] \emph{$a$ is weakly Church-Rosser (or weakly confluent)} if $c \bstep a \rstep b \implies c \mstep d \bmstep b$.
+        \item[$a \in \CR_R$] \emph{$a$ is Church-Rosser (or confluent)} if $c \bmstep a \mstep b \implies c \mstep d \bmstep b$.
+        \item[$a \in \NPe_R$] \emph{$a$ has the equivalence normal form property} if $a \estep b \implies a\mstep b$ for any $b \in \NF$.
+        \item[$a \in \NP_R$] \emph{$a$ has the normal form property} if $c \bmstep a \mstep b \implies c \mstep b$ for any $b \in \NF$\footnote{In \terese $\NF$ is used to denote $\NPe$, whereas we have chosen to use $\NF$ to denote normal form.}.
+        \item[$a \in \MP_R$] \emph{$a$ has the minimal form property} if $c \bmstep a \mstep b \implies c \mstep b$ for any $b \in \MF$.
+        \item[$a \in \UN_R$] \emph{$a$ has the unique normal form property} if $a \estep b \implies a \equiv b$  for any $a, b \in NF$.
+        \item[$a \in \UNto_R$] \emph{$a$ has the unique normal form property with respect to reduction} if $c \bmstep a \mstep b  \implies b \equiv c$  for any $b, c \in NF$.
+    \end{description}
+\end{definition}
+
+Again, we found that there was a strong interrelationship between the properties, captured in Figure \ref{fig:conf-hierarchy}, which are explored in Section \ref{sec:Implications}.
+
+\begin{figure}[h] 
+    \centering
+
+        \begin{tikzpicture}[auto,
+          arrowstyle/.style={->, line width=1pt, >={Latex[length=3mm, width=2mm]}, shorten >=2pt}]
+          % A box style
+          \tikzstyle{boxnode} = [draw, rectangle, text centered,minimum width=1.2cm, inner sep=3pt]
+
+          % Place the nodes vertically (top to bottom)
+          \node (Confluent) [boxnode] at (-4,0) {$\CR$};
+          \node (RP)        [boxnode, right=.5cm of Confluent] {$\MP$};
+          \node (WN)        [boxnode, right=.5cm of RP] {$\NP$};
+          \node (UN)        [boxnode, right=.5cm of WN] {$\UNto$};
+
+          % Draw arrows downwards
+          \draw[arrowstyle] (Confluent) -- (RP);
+          \draw[arrowstyle] (RP) -- (WN);
+          \draw[arrowstyle] (WN) -- (UN);
+
+          \end{tikzpicture}
+          \caption{A hierarchy of confluent properties.}
+          \label{fig:conf-hierarchy}
+
+\end{figure}
+
+\sacomment{Make sure somewhere it is mentioned that NP equals $NP_=$ and that UN does not equal UNto.}
+
+\sacomment{Work for Saturday: Get the final definitions written up: namely the RP definitions and maybe make a figure to show those interrelationships}.
+%     \begin{definition}
+
+%   An element $a \in A$ is \emph{R-weakly confluent} ($WCR_R$) if all single step relations from $a$ can always converge
+%     via multi-step relations to some common reduct.
+
+%     A relation $R$ is \emph{weakly confluent} (AKA weakly Church-Rosser (WCR)) if every $a \in A$ is R-weakly confluent.
+% \end{definition}
+
+% \begin{definition}
+%     An element $a \in A$ is \emph{R-confluent} ($CR_R$) if all multi-step relations from $a$ can always converge
+%     via multi-step relations to some common reduct.
+%     A relation $R$ is \emph{confluent} (AKA Church-Rosser (CR)) if every $a \in A$ is R-confluent.
+% \end{definition}
 
@@
 
-\begin{definition}
-    An element $a \in A$ is \emph{$R$-weakly normalizing} ($WN_{R}$)if $a \mstep b$ for some normal form $b \in A$.
+% \begin{definition}
+%     An element $a \in A$ is \emph{$R$-weakly normalizing} ($WN_{R}$)if $a \mstep b$ for some normal form $b \in A$.
 
-    A relation $R$ is weakly normalizing (WN) if every $a \in A$ is $R$- weakly normalizing.
-\end{definition}
+%     A relation $R$ is weakly normalizing (WN) if every $a \in A$ is $R$- weakly normalizing.
+% \end{definition}
 
-\begin{definition}
-    An element $a \in A$ is \emph{$R$-strongly normalizing} ($SN_R$) if every sequence of relations starting from $a$ is finite.
+% \begin{definition}
+%     An element $a \in A$ is \emph{$R$-strongly normalizing} ($SN_R$) if every sequence of relations starting from $a$ is finite.
 
-    A relation $R$ is strongly normalizing (SN) if every
-    $a \in A$ is $R$-strongly normalizing.
-\end{definition}
+%     A relation $R$ is strongly normalizing (SN) if every
+%     $a \in A$ is $R$-strongly normalizing.
+% \end{definition}
 
@@
 
-\begin{definition}
-    An element $a \in A$ has the \emph{$R$-weak normal form property} ($WNFP_{R}$) if $a \mstep b$ and
-    $a \mstep c \implies c \mstep b$, for all $c \in A$ and all normal form $b \in A$.
+% \begin{definition}
+%     An element $a \in A$ has the \emph{$R$-weak normal form property} ($WNFP_{R}$) if $a \mstep b$ and
+%     $a \mstep c \implies c \mstep b$, for all $c \in A$ and all normal form $b \in A$.
 
-    A relation $R$ has the \emph{weak normal form property} (WNFP) if every $a \in A$ has the $R$-weak normal form property.
-\end{definition}
+%     A relation $R$ has the \emph{weak normal form property} (WNFP) if every $a \in A$ has the $R$-weak normal form property.
+% \end{definition}
 
-\begin{definition}
-    The \emph{equivalence relation} of $R$ is the smallest relation $\estep$ that contains $R$ and is reflexive, transitive, and symmetric.
-\end{definition}
+% \begin{definition}
+%     The \emph{equivalence relation} of $R$ is the smallest relation $\estep$ that contains $R$ and is reflexive, transitive, and symmetric.
+% \end{definition}
 
-\begin{definition}
-An element $a \in A$ has the \emph{$R$-normal form property} ($NFP_{R}$) if
-$a \estep b$  $\implies$
-$a \mstep b$, for any normal form $b \in A$.
+% \begin{definition}
+% An element $a \in A$ has the \emph{$R$-normal form property} ($NFP_{R}$) if
+% $a \estep b$  $\implies$
+% $a \mstep b$, for any normal form $b \in A$.
 
-A relation $R$ has the \emph{normal form property} (NFP) if every $a \in A$ has the $R$-normal form property.
-\end{definition}
+% A relation $R$ has the \emph{normal form property} (NFP) if every $a \in A$ has the $R$-normal form property.
+% \end{definition}
 
-In ARS-Implications.agda we show the equivalence of WNFP and NFP when applied globally in the function $\mathtt{NP \leftrightarrow WNFP}$.
+% In ARS-Implications.agda we show the equivalence of WNFP and NFP when applied globally in the function $\mathtt{NP \leftrightarrow WNFP}$.
 
-In the next definition we deonte two elements $a, b \in A$ being equivalent with $a \equiv b$.
-\begin{definition}
-An element $a \in A$ has the \emph{{R}-unique normal form property} ($UN_{R}$) if
-$a \estep b$  $\implies$
-$a \equiv b$, for any normal form $b \in A$.
+% In the next definition we deonte two elements $a, b \in A$ being equivalent with $a \equiv b$.
+% \begin{definition}
+% An element $a \in A$ has the \emph{{R}-unique normal form property} ($UN_{R}$) if
+% $a \estep b$  $\implies$
+% $a \equiv b$, for any normal form $b \in A$.
 
-A relation $R$ has the \emph{unique normal form property} ($UN$) if every $a \in A$ has the $R$-unique normal form property.
-\end{definition}
+% A relation $R$ has the \emph{unique normal form property} ($UN$) if every $a \in A$ has the $R$-unique normal form property.
+% \end{definition}
 
-\begin{definition}
-An element $a \in A$ has the \emph{${R}$-unique normal form property with respect to reduction} ($UN^ \to _{R}$) if
-$b \bmstep  \cdot  \mstep c$  $\implies$ $b \equiv c$, for all normal forms $b,c \in A$.
+% \begin{definition}
+% An element $a \in A$ has the \emph{${R}$-unique normal form property with respect to reduction} ($UN^ \to _{R}$) if
+% $b \bmstep  \cdot  \mstep c$  $\implies$ $b \equiv c$, for all normal forms $b,c \in A$.
 
-A relation $R$ has the \emph{unique normal form property with respect to reduction} ($UN^\to$) if every $a \in A$ has the
-$R$-unique normal form property with respect to reduction.
-\end{definition}
-In ARS-Implications.agda we show that $UN$ implies $UN\to$ but the inverse implication doesn't hold, as seen
-in counterexample (\sacomment{TODO: put counterexample here when section is complete}).
+% A relation $R$ has the \emph{unique normal form property with respect to reduction} ($UN^\to$) if every $a \in A$ has the
+% $R$-unique normal form property with respect to reduction.
+% \end{definition}
+% In ARS-Implications.agda we show that $UN$ implies $UN\to$ but the inverse implication doesn't hold, as seen
+% in counterexample (\sacomment{TODO: put counterexample here when section is complete}).
 
@@
 
-\begin{definition}
-    An element $a \in A$ has the \emph{minimal form property} ($MF$) if $a \mstep b \implies b \mstep a$ for all $b \in A$.
-\end{definition}
+% \begin{definition}
+%     An element $a \in A$ has the \emph{minimal form property} ($MF$) if $a \mstep b \implies b \mstep a$ for all $b \in A$.
+% \end{definition}
 
-Note that being a normal form is a trivial case of the minimal form property (as we prove in ARS-implications.agda
-function $\mathtt{NF\subseteq MF : \forall {x} \to NF x \to MF x}$).
+% Note that being a normal form is a trivial case of the minimal form property (as we prove in ARS-implications.agda
+% function $\mathtt{NF\subseteq MF : \forall {x} \to NF x \to MF x}$).
 
@@
 
-\begin{definition}
-    An element $a \in A$ is \emph{$R$-weakly minimal} ($WM_{R}$)if $a \mstep b$ for some minimal form $b \in A$.
+% \begin{definition}
+%     An element $a \in A$ is \emph{$R$-weakly minimal} ($WM_{R}$)if $a \mstep b$ for some minimal form $b \in A$.
 
-    A relation $R$ is weakly minimal (WM) if every $a \in A$ is $R$-weakly minimal.
-\end{definition}
+%     A relation $R$ is weakly minimal (WM) if every $a \in A$ is $R$-weakly minimal.
+% \end{definition}
 
-\begin{definition}
-    An element $a \in A$ is \emph{$R$-strongly minimal} ($SM_R$) if either $a$ itself is a minimal form or every element one $R$ step
-    from $a$ is also strongly minimal.
+% \begin{definition}
+%     An element $a \in A$ is \emph{$R$-strongly minimal} ($SM_R$) if either $a$ itself is a minimal form or every element one $R$ step
+%     from $a$ is also strongly minimal.
 
-    A relation $R$ is strongly minimal (SM) if every
-    $a \in A$ is $R$-strongly minimal.
-\end{definition}
+%     A relation $R$ is strongly minimal (SM) if every
+%     $a \in A$ is $R$-strongly minimal.
+% \end{definition}
 
-\begin{definition}
-   An element $a \in A$ has the \emph{${R}$-weak minimal form property} ($WMFP_R$) if
-   $a \mstep b$ and $a \mstep c$  $\implies$
-   $c \mstep b$, for all $c \in A$ and all $b \in A$ with the minimal form property.
+% \begin{definition}
+%    An element $a \in A$ has the \emph{${R}$-weak minimal form property} ($WMFP_R$) if
+%    $a \mstep b$ and $a \mstep c$  $\implies$
+%    $c \mstep b$, for all $c \in A$ and all $b \in A$ with the minimal form property.
 
-   A relation $R$ has the \emph{weak minimal form property} (WMFP) if every $a \in A$ has the $R$-weak minimal form property.
-\end{definition}
+%    A relation $R$ has the \emph{weak minimal form property} (WMFP) if every $a \in A$ has the $R$-weak minimal form property.
+% \end{definition}
 \begin{definition}

### 2025-02-22 Relations/Paper/Formalization.tex
Progress throughout report

@@
 
-\verb|RP-↔RP : R is RP- ↔ R is RP| \footnote{ARS-implications.agda}
-
+\verb|RP-↔RP : R is RP- ↔ R is RP| \footnotemark[1]
+\footnotetext[1]{\texttt{ARS-implications.agda}}
 Three proofs are given in \terese of Newman's Lemma (Theorem 1.2.1). The first and third of 
@@
 
-\verb|NewmansLemma : R isSN → R isWCR → R isCR| \footnote{ARS-NewmansLemma.agda}
-
+\verb|NewmansLemma : R isSN → R isWCR → R isCR| \footnotemark[2]
+\footnotetext[2]{\texttt{ARS-NewmansLemma.agda}}
 We show in section \ref{sec:Implications} that $\SN$ implies $\SM$, and it is from this implication 
@@
 
-\verb|LocalNewmansLemmaRecurrent : R isWCR → SM ⊆ CR| \footnote{ARS-NewmansLemma.agda}
+\verb|LocalNewmansLemmaRecurrent : R isWCR → SM ⊆ CR| \footnotemark[2]
 
-and \verb|GlobalNewmansLemmaRecurrent : R isWCR → R isSM → R isCR| \footnote{ARS-NewmansLemma.agda}
+and \verb|GlobalNewmansLemmaRecurrent : R isWCR → R isSM → R isCR| \footnotemark[2]
 
@@
 we found that we still require a classical principle in order for the proof to hold (as can be seen in the type of our proof):
-\verb|iii : R isWN → R isWCR → R isRP- → dec (SN) → R isSN| \footnote{ARS-Theorems.agda}
+\verb|iii : R isWN → R isWCR → R isRP- → dec (SN) → R isSN| \footnotemark[3] \footnotetext[3]{\texttt{ARS-Theorems.agda}}
 The classical property $\decSN$ is a property that states it is decidable whether a given 

### 2025-02-22 Relations/Paper/Implications.tex
Progress throughout report

@@
 \label{sec:Implications}
+
+\newenvironment{counterexample}[1][]{%
+    \refstepcounter{CEcounter} % Increment the counter
+    \noindent \scriptsize\textbf{{\theCEcounter } }  #1\par
+}
 
@@
 The following tables show which combination of these properties implies a property higher in the hierarchy. Where a combination 
-does not imply a higher property an explanatory counterexample is given. The counterexamples referenced are in section \ref{sec:Counterexamples}.
+does not imply a higher property an explanatory counterexample is given. The counterexamples referenced are shown below the tables in subsection \ref{subsec:counterexamples}.
 
@@
 
+\sacomment{When the table and CE are finished, write an explanation that the CE to the local table 
+assume local WCr and the global table CEs assume global WCR!}
 \sacomment{UPDATE COUNTEREXAMPLES WHEN CE SECTION FINISHED}
@@
     \hline
-    $\UNto$ &  CE-, CE-     & CE, CE-       & $\CR$\footnotemark[1] , CE-          & $\CR$\footnotemark[1], CE            & $\CR$\footnotemark[2] , $\SN$ \\
+    $\UNto$ &  CE-\ref{CE:4}, CE-\ref{CE:12}     & CE-\ref{CE:4}, CE-\ref{CE:7}       & CE-\ref{CE:4} , CE-\ref{CE:9}          & CE-\ref{CE:4}, CE-\ref{CE:4}            & $\CR$\footnotemark[1] , $\SN$ \\
     \hline
-    $\NP$ & CE-, CE-      & $\CR$, CE-    & $\CR$\footnotemark[1] , CE-          & $\CR$, $\SN$      & $\CR$\footnotemark[2] , $\SN$ \\
+    $\NP$ & CE-\ref{CE:10},CE-\ref{CE:9}      & $\CR$, CE-\ref{CE:7}    & CE-\ref{CE:11} , CE-\ref{CE:9}          & $\CR$, $\SN$      & $\CR$\footnotemark[2] , $\SN$ \\
     \hline
-    $\MP$ & $\CR$ , CE-    & $\CR$, CE-    & $\CR$\footnotemark[2] , CE- & $\CR$, $\SN$      & $\CR$\footnotemark[2] , $\SN$ \\
+    $\MP$ & $\CR$ , CE-\ref{CE:9}    & $\CR$, CE-\ref{CE:7}    & $\CR$\footnotemark[2] , CE-\ref{CE:9} & $\CR$, $\SN$      & $\CR$\footnotemark[2] , $\SN$ \\
     \hline
-    $\CR$   & $\CR$, CE-     & $\CR$, CE-     & $\CR$, CE-        & $\CR$, $\SN$     & $\CR$ , $\SN$ \\
+    $\CR$   & $\CR$, CE-\ref{CE:9}     & $\CR$, CE-\ref{CE:7}     & $\CR$, CE-\ref{CE:9}        & $\CR$, $\SN$     & $\CR$ , $\SN$ \\
     \hline
@@
     \hline
-    $\UNto$ &  CE-, CE-     & $\CR$, CE-    & $\CR$\footnotemark[1] , CE-          & $\CR$, $\SN$      & $\CR$\footnotemark[2] , $\SN$ \\
+    $\UNto$ &  CE-\ref{CE:2}, CE-\ref{CE:9}     & $\CR$, CE-\ref{CE:7}    & $\CR$\footnotemark[1] , CE-\ref{CE:9}          & $\CR$, $\SN$      & $\CR$\footnotemark[2] , $\SN$ \\
     \hline
-    $\NP$ & CE-, CE-      & $\CR$, CE-    & $\CR$\footnotemark[1] , CE-          & $\CR$, $\SN$      & $\CR$\footnotemark[2] , $\SN$ \\
+    $\NP$ & CE-\ref{CE:3} , CE-\ref{CE:9}      & $\CR$, CE-\ref{CE:7}    & $\CR$\footnotemark[1] , CE-\ref{CE:9}          & $\CR$, $\SN$      & $\CR$\footnotemark[2] , $\SN$ \\
     \hline
-    $\MP$ & $\CR$ , CE    & $\CR$, CE-    & $\CR$\footnotemark[2] , CE- & $\CR$, $\SN$      & $\CR$\footnotemark[2] , $\SN$ \\
+    $\MP$ & $\CR$ , CE-\ref{CE:9}    & $\CR$, CE-\ref{CE:7}    & $\CR$\footnotemark[2] , CE-\ref{CE:9} & $\CR$, $\SN$      & $\CR$\footnotemark[2] , $\SN$ \\
     \hline
-    $\CR$   & $\CR$, CE     & $\CR$, CE     & $\CR$, CE-        & $\CR$, $\SN$      & $\CR$ , $\SN$ \\
+    $\CR$   & $\CR$, CE-\ref{CE:9}     & $\CR$, CE-\ref{CE:7}     & $\CR$, CE-\ref{CE:9}        & $\CR$, $\SN$      & $\CR$ , $\SN$ \\
     \hline
@@
 
+\subsection{Counterexamples}\label{subsec:counterexamples}
+% Setting up the ce counter 
+\newcounter{CEcounter}
+\renewcommand{\theCEcounter}{\arabic{CEcounter}}
+
+    \begin{center}
+        \begin{tabular}{ccc}  % Three columns per row
+            % First Counterexample
+            \begin{minipage}{0.3\textwidth}
+                \centering
+                \begin{counterexample}\label{CE:1}
+                    \begin{tikzcd}[row sep=small, column sep=small]
+                        a & b \arrow[l] \arrow[r, bend left] & c \arrow[l, bend left] \arrow[r] & d
+                    \end{tikzcd} \\
+                \end{counterexample}
+            \end{minipage}
+            &
+            % Second Counterexample
+            \begin{minipage}{0.3\textwidth}
+                \centering
+                \begin{counterexample}\label{CE:2}
+                    \begin{tikzcd}[row sep=small, column sep=small]
+                        a & b \arrow[l] \arrow[r, bend left] & c \arrow[l, bend left] \arrow[r] & d \arrow[loop right]
+                    \end{tikzcd} \\
+                \end{counterexample}
+            \end{minipage}
+            &
+            % Third Counterexample
+            \begin{minipage}{0.3\textwidth}
+                \centering
+                \begin{counterexample}\label{CE:3}
+                    \begin{tikzcd}[row sep=small, column sep=small]
+                        a \arrow[loop left] & b \arrow[l] \arrow[r, bend left] & c \arrow[l, bend left] \arrow[r] & d \arrow[loop right]
+                    \end{tikzcd} \\
+                \end{counterexample}
+            \end{minipage}
+            \\  % New row
+            \\
+
+            % Fourth Counterexample
+            \begin{minipage}{0.3\textwidth}
+                \centering
+                \begin{counterexample}\label{CE:4}
+                    \begin{tikzcd}[row sep=small, column sep=small]
+                        & a \arrow[d] \arrow[dl] \\ e & b \arrow[l] \arrow[r] & c \arrow[r, bend left] & d \arrow[l, bend left]
+                    \end{tikzcd} \\
+                \end{counterexample}
+            \end{minipage}
+            &
+            % Fifth Counterexample
+            % \begin{minipage}{0.3\textwidth}
+            %     \centering
+            %     \begin{counterexample}\label{CE:5}
+            %         \begin{tikzcd}[row sep=small, column sep=small]
+            %             d & a \arrow[l, two heads] \arrow[r, two heads] & b \arrow[r, bend left] & c \arrow[l, bend left]
+            %         \end{tikzcd} \\
+            %     \end{counterexample}
+            % \end{minipage}
+
+            % Sixth Counterexample - This one shows why UN -> doesn't imply UN
+            \begin{minipage}{0.3\textwidth}
+                \centering
+                \begin{counterexample}\label{CE:un}
+                    \begin{tikzcd}[row sep=small, column sep=small]
+                        n & c \arrow[l] \arrow[r] & a \arrow[r, bend left] & b \arrow[l, bend left]
+                        & d \arrow[l] \arrow[r] & m
+                    \end{tikzcd} \\
+                \end{counterexample}
+            \end{minipage}
+        % \\ % New row
+        % \\
+        &
+        \begin{minipage}{0.3\textwidth}
+            \centering
+            \begin{counterexample}\label{CE:7}
+            \begin{tikzcd}[row sep=small, column sep=small]
+                f_0 \arrow[r] \arrow[dr] & f_1 \arrow[r] \arrow[d] & f_2 \arrow[dl] \arrow[r] & \dots \arrow[dll] \\
+                & n 
+            \end{tikzcd} \\
+            \end{counterexample}
+        \end{minipage}
+        \\ % new row
+        \\
+
+        \begin{minipage}{0.3\textwidth}
+            \centering
+            \begin{counterexample}\label{CE:8}
+            \begin{tikzcd}[row sep=small, column sep=small]
+                f_0 \arrow[r] \arrow[d] & f_1 \arrow[r] \arrow[d] & f_2 \arrow[r] \arrow[d] & \dots \arrow[d] \\
+                n_0  & n_1  & n_2 & \dots 
+            \end{tikzcd} \\
+            \end{counterexample}
+        \end{minipage}
+
+        &
+        \begin{minipage}{0.3\textwidth}
+            \centering
+            \begin{counterexample}\label{CE:9}
+            \begin{tikzcd}[row sep=small, column sep=small]
+                a \arrow[r, bend left] & b \arrow[l, bend left]
+            \end{tikzcd} \\
+        \end{counterexample}
+    \end{minipage}
+    % \\ % New row
+    % \\
+    &
+    \begin{minipage}{0.3\textwidth}
+        \centering
+        \begin{counterexample}\label{CE:10}
+            \begin{tikzcd}[row sep=small, column sep=small]
+                d  \arrow[d] \arrow[rr, bend left] & a \arrow[r] \arrow[l]  &  
+                b \arrow[r, bend left] & c \arrow[l, bend left] \\  
+                f_0 \arrow[r] & f_1 \arrow[r] & f_2 \arrow[r] & \dots  
+            \end{tikzcd} \\
+        \end{counterexample}
+    \end{minipage}
+    % New row
+    \\
+    \\
+    \begin{minipage}{0.3\textwidth}
+        \centering
+        \begin{counterexample}\label{CE:11}
+            \begin{tikzcd}[row sep=small, column sep=small]
+                c \arrow[r, bend left] & b \arrow[l, bend left]  & a \arrow[l] \arrow[r] 
+                & d \arrow[r, bend left] & e \arrow[l, bend left]
+            \end{tikzcd} \\
+        \end{counterexample}
+    \end{minipage}
+    &
+    &
+    \begin{minipage}{0.3\textwidth}
+        \centering
+        \begin{counterexample}\label{CE:12}
+            \begin{tikzcd}[row sep=small, column sep=small]
+                c & a \arrow[r, bend left] \arrow[l] & b \arrow[l, bend left]
+            \end{tikzcd} \\
+        \end{counterexample}
+    \end{minipage}
+
+\end{tabular}
+\end{center}
+
 \sacomment{Need to update the tables with appropriate symbols for global and local. Colour for first row and column?}
 
-The tables show that there are two changes when moving from properties holding locally to globally. 
+\sacomment{Rewrite the below to reflect changes to the table.}
+The tables show a number of changes when moving from properties holding locally to globally. 
 Globally $\WN \land \UNto \implies \CR$ holds whereas it does not locally. Similarly, $\SM \land \WN \implies \SN$ holds 

### 2025-02-22 Relations/Paper/Definitions.tex
Definitions rewritten

@@
 \label{sec:Definitions}
-\sacomment{Need to update move from WNFP to NP, WMFP to MP, NP to NP\_0}
-\sacomment{Need to update to refer to macros for properties}
 The following definitions are provided to ensure clarity and precision
-in our discussion.
- When useful, we also include the name and type of
-definition as we have implemented it in Agda, allowing the report to guide the code
-and vice versa.
+in our discussion. Each subsection specifies the Agda file(s) which contain formalizations of the given definitions.
 
@@
 
+\subsection{Closure operators (\texttt{ClosureOperators.agda})}
 \begin{notation}
@@
 We next define rewriting-theoretic concepts like confluence and normalization relative to a fixed element of $A$; global versions of these properties are obtained by universal quantification.
-For equivalent definitions, see \texttt{ARS-Properties.agda}.
-
+\subsection{Normalization (\texttt{ARS-Properties.agda})}
 \begin{definition} The following definitions relate to normalization. Let $A$ and $R$ be as above, and let $a \in A$.
@@
     \item[$a \in \WN_R$] \emph{$a$ is weakly normalizing} if $a \mstep b$ for some $b \in \NF_R$.
-    \item[$a \in \SN_R$]  \emph{$a$ is $R$-accessible}, see Definition \ref{d:WFacc}.
+    \item[$a \in \SN_R$]  \emph{$a$ is strongly normalizing} if every reduction sequence starting from $a$ is well-founded\footnote{See Section \ref{sec:Well-foundedness} for definitions of being well-founded.
+Note that we are
+    making use of the alternative definition of $\SN$ provided in \terese.}. \sacomment{Check this defn}
   \end{description}
@@
         \item[$a \in \WM_R$] \emph{$a$ is weakly minimalizing} if $a \mstep b$ for some $b \in \MF_R$.
-        \item[$a \in \SM_R$]  \emph{$a$ is strongly minimalizing} if either $a \in MF_R$ or every element one $R$ step from $a$ is also strongly minimalizing.
+        \item[$a \in \SM_R$]  \emph{$a$ is strongly minimalizing} if either $a \in MF_R$, or every element one $R$ step from $a$ is also strongly minimalizing.
     \end{description}
@@
 \end{proof}
-
+\subsection{Confluence (\texttt{ARS-Properties.agda})}
 \begin{definition} The following definitions relate to confluence. Let $A$ and $R$ be as above, and let $a \in A$.
@@
 
-\sacomment{Make sure somewhere it is mentioned that NP equals $NP_=$ and that UN does not equal UNto.}
+\begin{proposition}
+    $\NPe \leftrightarrow \NP$ 
+\end{proposition}
+\begin{proof}
+    See, \verb|NP₌↔NP : R isNP₌ ↔ R isNP| in \texttt{ARS-Implications.agda}.
+\end{proof}
+\begin{proposition}
+    $\UN \implies \UNto $
+\end{proposition}
+\begin{proof}
+    See, \verb|UN→UN→ : R isUN → R isUN→| in \texttt{ARS-Implications.agda}
+\end{proof}
+The implication $\UNto \implies \UN$ does not hold, as can be seen in CE-\ref{CE:un} in Subsection \ref{subsec:counterexamples}.
+\subsection{Sequences and Recurrence (\texttt{ARS-Properties.agda}, \texttt{Seq.agda})}
+\begin{definition} The following definitions relate to the minimal definitions and are key to formalizing Theorem 1.2.3 in \terese. Let $A$ and $R$ be as above, and let $a \in A$.
+    \begin{description}
+        \item[$s : \nat \to A$] \emph{A sequence $s \in A$} is a function from the natural numbers to $A$.  
+        \item[$s \in R-increasing$] \emph{A sequence $s \in A$ is $R$-increasing} if every term is $R$-related to its preceding term.
+        \item[$a \in \BP$] \emph{$a$ is a bound} if there exists a sequence $s$ such that $s (i) \mstep a$ for any $i \in \nat$. 
+        \item[$R\, is\, \RP$] \emph{$R$ has the recurrence property} if every bounded, increasing sequence has an element $a \in MF$.
+        \item[$R\, is\, \RPm$] \emph{$R$ has the weak recurrence property} if for every increasing sequence $s$ with bound $b$ there exists an element $i$ of the sequence such that $a \mstep s (i)$.
+        \item[$R\, is\, Inc$] \emph{$R$ is increasing} if there exists a ``size function'' $|-| : A \to \nat$ satisfying, for all $a, b \in A$,
+        \[ Rab \to |a| < |b| \]       
+    \end{description}
+\end{definition}
+Proposition \ref{prop:SMRP} connects $\SM$ with $\RP$ and $\BP$.
+\begin{proposition}\label{prop:SMRP}
+    $SM \leftrightarrow RP \land BP$
+\end{proposition}
+\begin{proof}
+    See,\\ \verb|RP∧BP→SMseq : R isRP → R isBP → ∀ {x : A} → SMseq R x| \\ \verb|RisSMseq→RisRP : (∀ {x : A} → SMseq R x) → R isRP|
+    \\ \verb|RisSMseq→RisBP : (∀ {x : A} → SMseq R x) → R isBP| in \texttt{ARS-Implications.agda}.
+\end{proof}
 
-\sacomment{Work for Saturday: Get the final definitions written up: namely the RP definitions and maybe make a figure to show those interrelationships}.
-%     \begin{definition}
+\begin{proposition}
+    If $R$ is increasing, then no infinite $R$-increasing sequence is bounded.
+\end{proposition}
+\begin{proof}
+    Let $(a_i) = a_0 \to a_1 \to a_2 \to \cdots$ be an $R$-increasing sequence
+    and suppose that $(a_i)$ is bounded.  Let $b$ be the bound, so that $a_i \to b$ for all $i$.
 
-%   An element $a \in A$ is \emph{R-weakly confluent} ($WCR_R$) if all single step relations from $a$ can always converge
-%     via multi-step relations to some common reduct.
+    If $m = |b|$ then we have
+    \[ 0 \le |a_0| < |a_1| < |a_2| < \cdots < |a_m| < |b| = m \]
+    % \[ m > |a_m| > |a_{m-1}| > \cdots > |a_0| \ge 0 \]
+    which is a contradiction, since there are only $m-1$ integers strictly less than $m$.
+\end{proof}
+It follows that every relation that is increasing in the sense of \terese
+vacuously satisfies the RP condition.
 
-%     A relation $R$ is \emph{weakly confluent} (AKA weakly Church-Rosser (WCR)) if every $a \in A$ is R-weakly confluent.
-% \end{definition}
+\begin{corollary}
+    If $R$ is increasing, then $R$ has the recurrence property.
+\end{corollary}
+We discuss in Section \ref{sec:Formalization} the motivation for finding an alternative for the increasing property found in \terese.
 
-% \begin{definition}
-%     An element $a \in A$ is \emph{R-confluent} ($CR_R$) if all multi-step relations from $a$ can always converge
-%     via multi-step relations to some common reduct.
-%     A relation $R$ is \emph{confluent} (AKA Church-Rosser (CR)) if every $a \in A$ is R-confluent.
-% \end{definition}
-
-\begin{definition}
-  \label{d:WFacc}
-  An element is \emph{accessible} if ...
-\end{definition}
-
-% \begin{definition}
-%     An element $a \in A$ is \emph{$R$-weakly normalizing} ($WN_{R}$)if $a \mstep b$ for some normal form $b \in A$.
-
-%     A relation $R$ is weakly normalizing (WN) if every $a \in A$ is $R$- weakly normalizing.
-% \end{definition}
-
-% \begin{definition}
-%     An element $a \in A$ is \emph{$R$-strongly normalizing} ($SN_R$) if every sequence of relations starting from $a$ is finite.
-
-%     A relation $R$ is strongly normalizing (SN) if every
-%     $a \in A$ is $R$-strongly normalizing.
-% \end{definition}
-
-The above definition of SN is taken from [TeReSe].
-When working in Agda, we make use of the alternative definition presented in [TeReSe] ($\leftarrow$ is accessibly well-founded).
-The \ref{sec:Well-foundedness} section clarifies this definition.
-
-% \begin{definition}
-%     An element $a \in A$ has the \emph{$R$-weak normal form property} ($WNFP_{R}$) if $a \mstep b$ and
-%     $a \mstep c \implies c \mstep b$, for all $c \in A$ and all normal form $b \in A$.
-
-%     A relation $R$ has the \emph{weak normal form property} (WNFP) if every $a \in A$ has the $R$-weak normal form property.
-% \end{definition}
-
-% \begin{definition}
-%     The \emph{equivalence relation} of $R$ is the smallest relation $\estep$ that contains $R$ and is reflexive, transitive, and symmetric.
-% \end{definition}
-
-% \begin{definition}
-% An element $a \in A$ has the \emph{$R$-normal form property} ($NFP_{R}$) if
-% $a \estep b$  $\implies$
-% $a \mstep b$, for any normal form $b \in A$.
-
-% A relation $R$ has the \emph{normal form property} (NFP) if every $a \in A$ has the $R$-normal form property.
-% \end{definition}
-
-% In ARS-Implications.agda we show the equivalence of WNFP and NFP when applied globally in the function $\mathtt{NP \leftrightarrow WNFP}$.
-
-% In the next definition we deonte two elements $a, b \in A$ being equivalent with $a \equiv b$.
-% \begin{definition}
-% An element $a \in A$ has the \emph{{R}-unique normal form property} ($UN_{R}$) if
-% $a \estep b$  $\implies$
-% $a \equiv b$, for any normal form $b \in A$.
-
-% A relation $R$ has the \emph{unique normal form property} ($UN$) if every $a \in A$ has the $R$-unique normal form property.
-% \end{definition}
-
-% \begin{definition}
-% An element $a \in A$ has the \emph{${R}$-unique normal form property with respect to reduction} ($UN^ \to _{R}$) if
-% $b \bmstep  \cdot  \mstep c$  $\implies$ $b \equiv c$, for all normal forms $b,c \in A$.
-
-% A relation $R$ has the \emph{unique normal form property with respect to reduction} ($UN^\to$) if every $a \in A$ has the
-% $R$-unique normal form property with respect to reduction.
-% \end{definition}
-% In ARS-Implications.agda we show that $UN$ implies $UN\to$ but the inverse implication doesn't hold, as seen
-% in counterexample (\sacomment{TODO: put counterexample here when section is complete}).
-
-\begin{definition}
-    A \emph{sequence (in $A$)} is a function from the natural numbers to $A$:
-    \begin{align*}
-      &s : \nat \to A \\
-      &s = (s_0,s_1,s_2,\dots)
-    \end{align*}
-\end{definition}
-
-\begin{definition}
-    A sequence is \emph{$R$-increasing} if every term is $R$-related to its preceding term.
-\end{definition}
-
-\begin{definition}
-    A sequence is \emph{bounded} if there exists an element $a \in A$ to which all elements of the sequence reduce.
-\end{definition}
-
-% \begin{definition}
-%     An element $a \in A$ has the \emph{minimal form property} ($MF$) if $a \mstep b \implies b \mstep a$ for all $b \in A$.
-% \end{definition}
-
-% Note that being a normal form is a trivial case of the minimal form property (as we prove in ARS-implications.agda
-% function $\mathtt{NF\subseteq MF : \forall {x} \to NF x \to MF x}$).
-
-\begin{definition}\label{d:RP}
-    A relation $R$ has the \emph{recurrence property} (RP) if every bounded, increasing sequence 
-    has an element $a \in MF$.
-\end{definition}
-
-\begin{definition}\label{d:RP-}
-    A relation $R$ has the \emph{weak recurrence property} (RP-) if for every increasing 
-    sequence with bound $a$, there is an element $i$ of the sequence such that 
-    $a \mstep f(i)$.
-\end{definition}
-
-% \begin{definition}
-%     An element $a \in A$ is \emph{$R$-weakly minimal} ($WM_{R}$)if $a \mstep b$ for some minimal form $b \in A$.
-
-%     A relation $R$ is weakly minimal (WM) if every $a \in A$ is $R$-weakly minimal.
-% \end{definition}
-
-% \begin{definition}
-%     An element $a \in A$ is \emph{$R$-strongly minimal} ($SM_R$) if either $a$ itself is a minimal form or every element one $R$ step
-%     from $a$ is also strongly minimal.
-
-%     A relation $R$ is strongly minimal (SM) if every
-%     $a \in A$ is $R$-strongly minimal.
-% \end{definition}
-
-% \begin{definition}
-%    An element $a \in A$ has the \emph{${R}$-weak minimal form property} ($WMFP_R$) if
-%    $a \mstep b$ and $a \mstep c$  $\implies$
-%    $c \mstep b$, for all $c \in A$ and all $b \in A$ with the minimal form property.
-
-%    A relation $R$ has the \emph{weak minimal form property} (WMFP) if every $a \in A$ has the $R$-weak minimal form property.
-% \end{definition}
-\begin{definition}
-    \label{d:inc}
-    A relation $R \sse A \times A$ is called \emph{increasing} if there
-    exists a ``size function'' $|-| : A \to \nat$ satisfying, for all $x, y \in A$,
-    \[ Rxy \to |x| < |y| \]
-\end{definition}
-
-Definitions to add:
-\begin{enumerate}
-    \item Finite branching
-    \item Any other terms from well foundedness
-    \item The other terms we have for strongly
-\end{enumerate}
+\sacomment{Anything else to define such as finitely branching?}

### 2025-02-22 Relations/Paper/Formalization.tex
Definitions rewritten

@@
 
-\begin{proposition}
-    If $R$ is increasing, then no infinite $R$-increasing sequence is bounded.
-\end{proposition}
-\begin{proof}
-    Let $(a_i) = a_0 \to a_1 \to a_2 \to \cdots$ be an $R$-increasing sequence
-    and suppose that $(a_i)$ is bounded.  Let $b$ be the bound, so that $a_i \to b$ for all $i$.
-
-    If $m = |b|$ then we have
-    \[ 0 \le |a_0| < |a_1| < |a_2| < \cdots < |a_m| < |b| = m \]
-    % \[ m > |a_m| > |a_{m-1}| > \cdots > |a_0| \ge 0 \]
-    which is a contradiction, since there are only $m-1$ integers strictly less than $m$.
-\end{proof}
-It follows that every relation that is increasing in the sense of \terese
-vacuously satisfies the RP condition.
-
-\begin{corollary}
-    If $R$ is increasing, then $R$ has the recurrence property.
-\end{corollary}
-
 We investigated $\RP$ and thought that with $\RPm$ we had a candidate for a weaker definition that 

### 2025-02-22 Relations/Paper/Formalization.tex
Formalization update

@@
 \label{sec:Formalization}
-The original ambition of this project was to formalize the contents of the \emph{abstract reduction 
-systems} chapter in Term Rewriting Systems [TeReSe], a standard text in rewriting. 
-The motivation for the project was to provide construvtive proofs in Agda 
-of the propositions and theorems in the chapter. This in turn provides a foundation for 
-future work in programming languages theory.
+This sections acts as a guide of our formalization of \terese and explains the deviations we took.
 
-In order to formalize the chapter we have aimed to provide constructive counterparts to the 
-classical proofs found in the text, and to make explicit any classical properties we depend 
-on when a constructive proof could not be found. It is from this formalization that our 
-original work has emerged. We have gone beyond \terese in fleshing out the interrelationship 
-of the properties most interesting from the perspective of programming languages theory (namely 
-being confluent and strongly normalizing). 
-For some properties we suggest alternatives which are more conducive to a constructive project. 
-We look into many notions of well-foundedness and again explore their interrelationship.
+\subsection{Formalization of Definitions}
+We have formalized those definitions which were necessary for the formalization of the propositions and theorems found 
+in Chapter 1 of \terese. We use Agda's built-in \texttt{Set} for sets and define a relation in \texttt{Predicates.agda}.
+The closure operators are formalized in \texttt{ARS-Closure.agda}. 
+The definitions given in \terese in \texttt{1.1.8 DEFINITION (confluence)} 
+are formalized in \texttt{ARS-Base.agda}. We only cover $\WCR$ and $\CR$ of the definitions from this section 
+as the other definitions were not involved in the more interesting formalizations.
 
-This section explains the deviations we took from \terese and lays the groundwork for the original work 
-that we have carried out.
+The definitions given in \terese in \texttt{1.1.13 DEFINITION (normalization)} 
+are formalized in \texttt{ARS-Properties.agda}.
 
-\sacomment{Maybe mention where we have stayed true to the book, but I don't think this is key}
+The following is a summary of the differences in definition we have used as mentioned in Section \ref{sec:Definitions}. 
+\begin{description}
+    \item[$\SN$] We make use of the well-founded defintion, rather than the finite reduction sequence definition.
+    \item[$\NPe$] We use the equivalent $\NP$ definition. 
+    \item[$\Inc$] We use the more general property $\RP$.      
+\end{description}
 
-Our first deviation from \terese is in defining strong normalization. The book defines 
-an element as strongly normalizing if every reduction sequence starting from it is finite. 
-We wanted to avoid introducing the notion of finiteness to our definition and so we 
-followed the alternative definition given in \terese : a relation is strongly normalizing when its 
-converse is well founded. In \terese a particular definition of well-foundedness is given but 
-it is one with which we were not satisfied and so we explored different definitions of 
-well-foundedness. This exploration is detailed in section \ref{sec:Well-foundedness}.
+Our motivation for using $\RP$ rather than $\Inc$ is that we found $\Inc$ to be a particularly difficult property 
+to use in a constructive setting.
 
-Another deviation we have taken from \terese relates to the use of the definition of an 
-increasing relation (see dfn:\ref{d:inc}). This property was one we found particularly difficult 
-to make use of in a constructive setting (for example showing that it along with the properties 
-of being WCR and WN implies SN) and so we suggest an alternative property, $\RP$.
-(dfn:\ref{d:RP}).
+\subsection{Propositions}
+There are three sets of propositions given in \terese: \texttt{1.1.9}, \texttt{1.1.10}, \texttt{1.1.11}. 
+The formalization of the proofs are in \texttt{ARS-Propositions.agda}. These formalizations were straightforward 
+and as such are not the focus of this paper.
+
+\subsection{Theorems}
+\subsubsection{Newman's Lemma}
+There are three proofs of Newman's Lemma ($\SN \land \WCR \implies \CR$) given in \terese. 
+The first and third of these proofs make use of classical properties,
 

### 2025-02-22 Relations/Paper/Definitions.tex
update after call

@@
 
-\greyout{We denote by $\tilde R$ the relational converse of $R$ ($(x,y) \in \tilde R \iff (y,x) \in R$),
-and by $R;R'$ the relational composition of $R$ and $R'$.}
+% \greyout{We denote by $\tilde R$ the relational converse of $R$ ($(x,y) \in \tilde R \iff (y,x) \in R$),
+% and by $R;R'$ the relational composition of $R$ and $R'$.}
 
@@
     \item $R^s$ denotes the \emph{symmetric closure} of $R$.
-    \item $R^+$ denotes the \emph{transitive closure} of $R$.
-    \item $R^* = (R^r)^+$ denotes the \emph{reflexive-transitive closure} of $R$.
+    \item $\tclos{R}$ denotes the \emph{transitive closure} of $R$.
+    \item $R^* = (R^r)\tclos{}$ denotes the \emph{reflexive-transitive closure} of $R$.
     \item $R^= = (R^s)^*$ denotes the \emph{equivalence relation generated by} $R$.
@@
     \item[$a \in \WN_R$] \emph{$a$ is weakly normalizing} if $a \mstep b$ for some $b \in \NF_R$.
-    \item[$a \in \SN_R$]  \emph{$a$ is strongly normalizing} if every reduction sequence starting from $a$ is well-founded\footnote{See Section \ref{sec:Well-foundedness} for definitions of being well-founded.
-Note that we are
-    making use of the alternative definition of $\SN$ provided in \terese.}. \sacomment{Check this defn}
+    \item[$a \in \SN_R$] \emph{$a$ is strongly normalizing} if $a$ is accessible with respect to the converse relation $\bar{R} = {(y,x) | (x,y) \in R}$. See Section \ref{sec:Well-foundedness}. 
   \end{description}
@@
 
-\begin{definition} The folowing definitions relate to being minimal. Let $A$ and $R$ be as above, and let $a \in A$.
-    \begin{description}
-        \item[$a \in \MF_R$] \emph{$a$ is a minimal form} if $a \mstep b \implies b \mstep a$ for any $b \in A$.
-        \item[$a \in \WM_R$] \emph{$a$ is weakly minimalizing} if $a \mstep b$ for some $b \in \MF_R$.
-        \item[$a \in \SM_R$]  \emph{$a$ is strongly minimalizing} if either $a \in MF_R$, or every element one $R$ step from $a$ is also strongly minimalizing.
-    \end{description}
-\end{definition}
-We found that there was a strong interrelationship between the normalizing properties and the minimal properties. This relationship is 
-captured in Figure \ref{fig:norm-hierarchy}.
-
-\begin{figure}[h]   
-    \centering
-        \begin{tikzpicture}[auto,
-            arrowstyle/.style={->, line width=1pt, >={Latex[length=3mm, width=2mm]}, shorten >=2pt}]
-            % A box style
-            \tikzstyle{boxnode} = [draw, rectangle, text centered,minimum width=1.2cm, inner sep=3pt]   
-            % Define the nodes
-            \node (SN) [boxnode] at (4,0) {$\SN$};
-            \node (WN) [boxnode, above right=0.5cm and 0.5cm of SN] {$\WN$};
-            \node (SR) [boxnode, below right=0.5cm and 0.5cm of SN] {$\SM$};
-            \node (WR) [boxnode, below right=0.5cm and 0.5cm of WN] {$\WM$};
-
-            % Draw the arrows to form a diamond
-            \draw [arrowstyle] (SN) -- (WN);
-            \draw [arrowstyle] (SN) -- (SR);
-            \draw [arrowstyle] (WN) -- (WR);
-            \draw [arrowstyle] (SR) -- (WR);
-        \end{tikzpicture}
-        \caption{A hierarchy of normalizing and minimal properties.}
-        \label{fig:norm-hierarchy}
-\end{figure}
-
-The implications will be explored in detail in Section \ref{sec:Implications}.
-
-A trivial implication not captured in the above figure is covered in Proposition \ref{prop:nftomf}. 
-\begin{proposition}\label{prop:nftomf}
-    $a\in NF_R \implies a \in MF_R$ 
-\end{proposition}    
-\begin{proof}
-    See, \verb|NF ⊆ MF : ∀x → NFx → MFx| in \texttt{ARS-Implications.agda}.
-\end{proof}
 \subsection{Confluence (\texttt{ARS-Properties.agda})}
@@
         \item[$a \in \NPe_R$] \emph{$a$ has the equivalence normal form property} if $a \estep b \implies a\mstep b$ for any $b \in \NF$.
-        \item[$a \in \NP_R$] \emph{$a$ has the normal form property} if $c \bmstep a \mstep b \implies c \mstep b$ for any $b \in \NF$\footnote{In \terese $\NF$ is used to denote $\NPe$, whereas we have chosen to use $\NF$ to denote normal form.}.
-        \item[$a \in \MP_R$] \emph{$a$ has the minimal form property} if $c \bmstep a \mstep b \implies c \mstep b$ for any $b \in \MF$.
-        \item[$a \in \UN_R$] \emph{$a$ has the unique normal form property} if $a \estep b \implies a \equiv b$  for any $a, b \in NF$.
-        \item[$a \in \UNto_R$] \emph{$a$ has the unique normal form property with respect to reduction} if $c \bmstep a \mstep b  \implies b \equiv c$  for any $b, c \in NF$.
+        \item[$a \in \NP_R$] \emph{$a$ has the normal form property} if $c \bmstep a \mstep b \implies c \mstep b$ for any $b \in \NF$. 
+        \item[$a \in \UN_R$] \emph{$a$ has the unique normal form property} if $a \estep b \implies a \equiv b$  for any $a, b \in \NF$.
+        \item[$a \in \UNto_R$] \emph{$a$ has the unique normal form property with respect to reduction} if $c \bmstep a \mstep b  \implies b \equiv c$  for any $b, c \in \NF$.
     \end{description}
 \end{definition}
+For each of the subsets defined above we denote in bold face the proposition that the subset contains all of $A$.
+That is, for $\mathrm{X} \in \{\WCR , \CR , \NP , \UN \}$ we write $\mathbf{X}$ for the statement that $x \in \mathrm{X}_R$ for all $x \in A$.
 
-Again, we found that there was a strong interrelationship between the properties, captured in Figure \ref{fig:conf-hierarchy}, which are explored in Section \ref{sec:Implications}.
-
-\begin{figure}[h] 
-    \centering
-
-        \begin{tikzpicture}[auto,
-          arrowstyle/.style={->, line width=1pt, >={Latex[length=3mm, width=2mm]}, shorten >=2pt}]
-          % A box style
-          \tikzstyle{boxnode} = [draw, rectangle, text centered,minimum width=1.2cm, inner sep=3pt]
-
-          % Place the nodes vertically (top to bottom)
-          \node (Confluent) [boxnode] at (-4,0) {$\CR$};
-          \node (RP)        [boxnode, right=.5cm of Confluent] {$\MP$};
-          \node (WN)        [boxnode, right=.5cm of RP] {$\NP$};
-          \node (UN)        [boxnode, right=.5cm of WN] {$\UNto$};
-
-          % Draw arrows downwards
-          \draw[arrowstyle] (Confluent) -- (RP);
-          \draw[arrowstyle] (RP) -- (WN);
-          \draw[arrowstyle] (WN) -- (UN);
-
-          \end{tikzpicture}
-          \caption{A hierarchy of confluent properties.}
-          \label{fig:conf-hierarchy}
-
-\end{figure}
+In \terese $\NF$ is used to denote $\NPe$, whereas we have chosen to use $\NF$ to denote normal form. Moreover, ${\gNP}$ and ${\gNPe}$ are equivalent when
 
@@
 \subsection{Sequences and Recurrence (\texttt{ARS-Properties.agda}, \texttt{Seq.agda})}
-\begin{definition} The following definitions relate to the minimal definitions and are key to formalizing Theorem 1.2.3 in \terese. Let $A$ and $R$ be as above, and let $a \in A$.
+The following definitions are key to formalizing Theorem 1.2.3 in \terese.
+$R \models \mathbf{X}$ is $\forall a. a \in \mathrm{X}_R$. When $R$ is clear from the context, we will write $\gNP$ for $R \models \gNP$, etc. \sacomment{Mention this earlier}
+
+\begin{definition}
+    \begin{description}
+        \item[$R \models Inc$] \emph{$R$ is increasing} if there exists a ``size function'' $|-| : A \to \nat$ satisfying, for all $a, b \in A$,
+        $Rab \to |a| < |b|$  
+    \end{description}
+\end{definition}
+
+\sacomment{motivate here going from above defn to the following.}
+
+\begin{definition} Let $A$ and $R$ be as above, and let $a \in A$.
     \begin{description}
@@
         \item[$s \in R-increasing$] \emph{A sequence $s \in A$ is $R$-increasing} if every term is $R$-related to its preceding term.
-        \item[$a \in \BP$] \emph{$a$ is a bound} if there exists a sequence $s$ such that $s (i) \mstep a$ for any $i \in \nat$. 
-        \item[$R\, is\, \RP$] \emph{$R$ has the recurrence property} if every bounded, increasing sequence has an element $a \in MF$.
-        \item[$R\, is\, \RPm$] \emph{$R$ has the weak recurrence property} if for every increasing sequence $s$ with bound $b$ there exists an element $i$ of the sequence such that $a \mstep s (i)$.
-        \item[$R\, is\, Inc$] \emph{$R$ is increasing} if there exists a ``size function'' $|-| : A \to \nat$ satisfying, for all $a, b \in A$,
-        \[ Rab \to |a| < |b| \]       
+        \item[$a$ is an $s$-bound] if $s (i) \mstep a$ for all $i \in \nat$. 
+        \item[$a \in \BP_R$] if all $R$-increasing sequence $s$ with $s (0) = a$ there exists an $s$-bound. 
+        \item[$R \models \RPm$] \emph{$R$ has the weak recurrence property} if for every increasing sequence $s$ with bound $b$ there exists an $i \in \nat$ such that $b \mstep s (i)$.
+        \item[$R \models \RP$] \emph{$R$ has the recurrence property} if every bounded, increasing sequence $s$ with an $s$-bound, there exists an $i \in \nat$ such that 
+        $s (i) \in \MF$.
     \end{description}
 \end{definition}
-Proposition \ref{prop:SMRP} connects $\SM$ with $\RP$ and $\BP$.
-\begin{proposition}\label{prop:SMRP}
-    $SM \leftrightarrow RP \land BP$
+
+The following is immediate.
+\begin{proposition}\hfill 
+    \begin{enumerate}
+        \item $\Inc \implies \RPm$
+        \item $\RPm \implies \RP$
+    \end{enumerate}
 \end{proposition}
-\begin{proof}
-    See,\\ \verb|RP∧BP→SMseq : R isRP → R isBP → ∀ {x : A} → SMseq R x| \\ \verb|RisSMseq→RisRP : (∀ {x : A} → SMseq R x) → R isRP|
-    \\ \verb|RisSMseq→RisBP : (∀ {x : A} → SMseq R x) → R isBP| in \texttt{ARS-Implications.agda}.
-\end{proof}
 
-\begin{proposition}
-    If $R$ is increasing, then no infinite $R$-increasing sequence is bounded.
-\end{proposition}
-\begin{proof}
-    Let $(a_i) = a_0 \to a_1 \to a_2 \to \cdots$ be an $R$-increasing sequence
-    and suppose that $(a_i)$ is bounded.  Let $b$ be the bound, so that $a_i \to b$ for all $i$.
-
-    If $m = |b|$ then we have
-    \[ 0 \le |a_0| < |a_1| < |a_2| < \cdots < |a_m| < |b| = m \]
-    % \[ m > |a_m| > |a_{m-1}| > \cdots > |a_0| \ge 0 \]
-    which is a contradiction, since there are only $m-1$ integers strictly less than $m$.
-\end{proof}
 It follows that every relation that is increasing in the sense of \terese
@@
 
-\begin{corollary}
-    If $R$ is increasing, then $R$ has the recurrence property.
-\end{corollary}
-We discuss in Section \ref{sec:Formalization} the motivation for finding an alternative for the increasing property found in \terese.
+\sacomment{tidy up below on rp iff rp- .}
+We investigated $\RP$ and thought that with $\RPm$ we had a candidate for a weaker definition that 
+did not rely on the notion of $\MF$. We were able to proove that this weaker definition is 
+in fact an equivalent definition in the following proof in Agda:
 
+\verb|RP-↔RP : R is RP- ↔ R is RP| \footnotemark[1]
+
+\footnotetext[1]{\texttt{ARS-implications.agda}}
+\subsection{Finitely branching}
+\sacomment{This property is what makes a lot of the classical properties valid which otherwise wouldn't be. Valid in most interesting rewriting systems. Most 
+programming languages will satisfy finite branching.}
+\begin{definition}
+    \begin{description}
+        \item[TODO] TODO 
+    \end{description}
+\end{definition}
 \sacomment{Anything else to define such as finitely branching?}

### 2025-02-22 Relations/Paper/Formalization.tex
update after call

@@
-\section{Formalization of Terese}
+\section{Formalization of \terese}
 \label{sec:Formalization}
@@
 Our motivation for using $\RP$ rather than $\Inc$ is that we found $\Inc$ to be a particularly difficult property 
-to use in a constructive setting.
+to use in a constructive setting. \sacomment{Say more on this motivation and decide where it will be placed.}
 
@@
 The formalization of the proofs are in \texttt{ARS-Propositions.agda}. These formalizations were straightforward 
-and as such are not the focus of this paper.
+and as such are not the focus of this paper. \sacomment{Do we include more information on these propositions?}
 
@@
 
-We investigated $\RP$ and thought that with $\RPm$ we had a candidate for a weaker definition that 
-did not rely on the notion of $\MF$. We were able to proove that this weaker definition is 
-in fact an equivalent definition in the following proof in Agda:
-
-\verb|RP-↔RP : R is RP- ↔ R is RP| \footnotemark[1]
-\footnotetext[1]{\texttt{ARS-implications.agda}}
 Three proofs are given in \terese of Newman's Lemma (Theorem 1.2.1). The first and third of 

### 2025-02-22 Relations/Paper/Implications.tex
update after call

@@
 show chains of implications starting from these properties.
+
+\begin{definition} The folowing definitions relate to being minimal. Let $A$ and $R$ be as above, and let $a \in A$.
+    \begin{description}
+        \item[$a \in \MF_R$] \emph{$a$ is a minimal form} if $a \mstep b \implies b \mstep a$ for any $b \in A$.
+        \item[$a \in \WM_R$] \emph{$a$ is weakly minimalizing} if $a \mstep b$ for some $b \in \MF_R$.
+        \item[$a \in \SM_R$]  \emph{$a$ is strongly minimalizing} if either $a \in MF_R$, or every element one $R$ step from $a$ is also strongly minimalizing.
+        \item[$a \in \MP_R$] \emph{$a$ has the minimal form property} if $c \bmstep a \mstep b \implies c \mstep b$ for any $b \in \MF$.
+
+    \end{description}
+\end{definition}
+
+Again, we found that there was a strong interrelationship between the properties, captured in Figure \ref{fig:conf-hierarchy}, which are explored in Section \ref{sec:Implications}.
+
+\begin{figure}[h] 
+    \centering
+
+        \begin{tikzpicture}[auto,
+          arrowstyle/.style={->, line width=1pt, >={Latex[length=3mm, width=2mm]}, shorten >=2pt}]
+          % A box style
+          \tikzstyle{boxnode} = [draw, rectangle, text centered,minimum width=1.2cm, inner sep=3pt]
+
+          % Place the nodes vertically (top to bottom)
+          \node (Confluent) [boxnode] at (-4,0) {$\CR$};
+          \node (RP)        [boxnode, right=.5cm of Confluent] {$\MP$};
+          \node (WN)        [boxnode, right=.5cm of RP] {$\NP$};
+          \node (UN)        [boxnode, right=.5cm of WN] {$\UNto$};
+
+          % Draw arrows downwards
+          \draw[arrowstyle] (Confluent) -- (RP);
+          \draw[arrowstyle] (RP) -- (WN);
+          \draw[arrowstyle] (WN) -- (UN);
+
+          \end{tikzpicture}
+          \caption{A hierarchy of confluent properties.}
+          \label{fig:conf-hierarchy}
+
+\end{figure}
+We found that there was a strong interrelationship between the normalizing properties and the minimal properties. This relationship is 
+captured in Figure \ref{fig:norm-hierarchy}.
+
+\begin{figure}[h]   
+    \centering
+        \begin{tikzpicture}[auto,
+            arrowstyle/.style={->, line width=1pt, >={Latex[length=3mm, width=2mm]}, shorten >=2pt}]
+            % A box style
+            \tikzstyle{boxnode} = [draw, rectangle, text centered,minimum width=1.2cm, inner sep=3pt]   
+            % Define the nodes
+            \node (SN) [boxnode] at (4,0) {$\SN$};
+            \node (WN) [boxnode, above right=0.5cm and 0.5cm of SN] {$\WN$};
+            \node (SR) [boxnode, below right=0.5cm and 0.5cm of SN] {$\SM$};
+            \node (WR) [boxnode, below right=0.5cm and 0.5cm of WN] {$\WM$};
+
+            % Draw the arrows to form a diamond
+            \draw [arrowstyle] (SN) -- (WN);
+            \draw [arrowstyle] (SN) -- (SR);
+            \draw [arrowstyle] (WN) -- (WR);
+            \draw [arrowstyle] (SR) -- (WR);
+        \end{tikzpicture}
+        \caption{A hierarchy of normalizing and minimal properties.}
+        \label{fig:norm-hierarchy}
+\end{figure}
+
+The implications will be explored in detail in Section \ref{sec:Implications}.
+
+Proposition \ref{prop:SMRP} connects $\SM$ with $\RP$ and $\BP$. \sacomment{Need to relate SM and SMseq. Probably define SMseq and metion 
+we can only prove this for SMseq.}
+\begin{proposition}\label{prop:SMRP}
+    $SM \leftrightarrow RP \land BP$
+\end{proposition}
+\begin{proof}
+    See,\\ \verb|RP∧BP→SMseq : R isRP → R isBP → ∀ {x : A} → SMseq R x| \\ \verb|RisSMseq→RisRP : (∀ {x : A} → SMseq R x) → R isRP|
+    \\ \verb|RisSMseq→RisBP : (∀ {x : A} → SMseq R x) → R isBP| in \texttt{ARS-Implications.agda}.
+\end{proof}
+
+A trivial implication not captured in the above figure is covered in Proposition \ref{prop:nftomf}. 
+\begin{proposition}\label{prop:nftomf}
+    $a\in NF_R \implies a \in MF_R$ 
+\end{proposition}    
+\begin{proof}
+    See, \verb|NF ⊆ MF : ∀x → NFx → MFx| in \texttt{ARS-Implications.agda}.
+\end{proof}
 

### 2025-02-23 Relations/Paper/Definitions.tex
Pre call upload

@@
 For the rest of this section, let $A$ be a fixed set, and $R$ be a relation on $A$.
-(In the Agda code supplement, this is represented by a type $A : \bset$,
-and a binary type family $R : A \to A \to \bset$.)
 
@@
         \item[$a \in \CR_R$] \emph{$a$ is Church-Rosser (or confluent)} if $c \bmstep a \mstep b \implies c \mstep d \bmstep b$.
+        \item[$a \in \CRs_R$] \emph{$a$ is subcommutative} if $c \bmstep a \mstep b \implies c \rrstep d \brstep b$.
         \item[$a \in \NPe_R$] \emph{$a$ has the equivalence normal form property} if $a \estep b \implies a\mstep b$ for any $b \in \NF$.
@@
 
-In \terese $\NF$ is used to denote $\NPe$, whereas we have chosen to use $\NF$ to denote normal form. Moreover, ${\gNP}$ and ${\gNPe}$ are equivalent when
+In \terese $\NF$ is used to denote $\NPe$, whereas we have chosen to use $\NF$ to denote normal form.
 
-\begin{proposition}
-    $\NPe \leftrightarrow \NP$ 
+\begin{proposition}\hfill 
+    \begin{enumerate}
+        \item $\gNP \iff \gNPe$ 
+        \item $\gUN \implies \gUNto$
+    \end{enumerate}
 \end{proposition}
-\begin{proof}
-    See, \verb|NP₌↔NP : R isNP₌ ↔ R isNP| in \texttt{ARS-Implications.agda}.
+\begin{proof} \hfill
+    \begin{enumerate}
+        \item \verb|NP₌↔NP : R isNP₌ ↔ R isNP| in \texttt{ARS-Implications.agda}.
+        \item \verb|UN→UN→ : R isUN → R isUN→| in \texttt{ARS-Implications.agda}. 
+    \end{enumerate} 
 \end{proof}
-\begin{proposition}
-    $\UN \implies \UNto $
-\end{proposition}
-\begin{proof}
-    See, \verb|UN→UN→ : R isUN → R isUN→| in \texttt{ARS-Implications.agda}
-\end{proof}
-The implication $\UNto \implies \UN$ does not hold, as can be seen in CE-\ref{CE:un} in Subsection \ref{subsec:counterexamples}.
+
+The implication $\UNto \implies \UN$ does not hold, as can be seen in Example \ref{CE:un} in Subsection \ref{subsec:counterexamples}.
+
 \subsection{Sequences and Recurrence (\texttt{ARS-Properties.agda}, \texttt{Seq.agda})}
 The following definitions are key to formalizing Theorem 1.2.3 in \terese.
-$R \models \mathbf{X}$ is $\forall a. a \in \mathrm{X}_R$. When $R$ is clear from the context, we will write $\gNP$ for $R \models \gNP$, etc. \sacomment{Mention this earlier}
+
+\begin{notation}
+    $R \models \mathbf{X}$ is $\forall a.\; a \in \mathrm{X}_R$. When $R$ is clear from the context, we will write $\gNP$ for $R \models \gNP$, etc. 
+\end{notation}
 
@@
         $Rab \to |a| < |b|$  
+        \item[$a \in \CP$] \sacomment{Need a definition of cofinality here}
     \end{description}
@@
 
-\sacomment{motivate here going from above defn to the following.}
-
-\begin{definition} Let $A$ and $R$ be as above, and let $a \in A$.
+Having a "size function" that maps to the natural numbers is computationally taxing to satisfy. 
+Futher, it takes us outside of pure relational theory. The following definitions are for properties which allow us to forgo $\Inc$, for further discussion see Subsection \ref{subsec:def}.
+\begin{definition} \label{def:rp} Let $A$ and $R$ be as above, and let $a \in A$.
     \begin{description} 
@@
         \item[$R \models \RP$] \emph{$R$ has the recurrence property} if every bounded, increasing sequence $s$ with an $s$-bound, there exists an $i \in \nat$ such that 
-        $s (i) \in \MF$.
+        $s (i) \in \MF$. See Definition \ref{def:mf}. 
     \end{description}
 \end{definition}
+In \terese $\mathsf{Ind}$ is used to denote $\BP$.
 
@@
     \begin{enumerate}
-        \item $\Inc \implies \RPm$
-        \item $\RPm \implies \RP$
+        \item $\gInc \implies \gRPm$
+        \item $\gRPm \implies \gRP$
     \end{enumerate}
@@
 
-\sacomment{tidy up below on rp iff rp- .}
 We investigated $\RP$ and thought that with $\RPm$ we had a candidate for a weaker definition that 
-did not rely on the notion of $\MF$. We were able to proove that this weaker definition is 
-in fact an equivalent definition in the following proof in Agda:
+did not rely on the notion of $\MF$. We show that this weaker definition is 
+in fact an equivalent definition in the following proof in \texttt{ARS-Implications.agda}:
 
-\verb|RP-↔RP : R is RP- ↔ R is RP| \footnotemark[1]
+\verb|RP-↔RP : R is RP- ↔ R is RP|.
 
-\footnotetext[1]{\texttt{ARS-implications.agda}}
-\subsection{Finitely branching}
+\subsection{Finitely branching (\texttt{FinitelyBranching.agda})}
 \sacomment{This property is what makes a lot of the classical properties valid which otherwise wouldn't be. Valid in most interesting rewriting systems. Most 
 programming languages will satisfy finite branching.}
-\begin{definition}
+\begin{definition} Let $A$ and $R$ be as above, and let $a \in A$.
     \begin{description}
-        \item[TODO] TODO 
+        \item[$a \in \FB$] \emph{$a$ is finitely branching} if there is a finite amount of  $b \in A$ such that $a \rstep b$. 
     \end{description}
 \end{definition}
-\sacomment{Anything else to define such as finitely branching?}

### 2025-02-23 Relations/Paper/Formalization.tex
Pre call upload

@@
 
-\subsection{Formalization of Definitions}
+\subsection{Formalization of Definitions}\label{subsec:def}
 We have formalized those definitions which were necessary for the formalization of the propositions and theorems found 
-in Chapter 1 of \terese. We use Agda's built-in \texttt{Set} for sets and define a relation in \texttt{Predicates.agda}.
+in Chapter 1 of \terese. 
 The closure operators are formalized in \texttt{ARS-Closure.agda}. 
-The definitions given in \terese in \texttt{1.1.8 DEFINITION (confluence)} 
-are formalized in \texttt{ARS-Base.agda}. We only cover $\WCR$ and $\CR$ of the definitions from this section 
-as the other definitions were not involved in the more interesting formalizations.
-
-The definitions given in \terese in \texttt{1.1.13 DEFINITION (normalization)} 
-are formalized in \texttt{ARS-Properties.agda}.
+The definitions grouped as confluent \terese are formalized in \texttt{ARS-Base.agda}. 
+The definitions grouped as normalizing in \terese are formalized in \texttt{ARS-Properties.agda}.
 
 The following is a summary of the differences in definition we have used as mentioned in Section \ref{sec:Definitions}. 
-\begin{description}
-    \item[$\SN$] We make use of the well-founded defintion, rather than the finite reduction sequence definition.
-    \item[$\NPe$] We use the equivalent $\NP$ definition. 
-    \item[$\Inc$] We use the more general property $\RP$.      
-\end{description}
+\begin{itemize}
+    \item $\SN$ : We make use of the well-founded defintion, rather than the finite reduction sequence definition.
+    \item $\NPe$ : We use the equivalent $\NP$ definition. 
+    \item $\Inc$ : We use the more general property $\RP$.      
+\end{itemize}
 
-Our motivation for using $\RP$ rather than $\Inc$ is that we found $\Inc$ to be a particularly difficult property 
-to use in a constructive setting. \sacomment{Say more on this motivation and decide where it will be placed.}
+As already mentioned, the $\Inc$ property was one we wanted to move away from. We saw that $\Inc$ was being used only in Theorem 1.2.3 
+and that the crucial facet of $\Inc$ for the proof of the theorem was that every sequence has a bound \sacomment{is this the correct characterization?}. 
+So we established that the properties in Definition \ref{def:rp} were sufficient for the proving the theorems. This in turn led us to examining 
+a generalization of a normal form, the minimal form. We explore this further in Section \ref{sec:Implications}.
 
@@
 There are three proofs of Newman's Lemma ($\SN \land \WCR \implies \CR$) given in \terese. 
-The first and third of these proofs make use of classical properties,
+The first and third of these proofs make use of classical properties. The second proof is amenable to a 
+constructive formalization as shown in the following function in \texttt{ARS-NewmansLemma.agda}:
 
-Three proofs are given in \terese of Newman's Lemma (Theorem 1.2.1). The first and third of 
-these proofs we found to rely on classical principles. The second proof was amenablbe to a 
-constructive formalization which we carried out in the function
+\verb|NewmansLemma : R isSN → R isWCR → R isCR|.
 
-\verb|NewmansLemma : R isSN → R isWCR → R isCR| \footnotemark[2]
-\footnotetext[2]{\texttt{ARS-NewmansLemma.agda}}
-We show in section \ref{sec:Implications} that $\SN$ implies $\SM$, and it is from this implication 
-that we produce a new generalization of Newman's lemma. Every relation with the properties 
-$\SM$ and $\WCR$ has the property of $\CR$. This holds true both locally and globally as we show in:
+\sacomment{This is a point where it may be useful to examine MF earlier. However, the alternative is to discuss the generalization of NL in the section on implications.}
 
-\verb|LocalNewmansLemmaRecurrent : R isWCR → SM ⊆ CR| \footnotemark[2]
+We show in Section \ref{sec:Implications} a generalization of Newman's Lemma. \sacomment{Delete this comment when that generalization is written.}
 
-and \verb|GlobalNewmansLemmaRecurrent : R isWCR → R isSM → R isCR| \footnotemark[2]
+The formalizations of the remaining theorems are all found in \texttt{ARS-Theorems.agda}. 
+\subsubsection{Theorem 1.2.2}
+There are three parts to this theorem. 
+\begin{description}
+    \item[($i$)] $\gCR \implies \gNPe \implies \gUN$
+    \item[($ii$)] $\gWN \land \gUN \implies \gCR$  
+    \item[($iii$)] $\gCRs \implies \gCR$
+\end{description}
 
-The formalization of the proof that $\WCR \land \WN \land \Inc \implies \SN$ proved particularly difficult. 
-As already mentioned, we substituted out the property $\Inc$ for the property $\RP$ however 
-we found that we still require a classical principle in order for the proof to hold (as can be seen in the type of our proof):
-\verb|iii : R isWN → R isWCR → R isRP- → dec (SN) → R isSN| \footnotemark[3] \footnotetext[3]{\texttt{ARS-Theorems.agda}}
-The classical property $\decSN$ is a property that states it is decidable whether a given 
-element has the property of being $\SN$. \sacomment{Should say more on this proof.}
+($i$) is formalized in:
+\begin{itemize}
+    \item \verb|CR→NP : R isCR → R isNP₌|
+    \item \verb|NP→UN : R isNP₌ → R isUN|
+    \item \verb|CP→UN : R isCR → R isUN|
+\end{itemize}
 
-In the next section we take a closer look at the properties we found most crucial for termination and confluence, and the interrelationship between them.
+($ii$) is formalized in:
+\begin{itemize}
+    \item \verb|ii : R isWN × R isUN → R isCR|
+\end{itemize}
+In our formalization we show that $\gWN \land \gUNto \implies \gCR$ is true and so provide a generalization of ($ii$) as $\gUN \implies \gUNto$.
+
+($iii$) is formalized in:
+\begin{itemize}
+    \item \verb|iii : subcommutative R → R isCR|
+\end{itemize}
+
+\subsubsection{Theorem 1.2.3}
+There are four parts to this theorem. 
+\begin{description}
+    \item[($i$)] $\gWN \and \gUN \implies \gBP$
+    \item[($ii$)] $\gBP \land \gInc \implies \gSN$  
+    \item[($iii$)] $\gWCR \land \gWN \land \gInc \implies \gSN$
+    \item[($iv$)] $\gCR \iff \gCR$ ($\implies$ only holds if the ARS is countable.)
+\end{description}
+($i$) is formalized in: 
+\begin{itemize}
+    \item \verb|i : R isWN → R isUN → R isBP|
+    \item \verb|i→ : R isWN → R isUN→ → R isBP|
+\end{itemize}
+In $\mathtt{i\to}$ we again provide a generalization by using $\gUNto$ rather than $\gUN$.
+
+A near formalization of ($ii$) is provided in: 
+\begin{itemize}
+    \item \verb|iiSeq : R isWN → R isUN → R isRP → isWFseq- (~R R)|
+\end{itemize}
+\sacomment{Explain here why have we provided a near formalization rather than sticking to the same properties}
+
+($iii$) is formalized in: 
+\begin{itemize}
+    \item \verb|iii : R isWN → R isWCR → R isRP- → dec (SN) → R isSN|
+\end{itemize}
+As can be seen we have substituted $\gInc$ with $\gRPm$ which generalizes this theorem. We have also included the assumption that $\gSN$ 
+is decidable \sacomment{Is decidability being discussed elsewhere in the paper that we can reference here.} as this property enables us 
+to construct a witness for an element that either does or does not have the property $\SN$. Such a witness was necessary for our proof. \sacomment{More to say on this theorem?}
+
+The reverse implication of ($iv$) is formalized in: 
+\begin{itemize}
+    \item \verb|iv : R isCP → R isCR|
+\end{itemize}
+We did not formalize $\gCR \to gCP$ as it requires the ARS to be countable \sacomment{More to say?}.

### 2025-02-23 Relations/Paper/Implications.tex
Pre call upload

@@
 
-From the perspective of programming language theory, the two properties of abstract rewriting 
-systems that are most interesting are $\SN$ and $\CR$. The following hierarchies 
-show chains of implications starting from these properties.
+% From the perspective of programming language theory, the two properties of abstract rewriting 
+% systems that are most interesting are $\SN$ and $\CR$. The following hierarchies 
+% show chains of implications starting from these properties.
+As discussed in Subsection \ref{subsec:def} we put forward $\RP$ as an alternative for $\Inc$. It is through examining $\RP$ that 
+we came to the below definitions.
 
-\begin{definition} The folowing definitions relate to being minimal. Let $A$ and $R$ be as above, and let $a \in A$.
+\begin{definition}\label{def:mf}  Let $A$ and $R$ be as above, and let $a \in A$.
     \begin{description}
@@
 
-Again, we found that there was a strong interrelationship between the properties, captured in Figure \ref{fig:conf-hierarchy}, which are explored in Section \ref{sec:Implications}.
-
-\begin{figure}[h] 
-    \centering
-
-        \begin{tikzpicture}[auto,
-          arrowstyle/.style={->, line width=1pt, >={Latex[length=3mm, width=2mm]}, shorten >=2pt}]
-          % A box style
-          \tikzstyle{boxnode} = [draw, rectangle, text centered,minimum width=1.2cm, inner sep=3pt]
-
-          % Place the nodes vertically (top to bottom)
-          \node (Confluent) [boxnode] at (-4,0) {$\CR$};
-          \node (RP)        [boxnode, right=.5cm of Confluent] {$\MP$};
-          \node (WN)        [boxnode, right=.5cm of RP] {$\NP$};
-          \node (UN)        [boxnode, right=.5cm of WN] {$\UNto$};
-
-          % Draw arrows downwards
-          \draw[arrowstyle] (Confluent) -- (RP);
-          \draw[arrowstyle] (RP) -- (WN);
-          \draw[arrowstyle] (WN) -- (UN);
-
-          \end{tikzpicture}
-          \caption{A hierarchy of confluent properties.}
-          \label{fig:conf-hierarchy}
-
-\end{figure}
-We found that there was a strong interrelationship between the normalizing properties and the minimal properties. This relationship is 
-captured in Figure \ref{fig:norm-hierarchy}.
-
-\begin{figure}[h]   
-    \centering
-        \begin{tikzpicture}[auto,
-            arrowstyle/.style={->, line width=1pt, >={Latex[length=3mm, width=2mm]}, shorten >=2pt}]
-            % A box style
-            \tikzstyle{boxnode} = [draw, rectangle, text centered,minimum width=1.2cm, inner sep=3pt]   
-            % Define the nodes
-            \node (SN) [boxnode] at (4,0) {$\SN$};
-            \node (WN) [boxnode, above right=0.5cm and 0.5cm of SN] {$\WN$};
-            \node (SR) [boxnode, below right=0.5cm and 0.5cm of SN] {$\SM$};
-            \node (WR) [boxnode, below right=0.5cm and 0.5cm of WN] {$\WM$};
-
-            % Draw the arrows to form a diamond
-            \draw [arrowstyle] (SN) -- (WN);
-            \draw [arrowstyle] (SN) -- (SR);
-            \draw [arrowstyle] (WN) -- (WR);
-            \draw [arrowstyle] (SR) -- (WR);
-        \end{tikzpicture}
-        \caption{A hierarchy of normalizing and minimal properties.}
-        \label{fig:norm-hierarchy}
-\end{figure}
-
-The implications will be explored in detail in Section \ref{sec:Implications}.
-
-Proposition \ref{prop:SMRP} connects $\SM$ with $\RP$ and $\BP$. \sacomment{Need to relate SM and SMseq. Probably define SMseq and metion 
+\sacomment{Need to relate SM and SMseq. Probably define SMseq and metion 
 we can only prove this for SMseq.}
@@
 
-A trivial implication not captured in the above figure is covered in Proposition \ref{prop:nftomf}. 
+Trivially, the following also holds. 
 \begin{proposition}\label{prop:nftomf}
@@
 \end{proof}
+
+With these minimal definitions we can see the taxonomy of concepts that relate to termination and confluence.
 
@@
         % Define the nodes
-        \node (SN) [boxnode] at (4,0) {$\SN$};
-        \node (WN) [boxnode, above right=0.5cm and 0.5cm of SN] {$\WN$};
-        \node (SR) [boxnode, below right=0.5cm and 0.5cm of SN] {$\SM$};
-        \node (WR) [boxnode, below right=0.5cm and 0.5cm of WN] {$\WM$};
+        \node (NF) [boxnode] at (3,0) {$\NF$};
+        \node (MF) [boxnode] at (3,-1) {$\MF$};
+        \node (SN) [boxnode] at (5,0) {$\SN$};
+        \node (SR) [boxnode] at (5,-1) {$\SM$};
+        \node (WN) [boxnode] at (7,0) {$\WN$};
+        \node (WR) [boxnode] at (7,-1) {$\WM$};
 
         % Draw the arrows to form a diamond
+        \draw [arrowstyle] (NF) -- (SN);
+        \draw [arrowstyle] (NF) -- (MF);
+        \draw [arrowstyle] (MF) -- (SR);
         \draw [arrowstyle] (SN) -- (WN);
@@
 
-The classical property of being minimally decidable is required to complete the implcation 
-from $\SN$ to $\WN$, as can be seen in our formalization
+The implications in this diagram are formalized in \texttt{ARS-Implications.agda}. The classical property of being minimally decidable is 
+required to complete the implcation from $\SN$ to $\WN$, as can be seen in our formalization
 
-\verb|SNdec→WN : (~R R) isMinDec → SN ⊆ WN| \footnotemark[1]
+\verb|SNdec→WN : (~R R) isMinDec → SN ⊆ WN|
 
@@
 
-The following tables show which combination of these properties implies a property higher in the hierarchy. Where a combination 
-does not imply a higher property an explanatory counterexample is given. The counterexamples referenced are shown below the tables in subsection \ref{subsec:counterexamples}.
+We are interested in seeing which combination of properties a relation requires in order to be complete (that is, $\CR$ and $\SN$). 
+The following tables show either that a given combination is complete, or the appropriate counterexample which demonstrates why 
+those properties do not provide a property higher on the taxonomical hierarchy.
 
-The first table explores where the properties hold locally, the second explores where the properties hold globally. The proofs that the 
-following implications hold are primarily found in \texttt{ARS-implications.agda} unless they have been proven as part of the formalization 
-of \terese, in which case they will be found in either \texttt{ARS-thoerems.agda} or \texttt{ARS-NewmansLemma.agda}.
+The first table explores where the properties hold locally, the second explores where the properties hold globally. Counterexamples in the 
+first table assume $\WCR$ and in the second table assume $\gWCR$.
 
-\sacomment{When the table and CE are finished, write an explanation that the CE to the local table 
-assume local WCr and the global table CEs assume global WCR!}
-\sacomment{UPDATE COUNTEREXAMPLES WHEN CE SECTION FINISHED}
 \renewcommand*{\thefootnote}{\fnsymbol{footnote}}
@@
 \verb|isWN∧isSM→isSN : R isWN → R isSM → R isSN| \footnotemark[1]
+
+that $\SN$ implies $\SM$, and it is from this implication 
+that we produce a new generalization of Newman's lemma. Every relation with the properties 
+$\SM$ and $\WCR$ has the property of $\CR$. This holds true both locally and globally as we show in:
+
+\verb|LocalNewmansLemmaRecurrent : R isWCR → SM ⊆ CR| \footnotemark[2]
+
+and \verb|GlobalNewmansLemmaRecurrent : R isWCR → R isSM → R isCR| \footnotemark[2]
+
+\sacomment{We should remember that If global WCR and local SM implies local CR, then if we also have local WN, we get local SN.}

### 2025-02-23 Relations/Paper/Implications.tex
call update

@@
 
-We are interested in seeing which combination of properties a relation requires in order to be complete (that is, $\CR$ and $\SN$). 
+We are interested in seeing which combination of properties a relation requires in order to be complete (that is, $\gCR$ and $\gSN$). 
 The following tables show either that a given combination is complete, or the appropriate counterexample which demonstrates why 
@@
     \hline
-    $\UNto$ &  CE-\ref{CE:4}, CE-\ref{CE:12}     & CE-\ref{CE:4}, CE-\ref{CE:7}       & CE-\ref{CE:4} , CE-\ref{CE:9}          & CE-\ref{CE:4}, CE-\ref{CE:4}            & $\CR$\footnotemark[1] , $\SN$ \\
+    $\UNto$ &  CE-\ref{CE:4}, CE-\ref{CE:12}     & CE-\ref{CE:4}, CE-\ref{CE:7}       & $\CR$\footnotemark[1] , CE-\ref{CE:9}          & $\CR$\footnotemark[1] , CE-\ref{CE:4}            & $\CR$\footnotemark[1] , $\SN$ \\
     \hline
-    $\NP$ & CE-\ref{CE:10},CE-\ref{CE:9}      & $\CR$, CE-\ref{CE:7}    & CE-\ref{CE:11} , CE-\ref{CE:9}          & $\CR$, $\SN$      & $\CR$\footnotemark[2] , $\SN$ \\
+    $\NP$ & CE-\ref{CE:10},CE-\ref{CE:9}      & $\CR$, CE-\ref{CE:7}    & $\CR$\footnotemark[1]  , CE-\ref{CE:9}          & $\CR$, $\SN$      & $\CR$\footnotemark[2] , $\SN$ \\
     \hline
@@
     \hline
-    \rowcolor{gray!30}     & $\WM$         & $\WN$         & $\SM$             & $\SMandWN$        & $\SN$ \\
+    \rowcolor{gray!30}     & $\gWM$         & $\gWN$         & $\gSM$             & $\gSMandWN$        & $\gSN$ \\
     \hline
-    $\UNto$ &  CE-\ref{CE:2}, CE-\ref{CE:9}     & $\CR$, CE-\ref{CE:7}    & $\CR$\footnotemark[1] , CE-\ref{CE:9}          & $\CR$, $\SN$      & $\CR$\footnotemark[2] , $\SN$ \\
+    $\gUNto$ &  CE-\ref{CE:2}, CE-\ref{CE:9}     & $\gCR$, CE-\ref{CE:7}    & $\gCR$\footnotemark[1] , CE-\ref{CE:9}          & $\gCR$, $\gSN$      & $\gCR$\footnotemark[2] , $\gSN$ \\
     \hline
-    $\NP$ & CE-\ref{CE:3} , CE-\ref{CE:9}      & $\CR$, CE-\ref{CE:7}    & $\CR$\footnotemark[1] , CE-\ref{CE:9}          & $\CR$, $\SN$      & $\CR$\footnotemark[2] , $\SN$ \\
+    $\gNP$ & CE-\ref{CE:3} , CE-\ref{CE:9}      & $\gCR$, CE-\ref{CE:7}    & $\gCR$\footnotemark[1] , CE-\ref{CE:9}          & $\gCR$, $\gSN$      & $\gCR$\footnotemark[2] , $\gSN$ \\
     \hline
-    $\MP$ & $\CR$ , CE-\ref{CE:9}    & $\CR$, CE-\ref{CE:7}    & $\CR$\footnotemark[2] , CE-\ref{CE:9} & $\CR$, $\SN$      & $\CR$\footnotemark[2] , $\SN$ \\
+    $\gMP$ & $\gCR$ , CE-\ref{CE:9}    & $\gCR$, CE-\ref{CE:7}    & $\gCR$\footnotemark[2] , CE-\ref{CE:9} & $\gCR$, $\gSN$    & $\gCR$\footnotemark[2] , $\gSN$ \\
     \hline
-    $\CR$   & $\CR$, CE-\ref{CE:9}     & $\CR$, CE-\ref{CE:7}     & $\CR$, CE-\ref{CE:9}        & $\CR$, $\SN$      & $\CR$ , $\SN$ \\
+    $\gCR$   & $\gCR$, CE-\ref{CE:9}     & $\gCR$, CE-\ref{CE:7}     & $\gCR$, CE-\ref{CE:9}        & $\gCR$, $\gSN$      & $\gCR$ , $\gSN$ \\
     \hline
@@
 \end{table}
-\footnotetext[1]{This implication also requires global $\WCR$.}
-\footnotetext[2]{This implication also requires either global $\WCR$ or the classical property required to go from 
+\footnotetext[1]{This implication also requires $\gWCR$.}
+\footnotetext[2]{This implication also requires either $\gWCR$ or the classical property required to go from 
 $\SN \to \WN$ or $\SM \to \WM$.}
@@
 
-\sacomment{Need to update the tables with appropriate symbols for global and local. Colour for first row and column?}
+\subsubsection{Generalized Newman's Lemma}\label{subsec:newnewman}
+One interesting outcome from investigating the normalization taxonomy was a generalization of Newman's Lemma.
 
-\sacomment{Rewrite the below to reflect changes to the table.}
-The tables show a number of changes when moving from properties holding locally to globally. 
-Globally $\WN \land \UNto \implies \CR$ holds whereas it does not locally. Similarly, $\SM \land \WN \implies \SN$ holds 
-globally but not locally.
+\begin{proposition}
+    $\gWCR \land \SM \implies \CR$
+\end{proposition}
+\begin{proof}
+    See, \verb|LocalNewmansLemmaRecurrent : R isWCR → SM ⊆ CR|
+\end{proof}
 
-Theorem 1.2.2 ii in \terese is the claim that $\WN \land \UN \implies \CR$ holds, and we formalize this in
+This proof follows the same steps as the second proof of Newman's Lemma found in \terese, but 
+uses the generalization $\SM$ of $\SN$.
 
-\verb|ii : R isWN × R isUN → R isCR| \footnotemark[3]
-
-We have modestly generalized this theorem by showing that $\WN \land \UNto \implies \CR$ holds (and indeed this is the basis for our proof of the theorem). 
-Counterexample \sacomment{REF HERE} shows why this implication cannot hold when the properties are only local. Our proof is in the function:
-
-\verb|UN→∧WN→CR : R isUN→ → R isWN → R isCR| \footnotemark[1]
-
-To show that $\SM \land \WN \implies \SN$ we built on our proof that locally $\SM \land \WN \land \NP \implies \SN$. If $\WN$ applies 
-globally then our proof no longer requires the property $\NP$. This progression of proofs can be seen in the functions:
+% The tables show a number of changes when moving from properties holding locally to globally. 
+% Globally $\WN \land \UNto \implies \CR$ holds whereas it does not locally. Similarly, $\SM \land \WN \implies \SN$ holds 
+% globally but not locally. 
+\subsection{Relation between $\SM$, $\WN$, and $\SN$}
+One key takeaway from the tables is that we obtain completeness when we have the properties $\SM$, $\WN$, and $\WN$. We also 
+obtain completeness when we have $\gWN$ and $\gSM$. 
+To show that $\gSM \land \gWN \implies \gSN$ we built on our proof that $\SM \land \WN \land \NP \implies \SN$. If $\gWN$ holds 
+then our proof no longer requires the property $\NP$. This progression of proofs can be seen in the functions:
 
@@
 
-\verb|isWN∧isSM→isSN : R isWN → R isSM → R isSN| \footnotemark[1]
+\verb|isWN∧isSM→isSN : R isWN → R isSM → R isSN|
 
-that $\SN$ implies $\SM$, and it is from this implication 
-that we produce a new generalization of Newman's lemma. Every relation with the properties 
-$\SM$ and $\WCR$ has the property of $\CR$. This holds true both locally and globally as we show in:
-
-\verb|LocalNewmansLemmaRecurrent : R isWCR → SM ⊆ CR| \footnotemark[2]
-
-and \verb|GlobalNewmansLemmaRecurrent : R isWCR → R isSM → R isCR| \footnotemark[2]
-
+\sacomment{Are there any other features of the table that we would like to draw out?}
 \sacomment{We should remember that If global WCR and local SM implies local CR, then if we also have local WN, we get local SN.}

### 2025-02-23 Relations/Paper/Well-foundedness.tex
work

@@
 \section{Well-foundedness}
+
+\newcommand{\isWFacc}{\mathtt{isWFacc}}
+\newcommand{\isWFseq}{\mathtt{isWFseq}}
+\newcommand{\isWFmin}{\mathtt{isWFmin}}
+\newcommand{\isWFaccm}{\mathtt{isWFacc-}}
+\newcommand{\isWFseqm}{\mathtt{isWFseq-}}
+\newcommand{\isWFminm}{\mathtt{isWFmin-}}
+\newcommand{\then}{\Longrightarrow}
 \label{sec:Well-foundedness}
+
+An abstract reduction $\to_R$ is strongly normalizing
+if and only if the converse relation is well-founded.
+In this section, we will compare several definitions of well-foundedness.
+They will be based on the following notions.
+
+\begin{definition}
+  Let $R \subseteq A \times A$.
+  \begin{enumerate}
+    \item $P \subseteq A$ is \emph{inductive}
+    if, for each $x \in A$, $(\forall y. Ryx \to y \in P)$ implies $x \in P$.
+
+    \item $x \in A$ is \emph{accessible} if $x \in P$ for each inductive $P$.
+
+    \item $x \in A$ is \emph{$P$-minimal} if $x \in P$ and for all $y$,
+    $Ryx$ implies $y \notin P$.
+
+    \item $s : \nat \to A$ is \emph{$R$-decreasing} if for all $k$, $(s(k+1),s(n)) \in R$.
+  \end{enumerate}
+\end{definition}
+
+In TeReSe, well-foundedness is defined in the classical way,
+as the absence of an infinite $R$-decreasing sequence.
+Translating this directly into type theory yields the condition
+\[\isWFseqm : \lnot \big(\exists s : \nat \to A \forall k : \nat. (s(k+1),s(k)) \in R \big) \]
+
+Constructively, this is not a useful hypothesis, as it does not provide any positive computational content and requires an explicit sequence to be given.
+
+A stronger formulation asserts that, for any sequence, there exists an element
+in the sequence that does not reduce to the next one.  This yields
+\[\isWFseq : \forall s : \nat \to A \exists k : \nat. (s(k),s(k+1)) \notin R \]
+
+These are classically equivalent, but not constructively so.
+Indeed, we have $\isWFseq$ implying $\isWFseqm$, but not vice versa.
+
+Another classical formulation of well-foundedness
+asserts that every non-empty subset
+contains a minimal element.  That is,
+\[ \isWFmin : \forall P \subseteq A. P \neq \emptyset \to \exists x \in P. (\forall y. Ryx \to y\notin P) \]
+
+While classically equivalent to the above, see  \cite{Terese, Exercise 1.11?},
+constructively we only have the implication $\isWFmin \then \isWFseq$.
+
+The canonical constructive definition is that
+every inductive predicate is universally true.
+This is constructively equivalent to the statement that every element
+is accessible.  In Agda, these concepts are encoded as follows.
+{\small
+\begin{verbatim}
+  data _-accessible : 𝓟 A where
+    acc : ∀ {x : A} → (∀ y → R y x → _-accessible y) → _-accessible x
+
+  _isWFacc : Set
+  _isWFacc = ∀ (x : A) → x ∈ _-accessible
+
+  _-inductive_ : 𝓟 A → Set
+  _-inductive_ φ = ∀ x → (∀ y → R y x → φ y) → φ x
+
+  _isWFind : Set₁
+  _isWFind = ∀ (φ : 𝓟 A) → _-inductive_ φ → ∀ x → φ x
+\end{verbatim}
+}
+
+\greyout{ SN does not imply WN, we can now discuss this in detail.
+Notice that $x \in WFmin$ certainly implies WN, because we can ask for
+the minimal element of the predicate $P(y) = x \mstep y$
+(the reduction graph of $x$).  Note that this subset is nonempty because $P(x)$ holds.
+}
+
+We have now seen five notions of a well-founded relations, only two of which
+appear to be logically equivalent.
+
+This raises several questions.
+\begin{itemize}
+\item Are all these notions truly distinct?  If one cannot furnish a proof of implication,
+can we provide a counterexample?
+\item Under what hypotheses do the implications become provable?
+\item How ``admissible'' are these hypotheses, and how often can we hope for them to be valid?
+\end{itemize}
+
+The situation of constructing counterexamples is complicated by the fact that, for all
+\emph{definable} predicates, the notions do coincide.  (We have not formalized this,
+but see for example \cite{Berardi}, $A$-translation.)
+So there is little hope to separate these notions with explicit counterexamples.
+Rather, we could attempt to show that one does not imply the other by proving that
+such an implication would yield a ``constructive taboo'': a proposition known to be
+unprovable without addtional classical assumptions.
+
+These questions motivated us to take a closer look at the issue of well-foundedness.
+Our analysis revealed a number of additional related hypotheses, having a complex
+network of relations.  These are displayed in Figure \ref{f:wf}.
+
+Let us elaborate each of these further.
+
+First, we noticed that, analogously to $\isWFseq$ and $\isWFseqm$, there are weaker notions of
+$\isWFacc$ and $\isWFmin$.  These are
+\begin{align*}
+\isWFaccm &= \cdots \\
+\isWFminm &= \cdots \\
+\end{align*}
+
+Each notion of those listed trivially implies the weaker one.
+
+Moreover, we can show that \apcomment{add the ``easy'' relationships from the old report.}
+These elementary implications are summarized in the following diagram.
+
+\apcomment{insert the diagram with X implying X- downward, and chains horizontally,
+as X ranges of isWFacc, isWFind, isWFseq, isWFmin}
+
+Since $\isWFmin$ appears to be stronger than the rest, one may wonder whether
+it can be weakened.  Indeed, in the classical proof of the implication
+$\isWFacc \to \isWFmin$, the predicate $P$ is instantiated by the \emph{complement}
+of a given one.
+
+This yields the following two :
+  \begin{align*}
+    isWFminDNE
+    isWFmiEM
+  \end{align*}
+
+Surprisingly, although $\isWFmin$ seems very strong, it is not sufficient to
+conclude $\isWFacc$.  The culprit is in the conclusion, that the predicate becomes
+negated twice.
+
+This suggests an alternative restriction, where one directly works with the
+complement of a given predicate.  This leads us to two more variations.
+\begin{align*}
+  isWFmin+\\
+  isWFminRed+
+\end{align*}
+
+Of course, each of these also has weaker versions,
+with $\lnot\lnot$ in front of the existential quantifier.
+
+\apcomment{Should collect all these definitions in one table.
+Display this table next to the diagram showing all of the established implications.
+Perhaps do the same in section 4 as well...     }
+
+\subsection{Other things to say}
+\begin{itemize}
+  \item $\isWFmin$ splits into the restrictions on the predicate and the complement
+  \item The distinction between $\isWFseq$ and $\isWFmin$ concerns
+  the non-determinism/choice/coreductivity of the predicate.
+  With sequences, the path is deterministic and we don't have to
+  search for a reduct where the predicate retains its truth value.
+
+  But in case of minimality, it is not known how to find the successor
+  where the truth condition is preserved.
+
+  One remedy is to ask for this choice function directly --- this yields
+  the coreductivity hypothesis.
+
+  The other remedy is finite branching.
+
+  \item Generally, iswFMin EM will imply isWFseq.  This should be easy to prove.
+
+  \greyout{It should also imply/be implied by min+cor, maybe }
+
+\end{itemize}

### 2025-02-23 Relations/Paper/Definitions.tex
call update

@@
 
-\begin{definition}
+\begin{definition} \hfill
     \begin{description}
@@
         $Rab \to |a| < |b|$  
-        \item[$a \in \CP$] \sacomment{Need a definition of cofinality here}
     \end{description}
@@
 
-Having a "size function" that maps to the natural numbers is computationally taxing to satisfy. 
-Futher, it takes us outside of pure relational theory. The following definitions are for properties which allow us to forgo $\Inc$, for further discussion see Subsection \ref{subsec:def}.
+Having a size function that maps to the natural numbers is computationally taxing to satisfy. 
+Further, it takes us outside of purely relational theory. The following definitions are for properties which allow us to forgo $\Inc$, for further discussion see Subsection \ref{subsec:def}.
 \begin{definition} \label{def:rp} Let $A$ and $R$ be as above, and let $a \in A$.
@@
         \item[$R \models \RPm$] \emph{$R$ has the weak recurrence property} if for every increasing sequence $s$ with bound $b$ there exists an $i \in \nat$ such that $b \mstep s (i)$.
+
         \item[$R \models \RP$] \emph{$R$ has the recurrence property} if every bounded, increasing sequence $s$ with an $s$-bound, there exists an $i \in \nat$ such that 
-        $s (i) \in \MF$. See Definition \ref{def:mf}. 
+        $s (i) \mstep x \implies x \mstep s (i)$ for all $x\in A$. See Definition \ref{def:mf}. 
     \end{description}
@@
 \subsection{Finitely branching (\texttt{FinitelyBranching.agda})}
-\sacomment{This property is what makes a lot of the classical properties valid which otherwise wouldn't be. Valid in most interesting rewriting systems. Most 
-programming languages will satisfy finite branching.}
+
 \begin{definition} Let $A$ and $R$ be as above, and let $a \in A$.
     \begin{description}
-        \item[$a \in \FB$] \emph{$a$ is finitely branching} if there is a finite amount of  $b \in A$ such that $a \rstep b$. 
+        \item[$a \in \FB$] \emph{$a$ is finitely branching} if there is a finitely many $b \in A$ such that $a \rstep b$.  
     \end{description}
 \end{definition}
+Our Agda formulation of the above definition makes use of the List type constructor. 
+\verb|FB a = Σ[ xs ∈ List A ] (∀ b → R b a → b ∈List xs)|
+
+$\FB$ is a property that plays an important role in our discussion of well-foundedness in Section \ref{sec:Well-foundedness}.

### 2025-02-23 Relations/Paper/Formalization.tex
call update

@@
 \begin{itemize}
-    \item $\SN$ : We make use of the well-founded defintion, rather than the finite reduction sequence definition.
+    \item $\SN$ : We make use of the well-founded definition, rather than the finite reduction sequence definition.
     \item $\NPe$ : We use the equivalent $\NP$ definition. 
@@
 As already mentioned, the $\Inc$ property was one we wanted to move away from. We saw that $\Inc$ was being used only in Theorem 1.2.3 
-and that the crucial facet of $\Inc$ for the proof of the theorem was that every sequence has a bound \sacomment{is this the correct characterization?}. 
-So we established that the properties in Definition \ref{def:rp} were sufficient for the proving the theorems. This in turn led us to examining 
-a generalization of a normal form, the minimal form. We explore this further in Section \ref{sec:Implications}.
+and that the crucial facet of $\Inc$ for the proof of the theorem was that no $R$-increasing 
+sequence can have an upper bound.
+We established that the properties $\RP$ and $\RPm$ were sufficient for the proving the theorems. This in turn led us to 
+examine the condition in $\RP$ more closely. This condition provides a generalization of the notion of normal form, 
+which we analyze in detail in Section \ref{sec:Implications}. \sacomment{Try and get this para to flow better.}
 
@@
 
-\sacomment{This is a point where it may be useful to examine MF earlier. However, the alternative is to discuss the generalization of NL in the section on implications.}
-
-We show in Section \ref{sec:Implications} a generalization of Newman's Lemma. \sacomment{Delete this comment when that generalization is written.}
+We show in Subsection \ref{subsec:newnewman} a generalization of Newman's Lemma using $\MF$.
 
@@
 \end{itemize}
-In our formalization we show that $\gWN \land \gUNto \implies \gCR$ is true and so provide a generalization of ($ii$) as $\gUN \implies \gUNto$.
+\sacomment{Make below comment tidier}
+Note that we have provided a proof with the weaker hypothesis of $\gUNto$.
 
@@
 \subsubsection{Theorem 1.2.3}
+The following definition is required for this theorem.
+\begin{definition} Let $a \in A$.
+    \begin{description}
+        \item[$a \in CP_R$] \emph{$a$ has the cofinality property} if there exists a 
+        (not necessarily strictly) increasing sequence starting from $a$ such that every
+        reduct of $a$ reduces to some element of the sequence.
+    \end{description}
+\end{definition}
+
 There are four parts to this theorem. 
@@
     \item[($iii$)] $\gWCR \land \gWN \land \gInc \implies \gSN$
-    \item[($iv$)] $\gCR \iff \gCR$ ($\implies$ only holds if the ARS is countable.)
+    \item[($iv$)] $\gCR \iff \gCP$ ($\gCR \implies \gCP$ only holds if the ARS is countable.)
 \end{description}
@@
 
+\sacomment{neeed to define CP}
 The reverse implication of ($iv$) is formalized in: 

### 2025-02-23 Relations/Paper/Implications.tex
call update

@@
 
-\sacomment{Need to relate SM and SMseq. Probably define SMseq and metion 
+\sacomment{Need to relate SM and SMseq. Probably define SMseq and mention 
 we can only prove this for SMseq.}
@@
 The implications in this diagram are formalized in \texttt{ARS-Implications.agda}. The classical property of being minimally decidable is 
-required to complete the implcation from $\SN$ to $\WN$, as can be seen in our formalization
+required to complete the implication from $\SN$ to $\WN$, as can be seen in our formalization
 

### 2025-02-23 Relations/Paper/Definitions.tex
Figure for WF

@@
         \item[$R \models \RPm$] \emph{$R$ has the weak recurrence property} if for every increasing sequence $s$ with bound $b$ there exists an $i \in \nat$ such that $b \mstep s (i)$.
-
-        \item[$R \models \RP$] \emph{$R$ has the recurrence property} if every bounded, increasing sequence $s$ with an $s$-bound, there exists an $i \in \nat$ such that 
+        \item[$R \models \RP$] \emph{$R$ has the recurrence property} if for every bounded, increasing sequence $s$ with an $s$-bound, there exists an $i \in \nat$ such that 
         $s (i) \mstep x \implies x \mstep s (i)$ for all $x\in A$. See Definition \ref{def:mf}. 

### 2025-02-23 Relations/Paper/Formalization.tex
Figure for WF

@@
 
-As already mentioned, the $\Inc$ property was one we wanted to move away from. We saw that $\Inc$ was being used only in Theorem 1.2.3 
-and that the crucial facet of $\Inc$ for the proof of the theorem was that no $R$-increasing 
+As already mentioned, the $\Inc$ property has undesired requirements. $\Inc$ is used only in Theorem 1.2.3 
+and the crucial facet of $\Inc$ for the proof of the theorem is that no $R$-increasing 
 sequence can have an upper bound.
-We established that the properties $\RP$ and $\RPm$ were sufficient for the proving the theorems. This in turn led us to 
+We established that the properties $\RP$ and $\RPm$ were sufficient for proving the theorem (see Subsection \ref{subsec:theorems}). This in turn led us to 
 examine the condition in $\RP$ more closely. This condition provides a generalization of the notion of normal form, 
-which we analyze in detail in Section \ref{sec:Implications}. \sacomment{Try and get this para to flow better.}
+which we analyze in detail in Section \ref{sec:Implications}.
 
@@
 
-\subsection{Theorems}
+\subsection{Theorems}\label{subsec:theorems}
 \subsubsection{Newman's Lemma}
@@
 \begin{description}
-    \item[($i$)] $\gWN \and \gUN \implies \gBP$
+    \item[($i$)] $\gWN \land \gUN \implies \gBP$
     \item[($ii$)] $\gBP \land \gInc \implies \gSN$  
@@
 
-A near formalization of ($ii$) is provided in: 
+A formalization of ($ii$) is provided in: 
 \begin{itemize}
@@
 \end{itemize}
-\sacomment{Explain here why have we provided a near formalization rather than sticking to the same properties}
+This is a fundamentally classical result, and so the result is only classically equivalent to $\gSN$.
+\sacomment{Double check the above explanation.}
 
@@
 As can be seen we have substituted $\gInc$ with $\gRPm$ which generalizes this theorem. We have also included the assumption that $\gSN$ 
-is decidable \sacomment{Is decidability being discussed elsewhere in the paper that we can reference here.} as this property enables us 
+is decidable as this property enables us 
 to construct a witness for an element that either does or does not have the property $\SN$. Such a witness was necessary for our proof. \sacomment{More to say on this theorem?}
 
-\sacomment{neeed to define CP}
 The reverse implication of ($iv$) is formalized in: 
@@
 \end{itemize}
-We did not formalize $\gCR \to gCP$ as it requires the ARS to be countable \sacomment{More to say?}.
+We did not formalize $\gCR \to \gCP$ as it requires the ARS to be countable \sacomment{Add this proof to future todo}.

### 2025-02-23 Relations/Paper/Implications.tex
Figure for WF

@@
 % show chains of implications starting from these properties.
-As discussed in Subsection \ref{subsec:def} we put forward $\RP$ as an alternative for $\Inc$. It is through examining $\RP$ that 
-we came to the below definitions.
+As discussed in Subsection \ref{subsec:def} we put forward $\RP$ as an alternative property for $\Inc$. It is through examining $\RP$ that 
+we came to the definitions below.
 
@@
         \item[$a \in \WM_R$] \emph{$a$ is weakly minimalizing} if $a \mstep b$ for some $b \in \MF_R$.
+        \item[$a \in \SMseq_R$] \emph{$a$ is sequentially strongly minimalizing} if for every $R$-increasing sequence $s$ starting at $a$, there exists 
+        an $i \in \nat$ such that $s (i) \in \MF$. 
         \item[$a \in \SM_R$]  \emph{$a$ is strongly minimalizing} if either $a \in MF_R$, or every element one $R$ step from $a$ is also strongly minimalizing.
@@
 
-\sacomment{Need to relate SM and SMseq. Probably define SMseq and mention 
-we can only prove this for SMseq.}
+We show that $\SM \implies \SMseq$, however $\SMseq$ is only classically equivalent to $\SM$. The 
+following proposition relates these new definitions with our previous $\RP$ definitions.
 \begin{proposition}\label{prop:SMRP}
-    $SM \leftrightarrow RP \land BP$
+    $SMseq \leftrightarrow RP \land BP$
 \end{proposition}
@@
 \begin{proposition}\label{prop:nftomf}
-    $a\in NF_R \implies a \in MF_R$ 
+    $\NF \implies \MF$ 
 \end{proposition}    
@@
 
-\sacomment{Are we going to define this property here or elsewhere?}
-
-The isMinDec property states that all elements either have a relation to some other element, or 
+The isMinDec property \sacomment{refer to list of classical properties here} states that all elements either have a relation to some other element, or 
 there is no other element to which they have a relation. If the element relates to no other element then it is terminating 
-and so trivially $\WN$. If the element does relate to some other element $y \in A$, then we recursively apply our claim to 
-$y$ and because we know that we have the property of $\SN$ we must eventually reach a terminating element.
+and so trivially $\WN$. \greyout{If the element does relate to some other element $y \in A$, then we recursively apply our claim to 
+$y$ and because we know that we have the property of $\SN$ we must eventually reach a terminating element.}
 
@@
     \centering
-    \caption{Local implications}
     \begin{tabular}{|>{\columncolor{gray!30}}l|c|c|c|c|c|}
@@
     \end{tabular}
+    \caption{Local implications}
 \end{table} 
+\vspace{-1cm}
+% \\[-0.5cm]
 \begin{table}[h!]
     \centering
-    \caption{Global implications}
     \begin{tabular}{|>{\columncolor{gray!30}}l|c|c|c|c|c|}
@@
     \end{tabular}
+    \caption{Global implications}
 \end{table}
@@
 
+\begin{remark} The following are the key takeaways from the implication tables. \hfill
+    \begin{enumerate}
+        \item The property $\gWCR$ can sometimes be a substitute for the classical 
+        property required for $\SN \implies \WN$ (and similarly $\SM \implies WM$).   
+        \item $\gWN \land \gUNto \implies \gCR$ doesn't require any classical assumptions
+         or $\gWCR$ for $\gCR$, unlike $\gSN \land \gUNto$. 
+        \item $\gWN \land \gUNto \implies \gCR$ only holds when the properties are global. The 
+        counterexample provided illustrates why $\WCR \land \WN \land \UNto \nRightarrow \CR$.
+        \item Both $\SM$ and $\WN$ are required for $\SN$, this connection is explored in Subsection \ref{subsec:SMWNSN}.
+        \item We have a generalization of Newman's Lemma as $\SM \land \gWCR \implies \CR$. This is explored in Subsection \ref{subsec:newnewman}.
+    \end{enumerate}
+\end{remark}
+
 \subsubsection{Generalized Newman's Lemma}\label{subsec:newnewman}
@@
 % globally but not locally. 
-\subsection{Relation between $\SM$, $\WN$, and $\SN$}
-One key takeaway from the tables is that we obtain completeness when we have the properties $\SM$, $\WN$, and $\WN$. We also 
+\subsection{Relation between $\SM$, $\WN$, and $\SN$} \label{subsec:SMWNSN}
+One key takeaway from the tables is that we obtain completeness when we have the properties $\SM$, $\WN$, and $\NP$. We also 
 obtain completeness when we have $\gWN$ and $\gSM$. 
@@
 \verb|isWN∧isSM→isSN : R isWN → R isSM → R isSN|
-
-\sacomment{Are there any other features of the table that we would like to draw out?}
-\sacomment{We should remember that If global WCR and local SM implies local CR, then if we also have local WN, we get local SN.}

### 2025-02-23 Relations/Paper/WFFigure.tex
Figure for WF

\begin{figure}[h]
    \centering
    \begin{tikzpicture}[node distance=2cm, auto]
      % Standard definitions
      \node (std1) [draw] {isWFacc};
      \node (std2) [right of=std1, draw] {isWFind};
      \node (std3) [right of=std2, draw] {isWFseq};
      \node (std4) [right of=std3, draw] {isWFmin};

      % Weaker definitions
      \node (weak1) [below of=std1,  draw, yshift=1cm] {isWFacc-};
      \node (weak2) [below of=std2,  draw, yshift=1cm] {isWFind-};
      \node (weak3) [below of=std3,  draw, yshift=1cm] {isWFmin-};
      \node (weak4) [below of=std4,  draw, yshift=1cm] {isWFseq-};

      % Arrows
      \draw[->, thick] (std1) -- (weak1);
      \draw[->, thick] (std1) -- (std2);
      \draw[->, thick] (std2) -- (weak2);
      \draw[->, thick] (weak1) -- (weak2);
      \draw[->, thick] (std2) -- (std3) ;
      \draw[->, thick] (std3) -- (weak3);
      \draw[->, thick] (weak2) -- (weak3);
      \draw[->, thick] (std3) to (std4);
      \draw[->, thick] (weak3) to (weak4);
      \draw[->, thick] (std4) -- (weak4);
   \end{tikzpicture}
    % \caption{A graphic illustrating the implications we have found between the above
    % definitions and those we are still seeking to find. Green arrows indicate that one
    % definition implies another, red arrows indicate that we believe an implication should
    % be possible but we have not yet found it.
    % }
\end{figure}

### 2025-02-23 Relations/Paper/Definitions.tex
Refactored

--- 2025-02-23 Relations/Paper/Definitions.tex
@@
   \begin{description}
-    \item[$a \in \NF_R$] \emph{$a$ is a normal form} if $(a,b) \notin R$ for any $b \in A$ 
+    \item[$a \in \NF_R$] \emph{$a$ is a normal form} if $(a,b) \notin R$ for any $b \in A$.   
     \item[$a \in \WN_R$] \emph{$a$ is weakly normalizing} if $a \mstep b$ for some $b \in \NF_R$.
@@
 \end{definition}
+
 For each of the subsets defined above we denote in bold face the proposition that the subset contains all of $A$.
@@
     \begin{description}
-        \item[$R \models Inc$] \emph{$R$ is increasing} if there exists a ``size function'' $|-| : A \to \nat$ satisfying, for all $a, b \in A$,
+        \item[$R \models \gInc$] \emph{$R$ is increasing} if there exists a ``size function'' $|-| : A \to \nat$ satisfying, for all $a, b \in A$,
         $Rab \to |a| < |b|$  
@@
 Having a size function that maps to the natural numbers is computationally taxing to satisfy. 
-Further, it takes us outside of purely relational theory. The following definitions are for properties which allow us to forgo $\Inc$, for further discussion see Subsection \ref{subsec:def}.
+Further, it takes us outside of purely relational theory. The following definitions are for properties which allow us to forgo $\gInc$, for further discussion see Subsection \ref{subsec:def}.
 \begin{definition} \label{def:rp} Let $A$ and $R$ be as above, and let $a \in A$.
@@
         \item[$a$ is an $s$-bound] if $s (i) \mstep a$ for all $i \in \nat$. 
-        \item[$a \in \BP_R$] if all $R$-increasing sequence $s$ with $s (0) = a$ there exists an $s$-bound.  
-        \item[$R \models \RPm$] \emph{$R$ has the weak recurrence property} if for every increasing sequence $s$ with bound $b$ there exists an $i \in \nat$ such that $b \mstep s (i)$.
-
-        \item[$R \models \RP$] \emph{$R$ has the recurrence property} if every bounded, increasing sequence $s$ with an $s$-bound, there exists an $i \in \nat$ such that 
+        \item[$a \in \BP_R$] if for all $R$-increasing sequence $s$ with $s (0) = a$ there exists an $s$-bound.  
+        \item[$R \models \gRPm$] \emph{$R$ has the weak recurrence property} if for every increasing sequence $s$ with bound $b$ there exists an $i \in \nat$ such that $b \mstep s (i)$.
+        \item[$R \models \gRP$] \emph{$R$ has the recurrence property} if for every bounded, increasing sequence $s$ with an $s$-bound, there exists an $i \in \nat$ such that 
         $s (i) \mstep x \implies x \mstep s (i)$ for all $x\in A$. See Definition \ref{def:mf}. 
@@
 \end{definition}
-In \terese $\mathsf{Ind}$ is used to denote $\BP$.
+
+In \terese $\mathrm{Ind}$ is used to denote $\BP$.
 
@@
 
-We investigated $\RP$ and thought that with $\RPm$ we had a candidate for a weaker definition that 
+We wanted to generalize $\RP$ and thought that with $\RPm$ we had a good candidate for a weaker definition that 
 did not rely on the notion of $\MF$. We show that this weaker definition is 
@@
     \begin{description}
-        \item[$a \in \FB$] \emph{$a$ is finitely branching} if there is a finitely many $b \in A$ such that $a \rstep b$.  
+        \item[$a \in \FB$] \emph{$a$ is finitely branching} if there is finitely many $b \in A$ such that $a \rstep b$.  
     \end{description}
 \end{definition}
+
 Our Agda formulation of the above definition makes use of the List type constructor. 
@@
 
-$\FB$ is a property that plays an important role in our discussion of well-foundedness in Section \ref{sec:Well-foundedness}.
+$\FB$ is a property that plays an important role in our discussion of well-foundedness (see Section \ref{sec:Well-foundedness}).

### 2025-02-23 Relations/Paper/FinalTODO.tex
Definitions rewritten
Figure for WF
Refactored

@@
     \item Need to sort out a repository for the code and add it to the supplementary material section.  
+    \item Add contents sections?
+    \item Add bibliography/references.
     \item FINAL Remove this TODO section from the report 
@@
     \item We should create a good clear section of future work so we can pass this project on to future students.
+    \item {We should remember that If global WCR and local SM implies local CR, then if we also have local WN, we get local SN.}
+    \item \sacomment{Do we include more information on the propositions in the formalization section?}
+    \item \sacomment{Proove the forawrd direction of theorem 1.2.3 iv}
+    \item Show that SM and SMseq are classically equivalent.
 \end{enumerate}

### 2025-02-23 Relations/Paper/Formalization.tex
Refactored

@@
 \label{sec:Formalization}
-This sections acts as a guide of our formalization of \terese and explains the deviations we took.
+This sections is a guide to our formalization of \terese and explains the deviations we take from the text.
 
 \subsection{Formalization of Definitions}\label{subsec:def}
-We have formalized those definitions which were necessary for the formalization of the propositions and theorems found 
-in Chapter 1 of \terese. 
 The closure operators are formalized in \texttt{ARS-Closure.agda}. 
-The definitions grouped as confluent \terese are formalized in \texttt{ARS-Base.agda}. 
+The definitions grouped as confluent in \terese are formalized in \texttt{ARS-Base.agda}. 
 The definitions grouped as normalizing in \terese are formalized in \texttt{ARS-Properties.agda}.
@@
 
-As already mentioned, the $\Inc$ property has undesired requirements. $\Inc$ is used only in Theorem 1.2.3 
-and the crucial facet of $\Inc$ for the proof of the theorem is that no $R$-increasing 
+As mentioned, the $\Inc$ property imposes a computationally demanding requirement. However, $\Inc$ is used only in Theorem 1.2.3 
+and the only crucial aspect of $\Inc$ needed for the proof is that no $R$-increasing 
 sequence can have an upper bound.
-We established that the properties $\RP$ and $\RPm$ were sufficient for proving the theorem (see Subsection \ref{subsec:theorems}). This in turn led us to 
-examine the condition in $\RP$ more closely. This condition provides a generalization of the notion of normal form, 
-which we analyze in detail in Section \ref{sec:Implications}.
+We establish that the properties $\RP$ and $\RPm$ were sufficient for replacing $\Inc$ in the theorem (see Subsection \ref{subsec:theorems}), 
+which led us to examine the condition in $\RP$ more closely. This condition provides a generalization of the notion of a normal form, 
+which we explore in detail in Section \ref{sec:Implications}.
 
@@
 There are three sets of propositions given in \terese: \texttt{1.1.9}, \texttt{1.1.10}, \texttt{1.1.11}. 
-The formalization of the proofs are in \texttt{ARS-Propositions.agda}. These formalizations were straightforward 
-and as such are not the focus of this paper. \sacomment{Do we include more information on these propositions?}
+The formalization of the proofs are in \texttt{ARS-Propositions.agda}. These formalizations are straightforward 
+and as such are not the focus of this paper.
 
@@
 There are three proofs of Newman's Lemma ($\SN \land \WCR \implies \CR$) given in \terese. 
-The first and third of these proofs make use of classical properties. The second proof is amenable to a 
+The first and third of these proofs make use of classical assumptions. The second proof is amenable to a 
 constructive formalization as shown in the following function in \texttt{ARS-NewmansLemma.agda}:
@@
 We show in Subsection \ref{subsec:newnewman} a generalization of Newman's Lemma using $\MF$. 
-
 The formalizations of the remaining theorems are all found in \texttt{ARS-Theorems.agda}. 
@@
 \end{itemize}
-\sacomment{Make below comment tidier}
 Note that we have provided a proof with the weaker hypothesis of $\gUNto$.
@@
 \end{description}
+
 ($i$) is formalized in: 
@@
 \end{itemize}
+
 In $\mathtt{i\to}$ we again provide a generalization by using $\gUNto$ rather than $\gUN$.
@@
 This is a fundamentally classical result, and so the result is only classically equivalent to $\gSN$.
-\sacomment{Double check the above explanation.}
 
@@
 is decidable as this property enables us 
-to construct a witness for an element that either does or does not have the property $\SN$. Such a witness was necessary for our proof. \sacomment{More to say on this theorem?}
+to construct a witness for an element that either does or does not have the property $\SN$. Such a witness was necessary for our proof. \sacomment{Link to decidable in later section?}
 
@@
 \end{itemize}
-We did not formalize $\gCR \to \gCP$ as it requires the ARS to be countable \sacomment{Add this proof to future todo}.
+We did not formalize $\gCR \to \gCP$ as it requires the ARS to be countable.

### 2025-02-23 Relations/Paper/Implications.tex
Refactored

@@
 % show chains of implications starting from these properties.
-As discussed in Subsection \ref{subsec:def} we put forward $\RP$ as an alternative property for $\Inc$. It is through examining $\RP$ that 
+As discussed in Subsection \ref{subsec:def} we put forward $\RP$ as an alternative for $\Inc$. It is through examining $\RP$ that 
 we came to the definitions below.
@@
 
-We show that $\SM \implies \SMseq$, however $\SMseq$ is only classically equivalent to $\SM$. The 
+$\SMseq$ is only classically equivalent to $\SM$. The 
 following proposition relates these new definitions with our previous $\RP$ definitions.
@@
 The isMinDec property \sacomment{refer to list of classical properties here} states that all elements either have a relation to some other element, or 
-there is no other element to which they have a relation. If the element relates to no other element then it is terminating 
-and so trivially $\WN$. \greyout{If the element does relate to some other element $y \in A$, then we recursively apply our claim to 
+there is no other element to which they have a relation. \greyout{If the element relates to no other element then it is terminating 
+and so trivially $\WN$. If the element does relate to some other element $y \in A$, then we recursively apply our claim to 
 $y$ and because we know that we have the property of $\SN$ we must eventually reach a terminating element.}
@@
         \item $\gWN \land \gUNto \implies \gCR$ doesn't require any classical assumptions
-         or $\gWCR$ for $\gCR$, unlike $\gSN \land \gUNto$. 
+         or $\gWCR$ for the implication to $\gCR$, unlike $\gSN \land \gUNto$. 
         \item $\gWN \land \gUNto \implies \gCR$ only holds when the properties are global. The 

### 2025-02-23 Relations/Paper/Conclusion.tex
progress

--- 2025-02-11 Relations/Paper/Introduction.tex
@@
-\section{Introduction}
-\label{sec:Introduction}
+\section{Conclusion and Further Work}
+\label{sec:Conclusion}
 
-The text for the introduction will go here.
+Recap the main takeaways from each piece.
+\begin{itemize}
+  \item ARS results are effective for finitely branching and decidable relations
+  --- covers first-order TRSs and the lambda calculus.
+  \item Identification of ``sufficiency frontier'' for completeness (termination and confluence).
+  It also collapses many well-foundedness properties.
+  \item Also discuss open problems, unprovable implications, etc.
+  Maybe mention the Kleene tree idea, or at least include the reference to the Bezem--Coquand paper.
+  \item Throughout this effort, we found that the classical theorems often assume
+  more than is necessary, and these distinctions becomes especially pronounced
+  in the context of constructive logic.
+  \item \emph{Formalizing classical ARS theory in the Curry--Howard framework
+  lead to improvements of classical ARS results.}
+\end{itemize}

### 2025-02-23 Relations/Paper/Introduction.tex
work
progress

--- 2025-02-11 Relations/Paper/Introduction.tex
@@
 
-The text for the introduction will go here.
+% \section{Plan}
+% \begin{itemize}
+%   \item Start by discussing motivation
+%   \item Then contributions
+%   \item Plan of the paper
+%   \item At some point, there should be like a summary of what's been done and what are some interesting discoveries
+% \end{itemize}
+%
+
+We present a formalization of the basic Abstract Rewriting Systems (ARS) theory in the Agda proof assistant.
+This work is part of a larger effort to develop a library of formalized programming language theory (PL)
+at Appalachian State University.
+Since Term Rewriting Systems (TRS) play a foundational role in programming languages,
+while ARS encompass the basic facts about rewriting relations in general,
+establishing these facts is part of the necessary infrastructure required to
+pursue the broader project.  The present contribution can therefore be seen as
+``bootstrapping'' Appstate's new formalized PL repository.
+
+This broader goal also drives the main design choices in our approach.
+Since rewriting theory is concerned with a fine-grained analysis of computation,
+the most natural vehicle for formalizing it is type theory based on the
+Curry--Howard isomorphism, which Agda implements.  Proofs in this language
+are automatically effective, and implicitly carry the code implementing the
+transformations from the hypotheses to the conclusion.  For example,
+a proof that a given TRS is terminating automatically renders a function that
+computes a normal form of any term in its domain.
+
+Staying within this paradigm requires the proofs to be constructive.
+Moreover, it requires us to avoid any axioms or postulates, such as function
+extensionality, uniqueness of identity proofs, univalence, etc.
+While most of ARS results are indeed constructive, standard presentations,
+ including \cite{Terese}, make liberal use of classical logic.
+Our paper can thus be read as a thoroughly constructive
+development of elementary ARS theory.
+
+\subsection{Motivation}
+
+Before we proceed further, let us consider two formalization scenarios where
+a constructive ARS library can be useful.
+
+\begin{example}[Formalization of typed lambda calculus]
+Suppose one is formalizing the standard metatheory of
+a typed lambda calculus.  To show confluence, one can
+first establish the Church--Rosser theorem for the untyped lambda calculus,
+then invoke the Subject Reduction theorem.
+However, suppose that Strong Normalization had already been verified independently.
+Invoking Newman's lemma, one can conclude confluence from the weak
+diamond property --- which is generally easier to prove than full CR.
+\end{example}
+
+\begin{example}[Quotients of types]
+Suppose one wishes to construct the initial model of an algebraic theory $T$
+over a first-order signature $S$.
+(For example, the reader could think here of the free commutative semiring over a finite set of generators.)
+The classical definition involves the quotient of the term algebra $S^*$ by
+the equivalence relation $\approx_T$ induced by $T$.
+Direct encoding of quotients is problematic in pure type theory.
+While there are a number of solutions, such as Higher Inductive Types \cite{HoTT},
+Quotient Inductive--Inductive Types \cite{QIIT}, Cubical Type Theory \cite{CTT}, etc.,
+they involve extending type theory with new language constructs,
+incurring additional costs in complexity.
+
+Now, suppose $T$ admits a convergent presentation.
+That is, suppose that the equivalence relation on $S^*$ coincides
+with conversion generated by a confluent and terminating rewriting system
+${\cdot}{\to_R}{\cdot} : S^* \to S^* \to \bset$.
+Then one can replace $S^*/{\approx_T}$ by the type of $R$-normal forms.
+(In the semiring example, these would be appropriately sorted polynomial expressions.)
+This can be defined as a pure dependent type
+\[ NF(R) \quad := \quad (\Sigma n : S^*) (\Pi x : S^*) \lnot (n \to_R x) \]
+This type encodes the quotient in the sense that the type of functions $S^*/{\approx_T} \to A$ is isomorphic to plain functions from $NF(R)$ to $A$.
+Indeed, the elimination rule for the quotient type requires every equation in $T$
+to be validated in order to define a function $f : S^*/{\approx_T} \to A$.
+Any such function trivially specializes to $NF(R)$.  In the other direction,
+a plain function from $NF(R)$ to $A$
+can be extended to all of $S^*$ by induction on normalizing reduction sequences.
+Confluence ensures that $T$-equal elements are always mapped to the same value.
+
+It follows that $S^*/{\approx_T}$ is isomorphic to $NF(R)$.
+
+It also follows as a corollary that equality in the initial model is decidable.
+\end{example}
+
+As these examples illustrate, a fully effective implementation of basic ARS results
+can be helpful in many settings arising in programming language theory.
+
+\subsection{Formalization principles}
+With the explicit goal of having the results of basic abstract rewriting
+formalized in a canonical way, so that they can be used in building
+libraries of formalized PL theory, we adopted the following
+principles during our development.
+
+\begin{itemize}
+  \item No use of function extensionality;
+  \item No use of univalence, uniqueness of identity proofs, axiom K, or any other
+  assumptions related to equality;
+  \item Minimize the use of classical logic, and make decidability hypotheses explicit in every place where classical logic could not be avoided;
+  \item Stay as faithful as possible to the spirit of type theory based on the Curry--Howard isomorphism, so that in every explicit application, our proofs would compute.
+\end{itemize}
+
+In several places, we had to assume certain decidability hypotheses in order to make
+the proofs go through.  These were always flagged explicitly, and an effort was made to
+have as few of them as possible.
+
+We have also identified classes of ARSs where the needed classical principles are simply valid.
+In particular, for finitely branching relations, the implication SN to WN requires nothing else beyond plain decidability of the relation itself: $Rxy \lor \lnot Rxy$.
+For example, an ARS induced by a first-order TRS with a finite set of rules is both finitely branching and decidable.
+
+The main conclusion of our work is that most of the main ARS results can be made completely effective, at least for the practical examples encountered in first-order TRSs and lambda calculi.
+
+For more exotic rewrite systems --- like $\lambda \bot$ (underpinning sensible lambda theories), or coinductive rewriting ---
+these decidability assumptions no longer hold, and the utility of ARS results diminishes proportionally.
+
+% \subsection{Well-foundedness and classical logic}
+Since Strong Normalization is a central concept in ARS theory,
+special attention in our work was given to various incaranations of the concept of well-foundedness in the constructive context.
+(Strong normalization is well-foundedness of the converse relation.)
+The standard constructive definition does not even allow one to show that SN implies WN, see Example \ref{ex:undec}.
+We therefore looked at a number of variations of this notion, their classical counterparts all being logically equivalent.
+This gave rise to a rich set of concepts, see Figure \ref{f:wf}.
+
+\subsection{Contributions}
+Our contributions are as follows.
+\begin{itemize}
+  \item Formalization of elementary ARS theory as presented in
+  Chapter 1 of \cite{Terese};
+  \item An ontology of termination and confluence properties, and a detailed analysis of logical relationships between them;
+  \item Definition of a few new ARS concepts that serve to streamline the constructive verification of these relationships;
+  \item Marginal improvements to classical confluence and termination criteria;
+  \item An exploration of several distinct notions of well-foundedness.
+\end{itemize}
+
+\subsection{OLD>DELETE}
+{ \color{gray}
+Term Rewriting Systems (TRS) play a foundational role in the theory of
+programming languages.
+
+- Operational semantics
+- Reduction strategies
+
+At Appalachian State University, we are building a library of formalized theory,
+lambda calculus, and type theory. This is a first contribution in this effort.
+
+ARS is Establishing those properties of relations relevant for rewriting theory.
+
+- Formalization of "Abstract Rewriting" content from TeReSe,
+including background on logic, relations, etc.
+- Identifying constructive formulations of classical concepts and proofs
+- Studying implications between notions related to confluence and termination
+- Isolating classical principles from proofs and eliminating them where possible.
+}

### 2025-02-23 Relations/Paper/Main.tex
intro first draft
removed ce section
progress

@@
 \input{macros}
+
+% \usepackage[dvipsnames]{xcolor}
+
+\newcommand{\hired}[1]{{\color{red}{#1}}}
 
@@
 
+\author{Samuel Arkle}{Appalachian State University, USA}
+{arklesd@appstate.edu}{}{}
 \author{Andrew Polonsky}{Appalachian State University, USA}
@@
 %  name splitting when the last name consists of multiple name parts.
-\author{Samuel Arkle}{Appalachian State University, USA (Recent graduate)}
-{arklesd@appstate.edu}{}{}
 
-\authorrunning{A. Polonsky and S. Arkle}
+\authorrunning{S.\ Arkle and A.\ Polonsky}
 
-\Copyright{Andrew Polonsky and Samuel Arkle}
+\Copyright{Samuel Arkle and Andrew Polonsky}
 
@@
     We present a constructive formalization of Abstract Reduction Systems (ARS)
-     in the Agda proof assistant, focusing on the results given in Term Rewriting
-     Systems (Terese). We define a taxonomy of concepts related to termination and
+     in the Agda proof assistant, focusing on the results given in
+     the standard reference on Term Rewriting Systems \cite{Terese}. We define a taxonomy of concepts related to termination and
      confluence and investigate their relationships between each other and their
@@
 \end{abstract}
+
 \input{Introduction.tex}
 \input{Definitions.tex}
+\input{Formalization.tex}
 \input{Implications.tex}
-\input{Counterexamples.tex}
 \input{Well-foundedness.tex}
+\input{Conclusion.tex}
 \input{FinalTODO.tex}

### 2025-02-23 Relations/Paper/Introduction.tex
intro done

@@
 
-\begin{example}[Formalization of typed lambda calculus]
+\begin{example}[Formalization of a typed lambda calculus]
 Suppose one is formalizing the standard metatheory of
 a typed lambda calculus.  To show confluence, one can
-first establish the Church--Rosser theorem for the untyped lambda calculus,
-then invoke the Subject Reduction theorem.
+first establish the Church--Rosser theorem (CR) for the untyped lambda calculus,
+and then proceed via the Subject Reduction theorem.
 However, suppose that Strong Normalization had already been verified independently.
@@
 
+\subsection{Decidability}
 In several places, we had to assume certain decidability hypotheses in order to make
@@
 have as few of them as possible.
+
+Since Strong Normalization is a central concept in ARS theory,
+special attention in our work was given to various incaranations of the concept of well-foundedness in the constructive context.
+(Strong normalization is well-foundedness of the converse relation.)
+The standard constructive definition does not even allow one to show that SN implies WN, see Example \ref{ex:undec} \apcomment{Refer to DecidableCounterexamples.agda?}.
+  We therefore looked at a number of variations of this notion, their classical counterparts all being logically equivalent.  This gave rise to a rich set of concepts, see Figure \ref{f:wf}.
 
@@
 For more exotic rewrite systems --- like $\lambda \bot$ (underpinning sensible lambda theories), or coinductive rewriting ---
-these decidability assumptions no longer hold, and the utility of ARS results diminishes proportionally.
-
-% \subsection{Well-foundedness and classical logic}
-Since Strong Normalization is a central concept in ARS theory,
-special attention in our work was given to various incaranations of the concept of well-foundedness in the constructive context.
-(Strong normalization is well-foundedness of the converse relation.)
-The standard constructive definition does not even allow one to show that SN implies WN, see Example \ref{ex:undec}.
-We therefore looked at a number of variations of this notion, their classical counterparts all being logically equivalent.
-This gave rise to a rich set of concepts, see Figure \ref{f:wf}.
+these decidability assumptions no longer hold, and the utility of the ARS framework diminishes proportionally.
 
@@
   \item Formalization of elementary ARS theory as presented in
-  Chapter 1 of \cite{Terese};
+  \cite{Terese}, including relevant background;
+  % Chapter 1 of
   \item An ontology of termination and confluence properties, and a detailed analysis of logical relationships between them;
-  \item Definition of a few new ARS concepts that serve to streamline the constructive verification of these relationships;
+  \item Definitions of new ARS concepts that refine our understanding of these relationships;
   \item Marginal improvements to classical confluence and termination criteria;
-  \item An exploration of several distinct notions of well-foundedness.
+  \item An examination of several distinct notions of well-foundedness
+  in the constructive setting.
 \end{itemize}
 
-\subsection{OLD>DELETE}
-{ \color{gray}
-Term Rewriting Systems (TRS) play a foundational role in the theory of
-programming languages.
+\subsection{Plan of the paper}
 
-- Operational semantics
-- Reduction strategies
-
-At Appalachian State University, we are building a library of formalized theory,
-lambda calculus, and type theory. This is a first contribution in this effort.
-
-ARS is Establishing those properties of relations relevant for rewriting theory.
-
-- Formalization of "Abstract Rewriting" content from TeReSe,
-including background on logic, relations, etc.
-- Identifying constructive formulations of classical concepts and proofs
-- Studying implications between notions related to confluence and termination
-- Isolating classical principles from proofs and eliminating them where possible.
-}
+The structure of the paper roughly corresponds with the progression of the Agda code.
+% Agda files.
+% (with the exception of section \ref{sec:Well-foundedness}, which is put at the end)
+In the next section, we lay out the main properties of relations studied in ARS theory,
+setting the ground for what follows.  In Section \ref{sec:Formalization}, we
+outline our formalization of the ARS chapter from \cite{Terese}.
+Here we also discuss how this effort suggested new ARS properties that helped us overcome some obstacles we encountered along the way.
+These properties fit naturally within the rewriting paradigm.
+Thus in Section \ref{sec:Implications}, we dedicate some effort to investigating them further.
+The result is a broader ontology of ARS concepts, revealing interrelationships between conditions for completeness.
+In Section \ref{sec:Well-foundedness} we focus on what it means for a relation to be well-founded, identifying the classical principles needed to transition between different formulations.
+We conclude with a brief summary and suggestions for future work.

### 2025-02-23 Relations/Paper/Definitions.tex
typo fix
intro done
Update after call

@@
 The following definitions are provided to ensure clarity and precision
-in our discussion. Each subsection specifies the Agda file(s) which contain formalizations of the given definitions.
+in our discussion. Each subsection specifies the Agda file(s) which contains formalizations of the given definitions.
 
@@
     An abstract rewrite system (\emph{ARS}) is a structure $\mathcal{A} = (A, R_\alpha)$ where
-     $A$ is a set of elements and $R_\alpha$ is a set of binary relations on $A$.
+     $A$ is a set and $R_\alpha$ is a set of binary relations on $A$.
 \end{definition}
 
-For the rest of this section, let $A$ be a fixed set, and $R$ be a relation on $A$.
+For the rest of this paper, let $A$ be a fixed set, $R$ be a relation on $A$, and $a \in A$.
 
@@
 \subsection{Closure operators (\texttt{ClosureOperators.agda})}
+
 \begin{notation} 
-  The following notions are standard.  For precise definitions,
-  see \texttt{ClosureOperators.agda}.
+The following notations are standard.
   \begin{enumerate}
@@
 \subsection{Normalization (\texttt{ARS-Properties.agda})}
-\begin{definition} The following definitions relate to normalization. Let $A$ and $R$ be as above, and let $a \in A$.
+\begin{definition} The following definitions relate to normalization. 
   \begin{description}
-    \item[$a \in \NF_R$] \emph{$a$ is a normal form} if $(a,b) \notin R$ for any $b \in A$.   
-    \item[$a \in \WN_R$] \emph{$a$ is weakly normalizing} if $a \mstep b$ for some $b \in \NF_R$.
-    \item[$a \in \SN_R$] \emph{$a$ is strongly normalizing} if $a$ is accessible with respect to the converse relation $\bar{R} = {(y,x) | (x,y) \in R}$. See Section \ref{sec:Well-foundedness}. 
+    \item[\ule{$\mathbf{a \in \NF_R}$}] \emph{$a$ is a normal form} if $(a,b) \notin R$ for any $b \in A$.
+    \item[\ule{$a \in \WN_R$}] \emph{$a$ is weakly normalizing} if $a \mstep b$ for some $b \in \NF_R$.
+    \item[\ule{$a \in \SN_R$}] \emph{$a$ is strongly normalizing} if $a$ is accessible with respect to the converse relation $\bar{R} = \setof{(y,x) | (x,y) \in R}$ 
+    (see Section \ref{sec:Well-foundedness} for the notion of accessibility).
   \end{description}
@@
 \subsection{Confluence (\texttt{ARS-Properties.agda})}
-\begin{definition} The following definitions relate to confluence. Let $A$ and $R$ be as above, and let $a \in A$.
+\begin{definition} The following definitions relate to confluence.
     \begin{description}
@@
         \item[$a \in \CRs_R$] \emph{$a$ is subcommutative} if $c \bmstep a \mstep b \implies c \rrstep d \brstep b$.
-        \item[$a \in \NPe_R$] \emph{$a$ has the equivalence normal form property} if $a \estep b \implies a\mstep b$ for any $b \in \NF$.
+        \item[$a \in \NPe_R$] \emph{$a$ has the conversion normal form property} if $a \estep b \implies a\mstep b$ for any $b \in \NF$.
         \item[$a \in \NP_R$] \emph{$a$ has the normal form property} if $c \bmstep a \mstep b \implies c \mstep b$ for any $b \in \NF$.
@@
 
-For each of the subsets defined above we denote in bold face the proposition that the subset contains all of $A$.
-That is, for $\mathrm{X} \in \{\WCR , \CR , \NP , \UN \}$ we write $\mathbf{X}$ for the statement that $x \in \mathrm{X}_R$ for all $x \in A$.
+\begin{notation}
+    For each of the subsets $\mathrm{X}$ defined above we write 
+    $R \models \mathbf{X}$ if $\forall a.\; a \in \mathrm{X}_R$. When $R$ is clear from the context, we will write $\gNP$ for $R \models \gNP$, etc.
+    That is, for $\mathrm{X} \in \{\WCR , \CR , \NP , \UN, \dots \}$ we write $\mathbf{X}$ for the statement that $x \in \mathrm{X}_R$ for all $x \in A$.
+\end{notation}
 
-In \terese $\NF$ is used to denote $\NPe$, whereas we have chosen to use $\NF$ to denote normal form.
+In \terese $\NF$ is used to denote $\NPe$, whereas we have chosen to use $\NF$ to denote the set of normal forms.
 
@@
 
-\begin{notation}
-    $R \models \mathbf{X}$ is $\forall a.\; a \in \mathrm{X}_R$. When $R$ is clear from the context, we will write $\gNP$ for $R \models \gNP$, etc. 
-\end{notation}
-
 \begin{definition} \hfill
     \begin{description}
-        \item[$R \models \gInc$] \emph{$R$ is increasing} if there exists a ``size function'' $|-| : A \to \nat$ satisfying, for all $a, b \in A$,
-        $Rab \to |a| < |b|$  
+        \item[\ule{$R \models \gInc$}] \emph{$R$ is increasing} if there exists a ``size function'' $|{-}| : A \to \nat$ satisfying, for all $a, b \in A$,
+        $(a \rstep b) \implies |a| < |b|$
     \end{description}
@@
 
-Having a size function that maps to the natural numbers is computationally taxing to satisfy. 
+Having a size function that maps to the natural numbers can be computationally taxing to satisfy.
 Further, it takes us outside of purely relational theory. The following definitions are for properties which allow us to forgo $\gInc$, for further discussion see Subsection \ref{subsec:def}.
-\begin{definition} \label{def:rp} Let $A$ and $R$ be as above, and let $a \in A$.
+\begin{definition} \label{def:rp} \hfill
     \begin{description}
-        \item[$s : \nat \to A$] \emph{A sequence $s \in A$} is a function from the natural numbers to $A$.  
-        \item[$s \in R-increasing$] \emph{A sequence $s \in A$ is $R$-increasing} if every term is $R$-related to its preceding term.
-        \item[$a$ is an $s$-bound] if $s (i) \mstep a$ for all $i \in \nat$. 
-        \item[$a \in \BP_R$] if for all $R$-increasing sequence $s$ with $s (0) = a$ there exists an $s$-bound.  
-        \item[$R \models \gRPm$] \emph{$R$ has the weak recurrence property} if for every increasing sequence $s$ with bound $b$ there exists an $i \in \nat$ such that $b \mstep s (i)$.
-        \item[$R \models \gRP$] \emph{$R$ has the recurrence property} if for every bounded, increasing sequence $s$ with an $s$-bound, there exists an $i \in \nat$ such that 
-        $s (i) \mstep x \implies x \mstep s (i)$ for all $x\in A$. See Definition \ref{def:mf}. 
+        \item[\ule{$s : \nat \to A$}] \emph{A sequence $s \in A$} is a function from the natural numbers to $A$.
+        \item[\ule{$s$ is $R$-increasing}] \emph{A sequence $s \in A$ is $R$-increasing} if every term is $R$-related to its preceding term.
+        \item[\ule{$a$ is an $s$-bound}] if $s (i) \mstep a$ for all $i \in \nat$.
+        \item[\ule{$a \in \BP_R$}] \emph{$a$ has the bound property} if for each $R$-increasing sequence $s$ with $s (0) = a$ there exists an $s$-bound.
+        \item[\ule{$R \models \gRP$}] \emph{$R$ has the recurrence property} if for every bounded, increasing sequence $s$ with an $s$-bound, there exists an $i \in \nat$ such that
+        $s (i) \mstep x \implies x \mstep s (i)$ for all $x\in A$. 
+        \item[\ule{$R \models \gRPm$}] \emph{$R$ has the weak recurrence property} if for every increasing sequence $s$ with bound $b$ there exists an $i \in \nat$ such that $b \mstep s (i)$.
     \end{description}
@@
     \begin{enumerate}
-        \item $\gInc \implies \gRPm$
-        \item $\gRPm \implies \gRP$
+        \item $\gInc \implies \gRP$
+        \item $\gRP \implies \gRPm$
     \end{enumerate}
@@
 
-We wanted to generalize $\RP$ and thought that with $\RPm$ we had a good candidate for a weaker definition that 
-did not rely on the notion of $\MF$. We show that this weaker definition is 
-in fact an equivalent definition in the following proof in \texttt{ARS-Implications.agda}:
+We wanted to generalize $\RP$ and thought that with $\RPm$ we had a good candidate.
+ We show that this weaker definition is
+in fact equivalent in the following proof in \texttt{ARS-Implications.agda}:
 
@@
 
-\begin{definition} Let $A$ and $R$ be as above, and let $a \in A$.
+\begin{definition} \hfill
     \begin{description}
-        \item[$a \in \FB$] \emph{$a$ is finitely branching} if there is finitely many $b \in A$ such that $a \rstep b$.  
+        \item[$a \in \FB$] \emph{$a$ is finitely branching} if there are finitely many $b \in A$ such that $a \rstep b$.
     \end{description}

### 2025-02-23 Relations/Paper/Formalization.tex
Update after call

@@
 \begin{itemize}
-    \item $\SN$ : We make use of the well-founded definition, rather than the finite reduction sequence definition.
+    \item $\SN$ : We define this via the notion of accessibility rather than the non-existence of infinite reduction sequences. 
+     See Section \ref{sec:Well-foundedness} for further discussion.
     \item $\NPe$ : We use the equivalent $\NP$ definition. 
@@
 
-As mentioned, the $\Inc$ property imposes a computationally demanding requirement. However, $\Inc$ is used only in Theorem 1.2.3 
+As mentioned, the $\Inc$ property can impose a computationally demanding requirement. However, $\Inc$ is used only in Theorem 1.2.3 
 and the only crucial aspect of $\Inc$ needed for the proof is that no $R$-increasing 
 sequence can have an upper bound.
-We establish that the properties $\RP$ and $\RPm$ were sufficient for replacing $\Inc$ in the theorem (see Subsection \ref{subsec:theorems}), 
-which led us to examine the condition in $\RP$ more closely. This condition provides a generalization of the notion of a normal form, 
+We establish that the equivalent properties $\RP$ and $\RPm$ are sufficient for replacing $\Inc$ in the theorem (see Subsection \ref{subsec:theorems}), 
+which led us to examine the condition on $s (i)$ appearing inside $\RP$ more closely. This condition provides a generalization of the notion of a normal form, 
 which we explore in detail in Section \ref{sec:Implications}.
@@
 There are three proofs of Newman's Lemma ($\SN \land \WCR \implies \CR$) given in \terese. 
-The first and third of these proofs make use of classical assumptions. The second proof is amenable to a 
+The first and third of these proofs make use of classical reasoning. The second proof is amenable to a 
 constructive formalization as shown in the following function in \texttt{ARS-NewmansLemma.agda}:
@@
 
-We show in Subsection \ref{subsec:newnewman} a generalization of Newman's Lemma using $\MF$. 
+We show in Subsection \ref{subsec:newnewman} a generalization of Newman's Lemma using a condition distilled from $\RP$. 
 The formalizations of the remaining theorems are all found in \texttt{ARS-Theorems.agda}. 
@@
     \item \verb|NP→UN : R isNP₌ → R isUN|
-    \item \verb|CP→UN : R isCR → R isUN|
 \end{itemize}
 
-($ii$) is formalized in:
+($ii$) is formalized also from the weaker hypothesis of $\gUNto$:
 \begin{itemize}
     \item \verb|ii : R isWN × R isUN → R isCR|
+    \item \verb|UN→∧WN→CR : R isUN→ → R isWN → R isCR|
 \end{itemize}
-Note that we have provided a proof with the weaker hypothesis of $\gUNto$.
 
@@
 The following definition is required for this theorem.
-\begin{definition} Let $a \in A$.
+\begin{definition}\hfill
     \begin{description}
@@
 
-In $\mathtt{i\to}$ we again provide a generalization by using $\gUNto$ rather than $\gUN$.
+In $\mathtt{i\to}$ we again provide a slight improvement by using $\gUNto$ rather than $\gUN$.
 
@@
 \end{itemize}
-This is a fundamentally classical result, and so the result is only classically equivalent to $\gSN$.
+This is an inherently classical result, and so the result is only classically equivalent to $\gSN$.
 
@@
 \end{itemize}
-We did not formalize $\gCR \to \gCP$ as it requires the ARS to be countable.
+We did not formalize $\gCR \to \gCP$ as it requires cardinality assumptions.
+
+% the ARS to be countable.

### 2025-02-23 Relations/Paper/Implications.tex
Update after call

@@
 
-\begin{definition}\label{def:mf}  Let $A$ and $R$ be as above, and let $a \in A$.
+\begin{definition}\label{def:mf} \hfill
     \begin{description}
@@
         an $i \in \nat$ such that $s (i) \in \MF$. 
-        \item[$a \in \SM_R$]  \emph{$a$ is strongly minimalizing} if either $a \in MF_R$, or every element one $R$ step from $a$ is also strongly minimalizing.
+        \item[$a \in \SM_R$]  \emph{$a$ is strongly minimalizing} if either $a \in MF_R$, or every element one $R$ step from $a$ is strongly minimalizing. (This 
+        definition is to be understood inductively).
         \item[$a \in \MP_R$] \emph{$a$ has the minimal form property} if $c \bmstep a \mstep b \implies c \mstep b$ for any $b \in \MF$.
@@
 \end{definition}
+
+Trivially, the following holds. 
+\begin{proposition}\label{prop:nftomf}
+    $\NF \implies \MF$ 
+\end{proposition}    
+\begin{proof}
+    See, \verb|NF ⊆ MF : ∀x → NFx → MFx| in \texttt{ARS-Implications.agda}.
+\end{proof}
 
@@
 
-Trivially, the following also holds. 
-\begin{proposition}\label{prop:nftomf}
-    $\NF \implies \MF$ 
-\end{proposition}    
-\begin{proof}
-    See, \verb|NF ⊆ MF : ∀x → NFx → MFx| in \texttt{ARS-Implications.agda}.
-\end{proof}
-
-With these minimal definitions we can see the taxonomy of concepts that relate to termination and confluence.
+Proposition \ref{prop:nftomf} suggests that we consider $\MF$ as a termination property in its own right. This leads us to 
+explore the following broader taxonomy of concepts relating to termination and confluence.
 
@@
 The implications in this diagram are formalized in \texttt{ARS-Implications.agda}. The classical property of being minimally decidable is 
-required to complete the implication from $\SN$ to $\WN$, as can be seen in our formalization
+required to complete the implication from $\SN$ to $\WN$, as can be seen in our formalization \sacomment{Rewrite this section}
 
@@
 
-Similarly, the property of being minimally decidable is required in order to show that $\SM$ implies $\WM$.
+The same property is similarly required in order to show that $\SM$ implies $\WM$.
 
@@
 The following tables show either that a given combination is complete, or the appropriate counterexample which demonstrates why 
-those properties do not provide a property higher on the taxonomical hierarchy.
+those properties do not provide the next property on the hierarchy.
 
@@
 first table assume $\WCR$ and in the second table assume $\gWCR$.
-
+\clearpage
 \renewcommand*{\thefootnote}{\fnsymbol{footnote}}
@@
         \item The property $\gWCR$ can sometimes be a substitute for the classical 
-        property required for $\SN \implies \WN$ (and similarly $\SM \implies WM$).   
-        \item $\gWN \land \gUNto \implies \gCR$ doesn't require any classical assumptions
+        property required for $\SN \implies \WN$ (and similarly $\SM \implies \WM$).   
+        \item $\gWN \land \gUNto \implies \gCR$ does not require any classical assumptions
          or $\gWCR$ for the implication to $\gCR$, unlike $\gSN \land \gUNto$. 
@@
         counterexample provided illustrates why $\WCR \land \WN \land \UNto \nRightarrow \CR$.
+        \item We have a generalization of Newman's Lemma as $\SM \land \gWCR \implies \CR$. This is explored in Subsection \ref{subsec:newnewman}.
         \item Both $\SM$ and $\WN$ are required for $\SN$, this connection is explored in Subsection \ref{subsec:SMWNSN}.
-        \item We have a generalization of Newman's Lemma as $\SM \land \gWCR \implies \CR$. This is explored in Subsection \ref{subsec:newnewman}.
     \end{enumerate}
@@
 
-\subsubsection{Generalized Newman's Lemma}\label{subsec:newnewman}
+\subsection{Generalized Newman's Lemma}\label{subsec:newnewman}
 One interesting outcome from investigating the normalization taxonomy was a generalization of Newman's Lemma.
@@
 This proof follows the same steps as the second proof of Newman's Lemma found in \terese, but 
-uses the generalization $\SM$ of $\SN$.
+uses the weaker assumption $\SM$ in place of $\SN$.
 

### 2025-02-23 Relations/Paper/Definitions.tex
definition underlined.

@@
     \begin{description}
-        \item[$a \in \WCR_R$] \emph{$a$ is weakly Church-Rosser (or weakly confluent)} if $c \bstep a \rstep b \implies c \mstep d \bmstep b$.
-        \item[$a \in \CR_R$] \emph{$a$ is Church-Rosser (or confluent)} if $c \bmstep a \mstep b \implies c \mstep d \bmstep b$.
-        \item[$a \in \CRs_R$] \emph{$a$ is subcommutative} if $c \bmstep a \mstep b \implies c \rrstep d \brstep b$.
-        \item[$a \in \NPe_R$] \emph{$a$ has the conversion normal form property} if $a \estep b \implies a\mstep b$ for any $b \in \NF$.
-        \item[$a \in \NP_R$] \emph{$a$ has the normal form property} if $c \bmstep a \mstep b \implies c \mstep b$ for any $b \in \NF$.
-        \item[$a \in \UN_R$] \emph{$a$ has the unique normal form property} if $a \estep b \implies a \equiv b$  for any $a, b \in \NF$.
-        \item[$a \in \UNto_R$] \emph{$a$ has the unique normal form property with respect to reduction} if $c \bmstep a \mstep b  \implies b \equiv c$  for any $b, c \in \NF$.
+        \item[\ule{$a \in \WCR_R$}] \emph{$a$ is weakly Church-Rosser (or weakly confluent)} if $c \bstep a \rstep b \implies c \mstep d \bmstep b$.
+        \item[\ule{$a \in \CR_R$}] \emph{$a$ is Church-Rosser (or confluent)} if $c \bmstep a \mstep b \implies c \mstep d \bmstep b$.
+        \item[\ule{$a \in \CRs_R$}] \emph{$a$ is subcommutative} if $c \bmstep a \mstep b \implies c \rrstep d \brstep b$.
+        \item[\ule{$a \in \NPe_R$}] \emph{$a$ has the conversion normal form property} if $a \estep b \implies a\mstep b$ for any $b \in \NF$.
+        \item[\ule{$a \in \NP_R$}] \emph{$a$ has the normal form property} if $c \bmstep a \mstep b \implies c \mstep b$ for any $b \in \NF$.
+        \item[\ule{$a \in \UN_R$}] \emph{$a$ has the unique normal form property} if $a \estep b \implies a \equiv b$  for any $a, b \in \NF$.
+        \item[\ule{$a \in \UNto_R$}] \emph{$a$ has the unique normal form property with respect to reduction} if $c \bmstep a \mstep b  \implies b \equiv c$  for any $b, c \in \NF$.
     \end{description}
@@
     \begin{description}
-        \item[$a \in \FB$] \emph{$a$ is finitely branching} if there are finitely many $b \in A$ such that $a \rstep b$.
+        \item[\ule{$a \in \FB$}] \emph{$a$ is finitely branching} if there are finitely many $b \in A$ such that $a \rstep b$.
     \end{description}

### 2025-02-23 Relations/Paper/Formalization.tex
definition underlined.

@@
     \begin{description}
-        \item[$a \in CP_R$] \emph{$a$ has the cofinality property} if there exists a 
+        \item[\ule{$a \in CP_R$}] \emph{$a$ has the cofinality property} if there exists a 
         (not necessarily strictly) increasing sequence starting from $a$ such that every

### 2025-02-23 Relations/Paper/Implications.tex
definition underlined.

@@
     \begin{description}
-        \item[$a \in \MF_R$] \emph{$a$ is a minimal form} if $a \mstep b \implies b \mstep a$ for any $b \in A$.
-        \item[$a \in \WM_R$] \emph{$a$ is weakly minimalizing} if $a \mstep b$ for some $b \in \MF_R$.
-        \item[$a \in \SMseq_R$] \emph{$a$ is sequentially strongly minimalizing} if for every $R$-increasing sequence $s$ starting at $a$, there exists 
+        \item[\ule{$a \in \MF_R$}] \emph{$a$ is a minimal form} if $a \mstep b \implies b \mstep a$ for any $b \in A$.
+        \item[\ule{$a \in \WM_R$}] \emph{$a$ is weakly minimalizing} if $a \mstep b$ for some $b \in \MF_R$.
+        \item[\ule{$a \in \SMseq_R$}] \emph{$a$ is sequentially strongly minimalizing} if for every $R$-increasing sequence $s$ starting at $a$, there exists 
         an $i \in \nat$ such that $s (i) \in \MF$. 
-        \item[$a \in \SM_R$]  \emph{$a$ is strongly minimalizing} if either $a \in MF_R$, or every element one $R$ step from $a$ is strongly minimalizing. (This 
+        \item[\ule{$a \in \SM_R$}]  \emph{$a$ is strongly minimalizing} if either $a \in MF_R$, or every element one $R$ step from $a$ is strongly minimalizing. (This 
         definition is to be understood inductively).
-        \item[$a \in \MP_R$] \emph{$a$ has the minimal form property} if $c \bmstep a \mstep b \implies c \mstep b$ for any $b \in \MF$.
+        \item[\ule{$a \in \MP_R$}] \emph{$a$ has the minimal form property} if $c \bmstep a \mstep b \implies c \mstep b$ for any $b \in \MF$.
 

### 2025-02-23 Relations/Paper/Conclusion.tex
added item
Removing missing references

@@
   \item \emph{Formalizing classical ARS theory in the Curry--Howard framework
-  lead to improvements of classical ARS results.}
+  lead to improvements of classical ARS results.} In the process, new properties were identified,
+   offering a clearer structural understanding of how different properties interact
+    to establish completeness. These insights contribute to a more refined and
+     expressive formulation of ARS theory.
+  \item We believe the fact that $\isWFseq$ does not imply $\isWFacc$
+  can be established by the methods of Bezem et al.
+
 \end{itemize}

### 2025-02-23 Relations/Paper/FinalTODO.tex
Removing missing references

@@
 \begin{enumerate}
-    \item Wording question. I'm trying to avoid stating "reduction" when talking about relations. However, can I still refer to a reduct and make sense? See for example the defintion of WCR.
-    \item We have shown SN implies SMseq, can we show SN implies SM?
     \item Need to fill in ACM subject classifications
+    \item Establish [TeReSe] as how we refer to the book.
     \item Need to fill in keywords and phrases
     \item Need to check what other mandatory information is required in the file 
-    \item Need to fill in Digital object identifier 
-    \item Need to sort out a repository for the code and add it to the supplementary material section.  
-    \item Add contents sections?
     \item Add bibliography/references.

### 2025-02-23 Relations/Paper/Introduction.tex
Removing missing references

@@
 
-We present a formalization of the basic Abstract Rewriting Systems (ARS) theory in the Agda proof assistant.
+We present a formalization of the basic Abstract Rewriting Systems (ARS) theory as presented in Term Rewriting Systems [TeReSe]
+ \cite{Terese}, using the Agda proof assistant.
 This work is part of a larger effort to develop a library of formalized programming language theory (PL)
@@
 (Strong normalization is well-foundedness of the converse relation.)
-The standard constructive definition does not even allow one to show that SN implies WN, see Example \ref{ex:undec} \apcomment{Refer to DecidableCounterexamples.agda?}.
-  We therefore looked at a number of variations of this notion, their classical counterparts all being logically equivalent.  This gave rise to a rich set of concepts, see Figure \ref{f:wf}.
+The standard constructive definition does not even allow one to show that SN implies WN, as we discuss in Section \ref{sec:Well-foundedness} and formalize in \texttt{WFCounters.agda}.
+  We therefore looked at a number of variations of this notion, their classical counterparts all being logically equivalent. %This gave rise to a rich set of concepts, see Figure \ref{f:wf}.
 

### 2025-02-23 Relations/Paper/Main.tex
Removing missing references

@@
 
-\ccsdesc[100]{\textcolor{red}{Replace ccsdesc macro with valid one}} %TODO mandatory: Please choose ACM 2012 classifications from https://dl.acm.org/ccs/ccs_flat.cfm
+\ccsdesc[300]{Theory of computation~Type theory} %TODO mandatory: Please choose ACM 2012 classifications from https://dl.acm.org/ccs/ccs_flat.cfm
 
-\keywords{Dummy keyword} %TODO mandatory; please add comma-separated list of keywords
+\keywords{Abstract rewriting, Formalization, Confluence, Strong normalization, Newman's Lemma} %TODO mandatory; please add comma-separated list of keywords
 
-\supplement{https://github.com/DrPolonsky/LAM/tree/main/Relations}% TODO: set a repo just for this submissionoptional, e.g.
+\supplement{https://github.com/DrPolonsky/LAM//tree/main/ARS}% TODO: set a repo just for this submissionoptional, e.g.
 related research data, source code, ...
@@
 
+\begin{thebibliography}{10}
+    \bibitem{Terese}
+    Marc Bezem, Jan Willem Klop, and Roel de Vrijer.
+    \newblock {Term Rewriting Systems}.
+    \newblock {Cambridge University Press, 2003}.
+
+    \bibitem{HoTT}
+    Peter Aczel, Benedikt Ahrens, Thorsten Altenkirch, Steve Awodey,  
+    Bruno Barras, Andrej Bauer, Yves Bertot, Marc Bezem, Thierry Coquand,  
+    Eric Finster, et al.  
+    \newblock{Homotopy Type Theory: Univalent Foundations of Mathematics}.  
+    \newblock{The Univalent Foundations Program, Institute for Advanced Study, 2013}.
+
+    \bibitem{QIIT}
+    Thorsten Altenkirch, Paolo Capriotti, Gabe Dijkstra, Nicolai Kraus,  
+    and Fredrik Nordvall Forsberg.
+    \newblock{Quotient inductive-inductive types}.  
+    \newblock{Proceedings of the International Conference on Foundations of Software Science and Computation Structures},  
+    \newblock{pages 293--310. Springer International Publishing, Cham, 2018}.
+
+    \bibitem{CTT}
+    Thierry Coquand, Simon Huber, and Anders Mörtberg.
+    \newblock{On higher inductive types in cubical type theory}.  
+    \newblock{Proceedings of the 33rd Annual ACM/IEEE Symposium on Logic in Computer Science},  
+    \newblock{pages 255--264, 2018}.
+
+    \bibitem{mimram}
+    Mimram, Samuel
+    \newblock{Program= Proof}.
+    \newblock{2020}.
+
+    \bibitem{Berardi}
+    Marc Bezem, Thierry Coquand, Keiko Nakata, and Erik Parmann.
+    \newblock{Realizability at Work: Separating Two Constructive Notions of Finiteness}.
+    \newblock {In 22nd International Conference on Types for Proofs and Programs (TYPES 2016)}.
+    \newblock{Leibniz International Proceedings in Informatics (LIPIcs), Volume 97, pp. 6:1-6:23, Schloss Dagstuhl – Leibniz-Zentrum für Informatik (2018)}.
+    \newblock{https://doi.org/10.4230/LIPIcs.TYPES.2016.6}.
+
+    \bibitem{Bezem}
+    Stefano Berardi 
+    \newblock{Classical and Intuitionistic Arithmetic with Higher Order Comprehension Coincide on Inductive Well-Foundedness}.
+    \newblock{In 24th EACSL Annual Conference on Computer Science Logic (CSL 2015) }.
+    \newblock{Leibniz International Proceedings in Informatics (LIPIcs), Volume 41, pp. 343-358}.
+     \newblock{Schloss Dagstuhl – Leibniz-Zentrum für Informatik (2015)}.
+      \newblock{https://doi.org/10.4230/LIPIcs.CSL.2015.343}.
+
+\end{thebibliography}
+
 \end{document}

### 2025-02-23 Relations/Paper/Conclusion.tex
Done

--- 2025-02-23 Relations/Paper/Conclusion.tex
@@
 
-Recap the main takeaways from each piece.
-\begin{itemize}
-  \item ARS results are effective for finitely branching and decidable relations
-  --- covers first-order TRSs and the lambda calculus.
-  \item Identification of ``sufficiency frontier'' for completeness (termination and confluence).
-  It also collapses many well-foundedness properties.
-  \item Also discuss open problems, unprovable implications, etc.
-  Maybe mention the Kleene tree idea, or at least include the reference to the Bezem--Coquand paper.
-  \item Throughout this effort, we found that the classical theorems often assume
-  more than is necessary, and these distinctions becomes especially pronounced
+In conclusion, we have formalized the basic results of ARS theory as
+presented in \cite{Terese}.  Our investigations show that much of this
+theory can be made effective for most languages one typically encounters
+in programming language theory.
+Throughout this effort, we found that the classical theorems often assume
+  more than is necessary, and these distinctions become especially pronounced
   in the context of constructive logic.
-  \item \emph{Formalizing classical ARS theory in the Curry--Howard framework
-  lead to improvements of classical ARS results.}
-\end{itemize}
+  Seeking to optimize hypotheses in every proof, we obtaining marginal improvements of the standard
+termination and confluence criteria.
+We also identified several new ARS properties
+and established their relationship with the standard notions.
+This provided us with a
+clearer structural understanding of how different properties interact
+with one another, contributing to a more refined and
+expressive formulation of ARS theory.
+
+Our work lays the ground for further extensions.  It makes standard ARS results
+ready for immediate use in formalizations of term rewriting systems and typed
+lambda calculi.
+
+% In the future, we would like to formalize more advanced ARS results.
+% We would
+
+% Recap the main takeaways from each piece.
+% \begin{itemize}
+%   \item ARS results are effective for finitely branching and decidable relations
+%   --- covers first-order TRSs and the lambda calculus.
+%   \item Identification of ``sufficiency frontier'' for completeness (termination and confluence).
+%   It also collapses many well-foundedness properties.
+%   \item Also discuss open problems, unprovable implications, etc.
+%   Maybe mention the Kleene tree idea, or at least include the reference to the Bezem--Coquand paper.
+%   \item Throughout this effort, we found that the classical theorems often assume
+%   more than is necessary, and these distinctions becomes especially pronounced
+%   in the context of constructive logic.
+%   \item \emph{Formalizing classical ARS theory in the Curry--Howard framework
+%   lead to improvements of classical ARS results.} In the process, new properties were identified,
+%    offering a clearer structural understanding of how different properties interact
+%     to establish completeness. These insights contribute to a more refined and
+%      expressive formulation of ARS theory.
+%   \item We believe the fact that $\isWFseq$ does not imply $\isWFacc$
+%   can be established by the methods of Bezem et al.
+%
+% \end{itemize}

### 2025-02-28 Relations/Paper/FinalTODO.tex
updating ARS branch

@@
+\documentclass{scrartcl}
+
+\input{packages.tex}
+\input{macros.tex}
+
+\begin{document}
+
+\section{Feb 28 meeting}
+
+\begin{enumerate}
+  \item Add the implication RisWCR, x in WN and SM implies x in SN to Section 4.3.
+  \item Clean up [TeReSe] references.
+  \item Clean up the Well-foundedness
+  \item Put up all classical principles in one place
+  \item Organize the repo, hide private work.
+  \item Clean up the Implications file, rename section etc.
+  \item Getting rid of confluent/weakly confluent definition, standardize
+\end{enumerate}
+
+For the long term.
+\begin{itemize}
+  \item Knaster--Tarski, look over that
+  \item Kleene tree to disprove isWFseq implies isWFacc
+\end{itemize}
+
 \section{TODO}
@@
 \end{enumerate}
+
+\end{document}

### 2025-02-28 Relations/notes.tex
updating ARS branch

@@
 
-\usepackage{xcolor}
+\usepackage[dvipsnames]{xcolor}
 
@@
 
-\section*{Notes}
+\section{Final notes about well-foundedness}
+
+\begin{enumerate}
+  \item The implication acc $\to$ seq requires only decidability of the relation itself.
+  \item Finitely branching and decidable implies that they're all equivalent, almost.
+
+\end{enumerate}
 
@@
 Also discuss open problems, unprovable implications, etc.
-Maybe mention the Kleene tree idea, or at least include the reference to the Bezem-Coquand paper.
+Maybe mention the Kleene tree idea, or at least include the reference to the Bezem--Coquand paper.
 
-\section{Motivation}
+\section{Introduction}
+We present a formalization of the basic Abstract Rewriting Systems (ARS) theory in the Agda proof assistant.
+This is part of a larger effort to develop a library of formalized programming language theory (PL)
+at Appalachian State University.
+Since Term Rewriting Systems (TRS) play a foundational role in programming languages,
+while ARS encompass the basic facts about rewriting relations in general,
+establishing these facts is part of the necessary infrastructure required to
+pursue the broader project.  The present contribution can therefore be seen as
+``bootstrapping'' Appstate's new formalized PL repository.
 
-The standard presentation in Terese makes liberal use of classical logic.
-Should stress effectivity of type-theoretic formalization.
+This broader goal also drives the main design choices in our approach.
+Since rewriting theory is concerned with a fine-grained analysis of computation,
+the most natural vehicle for formalizing it is type theory based on the
+Curry--Howard isomorphism, which Agda implements.  Proofs in this language
+are automatically effective, and implicitly carry the code implementing the
+transformations from the hypotheses to the conclusion.  For example,
+a proof that a given TRS is terminating automatically renders a function that
+computes a normal form of any term in its domain.
+
+Staying within this paradigm requires the proofs to be constructive.
+Moreover, it requires us to avoid any axioms or postulates, such as function
+extensionality, uniqueness of identity proofs, univalence, etc.
+While most of ARS results are indeed constructive, standard presentations,
+ including \hired{[Terese]}, make liberal use of classical logic.
+Our paper can thus be read as a thoroughly constructive
+development of elementary ARS theory.
+
+Before we proceed further, let us consider two formalization scenarios where
+our contribution can be useful.
+
+\subsubsection*{Example 1. Formalization of typed lambda calculus.}
+
+Suppose one is formalizing the standard metatheory of
+a typed lambda calculus.  To show confluence, one possible approach is to
+first establish the Church--Rosser theorem for the untyped lambda calculus,
+then invoke the Subject Reduction Theorem.
+However, suppose one has already independently verified Strong Normalization.
+Invoking Newman's lemma, one can then conclude confluence from the weak
+diamond property, which is generally a much simpler fact to prove.
+
+\subsubsection*{Example 2. Quotients of types.}
+Suppose one wishes to construct the initial model of an algebraic theory.
+The classical definition involves the quotient of a free algebra by
+the equivalence relation induced by the theory.
+The quotient is problematic operation in type theory.
+While there are various solutions, such as Higher Inductive Types,
+or Quotient Inductive--Inductive Types, these require one to extend the
+basic type theory with new constructs.
+
+However, if the algebraic theory in question admits a convergent presentation,
+by a confluent and terminating relation $R : A \to A \to Set$, one can define the type of
+$R$-normal forms as
+\[  (\Sigma n : A) (\Pi x : A) \lnot P n x \]
+In many applications, this type can substitute the true quotient satisfactorily.
+(In univalent or cubical type theories, one can moreover show this type to be
+a set, provided the domain $A$ is.)
+
+As these examples illustrate, a fully effective implementation of basic ARS results
+can be very helpful in many settings arising in programming language theory.
+
 \section{Contributions}
-
+Our contributions
 \begin{itemize}
@@
 
-\section{Formalization principles}
+\subsection{Formalization principles}
+\hired{One of our design goals is to stay within pure type theory as much as possible,
+therefore we adopt the following principles.}
 
@@
 
+\subsection{Misc.}
 One big item in this development was studying various incaranations of the concept of well-foundedness in constructive context.

### 2025-03-13 QADT/iso_research_more_general.py
some examples and notes

@@ -1,7 +1,7 @@
 import re
 def main():
-    diff = [1, 0, 1]
-    poly = [0, 0, 0, 1, 0, 0, 0]
+    diff = [1, 0, 0, 0, 0, 0, 1]
+    poly = [1, 0, 0, 0, 1, 0, 0]
     # diff = [1, 0, 0, 0, 0, 1]
     # poly = [1, 1, 0, 0, 0, 1]
     # poly = [0, 0, 1, 1, 0, 0, 0, 1]

### 2025-03-13 Relations/Paper/Implications.tex

@@
 
-The implications in this diagram are formalized in \texttt{ARS-Implications.agda}. The classical property of being minimally decidable is 
-required to complete the implication from $\SN$ to $\WN$, as can be seen in our formalization \sacomment{Rewrite this section}
+The implications in this diagram are formalized in \texttt{ARS-Implications.agda}. 
+The implication from $\SN$ to $\WN$ relies on the classical decidability of the property 
+of being $R$-minimal, as demonstrated in our formalization:
 
 \verb|SNdec→WN : (~R R) isMinDec → SN ⊆ WN|
-
-The isMinDec property \sacomment{refer to list of classical properties here} states that all elements either have a relation to some other element, or 
-there is no other element to which they have a relation. \greyout{If the element relates to no other element then it is terminating 
-and so trivially $\WN$. If the element does relate to some other element $y \in A$, then we recursively apply our claim to 
-$y$ and because we know that we have the property of $\SN$ we must eventually reach a terminating element.}
 

### 2025-03-13 Relations/Paper/WFFigure.tex

@@
       \node (std1) [draw] {isWFacc};
-      \node (std2) [right of=std1, draw] {isWFind};
-      \node (std3) [right of=std2, draw] {isWFseq};
-      \node (std4) [right of=std3, draw] {isWFmin};
+      \node (std2) [right of=std1, draw, xshift=1cm] {isWFind};
+      \node (std3) [right of=std2, draw, xshift=1cm] {isWFseq};
+      \node (std4) [right of=std3, draw, xshift=1cm] {isWFmin};
 

### 2025-03-13 Relations/Paper/Well-foundedness.tex

--- 2025-02-11 Relations/Paper/Well-foundedness.tex
@@
 \section{Well-foundedness}
+
+\newcommand{\isWFacc}{\mathtt{isWFacc}}
+\newcommand{\isWFseq}{\mathtt{isWFseq}}
+\newcommand{\isWFmin}{\mathtt{isWFmin}}
+\newcommand{\isWFaccm}{\mathtt{isWFacc-}}
+\newcommand{\isWFseqm}{\mathtt{isWFseq-}}
+\newcommand{\isWFminm}{\mathtt{isWFmin-}}
+
+\newcommand{\isMinDec}{\mathtt{isMinDec}}
+
+\newcommand{\then}{\Longrightarrow}
 \label{sec:Well-foundedness}
+
+An abstract reduction $\to_R$ is strongly normalizing
+if and only if the converse relation is well-founded.
+In this section, we will compare several definitions of well-foundedness.
+
+\subsection{The main definitions}
+
+The various formulations of well-foundedness are based on the following notions.
+\begin{definition}
+  Let $R \subseteq A \times A$.  We write $Rxy$ when $(x,y) \in R$.
+  \begin{enumerate}
+    \item $P \subseteq A$ is \emph{inductive}
+    if, for each $x \in A$, $(\forall y. Ryx \to y \in P)$ implies $x \in P$.
+
+    \item $x \in A$ is \emph{accessible} if $x \in P$ for each inductive $P$.
+
+    \item $x \in A$ is \emph{$P$-minimal} if $x \in P$ and for all $y$,
+    $Ryx$ implies $y \notin P$.
+
+    \item $s : \nat \to A$ is \emph{$R$-decreasing} if for all $k$, $(s(k+1),s(k)) \in R$.
+  \end{enumerate}
+\end{definition}
+
+In \cite{Terese}, well-foundedness is defined as in the classical mathematics textbooks,
+as the absence of an infinite $R$-decreasing sequence.
+Translating this statement directly into type theory yields the formula
+\[\tag{$\isWFseqm$} \lnot \big(\exists s : \nat \to A \forall k : \nat. (s(k+1),s(k)) \in R \big) \]
+(The label $\isWFseqm$ refers to the name of the corresponding term in \texttt{Wellfoundedness.agda}.)
+Constructively, this is not a useful hypothesis, as it does not provide any positive computational content and requires an explicit sequence to be defined.
+
+A stronger formulation asserts that, for any sequence, there exists an element
+in the sequence that does not reduce to the next one.  This yields the statement
+\[\tag{$\isWFseq$} \forall s : \nat \to A \exists k : \nat. (s(k),s(k+1)) \notin R \]
+
+These two conditions are classically equivalent, but not constructively so.
+Indeed, $\isWFseq$ certainly implies $\isWFseqm$, but the converse only holds classically.
+
+Another classical formulation of well-foundedness
+asserts that every non-empty subset
+contains a minimal element.  That is,
+\[ \tag{$\isWFmin$} \forall P \subseteq A. P \neq \emptyset \to \exists x \in P. (\forall y. Ryx \to y\notin P) \]
+
+While classically equivalent to the previous one, see \cite[Exercise A.1.8]{Terese},
+constructively we only have the implication $\isWFmin \then \isWFseq$.
+
+The canonical constructive definition of well-foundedness is that
+every inductive predicate is universally true.
+This is constructively equivalent to the statement that every element
+is accessible.  In Agda, these concepts are encoded as follows.
+{\small
+\begin{verbatim}
+  _-inductive_ : 𝓟 A → Set
+  _-inductive_ φ = ∀ x → (∀ y → R y x → φ y) → φ x
+
+  _isWFind : Set₁
+  _isWFind = ∀ (φ : 𝓟 A) → _-inductive_ φ → ∀ x → φ x
+
+  data _-accessible : 𝓟 A where
+    acc : ∀ {x : A} → (∀ y → R y x → _-accessible y) → _-accessible x
+
+  _isWFacc : Set
+  _isWFacc = ∀ (x : A) → x ∈ _-accessible
+\end{verbatim}
+}
+Although the two notions are equivalent, the latter definition allows us to do induction on the proof of accessibility of an individual element $x \in A$.
+This makes such proofs easier to write in Agda, thus we take
+\verb|_isWFacc| as \emph{the} standard notion of well-foundedness for relations.
+
+\subsection{Relations between the main definitions}
+
+We have now seen five notions of a well-founded relation, only two of which
+are seen to be logically equivalent.
+
+This raises several questions.
+\begin{itemize}
+\item Are all these notions truly distinct?  If one cannot furnish a proof of implication,
+can we provide a counterexample?
+\item Under what hypotheses do the implications become provable?
+\item How ``admissible'' are such hypotheses, and how often can we hope for them to be valid?
+\end{itemize}
+
+The situation of separating these notions is complicated by the fact that, for all
+\emph{definable} predicates, the classical and constructive notions do coincide.
+(We have not proved this, but see \cite{Berardi} for a related result.)
+So there is no hope to discriminate these notions via explicit counterexamples.
+Rather, we could attempt to show that one does not imply the other by proving that
+such an implication would yield a ``constructive taboo'': a proposition known to be
+unprovable without additional classical assumptions.
+
+For example, the archetype of a well-founded relation is the strict order \verb|<|
+of natural numbers.  The usual induction readily validates $\isWFacc$ for \verb|<|.
+  At the same time, the file \texttt{WFCounters.agda} shows that
+asserting $\isWFmin$ for \verb|<| implies that every subset of the natural numbers is decidable.  Since this is clearly not provable in Agda without classical axioms,
+this argument shows that the implication from $\isWFacc$ to $\isWFmin$ is not provable.
+
+Such distinctions have consequences for rewriting theory.
+For example, $x\in \SN_R$ iff $x$ is $\bar{R}$-accessible (where $\bar{R}$ denotes
+the converse of $R$).  Thus, if $\bar{R}$ is well-founded, $R \models \gSN$.
+Yet actually computing the normal form of a given $x$ seems to require a
+strong form of decidability of being $R$-minimal, namely:
+\[
+\tag{$\isMinDec$} \forall x. \left(\exists y. Ryx\right) \lor \left(\forall y. \lnot Ryx\right)
+\]
+(Note that asking whether $x$ is a normal form constitutes the weaker disjunction
+$\lnot\lnot\left(\exists y. Ryx\right) \lor \left(\forall y. \lnot Ryx\right)$.)
+
+On the other hand, $\isWFmin$ trivially implies that each $x \in A$ is weakly normalizing.
+Indeed, given $x \in A$, consider the predicate $P_x(y) = x \mstep y$.
+This predicate is non-empty, since the empty reduction yields a proof of $P_x(x)$.
+Let $n$ be a $P_x$-minimal element.  Then $x \mstep n$.  Moreover, for any $y$,
+If $x \rstep y$, then $\lnot(P_x)$.  But since reductions from $x$ are closed downward,
+no such $y$ can exist, and hence $n$ is a normal form of $x$.
+
+% \greyout{From the perspective of rewriting theory, it would seem wild indeed if
+% $\SN$ did not imply $\WN$.
+%
+These questions motivated us to take a closer look at the issue of well-foundedness.
+Our analysis revealed a number of additional related hypotheses, having a complex
+network of relations.  %These are displayed in Figure \ref{f:wf}.
+These are recorded in the file \verb|Wellfounded.agda|

### 2025-03-13 UTA/notes.tex
more ura

@@
 \newcommand{\msl}{\mathpzc{Msl}}
+
+\newcommand{\mcI}{\mathcal{I}}
 
@@
   \item Implement/verify the decider for the subtyping relation between trees.
+  \item To look into strong normalization criterion.
 \end{itemize}
@@
 
+\section{Conjecture}
+
+Let $\types$ be the set of simple types.
+An \emph{inequational type theory} is a set of type inequalities
+  \[ \mcI = \setof{A_i \le B_i \mid i \in I, A_i \in \types, B_i \in \types} \]
+
+In most cases, we will be interested in the case when $I = |\mcI|$ is a finite set.
+
+Let $n \in \nat$, $I = \setof{1,..,n}$, and $\mcI$ an inequational type theory
+over $I$.
+
+Let $V$ be the set of type atoms --- to be treated as type variables ---
+occuring in $\mcI$.
+
+The theory $\mcI$ can be transformed into a set $\mcI^+,\mcI^-$, where
+each $(A \le B) \in \mcI^+$ is of the form $\alpha \le T$,
+for some $\alpha \in V$ and $T \in \types$, and
+each $(A \le B) \in \mcI^-$ is of the form $T \le \alpha$,
+for some $\alpha \in V$ and $T \in \types$.
+
+For $\alpha \in V$, put
+\begin{align*}
+\mcI^+(\alpha) &= \setof{A \mid (\alpha \le A) \in \mcI^+}\\
+\mcI^-(\alpha) &= \setof{A \mid (A \le \alpha) \in \mcI^-}
+\end{align*}
+
+We can further transform this subtyping theory by replacing the set of variables
+$V$ by $V^+ \cup V^-$, where
+\begin{align*}
+  V^+ &= \setof{\alpha^+ \mid \alpha \in V} \\
+  V^- &= \setof{\alpha^- \mid \alpha \in V}
+\end{align*}
+
+For $\alpha \in V$, and for $A=A(\alpha) \in \types$, let $A(\alpha^-,\alpha^+)$
+be obtained by replacing all positive occurrences of $\alpha$ in $A$ with $\alpha^+$,
+and all negative occurrences of $\alpha$ in $A$ with $\alpha^-$.
+
+Let $\mcS^0 = \setof{\alpha^- \le \alpha^+ \mid \alpha \in V}$.
+
+Let $\mcS(\mcI) = \mcS^0 \cup \mcS^+ \cup \mcS^-$, where
+\begin{align*}
+  \mcS^+ = \setof{\alpha^+ \le A(\alpha^+,\alpha^-) \mid A \in \mcI^+(\alpha)}\\
+  \mcS^- = \setof{A(\alpha^-,\alpha^+) \le \alpha^- \mid A \in \mcI^-(\alpha)}
+\end{align*}
+
+By taking inversion closure, these sets can be assumed to be minimal.
+
+\textsc{Proposition.}  $\mcI$ admits a solution in $\types_\cap$ if and only if
+$\mcS(\mcI)$ admits a solution in $\types_\cap$.
+
+\textsc{Conjecture.} $\mcS(\mcI)$ admits a solution in $\types_\cap$ if and only if
+there is no ``circular constraint'': a type $B$ such that, for some
+$\alpha \in V$, $A^+ \in \mcI^+(\alpha)$, $A^- \in \mcI^-(\alpha)$, one has:
+% \[ \greyout{A^+(\alpha^-,\alpha^+) \le B \le A^-(\alpha^-,\alpha^+)} \]
+\[ A^+(\alpha^+,\alpha^-) \le B \le A^-(\alpha^-,\alpha^+) \]
+
+\subsection*{2024.06.11 -- Reasons for believing the conjecture}
+
+The condition is obviously necessary, since a circular constraint immediately
+results in $\alpha = A(\alpha)$, which is not solvable in $\types_\cap$.
+
+As for the necessity, we can make the following observations.
+
+First, the ``positive'' side, $\mcS^+$ can be solved by taking
+$\alpha^+ := \alpha \cap A_1 \cap \cdots \cap A_k$, where $\mcI^+(\alpha) = \setof{A_1,\dots,A_k}$.
+
+As for the negative side, we could invert the constraints by mapping everything into
+a new type atom, $\gamma$.
+
+But how do we get the most ``general'' unifier?  That is, how do we get to the situation
+where, we know that the constraints are solvable, but want the most generic scheme
+of the solution types?
+
 \end{document}

### 2025-04-21 Relations/Paper/Introduction.tex
Todos started and simple fixes made.

@@
 Since Strong Normalization is a central concept in ARS theory,
-special attention in our work was given to various incaranations of the concept of well-foundedness in the constructive context.
+special attention in our work was given to various incarnations of the concept of well-foundedness in the constructive context.
 (Strong normalization is well-foundedness of the converse relation.)

### 2025-04-21 Relations/Paper/Summer_2025_TODO.tex
Todos started and simple fixes made.

\documentclass{article}
\usepackage{enumitem,amssymb}
\newlist{todolist}{itemize}{2}
\setlist[todolist]{label=$\square$}
\usepackage{pifont}
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%
\newcommand{\done}{\rlap{$\square$}{\raisebox{2pt}{\large\hspace{1pt}\cmark}}%
\hspace{-2.5pt}}
\newcommand{\wontfix}{\rlap{$\square$}{\large\hspace{1pt}\xmark}}

\begin{document}
\title{Summer 2025 ToDo}
\maketitle

\section*{Week starting 21st April}
\begin{itemize}
  \item Items from review

  \begin{todolist}
    \item (Review 1) Elaborate on our motivations in the introduction (reviewer wasn't sure how relevant this is to ARS theory itself/ sees it as too minor a contribution.)
    \item [\done] (Review 1) Typo: incaranations $\to$ incarnations. 
    \item (Review 1) Improve fonts for constant and text (refering to a definition on line 258). General formatting imrpovement for how we set out defns.
    \item (Review 1) Improve the layout on line 270 where we set out iiSeq. This should get fixed with an overall improvement in how we set out definitions. We should stop using itemize and verb combination.
    \item [\done] (Review 1) Typo: we obtaining $\to$ we obtain (this is in the conclusion which we want to rewrite entirely).
    \item [\done] (Review 1) Citation expansion for program=proof.
    \item (Review 2) Unconvinced by the motivations for the project, believes the same can be achieved in a classical framework. So maybe we should explain our motivations more clearly.
    \item (Review 2) Not convinced by our definitions, as they are imprecise and lack quantifiers. 
    \item (Review 2) Issue with definition of R|=RP on line 188. Use of bounded is ambiguous. We should clarify which use of bounded.
    \item (Our notes) Improve proposition 11 on line 194, we want to make the clame that RP- $\to$ RP, and either have a one line proof or refer to the proof in Agda. 
    \item (Review 2) Section 3 is "full of repeitions and paraphrases between the statements in natural language and corresponding formalization". We can try and think of a way to get it to flow bettwe, we do want to provide natural language summaries of what is in the code!
    \item (Review 2) Struggled to understand the implications tables. We should add a reminder that bold font is global. We should rethink the tables generally to make them clearer. Don't comma seperate and don't denote counterexamples as CE-XX.
    \item (Review 2) Struggled to find the relevant agda code for the various definitions. We should find a way to better link the two.
    \item (Review 2) TeReSe is not state of the art. We need state of the art references. Try this: https://termination-portal.org/wiki/WScT 
    \item (Review 2) Clarify Notation 7 on line 159: "Choose a uniform notation, X or NP, but not both".
    \item (Review 2) "l 169: An annoying notational collision between the two arrows -> at different heights."I'm not too sure what they're referring to, though there could be some ambiguity with the arrows here, especially with use of $UN\to$.
    \item (Review 2) "l 361: Swap s(k+1) and s(k) " We should clarify the definition here otherwise people (evidently) get confused. 
    \item (Review 2) "l 422: $P_x$ has no arguments?"
    \item (Review 3) Check out and include the following related work:
    \begin{itemize}
        \item Christian Sternagel and René Thieman formalized results on Abstract Rewriting in Isabelle https://www.isa-afp.org/entries/Abstract-Rewriting.html
        \item André Galdino and Mauricio Ayala-Rincón also developed a theory in PVS regarding ARS and TRS  https://github.com/nasa/pvslib/tree/master/TRS
        \item What are the differences and improvements of the formalization in this paper and the ones in the literature?  
    \end{itemize}
    \item (Review 3) * From the formalization, the authors could explain some features and syntax of Agda for readers unfamiliar with this proof assistant. What were the main attributes of Agda that helped you in the formalization process? In line 204, the paper brings the definition of an element being finitely branching and states that the formulation of such a definition is given in line 206. FB a seems to be a set (in line 206), not a boolean. Also, in the formalization of FB a, the authors use R b a instead of R a b. What elements of Agda allow such specification capturing exactly Def. 12.
    \item (Review 3) In line 270, isWFseq- is used in Section 3 but defined only in Section 5.
    \item (Review 3) In line 192, the authors state that (in TeReSe) Ind denotes BP. However, in line 186, BP is defined from an R-increasing sequence, whereas this statement is not required in the definition of Ind by TeReSe. How does this difference impact the formalizations and generalizations pointed out in Section 3.3.3? (Maybe we should explicitly address all difference with TeReSe in one location.)
  \end{todolist}

  \item Other ToDo 
  \begin{todolist}
    \item Make Latex version of WF implications .
    \item Verify which implications have and have not been formalized from the image.
  \end{todolist}
\end{itemize}
\end{document}

### 2025-04-22 Relations/Paper/WF_diagram.tex
Initial run of WF diagram

\documentclass{article}
\usepackage{tikz}
\usetikzlibrary{arrows.meta, positioning}

\begin{document}

\begin{tikzpicture}[
  node distance=1cm and .5cm,
  box/.style={draw, rectangle, rounded corners, minimum width=1cm, minimum height=1cm, align=center},
  arrow/.style={-{Latex}, thick}
]

% Row 1: WFacc
\node[box] (WFacc) {WFacc};
\node[box, right=of WFacc] (NNWFacc) {$\lnot\lnot$WFacc};
\node[box, right=of NNWFacc] (WFaccM) {WFacc-};

\draw[arrow] (WFacc) -- (NNWFacc);
\draw[arrow] (NNWFacc) -- (WFaccM);
\draw[arrow, bend right] (WFaccM) to node[above, text=red] {accDNE} (WFacc);

% Row 2: WFind
\node[box, below=of WFacc] (WFind) {WFind};
\node[box, right=of WFind] (NNWFind) {$\lnot\lnot$WFind};
\node[box, right=of NNWFind] (WFindM) {WFind-};

\draw[arrow] (WFind) -- (NNWFind);
\draw[arrow] (NNWFind) -- (WFindM);

% Row 3: WFseq
\node[box, below=of WFind] (WFseq) {WFseq};
\node[box, right=of WFseq] (NNWFseq) {$\lnot\lnot$WFseq};
\node[box, right=of NNWFseq] (WFseqM) {WFseq-};

\draw[arrow] (WFseq) -- (NNWFseq);
\draw[arrow] (NNWFseq) -- (WFseqM);

% Row 4: WFmin -> WFmin-
\node[box, below=of WFseq] (WFmin) {WFmin};
\node[box, right=2.8cm of WFmin] (WFminM) {WFmin-};

\draw[arrow] (WFmin) -- (WFminM);

% Row 5: WFminDNE -> WFminDNE-
\node[box, below=of WFmin] (WFminDNE) {WFminDNE};
\node[box, right=2.1cm of WFminDNE] (WFminDNEM) {WFminDNE-};

\draw[arrow] (WFminDNE) -- (WFminDNEM);

% Arrows between rows
\draw[arrow, <->] (WFacc) -- (WFind);
\draw[arrow, <->] (NNWFacc) -- (NNWFind);
\draw[arrow, <->] (WFaccM) -- (WFindM);

\draw[arrow] (WFind) to node[right, text = red] {Rdec} (WFseq);
\draw[arrow, bend left] (WFindM) to (WFseqM);
\draw[arrow, bend left] (WFseqM) to node[left, text=red] {accCor} (WFindM);  
\draw[arrow, bend left = 45] (WFindM) to (WFminM);

\draw[arrow] (WFmin) -- (WFseq);
\draw[arrow] (WFminM) -- (WFseqM);
\draw[arrow] (WFmin) -- (WFminDNE);
\draw[arrow, <->] (WFminM) -- (WFminDNEM);

\draw[arrow, bend left=60] (WFminDNE) to node[left, text = red] {accDNE} (WFacc);
\draw[arrow, bend left=45] (WFminDNE) to node[pos=0.9, left, text=red] {Rdec$+$MP} (WFseq);
\draw[arrow, bend right=45] (WFminDNEM) to node[right, text=red] {FB} (WFaccM);

\end{tikzpicture}

\end{document}

### 2025-04-23 Relations/Paper/Summer_2025_TODO.tex
Minor update to wellfounded

@@
   \begin{todolist}
-    \item Make Latex version of WF implications .
+    \item [\done] Make Latex version of WF implications (initial draft).
     \item Verify which implications have and have not been formalized from the image.
+    \item (Missing imp) $\lnot \lnot$ WFacc $\leftrightarrow$ $\lnot \lnot WFind$. 
+    \item [\done] (Missing imp) WFmin- $\to$ WFDNE-
+    \item (Missing imp) All of the implicaions from the standard WF definition to the $\lnot \lnot$ definition. 
+    \item Sam TODO: I still don't have a coherent understanding in my head as to how we relate the WF and ARS sections of the paper.
+I need to go through it and either understand it or come with questions to Friday's meeting.
   \end{todolist}

### 2025-04-28 Relations/Paper/Summer_2025_TODO.tex
Minor todo update
Progress on wellfounded, DNE error to fix.

@@
     \item [\done] Make Latex version of WF implications (initial draft).
-    \item Verify which implications have and have not been formalized from the image.
+    \item [\done] Verify which implications have and have not been formalized from the image.
     \item (Missing imp) $\lnot \lnot$ WFacc $\leftrightarrow$ $\lnot \lnot WFind$. 
     \item [\done] (Missing imp) WFmin- $\to$ WFDNE-
-    \item (Missing imp) All of the implicaions from the standard WF definition to the $\lnot \lnot$ definition. 
-    \item Sam TODO: I still don't have a coherent understanding in my head as to how we relate the WF and ARS sections of the paper.
+    \item [\done] (Missing imp) All of the implicaions from the standard WF definition to the $\lnot \lnot$ definition. 
+    \item [\done] Sam TODO: I still don't have a coherent understanding in my head as to how we relate the WF and ARS sections of the paper.
 I need to go through it and either understand it or come with questions to Friday's meeting.
@@
 \end{itemize}
+
+\section*{Week starting April 28th}
+\begin{itemize}
+  \item Below notes from meeting on April 25th.
+  \begin{todolist}
+    \item Fix Wellfounded.agda after changes made during meeting.
+    \item Carry on refactoring Wellfounded.agda once fixed, breaking it up if necessary.
+    \item Think about how to organize the Git repo going forward. For example, could be good to have a parent folder with ARS and WF, with a private dir for paper 
+    \item (Research item) How to go from WFseq to WFacc - possible that the Kleene Tree is a solution.
+    \item (Research item) Go deeper in the related works and see which are most relevant. Make a list of works and give summaries to be used in future papers. 
+    \item (Research item) Find a concrete application of generalized Newman's Lemma. 
+    \item (Research item) Use TeReSe to create a list of rewrite systems.
+    \item (Research item) Work on the missing implicaitons from the paper. So far we believe this is just CR $\to$ CP in the ARS section. 
+    \item (Research item) Formalize a first order term rewriting system (I can't remember what the motivation for this was).
+    \item (Research item) Carry out research on rewriting counterexamples like our own so we can try and put them into some sort of context. Have our counerexamples been shown before?
+    \item (Research item) Do we want to reincorporate Knaster Tarski?  
+  \end{todolist}
+\end{itemize}
 \end{document}

### 2025-05-26 QADT/notes.tex
new note

@@
 
+\section*{2025.05.22}
+\subsection*{Misc.\ notes}
+\begin{itemize}
+  \item Iterating linear functors does not change the roots
+  \item To compute the roots of $H(H(X))$, should solve $H(x) = r_i$, where $r_i$ are the roots of $H(x)$.
+\end{itemize}
+
+\subsection*{Questions}
+\begin{enumerate}
+  \item Are colimits of the diagram induced by an arbitrary polynomial functor $P$ and $P \circ P$ the same?
+
+  (Obviously, Yes.)
+
+  \item Can that be generalized to arbitrary unfoldings?
+
+  Can that be generalized to ``$1.5$-unfoldings'' ?
+
+  \item When we ``add a non-zero root'', do we automatically get a
+  rig isomorphism inducing an isomorphism to the original $\mu$-type?
+
+  \item Prove the surjectivity criterion relating the image of the fold
+  from the initial algebra to the final coalgebra?
+
+  \item Big goal: When an F-algebra structure is given by a rig iso,
+  the induced fold is epi (and thus iso).
+
+  \item What are the most generic iso rules for the mu-constructor?
+
+  \item Can every ADT $T(\vec x)$ (with any nesting of $\mu$s) be realized
+  ``with all $\mu$s on the outside''?
+
+  Strong version:  $T(\vec x) = \mu \vec y. P(\vec x, \vec y)$, where $P(\vec x, \vec y)$ is a polynomial.
+
+  Weak version:  $T(\vec x) = U(\vec x, \mu \vec y. P(\vec x, \vec y))$, where $U(\vec x)$,
+  $P(\vec x, \vec y)$ are polynomials.
+
+  Weaker version: Same, but allowing simultaneous solution to a system of equations
+  (I.E., working with fixed points of functors on $Set^n$.)
+
+  \item Prove that $\mu x. \mu y. P(x,y) = \mu x. P(x,x)$?
+
+  (Almost certainly yes.)
+
+  It would immediately follow that e.g.,
+  $\mu \vec x. P(\vec x) = \mu x. P(x,\dots,x) = \mu \vec x. P(\vec{\pi x})$,
+  where $\vec{\pi x}$ is any permutation/mere function
+  of $\vec x$.
+
+  \item Look at $\nat \times \nat$.
+
+  \item Look at equational laws between rig isos/elements of the iso type.
+
+  \item
+\end{enumerate}
+
 \maketitle
@@
 \begin{itemize}
-  \item $s(X) = 1 + 2\cdot X$, $S = \mu X. s(x)$
+  \item $s(X) = 1 + 2X$, $S = \mu X. s(x)$
   \item $t(X) = 1 + X^2$, $T = \mu X. t(x)$
@@
   \item $h(X) = 1 + X + X^3$, $H = \mu X. h(x)$
-  \item $h(X) = 1 + X^2 + X^4$
+  \item $q(X) = 1 + X^2 + X^4$, $Q = \mu X. q(x)$
 \end{itemize}
@@
   \item $T^3 = M^2$
-  \item $T^3$ and $M^2$ vs. $S$?
+  \item $T^3$ vs.\ $M^2$ vs.\ $S$?
   \item

### 2025-05-29 Relations/Paper/Formalization.tex
Renamed implications section to hierarchy. Updated hierarchy section.

@@
 which led us to examine the condition on $s (i)$ appearing inside $\RP$ more closely. This condition provides a generalization of the notion of a normal form, 
-which we explore in detail in Section \ref{sec:Implications}.
+which we explore in detail in Section \ref{sec:Hierarchy}.
 
@@
 is decidable as this property enables us 
-to construct a witness for an element that either does or does not have the property $\SN$. Such a witness was necessary for our proof. \sacomment{Link to decidable in later section?}
+to construct a witness for an element that either does or does not have the property $\SN$. Such a witness was necessary for our proof. 
+% \sacomment{Link to decidable in later section?}
 

### 2025-05-29 Relations/Paper/Implications.tex
Renamed implications section to hierarchy. Updated hierarchy section.

@@
-\section{Implications}
-\label{sec:Implications}
+\section{Hierarchy}
+\label{sec:Hierarchy}
 
@@
 % show chains of implications starting from these properties.
+This section examines the hierarchy of ARS properties. 
+In programming language theory, $\SN$ and $\CR$ constitute the essential properties that 
+jointly establish completeness. 
+Consequently, our analysis centers on two primary categories of properties: those associated 
+with termination and those associated with confluence.
+% Possibly redundant introductory paragraph
+
 As discussed in Subsection \ref{subsec:def} we put forward $\RP$ as an alternative for $\Inc$. It is through examining $\RP$ that 
-we came to the definitions below.
+we came to the 'minimal` family of properties below. These properties help to augment our ARS hierarchy.
 
@@
 \begin{center}
-
     \begin{tikzpicture}[auto,
@@
       % A box style
-      \tikzstyle{boxnode} = [draw, rectangle, text centered,minimum width=1.2cm, inner sep=3pt]
+      \tikzstyle{boxnode} = [draw, rectangle, text centered, minimum width=1.2cm, inner sep=3pt]
+
+      % Title nodes
+      \node[text width=4cm, align=center, font=\bfseries] at (-1.5,1) {Confluence Hierarchy};
+      \node[text width=4cm, align=center, font=\bfseries] at (5,1) {Termination Hierarchy};
 
@@
       \draw [arrowstyle] (SR) -- (WR);
+
+      % Optional: Add a separation line
+      \draw[dashed] (2.0,-1.5) -- (2.0,1.5);
     \end{tikzpicture}
@@
 The implications in this diagram are formalized in \texttt{ARS-Implications.agda}. 
+The hierarchy for confluencce requires no classical assumptions, however this is not the case for the hierarchy of terminating properties.
 The implication from $\SN$ to $\WN$ relies on the classical decidability of the property 
@@
 
-We are interested in seeing which combination of properties a relation requires in order to be complete (that is, $\gCR$ and $\gSN$). 
-The following tables show either that a given combination is complete, or the appropriate counterexample which demonstrates why 
-those properties do not provide the next property on the hierarchy.
+Having established the hierarchies of ARS properties, we now examine which property combinations are sufficient to reverse these implications and achieve completeness.
+The following tables illustrate, for each property combination, whether confluence (left box) and strong normalization (right box) are obtained.
+Where properties cannot be derived, we provide counterexamples demonstrating the necessity of additional conditions.
 
 The first table explores where the properties hold locally, the second explores where the properties hold globally. Counterexamples in the 
-first table assume $\WCR$ and in the second table assume $\gWCR$.
+first table assume $\WCR$ and in the second table assume $\gWCR$ (as a reminder, bold text is used to indicate a property holds globally).
+
 \clearpage
 \renewcommand*{\thefootnote}{\fnsymbol{footnote}}
+
 \begin{table}[h!]
     \centering
-    \begin{tabular}{|>{\columncolor{gray!30}}l|c|c|c|c|c|}
+    {\setlength{\arrayrulewidth}{1.5pt}  % Set horizontal rule thickness
+    \begin{tabular}{|>{\columncolor{gray!30}}l!{\vrule width 1.5pt}c|c!{\vrule width 1.5pt}c|c!{\vrule width 1.5pt}c|c!{\vrule width 1.5pt}c|c!{\vrule width 1.5pt}c|c|}
         \hline
-        \rowcolor{gray!30}     & $\WM$         & $\WN$         & $\SM$             & $\SMandWN$        & $\SN$ \\
+        \rowcolor{gray!30} & \multicolumn{2}{c!{\vrule width 1.5pt}}{$\WM$} & \multicolumn{2}{c!{\vrule width 1.5pt}}{$\WN$} & \multicolumn{2}{c!{\vrule width 1.5pt}}{$\SM$} & \multicolumn{2}{c!{\vrule width 1.5pt}}{$\SMandWN$} & \multicolumn{2}{c|}{$\SN$} \\
         \hline
-        $\UNto$ &  CE-\ref{CE:4}, CE-\ref{CE:12}     & CE-\ref{CE:4}, CE-\ref{CE:7}       & $\CR$\footnotemark[1] , CE-\ref{CE:9}          & $\CR$\footnotemark[1] , CE-\ref{CE:4}            & $\CR$\footnotemark[1] , $\SN$ \\
+        $\UNto$ & CE-\ref{CE:4} & CE-\ref{CE:12} & CE-\ref{CE:4} & CE-\ref{CE:7} & $\CR$\footnotemark[1] & CE-\ref{CE:9} & $\CR$\footnotemark[1] & CE-\ref{CE:4} & $\CR$\footnotemark[1] & $\SN$ \\
         \hline
-        $\NP$ & CE-\ref{CE:10},CE-\ref{CE:9}      & $\CR$, CE-\ref{CE:7}    & $\CR$\footnotemark[1]  , CE-\ref{CE:9}          & $\CR$, $\SN$      & $\CR$\footnotemark[2] , $\SN$ \\
+        $\NP$ & CE-\ref{CE:10} & CE-\ref{CE:9} & $\CR$ & CE-\ref{CE:7} & $\CR$\footnotemark[1] & CE-\ref{CE:9} & $\CR$ & $\SN$ & $\CR$\footnotemark[2] & $\SN$ \\
         \hline
-        $\MP$ & $\CR$ , CE-\ref{CE:9}    & $\CR$, CE-\ref{CE:7}    & $\CR$\footnotemark[2] , CE-\ref{CE:9} & $\CR$, $\SN$      & $\CR$\footnotemark[2] , $\SN$ \\
+        $\MP$ & $\CR$ & CE-\ref{CE:9} & $\CR$ & CE-\ref{CE:7} & $\CR$\footnotemark[2] & CE-\ref{CE:9} & $\CR$ & $\SN$ & $\CR$\footnotemark[2] & $\SN$ \\
         \hline
-        $\CR$   & $\CR$, CE-\ref{CE:9}     & $\CR$, CE-\ref{CE:7}     & $\CR$, CE-\ref{CE:9}        & $\CR$, $\SN$     & $\CR$ , $\SN$ \\
+        $\CR$ & $\CR$ & CE-\ref{CE:9} & $\CR$ & CE-\ref{CE:7} & $\CR$ & CE-\ref{CE:9} & $\CR$ & $\SN$ & $\CR$ & $\SN$ \\
         \hline
-
-    \end{tabular}
+    \end{tabular}}
     \caption{Local implications}

### 2025-05-29 Relations/Paper/Implications.tex
Tables updated to be clearer

@@
     \centering
-    {\setlength{\arrayrulewidth}{1.5pt}  % Set horizontal rule thickness
-    \begin{tabular}{|>{\columncolor{gray!30}}l!{\vrule width 1.5pt}c|c!{\vrule width 1.5pt}c|c!{\vrule width 1.5pt}c|c!{\vrule width 1.5pt}c|c!{\vrule width 1.5pt}c|c|}
-        \hline
-        \rowcolor{gray!30} & \multicolumn{2}{c!{\vrule width 1.5pt}}{$\WM$} & \multicolumn{2}{c!{\vrule width 1.5pt}}{$\WN$} & \multicolumn{2}{c!{\vrule width 1.5pt}}{$\SM$} & \multicolumn{2}{c!{\vrule width 1.5pt}}{$\SMandWN$} & \multicolumn{2}{c|}{$\SN$} \\
-        \hline
+    \renewcommand\arraystretch{1.2}
+    \begin{tabular}{!{\vrule width 1.5pt}
+        >{\columncolor{gray!30}}l
+        !{\vrule width 1.5pt}c|c
+        !{\vrule width 1.5pt}c|c
+        !{\vrule width 1.5pt}c|c
+        !{\vrule width 1.5pt}c|c
+        !{\vrule width 1.5pt}c|c!{\vrule width 1.5pt}}
+        \Xhline{1.5pt}
+        \rowcolor{gray!30} 
+        & \multicolumn{2}{c!{\vrule width 1.5pt}}{$\WM$}
+        & \multicolumn{2}{c!{\vrule width 1.5pt}}{$\WN$}
+        & \multicolumn{2}{c!{\vrule width 1.5pt}}{$\SM$}
+        & \multicolumn{2}{c!{\vrule width 1.5pt}}{$\SMandWN$}
+        & \multicolumn{2}{c!{\vrule width 1.5pt}}{$\SN$} \\
+        \Xhline{1.5pt}
         $\UNto$ & CE-\ref{CE:4} & CE-\ref{CE:12} & CE-\ref{CE:4} & CE-\ref{CE:7} & $\CR$\footnotemark[1] & CE-\ref{CE:9} & $\CR$\footnotemark[1] & CE-\ref{CE:4} & $\CR$\footnotemark[1] & $\SN$ \\
@@
         \hline
-    \end{tabular}}
+        \Xhline{1.5pt}
+    \end{tabular}
     \caption{Local implications}
 \end{table}
+
 \vspace{-1cm}
@@
     \centering
-    \begin{tabular}{|>{\columncolor{gray!30}}l|c|c|c|c|c|}
+    \renewcommand\arraystretch{1.2}
+    \begin{tabular}{!{\vrule width 1.5pt}
+        >{\columncolor{gray!30}}l
+        !{\vrule width 1.5pt}c|c
+        !{\vrule width 1.5pt}c|c
+        !{\vrule width 1.5pt}c|c
+        !{\vrule width 1.5pt}c|c
+        !{\vrule width 1.5pt}c|c!{\vrule width 1.5pt}}
+        \Xhline{1.5pt}
+        \rowcolor{gray!30} 
+        & \multicolumn{2}{c!{\vrule width 1.5pt}}{$\gWM$}
+        & \multicolumn{2}{c!{\vrule width 1.5pt}}{$\gWN$}
+        & \multicolumn{2}{c!{\vrule width 1.5pt}}{$\gSM$}
+        & \multicolumn{2}{c!{\vrule width 1.5pt}}{$\gSMandWN$}
+        & \multicolumn{2}{c!{\vrule width 1.5pt}}{$\gSN$} \\
+        \Xhline{1.5pt}
+        $\gUNto$ & CE-\ref{CE:2} & CE-\ref{CE:9} & $\gCR$ & CE-\ref{CE:7} & $\gCR$\footnotemark[1] & CE-\ref{CE:9} & $\gCR$ & $\gSN$ & $\gCR$\footnotemark[2] & $\gSN$ \\
         \hline
-        \rowcolor{gray!30}     & $\gWM$         & $\gWN$         & $\gSM$             & $\gSMandWN$        & $\gSN$ \\
+        $\gNP$ & CE-\ref{CE:3} & CE-\ref{CE:9} & $\gCR$ & CE-\ref{CE:7} & $\gCR$\footnotemark[1] & CE-\ref{CE:9} & $\gCR$ & $\gSN$ & $\gCR$\footnotemark[2] & $\gSN$ \\
         \hline
-        $\gUNto$ &  CE-\ref{CE:2}, CE-\ref{CE:9}     & $\gCR$, CE-\ref{CE:7}    & $\gCR$\footnotemark[1] , CE-\ref{CE:9}          & $\gCR$, $\gSN$      & $\gCR$\footnotemark[2] , $\gSN$ \\
+        $\gMP$ & $\gCR$ & CE-\ref{CE:9} & $\gCR$ & CE-\ref{CE:7} & $\gCR$\footnotemark[2] & CE-\ref{CE:9} & $\gCR$ & $\gSN$ & $\gCR$\footnotemark[2] & $\gSN$ \\
         \hline
-        $\gNP$ & CE-\ref{CE:3} , CE-\ref{CE:9}      & $\gCR$, CE-\ref{CE:7}    & $\gCR$\footnotemark[1] , CE-\ref{CE:9}          & $\gCR$, $\gSN$      & $\gCR$\footnotemark[2] , $\gSN$ \\
-        \hline
-        $\gMP$ & $\gCR$ , CE-\ref{CE:9}    & $\gCR$, CE-\ref{CE:7}    & $\gCR$\footnotemark[2] , CE-\ref{CE:9} & $\gCR$, $\gSN$    & $\gCR$\footnotemark[2] , $\gSN$ \\
-        \hline
-        $\gCR$   & $\gCR$, CE-\ref{CE:9}     & $\gCR$, CE-\ref{CE:7}     & $\gCR$, CE-\ref{CE:9}        & $\gCR$, $\gSN$      & $\gCR$ , $\gSN$ \\
-        \hline
-
+        $\gCR$ & $\gCR$ & CE-\ref{CE:9} & $\gCR$ & CE-\ref{CE:7} & $\gCR$ & CE-\ref{CE:9} & $\gCR$ & $\gSN$ & $\gCR$ & $\gSN$ \\
+        \Xhline{1.5pt}
     \end{tabular}

### 2025-05-29 Relations/Paper/Implications.tex
Updated the todos

@@
 
+The table should be interpreted as follows: for example, if a relation possesses the property $\NP$, then, according to the table, obtaining the property $\CR$ requires, at a minimum, the additional property $\WN$.
+Counterexample~\ref{CE:9} demonstrates that the combination of $\WM$ and $\NP$ is insufficient to guarantee $\CR$.
+
 \subsection{Counterexamples}\label{subsec:counterexamples}

### 2025-05-30 Relations/Paper/Implications.tex
Counterexamples badly numbered. Only halfway fixed!
Counterexmples updated in table. DOUBLE CHECK

@@
         \Xhline{1.5pt}
-        $\UNto$ & CE-\ref{CE:4} & CE-\ref{CE:12} & CE-\ref{CE:4} & CE-\ref{CE:7} & $\CR$\footnotemark[1] & CE-\ref{CE:9} & $\CR$\footnotemark[1] & CE-\ref{CE:4} & $\CR$\footnotemark[1] & $\SN$ \\
+        $\UNto$ & CE-\ref{CE:4} & CE-\ref{CE:11} & CE-\ref{CE:4} & CE-\ref{CE:6} & $\CR$\footnotemark[1] & CE-\ref{CE:8} & $\CR$\footnotemark[1] & CE-\ref{CE:4} & $\CR$\footnotemark[1] & $\SN$ \\
         \hline
-        $\NP$ & CE-\ref{CE:10} & CE-\ref{CE:9} & $\CR$ & CE-\ref{CE:7} & $\CR$\footnotemark[1] & CE-\ref{CE:9} & $\CR$ & $\SN$ & $\CR$\footnotemark[2] & $\SN$ \\
+        $\NP$ & CE-\ref{CE:9} & CE-\ref{CE:8} & $\CR$ & CE-\ref{CE:6} & $\CR$\footnotemark[1] & CE-\ref{CE:8} & $\CR$ & $\SN$ & $\CR$\footnotemark[2] & $\SN$ \\
         \hline
-        $\MP$ & $\CR$ & CE-\ref{CE:9} & $\CR$ & CE-\ref{CE:7} & $\CR$\footnotemark[2] & CE-\ref{CE:9} & $\CR$ & $\SN$ & $\CR$\footnotemark[2] & $\SN$ \\
+        $\MP$ & $\CR$ & CE-\ref{CE:8} & $\CR$ & CE-\ref{CE:6} & $\CR$\footnotemark[2] & CE-\ref{CE:8} & $\CR$ & $\SN$ & $\CR$\footnotemark[2] & $\SN$ \\
         \hline
-        $\CR$ & $\CR$ & CE-\ref{CE:9} & $\CR$ & CE-\ref{CE:7} & $\CR$ & CE-\ref{CE:9} & $\CR$ & $\SN$ & $\CR$ & $\SN$ \\
+        $\CR$ & $\CR$ & CE-\ref{CE:8} & $\CR$ & CE-\ref{CE:6} & $\CR$ & CE-\ref{CE:8} & $\CR$ & $\SN$ & $\CR$ & $\SN$ \\
         \hline
@@
         \Xhline{1.5pt}
-        $\gUNto$ & CE-\ref{CE:2} & CE-\ref{CE:9} & $\gCR$ & CE-\ref{CE:7} & $\gCR$\footnotemark[1] & CE-\ref{CE:9} & $\gCR$ & $\gSN$ & $\gCR$\footnotemark[2] & $\gSN$ \\
+        $\gUNto$ & CE-\ref{CE:2} & CE-\ref{CE:8} & $\gCR$ & CE-\ref{CE:6} & $\gCR$\footnotemark[1] & CE-\ref{CE:8} & $\gCR$ & $\gSN$ & $\gCR$\footnotemark[2] & $\gSN$ \\
         \hline
-        $\gNP$ & CE-\ref{CE:3} & CE-\ref{CE:9} & $\gCR$ & CE-\ref{CE:7} & $\gCR$\footnotemark[1] & CE-\ref{CE:9} & $\gCR$ & $\gSN$ & $\gCR$\footnotemark[2] & $\gSN$ \\
+        $\gNP$ & CE-\ref{CE:3} & CE-\ref{CE:8} & $\gCR$ & CE-\ref{CE:6} & $\gCR$\footnotemark[1] & CE-\ref{CE:8} & $\gCR$ & $\gSN$ & $\gCR$\footnotemark[2] & $\gSN$ \\
         \hline
-        $\gMP$ & $\gCR$ & CE-\ref{CE:9} & $\gCR$ & CE-\ref{CE:7} & $\gCR$\footnotemark[2] & CE-\ref{CE:9} & $\gCR$ & $\gSN$ & $\gCR$\footnotemark[2] & $\gSN$ \\
+        $\gMP$ & $\gCR$ & CE-\ref{CE:8} & $\gCR$ & CE-\ref{CE:6} & $\gCR$\footnotemark[2] & CE-\ref{CE:8} & $\gCR$ & $\gSN$ & $\gCR$\footnotemark[2] & $\gSN$ \\
         \hline
-        $\gCR$ & $\gCR$ & CE-\ref{CE:9} & $\gCR$ & CE-\ref{CE:7} & $\gCR$ & CE-\ref{CE:9} & $\gCR$ & $\gSN$ & $\gCR$ & $\gSN$ \\
+        $\gCR$ & $\gCR$ & CE-\ref{CE:8} & $\gCR$ & CE-\ref{CE:7} & $\gCR$ & CE-\ref{CE:8} & $\gCR$ & $\gSN$ & $\gCR$ & $\gSN$ \\
         \Xhline{1.5pt}
@@
                 \centering
-                \begin{counterexample}\label{CE:un}
+                \begin{counterexample}\label{CE:5}
                     \begin{tikzcd}[row sep=small, column sep=small]
@@
             \centering
-            \begin{counterexample}\label{CE:7}
+            \begin{counterexample}\label{CE:6}
             \begin{tikzcd}[row sep=small, column sep=small]
@@
             \centering
-            \begin{counterexample}\label{CE:8}
+            \begin{counterexample}\label{CE:7}
             \begin{tikzcd}[row sep=small, column sep=small]
@@
             \centering
-            \begin{counterexample}\label{CE:9}
+            \begin{counterexample}\label{CE:8}
             \begin{tikzcd}[row sep=small, column sep=small]
@@
         \centering
-        \begin{counterexample}\label{CE:10}
+        \begin{counterexample}\label{CE:9}
             \begin{tikzcd}[row sep=small, column sep=small]
@@
         \centering
-        \begin{counterexample}\label{CE:11}
+        \begin{counterexample}\label{CE:10}
             \begin{tikzcd}[row sep=small, column sep=small]
@@
         \centering
-        \begin{counterexample}\label{CE:12}
+        \begin{counterexample}\label{CE:11}
             \begin{tikzcd}[row sep=small, column sep=small]

### 2025-05-30 Relations/Paper/Formalization.tex
Formatting updates throughout. Updated references to agda code.

@@
 \label{sec:Formalization}
-This sections is a guide to our formalization of \terese and explains the deviations we take from the text.
+This sections is a guide to our formalization of \terese $\,$ and explains the deviations we take from the text.
 
 \subsection{Formalization of Definitions}\label{subsec:def}
-The closure operators are formalized in \texttt{ARS-Closure.agda}. 
-The definitions grouped as confluent in \terese are formalized in \texttt{ARS-Base.agda}. 
-The definitions grouped as normalizing in \terese are formalized in \texttt{ARS-Properties.agda}.
+The closure operators are formalized in \texttt{Closure.agda}. 
+The definitions grouped as confluent in \terese $\,$ are formalized in \texttt{Base.agda}. 
+The definitions grouped as normalizing in \terese $\,$ are formalized in \texttt{Properties.agda}.
 
@@
 There are three sets of propositions given in \terese: \texttt{1.1.9}, \texttt{1.1.10}, \texttt{1.1.11}. 
-The formalization of the proofs are in \texttt{ARS-Propositions.agda}. These formalizations are straightforward 
+The formalization of the proofs are in \texttt{Propositions.agda}. These formalizations are straightforward 
 and as such are not the focus of this paper.
@@
 
-($i$) is formalized in:
-\begin{itemize}
-    \item \verb|CR→NP : R isCR → R isNP₌|
-    \item \verb|NP→UN : R isNP₌ → R isUN|
-\end{itemize}
-
-($ii$) is formalized also from the weaker hypothesis of $\gUNto$:
-\begin{itemize}
-    \item \verb|ii : R isWN × R isUN → R isCR|
-    \item \verb|UN→∧WN→CR : R isUN→ → R isWN → R isCR|
-\end{itemize}
-
-($iii$) is formalized in:
-\begin{itemize}
-    \item \verb|iii : subcommutative R → R isCR|
-\end{itemize}
+\begin{proof}
+    See, \\
+    \verb|CR→NP : R isCR → R isNP₌|\\
+    \verb|NP→UN : R isNP₌ → R isUN|\\
+    \verb|ii : R isWN × R isUN → R isCR|\\
+    \verb|UN→∧WN→CR : R isUN→ → R isWN → R isCR|\\
+    \verb|iii : subcommutative R → R isCR|\\
+    in \texttt{Theorems.agda}.
+\end{proof}
+\begin{remark}
+    In $\mathtt{UN→∧WN→CR}$ a more general proof of ($ii$) is given using $\UNto$.
+\end{remark}
 
@@
     \begin{description}
-        \item[\ule{$a \in CP_R$}] \emph{$a$ has the cofinality property} if there exists a 
+        \item[\ule{$a \in CP_R$}] $a$ has the \emph{cofinality property} if there exists an 
         (not necessarily strictly) increasing sequence starting from $a$ such that every
@@
 \end{description}
+\begin{proof}
+    See, \\
+    \verb|i : R isWN → R isUN → R isBP|\\
+    \verb|i→ : R isWN → R isUN→ → R isBP|\\
+    \verb|iiSeq : R isWN → R isUN → R isRP → isWFseq- (~R R)|\\
+    \verb|iii : R isWN → R isWCR → R isRP- → dec (SN) → R isSN|\\
+    \verb|iv : R isCP → R isCR| \\
+    in \texttt{Theroems.agda}.
+\end{proof}
 
-($i$) is formalized in: 
+\begin{remark} \hfill
     \begin{itemize}        
-    \item \verb|i : R isWN → R isUN → R isBP|
-    \item \verb|i→ : R isWN → R isUN→ → R isBP|
+        \item In $\mathtt{i\to}$ we again provide a slight improvement by using $\gUNto$ rather than $\gUN$.
+        \item ($ii$) is inherently classical.
+In $\mathtt{iiSeq}$, we show that these properties imply $\isWFseqm$; establishing the implication to $\gSN$ would require additional classical assumptions.
+The definition and further discussion of $\isWFseqm$ are provided in Section~\ref{sec:Well-foundedness}.
+        \item In $\mathtt{iii}$, we replace $\gInc$ with the more general property $\gRPm$.
+We also assume that $\gSN$ is decidable, as this allows the construction of a witness for whether an element possesses the property $\SN$, which is essential for our proof.
+        \item We did not formalize $\gCR \to \gCP$ as it requires cardinality assumptions.
     \end{itemize}
-
-In $\mathtt{i\to}$ we again provide a slight improvement by using $\gUNto$ rather than $\gUN$.
-
-A formalization of ($ii$) is provided in: 
-\begin{itemize}
-    \item \verb|iiSeq : R isWN → R isUN → R isRP → isWFseq- (~R R)|
-\end{itemize}
-This is an inherently classical result, and so the result is only classically equivalent to $\gSN$.
-
-($iii$) is formalized in: 
-\begin{itemize}
-    \item \verb|iii : R isWN → R isWCR → R isRP- → dec (SN) → R isSN|
-\end{itemize}
-As can be seen we have substituted $\gInc$ with $\gRPm$ which generalizes this theorem. We have also included the assumption that $\gSN$ 
-is decidable as this property enables us 
-to construct a witness for an element that either does or does not have the property $\SN$. Such a witness was necessary for our proof. 
-% \sacomment{Link to decidable in later section?}
-
-The reverse implication of ($iv$) is formalized in: 
-\begin{itemize}
-    \item \verb|iv : R isCP → R isCR|
-\end{itemize}
-We did not formalize $\gCR \to \gCP$ as it requires cardinality assumptions.
-
-% the ARS to be countable.
+\end{remark}

### 2025-05-30 Relations/Paper/Implications.tex
Formatting updates throughout. Updated references to agda code.

@@
 As discussed in Subsection \ref{subsec:def} we put forward $\RP$ as an alternative for $\Inc$. It is through examining $\RP$ that 
-we came to the 'minimal` family of properties below. These properties help to augment our ARS hierarchy.
+we came to the `minimal' family of properties below. These properties help to augment our ARS hierarchy.
 
@@
 \begin{proof}
-    See, \verb|NF ⊆ MF : ∀x → NFx → MFx| in \texttt{ARS-Implications.agda}.
+    See, \verb|NF ⊆ MF : ∀x → NFx → MFx| in \texttt{Implications.agda}.
 \end{proof}
@@
 \begin{proof}
-    See,\\ \verb|RP∧BP→SMseq : R isRP → R isBP → ∀ {x : A} → SMseq R x| \\ \verb|RisSMseq→RisRP : (∀ {x : A} → SMseq R x) → R isRP|
-    \\ \verb|RisSMseq→RisBP : (∀ {x : A} → SMseq R x) → R isBP| in \texttt{ARS-Implications.agda}.
+    See,\\ 
+    \verb|RP∧BP→SMseq : R isRP → R isBP → ∀ {x : A} → SMseq R x| \\ 
+    \verb|RisSMseq→RisRP : (∀ {x : A} → SMseq R x) → R isRP|\\ 
+    \verb|RisSMseq→RisBP : (∀ {x : A} → SMseq R x) → R isBP| \\
+    in \texttt{Implications.agda}.
 \end{proof}
@@
 
-The implications in this diagram are formalized in \texttt{ARS-Implications.agda}. 
-The hierarchy for confluencce requires no classical assumptions, however this is not the case for the hierarchy of terminating properties.
+The implications in this diagram are formalized in \texttt{Implications.agda}. 
+The confluence hierarchy requires no classical assumptions, however this is not the case for the hierarchy of terminating properties.
 The implication from $\SN$ to $\WN$ relies on the classical decidability of the property 

### 2025-05-30 Relations/Paper/Summer_2025_TODO.tex
Updated the todos
Formatting updates throughout. Updated references to agda code.

@@
     \item (Review 1) Improve fonts for constant and text (refering to a definition on line 258). General formatting imrpovement for how we set out defns.
-    \item (Review 1) Improve the layout on line 270 where we set out iiSeq.
+    \item [\done] (Review 1) Improve the layout on line 270 where we set out iiSeq.
 This should get fixed with an overall improvement in how we set out definitions.
@@
     \item (Our notes) Improve proposition 11 on line 194, we want to make the clame that RP- $\to$ RP, and either have a one line proof or refer to the proof in Agda. 
-    \item (Review 2) Section 3 is "full of repeitions and paraphrases between the statements in natural language and corresponding formalization".
-We can try and think of a way to get it to flow bettwe, we do want to provide natural language summaries of what is in the code!
-    \item (Review 2) Struggled to understand the implications tables.
+    \item (Review 2) Section 3 is "full of repetitions and paraphrases between the statements in natural language and corresponding formalization".
+We can try and think of a way to get it to flow better, we do want to provide natural language summaries of what is in the code!
+    \item [\done] (Review 2) Struggled to understand the implications tables.
 We should add a reminder that bold font is global.
@@
   \end{todolist}
+
 \end{itemize}
+\section*{Week starting 26th May}
+\begin{todolist}
+  \item Double check the counterexamples match in the table to the diagrams.
+\end{todolist}
 \end{document}

### 2025-06-01 QADT/notes.tex
maintenance commit

--- 2024-12-16 QADT/notes.tex
@@
 \end{itemize}
+
+\section{2025.03.13}
+
+In many cases, some $\mu$ datatype, $\mu F$ being a fixed point of a functor $G$ will not result in a fold isomorphism. \\ 
+\textbf{Conjecture: } For all of these situations resulting from a rig isomorphism, all elements of $\mu F$ not in the range of the fold will have an image in the final coalgebra of $G$ which is rational.
+
+We want to try to prove surjectivity of the fold by proving that all preimages of elements of $\mu F$ are well-founded.
+
 \end{document}

### 2025-06-01 QADT/iso_research_more_general.py

@@ -1,7 +1,7 @@
 import re
 def main():
-    diff = [1, 0, 0, 0, 0, 0, 1]
-    poly = [1, 0, 0, 0, 1, 0, 0]
+    diff = [1, -1, 1]
+    poly = [0, 1]
     # diff = [1, 0, 0, 0, 0, 1]
     # poly = [1, 1, 0, 0, 0, 1]
     # poly = [0, 0, 1, 1, 0, 0, 0, 1]

### 2025-06-01 Relations/Paper/Definitions.tex
Counterexamples badly numbered. Only halfway fixed!

@@
 
-\subsection{Closure operators (\texttt{ClosureOperators.agda})}
+\subsection{Closure operators (\texttt{Closure.agda})}
 
@@
 We next define rewriting-theoretic concepts like confluence and normalization relative to a fixed element of $A$; global versions of these properties are obtained by universal quantification.
-\subsection{Normalization (\texttt{ARS-Properties.agda})}
+\subsection{Normalization (\texttt{Properties.agda})}
 \begin{definition} The following definitions relate to normalization. 
   \begin{description}
-    \item[\ule{$\mathbf{a \in \NF_R}$}] \emph{$a$ is a normal form} if $(a,b) \notin R$ for any $b \in A$.
+    \item[\ule{${a \in \NF_R}$}] \emph{$a$ is a normal form} if $(a,b) \notin R$ for any $b \in A$.
     \item[\ule{$a \in \WN_R$}] \emph{$a$ is weakly normalizing} if $a \mstep b$ for some $b \in \NF_R$.
@@
 
-\subsection{Confluence (\texttt{ARS-Properties.agda})}
+\subsection{Confluence (\texttt{Properties.agda})}
 \begin{definition} The following definitions relate to confluence.
@@
 
-In \terese $\NF$ is used to denote $\NPe$, whereas we have chosen to use $\NF$ to denote the set of normal forms.
+In \terese $\,\NF$ is used to denote $\NPe$, whereas we have chosen to use $\NF$ to denote the set of normal forms.
 
@@
     \begin{enumerate}
-        \item \verb|NP₌↔NP : R isNP₌ ↔ R isNP| in \texttt{ARS-Implications.agda}.
-        \item \verb|UN→UN→ : R isUN → R isUN→| in \texttt{ARS-Implications.agda}.
+        \item \verb|NP₌↔NP : R isNP₌ ↔ R isNP| in \texttt{Implications.agda}.
+        \item \verb|UN→UN→ : R isUN → R isUN→| in \texttt{Implications.agda}.
     \end{enumerate}
@@
 
-\subsection{Sequences and Recurrence (\texttt{ARS-Properties.agda}, \texttt{Seq.agda})}
+\subsection{Sequences and Recurrence (\texttt{Properties.agda}, \texttt{Seq.agda})}
 The following definitions are key to formalizing Theorem 1.2.3 in \terese.
@@
 
-In \terese $\mathrm{Ind}$ is used to denote $\BP$.
+In \terese $\mathrm{\,Ind}$ is used to denote $\BP$.
 
@@
  We show that this weaker definition is
-in fact equivalent in the following proof in \texttt{ARS-Implications.agda}:
+in fact equivalent in the following proof in \texttt{Implications.agda}:
 

### 2025-06-02 Relations/Paper/Summer_2025_TODO.tex
Minor code update to reflect changes to wf.

@@
   \item Double check the counterexamples match in the table to the diagrams.
+  \item Make clear in proof references to agda code how it should be read (especially the first one). Make clear the module as well. After doing once, the others don't need to be as explicit. 
+  \item find a seperate symbol for -> in the code sections in the paper for UN$\to$. Superscipt would be perfect. 
+  \item Mention theorem 123 ii and iii are inherently classical. For iii we require strong decidability. 
+  \item Working on CR $\to$ CP. Low priority.  
 \end{todolist}

### 2025-06-02 QADT/OpenProblems.tex

@@
 \documentclass{scrartcl}
+
+\usepackage{amsmath}
+\usepackage{amssymb}
+
+\newcommand{\cat}{\mathbb{C}}
+\newcommand{\op}{{op}}
+
+\newcommand{\bone}{\boldsymbol{1}}
+\newcommand{\then}{\quad\mathrel{\Longrightarrow}\quad}
+
+\newcommand{\ints}{\mathbb{Z}}
+\newcommand{\nat}{\mathbb{N}}
+
 \begin{document}
 
+\section{Open Questions}
 \begin{enumerate}
@@
   \end{itemize}
+  \item{A self-consistent type system with types of equalities}
+  \item{Sufficient conditions to generate an induced isomorphism from a rig isomorphism}
+  \begin{itemize}
+  	\item{When does there exist a rig isomorphism that generates an induced isomorphism?}
+	\item{Why do some rig isomorphisms generate an induced isomorphism and some do not?}
+  \end{itemize}
   \item{}
@@
 
+\section{Closed Questions}
+
+\begin{enumerate}
+  \item What is a strong isomorphism between ADTs?
+
+  A strong isomorphism, or rig isomorphism, is an isomorphism between two functors acting on an ADT that is a fixpoint of a polynomial functor.
+If we say $\mu F$ is the min fixpoint of a polynomial functor $F$, and $G$ and $H$ are polynomial functors, then the isomorphism $G(\mu F) \simeq H(\mu F)$ can be generated for free when:
+  \begin{itemize}
+  \item The roots of $F(X) - X = 0$ are a sub-multiset of the roots of $G(X) - H(X) = 0$.
+  \item $F(X)$ is a second degree or higher polynomial.
+  \item The content of $F(X)$ divides the content of $G(X) - H(X)$
+  \end{itemize}
+
+  \item What does it mean for a functor to be a factor of another functor?
+
+  A fixed point of the smaller degree functor is a fixed point of the larger degree functor.
+
+  \item A conception of a negative set in these terms.
+  \begin{itemize}
+    \item Universal $U$, and an ``integer set'' is a function from $U$ to $\mathbb{Z}$.
+    \item A contravariant functor $- : \cat \to \cat^\op$ that splits the identity
+    ($- \circ -^\op = id$)
+    \item A solution to $E(X)=X$, obtained by taking $X = Y + 1$ for some type $Y$.
+  \end{itemize}
+  \item All polynomials functors with degree at least two will have linear factors.
+  Can it solve arbitrary linear equation?
+  Are all linear datatypes isomorphic to each other?  Are they generated by $S = -1$?
+  \item Retractions between datatypes!
+  \item Isomorphisms induced by initial algebra maps.
+  \item Let $H(X) = 1 + X + X^3$, then $X$ contains sixth roots of unity as well as
+  a square root of unity.  $M(X) = 1 + X + X^2$ contains fourth roots of unity;
+  does this explain why we can ``divide $H(X)$ by $M(X)$''?
+
+  Is this the reason why a solution to $M(X)=X$, when squared, yields a solution to $H(X)$?
+  Why does this happen more generally?
+
+  A solution to $M$, when squared, yields a solution to $H$ because the roots of $M(X) - X = 0$ are a sub-multiset of the roots of $X^2 = H(X^2)$.
+
+  \item Can any equation $X=P(X)$, with $P(X)$ be an \emph{arbitrary}
+  polynomial --- containing both positive and negative coefficients ---
+  be solved by substitution $X = (Y+k)$, for some $k \ge 0$.
+
+  Can various solutions be compared?
+
+  We can obtain \textit{a} fixpoint of a Functor by making this substitution but not the least fixed point.
+
+  \item Generalize all of the above to \emph{systems of equations} of the form
+  \begin{align*}
+    P_1(X_1,\dots,X_k) &= Q_1(X_1,\dots,X_k)\\
+    P_2(X_1,\dots,X_k) &= Q_2(X_1,\dots,X_k)\\
+     &\quad \vdots \\
+    P_k(X_1,\dots,X_k) &= Q_k(X_1,\dots,X_k)
+  \end{align*}
+\end{enumerate}
+
 \end{document}

### 2025-06-02 Relations/Paper/Definitions.tex
More consistent proof environemnt. Update to UN->

@@
 \end{proposition}
-\begin{proof} \hfill
+\begin{proof} See\footnote{All proofs are formalized in the accompanying Agda code.
+References within the paper indicate the corresponding function names and their types to facilitate locating the relevant formalizations.} \hfill
     \begin{enumerate}
-        \item \verb|NP₌↔NP : R isNP₌ ↔ R isNP| in \texttt{Implications.agda}.
-        \item \verb|UN→UN→ : R isUN → R isUN→| in \texttt{Implications.agda}.
+        \item \verb|NP₌↔NP : R isNP₌ ↔ R isNP| 
+        \item \verb|UN→|\texttt{UN}$^{\to}$\verb|: R isUN → R is|\texttt{UN}$^{\to}$ \\ in \texttt{Implications.agda}.
     \end{enumerate}
@@
 
-The implication $\UNto \implies \UN$ does not hold, as can be seen in Example \ref{CE:un} in Subsection \ref{subsec:counterexamples}.
+\begin{remark}
+    The implication $\UNto \implies \UN$ does not hold, as can be seen in Counterexample~\ref{CE:5} in Subsection~\ref{subsec:counterexamples}.
+\end{remark}
 
@@
 
-The following is immediate.
 \begin{proposition}\hfill
@@
         \item $\gInc \implies \gRP$
-        \item $\gRP \implies \gRPm$
+        \item $\gRP \iff \gRPm$
     \end{enumerate}
@@
 
-It follows that every relation that is increasing in the sense of \terese
-vacuously satisfies the RP condition.
+\begin{proof}
+    See, \hfill
+    \begin{enumerate}
+        \item This is immediate.
+        \item \verb|RP-↔RP : R isRP- ↔ (R isRP)|
+    \end{enumerate}
+    in \texttt{Implications.agda}
+\end{proof}
 
-We wanted to generalize $\RP$ and thought that with $\RPm$ we had a good candidate.
- We show that this weaker definition is
-in fact equivalent in the following proof in \texttt{Implications.agda}:
-
-\verb|RP-↔RP : R is RP- ↔ R is RP|.
+%TODO: Update below to reflect new convenion for proofs and code.
+\begin{remark}
+    It follows that every relation that is increasing in the sense of \terese $\,$ vacuously satisfies the RP condition.
+\end{remark}
 

### 2025-06-02 Relations/Paper/Formalization.tex
Minor code update to reflect changes to wf.
More consistent proof environemnt. Update to UN->

@@
     \verb|ii : R isWN × R isUN → R isCR|\\
-    \verb|UN→∧WN→CR : R isUN→ → R isWN → R isCR|\\
+    \verb||\texttt{UN}$^{\to}$ \verb|∧WN→CR : R |\texttt{isUN}$^{\to}$ \verb| → R isWN → R isCR|\\
     \verb|iii : subcommutative R → R isCR|\\
@@
 \begin{remark}
-    In $\mathtt{UN→∧WN→CR}$ a more general proof of ($ii$) is given using $\UNto$.
+    In $\mathtt{UN^{→}∧WN→CR}$ a more general proof of ($ii$) is given using $\UNto$.
 \end{remark}
@@
     \verb|i : R isWN → R isUN → R isBP|\\
-    \verb|i→ : R isWN → R isUN→ → R isBP|\\
+    \verb|i→ : R isWN → R |\texttt{isUN}$^{\to}$ \verb|→ R isBP|\\
     \verb|iiSeq : R isWN → R isUN → R isRP → isWFseq- (~R R)|\\
@@
     \verb|iv : R isCP → R isCR| \\
-    in \texttt{Theroems.agda}.
+    in \texttt{Theorems.agda}.
 \end{proof}

### 2025-06-02 Relations/Paper/Summer_2025_TODO.tex
More consistent proof environemnt. Update to UN->

@@
 \documentclass{article}
+\input{macros}
 \usepackage{enumitem,amssymb}
@@
     \item (Review 2) Clarify Notation 7 on line 159: "Choose a uniform notation, X or NP, but not both".
-    \item (Review 2) "l 169: An annoying notational collision between the two arrows -> at different heights."I'm not too sure what they're referring to, though there could be some ambiguity with the arrows here, especially with use of $UN\to$.
+    \item [\done] (we think) (Review 2) "l 169: An annoying notational collision between the two arrows -> at different heights."I'm not too sure what they're referring to, though there could be some ambiguity with the arrows here, especially with use of $UN\to$.
     \item (Review 2) "l 361: Swap s(k+1) and s(k) " We should clarify the definition here otherwise people (evidently) get confused. 
@@
   \item Make clear in proof references to agda code how it should be read (especially the first one). Make clear the module as well. After doing once, the others don't need to be as explicit. 
-  \item find a seperate symbol for -> in the code sections in the paper for UN$\to$. Superscipt would be perfect. 
+  \item [\done] find a seperate symbol for -> in the code sections in the paper for UN$\to$. Superscipt would be perfect. $UN^{\rightarrow}$
   \item Mention theorem 123 ii and iii are inherently classical. For iii we require strong decidability. 
@@
 \end{todolist}
+
+\section*{Week starting 2nd June}
+\begin{todolist}
+  \item Should we add quantification to each definition(I think quantification for $a$ is already implied)? E.g.\\ 
+  \item [\ule{$a \in \WCR_R$}] \emph{$a$ is weakly Church-Rosser (or weakly confluent)} if $c \bstep a \rstep b \implies c \mstep d \bmstep b$.\\
+   Transforms to 
+  \item[\ule{$a \in \WCR_R$}] \emph{$a$ is weakly Church-Rosser (or weakly confluent)} if $c \bstep a \rstep b \implies c \mstep d \bmstep b$ for all $b, c, d \in A$. 
+  \item For showing inc -> RP we're currently just saying "This is immediate". Is this sufficient? We did have a proof previously but I think we removed it for space reasons. 
+\end{todolist}
 \end{document}

### 2025-06-03 Relations/Paper/Definitions.tex
section 2

@@
 
-For the rest of this paper, let $A$ be a fixed set, $R$ be a relation on $A$, and $a \in A$.
+For the rest of this paper, let $A$ be a fixed set, $R$ be a relation on $A$.
 
@@
 In the context of abstract rewriting, we will often write $a \rstep b$
-in place of $(a,b) \in R$.  Similarly, we will write $a \mstep b$ for $(a,b) \in R^*$,
+in place of $(a,b) \in R$.  We will also write $a \mstep b$ for $(a,b) \in R^*$, and
 $a \bstep b$ for $(b,a) \in R$.  When the relation $R$ is clear from the context,
@@
 
-We next define rewriting-theoretic concepts like confluence and normalization relative to a fixed element of $A$; global versions of these properties are obtained by universal quantification.
-\subsection{Normalization (\texttt{Properties.agda})}
-\begin{definition} The following definitions relate to normalization. 
+\subsection{Normalization and Confluence (\texttt{Properties.agda})}
+
+We define rewriting-theoretic concepts such as confluence and normalization as predicates on $A$, specifying when a given element $a \in A$ satisfies a property locally.
+Universal quantification over $a$ then yields the corresponding global property of the relation $R$
+
+% \subsection{Normalization (\texttt{Properties.agda})}
+\begin{definition} Let $a \in A$.
   \begin{description}
@@
     \item[\ule{$a \in \WN_R$}] \emph{$a$ is weakly normalizing} if $a \mstep b$ for some $b \in \NF_R$.
-    \item[\ule{$a \in \SN_R$}] \emph{$a$ is strongly normalizing} if $a$ is accessible with respect to the converse relation $\bar{R} = \setof{(y,x) | (x,y) \in R}$ 
-    (see Section \ref{sec:Well-foundedness} for the notion of accessibility).
+    \item[\ule{$a \in \SN_R$}] \emph{$a$ is strongly normalizing} if $a$ is accessible with respect to the converse relation $\bar{R} = \setof{(y,x) | (x,y) \in R}$.
+    See Section \ref{sec:Well-foundedness} for the notion of accessibility.
   \end{description}
@@
 
-\subsection{Confluence (\texttt{Properties.agda})}
-\begin{definition} The following definitions relate to confluence.
+% \subsection{Confluence (\texttt{Properties.agda})}
+\begin{definition} Let $a \in A$.
     \begin{description}
-        \item[\ule{$a \in \WCR_R$}] \emph{$a$ is weakly Church-Rosser (or weakly confluent)} if $c \bstep a \rstep b \implies c \mstep d \bmstep b$.
-        \item[\ule{$a \in \CR_R$}] \emph{$a$ is Church-Rosser (or confluent)} if $c \bmstep a \mstep b \implies c \mstep d \bmstep b$.
-        \item[\ule{$a \in \CRs_R$}] \emph{$a$ is subcommutative} if $c \bmstep a \mstep b \implies c \rrstep d \brstep b$.
-        \item[\ule{$a \in \NPe_R$}] \emph{$a$ has the conversion normal form property} if $a \estep b \implies a\mstep b$ for any $b \in \NF$.
-        \item[\ule{$a \in \NP_R$}] \emph{$a$ has the normal form property} if $c \bmstep a \mstep b \implies c \mstep b$ for any $b \in \NF$.
-        \item[\ule{$a \in \UN_R$}] \emph{$a$ has the unique normal form property} if $a \estep b \implies a \equiv b$  for any $a, b \in \NF$.
-        \item[\ule{$a \in \UNto_R$}] \emph{$a$ has the unique normal form property with respect to reduction} if $c \bmstep a \mstep b  \implies b \equiv c$  for any $b, c \in \NF$.
+        \item[\ule{$a \in \WCR_R$}] \emph{$a$ is weakly Church-Rosser} (or \emph{weakly confluent}) if for all $b,c \in A$, \[c \bstep a \rstep b \implies \exists d. c \mstep d \bmstep b\]
+        \item[\ule{$a \in \CR_R$}] \emph{$a$ is Church-Rosser} (or \emph{confluent}) if for all $b,c \in A$, \[c \bmstep a \mstep b \implies \exists d. c \mstep d \bmstep b\]
+        \item[\ule{$a \in \CRs_R$}] \emph{$a$ is subcommutative} if for all $b, c \in A$,
+        \[c \bmstep a \mstep b \implies c \rrstep d \brstep b\]
+        \item[\ule{$a \in \NPe_R$}] \emph{$a$ has the conversion normal form property} if for all $b \in \NF_R$, \[ a \estep b \implies a\mstep b\]
+        \item[\ule{$a \in \NP_R$}] \emph{$a$ has the normal form property} if for all $b \in \NF_R$,
+        \[c \bmstep a \mstep b \implies c \mstep b\]
+        \item[\ule{$a \in \UN_R$}] \emph{$a$ has the unique normal form property} if for all $a, b \in \NF_R$, \[a \estep b \implies a \equiv b\]
+        \item[\ule{$a \in \UNto_R$}] \emph{$a$ has the unique normal form property with respect to reduction} if for all $b, c \in \NF_R$,
+        \[c \bmstep a \mstep b  \implies b \equiv c\]
     \end{description}
 \end{definition}
+% \begin{definition} Let $a \in A$.
+%     \begin{description}
+%         \item[\ule{$a \in \WCR_R$}] \emph{$a$ is weakly Church-Rosser (or weakly confluent)} if $c \bstep a \rstep b \implies c \mstep d \bmstep b$.
+%         \item[\ule{$a \in \CR_R$}] \emph{$a$ is Church-Rosser (or confluent)} if $c \bmstep a \mstep b \implies c \mstep d \bmstep b$.
+%         \item[\ule{$a \in \CRs_R$}] \emph{$a$ is subcommutative} if $c \bmstep a \mstep b \implies c \rrstep d \brstep b$.
+%         \item[\ule{$a \in \NPe_R$}] \emph{$a$ has the conversion normal form property} if $a \estep b \implies a\mstep b$ for any $b \in \NF$.
+%         \item[\ule{$a \in \NP_R$}] \emph{$a$ has the normal form property} if $c \bmstep a \mstep b \implies c \mstep b$ for any $b \in \NF$.
+%         \item[\ule{$a \in \UN_R$}] \emph{$a$ has the unique normal form property} if $a \estep b \implies a \equiv b$  for any $a, b \in \NF$.
+%         \item[\ule{$a \in \UNto_R$}] \emph{$a$ has the unique normal form property with respect to reduction} if $c \bmstep a \mstep b  \implies b \equiv c$  for any $b, c \in \NF$.
+%     \end{description}
+% \end{definition}
 
 \begin{notation}
-    For each of the subsets $\mathrm{X}$ defined above we write 
-    $R \models \mathbf{X}$ if $\forall a.\; a \in \mathrm{X}_R$. When $R$ is clear from the context, we will write $\gNP$ for $R \models \gNP$, etc.
-    That is, for $\mathrm{X} \in \{\WCR , \CR , \NP , \UN, \dots \}$ we write $\mathbf{X}$ for the statement that $x \in \mathrm{X}_R$ for all $x \in A$.
+    For each of the predicates $\mathrm{X_R}$ defined above we write
+    $\mathbf{X}(R)$ if $\forall a.\; a \in \mathrm{X}_R$. When $R$ is clear from the context, we will write $\gNP$ for $\gNP(R)$, etc.
+
+    That is, for $\mathrm{X} \in \{\WCR , \CR , \NP , \UN, \dots \}$, $\mathbf{X}$ denotes the statement $\forall a. a \in \mathrm{X}_R$.
 \end{notation}
 
-In \terese $\,\NF$ is used to denote $\NPe$, whereas we have chosen to use $\NF$ to denote the set of normal forms.
+In \terese $\,\NF$ is used to denote the normal form property $\NPe$, whereas we have chosen to use $\NF$ to denote the set of normal forms.
 
@@
 \end{proposition}
-\begin{proof} See\footnote{All proofs are formalized in the accompanying Agda code.
-References within the paper indicate the corresponding function names and their types to facilitate locating the relevant formalizations.} \hfill
+\begin{proof} The majority of proofs in this work have been fully formalized in Agda and require no further elaboration.
+Throughout the paper, we refer to the relevant locations in the code base by giving the name of the Agda file, along with the names and types of the functions corresponding to each claim.
+
+  The following claims are formalized in \texttt{Implications.agda}.
     \begin{enumerate}
         \item \verb|NP₌↔NP : R isNP₌ ↔ R isNP|
-        \item \verb|UN→|\texttt{UN}$^{\to}$\verb|: R isUN → R is|\texttt{UN}$^{\to}$ \\ in \texttt{Implications.agda}.
+        \item \verb|UN→|\texttt{UN}$^{\to}$\verb|: R isUN → R is|\texttt{UN}$^{\to}$
     \end{enumerate}
@@
     The implication $\UNto \implies \UN$ does not hold, as can be seen in Counterexample~\ref{CE:5} in Subsection~\ref{subsec:counterexamples}.
+    \apcomment{Provide a ref to a figure, eventually.}
 \end{remark}
@@
 \subsection{Sequences and Recurrence (\texttt{Properties.agda}, \texttt{Seq.agda})}
-The following definitions are key to formalizing Theorem 1.2.3 in \terese.
+% The following definitions are key to formalizing Theorem 1.2.3 in \terese.
+The definitions in this subsections are key to formalizing Theorem 1.2.3 in \terese.
 
@@
     \begin{description}
-        \item[\ule{$R \models \gInc$}] \emph{$R$ is increasing} if there exists a ``size function'' $|{-}| : A \to \nat$ satisfying, for all $a, b \in A$,
+        \item[$\gInc(R)$] \emph{$R$ is increasing} if there exists a ``size function'' $|{-}| : A \to \nat$ satisfying, for all $a, b \in A$,
         $(a \rstep b) \implies |a| < |b|$
@@
 
-Having a size function that maps to the natural numbers can be computationally taxing to satisfy.
-Further, it takes us outside of purely relational theory. The following definitions are for properties which allow us to forgo $\gInc$, for further discussion see Subsection \ref{subsec:def}.
-\begin{definition} \label{def:rp} \hfill
+Having a size function that maps all of $A$ to the natural numbers can be computationally taxing to satisfy.
+Furthermore, it takes us outside of a purely relational theory. The following properties will allow us to substitute $\gInc$ with weaker hypotheses in all the relevant places.
+(For further discussion, see Subsection \ref{subsec:def}.)
+
+\begin{definition} \label{def:seq} \hfill
+  \begin{itemize}
+    \item A \emph{sequence} is a function $s$ from the natural numbers to $A$.
+    \item A sequence $s : \nat \to A$ is \emph{$R$-decreasing} if every element of the sequence is $R$-related to its preceding term.
+    \item A sequence $s : \nat \to A$ is \emph{$R$-increasing} if every element of the sequence is $R$-related to its succeeding term.
+  \end{itemize}
+\end{definition}
+
+\begin{definition} \label{def:rp} Let $a \in A$ and $s : \nat \to A$.
     \begin{description}
-        \item[\ule{$s : \nat \to A$}] \emph{A sequence $s \in A$} is a function from the natural numbers to $A$.
-        \item[\ule{$s$ is $R$-increasing}] \emph{A sequence $s \in A$ is $R$-increasing} if every term is $R$-related to its preceding term.
+        % \item[\ule{$s : \nat \to A$}] \emph{A sequence $s \in A$} is a function from the natural numbers to $A$.
+        % \item[\ule{$s$ is $R$-increasing}] \emph{A sequence $s \in A$ is $R$-increasing} if every term is $R$-related to its preceding term.
         \item[\ule{$a$ is an $s$-bound}] if $s (i) \mstep a$ for all $i \in \nat$.
         \item[\ule{$a \in \BP_R$}] \emph{$a$ has the bound property} if for each $R$-increasing sequence $s$ with $s (0) = a$ there exists an $s$-bound.
-        \item[\ule{$R \models \gRP$}] \emph{$R$ has the recurrence property} if for every bounded, increasing sequence $s$ with an $s$-bound, there exists an $i \in \nat$ such that
+        \item[\ule{$\gRP(R)$}] \emph{$R$ has the recurrence property} if for every bounded, increasing sequence $s$ with an $s$-bound, there exists an $i \in \nat$ such that
         $s (i) \mstep x \implies x \mstep s (i)$ for all $x\in A$.
-        \item[\ule{$R \models \gRPm$}] \emph{$R$ has the weak recurrence property} if for every increasing sequence $s$ with bound $b$ there exists an $i \in \nat$ such that $b \mstep s (i)$.
+        \item[\ule{$\gRPm(R)$}] \emph{$R$ has the weak recurrence property} if for every increasing sequence $s$ with bound $b$ there exists an $i \in \nat$ such that $b \mstep s (i)$.
     \end{description}
@@
 \begin{proof}
-    See, \hfill
     \begin{enumerate}
-        \item This is immediate.
-        \item \verb|RP-↔RP : R isRP- ↔ (R isRP)|
+        \item Immediate.
+        \item See \verb|RP-↔RP : R isRP- ↔ (R isRP)| in \texttt{Implications.agda}.
     \end{enumerate}
-    in \texttt{Implications.agda}
 \end{proof}
@@
 $\FB$ is a property that plays an important role in our discussion of well-foundedness (see Section \ref{sec:Well-foundedness}).
+
+\apcomment{Should expand this section, briefly summarize the definition of lists and the relevant lemmas, or
+point to standard the library.}

### 2025-06-06 Relations/Paper/Definitions.tex
Paper revision

@@
 
-\subsection{Closure operators (\texttt{Closure.agda})}
+\subsection{Closure operators (\texttt{ClosureOperators.agda})}
 
@@
     \item $\tclos{R}$ denotes the \emph{transitive closure} of $R$.
-    \item $R^* = (R^r)\tclos{}$ denotes the \emph{reflexive-transitive closure} of $R$.
+    \item $R^* = (R^r)\tclos{}$ denotes the \emph{reflexive--transitive closure} of $R$.
     \item $R^= = (R^s)^*$ denotes the \emph{equivalence relation generated by} $R$.
@@
 we may drop the corresponding subscript.
+
+The file \texttt{ClosureOperators.agda} verifies a number of properties of these operators
+on relations needed in the subsequent development, including interaction between them,
+monotonicity, preservation of logical equivalence, etc.
+\apcomment{Edit/Improve this!}
 
@@
         \item \verb|NP₌↔NP : R isNP₌ ↔ R isNP|
-        \item \verb|UN→|\texttt{UN}$^{\to}$\verb|: R isUN → R is|\texttt{UN}$^{\to}$
+        \item \verb|UN→|\texttt{UN}$^{\to}$\verb|: R isUN → R is|\texttt{UN}$^{\to}$ \qedhere
     \end{enumerate}
@@
 
-\subsection{Sequences and Recurrence (\texttt{Properties.agda}, \texttt{Seq.agda})}
+\subsection{Sequences and Recurrence (\texttt{Seq.agda})}
 % The following definitions are key to formalizing Theorem 1.2.3 in \terese.
 The definitions in this subsections are key to formalizing Theorem 1.2.3 in \terese.
+
+\begin{definition} \label{def:seq} \hfill
+  \begin{itemize}
+    \item A \emph{sequence} is a function $s$ from the natural numbers to $A$.
+    \item A sequence $s : \nat \to A$ is \emph{$R$-decreasing} if every element of the sequence is $R$-related to its preceding term.
+    \item A sequence $s : \nat \to A$ is \emph{$R$-increasing} if every element of the sequence is $R$-related to its succeeding term.
+  \end{itemize}
+\end{definition}
+
+\begin{definition}\hfill
+    \begin{description}
+        \item[\ule{$x \in CP_R$}] \emph{$x$ has the cofinality property} if there exists an $R^r$-increasing sequence
+        \mbox{$s : \nat {\to} A$} starting from $x$ such that every
+        reduct of $x$ reduces to some element of the sequence.
+        \[ x \mstep y \implies \exists i. y \mstep s(i) \]
+        % \item[\ule{$x \in CP_R$}] \emph{$x$ has the cofinality property} if there exists an
+        % (not necessarily strictly) increasing sequence starting from $x$ such that every
+        % reduct of $x$ reduces to some element of the sequence.
+    \end{description}
+\end{definition}
+
+\begin{definition} \label{def:bound} \hfill
+  \begin{description}
+    \item[\ule{$a \in A$ is an $s$-bound}] if for all $i \in \nat$, $s (i) \mstep a$.
+    \item[\ule{$s : \nat \to A$ is bounded}] if there exists $a \in A$ that is an $s$-bound.
+  \end{description}
+\end{definition}
+
+\begin{definition} \label{def:rp}
+  The following are global properties of the given relation $R$.  \hfill
+    \begin{description}
+        \item[\ule{$\gBP(R)$}] \emph{$R$ has the boundedness property} if every $R$-increasing sequence is bounded.
+        \item[\ule{$\gRP(R)$}] \emph{$R$ has the recurrence property} if for every bounded, increasing sequence $s$ with an $s$-bound, there exists an $i \in \nat$ such that
+        $s (i) \mstep x \implies x \mstep s (i)$ for all $x\in A$.
+        \item[\ule{$\gRPm(R)$}] \emph{$R$ has the weak recurrence property} if for every increasing sequence $s$ with bound $b$ there exists an $i \in \nat$ such that $b \mstep s (i)$.
+    \end{description}
+\end{definition}
+
+In \terese, $\mathrm{\,Ind}$ is used to denote $\gBP$.
+
+\terese also defines the following property, which is not included in our formalization.
 
@@
 Having a size function that maps all of $A$ to the natural numbers can be computationally taxing to satisfy.
-Furthermore, it takes us outside of a purely relational theory. The following properties will allow us to substitute $\gInc$ with weaker hypotheses in all the relevant places.
+Furthermore, it takes us outside of a purely relational theory.
+The weaker property $\gRP$ defined above will substitute $\gInc$ all places that require it.
 (For further discussion, see Subsection \ref{subsec:def}.)
-
-\begin{definition} \label{def:seq} \hfill
-  \begin{itemize}
-    \item A \emph{sequence} is a function $s$ from the natural numbers to $A$.
-    \item A sequence $s : \nat \to A$ is \emph{$R$-decreasing} if every element of the sequence is $R$-related to its preceding term.
-    \item A sequence $s : \nat \to A$ is \emph{$R$-increasing} if every element of the sequence is $R$-related to its succeeding term.
-  \end{itemize}
-\end{definition}
-
-\begin{definition} \label{def:rp} Let $a \in A$ and $s : \nat \to A$.
-    \begin{description}
-        % \item[\ule{$s : \nat \to A$}] \emph{A sequence $s \in A$} is a function from the natural numbers to $A$.
-        % \item[\ule{$s$ is $R$-increasing}] \emph{A sequence $s \in A$ is $R$-increasing} if every term is $R$-related to its preceding term.
-        \item[\ule{$a$ is an $s$-bound}] if $s (i) \mstep a$ for all $i \in \nat$.
-        \item[\ule{$a \in \BP_R$}] \emph{$a$ has the bound property} if for each $R$-increasing sequence $s$ with $s (0) = a$ there exists an $s$-bound.
-        \item[\ule{$\gRP(R)$}] \emph{$R$ has the recurrence property} if for every bounded, increasing sequence $s$ with an $s$-bound, there exists an $i \in \nat$ such that
-        $s (i) \mstep x \implies x \mstep s (i)$ for all $x\in A$.
-        \item[\ule{$\gRPm(R)$}] \emph{$R$ has the weak recurrence property} if for every increasing sequence $s$ with bound $b$ there exists an $i \in \nat$ such that $b \mstep s (i)$.
-    \end{description}
-\end{definition}
-
-In \terese $\mathrm{\,Ind}$ is used to denote $\BP$.
 
@@
 
-\begin{proof}
+\begin{proof} \hfill
     \begin{enumerate}
-        \item Immediate.
-        \item See \verb|RP-↔RP : R isRP- ↔ (R isRP)| in \texttt{Implications.agda}.
+        \item $\gInc$ implies that there are no bounded $R$-increasing sequences,
+        so $\gRP$ holds vacuously.
+        \item See \verb|RP-↔RP : R isRP- ↔ R isRP| in \texttt{Seq.agda}. \qedhere
     \end{enumerate}
@@
 
-%TODO: Update below to reflect new convenion for proofs and code.
-\begin{remark}
-    It follows that every relation that is increasing in the sense of \terese $\,$ vacuously satisfies the RP condition.
-\end{remark}
+\apcomment{Make sure to move this stuff to Seq.agda!}
+
+% %TODO: Update below to reflect new convenion for proofs and code.
+% \begin{remark}
+%     It follows that every relation that is increasing in the sense of \terese $\,$ vacuously satisfies the RP condition.
+% \end{remark}
 

### 2025-06-06 Relations/Paper/Formalization.tex
Paper revision

@@
 
-\subsection{Formalization of Definitions}\label{subsec:def}
+\subsection{Formalization of Definitions (\texttt{Base.agda})}\label{subsec:def}
+
+\apcomment{Rephrase this?  Or rewrite this subsection.}
+
+Most standard termination and confluence properties are defined in the file \texttt{Properties.agda}
+and related files discussed in the previous seciton.  The file \texttt{Base.agda} imports all of these files
+and introduces a few more notations used specifically for formalizing chapter 1 of \cite{Terese}.
+\apcomment{Discuss these...}
+
 The closure operators are formalized in \texttt{Closure.agda}.
@@
 The definitions grouped as normalizing in \terese $\,$ are formalized in \texttt{Properties.agda}.
+
+\apcomment{Should articulate the fact that normalization is defined as well-foundedness of the \emph{converse}
+relation, per \cite{Terese}.  Will discuss this separately in WF section, but should remind the reader of this
+whenever SN/SM comes up. }
+
+\apcomment{When SMseq comes up, also point to section 5, and the need for classical logic in going from
+sequential versions to inductive ones.  IOW, elaborate the summary below. }
 
@@
 
-\subsection{Propositions}
+\subsection{\texttt{Propositions.agda}}
 There are three sets of propositions given in \terese: \texttt{1.1.9}, \texttt{1.1.10}, \texttt{1.1.11}.
@@
 
-\subsection{Theorems}\label{subsec:theorems}
-\subsubsection{Newman's Lemma}
-There are three proofs of Newman's Lemma ($\SN \land \WCR \implies \CR$) given in \terese. 
+\subsection{\texttt{Theorems.agda}} \label{subsec:theorems}
+
+\begin{theorem}(Newman's Lemma)
+  $\gSN \land \gWCR \implies \gCR$
+\end{theorem}
+
+\begin{proof}
+  There are three proofs of Newman's Lemma given in \terese.
   The first and third of these proofs make use of classical reasoning. The second proof is amenable to a
@@
 
-We show in Subsection \ref{subsec:newnewman} a generalization of Newman's Lemma using a condition distilled from $\RP$. 
+  We show in Subsection \ref{subsec:newnewman} a generalization of Newman's Lemma using a condition distilled from $\gRP$.
   The formalizations of the remaining theorems are all found in \texttt{ARS-Theorems.agda}.
-\subsubsection{Theorem 1.2.2}
-There are three parts to this theorem. 
+\end{proof}
+
+\begin{theorem}(Thm 1.2.2 in [Terese])
 \begin{description}
@@
 \end{description}
+\end{theorem}
 
@@
 \end{proof}
-\begin{remark}
+\begin{proof}[Discussion.]
     In $\mathtt{UN^{→}∧WN→CR}$ a more general proof of ($ii$) is given using $\UNto$.
-\end{remark}
+\end{proof}
+\apcomment{Perhaps change the fourth implication to use $\times$ instead of $\to$ ??}
 
-\subsubsection{Theorem 1.2.3}
-The following definition is required for this theorem.
-\begin{definition}\hfill
-    \begin{description}
-        \item[\ule{$a \in CP_R$}] $a$ has the \emph{cofinality property} if there exists an 
-        (not necessarily strictly) increasing sequence starting from $a$ such that every
-        reduct of $a$ reduces to some element of the sequence.
-    \end{description}
-\end{definition}
+\begin{theorem}(Thm. 1.2.3 in [Terese])
+  \begin{enumerate}[(i)]
+    \item $\gWN \land \gUN \implies \gBP$
+    \item $\gBP \land \gInc \implies \gSN$
+    \item $\gWCR \land \gWN \land \gInc \implies \gSN$
+    \item $\gCR \iff \gCP$ ($\gCR \implies \gCP$ only holds if the ARS is countable.)
+  \end{enumerate}
+  % \begin{description}
+  %   \item[($i$)] $\gWN \land \gUN \implies \gBP$
+  %   \item[($ii$)] $\gBP \land \gInc \implies \gSN$
+  %   \item[($iii$)] $\gWCR \land \gWN \land \gInc \implies \gSN$
+  %   \item[($iv$)] $\gCR \iff \gCP$ ($\gCR \implies \gCP$ only holds if the ARS is countable.)
+  % \end{description}
+\end{theorem}
+\apcomment{Do the same for 1.2.2, and below!}
 
-There are four parts to this theorem. 
-\begin{description}
-    \item[($i$)] $\gWN \land \gUN \implies \gBP$
-    \item[($ii$)] $\gBP \land \gInc \implies \gSN$  
-    \item[($iii$)] $\gWCR \land \gWN \land \gInc \implies \gSN$
-    \item[($iv$)] $\gCR \iff \gCP$ ($\gCR \implies \gCP$ only holds if the ARS is countable.)
-\end{description}
 \begin{proof}
-    See, \\
+    See \texttt{Theorems.agda},\\
     \verb|i     : R isWN → R isUN → R isBP|\\
-    \verb|i→ : R isWN → R |\texttt{isUN}$^{\to}$ \verb|→ R isBP|\\
+    $\mathtt{i^\to}$\hspace{5mm} \verb|: R isWN → R |\texttt{isUN}$^{\to}$ \verb|→ R isBP|\\
     \verb|iiSeq : R isWN → R isUN → R isRP → isWFseq- (~R R)|\\
     \verb|iii   : R isWN → R isWCR → R isRP- → dec (SN) → R isSN|\\
-    \verb|iv : R isCP → R isCR| \\
-    in \texttt{Theorems.agda}.
+    \verb|iv    : R isCP → R isCR|
+\end{proof}
+\apcomment{Apply similar formatting elsewhere.}
+\begin{proof}[Discussion.]\hfill
+  \begin{description}
+    \item[($i$)] In $\mathtt{i^\to}$ we again provide a slight improvement by using $\gUNto$ rather than $\gUN$.
+    \item[($ii$)] This proof is inherently classical.
+In $\mathtt{iiSeq}$, we show that these properties imply $\isWFseqm$; establishing the implication to $\gSN$ would require additional classical assumptions.
+The definition and further discussion of $\isWFseqm$ are provided in Section~\ref{sec:Well-foundedness}.
+    \item[($iii$)] In $\mathtt{iii}$, we replace $\gInc$ with the more general property $\gRPm$.
+We also assume that $\gSN$ is decidable, as this allows the construction of a witness for whether an element possesses the property $\SN$, which is essential for our proof.
+    \item[($iv$)] We did not formalize $\gCR \to \gCP$ as it requires cardinality assumptions. \qedhere
+  \end{description}
 \end{proof}
 
-\begin{remark} \hfill
-    \begin{itemize}        
-        \item In $\mathtt{i\to}$ we again provide a slight improvement by using $\gUNto$ rather than $\gUN$.
-        \item ($ii$) is inherently classical.
+% \begin{remark} \hfill
+%     \begin{itemize}
+%         \item In $\mathtt{i^\to}$ we again provide a slight improvement by using $\gUNto$ rather than $\gUN$.
+%         \item ($ii$) is inherently classical.
 In $\mathtt{iiSeq}$, we show that these properties imply $\isWFseqm$; establishing the implication to $\gSN$ would require additional classical assumptions.
 The definition and further discussion of $\isWFseqm$ are provided in Section~\ref{sec:Well-foundedness}.
-        \item In $\mathtt{iii}$, we replace $\gInc$ with the more general property $\gRPm$.
+%         \item In $\mathtt{iii}$, we replace $\gInc$ with the more general property $\gRPm$.
 We also assume that $\gSN$ is decidable, as this allows the construction of a witness for whether an element possesses the property $\SN$, which is essential for our proof.
-        \item We did not formalize $\gCR \to \gCP$ as it requires cardinality assumptions.
-    \end{itemize}
-\end{remark}
+%         \item We did not formalize $\gCR \to \gCP$ as it requires cardinality assumptions.
+%     \end{itemize}
+% \end{remark}

### 2025-06-06 Relations/Paper/Summer_2025_TODO.tex
Paper revision

@@
     \item [\done] (Review 1) Typo: incaranations $\to$ incarnations.
-    \item (Review 1) Improve fonts for constant and text (refering to a definition on line 258). General formatting imrpovement for how we set out defns.
+    \item [\done] Improve fonts for constant and text (refering to a definition on line 258). General formatting imrpovement for how we set out defns.
     \item [\done] (Review 1) Improve the layout on line 270 where we set out iiSeq.
@@
     \item (Review 2) Unconvinced by the motivations for the project, believes the same can be achieved in a classical framework. So maybe we should explain our motivations more clearly.
-    \item (Review 2) Not convinced by our definitions, as they are imprecise and lack quantifiers. 
-    \item (Review 2) Issue with definition of R|=RP on line 188. Use of bounded is ambiguous. We should clarify which use of bounded.
-    \item (Our notes) Improve proposition 11 on line 194, we want to make the clame that RP- $\to$ RP, and either have a one line proof or refer to the proof in Agda. 
-    \item (Review 2) Section 3 is "full of repetitions and paraphrases between the statements in natural language and corresponding formalization".
+    \item [\done] Not convinced by our definitions, as they are imprecise and lack quantifiers.
+    \item [\done] Issue with definition of R|=RP on line 188. Use of bounded is ambiguous. We should clarify which use of bounded.
+    \item [\done] Improve proposition 11 on line 194, we want to make the clame that RP- $\to$ RP, and either have a one line proof or refer to the proof in Agda.
+    \item [\done] Section 3 is "full of repetitions and paraphrases between the statements in natural language and corresponding formalization".
 We can try and think of a way to get it to flow better, we do want to provide natural language summaries of what is in the code!
@@
 We should rethink the tables generally to make them clearer.
-Don't comma seperate and don't denote counterexamples as CE-XX.
-    \item (Review 2) Struggled to find the relevant agda code for the various definitions. We should find a way to better link the two.
-    \item (Review 2) TeReSe is not state of the art. We need state of the art references. Try this: https://termination-portal.org/wiki/WScT 
-    \item (Review 2) Clarify Notation 7 on line 159: "Choose a uniform notation, X or NP, but not both".
-    \item [\done] (we think) (Review 2) "l 169: An annoying notational collision between the two arrows -> at different heights."I'm not too sure what they're referring to, though there could be some ambiguity with the arrows here, especially with use of $UN\to$.
+\apcomment{Don't comma seperate and don't denote counterexamples as CE-XX.
+?}
+    \item [\done] Struggled to find the relevant agda code for the various definitions. We should find a way to better link the two.
+    \item [\done] Clarify Notation 7 on line 159: "Choose a uniform notation, X or NP, but not both".
+    \item [\done] l 169: An annoying notational collision between the two arrows -> at different heights."I'm not too sure what they're referring to, though there could be some ambiguity with the arrows here, especially with use of $UN\to$.
     \item (Review 2) "l 361: Swap s(k+1) and s(k) " We should clarify the definition here otherwise people (evidently) get confused.
@@
         \item What are the differences and improvements of the formalization in this paper and the ones in the literature?
+        \item (Review 2) TeReSe is not state of the art. We need state of the art references. Try this: https://termination-portal.org/wiki/WScT
     \end{itemize}
@@
   \item For showing inc -> RP we're currently just saying "This is immediate". Is this sufficient? We did have a proof previously but I think we removed it for space reasons.
+  \item Remove "desired implications" and similar organizational issues in the code (general review)
+  \item Consider defining FB in terms of existing list library; especially in the rebooted repo,
+  we shouldn't use manual List type just for this.
+  \item Move all definitions and properties from Section 2.3 to Seq.agda, except Inc.
+  \item Revise section 3.1
 \end{todolist}

### 2025-06-12 Relations/Paper/Summer_2025_TODO.tex
Update with email todos

@@
 \end{todolist}
+\section*{Week starting 9th June (some of these items taken from Dr. Polonsky's email sent June 6th)}
+\begin{todolist}
+  \item [\done] Thm. 19(iv), i don't like that the parens are italicized.  maybe it would be okay if instead of CR => CP we just write "the forward implication"
+  \item [\done] Proof of (iii), line 296: do we really need () around SN?
+  \item Page 9, second half (the hierarchy): we should add a proof that $\MF \cap \SN \iff \NF$, say this in the text, and note that this does NOT hold for $\SM$ and $\WN$.
+Hence, the tables include a separate column for their combination.
+  \item  In the par before 4.1 counterexamples, add that in the global table, the counterexample 3 satisfies the hypotheses globally.
+(I actually wonder whether we need example 9 at all, if we have a counterexample to the global one.
+Am I missing something?).
+\sacomment{I don't think we need to expand that CE:3 satisfies the global hypotheses.
+I'm hoping that we've done enough to show to the reader how to read the table at this point.
+If you disagree I'm happy to add it in though.
+As to why have local and global counterexamples, good point.
+Unless either of us can think of a reason we'll remove in the next meeting.}
+    \item [\done] the * and dagger in the table should be explained in the caption, or in the text.
+    \sacomment{I prefer to have this as a footnote. I have put it as a caption for now but I would revert it to what we had before.  }
+\end{todolist}
 \end{document}

### 2025-06-13 Relations/Paper/Definitions.tex
Various small changes

@@
 
-The file \texttt{ClosureOperators.agda} verifies a number of properties of these operators
-on relations needed in the subsequent development, including interaction between them,
-monotonicity, preservation of logical equivalence, etc.
-\apcomment{Edit/Improve this!}
+The file \texttt{ClosureOperators.agda} verifies key properties of closure operators
+on relations, including their monotonicity, preservation of equivalence, and interactions such as inclusions and equivalences between different closures.
 
@@
     \begin{description}
-        \item[\ule{$a \in \WCR_R$}] \emph{$a$ is weakly Church-Rosser} (or \emph{weakly confluent}) if for all $b,c \in A$, \[c \bstep a \rstep b \implies \exists d. c \mstep d \bmstep b\]
-        \item[\ule{$a \in \CR_R$}] \emph{$a$ is Church-Rosser} (or \emph{confluent}) if for all $b,c \in A$, \[c \bmstep a \mstep b \implies \exists d. c \mstep d \bmstep b\]
+        \item[\ule{$a \in \WCR_R$}] \emph{$a$ is weakly Church-Rosser} (or \emph{weakly confluent}) if for all $b,c \in A$, \[c \bstep a \rstep b \implies \exists d.\, c \mstep d \bmstep b\]
+        \item[\ule{$a \in \CR_R$}] \emph{$a$ is Church-Rosser} (or \emph{confluent}) if for all $b,c \in A$, \[c \bmstep a \mstep b \implies \exists d.\, c \mstep d \bmstep b\]
         \item[\ule{$a \in \CRs_R$}] \emph{$a$ is subcommutative} if for all $b, c \in A$,
-        \[c \bmstep a \mstep b \implies c \rrstep d \brstep b\]
+        \[c \bmstep a \mstep b \implies \exists d. \, c \rrstep d \brstep b\]
         \item[\ule{$a \in \NPe_R$}] \emph{$a$ has the conversion normal form property} if for all $b \in \NF_R$, \[ a \estep b \implies a\mstep b\]
@@
 \begin{remark}
-    The implication $\UNto \implies \UN$ does not hold, as can be seen in Counterexample~\ref{CE:5} in Subsection~\ref{subsec:counterexamples}.
-    \apcomment{Provide a ref to a figure, eventually.}
+    The implication $\UNto \implies \UN$ does not hold, as can be seen in Counterexample~\ref{CE:5} in Figure~\ref{fig:counterexamples}.
 \end{remark}
@@
 
-\terese also defines the following property, which is not included in our formalization.
+\terese $\,$ also defines the following property, which is not included in our formalization.
 
@@
 The weaker property $\gRP$ defined above will substitute $\gInc$ all places that require it.
-(For further discussion, see Subsection \ref{subsec:def}.)
+(For further discussion, see Subsection~\ref{subsec:def}.)
 
@@
 \apcomment{Make sure to move this stuff to Seq.agda!}
+\sacomment{This will create a circular dependency as Seq is used in properties (the increasing definition is needed for BP, CP, RP, SMseq, SRv2).
+Simple solution is to leave RP-iffRP in implications.agda.}
 

### 2025-06-17 Relations/Paper/Implications.tex
Paper revision
CEs now a figure. Table footnotes moved.
Update to CE 9

@@
 
-\begin{definition}\label{def:mf} \hfill
+\begin{definition}\label{def:mf} Let $a \in A$. \hfill
     \begin{description}
@@
         \item[\ule{$a \in \MP_R$}] \emph{$a$ has the minimal form property} if $c \bmstep a \mstep b \implies c \mstep b$ for any $b \in \MF$.
-
     \end{description}
@@
         \hline
-        $\NP$ & CE-\ref{CE:9} & CE-\ref{CE:8} & $\CR$ & CE-\ref{CE:6} & $\CR$\footnotemark[1] & CE-\ref{CE:8} & $\CR$ & $\SN$ & $\CR$\footnotemark[2] & $\SN$ \\
+        $\NP$ & CE-\ref{CE:3} & CE-\ref{CE:8} & $\CR$ & CE-\ref{CE:6} & $\CR$\footnotemark[1] & CE-\ref{CE:8} & $\CR$ & $\SN$ & $\CR$\footnotemark[2] & $\SN$ \\
         \hline
@@
     \end{tabular}
-    \caption{Global implications}
+    \caption{Global implications.
+\\$^*$~This implication also requires $\gWCR$.
+\\ $^\dagger$~This implication also requires either $\gWCR$ or the classical property required to go from $\SN \to \WN$ or $\SM \to \WM$.}
 \end{table}
-\footnotetext[1]{This implication also requires $\gWCR$.}
-\footnotetext[2]{This implication also requires either $\gWCR$ or the classical property required to go from 
-$\SN \to \WN$ or $\SM \to \WM$.}
+% \footnotetext[1]{This implication also requires $\gWCR$.}
+% \footnotetext[2]{This implication also requires either $\gWCR$ or the classical property required to go from
+% $\SN \to \WN$ or $\SM \to \WM$.}
 \renewcommand*{\thefootnote}{\arabic{footnote}}
@@
 The table should be interpreted as follows: for example, if a relation possesses the property $\NP$, then, according to the table, obtaining the property $\CR$ requires, at a minimum, the additional property $\WN$.
-Counterexample~\ref{CE:9} demonstrates that the combination of $\WM$ and $\NP$ is insufficient to guarantee $\CR$.
+Counterexample~\ref{CE:3} demonstrates that the combination of $\WM$ and $\NP$ is insufficient to guarantee $\CR$.
 
@@
 \newcounter{CEcounter}
+\begin{figure}[htbp]
+    \centering
+    % \begin{center}
     \renewcommand{\theCEcounter}{\arabic{CEcounter}}
-
-    \begin{center}
         \begin{tabular}{ccc}  % Three columns per row
@@
     % \\
+    % &
+    % \begin{minipage}{0.3\textwidth}
+    %     \centering
+    %     \begin{counterexample}\label{CE:9}  \\ We think CE:9 is covered by CE:3
+    %         \begin{tikzcd}[row sep=small, column sep=small]
+    %             d  \arrow[d] \arrow[rr, bend left] & a \arrow[r] \arrow[l]  &
+    %             b \arrow[r, bend left] & c \arrow[l, bend left] \\
+    %             f_0 \arrow[r] & f_1 \arrow[r] & f_2 \arrow[r] & \dots
+    %         \end{tikzcd} \\
+    %     \end{counterexample}
+    % \end{minipage}
+    % New row
+    % \\
+    % \\
     &
-    \begin{minipage}{0.3\textwidth}
-        \centering
-        \begin{counterexample}\label{CE:9}
-            \begin{tikzcd}[row sep=small, column sep=small]
-                d  \arrow[d] \arrow[rr, bend left] & a \arrow[r] \arrow[l]  &  
-                b \arrow[r, bend left] & c \arrow[l, bend left] \\  
-                f_0 \arrow[r] & f_1 \arrow[r] & f_2 \arrow[r] & \dots  
-            \end{tikzcd} \\
-        \end{counterexample}
-    \end{minipage}
-    % New row
-    \\
-    \\
     \begin{minipage}{0.3\textwidth}
@@
     \end{minipage}
-    &
+    % &
+    % &
+      % New row
+    \\
+    \\
     &
@@
 \end{tabular}
-\end{center}
+\caption{Counterexamples}
+\label{fig:counterexamples}
+\end{figure}
 

### 2025-06-17 Relations/Paper/Summer_2025_TODO.tex

@@
     \item [\done] Verify which implications have and have not been formalized from the image.
-    \item (Missing imp) $\lnot \lnot$ WFacc $\leftrightarrow$ $\lnot \lnot WFind$.
+    \item [\done] $\lnot \lnot$ WFacc $\leftrightarrow$ $\lnot \lnot WFind$.
+    \apcomment{WFind to be removed, this is addressed in the Friday June 13th notes}
     \item [\done] (Missing imp) WFmin- $\to$ WFDNE-
@@
   \item Mention theorem 123 ii and iii are inherently classical. For iii we require strong decidability.
-  \item Working on CR $\to$ CP. Low priority.
+  \item [\done] Working on CR $\to$ CP. Low priority. \apcomment{This is mentioned as one of the research items above}
 \end{todolist}
@@
   \item[\ule{$a \in \WCR_R$}] \emph{$a$ is weakly Church-Rosser (or weakly confluent)} if $c \bstep a \rstep b \implies c \mstep d \bmstep b$ for all $b, c, d \in A$.
-  \item For showing inc -> RP we're currently just saying "This is immediate". Is this sufficient? We did have a proof previously but I think we removed it for space reasons.
+  \item [\done] For showing inc -> RP we're currently just saying "This is immediate". Is this sufficient? We did have a proof previously but I think we removed it for space reasons.
   \item Remove "desired implications" and similar organizational issues in the code (general review)
@@
   we shouldn't use manual List type just for this.
-  \item Move all definitions and properties from Section 2.3 to Seq.agda, except Inc.
+  \item [\done] Move all definitions and properties from Section 2.3 to Seq.agda, except Inc.
   \item Revise section 3.1
@@
 \end{todolist}
+
+\subsection*{Notes from meeting on Friday June 13th}
+
+\begin{itemize}
+  \item Perhaps we should not create variations and multiple implications of WFind,
+  but rather prove that it's equivalent to WFacc, but lands in a higher universe.
+  Mention this once at the beginning of section 5 then proceed to analyze
+  connections between WFacc and WFseq/WFmin.
+\end{itemize}
+
 \end{document}

### 2025-06-18 Relations/Paper/Definitions.tex
Minor updates to the report

@@
 
-\apcomment{Make sure to move this stuff to Seq.agda!}
-\sacomment{This will create a circular dependency as Seq is used in properties (the increasing definition is needed for BP, CP, RP, SMseq, SRv2).
-Simple solution is to leave RP-iffRP in implications.agda.}
-
-% %TODO: Update below to reflect new convenion for proofs and code.
-% \begin{remark}
-%     It follows that every relation that is increasing in the sense of \terese $\,$ vacuously satisfies the RP condition.
-% \end{remark}
-
 \subsection{Finitely branching (\texttt{FinitelyBranching.agda})}
@@
 
-Our Agda formulation of the above definition makes use of the List type constructor.
+Our Agda formulation of the above definition makes use of the List type constructor, which we import from the \href{https://agda.github.io/agda-stdlib/v2.1/Agda.Builtin.List.html}{Agda standard library}.
+
 \verb|FB a = Σ[ xs ∈ List A ] (∀ b → R b a → b ∈List xs)|

### 2025-06-18 Relations/Paper/Formalization.tex
Minor changes
Minor updates to the report

@@
 
-Most standard termination and confluence properties are defined in the file \texttt{Properties.agda}
-and related files discussed in the previous seciton.  The file \texttt{Base.agda} imports all of these files
+Most standard termination and confluence properties are defined in the file \texttt{Properties.agda} and related files discussed in the previous section.
+The file \texttt{Base.agda} imports all of these files
 and introduces a few more notations used specifically for formalizing chapter 1 of \cite{Terese}.
@@
 
-The closure operators are formalized in \texttt{Closure.agda}.
+The closure operators are formalized in \texttt{ClosureOperators.agda}.
 The definitions grouped as confluent in \terese $\,$ are formalized in \texttt{Base.agda}.
@@
     \item $\gWCR \land \gWN \land \gInc \implies \gSN$
-    \item $\gCR \iff \gCP$ ($\gCR \implies \gCP$ only holds if the ARS is countable.)
+    \item $\gCR \iff \gCP$ $($the forward implication only holds if the ARS is countable.$)$
   \end{enumerate}
@@
     \verb|iiSeq : R isWN → R isUN → R isRP → isWFseq- (~R R)|\\
-    \verb|iii   : R isWN → R isWCR → R isRP- → dec (SN) → R isSN|\\
+    \verb|iii   : R isWN → R isWCR → R isRP- → dec SN → R isSN|\\
     \verb|iv    : R isCP → R isCR|

### 2025-06-18 Relations/Paper/Formalization.tex
Rewording the intro to base.agda

@@
 
-Most standard termination and confluence properties are defined in the file \texttt{Properties.agda} and related files discussed in the previous section.
-The file \texttt{Base.agda} imports all of these files
-and introduces a few more notations used specifically for formalizing chapter 1 of \cite{Terese}.
-\apcomment{Discuss these...}
-
-The closure operators are formalized in \texttt{ClosureOperators.agda}.
-The definitions grouped as confluent in \terese $\,$ are formalized in \texttt{Base.agda}.
-The definitions grouped as normalizing in \terese $\,$ are formalized in \texttt{Properties.agda}.
+As outlined in the previous section, \texttt{Properties.agda}, \texttt{Seq.agda}, and \texttt{ClosureOperators.agda} define most standard termination and confluence properties.
+The file \texttt{Base.agda} introduces additional defitions which are required for the formalization of the propositions found in Chapter 1 of \terese.
 

### 2025-07-08 Relations/Paper/Definitions.tex
Updates to formalization section. Mainly proof environment.

@@
 
-Our Agda formulation of the above definition makes use of the List type constructor, which we import from the \href{https://agda.github.io/agda-stdlib/v2.1/Agda.Builtin.List.html}{Agda standard library}.
+Our Agda formulation of the above definition makes use of the List type constructor, which we import from the Agda Standard Library \cite{AgdaLibraryList}.
 
@@
 $\FB$ is a property that plays an important role in our discussion of well-foundedness (see Section \ref{sec:Well-foundedness}).
-
-\apcomment{Should expand this section, briefly summarize the definition of lists and the relevant lemmas, or
-point to standard the library.}

### 2025-07-08 Relations/Paper/Formalization.tex
Updates to formalization section. Mainly proof environment.

@@
 
-\apcomment{Rephrase this?  Or rewrite this subsection.}
-
 As outlined in the previous section, \texttt{Properties.agda}, \texttt{Seq.agda}, and \texttt{ClosureOperators.agda} define most standard termination and confluence properties.
 The file \texttt{Base.agda} introduces additional defitions which are required for the formalization of the propositions found in Chapter 1 of \terese.
-
-\apcomment{Should articulate the fact that normalization is defined as well-foundedness of the \emph{converse}
-relation, per \cite{Terese}.  Will discuss this separately in WF section, but should remind the reader of this
-whenever SN/SM comes up. }
 
@@
     \item $\SN$ : We define this via the notion of accessibility rather than the non-existence of infinite reduction sequences.
+Both definitions articulate normalization as well-foundedness of the converse relation.
+However, different notions of well-foundedness are used in the two definitions.
+The differences are highlighted in Sections~\ref{sec:Well-foundedness}.
      See Section \ref{sec:Well-foundedness} for further discussion.
@@
   \verb|NewmansLemma : R isSN → R isWCR → R isCR|.
+\end{proof}
 
   We show in Subsection \ref{subsec:newnewman} a generalization of Newman's Lemma using a condition distilled from $\gRP$.
-  The formalizations of the remaining theorems are all found in \texttt{ARS-Theorems.agda}.
-\end{proof}
+  The formalizations of the remaining theorems are all found in \texttt{Theorems.agda}.
 
 \begin{theorem}(Thm 1.2.2 in [Terese])
-\begin{description}
-  \item[($i$)] $\gCR \implies \gNPe \implies \gUN$
-  \item[($ii$)] $\gWN \land \gUN \implies \gCR$
-  \item[($iii$)] $\gCRs \implies \gCR$
-\end{description}
+\begin{enumerate}[(i)]
+  \item $\gCR \implies \gNPe \implies \gUN$
+  \item $\gWN \land \gUN \implies \gCR$
+  \item $\gCRs \implies \gCR$
+\end{enumerate}
 \end{theorem}
@@
 \begin{proof}
-    See, \\
+    See \texttt{module Theorem-1-2-2} in \texttt{Theorems.agda}, \\
     \verb|CR→NP : R isCR → R isNP₌|\\
@@
     \verb|iii : subcommutative R → R isCR|\\
-    in \texttt{Theorems.agda}.
 \end{proof}
@@
   \end{enumerate}
-  % \begin{description}
-  %   \item[($i$)] $\gWN \land \gUN \implies \gBP$
-  %   \item[($ii$)] $\gBP \land \gInc \implies \gSN$
-  %   \item[($iii$)] $\gWCR \land \gWN \land \gInc \implies \gSN$
-  %   \item[($iv$)] $\gCR \iff \gCP$ ($\gCR \implies \gCP$ only holds if the ARS is countable.)
-  % \end{description}
 \end{theorem}
-\apcomment{Do the same for 1.2.2, and below!}
 
 \begin{proof}
-    See \texttt{Theorems.agda},\\
+    See \texttt{module Theorem-1-2-3} in \texttt{Theorems.agda},\\
     \verb|i     : R isWN → R isUN → R isBP|\\
@@
 \end{proof}
-\apcomment{Apply similar formatting elsewhere.}
 \begin{proof}[Discussion.]\hfill
@@
 \end{proof}
-
-% \begin{remark} \hfill
-%     \begin{itemize}
-%         \item In $\mathtt{i^\to}$ we again provide a slight improvement by using $\gUNto$ rather than $\gUN$.
-%         \item ($ii$) is inherently classical.
-In $\mathtt{iiSeq}$, we show that these properties imply $\isWFseqm$; establishing the implication to $\gSN$ would require additional classical assumptions.
-The definition and further discussion of $\isWFseqm$ are provided in Section~\ref{sec:Well-foundedness}.
-%         \item In $\mathtt{iii}$, we replace $\gInc$ with the more general property $\gRPm$.
-We also assume that $\gSN$ is decidable, as this allows the construction of a witness for whether an element possesses the property $\SN$, which is essential for our proof.
-%         \item We did not formalize $\gCR \to \gCP$ as it requires cardinality assumptions.
-%     \end{itemize}
-% \end{remark}

### 2025-07-08 Relations/Paper/Summer_2025_TODO.tex
Implications and summertodo minor changes update

@@
     \item Carry on refactoring Wellfounded.agda once fixed, breaking it up if necessary.
-    \item Think about how to organize the Git repo going forward. For example, could be good to have a parent folder with ARS and WF, with a private dir for paper
+    \item [\done] Think about how to organize the Git repo going forward. For example, could be good to have a parent folder with ARS and WF, with a private dir for paper
     \item (Research item) How to go from WFseq to WFacc - possible that the Kleene Tree is a solution.
@@
   \item Double check the counterexamples match in the table to the diagrams.
-  \item Make clear in proof references to agda code how it should be read (especially the first one). Make clear the module as well. After doing once, the others don't need to be as explicit.
+  \item [\done] Make clear in proof references to agda code how it should be read (especially the first one). Make clear the module as well. After doing once, the others don't need to be as explicit.
   \item [\done] find a seperate symbol for -> in the code sections in the paper for UN$\to$. Superscipt would be perfect. $UN^{\rightarrow}$
-  \item Mention theorem 123 ii and iii are inherently classical. For iii we require strong decidability.
+  \item [\done] Mention theorem 123 ii and iii are inherently classical. For iii we require strong decidability.
   \item [\done] Working on CR $\to$ CP. Low priority. \apcomment{This is mentioned as one of the research items above}
@@
 \begin{todolist}
-  \item Should we add quantification to each definition(I think quantification for $a$ is already implied)? E.g.\\
+  \item [\done] Should we add quantification to each definition(I think quantification for $a$ is already implied)? E.g.\\
   \item [\ule{$a \in \WCR_R$}] \emph{$a$ is weakly Church-Rosser (or weakly confluent)} if $c \bstep a \rstep b \implies c \mstep d \bmstep b$.\\
@@
   \item [\done] For showing inc -> RP we're currently just saying "This is immediate". Is this sufficient? We did have a proof previously but I think we removed it for space reasons.
-  \item Remove "desired implications" and similar organizational issues in the code (general review)
-  \item Consider defining FB in terms of existing list library; especially in the rebooted repo,
+  \item [\done] Remove "desired implications" and similar organizational issues in the code (general review)
+  \item [\done] Consider defining FB in terms of existing list library; especially in the rebooted repo,
   we shouldn't use manual List type just for this.
   \item [\done] Move all definitions and properties from Section 2.3 to Seq.agda, except Inc.
-  \item Revise section 3.1
+  \item [\done] Revise section 3.1
 \end{todolist}

### 2025-07-08 Relations/Paper/Formalization.tex
Implications and summertodo minor changes update
Changes made on meeting 8th July

@@
 
-\apcomment{When SMseq comes up, also point to section 5, and the need for classical logic in going from
-sequential versions to inductive ones.  IOW, elaborate the summary below. }
-
-The following is a summary of the differences in definition we have used as mentioned in Section \ref{sec:Definitions}.
+The following is a summary of the differences in definitions we have used as mentioned in Section \ref{sec:Definitions}.
 \begin{itemize}
@@
 However, different notions of well-foundedness are used in the two definitions.
-The differences are highlighted in Sections~\ref{sec:Well-foundedness}.
+The differences are highlighted in Section~\ref{sec:Well-foundedness}.
      See Section \ref{sec:Well-foundedness} for further discussion.
@@
 sequence can have an upper bound.
-We establish that the equivalent properties $\RP$ and $\RPm$ are sufficient for replacing $\Inc$ in the theorem (see Subsection \ref{subsec:theorems}),
-which led us to examine the condition on $s (i)$ appearing inside $\RP$ more closely. This condition provides a generalization of the notion of a normal form,
+We establish that the weaker property $\RP$ (or its equivalent $\RPm$) is sufficient for replacing $\Inc$ in the theorem (see Subsection \ref{subsec:theorems}).
+This led us to examine the condition on $s (i)$ appearing inside $\RP$ more closely. This condition provides a generalization of the notion of a normal form,
 which we explore in detail in Section \ref{sec:Hierarchy}.
@@
     \verb|ii     : R isWN × R isUN → R isCR|\\
-    \verb||\texttt{UN}$^{\to}$ \verb|∧WN→CR : R |\texttt{isUN}$^{\to}$ \verb| → R isWN → R isCR|\\
+    \verb|ii+    : R isWN × R |\texttt{isUN}$^{\to}$ \verb|→ R isCR|\\
     \verb|iii    : subcommutative R → R isCR|\\
@@
 \end{proof}
-\apcomment{Perhaps change the fourth implication to use $\times$ instead of $\to$ ??}
 

### 2025-07-08 Relations/Paper/Implications.tex
Implications and summertodo minor changes update
Changes made on meeting 8th July

@@
 
-% From the perspective of programming language theory, the two properties of abstract rewriting
-% systems that are most interesting are $\SN$ and $\CR$. The following hierarchies
-% show chains of implications starting from these properties.
 This section examines the hierarchy of ARS properties.
@@
 with termination and those associated with confluence.
-% Possibly redundant introductory paragraph
 
@@
         \item[\ule{$a \in \WM_R$}] \emph{$a$ is weakly minimalizing} if $a \mstep b$ for some $b \in \MF_R$.
+        \item[\ule{$a \in \SM_R$}]  \emph{$a$ is strongly minimalizing} if either $a \in MF_R$, or every element one $R$ step from $a$ is strongly minimalizing. (This
+        definition is to be understood inductively).
         \item[\ule{$a \in \SMseq_R$}] \emph{$a$ is sequentially strongly minimalizing} if for every $R$-increasing sequence $s$ starting at $a$, there exists
         an $i \in \nat$ such that $s (i) \in \MF$.
-        \item[\ule{$a \in \SM_R$}]  \emph{$a$ is strongly minimalizing} if either $a \in MF_R$, or every element one $R$ step from $a$ is strongly minimalizing. (This
-        definition is to be understood inductively).
         \item[\ule{$a \in \MP_R$}] \emph{$a$ has the minimal form property} if $c \bmstep a \mstep b \implies c \mstep b$ for any $b \in \MF$.
@@
 \begin{proposition}\label{prop:nftomf}
-    $\NF \implies \MF$
+    $\forall x.\, x\in \NF \implies x \in \MF$
 \end{proposition}
@@
 \begin{proposition}\label{prop:SMRP}
-    $SMseq \leftrightarrow RP \land BP$
+    $\gSMseq \iff \gRP \land \gBP$
 \end{proposition}
 \begin{proof}
-    See,\\
+    See \texttt{Implications.agda},\\
     \verb|RP∧BP→SMseq    : R isRP → R isBP → ∀ {x : A} → SMseq R x| \\
@@
     \verb|RisSMseq→RisBP : (∀ {x : A} → SMseq R x) → R isBP| \\
-    in \texttt{Implications.agda}.
 \end{proof}
@@
 The same property is similarly required in order to show that $\SM$ implies $\WM$.
+
+\begin{proposition}\label{prop:MFtoNF} \hfill
+    \begin{enumerate}
+        \item $\forall x.\, x\in \MF \land x \in \WN \iff x \in \NF$
+        \item $\forall x.\, x\in \MF \land x \in \SN \iff x \in \NF$
+    \end{enumerate}
+
+\end{proposition}
+\begin{proof}
+    See \texttt{module Normalizing-Implications} in \texttt{Implications.agda},\\
+    \verb|MF∧WN↔NF : ∀ {x} → MF x × WN x ↔ NF x|\\
+    \verb|MF∧SN↔NF : ∀ {x} → MF x × SN x ↔ NF x| \qedhere
+\end{proof}
+
+In contrast to the above proposition, the inclusion $\SN \subset \SM \cap \WN $ is strict: in Counterexample~\ref{CE:4}, $a \in \SM \cap \WN$, but $a \notin \SN$.
+In the tables below, we therefore include a seperate column for the combination of $\SM$ and $\WN$.
 

### 2025-07-08 Relations/Paper/Summer_2025_TODO.tex
Changes made on meeting 8th July

@@
     \item [\done] l 169: An annoying notational collision between the two arrows -> at different heights."I'm not too sure what they're referring to, though there could be some ambiguity with the arrows here, especially with use of $UN\to$.
-    \item (Review 2) "l 361: Swap s(k+1) and s(k) " We should clarify the definition here otherwise people (evidently) get confused.
-    \item (Review 2) "l 422: $P_x$ has no arguments?"
+    \item [\done] (Review 2) "l 361: Swap s(k+1) and s(k) " We should clarify the definition here otherwise people (evidently) get confused.
+    \item [\done](Review 2) "l 422: $P_x$ has no arguments?"
     \item (Review 3) Check out and include the following related work:
@@
 12.
-    \item (Review 3) In line 270, isWFseq- is used in Section 3 but defined only in Section 5.
-    \item (Review 3) In line 192, the authors state that (in TeReSe) Ind denotes BP.
+    \item [\done](Review 3) In line 270, isWFseq- is used in Section 3 but defined only in Section 5.
+    \item [\done] (Review 3) In line 192, the authors state that (in TeReSe) Ind denotes BP.
 However, in line 186, BP is defined from an R-increasing sequence, whereas this statement is not required in the definition of Ind by TeReSe.
@@
   \begin{todolist}
-    \item  Fix Wellfounded.agda after changes made during meeting.
-    \item Carry on refactoring Wellfounded.agda once fixed, breaking it up if necessary.
+    \item [\done] Fix Wellfounded.agda after changes made during meeting.
     \item [\done] Think about how to organize the Git repo going forward. For example, could be good to have a parent folder with ARS and WF, with a private dir for paper
-    \item (Research item) How to go from WFseq to WFacc - possible that the Kleene Tree is a solution.
-    \item (Research item) Go deeper in the related works and see which are most relevant. Make a list of works and give summaries to be used in future papers.
-    \item (Research item) Find a concrete application of generalized Newman's Lemma.
-    \item (Research item) Use TeReSe to create a list of rewrite systems.
-    \item (Research item) Work on the missing implicaitons from the paper. So far we believe this is just CR $\to$ CP in the ARS section.
-    \item (Research item) Formalize a first order term rewriting system (I can't remember what the motivation for this was).
-    \item (Research item) Carry out research on rewriting counterexamples like our own so we can try and put them into some sort of context. Have our counerexamples been shown before?
-    \item (Research item) Do we want to reincorporate Knaster Tarski?
+
   \end{todolist}
@@
 \begin{todolist}
-  \item Double check the counterexamples match in the table to the diagrams.
+  \item [\done] Double check the counterexamples match in the table to the diagrams.
   \item [\done] Make clear in proof references to agda code how it should be read (especially the first one). Make clear the module as well. After doing once, the others don't need to be as explicit.
@@
   \item [\done] Proof of (iii), line 296: do we really need () around SN?
-  \item Page 9, second half (the hierarchy): we should add a proof that $\MF \cap \SN \iff \NF$, say this in the text, and note that this does NOT hold for $\SM$ and $\WN$.
+  \item [\done] Page 9, second half (the hierarchy): we should add a proof that $\MF \cap \SN \iff \NF$, say this in the text, and note that this does NOT hold for $\SM$ and $\WN$.
 Hence, the tables include a separate column for their combination.
-  \item  In the par before 4.1 counterexamples, add that in the global table, the counterexample 3 satisfies the hypotheses globally.
+  \item [\done] In the par before 4.1 counterexamples, add that in the global table, the counterexample 3 satisfies the hypotheses globally.
 (I actually wonder whether we need example 9 at all, if we have a counterexample to the global one.
@@
 
+\section*{July TODO}
+\begin{todolist}
+  \item Carry on refactoring Wellfounded.agda once fixed, breaking it up if necessary.
+  \item To finish the paper: We should do a final walk through and make sure we haven't introduced errors with our edits.
+In particular, do all the counterexamples line up.
+Do all the references to different sections and pieces of code in Agda line up.
+  \item Do we remove all our local counterexamples in favour of global ones?
+  \item Rework well-foundedness section 
+  \item Rework conclusion 
+  \item Rework introduction 
+  \item Do we introduce a new section for discussing Agda? Talking about why we think there is an advantage to doing this work in Agda vs (say) Isabelle
+
+\end{todolist}
+
+\section*{Research items}
+\begin{todolist}
+  \item (Research item) Go deeper in the related works and see which are most relevant.
+Make a list of works and give summaries to be used in future papers.
+* Look into the literature and related works.
+There should be an Agda formulation of rewrite systems (check agda standard library stuff on relations).
+  \item (Research item) Find a concrete application of generalized Newman's Lemma.
+* Finding a term rewrite system where it's eassier to see that it is weakly cr and that every term is SM (as opposed to being CR).
+  \item (Research item) Formalize a first order term rewriting system (I can't remember what the motivation for this was). Use TeReSe to create a list of rewrite systems.
+  \item (Research item) Carry out research on rewriting counterexamples like our own so we can try and put them into some sort of context. Have our counerexamples been shown before?
+  \item (Research item) Work on the missing implicaitons from the paper. So far we believe this is just CR $\to$ CP in the ARS section. - Will probably be quite a bit of work (low priority)
+  \item (Research item) Do we want to reincorporate Knaster Tarski? - Not this paper 
+  \item (Research item) How to go from WFseq to WFacc - possible that the Kleene Tree is a solution. - Not this paper
+
+\end{todolist}
+
 \end{document}

### 2025-07-08 Relations/Paper/Well-foundedness.tex
Changes made on meeting 8th July

@@
 \section{Well-foundedness}
-
-\newcommand{\isWFacc}{\mathtt{isWFacc}}
-\newcommand{\isWFseq}{\mathtt{isWFseq}}
-\newcommand{\isWFmin}{\mathtt{isWFmin}}
-\newcommand{\isWFaccm}{\mathtt{isWFacc-}}
-\newcommand{\isWFseqm}{\mathtt{isWFseq-}}
-\newcommand{\isWFminm}{\mathtt{isWFmin-}}
-
-\newcommand{\isMinDec}{\mathtt{isMinDec}}
 
@@
 as the absence of an infinite $R$-decreasing sequence.
+(Again, well-foundedness of $R$ corresponds to strong normalization of its converse.)
 Translating this statement directly into type theory yields the formula
-\[\tag{$\isWFseqm$} \lnot \big(\exists s : \nat \to A \forall k : \nat. (s(k+1),s(k)) \in R \big) \]
+
+\[\tag{$\isWFseqm$} \lnot \big(\exists s : \nat \to A \forall k : \nat. \  R \,(s\,(k+1)) \, (s\, k) \big) \]
+
 (The label $\isWFseqm$ refers to the name of the corresponding term in \texttt{Wellfoundedness.agda}.)
@@
 in the sequence that does not reduce to the next one.  This yields the statement
-\[\tag{$\isWFseq$} \forall s : \nat \to A \exists k : \nat. (s(k),s(k+1)) \notin R \]
+\[\tag{$\isWFseq$} \forall s : \nat \to A \exists k : \nat.\, \lnot \, R \,(s\,k)\,(s\,(k+1)) \]
 
@@
 Let $n$ be a $P_x$-minimal element.  Then $x \mstep n$.  Moreover, for any $y$,
-If $x \rstep y$, then $\lnot(P_x)$.  But since reductions from $x$ are closed downward,
+If $n \rstep y$, then $\lnot(P_x(y))$.  But since reductions from $x$ are closed downward,
 no such $y$ can exist, and hence $n$ is a normal form of $x$.

### 2025-07-11 Relations/Paper/Summer_2025_TODO.tex
reflecting  the agda standard library rewriting section

@@
 
+\section*{Agda standard library}
+\\ Some of the work we have explored is formalized in the Agda standard library.  
+% https://agda.github.io/agda-stdlib/v1.7.3/Relation.Binary.Rewriting.html#2096
+\begin{todolist}
+  \item Write about the standard library formalization in our paper and talk about how ours differs. 
+  \item Create an equivalences file showing that our formalization agrees with the ASL (specifically definitions such as confluet, wcr, nf, leading up to showing our formalizations of Newman's lemma agree).
+  \item Investigate contributing work to the ASL.
+This may mean refactoring the work already done to conform with the ASL.
+Specific contributions would likely be: Generalized NL.
+Theorem's 122 and 123.
+Alternative definitions of Wellfounded.
+\end{todolist}
+
 \end{document}

### 2025-07-21 Relations/Paper/Well-foundedness.tex
Updated typed lambda calculus code, also New outline of Section 5 in the ARS paper.

@@
 
+\newcommand{\accCor}{\textbf{accCor}}
+\newcommand{\accDNE}{\textbf{accDNE}}
+
 An abstract reduction $\to_R$ is strongly normalizing
@@
 In this section, we will compare several definitions of well-foundedness.
+
+\subsection{New version: Synopsis and Outline}
+
+Classically, well-foundedness can be defined in several equivalent but distinct ways:
+by induction, by absence of decreasing sequences, and by the fact that every
+subset has a minimal element.  Constructively, these are no longer equivalent.
+Moreover, even individual classical definitions can be given constructive
+interpretations in varying degrees of logical strength.
+
+For example, the implication from ``every non-empty subset has a minimal element'' to
+``every element is accessible"  is a classical proof by contradiction.
+(Assuming that there exists an inaccessible element, the hypothesis implies that
+there must be a minimal such element, which immediately yields a contradiction:
+every minimal element is accessible.)
+
+Constructively, this argument only goes so far as to show that, if every non-empty
+subset has a minimal element, then no element is inaccessible.
+That is, the universal statement being proved is that every $x \in A$
+is not-not-accessible. The final step needed to infer that $x$ is indeed accessible
+is not constructively provable in general, therefore it needs to be assumed as
+an additional hypothesis in order to recover the full implication.
+
+On the other hand, assuming accessibility is $\lnot\lnot$-closed, the other
+hypothesis can now be weakened, to only require existence of minimal elements
+for $\lnot\lnot$-closed subsets.  This is a significant restriction, which may
+be validated in many cases of interests.  In contrast, the original hypothesis
+is generally equivalent to every subset being decidable.
+(The file WFCounters.agda shows that assuming the full minimality hypothesis
+for the standard strict order on the natural numbers entails decidability
+of every subset of $\nat$, clearly incompatible with effective semantics.)
+
+One could also consider proving well-foundedness ``up to $\lnot\lnot$",
+asserting that every element is $\lnot\lnot$-accessible,
+every sequence $\lnot\lnot$-contains a non-decreasing index,
+for every non-empty subset there $\lnot\lnot$-exists a minimal element, etc.
+This cuts down some, but not all, of the complexity.
+For example, the two minimality principles
+described above are equivalent with this formulation.
+On the other hand, the implication from the sequential to inductive definition
+still requires an additional hypothesis, which may be described as the
+constructive contrapositive of the definition of accessibility.
+Specifically, we call {\accCor} the statement that, if an element $x$
+is \emph{not} accessible, then there (strongly) exists a $y$ with $Ryx$
+and $y$ not accessible.  Assuming \accCor, all notions of well-foundedness
+are constructively equivalent up to $\lnot\lnot$.
+
+As this discussion illustrates, the network of relationships between the
+constructive notions of well-foundedness is quite rich.  The purpose of
+this section is to present the basic picture of these implications,
+and elaborate on some of them.  Our key observations are summarized
+in the following list.
+\begin{enumerate}
+  \item The implication from the inductive to the sequential definition
+  requires the underlying relation to be decidable. This assumption is no longer
+  necessary on the $\lnot\lnot$-translated side.
+  \item WFmin is a very strong assumption and implies WFseq unconditionally.
+  The more reasonable WFminDNE requires Markov's Principle
+  (and decidability of $R$) to yield the same consequence.
+  \item On the $\lnot\lnot$-side, WFmin- and WFminDNE- are equivalent,
+  and imply WFacc- via WFseq-, requiring {\accCor} assumption in the final inference.
+  \item At the same time, if the relation is finitely branching, then WFminDNE-
+  implies WFacc- directly.
+  \item Finite branchingness together with (weak) decidability of minimality
+  implies \accCor.
+  % \apcomment{The previous observation suggests the question of whether isWFseq- might
+  % imply isWFminDNE- via decidability of minimal elements.\\
+  % However, in trying to prove this implication, the hypothesis asserting non-existence of
+  %  a minimal element of some given non-empty $\lnot\lnot$-closed predicate
+  %  automatically entails that any particular element of interest is not normal.\\
+  %  Unless it's not satisfying $P$? \emph{We need to decide whether it is P-minimal as well.}}
+  \item Assuming \accCor, isWFacc- can also be derived from a weaker condition, isWFminCor(-).
+  (Just like isWFminDNE is a natural weakening of isWFmin sufficient to recover isWFacc
+  when {\accDNE} is available.)
+  It is implied by isWFseq-, but does not appear to imply anything on its own.
+
+  \apcomment{(This seems easy: The converse implication isWFminCor to isWFseq- requires the sequence in question to
+  have decidable image, leading to a further weakening of isWFseq-.)}
+  \item Since isWFminDNE- implies isWFseq-, the former also implies isWFminCor-.
+  But the converse fails: If a subset/predicate $P$ is $\lnot\lnot$-closed,
+  we cannot conclude it is coreductive.
+
+  \item In general, the coreductive properties speak to the ability to choose
+  a successor (strong existence).  This ability is central to being able to
+  define sequences.  Therefore, sequential definitions generally require
+  some coreductive situation to be applicable.
+
+  \item Assuming normal forms are decidable,
+  isWFseq implies a very weak version of minimality, isWFminEM.
+  On its own this property is insufficient to imply anything else,
+  so we have nothing else to say about it.
+\end{enumerate}
 

### 2025-07-23 Relations/Paper/Well-foundedness.tex
WF edits

@@
 \newcommand{\accDNE}{\textbf{accDNE}}
+
+\apcomment{Well-foundedness or wellfoundedness?}
 
@@
 For example, the implication from ``every non-empty subset has a minimal element'' to
-``every element is accessible"  is a classical proof by contradiction.
+``every element is accessible''  is a classical proof by contradiction.
 (Assuming that there exists an inaccessible element, the hypothesis implies that
@@
 
-One could also consider proving well-foundedness ``up to $\lnot\lnot$",
+One could also consider proving well-foundedness ``up to $\lnot\lnot$'',
 asserting that every element is $\lnot\lnot$-accessible,
@@
 described above are equivalent with this formulation.
-On the other hand, the implication from the sequential to inductive definition
+% The implication from the inductive to sequential definition no longer requires
+% decidability of $R$.
+% On the other hand, the reverse
+At the same time, the
+implication from sequential to inductive wellfoundedness
 still requires an additional hypothesis, which may be described as the
@@
 is \emph{not} accessible, then there (strongly) exists a $y$ with $Ryx$
-and $y$ not accessible.  Assuming \accCor, all notions of well-foundedness
+and $y$ not accessible.  (In the context of rewriting systems,
+this condition asserts the existence of a function which maps any
+non-strongly normalizing element to a one-step reduct with the same property.)
+Assuming \accCor, all notions of well-foundedness
 are constructively equivalent up to $\lnot\lnot$.
@@
   \item Assuming \accCor, isWFacc- can also be derived from a weaker condition, isWFminCor(-).
-  (Just like isWFminDNE is a natural weakening of isWFmin sufficient to recover isWFacc
-  when {\accDNE} is available.)
+  (Just like isWFminDNE is a natural weakening of isWFmin that is sufficient to recover isWFacc
+  in the presence of {\accDNE}.)
   It is implied by isWFseq-, but does not appear to imply anything on its own.

### 2025-07-23 Relations/Paper/Formalization.tex

@@
     \item[($ii$)] This proof is inherently classical.
-In $\mathtt{iiSeq}$, we show that these properties imply $\isWFseqm$; establishing the implication to $\gSN$ would require additional classical assumptions.
+For the closest constructive analogue to this proof we have written $\mathtt{iiSeq}$, where we replace $\gBP$ with the stronger properties $\gWN$ and $\gUN$ and we replace $\gInc$ with the weaker property $\gRP$.
+    With the original property $\gBP$ and $gRP$ we can imply the related property $gSM$ ($\gSM$ is defined in Section~\ref{sec:Hierarchy} and its relation to $gSN$ is expanded upon).
 The definition and further discussion of $\isWFseqm$ are provided in Section~\ref{sec:Well-foundedness}.

### 2025-07-25 Relations/Paper/WF_diagram.tex
wf diagram update

@@
 % Row 2: WFind
-\node[box, below=of WFacc] (WFind) {WFind};
-\node[box, right=of WFind] (NNWFind) {$\lnot\lnot$WFind};
-\node[box, right=of NNWFind] (WFindM) {WFind-};
+% \node[box, below=of WFacc] (WFind) {WFind};
+% \node[box, right=of WFind] (NNWFind) {$\lnot\lnot$WFind};
+% \node[box, right=of NNWFind] (WFindM) {WFind-};
 
-\draw[arrow] (WFind) -- (NNWFind);
-\draw[arrow] (NNWFind) -- (WFindM);
+% \draw[arrow] (WFind) -- (NNWFind);
+% \draw[arrow] (NNWFind) -- (WFindM);
 
 % Row 3: WFseq
-\node[box, below=of WFind] (WFseq) {WFseq};
+\node[box, below=of WFacc] (WFseq) {WFseq};
 \node[box, right=of WFseq] (NNWFseq) {$\lnot\lnot$WFseq};
@@
 % Arrows between rows
-\draw[arrow, <->] (WFacc) -- (WFind);
-\draw[arrow, <->] (NNWFacc) -- (NNWFind);
-\draw[arrow, <->] (WFaccM) -- (WFindM);
+% \draw[arrow, <->] (WFacc) -- (WFind);
+% \draw[arrow, <->] (NNWFacc) -- (NNWFind);
+% \draw[arrow, <->] (WFaccM) -- (WFindM);
 
-\draw[arrow] (WFind) to node[right, text = red] {Rdec} (WFseq);
-\draw[arrow, bend left] (WFindM) to (WFseqM);
-\draw[arrow, bend left] (WFseqM) to node[left, text=red] {accCor} (WFindM);  
-\draw[arrow, bend left = 45] (WFindM) to (WFminM);
+\draw[arrow] (WFacc) to node[right, text = red] {Rdec} (WFseq);
+\draw[arrow, bend left] (WFaccM) to (WFseqM);
+\draw[arrow, bend left] (WFseqM) to node[left, text=red] {accCor} (WFaccM);  
+\draw[arrow, bend left = 45] (WFaccM) to (WFminM);
 
@@
 
-\draw[arrow, bend left=60] (WFminDNE) to node[left, text = red] {accDNE} (WFacc);
+\draw[arrow, bend left=90] (WFminDNE) to node[left, text = red] {accDNE} (WFacc);
 \draw[arrow, bend left=45] (WFminDNE) to node[pos=0.9, left, text=red] {Rdec$+$MP} (WFseq);

### 2025-07-25 Relations/Paper/Well-foundedness.tex
wf diagram update
Well-founded work in progress update

@@
 
-\apcomment{Well-foundedness or wellfoundedness?}
+% We use Well-founded not Wellfounded
 
@@
 if and only if the converse relation is well-founded.
-In this section, we will compare several definitions of well-foundedness.
+In this section, we will compare several definitions of well-foundedness, which depend on the following properties.
+\begin{definition}
+  Let $R \subseteq A \times A$.  We write $Rxy$ when $(x,y) \in R$.
+  \begin{enumerate}
+    \item $P \subseteq A$ is \emph{inductive}
+    if, for each $x \in A$, $(\forall y. Ryx \to y \in P)$ implies $x \in P$.
 
+    \item $x \in A$ is \emph{accessible} if $x \in P$ for each inductive $P$.
+
+    \item $x \in A$ is \emph{$P$-minimal} if $x \in P$ and for all $y$,
+    $Ryx$ implies $y \notin P$.
+
+    \item $s : \nat \to A$ is \emph{$R$-decreasing} if for all $k$, $(s(k+1),s(k)) \in R$.
+  \end{enumerate}
+\end{definition}
+\apcomment{Add the definitions of well-foundedness here and then continue with the text as below.}
 \subsection{New version: Synopsis and Outline}
 
-Classically, well-foundedness can be defined in several equivalent but distinct ways:
-by induction, by absence of decreasing sequences, and by the fact that every
-subset has a minimal element.  Constructively, these are no longer equivalent.
+Classically, the above notions of well-foundedness are all equivalent.
+Constructively, only the first two are equivalent; the remaining definitions are not.
 Moreover, even individual classical definitions can be given constructive
@@
 \end{enumerate}
-
-\subsection{The main definitions}
-
-The various formulations of well-foundedness are based on the following notions.
-\begin{definition}
-  Let $R \subseteq A \times A$.  We write $Rxy$ when $(x,y) \in R$.
-  \begin{enumerate}
-    \item $P \subseteq A$ is \emph{inductive}
-    if, for each $x \in A$, $(\forall y. Ryx \to y \in P)$ implies $x \in P$.
-
-    \item $x \in A$ is \emph{accessible} if $x \in P$ for each inductive $P$.
-
-    \item $x \in A$ is \emph{$P$-minimal} if $x \in P$ and for all $y$,
-    $Ryx$ implies $y \notin P$.
-
-    \item $s : \nat \to A$ is \emph{$R$-decreasing} if for all $k$, $(s(k+1),s(k)) \in R$.
-  \end{enumerate}
-\end{definition}
 

### 2025-08-06 Relations/Paper/WF_table.tex
Minor paper changes + new WF table

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{array}
\usepackage{caption}
\usepackage{graphicx}  % <--- For \resizebox

\geometry{margin=1in}

\begin{document}

\begin{table}[h!]
\centering
\caption{Relational Table of Properties. Read along row and not down column. Note: Not determined whether being local or global makes an impact on the table.}
\renewcommand{\arraystretch}{1.3}
\resizebox{\textwidth}{!}{ % <--- This line scales the table
\begin{tabular}{|l|l|l|l|l|l|l|l|l|l|l|}
\hline
 & WFacc & WFseq & WFmin & WFminDN & WFacc- & WFseq- & WFmin- & WFminDNE & WFmincor \\
\hline
WFacc     & - & Rdec & ? & ? & - & - & - & - & - \\
\hline
WFseq     & ? & - & ? & ? & accCor & - & accCor & accCor & - \\
\hline
WFmin     & {accDNE} & - & - & ? & FB or accCor & - & accCor & accCor & - \\
\hline
WFminDN   & {accDNE} & Rdec + MP & ? & - & accDNE or & - & - & - & - \\
\hline
WFacc-    & {accDNE} & accDNE + Rdec & ? & - & - & - & - & - & - \\
\hline
WFseq-    & accCor + {accDNE} & accCor + accDNE + Rdec & ? & ? & accCor & - & accCor & accCor & - \\
\hline
WFmin-    & (accCor or FB) + {accDNE} & (accCor or FB) + accDNE + Rdec & ? & ? & accCor or & - & - & - & - \\
\hline
WFminDN   & (accCor or FB) + {accDNE} & (accCor or FB) + accDNE + Rdec & ? & ? & accCor or & - & - & - & - \\
\hline
WFminCor  & ? & ? & ? & ? & ? & ? & ? & ? & - \\
\hline
\end{tabular}
} % <--- End resizebox
\end{table}

\end{document}

### 2025-08-06 Relations/Paper/WF_table.tex
Table improvements

@@
 \hline
- & WFacc & WFseq & WFmin & WFminDN & WFacc- & WFseq- & WFmin- & WFminDNE & WFmincor \\
+ & WFacc & WFseq & WFmin & WFminDNE& WFacc- & WFseq- & WFmin- & WFminDNE & WFminCor \\
 \hline
@@
 \hline
-WFseq     & ? & - & ? & ? & accCor & - & accCor & accCor & - \\
+WFseq     & accCor + accDNE & - & ? & ? & accCor & - & accCor & accCor & - \\
 \hline
-WFmin     & {accDNE} & - & - & ? & FB or accCor & - & accCor & accCor & - \\
+WFmin     & {accDNE} & - & - & - & FB or accCor & - & accCor & accCor & - \\
 \hline
-WFminDN   & {accDNE} & Rdec + MP & ? & - & accDNE or & - & - & - & - \\
+WFminDNE  & {accDNE} & Rdec + MP & ? & - & accDNE or & - & - & - & - \\
 \hline
@@
 \hline
-WFminDN   & (accCor or FB) + {accDNE} & (accCor or FB) + accDNE + Rdec & ? & ? & accCor or & - & - & - & - \\
+WFminDNE-  & (accCor or FB) + {accDNE} & (accCor or FB) + accDNE + Rdec & ? & ? & accCor or & - & - & - & - \\
 \hline

### 2025-08-06 Relations/Paper/WF_diagram.tex
Diagram WFminCor WIP
WF diagram update

@@
 \node[box] (WFacc) {WFacc};
-\node[box, right=of WFacc] (NNWFacc) {$\lnot\lnot$WFacc};
-\node[box, right=of NNWFacc] (WFaccM) {WFacc-};
+% \node[box, right=of WFacc] (NNWFacc) {$\lnot\lnot$WFacc};
+\node[box, right=2.9cm of WFacc] (WFaccM) {WFacc-};
 
-\draw[arrow] (WFacc) -- (NNWFacc);
-\draw[arrow] (NNWFacc) -- (WFaccM);
+\draw[arrow] (WFacc) -- (WFaccM);
+% \draw[arrow] (NNWFacc) -- (WFaccM);
 \draw[arrow, bend right] (WFaccM) to node[above, text=red] {accDNE} (WFacc);
@@
 
-% Row 3: WFseq
-\node[box, below=of WFacc] (WFseq) {WFseq};
-\node[box, right=of WFseq] (NNWFseq) {$\lnot\lnot$WFseq};
-\node[box, right=of NNWFseq] (WFseqM) {WFseq-};
+% \draw[arrow] (NNWFseq) -- (WFseqM);
 
-\draw[arrow] (WFseq) -- (NNWFseq);
-\draw[arrow] (NNWFseq) -- (WFseqM);
+% Row 5: WFminDNE -> WFminDNE-
+\node[box, below=of WFacc] (WFminDNE) {WFminDNE};
+\node[box, right=2.0cm of WFminDNE] (WFminDNEM) {WFminDNE-};
+
+\draw[arrow] (WFminDNE) -- (WFminDNEM);
 
 % Row 4: WFmin -> WFmin-
-\node[box, below=of WFseq] (WFmin) {WFmin};
+\node[box, below=of WFminDNE] (WFmin) {WFmin};
 \node[box, right=2.8cm of WFmin] (WFminM) {WFmin-};
@@
 
-% Row 5: WFminDNE -> WFminDNE-
-\node[box, below=of WFmin] (WFminDNE) {WFminDNE};
-\node[box, right=2.1cm of WFminDNE] (WFminDNEM) {WFminDNE-};
+% Row 3: WFseq
+\node[box, below=of WFmin] (WFseq) {WFseq};
+% \node[box, right=of WFseq] (NNWFseq) {$\lnot\lnot$WFseq};
+\node[box, right=2.9cm of WFseq] (WFseqM) {WFseq-};
 
-\draw[arrow] (WFminDNE) -- (WFminDNEM);
+\draw[arrow] (WFseq) -- (WFseqM);
+
+% Row 6: WFcor 
+\node[box, below=of WFseqM] (WFminCor) {WFminCor};
 
@@
 
-\draw[arrow] (WFacc) to node[right, text = red] {Rdec} (WFseq);
-\draw[arrow, bend left] (WFaccM) to (WFseqM);
-\draw[arrow, bend left] (WFseqM) to node[left, text=red] {accCor} (WFaccM);  
-\draw[arrow, bend left = 45] (WFaccM) to (WFminM);
+\draw[arrow, bend right = 90] (WFacc) to node[left, text = red] {Rdec} (WFseq);
+\draw[arrow, bend right] (WFaccM) to (WFminDNEM);
+\draw[arrow, bend right = 90] (WFseqM) to node[right, text=red] {accCor} (WFaccM);  
+% \draw[arrow, bend left = 55] (WFaccM) to (WFminM);
 
@@
 
-\draw[arrow, bend left=90] (WFminDNE) to node[left, text = red] {accDNE} (WFacc);
-\draw[arrow, bend left=45] (WFminDNE) to node[pos=0.9, left, text=red] {Rdec$+$MP} (WFseq);
-\draw[arrow, bend right=45] (WFminDNEM) to node[right, text=red] {FB} (WFaccM);
+\draw[arrow] (WFminDNE) to node[left, text = red] {accDNE} (WFacc);
+\draw[arrow, bend right=45] (WFminDNE) to node[pos=0.5, left, text=red] {MP$\equiv$} (WFseq);
+\draw[arrow, bend right] (WFminDNEM) to node[right, text=red] {FB} (WFaccM);
+\draw[arrow, bend right] (WFseqM) to (WFminCor);
+\draw[arrow, bend right] (WFminCor) to node [right, text=red] {MP$\equiv$} (WFseqM);
 

### 2025-08-14 QADT/notes.tex
QADT notes and open problems
new entry in QADT notes

@@
 \usepackage{amssymb}
+\usepackage[dvipsnames]{xcolor}
 
@@
 
+\newcommand{\hired}[1]{\textcolor{Red}{#1}}
 \begin{document}
+
+\section*{2025.08.14}
+
+Looked at the equation $1 + X = X + X^2$.
+Ben presented a method for deriving an ADT solution to this equation.
+The following points came up during the discussion.
+\begin{itemize}
+  \item The answer matches up with the polynomial obtained by the trick
+  $X := Z + 2$; this should be explained.
+  \item Similarly, for any adt with roots $p$ and $-q$, we can
+  write $F(x) = x + (x+1)(x+(q+p+1))$, then $\mu F + (p+1)$ gives those roots.
+  \item Adding two \emph{linear} ADTs corresponds to adding their roots.
+  \item How does the sum/product of two \emph{general} ADTs influence their
+  roots?
+  \item What is the general method for treating a ``difference'' of two
+  ADTs $P(x) - Q(x)$, as an ADT in its own right?
+  \item \hired{AP:} The trick of adding \emph{positive integers} to ADT
+  seems to work for specific roots, specifically it should work for all real roots.
+
+  How do we treat roots that have a complex component to them?
+\end{itemize}
+
+\section*{2025.07.22}
+\begin{itemize}
+  \item Theorem giving sufficient condition for surjectivity of the fold
+  (from the initial algebra of a functor to any other fixed point of it)
+  in terms of the image of its composite with the map to the final coalgebra.
+
+\end{itemize}
 

### 2025-08-20 Relations/Paper/Well-foundedness.tex
minor comment for future edit
Minor paper changes + new WF table
WFdefinitions added (First pass)

@@
 if and only if the converse relation is well-founded.
-In this section, we will compare several definitions of well-foundedness, which depend on the following properties.
+In this section, we will compare several definitions of well-foundedness, which depend on the following properties. \apcomment{Want to say something like: "Relating properties of a relation R"}
 \begin{definition}
@@
     \item $s : \nat \to A$ is \emph{$R$-decreasing} if for all $k$, $(s(k+1),s(k)) \in R$.
+
+    \item $P \subseteq A$ is \emph{coreductive} if, for each $x \in A$, $x \notin P$ implies $\exists y \in A$ such that $Ryx$ and $y \notin P$. 
   \end{enumerate}
 \end{definition}
+The definition of a $R$-decreasing sequence is repeated from Section~\ref{sec:Definitions}, as it is used extensively in this section.
+
 \apcomment{Add the definitions of well-foundedness here and then continue with the text as below.}
+\sacomment{Do we want local or global definitions here?}
+\begin{definition}
+  Let $R \subseteq A \times A$. We write $Rxy$ when $(x,y) \in R$.
+  \begin{enumerate}
+    \item $R$ is \emph{accessibly well-founded} ($\WFacc$) if every element is accessible:
+      \[
+        \forall x \in A.\; x \text{ is accessible}.
+      \]
+    \item $R$ is \emph{inductively well-founded} ($\WFind$) if every inductive $P \subseteq A$ is universal:
+      \[
+        \forall P \subseteq A.\;(\text{$P$ is inductive}) \Rightarrow \forall x \in A.\; x \in P.
+      \]
+    \item $R$ is \emph{sequentially well-founded} ($\WFseq$) if every sequence contains an index at which it is not decreasing:
+      \[
+        \forall s : \nat \to A \exists k : \nat.\, \lnot \, R \,(s\,k)\,(s\,(k+1)).
+      \]
+    \item  $R$ is \emph{minimally well-founded} ($\WFmin$) if every nonempty subset has a $P$-minimal element:
+      \[
+        \forall P \subseteq A.\; P \neq \varnothing \Rightarrow
+        \exists x \in P.\; \text{$x$ is $P$-minimal}.
+      \]
+    \item  $R$ is \emph{minimally well-founded under double negation elimination} ($\WFminDNE$) if every nonempty $\lnot \lnot$-closed subset contains a $P$-minimal element:
+      \[
+        \forall P \subseteq A.\; P \neq \varnothing \Rightarrow (\lnot \lnot P \Rightarrow P) \Rightarrow
+        \exists x \in P.\; \text{$x$ is $P$-minimal}.
+      \]
+    \item $R$ is \emph{coreductively well-founded} ($\WFcor$) if every coreductive $P \subseteq A$ is universal:
+
+      \[
+        \forall P \subseteq A.\;(\text{$P$ is coreductive}) \Rightarrow \forall x \in A.\; x \in P.
+      \]
+
+  \end{enumerate}
+\end{definition}
+We have formalized the above definitions of well-foundedness in \texttt{WFDefinitions.agda}.
+
+To explore how these definitions interrelate it helps to consider the following corresponding weaker definitions (which are formalized in \texttt{WFWeakDefinitions}).
+
+\begin{definition}
+  Let $R \subseteq A \times A$. We write $Rxy$ when $(x,y) \in R$.
+  \begin{enumerate}
+    \item $R$ is \emph{weakly accessibly well-founded} ($\WFaccm$) if accessibility holds up to double negation:
+      \[
+        \forall x \in A.\; \lnot \lnot  (x \text{ is accessible}).
+      \]
+    \item $R$ is \emph{weakly inductively well-founded} ($\WFindm$) if every inductive predicate holds for all elements up to double negation:
+      \[
+        \forall P \subseteq A.\;(\text{$P$ is inductive}) \Rightarrow \forall x \in A.\; \lnot \lnot (x \in P).
+      \]
+    \item $R$ is \emph{weakly sequentially well-founded} ($\WFseqm$) if no sequence is $R$-decreasing:
+      \[
+        \forall s:\nat \to A.\; \lnot \text{($s$ is $R$-decreasing)}.
+      \]
+    \item  $R$ is \emph{weakly minimally well-founded} ($\WFmin$) if every nonempty subset contains a $\lnot \lnot P$-minimal element:
+      \[
+        \forall P \subseteq A.\; P \neq \varnothing \Rightarrow \lnot \lnot \;
+        (\exists x \in P.\; \text{$x$ is $P$-minimal}).
+      \]
+    \item  $R$ is \emph{weakly minimally well-founded under double negation elimination} ($\WFminDNE$) if every nonempty $\lnot \lnot$-closed subset $\lnot \lnot$ contains a $P$-minimal element:
+      \[
+        \forall P \subseteq A.\; P \neq \varnothing \Rightarrow (\lnot \lnot P \Rightarrow P) \Rightarrow \lnot \lnot \;
+        (\exists x \in P.\; \text{$x$ is $P$-minimal}).
+      \]      
+  \end{enumerate}
+\end{definition}
+
+In \cite{Terese}, the $WFseqm$ definition is used, as in the classical mathematics textbooks. 
 \subsection{New version: Synopsis and Outline}

### 2025-08-20 Relations/Paper/Summer_2025_TODO.tex
bugfix newline
New todo items
Progress in WF section. Work to be done.

@@
 \section*{Agda standard library}
-\\ Some of the work we have explored is formalized in the Agda standard library.  
+Some of the work we have explored is formalized in the Agda standard library.  
 % https://agda.github.io/agda-stdlib/v1.7.3/Relation.Binary.Rewriting.html#2096
@@
 Theorem's 122 and 123.
-Alternative definitions of Wellfounded.
+Alternative definitions of Wellfounded, the implications for the hierarchy.
+\end{todolist}
+
+\section*{20th August todos}
+\begin{todolist}
+  \item (Secondary) Find consistency with NP and UN with respect to reduction and conversion. Should the default be by reduction for both. Should we be explicit with $\to$ and = in each case. 
+  \item Carry on modifying the names of wfXXX- to wfXXXnotnot with prefix underscore in agda and in latex.
+  \item Make a decision regarding WFcor. We use it to imply WFacc using AccCor. But otherwise it is sort of orphaned off. Does it help contribute to the overall story?
 \end{todolist}

### 2025-08-20 Relations/Paper/Well-foundedness.tex
Progress in WF section. Work to be done.

--- 2025-07-25 Relations/Paper/Well-foundedness.tex
@@
 if and only if the converse relation is well-founded.
-In this section, we will compare several definitions of well-foundedness, which depend on the following properties.
-\begin{definition}
+In this section, we will compare several definitions of well-foundedness, which depend on the properties in Defintion~\ref{def:WFproperties} below.
+
+For $P \subseteq A$, let $\ol{P} = \{ x \in A \mid x \notin P\}$ denote the complement of $P$.
+\begin{definition}\label{def:WFproperties}
   Let $R \subseteq A \times A$.  We write $Rxy$ when $(x,y) \in R$.
@@
 
+    \item $P \subseteq A$ is \emph{coreductive} if, for each $x \in \ol{P}$, there is a $y \in A$ such that $Ryx$ and $y \in \ol{P}$.
+
     \item $s : \nat \to A$ is \emph{$R$-decreasing} if for all $k$, $(s(k+1),s(k)) \in R$. 
@@
 \end{definition}
-\apcomment{Add the definitions of well-foundedness here and then continue with the text as below.}
-\subsection{New version: Synopsis and Outline}
+The definition of a $R$-decreasing sequence is repeated from Section~\ref{sec:Definitions}, as it is used extensively in this section.
+
+\begin{definition}
+  Let $R \subseteq A \times A$. We write $Rxy$ when $(x,y) \in R$.
+  \begin{enumerate}
+    \item $R$ is \emph{accessibly well-founded} ($\WFacc$) if every element is accessible:
+      \[
+        \forall x \in A.\; x \text{ is accessible}.
+      \]
+    \item $R$ is \emph{inductively well-founded} ($\WFind$) if every inductive $P \subseteq A$ is universally true:
+      \[
+        \forall P \subseteq A.\;\text{$P$ is inductive} \Rightarrow \forall x \in A.\; x \in P.
+      \]
+    \item $R$ is \emph{sequentially well-founded} ($\WFseq$) if every sequence contains an index at which it is not decreasing:
+      \[
+        \forall s : \nat \to A \exists k : \nat.\, \lnot \, R \,(s\,k)\,(s\,(k+1)).
+      \]
+    \item  $R$ is \emph{minimally well-founded} ($\WFmin$) if every nonempty subset has a $P$-minimal element:
+      \[
+        \forall P \subseteq A.\; P \neq \varnothing \Rightarrow
+        \exists x \in P.\; \text{$x$ is $P$-minimal}.
+      \]
+    \item  $R$ is \emph{minimally well-founded for $\lnot \lnot$-closed predicates} ($\WFminDNE$) if every nonempty $\lnot \lnot$-closed subset contains a $P$-minimal element:
+      \[
+        \forall P \subseteq A.\; P \neq \varnothing \Rightarrow \left(\ol{\ol P} \subseteq P\right) \Rightarrow
+        \exists x \in P.\; \text{$x$ is $P$-minimal}.
+      \]
+    \item $R$ is \emph{coreductively well-founded} ($\WFcor$) if every coreductive $P \subseteq A$ is universally true:
+      \[
+        \forall P \subseteq A.\;(\text{$P$ is coreductive}) \Rightarrow \forall x \in A.\; x \in P.
+      \]
+
+  \end{enumerate}
+\end{definition}
+We have formalized the above definitions of well-foundedness in \texttt{WFDefinitions.agda}.
 
@@
 every sequence $\lnot\lnot$-contains a non-decreasing index,
-for every non-empty subset there $\lnot\lnot$-exists a minimal element, etc.
+for every non-empty subset there $\lnot\lnot$-exists a minimal element, etc. These are formalized in the definition below (and in \texttt{WFWeakDefinitions.agda}).
+
+\begin{definition}
+  Let $R \subseteq A \times A$. We write $Rxy$ when $(x,y) \in R$.
+  \begin{enumerate}
+    \item $R$ is \emph{weakly accessibly well-founded} ($\WFaccm$) if accessibility holds up to double negation:
+      \[
+        \forall x \in A.\; \lnot \lnot  (x \text{ is accessible}).
+      \]
+    \item $R$ is \emph{weakly inductively well-founded} ($\WFindm$) if every inductive predicate holds for all elements up to double negation:
+      \[
+        \forall P \subseteq A.\;(\text{$P$ is inductive}) \Rightarrow \forall x \in A.\; \lnot \lnot (x \in P).
+      \]
+    \item $R$ is \emph{weakly sequentially well-founded} ($\WFseqm$) if no sequence is $R$-decreasing:
+      \[
+        \forall s:\nat \to A.\; \lnot \text{($s$ is $R$-decreasing)}.
+      \]
+    \item  $R$ is \emph{weakly minimally well-founded} ($\WFminm$) if every nonempty subset contains a $\lnot \lnot P$-minimal element:
+      \[
+        \forall P \subseteq A.\; P \neq \varnothing \Rightarrow \lnot \lnot \;
+        (\exists x \in P.\; \text{$x$ is $P$-minimal}).
+      \]
+    \item  $R$ is \emph{weakly minimally well-founded under double negation elimination} ($\WFminDNEm$) if every nonempty $\lnot \lnot$-closed subset $\lnot \lnot$ contains a $P$-minimal element:
+      \[
+        \forall P \subseteq A.\; P \neq \varnothing \Rightarrow \left(\ol{\ol P} \subseteq P\right) \Rightarrow \lnot \lnot \;
+        (\exists x \in P.\; \text{$x$ is $P$-minimal}).
+      \]      
+  \end{enumerate}
+\end{definition}
+
+\begin{figure}[ht]
+\centering  
+\begin{tikzpicture}[
+  node distance=1cm and .5cm,
+  box/.style={draw, rectangle, rounded corners, minimum width=1cm, minimum height=1cm, align=center},
+  arrow/.style={-{Latex}, thick}
+]
+
+% Row 1: WFacc
+\node[box] (WFacc) {WFacc};
+% \node[box, right=of WFacc] (NNWFacc) {$\lnot\lnot$WFacc};
+\node[box, right=2.9cm of WFacc] (WFaccM) {WFacc-};
+
+\draw[arrow] (WFacc) -- (WFaccM);
+% \draw[arrow] (NNWFacc) -- (WFaccM);
+\draw[arrow, bend right] (WFaccM) to node[above, text=red] {accDNE} (WFacc);
+
+% Row 2: WFind
+% \node[box, below=of WFacc] (WFind) {WFind};
+% \node[box, right=of WFind] (NNWFind) {$\lnot\lnot$WFind};
+% \node[box, right=of NNWFind] (WFindM) {WFind-};
+
+% \draw[arrow] (WFind) -- (NNWFind);
+% \draw[arrow] (NNWFind) -- (WFindM);
+
+% \draw[arrow] (NNWFseq) -- (WFseqM);
+
+% Row 5: WFminDNE -> WFminDNE-
+\node[box, below=of WFacc] (WFminDNE) {WFminDNE};
+\node[box, right=2.0cm of WFminDNE] (WFminDNEM) {WFminDNE-};
+
+\draw[arrow] (WFminDNE) -- (WFminDNEM);
+
+% Row 4: WFmin -> WFmin-
+\node[box, below=of WFminDNE] (WFmin) {WFmin};
+\node[box, right=2.8cm of WFmin] (WFminM) {WFmin-};
+
+\draw[arrow] (WFmin) -- (WFminM);
+
+% Row 3: WFseq
+\node[box, below=of WFmin] (WFseq) {WFseq};
+% \node[box, right=of WFseq] (NNWFseq) {$\lnot\lnot$WFseq};
+\node[box, right=2.9cm of WFseq] (WFseqM) {WFseq-};
+
+\draw[arrow] (WFseq) -- (WFseqM);
+
+% Row 6: WFcor 
+\node[box, below=of WFseqM] (WFminCor) {WFminCor};
+
+% Arrows between rows
+% \draw[arrow, <->] (WFacc) -- (WFind);
+% \draw[arrow, <->] (NNWFacc) -- (NNWFind);
+% \draw[arrow, <->] (WFaccM) -- (WFindM);
+
+\draw[arrow, bend right = 90] (WFacc) to node[left, text = red] {Rdec} (WFseq);
+\draw[arrow, bend right] (WFaccM) to (WFminDNEM);
+\draw[arrow, bend right = 90] (WFseqM) to node[right, text=red] {accCor} (WFaccM);  
+% \draw[arrow, bend left = 55] (WFaccM) to (WFminM);
+
+\draw[arrow] (WFmin) -- (WFseq);
+\draw[arrow] (WFminM) -- (WFseqM);
+\draw[arrow] (WFmin) -- (WFminDNE);
+\draw[arrow, <->] (WFminM) -- (WFminDNEM);
+
+\draw[arrow] (WFminDNE) to node[left, text = red] {accDNE} (WFacc);
+\draw[arrow, bend right=45] (WFminDNE) to node[pos=0.5, left, text=red] {MP$\equiv$} (WFseq);
+\draw[arrow, bend right] (WFminDNEM) to node[right, text=red] {FB} (WFaccM);
+\draw[arrow, bend right] (WFseqM) to (WFminCor);
+\draw[arrow, bend right] (WFminCor) to node [right, text=red] {MP$\equiv$} (WFseqM);
+
+\end{tikzpicture}
+\caption{The logical relationships between notions of well-foundedness}
+ \label{fig:WF} 
+\end{figure}
+\clearpage
+
+In \cite{Terese}, the $\WFseqm$ definition is used, as in the classical mathematics textbooks.
+
+To explore how these definitions interrelate it helps to consider the following corresponding weaker definitions (which are formalized in \texttt{WFWeakDefinitions.agda}). 
+The weaker definitions help us to explore how the standard well-founded definitions interrelate. This is made clear in the following diagram.
+
+\subsection{New version: Synopsis and Outline} 
 This cuts down some, but not all, of the complexity.

### 2025-08-26 Relations/Paper/Summer_2025_TODO.tex
Changes from last meeting and minor edits.

@@
 \begin{todolist}
-  \item (Secondary) Find consistency with NP and UN with respect to reduction and conversion. Should the default be by reduction for both. Should we be explicit with $\to$ and = in each case. 
+  \item (Secondary) Find consistency with NP and UN with respect to reduction and conversion.
+Should the default be by reduction for both.
+Should we be explicit with $\to$ and = in each case.
+\sacomment{Main issue here is that we'll either introduce an inconsistency with our code or we'll have a hard to read symbol.
+We can do $\to$ as super or sub-script in Agda.
+If we're happy with $NP\to$ in agda but using a different script in the paper then I think we should go ahead and be explicit for both UN and NP as to whether it is WRT conversion or reduction.
+We already have this inconsistency in the code with $UN\to$}
   \item Carry on modifying the names of wfXXX- to wfXXXnotnot with prefix underscore in agda and in latex.
-  \item Make a decision regarding WFcor. We use it to imply WFacc using AccCor. But otherwise it is sort of orphaned off. Does it help contribute to the overall story?
+\sacomment{Done with the exception of WFseq-.
+This needs a bit more thought.
+Similarly for the relation between WFcor and WFminCor.}
+  \item Make a decision regarding WFcor.
+We use it to imply WFacc using AccCor.
+But otherwise it is sort of orphaned off.
+Does it help contribute to the overall story?
+\sacomment{We've now related it to WFmin by requiring that correductive predicates have double negation elimination.
+Is this too strong a requirement?
+Similarly we have linked WFacc to WFcor but this proof requires the same property as well as limiting ourselves to accessible predicates.
+Again, is this too much?}
+  \item Get the classical hypothesis and relations organized and see how they're used in the implications (organize implications by classical requirement.
+In the implications file we can import the classical implications.
+Basically, refactor the code.) \sacomment{Done but could be further refactored.}
+  \item Make a cheat sheet for the next meeting regarding to talk about coreductive.
+How it relates on the weak side and on the strong side.
+SEQ seq+- , how to present these.
+Try and clarify what the issues are here and what exactly are the differences between them in terms of definition and implication.
+Could one be removed and the overall story stay the same?
+\sacomment{Regarding seq+ (and seq+-) we currently only show that seq+ implies seq and seq+- implies seq- so could be removed without changing any of our other implictions.}
 \end{todolist}

### 2025-08-26 Relations/Paper/Well-foundedness.tex
Changes from last meeting and minor edits.

@@
 % Row 1: WFacc
-\node[box] (WFacc) {WFacc};
+\node[box] (WFacc) {$WFacc$};
 % \node[box, right=of WFacc] (NNWFacc) {$\lnot\lnot$WFacc};
-\node[box, right=2.9cm of WFacc] (WFaccM) {WFacc-};
+\node[box, right=2.9cm of WFacc] (WFaccM) {$WFacc\lnot\lnot$};
 
@@
 % Row 5: WFminDNE -> WFminDNE-
-\node[box, below=of WFacc] (WFminDNE) {WFminDNE};
-\node[box, right=2.0cm of WFminDNE] (WFminDNEM) {WFminDNE-};
+\node[box, below=of WFacc] (WFminDNE) {$WFminDNE$};
+\node[box, right=2.0cm of WFminDNE] (WFminDNEM) {$WFminDNE\lnot\lnot$};
 
@@
 % Row 4: WFmin -> WFmin-
-\node[box, below=of WFminDNE] (WFmin) {WFmin};
-\node[box, right=2.8cm of WFmin] (WFminM) {WFmin-};
+\node[box, below=of WFminDNE] (WFmin) {$WFmin$};
+\node[box, right=2.8cm of WFmin] (WFminM) {$WFmin\lnot\lnot$};
 
@@
 % Row 3: WFseq
-\node[box, below=of WFmin] (WFseq) {WFseq};
+\node[box, below=of WFmin] (WFseq) {$WFseq$};
 % \node[box, right=of WFseq] (NNWFseq) {$\lnot\lnot$WFseq};
-\node[box, right=2.9cm of WFseq] (WFseqM) {WFseq-};
+\node[box, right=2.9cm of WFseq] (WFseqM) {$WFseq-$};
 
@@
 % Row 6: WFcor 
-\node[box, below=of WFseqM] (WFminCor) {WFminCor};
+\node[box, below=of WFseq] (WFCor) {$WFCor$};
+\node[box, below=of WFseqM] (WFminCor) {$WFminCor$};
 
@@
 
-\draw[arrow, bend right = 90] (WFacc) to node[left, text = red] {Rdec} (WFseq);
+\draw[arrow, bend right = 90] (WFacc) to node[pos = 0.75,left, text = red] {Rdec} (WFseq);
 \draw[arrow, bend right] (WFaccM) to (WFminDNEM);
@@
 \draw[arrow, bend right] (WFminCor) to node [right, text=red] {MP$\equiv$} (WFseqM);
+\draw[arrow] (WFCor) -- (WFminCor);
+\draw[arrow, bend left = 110] (WFCor) to node[left, text=red] {AccCor} (WFacc);
 

### 2025-09-05 Relations/Paper/Definitions.tex
Changes made on meeting 8th July
Symbol changes reflected in todo list

@@
         \item[\ule{$a \in \NPe_R$}] \emph{$a$ has the conversion normal form property} if for all $b \in \NF_R$, \[ a \estep b \implies a\mstep b\]
-        \item[\ule{$a \in \NP_R$}] \emph{$a$ has the normal form property} if for all $b \in \NF_R$,
+        \item[\ule{$a \in \NP_R$}] \emph{$a$ has the reduction normal form property} if for all $b \in \NF_R$,
         \[c \bmstep a \mstep b \implies c \mstep b\]
-        \item[\ule{$a \in \UN_R$}] \emph{$a$ has the unique normal form property} if for all $a, b \in \NF_R$, \[a \estep b \implies a \equiv b\]
-        \item[\ule{$a \in \UNto_R$}] \emph{$a$ has the unique normal form property with respect to reduction} if for all $b, c \in \NF_R$,
+        \item[\ule{$a \in \UN_R$}] \emph{$a$ has the conversion unique normal form property} if for all $a, b \in \NF_R$, \[a \estep b \implies a \equiv b\]
+        \item[\ule{$a \in \UNto_R$}] \emph{$a$ has the reduction unique normal form property} if for all $b, c \in \NF_R$,
         \[c \bmstep a \mstep b  \implies b \equiv c\]
@@
 
-In \terese, $\mathrm{\,Ind}$ is used to denote $\gBP$.
+The property $\gBP$ is equivalent to the property called $\mathrm{\,Ind}$ in \terese.
+(Specifically, $\mathrm{\,Ind}$ asserts the exists of a bound for finite sequences as well, but that is automatic, since the last term of a finite reduction sequence is a bound for that sequence.)
 

### 2025-09-05 Relations/Paper/Summer_2025_TODO.tex
Symbol changes reflected in todo list

@@
 \begin{todolist}
-  \item (Secondary) Find consistency with NP and UN with respect to reduction and conversion.
+  \item [\done] (Secondary) Find consistency with NP and UN with respect to reduction and conversion.
 Should the default be by reduction for both.
@@
 If we're happy with $NP\to$ in agda but using a different script in the paper then I think we should go ahead and be explicit for both UN and NP as to whether it is WRT conversion or reduction.
-We already have this inconsistency in the code with $UN\to$}
+We already have this inconsistency in the code with $UN\to$} \apcomment{In the agda code let's not use arrow and have arrow implied as default but be explicit with '=' sign.}
   \item Carry on modifying the names of wfXXX- to wfXXXnotnot with prefix underscore in agda and in latex.

### 2025-09-05 Relations/Paper/Well-foundedness.tex
Symbol changes reflected in todo list

@@
       \]
-    \item  $R$ is \emph{minimally well-founded} ($\WFmin$) if every nonempty subset has a $P$-minimal element:
+    \item  $R$ is \emph{well-founded with regard to minimality} ($\WFmin$) if every nonempty subset has a $P$-minimal element:
       \[
@@
       \]
-    \item  $R$ is \emph{minimally well-founded for $\lnot \lnot$-closed predicates} ($\WFminDNE$) if every nonempty $\lnot \lnot$-closed subset contains a $P$-minimal element:
+    \item  $R$ is \emph{well-founded with regard to minimality for $\lnot \lnot$-closed predicates} ($\WFminDNE$) if every nonempty $\lnot \lnot$-closed subset contains a $P$-minimal element:
       \[
@@
       \]
-    \item  $R$ is \emph{weakly minimally well-founded} ($\WFminm$) if every nonempty subset contains a $\lnot \lnot P$-minimal element:
+    \item  $R$ is \emph{weakly well-founded with regard to a minimal element} ($\WFminm$) if for every nonempty subset there $\lnot \lnot$-exists a $P$-minimal element:
       \[
@@
       \]
-    \item  $R$ is \emph{weakly minimally well-founded under double negation elimination} ($\WFminDNEm$) if every nonempty $\lnot \lnot$-closed subset $\lnot \lnot$ contains a $P$-minimal element:
+    \item  $R$ is \emph{weakly well-founded with regard to a minimal element under double negation elimination} ($\WFminDNEm$) if every nonempty $\lnot \lnot$-closed subset $\lnot \lnot$-contains a $P$-minimal element:
       \[
@@
       \]      
+    \item [need to define wfmincor]
   \end{enumerate} 
@@
 \draw[arrow, bend right] (WFaccM) to (WFminDNEM);
-\draw[arrow, bend right = 90] (WFseqM) to node[right, text=red] {accCor} (WFaccM);  
+\draw[arrow, bend right = 90] (WFminCor) to node[right, text=red] {accCor} (WFaccM);  
 % \draw[arrow, bend left = 55] (WFaccM) to (WFminM);
@@
   %  Unless it's not satisfying $P$? \emph{We need to decide whether it is P-minimal as well.}}
-  \item Assuming \accCor, isWFacc- can also be derived from a weaker condition, isWFminCor(-).
-  (Just like isWFminDNE is a natural weakening of isWFmin that is sufficient to recover isWFacc
-  in the presence of {\accDNE}.)
-  It is implied by isWFseq-, but does not appear to imply anything on its own.
+  \item Assuming \accCor, $\isWFacc$ ($\isWFaccm$) can also be derived from a weaker condition, $\isWFmin$ ($\isWFminm$).
+  (Just like $\isWFminDNE$ is a natural weakening of $\isWFmin$ that is sufficient to recover $\isWFacc$ in the presence of {\accDNE}.)
+  It is implied by $\isWFseqm$, but does not appear to imply anything on its own.
 
-  \apcomment{(This seems easy: The converse implication isWFminCor to isWFseq- requires the sequence in question to
-  have decidable image, leading to a further weakening of isWFseq-.)}
+  % \apcomment{(This seems easy: The converse implication isWFminCor to isWFseq- requires the sequence in question to
+  % have decidable image, leading to a further weakening of isWFseq-.)}
   \item Since isWFminDNE- implies isWFseq-, the former also implies isWFminCor-.

### 2025-09-07 Relations/Paper/Summer_2025_TODO.tex
added comment about isWFCor

@@
 \maketitle
+
+\section*{September 2025}
+\subsection*{Notes from 7th September}
+Thoughts on the current state of the paper.
+\begin{description}
+\item[The status of wfCor]
+  \begin{itemize}
+    \item 
+      On the ``missing'' implication isWFCor$\lnot\lnot$ to isWFminDNE$\lnot\lnot$.
+
+      The wfCor hypothesis needs a ``choice function'' that will pick a successor $y$ of a given element $x$
+      (while still refuting the given predicate).
+
+      The property wfMinDNE$\lnot\lnot$ is equivalent to the statement that, if a $\lnot\lnot$-closed 
+      predicate $P$ has no minimal element, then its complement is universally true.
+
+      The ``no minimal element'' for not-not-closed $P$ is close to saying that its complement is coreductive; 
+      the difference is precisely that between the ``strong'' existential in the coreductive statement ---
+      and the weak one (with $\lnot\lnot$ applied to it) in the minimality one.
+
+      Assuming finite branchingness and weak decidability of $P$, we could get the strong existential 
+      from the weak one.  However, weak decidability and DNE are already equivalent with EM, so that 
+      will only apply to decidable predicates.  There may be a relationship to isWFminEM, but that 
+      would be a question for another paper.
+
+    \item 
+      On the ``strong side'' of the WF diagram, the situation is even worse.
+      Neither implication between isWFCor and isWFminDNE is provable, and similarly for isWFCor and isWFSeq.
+
+    \item 
+      At this point, there does not appear to be much more to say isWFCor, so we should consider removing it.
+
+      On Monday, we should quickly discuss the different versions of sequentially,
+      and move on to writing the text of the paper.
+    \end{itemize}
+\end{descriptioni}
 

### 2025-09-10 Relations/Paper/Well-foundedness.tex
Update to WF figure.

@@
 
-\newcommand{\accCor}{\textbf{accCor}}
-\newcommand{\accDNE}{\textbf{accDNE}}
+% \newcommand{\accCor}{\textbf{accCor}}
+% \newcommand{\accDNE}{\textbf{accDNE}}
 
@@
 % Row 1: WFacc
-\node[box] (WFacc) {$WFacc$};
+\node[box] (WFacc) {$\WFacc$};
 % \node[box, right=of WFacc] (NNWFacc) {$\lnot\lnot$WFacc};
-\node[box, right=2.9cm of WFacc] (WFaccM) {$WFacc\lnot\lnot$};
+\node[box, right=2.9cm of WFacc] (WFaccM) {$\WFaccm$};
 
@@
 % \draw[arrow] (NNWFacc) -- (WFaccM);
-\draw[arrow, bend right] (WFaccM) to node[above, text=red] {accDNE} (WFacc);
+\draw[arrow, bend right] (WFaccM) to node[above, text=red] {$\accDNE$} (WFacc);
 
@@
 % Row 5: WFminDNE -> WFminDNE-
-\node[box, below=of WFacc] (WFminDNE) {$WFminDNE$};
-\node[box, right=2.0cm of WFminDNE] (WFminDNEM) {$WFminDNE\lnot\lnot$};
+\node[box, below=of WFacc] (WFminDNE) {$\WFminDNE$};
+\node[box, below=of WFaccM] (WFminDNEM) {$\WFminDNEm$};
 
@@
 % Row 4: WFmin -> WFmin-
-\node[box, below=of WFminDNE] (WFmin) {$WFmin$};
-\node[box, right=2.8cm of WFmin] (WFminM) {$WFmin\lnot\lnot$};
+\node[box, below=of WFminDNE] (WFmin) {$\WFmin$};
+\node[box, below = of WFminDNEM] (WFminM) {$\WFminm$};
 
@@
 % Row 3: WFseq
-\node[box, below=of WFmin] (WFseq) {$WFseq$};
+\node[box, below=of WFmin] (WFseq) {$\WFseq$};
 % \node[box, right=of WFseq] (NNWFseq) {$\lnot\lnot$WFseq};
-\node[box, right=2.9cm of WFseq] (WFseqM) {$WFseq-$};
+\node[box, below= of WFminM] (WFseqM) {$\WFseqm$};
 
@@
 % Row 6: WFcor 
-\node[box, below=of WFseq] (WFCor) {$WFCor$};
-\node[box, below=of WFseqM] (WFminCor) {$WFminCor$};
+\node[box, below=of WFseq] (WFCor) {$\WFcor$};
+\node[box, below=of WFseqM] (WFminCor) {$\WFcorm$};
 
@@
 
-\draw[arrow, bend right = 90] (WFacc) to node[pos = 0.75,left, text = red] {Rdec} (WFseq);
+\draw[arrow, bend right = 90] (WFacc) to node[pos = 0.75,left, text = red] {$\rdec$} (WFseq);
 \draw[arrow, bend right] (WFaccM) to (WFminDNEM);
-\draw[arrow, bend right = 90] (WFminCor) to node[right, text=red] {accCor} (WFaccM);  
+\draw[arrow, bend right = 90] (WFminCor) to node[right, text=red] {$\accCor$} (WFaccM);  
 % \draw[arrow, bend left = 55] (WFaccM) to (WFminM);
@@
 \draw[arrow] (WFmin) -- (WFminDNE);
-\draw[arrow, <->] (WFminM) -- (WFminDNEM);
+\draw[arrow, bend right] (WFminM) to (WFminDNEM);
+\draw[arrow, bend right] (WFminDNEM) to (WFminM);
 
-\draw[arrow] (WFminDNE) to node[left, text = red] {accDNE} (WFacc);
-\draw[arrow, bend right=45] (WFminDNE) to node[pos=0.5, left, text=red] {MP$\equiv$} (WFseq);
-\draw[arrow, bend right] (WFminDNEM) to node[right, text=red] {FB} (WFaccM);
+\draw[arrow] (WFminDNE) to node[left, text = red] {$\accDNE$} (WFacc);
+\draw[arrow, bend right=45] (WFminDNE) to node[pos=0.5, left, text=red] {$\mpe$} (WFseq);
+\draw[arrow, bend right] (WFminDNEM) to node[right, text=red] {$\FB$} (WFaccM);
 \draw[arrow, bend right] (WFseqM) to (WFminCor);
-\draw[arrow, bend right] (WFminCor) to node [right, text=red] {MP$\equiv$} (WFseqM);
+\draw[arrow, bend right] (WFminCor) to node [right, text=red] {$\mpe$} (WFseqM);
 \draw[arrow] (WFCor) -- (WFminCor);
-\draw[arrow, bend left = 110] (WFCor) to node[left, text=red] {AccCor} (WFacc);
+\draw[arrow, bend left = 110] (WFCor) to node[left, text=red] {$\accCor$} (WFacc);
+\draw[arrow, bend left] (WFminCor) to node[below, text=red] {$\corDNE$} (WFCor);
 
@@
 constructive contrapositive of the definition of accessibility.
-Specifically, we call {\accCor} the statement that, if an element $x$
+Specifically, we call {$\accCor$} the statement that, if an element $x$
 is \emph{not} accessible, then there (strongly) exists a $y$ with $Ryx$
@@
 non-strongly normalizing element to a one-step reduct with the same property.)
-Assuming \accCor, all notions of well-foundedness
+Assuming $\accCor$, all notions of well-foundedness
 are constructively equivalent up to $\lnot\lnot$.
@@
   \item On the $\lnot\lnot$-side, WFmin- and WFminDNE- are equivalent,
-  and imply WFacc- via WFseq-, requiring {\accCor} assumption in the final inference.
+  and imply WFacc- via WFseq-, requiring {$\accCor$} assumption in the final inference.
   \item At the same time, if the relation is finitely branching, then WFminDNE-
@@
   \item Finite branchingness together with (weak) decidability of minimality
-  implies \accCor.
+  implies $\accCor$.
   % \apcomment{The previous observation suggests the question of whether isWFseq- might
@@
   %  Unless it's not satisfying $P$? \emph{We need to decide whether it is P-minimal as well.}}
-  \item Assuming \accCor, $\isWFacc$ ($\isWFaccm$) can also be derived from a weaker condition, $\isWFmin$ ($\isWFminm$).
-  (Just like $\isWFminDNE$ is a natural weakening of $\isWFmin$ that is sufficient to recover $\isWFacc$ in the presence of {\accDNE}.)
+  \item Assuming $\accCor$, $\isWFacc$ ($\isWFaccm$) can also be derived from a weaker condition, $\isWFmin$ ($\isWFminm$).
+  (Just like $\isWFminDNE$ is a natural weakening of $\isWFmin$ that is sufficient to recover $\isWFacc$ in the presence of {$\accDNE$}.)
   It is implied by $\isWFseqm$, but does not appear to imply anything on its own.

### 2025-09-15 Relations/Paper/Well-foundedness.tex
Update to the well-foundedness section

@@
 if and only if the converse relation is well-founded.
-In this section, we will compare several definitions of well-foundedness, which depend on the properties in Defintion~\ref{def:WFproperties} below.
+In this section, we will compare several definitions of well-foundedness,
+which depend on the basic notions given in Definition~\ref{def:WFnotions} below.
+
+For the rest of this section, fix $R \subseteq A \times A$.  We write $Rxy$ for $(x,y) \in R$.
+
+In the context of ARS, the reader should think of the converse relation, 
+interpreting $Rxy$ as denoting a reduction step $y \to_R x$.
 
 For $P \subseteq A$, let $\ol{P} = \{ x \in A \mid x \notin P\}$ denote the complement of $P$.
-\begin{definition}\label{def:WFproperties}
-  Let $R \subseteq A \times A$.  We write $Rxy$ when $(x,y) \in R$.
+\begin{definition}\label{def:WFnotions} \hfill 
    \begin{enumerate}
+    \item $x \in A$ is \emph{accessible} if for all $y \in A$, $Ryx$ implies $y$ is accessible. 
+      This is an inductive definition, with the base case obtained at 
+     those $x$ satisfying $\lnot Ryx$ for all $y$.
     \item $P \subseteq A$ is \emph{inductive}
     if, for each $x \in A$, $(\forall y. Ryx \to y \in P)$ implies $x \in P$.
-
-    \item $x \in A$ is \emph{accessible} if $x \in P$ for each inductive $P$.
 
@@
 
-    \item $s : \nat \to A$ is \emph{$R$-decreasing} if for all $k$, $(s(k+1),s(k)) \in R$. 
+    % \item $s : \nat \to A$ is \emph{$R$-decreasing} if for all $k$, $(s(k+1),s(k)) \in R$. 
   \end{enumerate}
 \end{definition}
-The definition of a $R$-decreasing sequence is repeated from Section~\ref{sec:Definitions}, as it is used extensively in this section.
 
-\begin{definition}
-  Let $R \subseteq A \times A$. We write $Rxy$ when $(x,y) \in R$.
+The above notions give rise to several distinct definitions of well-foundedness, given below. 
+Recall the definition of an $R$-decreasing sequence from Section~\ref{sec:Definitions}:
+this is a function $s : \nat \to A$ satisfying $(s(k+1),s(k)) \in R$ for all $k \in \nat$.
+
+\begin{definition} \label{def:WFproperties} \hfill 
   \begin{enumerate}
@@
       \[
-        \forall x \in A.\; x \text{ is accessible}.
+        \forall x \in A.\; x \text{ is accessible}
       \]
-    \item $R$ is \emph{inductively well-founded} ($\WFind$) if every inductive $P \subseteq A$ is universally true:
+    \item $R$ is \emph{inductively well-founded} ($\WFind$) if every inductive predicate is universally true:
       \[
-        \forall P \subseteq A.\;\text{$P$ is inductive} \Rightarrow \forall x \in A.\; x \in P.
+        \forall P \subseteq A.\;\text{$P$ is inductive} \Rightarrow \forall x \in A.\; x \in P
+      \]
+    \item $R$ is \emph{coreductively well-founded} ($\WFcor$) if every coreductive predicate is universally true:
+      \[
+        \forall P \subseteq A.\;\text{$P$ is coreductive} \Rightarrow \forall x \in A.\; x \in P
+      \]
+    \item  $R$ is \emph{well-founded minimality-wise} ($\WFmin$) if every nonempty subset contains a minimal element:
+      \[
+        \forall P \subseteq A.\; P \neq \varnothing \Rightarrow
+        \exists x \in A.\; \text{$x$ is $P$-minimal}
+      \]
+    \item  $R$ is \emph{well-founded minimality-wise for $\lnot \lnot$-closed predicates} ($\WFminDNE$) if every nonempty $\lnot \lnot$-closed subset contains a minimal element:
+      \[
+        \forall P \subseteq A.\; P \neq \varnothing \Rightarrow \ol{\ol P} \subseteq P \Rightarrow
+        \exists x \in A.\; \text{$x$ is $P$-minimal}
       \]
@@
       \[
-        \forall s : \nat \to A \exists k : \nat.\, \lnot \, R \,(s\,k)\,(s\,(k+1)).
+        \forall s : \nat \to A\ \exists k : \nat.\, \lnot \, R \,(s\,k)\,(s\,(k+1))
       \]
-    \item  $R$ is \emph{well-founded with regard to minimality} ($\WFmin$) if every nonempty subset has a $P$-minimal element:
-      \[
-        \forall P \subseteq A.\; P \neq \varnothing \Rightarrow
-        \exists x \in P.\; \text{$x$ is $P$-minimal}.
-      \]
-    \item  $R$ is \emph{well-founded with regard to minimality for $\lnot \lnot$-closed predicates} ($\WFminDNE$) if every nonempty $\lnot \lnot$-closed subset contains a $P$-minimal element:
-      \[
-        \forall P \subseteq A.\; P \neq \varnothing \Rightarrow \left(\ol{\ol P} \subseteq P\right) \Rightarrow
-        \exists x \in P.\; \text{$x$ is $P$-minimal}.
-      \]
-    \item $R$ is \emph{coreductively well-founded} ($\WFcor$) if every coreductive $P \subseteq A$ is universally true:
-      \[
-        \forall P \subseteq A.\;(\text{$P$ is coreductive}) \Rightarrow \forall x \in A.\; x \in P.
-      \]
-
   \end{enumerate}
@@
 be validated in many cases of interests.  In contrast, the original hypothesis
+(postulating minimal elements for ALL predicates)
 is generally equivalent to every subset being decidable.
-(The file WFCounters.agda shows that assuming the full minimality hypothesis
+For example, the file \texttt{WFCounters.agda} shows that assuming the full minimality hypothesis
 for the standard strict order on the natural numbers entails decidability
-of every subset of $\nat$, clearly incompatible with effective semantics.)
+of every subset of $\nat$ --- which is clearly incompatible with effective semantics.
+\apcomment{Make sure the file exists, recover it if necessary!}
 
@@
 every sequence $\lnot\lnot$-contains a non-decreasing index,
-for every non-empty subset there $\lnot\lnot$-exists a minimal element, etc. These are formalized in the definition below (and in \texttt{WFWeakDefinitions.agda}).
+for every non-empty subset there $\lnot\lnot$-exists a minimal element, etc.
+These are formalized in the definition below, and in the corresponding file
+\texttt{WFWeakDefinitions.agda}.
 
-\begin{definition}
-  Let $R \subseteq A \times A$. We write $Rxy$ when $(x,y) \in R$.
+\begin{definition} \label{def:WFweakproperties} \hfill 
   \begin{enumerate}
-    \item $R$ is \emph{weakly accessibly well-founded} ($\WFaccm$) if accessibility holds up to double negation:
+    \item $R$ is \emph{weakly accessibly well-founded} ($\WFaccm$) if accessibility holds for all elements up to double negation:
       \[
-        \forall x \in A.\; \lnot \lnot  (x \text{ is accessible}).
+        \forall x \in A.\; \lnot \lnot  (x \text{ is accessible})
       \]
@@
       \[
-        \forall P \subseteq A.\;(\text{$P$ is inductive}) \Rightarrow \forall x \in A.\; \lnot \lnot (x \in P).
+        \forall P \subseteq A.\;\text{$P$ is inductive} \Rightarrow \forall x \in A.\; \lnot \lnot (x \in P)
+      \]
+    \item $R$ is \emph{weakly coreductively well-founded} ($\WFcorm$) if every coreductive predicate holds for all elements up to double negation:
+      \[
+        \forall P \subseteq A.\;\text{$P$ is coreductive} \Rightarrow \forall x \in A.\; \lnot\lnot(x \in P)
+      \]
+    \item  $R$ is \emph{weakly well-founded minimality-wise} ($\WFminm$)
+      if for every nonempty subset $P$ there $\lnot \lnot$-exists a minimal element in $P$:
+      \[
+        \forall P \subseteq A.\; P \neq \varnothing \Rightarrow \lnot \lnot \;
+        (\exists x \in A.\; \text{$x$ is $P$-minimal})
+      \]
+    \item  $R$ is \emph{weakly well-founded minimality-wise for $\lnot \lnot$-closed predicates} ($\WFminDNEm$)
+      if for every nonempty $\lnot \lnot$-closed subset $P$ there $\lnot \lnot$-exists a minimal element in $P$:
+      % \[
+      %   \forall P \subseteq A.\; P \neq \varnothing \Rightarrow \left(\ol{\ol P} \subseteq P\right) \Rightarrow \lnot \lnot \;
+      % (\exists x \in P.\; \text{$x$ is $P$-minimal}) \]
+      \[
+        \forall P \subseteq A.\; P \neq \varnothing \Rightarrow \ol{\ol P} \subseteq P\Rightarrow \lnot \lnot \;
+        (\exists x \in A.\; \text{$x$ is $P$-minimal})
       \]      
@@
     \[
-        \forall s:\nat \to A.\; \lnot \text{($s$ is $R$-decreasing)}.
+      \forall s:\nat \to A.\; \lnot \text{($s$ is $R$-decreasing)}
     \]
-    \item  $R$ is \emph{weakly well-founded with regard to a minimal element} ($\WFminm$) if for every nonempty subset there $\lnot \lnot$-exists a $P$-minimal element:
-      \[
-        \forall P \subseteq A.\; P \neq \varnothing \Rightarrow \lnot \lnot \;
-        (\exists x \in P.\; \text{$x$ is $P$-minimal}).
-      \]
-    \item  $R$ is \emph{weakly well-founded with regard to a minimal element under double negation elimination} ($\WFminDNEm$) if every nonempty $\lnot \lnot$-closed subset $\lnot \lnot$-contains a $P$-minimal element:
-      \[
-        \forall P \subseteq A.\; P \neq \varnothing \Rightarrow \left(\ol{\ol P} \subseteq P\right) \Rightarrow \lnot \lnot \;
-        (\exists x \in P.\; \text{$x$ is $P$-minimal}).
-      \]      
-    \item [need to define wfmincor]
 \end{enumerate} 

### 2025-09-15 QADT/notes.tex
QADT notes

@@
 
+\newcommand{\mcS}{\mathcal{S}}
+
 \newcommand{\hired}[1]{\textcolor{Red}{#1}}
 \begin{document}
+
+\section{2025.09.15}
+\begin{enumerate}
+  \item Generalization of Fiore--Leinster result.
+
+  \textsc{Conjecture 1.}
+  If $X_1=P_1(X_1),\dots,X_n=P_n(X_n) \then Q_1(\vec X) = Q_2(\vec X)$
+  in the complex numbers, then this is true in all rigs (incl. all ``rig categories'').
+
+  Conditions: the polynomials $P_i$ must have a non-zero constant term and degree at least 2,
+  and each $Q_i$ must have a monomial involving a non-zero degree of each indeterminate $X_j$.
+
+  \textsc{Conjecture 2.}
+  If $X_1=P_1(\vec X),\dots,X_n=P_n(\vec X) \then Q_1(\vec X) = Q_2(\vec X)$
+  in the complex numbers, then this is true in all rigs (incl. all ``rig categories'').
+
+  Conditions: the polynomials $P_i$ must have a non-zero constant term and a monomial where $X_i$ has degree at least 2,
+  and each $Q_i$ must have a monomial involving a non-zero degree of each indeterminate $X_j$.
+
+\end{enumerate}
+
+\section*{2025.08.27}
+
+Ben will focus on completing the following proofs.
+\begin{enumerate}
+  \item Complete the substitution principle.
+
+  The theorem we want to prove is the following.
+
+  \emph{Let $P$ be a polynomial functor with integer coefficients. Then}
+  \[n + (\mu X. P(X + n) + X) \simeq \mu X. PX + X\]
+  \item Triangle/colimit lemma, toward proving $\mu X. \mu Y. F(X,Y) = \mu X. F(X,X)$
+  \item $A \cdot (\mu X. m X + n) \simeq \mu X. (m X + n A)$
+  \item At some point, write up the proof that if an $F$-algebra morphism is
+  mono, then the so is the initial algebra morphism.
+  \item A rigorous proof of the following sufficient condition for a fixed
+  point of the functor to be (isomorphic to) the least fixed point.
+
+  \emph{If the image of the morphism from a fixed point of $F$ to the final $F$-coalgebra
+  is a subset of the image of its composition with the morphism from the initial algebra,
+  then the initial algebra morphism IS epi (and hence iso).}
+
+  \item Characterizing all linear datatypes.
+\end{enumerate}
+
+\section*{2025.08.22}
+\begin{enumerate}
+  \item The substitution trick seems to prove the lemma Ben wants.
+  (Item 2 from 8.14)
+  \item Use $\mcS_n$ for the type of $n$-ary strings.
+
+  Notice that $1 + \mcS_2 \models X = 2X$.
+
+  \item Looked at $B \times M$, where $B = \mu X. 1 + X^2$ and $M = \mu X. 1 + X + X^2$.
+
+  Decided that their product should be $\mu X. 1 + X + X^6$, but realized it's more likely
+  that this is the product of $M$ and $T = \mu X. 1 + X + X^3$.
+
+  Ben is going to try to prove this.
+\end{enumerate}
 
@@
 The following points came up during the discussion.
-\begin{itemize}
+\begin{enumerate}
   \item The answer matches up with the polynomial obtained by the trick
@@
   How do we treat roots that have a complex component to them?
-\end{itemize}
+\end{enumerate}
 

### 2025-09-19 Relations/Paper/Well-foundedness.tex
Well-foundedness update

@@
 of every subset of $\nat$ --- which is clearly incompatible with effective semantics.
-\apcomment{Make sure the file exists, recover it if necessary!}
+\apcomment{Make sure the file exists (Done), check it wrt other new stuff in the FPLA repo.}
 
@@
 
-\begin{figure}[ht]
+\begin{figure}[hb]
 \centering  
 \begin{tikzpicture}[
+  scale=0.7,
+  every node/.style={transform shape},
   node distance=1cm and .5cm,
@@
 In \cite{Terese}, the $\WFseqm$ definition is used, as in the classical mathematics textbooks.
+\apcomment{Move this comment elsewhere? Perhaps we should have a separate discussion between isWFseq- and isWFseq-not-not?}
 
-To explore how these definitions interrelate it helps to consider the following corresponding weaker definitions (which are formalized in \texttt{WFWeakDefinitions.agda}). 
-The weaker definitions help us to explore how the standard well-founded definitions interrelate. This is made clear in the following diagram.
+The logical relationships between the various definitions of well-foundedness are summarized in 
+Figure \ref{fig:WF}.
+Again, all of the definitions appearing in this figure are classically equivalent.
+But constructively, some implications are not provable in general.
+Formalizing these implications enabled us to identify where exactly classical logic 
+is used, and how much of it is truly needed.
+An arrow from one node to another with no label indicates direct logical implication,
+provable constructively with no additional assumptions. An arrow with a label indicates an additional 
+(semi-)classical hypothesis needed to establish the implication. All of these facts have been 
+formalized within the WellFounded subdirectory of the Agda repository.
 
+\apcomment{Things to do:}
+\begin{itemize}
+  \item Reiterate/articulate the role of classical principles in establishing relationships between definitions of 
+    well-foundedness constructively 
+  \item List/discuss? classical principles appearing in the figure 
+  \item Discuss the figure overall -- refer to the enumerated list below 
+  \item Create ``narrative bridges'' between these items 
+  \item Final thing: Instantiate some of the classical principles on simple examples of term rewrite systems.
+\end{itemize}
+
+% As the figure illustrates, the concept of well-foundness is very rich from the vantage point of constructive logic.
+% Our analysis resulted in the following principles, 
+%
+% The additional classical hypotheses needed to recover some of the implications on the diagram 
+%
+% The principles appearing in the labels of Figure \ref{fig:WF} are valid for many rewriting systems,
+% and are classically true.  
+%
+% The weaker definitions help us to explore how the standard well-founded definitions interrelate. This is made clear in the following diagram.
+%
 \subsection{New version: Synopsis and Outline} 

### 2025-09-26 Relations/Paper/Summer_2025_TODO.tex
Update to WF figure.
todo update

@@
     \end{itemize}
-\end{descriptioni}
+\end{description}
 
@@
 Similarly for the relation between WFcor and WFminCor.}
-  \item Make a decision regarding WFcor.
+  \item [\done] Make a decision regarding WFcor.
 We use it to imply WFacc using AccCor.
@@
 Again, is this too much?}
-  \item Get the classical hypothesis and relations organized and see how they're used in the implications (organize implications by classical requirement.
+  \item [\done] Get the classical hypothesis and relations organized and see how they're used in the implications (organize implications by classical requirement.
 In the implications file we can import the classical implications.
@@
 
+\section*{September 15th todo}
+\begin{todolist}
+  \item (Minor) We want to have a sentence in our WF section making clear that we can consider local properties as well and maybe make an example from accessible to sequential. 
+  \item Sentence explaining that wfacc is equivalent to wfind and therefore isn't included in the diagram (wfind).
+  \item 
+\end{todolist}
+
 \end{document}

### 2025-10-01 Relations/Paper/Well-foundedness.tex
WIP swapping control
well-foundedness

@@
 of every subset of $\nat$ --- which is clearly incompatible with effective semantics.
-\apcomment{Make sure the file exists (Done), check it wrt other new stuff in the FPLA repo.}
 
@@
 These are formalized in the definition below, and in the corresponding file
-\texttt{WFWeakDefinitions.agda}.
+\texttt{WFWeakDefinitions.agda}. The logical relationships between all notions of well-foundedness are presented in Figure~\ref{fig:WF}.
 
@@
 formalized within the WellFounded subdirectory of the Agda repository.
+
+{
+\def\arraystretch{1.3}
+\begin{figure}[h!]
+\small 
+\begin{tabular}{@{}l l l @{}}
+\toprule
+\textbf{Property} & \textbf{Definition}  &\textbf{Agda Code}  \\
+\midrule
+$\rdec$   & $R$ is decidable 
+          & $\forall$ \verb|{x} {y}| $\to$ \verb|EM (R x y)|\\
+$\FB$     & $R$ is finitely branching 
+          & $\mathtt{\forall (a : A) \to \Sigma [ xs \in List A ] (\forall b \to R a b \to b \in{}List\, xs)}$ \\
+$\accCor$ & Accessibility is coreductive 
+          & \verb|R -coreductive (R -accessible)| \\
+$\accDNE$ & Accessibility is $\lnot\lnot$-closed
+          & $\lnot\lnot$\verb|Closed (R -accessible)| \\
+$\corDNE$ & Coreductives are $\lnot\lnot$-closed 
+          & $\mathtt{\forall (P : \mathcal{P} A) \to R}$-$\mathtt{coreductive\ P \to \lnot\lnot Closed\ P}$\\ 
+$\mpe$    & Sequences are $\lnot\lnot$-closed
+          & $\forall\ \mathtt{(f : \nat \to A) \to \lnot\lnot Closed 
+          (\lambda x \to \Sigma [ k \in \nat ] (f\, k \equiv x))}$ \\
+\bottomrule
+\end{tabular}
+\centering
+\caption{Classical Properties Used in the Well-Foundedness Diagram}
+\label{tab:cprop}
+\end{figure}
+}
+
+{
+\def\arraystretch{1.3}
+\begin{figure}[h!]
+\small 
+\begin{tabular}{@{}l l l @{}}
+\toprule
+\textbf{Property} & \textbf{Definition}  &\textbf{Agda Code}  \\
+\midrule
+$\rdec$   & $R$ is decidable 
+          & $\forall$ \verb|{x} {y}| $\to$ \verb|EM (R x y)|\\
+$\FB$     & $R$ is finitely branching 
+          & $\mathtt{\forall (a : A) \to \Sigma [ xs \in List A ] (\forall b \to R a b \to b \in{}List\, xs)}$ \\
+$\mpe$    & Sequences are $\lnot\lnot$-closed
+          & $\forall\ \mathtt{(f : \nat \to A) \to \lnot\lnot Closed 
+          (\lambda x \to \Sigma [ k \in \nat ] (f\, k \equiv x))}$ \\
+$\corDNE$ & Coreductives are $\lnot\lnot$-closed 
+          & $\mathtt{\forall (P : \mathcal{P} A) \to R}$-$\mathtt{coreductive\ P \to \lnot\lnot Closed\ P}$\\ 
+$\accDNE$ & Accessibility is $\lnot\lnot$-closed
+          & $\lnot\lnot$\verb|Closed (R -accessible)| \\
+$\accCor$ & Accessibility is coreductive 
+          & \verb|R -coreductive (R -accessible)| \\
+\bottomrule
+\end{tabular}
+\centering
+\caption{Classical Properties Used in the Well-Foundedness Diagram}
+\label{tab:cprop}
+\end{figure}
+}
 

### 2025-10-10 Relations/Paper/Well-foundedness.tex
work on well-foundedness

@@
 if and only if the converse relation is well-founded.
-In this section, we will compare several definitions of well-foundedness,
-which depend on the basic notions given in Definition~\ref{def:WFnotions} below.
+In this section, we will compare several definitions of well-foundedness.
+%which depend on the basic notions given in Definition~\ref{def:WFnotions} below.
+
+\subsection{Definitions of well-foundedness}
 
@@
       \[
-        \forall s : \nat \to A\ \exists k : \nat.\, \lnot \, R \,(s\,k)\,(s\,(k+1))
+        \forall s : \nat \to A\ \exists k : \nat.\, \lnot \, R \,(s\,(k+1))\,(s\,k)
       \]
@@
 for $\lnot\lnot$-closed subsets.  This is a significant restriction, which may
-be validated in many cases of interests.  In contrast, the original hypothesis
+be validated in certain cases.  In contrast, the original hypothesis
 (postulating minimal elements for ALL predicates)
 is generally equivalent to every subset being decidable.
-For example, the file \texttt{WFCounters.agda} shows that assuming the full minimality hypothesis
+Indeed, the file \texttt{WFCounters.agda} shows that assuming the full minimality hypothesis
 for the standard strict order on the natural numbers entails decidability
 of every subset of $\nat$ --- which is clearly incompatible with effective semantics.
+The restriction to $\lnot\lnot$-closed subsets implies (and is equivalent to) 
+every subset $P$ being merely \emph{weakly} decidable (satisfying $\lnot \lnot P(x) \lor \lnot P(X)$ 
+for all $x$).
 
@@
 These are formalized in the definition below, and in the corresponding file
-\texttt{WFWeakDefinitions.agda}. The logical relationships between all notions of well-foundedness are presented in Figure~\ref{fig:WF}.
+\texttt{WFWeakDefinitions.agda}.
 
@@
 
+In \cite{Terese}, the $\WFseqm$ definition is used, as in the classical mathematics textbooks.
+\apcomment{Perhaps we should have a separate discussion between isWFseq- and isWFseq-not-not?}
+
+\subsection{Implications between the definitions}
+
+% The logical relationships between all of the notions of well-foundedness defined 
+% above are presented in Figure~\ref{fig:WF}.
+%
 \begin{figure}[hb]
@@
 
-In \cite{Terese}, the $\WFseqm$ definition is used, as in the classical mathematics textbooks.
-\apcomment{Move this comment elsewhere? Perhaps we should have a separate discussion between isWFseq- and isWFseq-not-not?}
+All of the above definitions of well-foundedness are classically equivalent.
+But constructively, the only provable equivalence is between the inductive and accessible 
+formluations (reflecting the fact that accessibility is defined as the least inductive predicate).
+Formalizing the remaining implications enabled us to identify where exactly classical logic 
+is used, and how much of it is truly needed.
 
-The logical relationships between the various definitions of well-foundedness are summarized in 
-Figure \ref{fig:WF}.
-Again, all of the definitions appearing in this figure are classically equivalent.
-But constructively, some implications are not provable in general.
-Formalizing these implications enabled us to identify where exactly classical logic 
-is used, and how much of it is truly needed.
+The logical relationships between the various definitions are summarized in Figure \ref{fig:WF}.
 An arrow from one node to another with no label indicates direct logical implication,
 provable constructively with no additional assumptions. An arrow with a label indicates an additional 
-(semi-)classical hypothesis needed to establish the implication. All of these facts have been 
+(semi-)classical hypothesis needed to establish the implication. 
+The definitions of these hypotheses are given in Figure \ref{tab:cprop}.
+All of the implications have been 
 formalized within the WellFounded subdirectory of the Agda repository.
-
-{
-\def\arraystretch{1.3}
-\begin{figure}[h!]
-\small 
-\begin{tabular}{@{}l l l @{}}
-\toprule
-\textbf{Property} & \textbf{Definition}  &\textbf{Agda Code}  \\
-\midrule
-$\rdec$   & $R$ is decidable 
-          & $\forall$ \verb|{x} {y}| $\to$ \verb|EM (R x y)|\\
-$\FB$     & $R$ is finitely branching 
-          & $\mathtt{\forall (a : A) \to \Sigma [ xs \in List A ] (\forall b \to R a b \to b \in{}List\, xs)}$ \\
-$\accCor$ & Accessibility is coreductive 
-          & \verb|R -coreductive (R -accessible)| \\
-$\accDNE$ & Accessibility is $\lnot\lnot$-closed
-          & $\lnot\lnot$\verb|Closed (R -accessible)| \\
-$\corDNE$ & Coreductives are $\lnot\lnot$-closed 
-          & $\mathtt{\forall (P : \mathcal{P} A) \to R}$-$\mathtt{coreductive\ P \to \lnot\lnot Closed\ P}$\\ 
-$\mpe$    & Sequences are $\lnot\lnot$-closed
-          & $\forall\ \mathtt{(f : \nat \to A) \to \lnot\lnot Closed 
-          (\lambda x \to \Sigma [ k \in \nat ] (f\, k \equiv x))}$ \\
-\bottomrule
-\end{tabular}
-\centering
-\caption{Classical Properties Used in the Well-Foundedness Diagram}
-\label{tab:cprop}
-\end{figure}
-}
 
@@
 
-\apcomment{Things to do:}
-\begin{itemize}
-  \item Reiterate/articulate the role of classical principles in establishing relationships between definitions of 
-    well-foundedness constructively 
-  \item List/discuss? classical principles appearing in the figure 
-  \item Discuss the figure overall -- refer to the enumerated list below 
-  \item Create ``narrative bridges'' between these items 
-  \item Final thing: Instantiate some of the classical principles on simple examples of term rewrite systems.
-\end{itemize}
-
 % As the figure illustrates, the concept of well-foundness is very rich from the vantage point of constructive logic.
@@
 %
-\subsection{New version: Synopsis and Outline} 
-This cuts down some, but not all, of the complexity.
+As can be seen from the figure, taking the $\lnot\lnot$-closures of 
+well-foundedness properties cuts down some, but not all, of the complexity.
 For example, the two minimality principles
@@
 % On the other hand, the reverse
-At the same time, the
-implication from sequential to inductive wellfoundedness
-still requires an additional hypothesis, which may be described as the
-constructive contrapositive of the definition of accessibility.
-Specifically, we call {$\accCor$} the statement that, if an element $x$
-is \emph{not} accessible, then there (strongly) exists a $y$ with $Ryx$
-and $y$ not accessible.  (In the context of rewriting systems,
+At the same time, the weak version of the sequential definition is unable to imply 
+the (weak version of) accessible one without an additional hypothesis $\accCor$, 
+which may be described as the constructive contrapositive of the definition of accessibility.
+In the context of rewriting systems,
 this condition asserts the existence of a function which maps any
-non-strongly normalizing element to a one-step reduct with the same property.)
+non-strongly normalizing element to a one-step reduct with the same property.
 Assuming $\accCor$, all notions of well-foundedness
@@
 
-As this discussion illustrates, the network of relationships between the
-constructive notions of well-foundedness is quite rich.  The purpose of
-this section is to present the basic picture of these implications,
-and elaborate on some of them.  Our key observations are summarized
-in the following list.
+As the Figure \ref{tab:cprop} illustrates, the network of relationships between the
+constructive notions of well-foundedness is quite rich. 
+The main observations can now be read off from the figure.
 \begin{enumerate}
-  \item The implication from the inductive to the sequential definition
-  requires the underlying relation to be decidable. This assumption is no longer
-  necessary on the $\lnot\lnot$-translated side.
+  \item The implication from $\isWFacc$ to $\isWFseq$ requires the underlying relation to be decidable. 
+    This assumption is no longer necessary on the $\lnot\lnot$-translated side.
   \item WFmin is a very strong assumption and implies WFseq unconditionally.
-  The more reasonable WFminDNE requires Markov's Principle
-  (and decidability of $R$) to yield the same consequence.
+  The more reasonable WFminDNE requires the image of every sequence to be $\lnot\lnot$-closed 
+  to complete the implication.  This condition can be considered as a special case of Markov's Principle
+  (assuming decidability of equality on $A$).
   \item On the $\lnot\lnot$-side, WFmin- and WFminDNE- are equivalent,
   and imply WFacc- via WFseq-, requiring {$\accCor$} assumption in the final inference.
-  \item At the same time, if the relation is finitely branching, then WFminDNE-
-  implies WFacc- directly.
-  \item Finite branchingness together with (weak) decidability of minimality
-  implies $\accCor$.
+  \item At the same time, if the relation is finitely branching ($\FB$), then WFminDNE-
+  implies WFacc- directly.  It should be noted that, $\FB$ together with (weak) decidability of minimality
+  implies $\accCor$.  \apcomment{Fix this: This is proved in \texttt{FinitelyBranching.agda}.}.
   % \apcomment{The previous observation suggests the question of whether isWFseq- might
@@
   %  Unless it's not satisfying $P$? \emph{We need to decide whether it is P-minimal as well.}}
-  \item Assuming $\accCor$, $\isWFacc$ ($\isWFaccm$) can also be derived from a weaker condition, $\isWFmin$ ($\isWFminm$).
+  \item Assuming $\accCor$, $\isWFacc$ ($\isWFaccm$) can also be derived from a weaker condition, $\WFcor$ ($\WFcorm$).
+    \apcomment{Add the ``is''!}
     (Just like $\isWFminDNE$ is a natural weakening of $\isWFmin$ that is sufficient to recover $\isWFacc$ in the presence of {$\accDNE$}.)
-  It is implied by $\isWFseqm$, but does not appear to imply anything on its own.
+  \apcomment{True?  It is implied by $\isWFseqm$, but does not appear to imply anything on its own.}
 
@@
   % have decidable image, leading to a further weakening of isWFseq-.)}
-  \item Since isWFminDNE- implies isWFseq-, the former also implies isWFminCor-.
+\item \apcomment{Fix with macros}. Since isWFminDNE- implies isWFseq-, the former also implies isWFminCor-.
   But the converse fails: If a subset/predicate $P$ is $\lnot\lnot$-closed,
@@
 
-  \item Assuming normal forms are decidable,
-  isWFseq implies a very weak version of minimality, isWFminEM.
-  On its own this property is insufficient to imply anything else,
-  so we have nothing else to say about it.
+  % \item Assuming normal forms are decidable,
+  % isWFseq implies a very weak version of minimality, isWFminEM.
+  % On its own this property is insufficient to imply anything else,
+  % so we have nothing else to say about it.
 \end{enumerate}
@@
 These are recorded in the file \verb|Wellfounded.agda|
+
+% \apcomment{Things to do:}
+% \begin{itemize}
+%   \item Reiterate/articulate the role of classical principles in establishing relationships between definitions of 
+%     well-foundedness constructively 
+%   \item List/discuss? classical principles appearing in the figure 
+%   \item Discuss the figure overall -- refer to the enumerated list below 
+%   \item Create ``narrative bridges'' between these items 
+%   \item Final thing: Instantiate some of the classical principles on simple examples of term rewrite systems.
+% \end{itemize}
+%
+%

### 2025-10-15 Relations/Paper/Well-foundedness.tex
getting close to finishing section 5

@@
       \]
-    \item $R$ is \emph{inductively well-founded} ($\WFind$) if every inductive predicate is universally true:
+    \item \label{def:WFind} $R$ is \emph{inductively well-founded} ($\WFind$) if every inductive predicate is universally true:
       \[
@@
 
-% As the figure illustrates, the concept of well-foundness is very rich from the vantage point of constructive logic.
-% Our analysis resulted in the following principles, 
-%
-% The additional classical hypotheses needed to recover some of the implications on the diagram 
-%
+\apcomment{Make another version of the diagram, swapping WFmin and WFacc rows.}
+
 % The principles appearing in the labels of Figure \ref{fig:WF} are valid for many rewriting systems,
 % and are classically true.  
-%
-% The weaker definitions help us to explore how the standard well-founded definitions interrelate. This is made clear in the following diagram.
-%
-As can be seen from the figure, taking the $\lnot\lnot$-closures of 
+Figure \ref{tab:cprop} illustrates that the network of logical relationships between
+constructive notions of well-foundedness is quite rich indeed. 
+Taking the $\lnot\lnot$-closures of 
 well-foundedness properties cuts down some, but not all, of the complexity.
-For example, the two minimality principles
-described above are equivalent with this formulation.
+For example, the two minimality principles become equivalent.
 % The implication from the inductive to sequential definition no longer requires
@@
 At the same time, the weak version of the sequential definition is unable to imply 
-the (weak version of) accessible one without an additional hypothesis $\accCor$, 
+the (weak) accessible one without an additional hypothesis $\accCor$, 
 which may be described as the constructive contrapositive of the definition of accessibility.
@@
 this condition asserts the existence of a function which maps any
-non-strongly normalizing element to a one-step reduct with the same property.
+element that is \emph{not} strongly normalizing to a one-step reduct of it having the same property.
 Assuming $\accCor$, all notions of well-foundedness
@@
 
-As the Figure \ref{tab:cprop} illustrates, the network of relationships between the
-constructive notions of well-foundedness is quite rich. 
-The main observations can now be read off from the figure.
+Other observations that can be gleaned from the figure include the following.
+\apcomment{The macros have to fixed throughout.}
 \begin{enumerate}
@@
   to complete the implication.  This condition can be considered as a special case of Markov's Principle
-  (assuming decidability of equality on $A$).
-  \item On the $\lnot\lnot$-side, WFmin- and WFminDNE- are equivalent,
-  and imply WFacc- via WFseq-, requiring {$\accCor$} assumption in the final inference.
+  (if one assumes that equality on $A$ is decidable).
+  \item On the $\lnot\lnot$-side, WFmin- and WFminDNE- are equivalent, are directly implied by $\isWFaccm$, 
+    and directly imply $\isWFseqm$  \apcomment{Fix macros}.
+  \item All definitions imply $\WFcorm$.  This weakest definition implies $\isWFaccm$ assuming the 
+    ``constructive contrapositive of accessibility'', $\accCor$.
+    %While this condition is implied by $\isWFseqm$, it does not appear to imply anything on its own.
+  \item Assuming $\accCor$, $\isWFacc$ can also be derived from $\WFcor$. % , the stronger version of $\WFcorm$.
+    \apcomment{Add the ``is''!}
+
+    (This is analogous to how $\isWFminDNE$ is a natural weakening of 
+    $\isWFmin$ that is sufficient to recover $\isWFacc$ in the presence of {$\accDNE$}.)
+
   \item At the same time, if the relation is finitely branching ($\FB$), then WFminDNE-
-  implies WFacc- directly.  It should be noted that, $\FB$ together with (weak) decidability of minimality
-  implies $\accCor$.  \apcomment{Fix this: This is proved in \texttt{FinitelyBranching.agda}.}.
+    implies WFacc- directly.
+
+    (It may be noted that $\FB$ implies $\accCor$ whenever the relation $R$ is decidable
+    and $R$-accessibility is \emph{weakly} decidable;  this is proved in \texttt{Coreductive.agda}.)
   % \apcomment{The previous observation suggests the question of whether isWFseq- might
@@
   %  Unless it's not satisfying $P$? \emph{We need to decide whether it is P-minimal as well.}}
-  \item Assuming $\accCor$, $\isWFacc$ ($\isWFaccm$) can also be derived from a weaker condition, $\WFcor$ ($\WFcorm$).
-    \apcomment{Add the ``is''!}
-    (Just like $\isWFminDNE$ is a natural weakening of $\isWFmin$ that is sufficient to recover $\isWFacc$ in the presence of {$\accDNE$}.)
-  \apcomment{True?  It is implied by $\isWFseqm$, but does not appear to imply anything on its own.}
-
   % \apcomment{(This seems easy: The converse implication isWFminCor to isWFseq- requires the sequence in question to
   % have decidable image, leading to a further weakening of isWFseq-.)}
-\item \apcomment{Fix with macros}. Since isWFminDNE- implies isWFseq-, the former also implies isWFminCor-.
-  But the converse fails: If a subset/predicate $P$ is $\lnot\lnot$-closed,
-  we cannot conclude it is coreductive.
 
-  \item In general, the coreductive properties speak to the ability to choose
+% \item \apcomment{Fix with macros}. Since isWFminDNE- implies isWFseq-, the former also implies isWFminCor-.
+%   But the converse fails: If a subset/predicate $P$ is $\lnot\lnot$-closed,
+%   we cannot, in general, conclude it is coreductive.
+  \item \apcomment{Delete? In general, the coreductive properties speak to the ability to choose
   a successor (strong existence).  This ability is central to being able to
   define sequences.  Therefore, sequential definitions generally require
-  some coreductive situation to be applicable.
+some coreductive situation to be applicable.}
 
@@
 
+We have also considered the statement that the complement of every coreductive predicate
+  has a least element.  This statement and its $\lnot\lnot$-version are both equivalent to $\WFcorm$
+  (see \texttt{CoreductiveImplications.agda}), so we have not included them in the figure.
+
+We also did not include the inductive definition, Definition \ref{def:WFproperties}.\ref{def:WFind}.
+  Logically, it is trivially equivalent to the accessible one, but its Agda formulation has a defect: 
+  the inductive well-foundedness property lands in the larger universe $\mathtt{Set}_1$, due to 
+  quantification over all predicates on $A$.  (This defect is also present in $\isWFmin$, $\isWFminDNE$, and \texttt{isWFcor}.)
+
 In \cite{Terese}, well-foundedness is defined as in the classical mathematics textbooks,
@@
 (Again, well-foundedness of $R$ corresponds to strong normalization of its converse.)
+\apcomment{Add a discussion about isWFseq- vs. isWFseq$\lnot\lnot$.}
+
+We consider $\isWFacc$ the canonical constructive definition of a well-founded relation.
+
+\apcomment{Todo: 1. Filter through the rest, and see if there's anything we may still want to keep.\\
+  2. Include a subsection, or a section, with examples.  Provide examples where some decidability 
+properties are provable, and others are not.}
+
+\subsection{Old. Delete?}
+
 Translating this statement directly into type theory yields the formula

### 2025-10-22 Relations/Paper/Summer_2025_TODO.tex
WIP swapping control

@@
   \item Sentence explaining that wfacc is equivalent to wfind and therefore isn't included in the diagram (wfind).
+\end{todolist}
+
+\section*{September 26th TODO}
+\begin{todolist}     
+  \item Focus for next meeting on writing. 
+  \item [\done] Are not not closed predicates over natural numbers dedcidable: If not is this a counterexample for WFminDNE.
+\end{todolist}
+
+\section*{October 10th TODO}
+\begin{todolist}     
+  \item Want to show that FB and weak decidability gives us accCor (think we may have shown this previously)
+  \item Add 'is' to wfcor macros.
+  \item make a decision on wfseq not not name. 
+  \item Keep on cleaning the WF section in paper. 
+  \item 
+\end{todolist}
+
+\section*{October 15th TODO}
+\begin{todolist}     
+  \item It's possible to have a term rewrite system with good properties like FB and the relation being decidable.
+But not satisfying accCor.
+That is something that can be added in a final touch of the paper.
+Either a remark or example, where a term rewrite system does not validate accCor.
+(In the lambda calculus, there are computable perpetual strategies.
+We think they're concerned with weak normalization.
+Not sure if it can be done with strong normalization.)
+  \item Do a final read through of the information below the figure. Have we captured all the most important information / Are we repeating ourselves?
+  \item Do we want to keep anything in the old/delete section of WF?
+  \item Do we want to add anything about counter examples or positive examples? 
+  \item We may want to use words rather than macros in certain locations
+  \item Check through the comments in general in the section. 
   \item 

### 2025-10-22 Relations/Paper/Well-foundedness.tex

@@
  \label{fig:WF} 
+\end{figure}
+\clearpage
+
+\begin{figure}[hb]
+\centering  
+\begin{tikzpicture}[
+  scale=0.7,
+  every node/.style={transform shape},
+  node distance=1cm and .5cm,
+  box/.style={draw, rectangle, rounded corners, minimum width=1cm, minimum height=1cm, align=center},
+  arrow/.style={-{Latex}, thick}
+]
+
+% Row 1: WFmin -> WFmin-
+\node[box] (WFmin) {$\WFmin$};
+\node[box, right=2.9cm of WFmin] (WFminM) {$\WFminm$};
+
+\draw[arrow] (WFmin) -- (WFminM);
+
+% Row 2: WFminDNE -> WFminDNE-
+\node[box, below=of WFmin] (WFminDNE) {$\WFminDNE$};
+\node[box, below=of WFminM] (WFminDNEM) {$\WFminDNEm$};
+
+\draw[arrow] (WFminDNE) -- (WFminDNEM);
+
+% Row 3: WFacc
+
+\node[box, below=of WFminDNE] (WFacc) {$\WFacc$};
+
+\node[box, below = of WFminDNEM] (WFaccM) {$\WFaccm$};
+\draw[arrow, bend right] (WFacc) to (WFaccM);
+\draw[arrow, bend right] (WFaccM) to node[below, text=red] {$\accDNE$} (WFacc);
+
+% Row 4: WFseq
+\node[box, below=of WFacc] (WFseq) {$\WFseq$};
+\node[box, below= of WFaccM] (WFseqM) {$\WFseqm$};
+
+\draw[arrow] (WFseq) -- (WFseqM);
+
+% Row 5: WFcor 
+\node[box, below=of WFseq] (WFCor) {$\WFcor$};
+\node[box, below=of WFseqM] (WFminCor) {$\WFcorm$};
+
+% \draw[arrow, bend left = 55] (WFaccM) to (WFminM);
+
+% Inter-row arrows
+\draw[arrow] (WFacc) to node[right, text = red] {$\rdec$} (WFseq);
+\draw[arrow, bend right] (WFaccM) to (WFminDNEM);
+\draw[arrow, bend right = 90] (WFminCor) to node[right, text=red] {$\accCor$} (WFaccM);
+
+\draw[arrow, bend right = 90] (WFmin) to (WFseq);
+\draw[arrow] (WFaccM) -- (WFseqM);
+\draw[arrow] (WFmin) -- (WFminDNE);
+\draw[arrow, bend right] (WFminM) to (WFminDNEM);
+\draw[arrow, bend right] (WFminDNEM) to (WFminM);
+
+\draw[arrow] (WFminDNE) to node[right, text = red] {$\accDNE$} (WFacc);
+\draw[arrow, bend right=45] (WFminDNE) to node[pos=0.5, left, text=red] {$\mpe$} (WFseq);
+\draw[arrow, bend right] (WFminDNEM) to node[left, text=red] {$\FB$} (WFaccM);
+\draw[arrow, bend right] (WFseqM) to (WFminCor);
+\draw[arrow, bend right] (WFminCor) to node [right, text=red] {$\mpe$} (WFseqM);
+\draw[arrow] (WFCor) -- (WFminCor);
+% \draw[arrow, bend left = 110] (WFCor) to node[left, text=red] {$\accCor$} (WFacc);
+\draw[arrow, bend left] (WFminCor) to node[below, text=red] {$\corDNE$} (WFCor);
+
+\draw[arrow, dashed, bend left=80, blue] (WFCor) to node[left, text=blue] {$\accCor$} (WFacc);
+
+\end{tikzpicture}
+\caption{The logical relationships between notions of well-foundedness}
+ \label{fig:WF2} 
 \end{figure}

### 2025-10-22 Relations/Paper/Well-foundedness.tex
Almost done with section 5

@@
 Recall the definition of an $R$-decreasing sequence from Section~\ref{sec:Definitions}:
-this is a function $s : \nat \to A$ satisfying $(s(k+1),s(k)) \in R$ for all $k \in \nat$.
+this is a function $s : \nat \to A$ satisfying $R(s(k+1))(sk) \in R$ for all $k \in \nat$.
 
@@
 interpretations in varying degrees of logical strength.
+Formalizing the remaining implications enabled us to identify where exactly classical logic
+is used, and how much of it is truly needed.
 
@@
 is generally equivalent to every subset being decidable.
-Indeed, the file \texttt{WFCounters.agda} shows that assuming the full minimality hypothesis
-for the standard strict order on the natural numbers entails decidability
-of every subset of $\nat$ --- which is clearly incompatible with effective semantics.
-The restriction to $\lnot\lnot$-closed subsets implies (and is equivalent to) 
-every subset $P$ being merely \emph{weakly} decidable (satisfying $\lnot \lnot P(x) \lor \lnot P(X)$ 
-for all $x$).
+The file \texttt{WFCounters.agda} shows that assuming the full minimality hypothesis $\WFmin$ for the standard strict order on the natural numbers entails decidability of every subset of $\nat$ (which is clearly incompatible with effective semantics), while its restriction $\WFminDNE$ implies
+%(and is equivalent to)
+that each subset $P$ it \emph{weakly} decidable,
+satisfying $\lnot \lnot P(x) \lor \lnot P(X)$ for all $x$.
 
@@
 for every non-empty subset there $\lnot\lnot$-exists a minimal element, etc.
-These are formalized in the definition below, and in the corresponding file
+These weaker notions are formalized in the definition below, and in the corresponding file
 \texttt{WFWeakDefinitions.agda}.
@@
 
-In \cite{Terese}, the $\WFseqm$ definition is used, as in the classical mathematics textbooks.
-\apcomment{Perhaps we should have a separate discussion between isWFseq- and isWFseq-not-not?}
+In \cite{Terese}, the $\WFseqm$ definition is used, as in the classical mathematics textbooks.  This definition appears to be strictly weaker than
+WFseqm-not-not, asserting that every sequence not-not contains a
+non-decreasing index.
+\apcomment{fix the macro please!}
+% \apcomment{Perhaps we should have a separate discussion between isWFseq- and isWFseq-not-not?}
 
@@
 
-% The logical relationships between all of the notions of well-foundedness defined 
-% above are presented in Figure~\ref{fig:WF}.
-%
-\begin{figure}[hb]
-\centering  
-\begin{tikzpicture}[
-  scale=0.7,
-  every node/.style={transform shape},
-  node distance=1cm and .5cm,
-  box/.style={draw, rectangle, rounded corners, minimum width=1cm, minimum height=1cm, align=center},
-  arrow/.style={-{Latex}, thick}
-]
+The logical relationships between all of the above definitions are summarized in Figure \ref{fig:WF}.
+All of the implications in the figure have been
+formalized within the WellFounded subdirectory of the Agda repository.
+An arrow from one node to another with no label indicates direct logical implication,
+provable constructively with no additional assumptions. An arrow with a label indicates an additional
+(semi-)classical hypothesis needed to establish the implication.
+The definitions of these hypotheses are given in Figure \ref{tab:cprop}.
 
-% Row 1: WFacc
-\node[box] (WFacc) {$\WFacc$};
-% \node[box, right=of WFacc] (NNWFacc) {$\lnot\lnot$WFacc};
-\node[box, right=2.9cm of WFacc] (WFaccM) {$\WFaccm$};
+We consider $\WFacc$ to be the canonical constructive definition of
+a well-founded relation (hence the emphasis in the figure).
+In the ARS setting, this corresponds to defining
+strong normalization inductively in terms of reductions to normal forms.
+As can be seen from the figure, it is implied by
+Terese's definition $\WFseqm$ only when \emph{two}
+strongly classical conditions are in place.
+These are $\accDNE$ (not-not-closure of strong normalization)
+and $\accCor$ (which is related to the existence of an effective perpetual reduction strategy).
 
-\draw[arrow] (WFacc) -- (WFaccM);
-% \draw[arrow] (NNWFacc) -- (WFaccM);
-\draw[arrow, bend right] (WFaccM) to node[above, text=red] {$\accDNE$} (WFacc);
-
-% Row 2: WFind
-% \node[box, below=of WFacc] (WFind) {WFind};
-% \node[box, right=of WFind] (NNWFind) {$\lnot\lnot$WFind};
-% \node[box, right=of NNWFind] (WFindM) {WFind-};
-
-% \draw[arrow] (WFind) -- (NNWFind);
-% \draw[arrow] (NNWFind) -- (WFindM);
-
-% \draw[arrow] (NNWFseq) -- (WFseqM);
-
-% Row 5: WFminDNE -> WFminDNE-
-\node[box, below=of WFacc] (WFminDNE) {$\WFminDNE$};
-\node[box, below=of WFaccM] (WFminDNEM) {$\WFminDNEm$};
-
-\draw[arrow] (WFminDNE) -- (WFminDNEM);
-
-% Row 4: WFmin -> WFmin-
-\node[box, below=of WFminDNE] (WFmin) {$\WFmin$};
-\node[box, below = of WFminDNEM] (WFminM) {$\WFminm$};
-
-\draw[arrow] (WFmin) -- (WFminM);
-
-% Row 3: WFseq
-\node[box, below=of WFmin] (WFseq) {$\WFseq$};
-% \node[box, right=of WFseq] (NNWFseq) {$\lnot\lnot$WFseq};
-\node[box, below= of WFminM] (WFseqM) {$\WFseqm$};
-
-\draw[arrow] (WFseq) -- (WFseqM);
-
-% Row 6: WFcor 
-\node[box, below=of WFseq] (WFCor) {$\WFcor$};
-\node[box, below=of WFseqM] (WFminCor) {$\WFcorm$};
-
-% Arrows between rows
-% \draw[arrow, <->] (WFacc) -- (WFind);
-% \draw[arrow, <->] (NNWFacc) -- (NNWFind);
-% \draw[arrow, <->] (WFaccM) -- (WFindM);
-
-\draw[arrow, bend right = 90] (WFacc) to node[pos = 0.75,left, text = red] {$\rdec$} (WFseq);
-\draw[arrow, bend right] (WFaccM) to (WFminDNEM);
-\draw[arrow, bend right = 90] (WFminCor) to node[right, text=red] {$\accCor$} (WFaccM);  
-% \draw[arrow, bend left = 55] (WFaccM) to (WFminM);
-
-\draw[arrow] (WFmin) -- (WFseq);
-\draw[arrow] (WFminM) -- (WFseqM);
-\draw[arrow] (WFmin) -- (WFminDNE);
-\draw[arrow, bend right] (WFminM) to (WFminDNEM);
-\draw[arrow, bend right] (WFminDNEM) to (WFminM);
-
-\draw[arrow] (WFminDNE) to node[left, text = red] {$\accDNE$} (WFacc);
-\draw[arrow, bend right=45] (WFminDNE) to node[pos=0.5, left, text=red] {$\mpe$} (WFseq);
-\draw[arrow, bend right] (WFminDNEM) to node[right, text=red] {$\FB$} (WFaccM);
-\draw[arrow, bend right] (WFseqM) to (WFminCor);
-\draw[arrow, bend right] (WFminCor) to node [right, text=red] {$\mpe$} (WFseqM);
-\draw[arrow] (WFCor) -- (WFminCor);
-\draw[arrow, bend left = 110] (WFCor) to node[left, text=red] {$\accCor$} (WFacc);
-\draw[arrow, bend left] (WFminCor) to node[below, text=red] {$\corDNE$} (WFCor);
-
-\end{tikzpicture}
-\caption{The logical relationships between notions of well-foundedness}
- \label{fig:WF} 
-\end{figure}
-\clearpage
-
-\begin{figure}[hb]
+\begin{figure}[h]
 \centering
@@
 
-\node[box, below=of WFminDNE] (WFacc) {$\WFacc$};
+\node[box, line width = 0.5mm, below=of WFminDNE] (WFacc) {$\WFacc$};
 
 \node[box, below = of WFminDNEM] (WFaccM) {$\WFaccm$};
-\draw[arrow, bend right] (WFacc) to (WFaccM);
-\draw[arrow, bend right] (WFaccM) to node[below, text=red] {$\accDNE$} (WFacc);
+\draw[arrow] (WFacc) to (WFaccM);
+\draw[arrow, bend left] (WFaccM) to node[below, text=red] {$\accDNE$} (WFacc);
 
@@
 \draw[arrow, bend right] (WFaccM) to (WFminDNEM);
-\draw[arrow, bend right = 90] (WFminCor) to node[right, text=red] {$\accCor$} (WFaccM);
+\draw[arrow, bend right = 90] (WFminCor) to node[pos = 0.4, right, text=red] {$\accCor$} (WFaccM);
 
-\draw[arrow, bend right = 90] (WFmin) to (WFseq);
+\draw[arrow, bend right = 75] (WFmin) to (WFseq);
+\draw[arrow, bend left = 75] (WFminM) to (WFseqM);
 \draw[arrow] (WFaccM) -- (WFseqM);
@@
 \draw[arrow] (WFminDNE) to node[right, text = red] {$\accDNE$} (WFacc);
-\draw[arrow, bend right=45] (WFminDNE) to node[pos=0.5, left, text=red] {$\mpe$} (WFseq);
+\draw[arrow, bend right=45] (WFminDNE) to node[pos=0.3, left, text=red] {$\mpe$} (WFseq);
 \draw[arrow, bend right] (WFminDNEM) to node[left, text=red] {$\FB$} (WFaccM);
@@
 
-\draw[arrow, dashed, bend left=80, blue] (WFCor) to node[left, text=blue] {$\accCor$} (WFacc);
+\draw[arrow, bend left=80] (WFCor) to node[pos = 0.4, left, text=red] {$\accCor$} (WFacc);
 
@@
 \caption{The logical relationships between notions of well-foundedness}
- \label{fig:WF2} 
+ \label{fig:WF}
 \end{figure}
-\clearpage
+% \clearpage
 
-All of the above definitions of well-foundedness are classically equivalent.
-But constructively, the only provable equivalence is between the inductive and accessible 
-formluations (reflecting the fact that accessibility is defined as the least inductive predicate).
-Formalizing the remaining implications enabled us to identify where exactly classical logic 
-is used, and how much of it is truly needed.
-
-The logical relationships between the various definitions are summarized in Figure \ref{fig:WF}.
-An arrow from one node to another with no label indicates direct logical implication,
-provable constructively with no additional assumptions. An arrow with a label indicates an additional 
-(semi-)classical hypothesis needed to establish the implication. 
-The definitions of these hypotheses are given in Figure \ref{tab:cprop}.
-All of the implications have been 
-formalized within the WellFounded subdirectory of the Agda repository.
+% All of the above definitions of well-foundedness are classically equivalent.
+% But constructively, the only provable equivalence is between the inductive and accessible
+% formluations, reflecting the fact that accessibility is defined as the least inductive predicate.
+% Formalizing the remaining implications enabled us to identify where exactly classical logic
+% is used, and how much of it is truly needed.
 
@@
 
-\apcomment{Make another version of the diagram, swapping WFmin and WFacc rows.}
-
 % The principles appearing in the labels of Figure \ref{fig:WF} are valid for many rewriting systems,
 % and are classically true.
-Figure \ref{tab:cprop} illustrates that the network of logical relationships between
+Figure \ref{fig:WF} illustrates that the network of logical relationships between
 constructive notions of well-foundedness is quite rich indeed.
 Taking the $\lnot\lnot$-closures of
-well-foundedness properties cuts down some, but not all, of the complexity.
+these notions cuts down some, but not all, of the complexity.
 For example, the two minimality principles become equivalent.
@@
   \item Assuming $\accCor$, $\isWFacc$ can also be derived from $\WFcor$. % , the stronger version of $\WFcorm$.
-    \apcomment{Add the ``is''!}
+    \apcomment{Remove the ``is''!}
 
-    (This is analogous to how $\isWFminDNE$ is a natural weakening of 
+    \apcomment{Remove?} (This is analogous to how $\isWFminDNE$ is a natural weakening of
     $\isWFmin$ that is sufficient to recover $\isWFacc$ in the presence of {$\accDNE$}.)
@@
   quantification over all predicates on $A$.  (This defect is also present in $\isWFmin$, $\isWFminDNE$, and \texttt{isWFcor}.)
-
-In \cite{Terese}, well-foundedness is defined as in the classical mathematics textbooks,
-as the absence of an infinite $R$-decreasing sequence.
-(Again, well-foundedness of $R$ corresponds to strong normalization of its converse.)
-\apcomment{Add a discussion about isWFseq- vs. isWFseq$\lnot\lnot$.}
-
-We consider $\isWFacc$ the canonical constructive definition of a well-founded relation.
 

### 2025-10-24 Relations/Paper/Well-foundedness.tex
Minor fixes to WF

@@
 
-In \cite{Terese}, the $\WFseqm$ definition is used, as in the classical mathematics textbooks.  This definition appears to be strictly weaker than
-WFseqm-not-not, asserting that every sequence not-not contains a
+In \cite{Terese}, the $\WFseqm$ definition is used, as in the classical mathematics textbooks.
+Constructively, this is not a useful definition, as it does not provide any positive computational content and requires an explicit sequence to be defined.
+This definition appears to be strictly weaker than
+$\WFseqnn$, asserting that every sequence not-not contains a
 non-decreasing index.
-\apcomment{fix the macro please!}
+
 % \apcomment{Perhaps we should have a separate discussion between isWFseq- and isWFseq-not-not?}
@@
 
+\begin{figure}[h]
+\centering
+\begin{tikzpicture}[
+  scale=0.6,
+  every node/.style={transform shape},
+  node distance=1cm and .5cm,
+  box/.style={draw, rectangle, rounded corners, minimum width=1cm, minimum height=1cm, align=center},
+  arrow/.style={-{Latex}, thick}
+]
+
+% Row 1: Basic definitions
+\node[box] (WFmin) {$\WFmin$};
+\node[box, right=2.9cm of WFmin] (WFminDNE) {$\WFminDNE$};
+\node[box, right=2.9cm of WFminDNE, line width = 0.5mm] (WFacc) {$\WFacc$};
+\node[box, right=2.9cm of WFacc] (WFseq) {$\WFseq$};
+\node[box, right=2.9cm of WFseq] (WFCor) {$\WFcor$};
+
+% Row 2: Weak definitions
+\node[box, below=2cm of WFmin] (WFminM) {$\WFminm$};
+\node[box, below=2cm of WFminDNE] (WFminDNEM) {$\WFminDNEm$};
+\node[box, below=2cm of WFacc] (WFaccM) {$\WFaccm$};
+\node[box, below=2cm of WFseq] (WFseqM) {$\WFseqm$};
+\node[box, below=2cm of WFCor] (WFminCor) {$\WFcorm$};
+
+% Arrows within rows
+\draw[arrow] (WFmin) -- (WFminDNE);
+\draw[arrow, bend left=45] (WFmin) to (WFseq);
+
+\draw[arrow] (WFminM) -- (WFminDNEM);
+\draw[arrow, bend right=45] (WFminM) to (WFaccM);
+\draw[arrow] (WFaccM) -- (WFseqM);
+\draw[arrow, bend right=45] (WFaccM) to (WFminDNEM);
+\draw[arrow, bend right=45] (WFminDNEM) to (WFminM);
+\draw[arrow, bend right=45] (WFminDNEM) to (WFseqM);
+\draw[arrow] (WFseqM) -- (WFminCor);
+
+% Inter-row arrows
+\draw[arrow] (WFmin) -- (WFminM);
+\draw[arrow] (WFminDNE) -- (WFminDNEM);
+\draw[arrow] (WFacc) -- (WFaccM);
+\draw[arrow] (WFseq) -- (WFseqM);
+\draw[arrow] (WFCor) -- (WFminCor);
+
+% Additional labeled arrows
+\draw[arrow] (WFminDNEM) to node[above, text=red] {$\FB$} (WFaccM);
+\draw[arrow, bend right=45] (WFminCor) to node[above, text=red] {$\mpe$} (WFseqM);
+\draw[arrow, bend right=45] (WFCor) to node[above, text=red] {$\accCor$} (WFacc);
+\draw[arrow] (WFminDNE) to node[below, text=red]{$\accDNE$} (WFacc);
+\draw[arrow, bend left = 45] (WFminDNE) to node[below, text=red]{$\mpe$} (WFseq);
+\draw[arrow, bend right = 45] (WFminCor) to node[right, text=red]{$\corDNE$} (WFCor);
+\draw[arrow, bend right = 45] (WFaccM) to node[right, text=red]{$\accDNE$} (WFacc);
+\draw[arrow] (WFacc) to node[below, text=red]{$\rdec$} (WFseq);
+\draw[arrow, bend left=45] (WFminCor) to node[below, text=red]{$\accCor$} (WFaccM);
+
+\end{tikzpicture}
+\caption{The logical relationships between notions of well-foundedness}
+\label{fig:WF2}
+\end{figure}
+
 % All of the above definitions of well-foundedness are classically equivalent.
@@
 }
-
+\clearpage
 % The principles appearing in the labels of Figure \ref{fig:WF} are valid for many rewriting systems,
@@
 Other observations that can be gleaned from the figure include the following.
-\apcomment{The macros have to fixed throughout.}
 \begin{enumerate}
-  \item The implication from $\isWFacc$ to $\isWFseq$ requires the underlying relation to be decidable.
+  \item The implication from $\WFacc$ to $\WFseq$ requires the underlying relation to be decidable.
     This assumption is no longer necessary on the $\lnot\lnot$-translated side.
-  \item WFmin is a very strong assumption and implies WFseq unconditionally.
-  The more reasonable WFminDNE requires the image of every sequence to be $\lnot\lnot$-closed
+  \item $\WFmin$ is a very strong assumption and implies $\WFseq$ unconditionally.
+  The more reasonable $\WFminDNE$ requires the image of every sequence to be $\lnot\lnot$-closed
   to complete the implication.  This condition can be considered as a special case of Markov's Principle
   (if one assumes that equality on $A$ is decidable).
-  \item On the $\lnot\lnot$-side, WFmin- and WFminDNE- are equivalent, are directly implied by $\isWFaccm$,
-    and directly imply $\isWFseqm$  \apcomment{Fix macros}.
-  \item All definitions imply $\WFcorm$.  This weakest definition implies $\isWFaccm$ assuming the
+  \item On the $\lnot\lnot$-side, $\WFminm$ and $\WFminDNEm$ are equivalent. Both are directly implied by $\WFaccm$,
+    and all three directly imply $\WFseqm$.
+  \item All definitions imply $\WFcorm$.  This weakest definition implies $\WFaccm$ assuming the
     ``constructive contrapositive of accessibility'', $\accCor$.
     %While this condition is implied by $\isWFseqm$, it does not appear to imply anything on its own.
-  \item Assuming $\accCor$, $\isWFacc$ can also be derived from $\WFcor$. % , the stronger version of $\WFcorm$.
-    \apcomment{Remove the ``is''!}
+  \item Assuming $\accCor$, $\WFacc$ can also be derived from $\WFcor$. % , the stronger version of $\WFcorm$.
 
-    \apcomment{Remove?} (This is analogous to how $\isWFminDNE$ is a natural weakening of
-    $\isWFmin$ that is sufficient to recover $\isWFacc$ in the presence of {$\accDNE$}.)
+    % \apcomment{Remove?} (This is analogous to how $\isWFminDNE$ is a natural weakening of
+    % $\isWFmin$ that is sufficient to recover $\isWFacc$ in the presence of {$\accDNE$}.)
 
-  \item At the same time, if the relation is finitely branching ($\FB$), then WFminDNE-
-    implies WFacc- directly.
+  \item At the same time, if the relation is finitely branching ($\FB$), then $\WFminDNEm$
+    implies $WFaccm$ directly.
 
@@
 %   we cannot, in general, conclude it is coreductive.
-  \item \apcomment{Delete? In general, the coreductive properties speak to the ability to choose
-  a successor (strong existence).  This ability is central to being able to
-  define sequences.  Therefore, sequential definitions generally require
-some coreductive situation to be applicable.}
+%   \item \apcomment{Delete? In general, the coreductive properties speak to the ability to choose
+%   a successor (strong existence).  This ability is central to being able to
+%   define sequences.  Therefore, sequential definitions generally require
+% some coreductive situation to be applicable.}
 
@@
   the inductive well-foundedness property lands in the larger universe $\mathtt{Set}_1$, due to
-  quantification over all predicates on $A$.  (This defect is also present in $\isWFmin$, $\isWFminDNE$, and \texttt{isWFcor}.)
+  quantification over all predicates on $A$.  (This defect is also present in $\WFmin$, $\WFminDNE$, and \texttt{WFcor}.)
 
@@
 Constructively, this is not a useful hypothesis, as it does not provide any positive computational content and requires an explicit sequence to be defined.
+\sacomment{This sentence added into where we discuss wfseq- as being the textbook definition.
+Can now be deleted here.}
 
@@
 These two conditions are classically equivalent, but not constructively so.
-Indeed, $\isWFseq$ certainly implies $\isWFseqm$, but the converse only holds classically.
+Indeed, $\isWFseq$ certainly implies $\isWFseqm$, but the converse only holds classically. \sacomment{We say this through the figure and so can delete it?}
 
@@
 While classically equivalent to the previous one, see \cite[Exercise A.1.8]{Terese},
-constructively we only have the implication $\isWFmin \then \isWFseq$.
+constructively we only have the implication $\isWFmin \then \isWFseq$. \sacomment{Again, this is covered by our new definitions and figure and can be deleted.}
 
@@
 \verb|_isWFacc| as \emph{the} standard notion of well-foundedness for relations.
+\sacomment{We don't talk about which proof is easier to write in Agda, but I don't think we need to include this discussion.
+I suggest we delete.}
 
@@
 For example, the archetype of a well-founded relation is the strict order \verb|<|
-of natural numbers.  The usual induction readily validates $\isWFacc$ for \verb|<|.
+of natural numbers.  The usual induction readily validates $\WFacc$ for \verb|<|.
   At the same time, the file \texttt{WFCounters.agda} shows that
-asserting $\isWFmin$ for \verb|<| implies that every subset of the natural numbers is decidable.  Since this is clearly not provable in Agda without classical axioms,
-this argument shows that the implication from $\isWFacc$ to $\isWFmin$ is not provable.
+asserting $\WFmin$ for \verb|<| implies that every subset of the natural numbers is decidable.  Since this is clearly not provable in Agda without classical axioms,
+this argument shows that the implication from $\WFacc$ to $\WFmin$ is not provable.
 
@@
 
-On the other hand, $\isWFmin$ trivially implies that each $x \in A$ is weakly normalizing.
+On the other hand, $\WFmin$ trivially implies that each $x \in A$ is weakly normalizing.
 Indeed, given $x \in A$, consider the predicate $P_x(y) = x \mstep y$.
@@
 network of relations.  %These are displayed in Figure \ref{f:wf}.
-These are recorded in the file \verb|Wellfounded.agda|
+These are recorded in the file \verb|Wellfounded.agda| /sacomment{Which file do we now want to refer to here. Or just refer to the entire subfolder?}
 

### 2025-10-24 Relations/Paper/Summer_2025_TODO.tex

@@
 
-\section*{October 15th TODO}
+\section*{October 15th TODO / Oct 22nd}
 \begin{todolist}     
@@
   \item Check through the comments in general in the section. 
+  \item (Long term) Investigate: what we've done for natural numbers could be done for an arbitrary ARS (in the counter examples files).
+The sentence: ''The restriction to $\lnot\lnot$-closed subsets implies (and is equivalent to)
+every subset $P$ being merely \emph{weakly} decidable (satisfying $\lnot \lnot P(x) \lor \lnot P(X)$ 
+for all $x$)'' needs further exploration. We could not say it/say it differently. 
+\item CHange WFseq not not to WFseq- in the macro. We are sticking with this for now. If we have time we can investigate the relation between the two.
+\item Make the diagram horizontal rather than vertical. Spoof it up and we can compare next week.
+\item Use of macros ni WF section. Double check the right one is being used. Don't use the "is'' macro at all in this section. Be consistent on whether we are using macros. 
 \item 
@@
 
+\section*{Plan for PLDI submission}
+\begin{todolist}
+  \item Aim for first draft finished by the end of the 29th.
+  \item Make a new branch at this point to conform to this conference's style?
+  \item Submission deadline is Thursday 13th 
+  \item Once we've got a current draft finished. Look in Teresa for first order term rewrite systems and see how many we can represent using our code.
+\end{todolist}
+
 \end{document}

### 2025-10-24 Relations/Paper/WF_potential_update.tex

--- 2025-08-06 Relations/Paper/WF_diagram.tex
@@
 
+\begin{figure}[ht]
+\centering  
 \begin{tikzpicture}[
@@
 \draw[arrow, bend right] (WFminCor) to node [right, text=red] {MP$\equiv$} (WFseqM);
+\draw[arrow] (WFCor) -- (WFminCor);
+\draw[arrow, bend left = 110] (WFCor) to node[left, text=red] {AccCor} (WFacc);
+\draw[arrow, bend left = 80, color=blue] (WFmin) to node[right, text=blue, pos=0.75] {corDNE} (WFCor);
 
 \end{tikzpicture}
+\caption{The logical relationships between notions of well-foundedness}
+ \label{fig:WF} 
+\end{figure}
+\clearpage
 

### 2025-10-24 Relations/Paper/Well-foundedness.tex

@@
 \draw[arrow] (WFmin) -- (WFminDNE);
-\draw[arrow, bend left=45] (WFmin) to (WFseq);
+\draw[arrow, bend left=25] (WFmin) to (WFseq);
 
 \draw[arrow] (WFminM) -- (WFminDNEM);
-\draw[arrow, bend right=45] (WFminM) to (WFaccM);
 \draw[arrow] (WFaccM) -- (WFseqM);
-\draw[arrow, bend right=45] (WFaccM) to (WFminDNEM);
-\draw[arrow, bend right=45] (WFminDNEM) to (WFminM);
-\draw[arrow, bend right=45] (WFminDNEM) to (WFseqM);
+\draw[arrow, bend right=35] (WFaccM) to (WFminDNEM);
+\draw[arrow, bend right=35] (WFminDNEM) to (WFminM);
+\draw[arrow, bend right=25] (WFminDNEM) to (WFseqM);
 \draw[arrow] (WFseqM) -- (WFminCor);
@@
 \draw[arrow] (WFminDNEM) to node[above, text=red] {$\FB$} (WFaccM);
-\draw[arrow, bend right=45] (WFminCor) to node[above, text=red] {$\mpe$} (WFseqM);
-\draw[arrow, bend right=45] (WFCor) to node[above, text=red] {$\accCor$} (WFacc);
+\draw[arrow, bend right=35] (WFminCor) to node[above, text=red] {$\mpe$} (WFseqM);
+\draw[arrow, bend right=25] (WFCor) to node[above, text=red] {$\accCor$} (WFacc);
 \draw[arrow] (WFminDNE) to node[below, text=red]{$\accDNE$} (WFacc);
-\draw[arrow, bend left = 45] (WFminDNE) to node[below, text=red]{$\mpe$} (WFseq);
+\draw[arrow, bend left = 25] (WFminDNE) to node[below, text=red]{$\mpe$} (WFseq);
 \draw[arrow, bend right = 45] (WFminCor) to node[right, text=red]{$\corDNE$} (WFCor);
@@
 \draw[arrow] (WFacc) to node[below, text=red]{$\rdec$} (WFseq);
-\draw[arrow, bend left=45] (WFminCor) to node[below, text=red]{$\accCor$} (WFaccM);
+\draw[arrow, bend left=25] (WFminCor) to node[below, text=red]{$\accCor$} (WFaccM);
 
@@
     %While this condition is implied by $\isWFseqm$, it does not appear to imply anything on its own.
-  \item Assuming $\accCor$, $\WFacc$ can also be derived from $\WFcor$. % , the stronger version of $\WFcorm$.
+
+    With this assumption, $\WFacc$ can also be derived from $\WFcor$. % , the stronger version of $\WFcorm$.
 
@@
 
-  \item At the same time, if the relation is finitely branching ($\FB$), then $\WFminDNEm$
-    implies $WFaccm$ directly.
+  \item If the relation is finitely branching ($\FB$), then $\WFminDNEm$
+    implies $\WFaccm$ directly.
 
@@
 We also did not include the inductive definition, Definition \ref{def:WFproperties}.\ref{def:WFind}.
-  Logically, it is trivially equivalent to the accessible one, but its Agda formulation has a defect:
+  Logically, it is trivially equivalent to the accessible one, but its Agda formalization has a defect:
   the inductive well-foundedness property lands in the larger universe $\mathtt{Set}_1$, due to
-  quantification over all predicates on $A$.  (This defect is also present in $\WFmin$, $\WFminDNE$, and \texttt{WFcor}.)
+  quantification over all predicates on $A$.  This defect is also present in $\WFmin$, $\WFminDNE$,
+  and $\WFcor$.
 
@@
 
-\subsection{Old. Delete?}
+\subsection{Well-foundedness and rewriting}
 
-Translating this statement directly into type theory yields the formula
+One may wonder whether the difference between the various definitions above matters for 
+rewriting theory.  In particular, how often are the properties listed in 
+Figure \ref{tab:cprop} actually valid for a given rewrite system, so that its termination 
+($\WFacc$) could be inferred from a weaker statement, such as $\WFminDNEm$?
 
-\[\tag{$\isWFseqm$} \lnot \big(\exists s : \nat \to A \forall k : \nat. \  R \,(s\,(k+1)) \, (s\, k) \big) \]
+On the one hand, \cite{Berardi} proves a general result to the effect that
+$\accDNE$ is valid \emph{metatheoretically} for a large class of definable relations.
+Specifically, if $R$ is a primitive recursive predicate on the natural numbers and
+$\WFaccm(R)$ can be proved in higher-order arithmetic, then an intuitionistic proof 
+of $\WFacc(R)$ is also possible.
+% situation of separating these notions is complicated by the fact that, for all
+% \emph{definable} predicates, the classical and constructive notions do coincide.
+% (We have not proved this, but see \cite{Berardi} for a related result.)
+So there is little hope of distinguishing between these notions via an explicit counterexample.
 
-(The label $\isWFseqm$ refers to the name of the corresponding term in \texttt{Wellfoundedness.agda}.)
-Constructively, this is not a useful hypothesis, as it does not provide any positive computational content and requires an explicit sequence to be defined.
-\sacomment{This sentence added into where we discuss wfseq- as being the textbook definition.
-Can now be deleted here.}
-
-A stronger formulation asserts that, for any sequence, there exists an element
-in the sequence that does not reduce to the next one.  This yields the statement
-\[\tag{$\isWFseq$} \forall s : \nat \to A \exists k : \nat.\, \lnot \, R \,(s\,k)\,(s\,(k+1)) \]
-
-These two conditions are classically equivalent, but not constructively so.
-Indeed, $\isWFseq$ certainly implies $\isWFseqm$, but the converse only holds classically. \sacomment{We say this through the figure and so can delete it?}
-
-Another classical formulation of well-foundedness
-asserts that every non-empty subset
-contains a minimal element.  That is,
-\[ \tag{$\isWFmin$} \forall P \subseteq A. P \neq \emptyset \to \exists x \in P. (\forall y. Ryx \to y\notin P) \]
-
-While classically equivalent to the previous one, see \cite[Exercise A.1.8]{Terese},
-constructively we only have the implication $\isWFmin \then \isWFseq$. \sacomment{Again, this is covered by our new definitions and figure and can be deleted.}
-
-The canonical constructive definition of well-foundedness is that
-every inductive predicate is universally true.
-This is constructively equivalent to the statement that every element
-is accessible.  In Agda, these concepts are encoded as follows.
-{\small
-\begin{verbatim}
-  _-inductive_ : 𝓟 A → Set
-  _-inductive_ φ = ∀ x → (∀ y → R y x → φ y) → φ x
-
-  _isWFind : Set₁
-  _isWFind = ∀ (φ : 𝓟 A) → _-inductive_ φ → ∀ x → φ x
-
-  data _-accessible : 𝓟 A where
-    acc : ∀ {x : A} → (∀ y → R y x → _-accessible y) → _-accessible x
-
-  _isWFacc : Set
-  _isWFacc = ∀ (x : A) → x ∈ _-accessible
-\end{verbatim}
-}
-Although the two notions are equivalent, the latter definition allows us to do induction on the proof of accessibility of an individual element $x \in A$.
-This makes such proofs easier to write in Agda, thus we take
-\verb|_isWFacc| as \emph{the} standard notion of well-foundedness for relations.
-\sacomment{We don't talk about which proof is easier to write in Agda, but I don't think we need to include this discussion.
-I suggest we delete.}
-
-\subsection{Relations between the main definitions}
-
-We have now seen five notions of a well-founded relation, only two of which
-are seen to be logically equivalent.
-
-This raises several questions.
-\begin{itemize}
-\item Are all these notions truly distinct?  If one cannot furnish a proof of implication,
-can we provide a counterexample?
-\item Under what hypotheses do the implications become provable?
-\item How ``admissible'' are such hypotheses, and how often can we hope for them to be valid?
-\end{itemize}
-
-The situation of separating these notions is complicated by the fact that, for all
-\emph{definable} predicates, the classical and constructive notions do coincide.
-(We have not proved this, but see \cite{Berardi} for a related result.)
-So there is no hope to discriminate these notions via explicit counterexamples.
-Rather, we could attempt to show that one does not imply the other by proving that
-such an implication would yield a ``constructive taboo'': a proposition known to be
-unprovable without additional classical assumptions.
-
+On the other hand, some of these properties could be discriminated
+by showing that an implication between them yields a ``constructive taboo'':
+a proposition known to be unprovable without additional classical assumptions.
 For example, the archetype of a well-founded relation is the strict order \verb|<|
-of natural numbers.  The usual induction readily validates $\WFacc$ for \verb|<|.
+on the natural numbers.  The usual induction readily validates $\WFacc$ for \verb|<|.
   At the same time, the file \texttt{WFCounters.agda} shows that
-asserting $\WFmin$ for \verb|<| implies that every subset of the natural numbers is decidable.  Since this is clearly not provable in Agda without classical axioms,
-this argument shows that the implication from $\WFacc$ to $\WFmin$ is not provable.
+asserting $\WFmin$ for \verb|<| implies that every subset of the natural numbers is decidable.
+Since this is clearly not provable in Agda without classical axioms,
+this argument shows that the implication from $\WFacc$ to $\WFmin$ is not provable either.
 
 Such distinctions have consequences for rewriting theory.
-For example, $x\in \SN_R$ iff $x$ is $\bar{R}$-accessible (where $\bar{R}$ denotes
-the converse of $R$).  Thus, if $\bar{R}$ is well-founded, $R \models \gSN$.
+For example, recall that $x\in \SN_R$ iff $x$ is $\bar{R}$-accessible, where $\bar{R}$ 
+is the converse of $R$.  Thus, if $\bar{R}$ is well-founded, $R \models \gSN$.
 Yet actually computing the normal form of a given $x$ seems to require a
@@
 \]
-(Note that asking whether $x$ is a normal form constitutes the weaker disjunction
-$\lnot\lnot\left(\exists y. Ryx\right) \lor \left(\forall y. \lnot Ryx\right)$.)
+This is weaker than deciding whether $x$ is a normal form:
+% Note that deciding whether $x$ is a normal form constitutes the weaker disjunction
+$\lnot\lnot\left(\exists y. Ryx\right) \lor \left(\forall y. \lnot Ryx\right)$.
 
@@
 
+Combined with the natural numbers example in \texttt{WFCounters.agda}, this shows
+that the intuitive implication $\SN_R \to \WN_R$ is not actually intuitionistically valid.
+
 % \greyout{From the perspective of rewriting theory, it would seem wild indeed if
@@
 %
-These questions motivated us to take a closer look at the issue of well-foundedness.
-Our analysis revealed a number of additional related hypotheses, having a complex
-network of relations.  %These are displayed in Figure \ref{f:wf}.
-These are recorded in the file \verb|Wellfounded.agda| /sacomment{Which file do we now want to refer to here. Or just refer to the entire subfolder?}
+% These questions motivated us to take a closer look at the issue of well-foundedness.
+% Our analysis revealed a number of additional related hypotheses, having a complex
+% network of relations.  %These are displayed in Figure \ref{f:wf}.
+% These are recorded in the file \verb|Wellfounded.agda| /sacomment{Which file do we now want to refer to here. Or just refer to the entire subfolder?}
+%
 

### 2025-10-29 Relations/Paper/Summer_2025_TODO.tex
Bold font for WF macros

@@
   \item Do a final read through of the information below the figure. Have we captured all the most important information / Are we repeating ourselves?
-  \item Do we want to keep anything in the old/delete section of WF?
+  \item [\done] Do we want to keep anything in the old/delete section of WF?
   \item Do we want to add anything about counter examples or positive examples? 
   \item We may want to use words rather than macros in certain locations
-  \item Check through the comments in general in the section. 
+  \item [\done] Check through the comments in general in the section. 
   \item (Long term) Investigate: what we've done for natural numbers could be done for an arbitrary ARS (in the counter examples files).
@@
 for all $x$)'' needs further exploration. We could not say it/say it differently. 
-\item CHange WFseq not not to WFseq- in the macro. We are sticking with this for now. If we have time we can investigate the relation between the two.
-\item Make the diagram horizontal rather than vertical. Spoof it up and we can compare next week.
-\item Use of macros ni WF section. Double check the right one is being used. Don't use the "is'' macro at all in this section. Be consistent on whether we are using macros. 
-\item 
+\item [\done]  CHange WFseq not not to WFseq- in the macro. We are sticking with this for now. If we have time we can investigate the relation between the two.
+\item [\done]  Make the diagram horizontal rather than vertical. Spoof it up and we can compare next week.
+\item [\done]  Use of macros in WF section. Double check the right one is being used. Don't use the "is'' macro at all in this section. Be consistent on whether we are using macros. 
+\item Does WFseq- with MP== imply WFseq? (W're thinking it will need rdec as well to give us the implication).
+\item make the WF macro bold font?
+\item add wfseq not not to the definitions?
+\item [\done] Go through the bibliography links. Not all of them are currently working!
+\item We want to start looking at examples.
+What we want to know is whether a first order rewrite system with some minimal properties implies some of our classical properties.
+E.g.
+lambda calculus satisfies some of our classical properties.
+As does first order term rewrite system.
+Follow up question: how big of an issue is it that accCor is not provable?
+Can we prove is isn't satisfied?
+\item Make a connection in the final WF section talking about how SN doesn't imply WN constructively. (we've started writing this sentence). 
+\item We may need to add to the WFCounters file, if we have SN implies WN then every subset of the natural numbers is decidable.  
 \end{todolist}

### 2025-10-29 Relations/Paper/Summer_2025_TODO.tex
todo update prior to session

@@
   \item Do we want to add anything about counter examples or positive examples? 
-  \item We may want to use words rather than macros in certain locations
+  \item [\done] We may want to use words rather than macros in certain locations
   \item [\done] Check through the comments in general in the section. 
@@
 \item Does WFseq- with MP== imply WFseq? (W're thinking it will need rdec as well to give us the implication).
-\item make the WF macro bold font?
+\item [\done] make the WF macro bold font?
 \item add wfseq not not to the definitions?
@@
 Can we prove is isn't satisfied?
-\item Make a connection in the final WF section talking about how SN doesn't imply WN constructively. (we've started writing this sentence). 
+\item [\done] Make a connection in the final WF section talking about how SN doesn't imply WN constructively. (we've started writing this sentence). 
 \item We may need to add to the WFCounters file, if we have SN implies WN then every subset of the natural numbers is decidable.  
@@
   \item Aim for first draft finished by the end of the 29th.
-  \item Make a new branch at this point to conform to this conference's style?
+  \item Make a main file at this point to conform to this conference's style. Possibly a sub-folder for each conference.
   \item Submission deadline is Thursday 13th 

### 2025-10-29 Relations/Paper/Introduction.tex
Renamed implications section to hierarchy. Updated hierarchy section.
Intro update

@@
 Curry--Howard isomorphism, which Agda implements.  Proofs in this language
-are automatically effective, and implicitly carry the code implementing the
-transformations from the hypotheses to the conclusion.  For example,
-a proof that a given TRS is terminating automatically renders a function that
-computes a normal form of any term in its domain.
+are automatically effective, and implicitly carry the code that implements
+a transformation from the hypotheses to the conclusion of the claim.  For example,
+a type-checked proof that a given TRS is confluent automatically renders a function that
+computes a common reduct between any two reducts of a given term.
 
@@
 with conversion generated by a confluent and terminating rewriting system
-${\cdot}{\to_R}{\cdot} : S^* \to S^* \to \bset$.
+$\to_R : S^* \to S^* \to \bset$.
 Then one can replace $S^*/{\approx_T}$ by the type of $R$-normal forms.
-(In the semiring example, these would be appropriately sorted polynomial expressions.)
+(In the semiring example, these would be polynomial expressions sorted according to 
+an appropriate ordering on monomials.)
 This can be defined as a pure dependent type
@@
   \item Minimize the use of classical logic, and make decidability hypotheses explicit in every place where classical logic could not be avoided;
-  \item Stay as faithful as possible to the spirit of type theory based on the Curry--Howard isomorphism, so that in every explicit application, our proofs would compute.
+  \item Stay as faithful as possible to the spirit of type theory based on the Curry--Howard isomorphism, so that in every concrete application, our proofs would compute.
 \end{itemize}
@@
 
-Since Strong Normalization is a central concept in ARS theory,
-special attention in our work was given to various incarnations of the concept of well-foundedness in the constructive context.
-(Strong normalization is well-foundedness of the converse relation.)
-The standard constructive definition does not even allow one to show that SN implies WN, as we discuss in Section \ref{sec:Well-foundedness} and formalize in \texttt{WFCounters.agda}.
-  We therefore looked at a number of variations of this notion, their classical counterparts all being logically equivalent. %This gave rise to a rich set of concepts, see Figure \ref{f:wf}.
+Recall that a relation is strongly normalizing iff its converse is well-founded. \cite[Def.1.1.13]{Terese}.
+Since normalization is a central concept in ARS theory,
+we pay special attention to the concept of well-foundedness.
+The standard constructive definition does not even allow one to show that SN implies WN, 
+as we discuss in Section \ref{sec:Well-foundedness} and formalize in \texttt{WFCounters.agda}.
+We therefore looked at a number of variations of this notion in the constructive context, 
+their classical counterparts all being logically equivalent. %This gave rise to a rich set of concepts, see Figure \ref{f:wf}.
 
@@
 These properties fit naturally within the rewriting paradigm.
-Thus in Section \ref{sec:Implications}, we dedicate some effort to investigating them further.
+Thus in Section \ref{sec:Hierarchy}, we dedicate some effort to investigating them further.
 The result is a broader ontology of ARS concepts, revealing interrelationships between conditions for completeness.

### 2025-11-03 Relations/Paper/Main.tex
remove todo from main
Todos started and simple fixes made.
section 2
Updated bibliography
Changes from last meeting and minor edits.
Finished section 5

@@
 % \usepackage[dvipsnames]{xcolor}
+\newtheorem{notation}[theorem]{Notation}
 
@@
 
-\keywords{Abstract rewriting, Formalization, Confluence, Strong normalization, Newman's Lemma} %TODO mandatory; please add comma-separated list of keywords
+\keywords{Abstract rewriting, Formalization, Confluence, Strong normalization, Newman's Lemma, Well-foundedness} %TODO mandatory; please add comma-separated list of keywords
 
-\supplement{https://github.com/DrPolonsky/LAM//tree/main/ARS}% TODO: set a repo just for this submissionoptional, e.g.
-related research data, source code, ...
-hosted on a repository like zenodo, figshare, GitHub, ...
+\supplement{https://github.com/DrPolonsky/FPLA/tree/main}
 
+\renewcommand\eminnershape{\bfseries}
 \begin{document}
@@
       generalizations of classical termination and confluence criteria.
+      Finally, we investigate logical relationships between several notions of termination, 
+      arising from different formulations of the concept of a well-founded relation.
     \end{abstract}
@@
 \input{Conclusion.tex}
-\input{FinalTODO.tex}
+% \input{FinalTODO.tex}
 
@@
     \newblock{2020}.
+    \newblock{isbn = 9798615591839}.
+    \newblock{Independently Published}.
 
-    \bibitem{Berardi}
+    \bibitem{Bezem}
     Marc Bezem, Thierry Coquand, Keiko Nakata, and Erik Parmann.
@@
 
-    \bibitem{Bezem}
+    \bibitem{Berardi}
     Stefano Berardi
@@
       \newblock{https://doi.org/10.4230/LIPIcs.CSL.2015.343}.
+
+    \bibitem{AgdaLibraryList}
+    Agda Standard Library: List 
+    \newblock{https://agda.github.io/agda-stdlib/v2.2/Agda.Builtin.List.html}
+    \newblock{Accessed: 8th July 2025}
 

### 2025-11-05 Relations/Paper/Introduction.tex
Macro update, related works added to intro, main bibliography update.

@@
 Our contributions are as follows.
-\begin{itemize}
+\begin{enumerate} \label{list:ourContributions}
   \item Formalization of elementary ARS theory as presented in
-  \cite{Terese}, including relevant background;
+  \cite{Terese}, including relevant background; \sacomment{Should we remove this contribution as it is provided already in the agda standard library?}
   % Chapter 1 of
@@
   in the constructive setting.
-\end{itemize}
+\end{enumerate}
+
+\subsection{Related works}
+% We should cover the following in this section:
+% \begin{itemize}
+%   \item The IsaFoR/CeTA tool for certification of termination/confluence proofs provided by some automated tool (http://cl-informatik.uibk.ac.at/software/ceta/#introduction).
+Specifically this paper (https://www.isa-afp.org/entries/Abstract-Rewriting.html) deals with the formalization of strong normalization and Neman's lemma as part of the CeTA project.
+They use Isabelle for their formalization.
+%   \item This termination portal which gives an overview of various termination tools: https://termination-portal.org/wiki/Termination_Portal.
+Specifically here is a list of different termination tools: https://termination-portal.org/wiki/Category:Tools .
+We should talk about what distinguishes our project from a termination tool.
+%   \item Similarly this project is a collection of formalizations of theorems related to term rewrite systems in the language of the proof assistant PVS.
+http://trs.cic.unb.br/ (here is the formalization of Newman's lemma if you're interested!
+https://github.com/nasa/pvslib/blob/master/TRS/newman_yokouchi.pvs).
+%   \item Can nention that the agda standard library has a rewriting formalization too based on TeReSe
+% \end{itemize}
+Several formalizations of elementary ARS theory exist, including projects in Isabelle \cite{isabelleFormalization}, PVS \cite{trs}, and Coq \cite{coqARS}, as well as the Agda standard library \cite{AgdaLibraryRewriting}.
+Our work distinguishes itself through contributions 2-5 above: the detailed ontology of termination and confluence properties, new ARS concepts, refinements to classical criteria, and  examining multiple notions of well-foundedness.
 

### 2025-11-05 Relations/Paper/Main.tex
Macro update, related works added to intro, main bibliography update.

@@
 
+    \bibitem{AgdaLibraryRewriting}
+    Agda Standard Library: Rewriting 
+    \newblock{https://agda.github.io/agda-stdlib/v1.7.3/Relation.Binary.Rewriting.html}
+    \newblock{Accessed: 5th November 2025}
+
+    \bibitem{isabelleFormalization}
+    Christian Sternagel and René Thiemann
+    \newblock{https://www.isa-afp.org/entries/Abstract-Rewriting.html}
+    \newblock{Accessed: 5th November 2025}
+
+    \bibitem{trs}
+    André Galdino, Mauricio Ayala-Rincón
+    \newblock{http://trs.cic.unb.br/}
+    \newblock{Accessed: 5th November 2025}
+
+    \bibitem{coqARS}
+
+    BLANQUI, FRÉDÉRIC, and ADAM KOPROWSKI. 
+    \newblock{“CoLoR: A Coq Library on Well-Founded Rewrite Relations and Its Application to the Automated Verification of Termination Certificates.”}
+    \newblock{Mathematical Structures in Computer Science 21, no. 4 (2011): 827–59.}
+    \newblock{https://doi.org/10.1017/S0960129511000120.}
+
 \end{thebibliography}

### 2025-11-05 Relations/Paper/Summer_2025_TODO.tex
todo update
Macro update, related works added to intro, main bibliography update.

@@
 \item We may need to add to the WFCounters file, if we have SN implies WN then every subset of the natural numbers is decidable.  
+\item Make sure we have a proof of the implication from SN to WN given FB and decidability of a relation (to back up our claim in our introduction).
+\item check TERESE and see first order term rewrite systems example which could be valid for showing classical and constructive formalization coincide.
+First order term rewrite systems are (always?) fb and R is dec.
+\item [\done] Change the macro for FB so that it is also boldface
+\item from wellfounded extra move the implication of fb -> isdec -> isMinDec. move to implications. 
+Use this to take this SNdec→WN to have a full proof from fb, isdec, sn -> wn. (issue in moving to fb file due to reversal of relation direction!)
 \end{todolist}

### 2025-11-05 Relations/Paper/Introduction.tex
Fixing urls

@@
 \begin{enumerate} \label{list:ourContributions}
-  \item Formalization of elementary ARS theory as presented in
-  \cite{Terese}, including relevant background; \sacomment{Should we remove this contribution as it is provided already in the agda standard library?}
+  \item An original formalization of elementary ARS theory as presented in
+  \cite{Terese}, including relevant background; 
   % Chapter 1 of
@@
 % \end{itemize}
-Several formalizations of elementary ARS theory exist, including projects in Isabelle \cite{isabelleFormalization}, PVS \cite{trs}, and Coq \cite{coqARS}, as well as the Agda standard library \cite{AgdaLibraryRewriting}.
+Several formalizations of the concepts of elementary ARS theory exist, including projects in Isabelle \cite{isabelleFormalization}, PVS \cite{trs}, and Coq \cite{coqARS}, as well as the Agda standard library \cite{AgdaLibraryRewriting}.
 Our work distinguishes itself through contributions 2-5 above: the detailed ontology of termination and confluence properties, new ARS concepts, refinements to classical criteria, and  examining multiple notions of well-foundedness.

### 2025-11-05 Relations/Paper/Introduction.tex
related work and contributions merged

@@
 
-\subsection{Contributions}
-Our contributions are as follows.
-\begin{enumerate} \label{list:ourContributions}
-  \item An original formalization of elementary ARS theory as presented in
-  \cite{Terese}, including relevant background; 
+\subsection{Contributions and related works}
+Several formalizations of the concepts of elementary ARS theory exist, including projects in Isabelle \cite{isabelleFormalization}, PVS \cite{trs}, and Rocq \cite{coqARS} as well as the Agda standard library \cite{AgdaLibraryRewriting}.
+The first three are quite mature large-scale projects for certifying termination of
+general rewrite systems.  Our work is more comparable in scale to the rewriting development in the
+Agda library, and is meant to serve as a starting point for a new library of formalized
+programming language theory.  The specific contributions we provide beyond the works cited above
+are as follows.
+% Our work distinguishes itself through contributions 2-5 above: the detailed ontology of termination and confluence properties, new ARS concepts, refinements to classical criteria, and  examining multiple notions of well-foundedness.
+% Our contributions are as follows.
+\begin{itemize} \label{list:ourContributions}
+  \item An original formalization of elementary ARS theory as presented in Terese
+  \cite{Terese}, including relevant background about relations and logic;
   % Chapter 1 of
@@
   in the constructive setting.
-\end{enumerate}
+\end{itemize}
 
-\subsection{Related works}
+% \subsection{Related works}
 % We should cover the following in this section:
@@
 % \end{itemize}
-Several formalizations of the concepts of elementary ARS theory exist, including projects in Isabelle \cite{isabelleFormalization}, PVS \cite{trs}, and Coq \cite{coqARS}, as well as the Agda standard library \cite{AgdaLibraryRewriting}.
-Our work distinguishes itself through contributions 2-5 above: the detailed ontology of termination and confluence properties, new ARS concepts, refinements to classical criteria, and  examining multiple notions of well-foundedness.
 

### 2025-11-06 Relations/Paper/Formalization.tex
Typo

@@
 As outlined in the previous section, \texttt{Properties.agda}, \texttt{Seq.agda}, and \texttt{ClosureOperators.agda} define most standard termination and confluence properties.
-The file \texttt{Base.agda} introduces additional defitions which are required for the formalization of the propositions found in Chapter 1 of \terese.
+The file \texttt{Base.agda} introduces additional definitions which are required for the formalization of the propositions found in Chapter 1 of \terese.
 

### 2025-11-06 Relations/Paper/Well-foundedness.tex
Commenting out the old WF graph

@@
 
-The logical relationships between all of the above definitions are summarized in Figure \ref{fig:WF}.
+The logical relationships between all of the above definitions are summarized in Figure~\ref{fig:WF}.
 All of the implications in the figure have been
@@
 
-\begin{figure}[h]
-\centering
-\begin{tikzpicture}[
-  scale=0.7,
-  every node/.style={transform shape},
-  node distance=1cm and .5cm,
-  box/.style={draw, rectangle, rounded corners, minimum width=1cm, minimum height=1cm, align=center},
-  arrow/.style={-{Latex}, thick}
-]
+% \begin{figure}[h]
+% \centering
+% \begin{tikzpicture}[
+%   scale=0.7,
+%   every node/.style={transform shape},
+%   node distance=1cm and .5cm,
+%   box/.style={draw, rectangle, rounded corners, minimum width=1cm, minimum height=1cm, align=center},
+%   arrow/.style={-{Latex}, thick}
+% ]
 
-% Row 1: WFmin -> WFmin-
-\node[box] (WFmin) {$\WFmin$};
-\node[box, right=2.9cm of WFmin] (WFminM) {$\WFminm$};
+% % Row 1: WFmin -> WFmin-
+% \node[box] (WFmin) {$\WFmin$};
+% \node[box, right=2.9cm of WFmin] (WFminM) {$\WFminm$};
 
-\draw[arrow] (WFmin) -- (WFminM);
+% \draw[arrow] (WFmin) -- (WFminM);
 
-% Row 2: WFminDNE -> WFminDNE-
-\node[box, below=of WFmin] (WFminDNE) {$\WFminDNE$};
-\node[box, below=of WFminM] (WFminDNEM) {$\WFminDNEm$};
+% % Row 2: WFminDNE -> WFminDNE-
+% \node[box, below=of WFmin] (WFminDNE) {$\WFminDNE$};
+% \node[box, below=of WFminM] (WFminDNEM) {$\WFminDNEm$};
 
-\draw[arrow] (WFminDNE) -- (WFminDNEM);
+% \draw[arrow] (WFminDNE) -- (WFminDNEM);
 
-% Row 3: WFacc
+% % Row 3: WFacc
 
-\node[box, line width = 0.5mm, below=of WFminDNE] (WFacc) {$\WFacc$};
+% \node[box, line width = 0.5mm, below=of WFminDNE] (WFacc) {$\WFacc$};
 
-\node[box, below = of WFminDNEM] (WFaccM) {$\WFaccm$};
-\draw[arrow] (WFacc) to (WFaccM);
-\draw[arrow, bend left] (WFaccM) to node[below, text=red] {$\accDNE$} (WFacc);
+% \node[box, below = of WFminDNEM] (WFaccM) {$\WFaccm$};
+% \draw[arrow] (WFacc) to (WFaccM);
+% \draw[arrow, bend left] (WFaccM) to node[below, text=red] {$\accDNE$} (WFacc);
 
-% Row 4: WFseq
-\node[box, below=of WFacc] (WFseq) {$\WFseq$};
-\node[box, below= of WFaccM] (WFseqM) {$\WFseqm$};
+% % Row 4: WFseq
+% \node[box, below=of WFacc] (WFseq) {$\WFseq$};
+% \node[box, below= of WFaccM] (WFseqM) {$\WFseqm$};
 
-\draw[arrow] (WFseq) -- (WFseqM);
+% \draw[arrow] (WFseq) -- (WFseqM);
 
-% Row 5: WFcor
-\node[box, below=of WFseq] (WFCor) {$\WFcor$};
-\node[box, below=of WFseqM] (WFminCor) {$\WFcorm$};
+% % Row 5: WFcor
+% \node[box, below=of WFseq] (WFCor) {$\WFcor$};
+% \node[box, below=of WFseqM] (WFminCor) {$\WFcorm$};
 
-% \draw[arrow, bend left = 55] (WFaccM) to (WFminM);
+% % \draw[arrow, bend left = 55] (WFaccM) to (WFminM);
 
-% Inter-row arrows
-\draw[arrow] (WFacc) to node[right, text = red] {$\rdec$} (WFseq);
-\draw[arrow, bend right] (WFaccM) to (WFminDNEM);
-\draw[arrow, bend right = 90] (WFminCor) to node[pos = 0.4, right, text=red] {$\accCor$} (WFaccM);
+% % Inter-row arrows
+% \draw[arrow] (WFacc) to node[right, text = red] {$\rdec$} (WFseq);
+% \draw[arrow, bend right] (WFaccM) to (WFminDNEM);
+% \draw[arrow, bend right = 90] (WFminCor) to node[pos = 0.4, right, text=red] {$\accCor$} (WFaccM);
 
-\draw[arrow, bend right = 75] (WFmin) to (WFseq);
-\draw[arrow, bend left = 75] (WFminM) to (WFseqM);
-\draw[arrow] (WFaccM) -- (WFseqM);
-\draw[arrow] (WFmin) -- (WFminDNE);
-\draw[arrow, bend right] (WFminM) to (WFminDNEM);
-\draw[arrow, bend right] (WFminDNEM) to (WFminM);
+% \draw[arrow, bend right = 75] (WFmin) to (WFseq);
+% \draw[arrow, bend left = 75] (WFminM) to (WFseqM);
+% \draw[arrow] (WFaccM) -- (WFseqM);
+% \draw[arrow] (WFmin) -- (WFminDNE);
+% \draw[arrow, bend right] (WFminM) to (WFminDNEM);
+% \draw[arrow, bend right] (WFminDNEM) to (WFminM);
 
-\draw[arrow] (WFminDNE) to node[right, text = red] {$\accDNE$} (WFacc);
-\draw[arrow, bend right=45] (WFminDNE) to node[pos=0.3, left, text=red] {$\mpe$} (WFseq);
-\draw[arrow, bend right] (WFminDNEM) to node[left, text=red] {$\FB$} (WFaccM);
-\draw[arrow, bend right] (WFseqM) to (WFminCor);
-\draw[arrow, bend right] (WFminCor) to node [right, text=red] {$\mpe$} (WFseqM);
-\draw[arrow] (WFCor) -- (WFminCor);
-% \draw[arrow, bend left = 110] (WFCor) to node[left, text=red] {$\accCor$} (WFacc);
-\draw[arrow, bend left] (WFminCor) to node[below, text=red] {$\corDNE$} (WFCor);
+% \draw[arrow] (WFminDNE) to node[right, text = red] {$\accDNE$} (WFacc);
+% \draw[arrow, bend right=45] (WFminDNE) to node[pos=0.3, left, text=red] {$\mpe$} (WFseq);
+% \draw[arrow, bend right] (WFminDNEM) to node[left, text=red] {$\FB$} (WFaccM);
+% \draw[arrow, bend right] (WFseqM) to (WFminCor);
+% \draw[arrow, bend right] (WFminCor) to node [right, text=red] {$\mpe$} (WFseqM);
+% \draw[arrow] (WFCor) -- (WFminCor);
+% % \draw[arrow, bend left = 110] (WFCor) to node[left, text=red] {$\accCor$} (WFacc);
+% \draw[arrow, bend left] (WFminCor) to node[below, text=red] {$\corDNE$} (WFCor);
 
-\draw[arrow, bend left=80] (WFCor) to node[pos = 0.4, left, text=red] {$\accCor$} (WFacc);
+% \draw[arrow, bend left=80] (WFCor) to node[pos = 0.4, left, text=red] {$\accCor$} (WFacc);
 
-\end{tikzpicture}
-\caption{The logical relationships between notions of well-foundedness}
- \label{fig:WF}
-\end{figure}
-% \clearpage
+% \end{tikzpicture}
+% \caption{The logical relationships between notions of well-foundedness}
+%  \label{fig:WF}
+% \end{figure}
+% % \clearpage
 
@@
 \caption{The logical relationships between notions of well-foundedness}
-\label{fig:WF2}
+\label{fig:WF}
 \end{figure}
@@
 }
-\clearpage
+% \clearpage
 % The principles appearing in the labels of Figure \ref{fig:WF} are valid for many rewriting systems,
@@
 
-\apcomment{Todo: 1. Filter through the rest, and see if there's anything we may still want to keep.\\
-  2. Include a subsection, or a section, with examples.  Provide examples where some decidability
-properties are provable, and others are not.}
+% \apcomment{Todo: 1. Filter through the rest, and see if there's anything we may still want to keep.\\
+%   2. Include a subsection, or a section, with examples.  Provide examples where some decidability
+% properties are provable, and others are not.}
 

### 2025-11-06 Relations/Paper/Formalization-pldi.tex
Required changes to theorem
typo fix

--- 2025-07-23 Relations/Paper/Formalization.tex
@@
 
-\begin{theorem}(Thm 1.2.2 in [Terese])
-\begin{enumerate}[(i)]
+\begin{theorem}[Thm 1.2.2 in \terese] 
+\begin{enumerate}[label=\roman*.]
+  \item[]
   \item $\gCR \implies \gNPe \implies \gUN$
@@
 
-\begin{theorem}(Thm. 1.2.3 in [Terese])
-  \begin{enumerate}[(i)]
+\begin{theorem}[Thm. 1.2.3 in \terese]
+  \begin{enumerate}[label=\roman*.]
+    \item[]
     \item $\gWN \land \gUN \implies \gBP$

### 2025-11-09 Relations/Paper/Summer_2025_TODO.tex
Conforming to pldi style
todo update from previous meeting

@@
 Use this to take this SNdec→WN to have a full proof from fb, isdec, sn -> wn. (issue in moving to fb file due to reversal of relation direction!)
+\item Need to fix how we put urls in for bibliography. Currently not quite working. 
+\item update wfcounters to show that asserting wfmin implies the excluded middle (and wfmindne the weak excluded middle).
+\item In wfcounters we should have a system that is SN but not WN (WN implies excluded middle). 
 \end{todolist}
@@
   \item Once we've got a current draft finished. Look in Teresa for first order term rewrite systems and see how many we can represent using our code.
+  \item discussion env has qed boxes which shouldn't be there.
+  \item Work on the conclusion
 \end{todolist}

### 2025-11-09 Relations/Paper/Conclusion.tex
paper update

@@
 Throughout this effort, we found that the classical theorems often assume
-  more than is necessary, and these distinctions become especially pronounced
-  in the context of constructive logic.
-  Seeking to optimize hypotheses in every proof, we obtaining marginal improvements of the standard
+  more than is necessary.
+  % , and these distinctions become especially pronounced
+  % in the context of constructive logic.
+  Seeking to optimize hypotheses in every proof, we obtain marginal improvements of the standard
 termination and confluence criteria.
@@
 expressive formulation of ARS theory.
+
+We also analyzed the subtleties in formulating the concept of a well-founded relation
+precisely in a constructive metatheory.  We identified several classical principles
+that are needed to relate these different variations of the concept.
 

### 2025-11-09 Relations/Paper/Formalization-pldi.tex
paper update

@@
 The formalization of the proofs are in \texttt{Propositions.agda}. These formalizations are straightforward
-and as such are not the focus of this paper.
+and do not merit further discussion.
 
@@
     \verb|ii+    : R isWN × R |\texttt{isUN}$^{\to}$ \verb|→ R isCR|\\
-    \verb|iii    : subcommutative R → R isCR|\\
+    \verb|iii    : subcommutative R → R isCR|
 \end{proof}
-\begin{proof}[Discussion.]
+\begin{remark}
     In $\mathtt{UN^{→}∧WN→CR}$ a more general proof of ($ii$) is given using $\UNto$.
-\end{proof}
+\end{remark}
 
@@
 \end{proof}
-\begin{proof}[Discussion.]\hfill
+\begin{remark} \hfill
   \begin{description}
@@
 We also assume that $\gSN$ is decidable, as this allows the construction of a witness for whether an element possesses the property $\SN$, which is essential for our proof.
-    \item[($iv$)] We did not formalize $\gCR \to \gCP$ as it requires cardinality assumptions. \qedhere
   \end{description}
-\end{proof}
+\end{remark}

### 2025-11-09 Relations/Paper/Implications.tex
wf diagram update
Minor paper changes + new WF table
paper update

@@
 
+% BP and RP imply SM. So BP and RP and WN classically implies SN.
 Proposition \ref{prop:nftomf} suggests that we consider $\MF$ as a termination property in its own right. This leads us to
@@
 
-\clearpage
+% \clearpage
 \renewcommand*{\thefootnote}{\fnsymbol{footnote}}
-
 \begin{table}[h!]
@@
     \end{tabular}
-    \caption{Global implications.
-\\$^*$~This implication also requires $\gWCR$.
-\\ $^\dagger$~This implication also requires either $\gWCR$ or the classical property required to go from $\SN \to \WN$ or $\SM \to \WM$.}
+    \caption{Global implications. \\$^*$~This implication also requires $\gWCR$. \\ $^\dagger$~This requires either $\gWCR$ or the classical implication $\SN \to \WN$ or $\SM \to \WM$.}
 \end{table}
@@
          or $\gWCR$ for the implication to $\gCR$, unlike $\gSN \land \gUNto$.
-        \item $\gWN \land \gUNto \implies \gCR$ only holds when the properties are global. The
-        counterexample provided illustrates why $\WCR \land \WN \land \UNto \nRightarrow \CR$.
+        \item $\gWN \land \gUNto \implies \gCR$ only holds when the properties are global. Counterexample~\ref{CE:4} shows that $\WCR \land \WN \land \UNto \nRightarrow \CR$.
         \item We have a generalization of Newman's Lemma as $\SM \land \gWCR \implies \CR$. This is explored in Subsection \ref{subsec:newnewman}.
@@
 \verb|isWN∧isSM→isSN : R isWN → R isSM → R isSN|
+
+\subsection{A sufficient condition for $\gSN \to \gWN$}
+\label{sec:SNtoWN}
+It is perhaps surprising that the intuitively obvious implication from strong
+normalization to weak normalization is actually not provable.
+A counterexample is furnished in the file \texttt{WFCounters.agda}.
+% This fact is related to the subtleties arising in constructive formulation of
+% well-foundedness, as we discuss at the end of Section \ref{sec:Well-foundedness}.
+At the same time, this implication is valid for all relations which are
+1) decidable, and 2) finitely branching.
+This is formalized in file \apcomment{Need to fill this in.}
+
+Since these conditions are in fact satisfied by all of the standard
+term rewrite systems and lambda calculi, we see that for such ARSs the implication
+is automatically valid.

### 2025-11-09 Relations/Paper/Well-foundedness.tex
paper update

@@
 
-One may wonder whether the difference between the various definitions above matters for 
+One may wonder whether the differences between the various definitions above matter for
 rewriting theory.  In particular, how often are the properties listed in
@@
 $\WFaccm(R)$ can be proved in higher-order arithmetic, then an intuitionistic proof
-of $\WFacc(R)$ is also possible.
+of $\WFacc(R)$ in higher arithmetic must also exist.
 % situation of separating these notions is complicated by the fact that, for all
@@
 \]
-This is weaker than deciding whether $x$ is a normal form:
+This is stronger than deciding whether $x$ is a normal form:
 % Note that deciding whether $x$ is a normal form constitutes the weaker disjunction
 $\lnot\lnot\left(\exists y. Ryx\right) \lor \left(\forall y. \lnot Ryx\right)$.
+Indeed, in the file \texttt{ARS/Examples.agda} the implication $\gSN \to \gWN$ 
+is equivalent to the principle of excluded middle.
 
@@
 
-Combined with the natural numbers example in \texttt{WFCounters.agda}, this shows
-that the intuitive implication $\SN_R \to \WN_R$ is not actually intuitionistically valid.
+It follows that there can be no constructive proof of $\WFmin$ from $\WFacc$,
+as the axiom of excluded middle would be a consequence of such a proof.
 

### 2025-11-10 Relations/Paper/Summer_2025_TODO.tex
paper update
TODO update pre-meeting

@@
 \item [\done] Make a connection in the final WF section talking about how SN doesn't imply WN constructively. (we've started writing this sentence). 
-\item We may need to add to the WFCounters file, if we have SN implies WN then every subset of the natural numbers is decidable.  
+\item [\done] We may need to add to the WFCounters file, if we have SN implies WN then every subset of the natural numbers is decidable.  
 \item Make sure we have a proof of the implication from SN to WN given FB and decidability of a relation (to back up our claim in our introduction).
@@
 \item [\done] Change the macro for FB so that it is also boldface
-\item from wellfounded extra move the implication of fb -> isdec -> isMinDec. move to implications. 
-Use this to take this SNdec→WN to have a full proof from fb, isdec, sn -> wn. (issue in moving to fb file due to reversal of relation direction!)
 \item Need to fix how we put urls in for bibliography. Currently not quite working. 
 \item update wfcounters to show that asserting wfmin implies the excluded middle (and wfmindne the weak excluded middle).
-\item In wfcounters we should have a system that is SN but not WN (WN implies excluded middle). 
+\item [\done] In wfcounters we should have a system that is SN but not WN (WN implies excluded middle). 
 \end{todolist}
@@
 \begin{todolist}
-  \item Aim for first draft finished by the end of the 29th.
+\item[X] Aim for first draft finished by the end of the 29th.
   \item Make a main file at this point to conform to this conference's style. Possibly a sub-folder for each conference.
@@
   \item Once we've got a current draft finished. Look in Teresa for first order term rewrite systems and see how many we can represent using our code.
-  \item discussion env has qed boxes which shouldn't be there.
+  \item [\done] discussion env has qed boxes which shouldn't be there.
   \item Work on the conclusion
+  \item from wellfounded extra move the implication of fb -> isdec -> isMinDec. move to implications. 
+  Use this to take this SNdec→WN to have a full proof from fb, isdec, sn -> wn. (issue in moving to fb file due to reversal of relation direction!)
+  \item Make consistent how we display definitions. 
+  \item Final read through (wed?)
 \end{todolist}

### 2025-11-10 Relations/Paper/Introduction.tex
Preparing to submit the paper

@@
 a transformation from the hypotheses to the conclusion of the claim.  For example,
-a type-checked proof that a given TRS is confluent automatically renders a function that
-computes a common reduct between any two reducts of a given term.
+a type-checked proof that a given TRS is Church--Rosser automatically renders a function that
+computes a common reduct between any two convertible terms.
 

### 2025-11-10 Relations/Paper/Summer_2025_TODO.tex
Preparing to submit the paper

@@
     \item [\done](Review 2) "l 422: $P_x$ has no arguments?"
-    \item (Review 3) Check out and include the following related work:
+    \item [\done] (Review 3) Check out and include the following related work:
     \begin{itemize}
@@
 \begin{itemize}
-  \item Perhaps we should not create variations and multiple implications of WFind,
+  \item[\done] Perhaps we should not create variations and multiple implications of WFind,
   but rather prove that it's equivalent to WFacc, but lands in a higher universe.
@@
 \begin{todolist}
-  \item Carry on refactoring Wellfounded.agda once fixed, breaking it up if necessary.
-  \item To finish the paper: We should do a final walk through and make sure we haven't introduced errors with our edits.
+\item [\done] Carry on refactoring Wellfounded.agda once fixed, breaking it up if necessary.
+\item [\done] To finish the paper: We should do a final walk through and make sure we haven't introduced errors with our edits.
 In particular, do all the counterexamples line up.
 Do all the references to different sections and pieces of code in Agda line up.
-  \item Do we remove all our local counterexamples in favour of global ones?
-  \item Rework well-foundedness section 
-  \item Rework conclusion 
-  \item Rework introduction 
-  \item Do we introduce a new section for discussing Agda? Talking about why we think there is an advantage to doing this work in Agda vs (say) Isabelle
+  \item [\done] Do we remove all our local counterexamples in favour of global ones?
+  \item [\done] Rework well-foundedness section 
+  \item[\done]  Rework conclusion 
+  \item [\done]  Rework introduction 
+  \item  [\done] Do we introduce a new section for discussing Agda? Talking about why we think there is an advantage to doing this work in Agda vs (say) Isabelle
 
@@
 \begin{todolist}
-  \item (Research item) Go deeper in the related works and see which are most relevant.
+\item[\done] (Research item) Go deeper in the related works and see which are most relevant.
 Make a list of works and give summaries to be used in future papers.
@@
   \item (Research item) How to go from WFseq to WFacc - possible that the Kleene Tree is a solution. - Not this paper
-
+  \item (Research item) Investigate: what we've done for natural numbers could be done for an arbitrary ARS (in the counter examples files), but for weak minimality and weak excluded middle. 
   \end{todolist}
@@
 \begin{todolist}
-  \item Write about the standard library formalization in our paper and talk about how ours differs. 
-  \item Create an equivalences file showing that our formalization agrees with the ASL (specifically definitions such as confluet, wcr, nf, leading up to showing our formalizations of Newman's lemma agree).
+\item[\done] Write about the standard library formalization in our paper and talk about how ours differs. 
+\item[X]  Create an equivalences file showing that our formalization agrees with the ASL (specifically definitions such as confluet, wcr, nf, leading up to showing our formalizations of Newman's lemma agree).
   \item Investigate contributing work to the ASL.
@@
 We already have this inconsistency in the code with $UN\to$} \apcomment{In the agda code let's not use arrow and have arrow implied as default but be explicit with '=' sign.}
-  \item Carry on modifying the names of wfXXX- to wfXXXnotnot with prefix underscore in agda and in latex.
+  \item [\done] Carry on modifying the names of wfXXX- to wfXXXnotnot with prefix underscore in agda and in latex.
 \sacomment{Done with the exception of WFseq-.
@@
 Basically, refactor the code.) \sacomment{Done but could be further refactored.}
-  \item Make a cheat sheet for the next meeting regarding to talk about coreductive.
+  \item [\done] Make a cheat sheet for the next meeting regarding to talk about coreductive.
 How it relates on the weak side and on the strong side.
@@
 \begin{todolist}
-  \item (Minor) We want to have a sentence in our WF section making clear that we can consider local properties as well and maybe make an example from accessible to sequential. 
-  \item Sentence explaining that wfacc is equivalent to wfind and therefore isn't included in the diagram (wfind).
+\item[\done] (Minor) We want to have a sentence in our WF section making clear that we can consider local properties as well and maybe make an example from accessible to sequential. 
+  \item[\done] Sentence explaining that wfacc is equivalent to wfind and therefore isn't included in the diagram (wfind).
 \end{todolist}
@@
 \begin{todolist}     
-  \item Focus for next meeting on writing. 
+\item[\done] Focus for next meeting on writing. 
   \item [\done] Are not not closed predicates over natural numbers dedcidable: If not is this a counterexample for WFminDNE.
@@
 \begin{todolist}     
-  \item Want to show that FB and weak decidability gives us accCor (think we may have shown this previously)
-  \item Add 'is' to wfcor macros.
-  \item make a decision on wfseq not not name. 
-  \item Keep on cleaning the WF section in paper. 
-  \item 
+\item[\done] Want to show that FB and weak decidability gives us accCor (think we may have shown this previously)
+  \item[\done] Add 'is' to wfcor macros.
+  \item[\done] make a decision on wfseq not not name. 
+  \item[\done] Keep on cleaning the WF section in paper. 
 \end{todolist}
@@
 Not sure if it can be done with strong normalization.)
-  \item Do a final read through of the information below the figure. Have we captured all the most important information / Are we repeating ourselves?
+  \item [\done] Do a final read through of the information below the figure. Have we captured all the most important information / Are we repeating ourselves?
   \item [\done] Do we want to keep anything in the old/delete section of WF?
-  \item Do we want to add anything about counter examples or positive examples? 
+  \item [\done] Do we want to add anything about counter examples or positive examples? 
   \item [\done] We may want to use words rather than macros in certain locations
   \item [\done] Check through the comments in general in the section. 
-  \item (Long term) Investigate: what we've done for natural numbers could be done for an arbitrary ARS (in the counter examples files).
-The sentence: ''The restriction to $\lnot\lnot$-closed subsets implies (and is equivalent to)
-every subset $P$ being merely \emph{weakly} decidable (satisfying $\lnot \lnot P(x) \lor \lnot P(X)$ 
-for all $x$)'' needs further exploration. We could not say it/say it differently. 
 \item [\done]  CHange WFseq not not to WFseq- in the macro. We are sticking with this for now. If we have time we can investigate the relation between the two.
@@
 \item [\done] We may need to add to the WFCounters file, if we have SN implies WN then every subset of the natural numbers is decidable.  
-\item Make sure we have a proof of the implication from SN to WN given FB and decidability of a relation (to back up our claim in our introduction).
+\item [\done] Make sure we have a proof of the implication from SN to WN given FB and decidability of a relation (to back up our claim in our introduction).
 \item check TERESE and see first order term rewrite systems example which could be valid for showing classical and constructive formalization coincide.
@@
 \item [\done] Change the macro for FB so that it is also boldface
-\item Need to fix how we put urls in for bibliography. Currently not quite working. 
-\item update wfcounters to show that asserting wfmin implies the excluded middle (and wfmindne the weak excluded middle).
+\item [\done, did SN to WN instead] update wfcounters to show that asserting wfmin implies the excluded middle (and wfmindne the weak excluded middle).
 \item [\done] In wfcounters we should have a system that is SN but not WN (WN implies excluded middle). 
@@
 \item[X] Aim for first draft finished by the end of the 29th.
-  \item Make a main file at this point to conform to this conference's style. Possibly a sub-folder for each conference.
-  \item Submission deadline is Thursday 13th 
-  \item Once we've got a current draft finished. Look in Teresa for first order term rewrite systems and see how many we can represent using our code.
+\item[\done] Make a main file at this point to conform to this conference's style. Possibly a sub-folder for each conference.
 \item [\done] discussion env has qed boxes which shouldn't be there.
-  \item Work on the conclusion
-  \item from wellfounded extra move the implication of fb -> isdec -> isMinDec. move to implications. 
+\item[\done] from wellfounded extra move the implication of fb -> isdec -> isMinDec. move to implications. 
   Use this to take this SNdec→WN to have a full proof from fb, isdec, sn -> wn. (issue in moving to fb file due to reversal of relation direction!) 
 \item Make consistent how we display definitions. 
+\item [\done] Work on the conclusion
+\item Need to fix how we put urls in for bibliography. Currently not quite working. 
+\item Run through and compile everything, make sure we didn't introduce any bugs
+\item Submit 
+\item Add a paragraph or two giving a short overview/summary of Agda.
+\item Go through the code, make naming consistent and self-documenting
+\item Once we've got a current draft finished. Look in Teresa for first order term rewrite systems and see how many we can represent using our code.
+\item Consider adding some more motivations 
+\item Look at the seq-minus vs. seq-not-not issue 
 \item Final read through (wed?)
+\item Submission deadline is Thursday 13th 
 \end{todolist}

### 2025-11-10 Relations/Paper/Well-foundedness.tex
Preparing to submit the paper

@@
 
+\newcommand{\gWF}{\mathbf{WF}}
+\newcommand{\WF}{\mathrm{WF}}
+
 An abstract reduction $\to_R$ is strongly normalizing
@@
 In this section, we will compare several definitions of well-foundedness.
+For ease of exposition, we will only consider local versions of these notions.
+(There is no loss of generality in this; any global well-foundedness property $\gWF(A;R)$ 
+restricts to a predicate $WF_R$ on $A$ via $WF_R(x) = \gWF(\Sigma y : A. R^* x y;R')$, 
+where $R'((y,\rho),(z,\sigma)) = R(y,z)$.)
 %which depend on the basic notions given in Definition~\ref{def:WFnotions} below.
@@
 is the converse of $R$.  Thus, if $\bar{R}$ is well-founded, $R \models \gSN$.
-Yet actually computing the normal form of a given $x$ seems to require a
-strong form of decidability of being $R$-minimal, namely:
+Yet actually computing the normal form of a given $x$ requires a
+strong form of decidability of being $R$-minimal:
 \[
@@
 \]
-This is stronger than deciding whether $x$ is a normal form:
+Note that merely deciding whether $x$ is a normal form is the weaker statement
 % Note that deciding whether $x$ is a normal form constitutes the weaker disjunction
 $\lnot\lnot\left(\exists y. Ryx\right) \lor \left(\forall y. \lnot Ryx\right)$.
-Indeed, in the file \texttt{ARS/Examples.agda} the implication $\gSN \to \gWN$ 
-is equivalent to the principle of excluded middle.
+Indeed, in the file \texttt{ARS/Examples.agda} the implication $\gSN \to \gWN$ for all relations $R$
+is shown to be equivalent to the principle of excluded middle.
 

### 2025-11-12 Relations/Paper/Definitions.tex
paper update
New definition layout. Typos fixed. Proper URLs

@@
   \begin{description}
-    \item[\ule{${a \in \NF_R}$}] \emph{$a$ is a normal form} if $(a,b) \notin R$ for any $b \in A$.
-    \item[\ule{$a \in \WN_R$}] \emph{$a$ is weakly normalizing} if $a \mstep b$ for some $b \in \NF_R$.
-    \item[\ule{$a \in \SN_R$}] \emph{$a$ is strongly normalizing} if $a$ is accessible with respect to the converse relation $\bar{R} = \setof{(y,x) | (x,y) \in R}$.
+    \item[\bq \ule{${a \in \NF_R}$}] \emph{$a$ is a normal form} if $(a,b) \notin R$ for any $b \in A$.
+    \item[\bq \ule{$a \in \WN_R$}] \emph{$a$ is weakly normalizing} if $a \mstep b$ for some $b \in \NF_R$.
+    \item[\bq \ule{$a \in \SN_R$}] \emph{$a$ is strongly normalizing} if $a$ is accessible with respect to the converse relation $\bar{R} = \setof{(y,x) | (x,y) \in R}$.
     See Section \ref{sec:Well-foundedness} for the notion of accessibility.
@@
     \begin{description}
-        \item[\ule{$a \in \WCR_R$}] \emph{$a$ is weakly Church-Rosser} (or \emph{weakly confluent}) if for all $b,c \in A$, \[c \bstep a \rstep b \implies \exists d.\, c \mstep d \bmstep b\]
-        \item[\ule{$a \in \CR_R$}] \emph{$a$ is Church-Rosser} (or \emph{confluent}) if for all $b,c \in A$, \[c \bmstep a \mstep b \implies \exists d.\, c \mstep d \bmstep b\]
-        \item[\ule{$a \in \CRs_R$}] \emph{$a$ is subcommutative} if for all $b, c \in A$,
+        \item[\bq \ule{$a \in \WCR_R$}] \emph{$a$ is weakly Church-Rosser} (or \emph{weakly confluent}) if for all $b,c \in A$, \[c \bstep a \rstep b \implies \exists d.\, c \mstep d \bmstep b\]
+        \item[\bq \ule{$a \in \CR_R$}] \emph{$a$ is Church-Rosser} (or \emph{confluent}) if for all $b,c \in A$, \[c \bmstep a \mstep b \implies \exists d.\, c \mstep d \bmstep b\]
+        \item[\bq \ule{$a \in \CRs_R$}] \emph{$a$ is subcommutative} if for all $b, c \in A$,
         \[c \bmstep a \mstep b \implies \exists d. \, c \rrstep d \brstep b\]
-        \item[\ule{$a \in \NPe_R$}] \emph{$a$ has the conversion normal form property} if for all $b \in \NF_R$, \[ a \estep b \implies a\mstep b\]
-        \item[\ule{$a \in \NP_R$}] \emph{$a$ has the reduction normal form property} if for all $b \in \NF_R$,
+        \item[\bq \ule{$a \in \NPe_R$}] \emph{$a$ has the conversion normal form property} if for all $b \in \NF_R$, \[ a \estep b \implies a\mstep b\]
+        \item[\bq \ule{$a \in \NP_R$}] \emph{$a$ has the reduction normal form property} if for all $b \in \NF_R$,
         \[c \bmstep a \mstep b \implies c \mstep b\]
-        \item[\ule{$a \in \UN_R$}] \emph{$a$ has the conversion unique normal form property} if for all $a, b \in \NF_R$, \[a \estep b \implies a \equiv b\]
-        \item[\ule{$a \in \UNto_R$}] \emph{$a$ has the reduction unique normal form property} if for all $b, c \in \NF_R$,
+        \item[\bq \ule{$a \in \UN_R$}] \emph{$a$ has the conversion unique normal form property} if for all $a, b \in \NF_R$, \[a \estep b \implies a \equiv b\]
+        \item[\bq \ule{$a \in \UNto_R$}] \emph{$a$ has the reduction unique normal form property} if for all $b, c \in \NF_R$,
         \[c \bmstep a \mstep b  \implies b \equiv c\]
@@
 \begin{definition} \label{def:seq} \hfill
-  \begin{itemize}
-    \item A \emph{sequence} is a function $s$ from the natural numbers to $A$.
-    \item A sequence $s : \nat \to A$ is \emph{$R$-decreasing} if every element of the sequence is $R$-related to its preceding term.
-    \item A sequence $s : \nat \to A$ is \emph{$R$-increasing} if every element of the sequence is $R$-related to its succeeding term.
-  \end{itemize}
+  \begin{description}
+    \item \bq \ule{A {sequence}} is a function $s$ from the natural numbers to $A$.
+    \item \bq \ule{A sequence $s : \nat \to A$ is {$R$-decreasing}} if every element of the sequence is $R$-related to its preceding term.
+    \item \bq \ule{A sequence $s : \nat \to A$ is {$R$-increasing}} if every element of the sequence is $R$-related to its succeeding term.
+  \end{description}
 \end{definition}
@@
     \begin{description}
-        \item[\ule{$x \in CP_R$}] \emph{$x$ has the cofinality property} if there exists an $R^r$-increasing sequence
+        \item[\bq \ule{$x \in CP_R$}] \emph{$x$ has the cofinality property} if there exists an $R^r$-increasing sequence
         \mbox{$s : \nat {\to} A$} starting from $x$ such that every
@@
   \begin{description}
-    \item[\ule{$a \in A$ is an $s$-bound}] if for all $i \in \nat$, $s (i) \mstep a$.
-    \item[\ule{$s : \nat \to A$ is bounded}] if there exists $a \in A$ that is an $s$-bound.
+    \item[\bq \ule{$a \in A$ is an $s$-bound}] if for all $i \in \nat$, $s (i) \mstep a$.
+    \item[\bq \ule{$s : \nat \to A$ is bounded}] if there exists $a \in A$ that is an $s$-bound.
   \end{description}
@@
     \begin{description}
-        \item[\ule{$\gBP(R)$}] \emph{$R$ has the boundedness property} if every $R$-increasing sequence is bounded.
-        \item[\ule{$\gRP(R)$}] \emph{$R$ has the recurrence property} if for every bounded, increasing sequence $s$ with an $s$-bound, there exists an $i \in \nat$ such that
+        \item[\bq \ule{$\gBP(R)$}] \emph{$R$ has the boundedness property} if every $R$-increasing sequence is bounded.
+        \item[\bq \ule{$\gRP(R)$}] \emph{$R$ has the recurrence property} if for every bounded, increasing sequence $s$ with an $s$-bound, there exists an $i \in \nat$ such that
         $s (i) \mstep x \implies x \mstep s (i)$ for all $x\in A$.
-        \item[\ule{$\gRPm(R)$}] \emph{$R$ has the weak recurrence property} if for every increasing sequence $s$ with bound $b$ there exists an $i \in \nat$ such that $b \mstep s (i)$.
+        \item[\bq \ule{$\gRPm(R)$}] \emph{$R$ has the weak recurrence property} if for every increasing sequence $s$ with bound $b$ there exists an $i \in \nat$ such that $b \mstep s (i)$.
     \end{description}
@@
     \begin{description}
-        \item[$\gInc(R)$] \emph{$R$ is increasing} if there exists a ``size function'' $|{-}| : A \to \nat$ satisfying, for all $a, b \in A$,
+        \item[\bq  \ule{$\gInc(R)$}] \emph{$R$ is increasing} if there exists a ``size function'' $|{-}| : A \to \nat$ satisfying, for all $a, b \in A$,
         $(a \rstep b) \implies |a| < |b|$
@@
     \begin{description}
-        \item[\ule{$a \in \FB$}] \emph{$a$ is finitely branching} if there are finitely many $b \in A$ such that $a \rstep b$.
+        \item[\bq \ule{$a \in \FB$}] \emph{$a$ is finitely branching} if there are finitely many $b \in A$ such that $a \rstep b$.
     \end{description}
@@
 
-$\FB$ is a property that plays an important role in our discussion of well-foundedness (see Section \ref{sec:Well-foundedness}).
+$\FB$ plays an important role in our discussion of well-foundedness, see Section \ref{sec:Well-foundedness}.

### 2025-11-12 Relations/Paper/Implications.tex
New definition layout. Typos fixed. Proper URLs

@@
     \begin{description}
-        \item[\ule{$a \in \MF_R$}] \emph{$a$ is a minimal form} if $a \mstep b \implies b \mstep a$ for any $b \in A$.
-        \item[\ule{$a \in \WM_R$}] \emph{$a$ is weakly minimalizing} if $a \mstep b$ for some $b \in \MF_R$.
-        \item[\ule{$a \in \SM_R$}]  \emph{$a$ is strongly minimalizing} if either $a \in MF_R$, or every element one $R$ step from $a$ is strongly minimalizing. (This
+        \item[\bq \ule{$a \in \MF_R$}] \emph{$a$ is a minimal form} if $a \mstep b \implies b \mstep a$ for any $b \in A$.
+        \item[\bq \ule{$a \in \WM_R$}] \emph{$a$ is weakly minimalizing} if $a \mstep b$ for some $b \in \MF_R$.
+        \item[\bq \ule{$a \in \SM_R$}]  \emph{$a$ is strongly minimalizing} if either $a \in MF_R$, or every element one $R$ step from $a$ is strongly minimalizing. (This
         definition is to be understood inductively).
-        \item[\ule{$a \in \SMseq_R$}] \emph{$a$ is sequentially strongly minimalizing} if for every $R$-increasing sequence $s$ starting at $a$, there exists
+        \item[\bq \ule{$a \in \SMseq_R$}] \emph{$a$ is sequentially strongly minimalizing} if for every $R$-increasing sequence $s$ starting at $a$, there exists
         an $i \in \nat$ such that $s (i) \in \MF$.
-        \item[\ule{$a \in \MP_R$}] \emph{$a$ has the minimal form property} if $c \bmstep a \mstep b \implies c \mstep b$ for any $b \in \MF$.
+        \item[\bq \ule{$a \in \MP_R$}] \emph{$a$ has the minimal form property} if $c \bmstep a \mstep b \implies c \mstep b$ for any $b \in \MF$.
     \end{description}
@@
 In contrast to the above proposition, the inclusion $\SN \subset \SM \cap \WN $ is strict: in Counterexample~\ref{CE:4}, $a \in \SM \cap \WN$, but $a \notin \SN$.
-In the tables below, we therefore include a seperate column for the combination of $\SM$ and $\WN$.
+In the tables below, we therefore include a separate column for the combination of $\SM$ and $\WN$.
 

### 2025-11-12 Relations/Paper/Summer_2025_TODO.tex
New definition layout. Typos fixed. Proper URLs
todo update

@@
 \item [\done] In wfcounters we should have a system that is SN but not WN (WN implies excluded middle). 
+\item make an external bibliography file rather than inlining in main file.
 \end{todolist}
@@
 \item Make consistent how we display definitions.
+\sacomment{I've made a change which I think looks better (bullet point style.) If we're happy with this change we can apply it to the wellfoundedness section too unless we rely on the numbering/reference the numbers}
 \item [\done] Work on the conclusion
-\item Need to fix how we put urls in for bibliography. Currently not quite working. 
+\item Need to fix how we put urls in for bibliography. Currently not quite working. \sacomment{Now all urls, if happy with how it looks we can tick it off. }
+\item Check the PLDI page for submission rules/requirements. In particular the bibliography style 
 \item Run through and compile everything, make sure we didn't introduce any bugs
+\item Check the layout of figures through the paper. Counterexamples for example is currently `off'. 
 \item Submit 

### 2025-11-13 Relations/Paper/Definitions.tex
Minor edits

@@
 \begin{definition}
-    An abstract rewrite system (\emph{ARS}) is a structure $\mathcal{A} = (A, R_\alpha)$ where
+    \ule{An abstract rewrite system({ARS})} is a structure $\mathcal{A} = (A, R_\alpha)$ where
      $A$ is a set and $R_\alpha$ is a set of binary relations on $A$.

### 2025-11-13 Relations/Paper/Introduction.tex
New definition layout. Typos fixed. Proper URLs
Minor edits

@@
 pursue the broader project.  The present contribution can therefore be seen as
-``bootstrapping'' Appstate's new formalized PL repository.
+``bootstrapping'' Appalachian State's new formalized PL repository.
 
@@
 The standard constructive definition does not even allow one to show that SN implies WN,
-as we discuss in Section \ref{sec:Well-foundedness} and formalize in \texttt{WFCounters.agda}.
+as we discuss in Section \ref{sec:Well-foundedness} and formalize in \texttt{WFCounters.agda} \sacomment{Should this now be ARS/Examples.agda?}.
 We therefore looked at a number of variations of this notion in the constructive context,

### 2025-11-13 Relations/Paper/Definitions.tex
Finalizing the paper

@@
 in our discussion. Each subsection specifies the Agda file(s) which contains formalizations of the given definitions.
+%All the files in this section are found in the \texttt{Relations} folder.
 
 \begin{definition}
-    \ule{An abstract rewrite system({ARS})} is a structure $\mathcal{A} = (A, R_\alpha)$ where
+    An \bemph{abstract rewrite system ({ARS})} is a structure $\mathcal{A} = (A, R_\alpha)$ where
      $A$ is a set and $R_\alpha$ is a set of binary relations on $A$.
@@
 
-\subsection{Closure operators (\texttt{ClosureOperators.agda})}
+\subsection{Closure operators (\texttt{Relations/ClosureOperators.agda})}
 
@@
   \begin{enumerate}
-    \item $R^r$ denotes the \emph{reflexive closure} of $R$.
-    \item $R^s$ denotes the \emph{symmetric closure} of $R$.
-    \item $\tclos{R}$ denotes the \emph{transitive closure} of $R$.
-    \item $R^* = (R^r)\tclos{}$ denotes the \emph{reflexive--transitive closure} of $R$.
-    \item $R^= = (R^s)^*$ denotes the \emph{equivalence relation generated by} $R$.
+    \item $R^r$ denotes the \bemph{reflexive closure} of $R$.
+    \item $R^s$ denotes the \bemph{symmetric closure} of $R$.
+    \item $\tclos{R}$ denotes the \bemph{transitive closure} of $R$.
+    \item $R^* = (R^r)\tclos{}$ denotes the \bemph{reflexive--transitive closure} of $R$.
+    \item $R^= = (R^s)^*$ denotes the \bemph{equivalence relation generated by} $R$.
   \end{enumerate}
@@
 
-\subsection{Normalization and Confluence (\texttt{Properties.agda})}
+\subsection{Normalization and Confluence (\texttt{ARS/Properties.agda})}
 
@@
   \begin{description}
-    \item[\bq \ule{${a \in \NF_R}$}] \emph{$a$ is a normal form} if $(a,b) \notin R$ for any $b \in A$.
-    \item[\bq \ule{$a \in \WN_R$}] \emph{$a$ is weakly normalizing} if $a \mstep b$ for some $b \in \NF_R$.
-    \item[\bq \ule{$a \in \SN_R$}] \emph{$a$ is strongly normalizing} if $a$ is accessible with respect to the converse relation $\bar{R} = \setof{(y,x) | (x,y) \in R}$.
+    \item[\bq \ule{${a \in \NF_R}$}] $a$ is a \bemph{normal form} if $(a,b) \notin R$ for any $b \in A$ .
+    \item[\bq \ule{$a \in \WN_R$}] $a$ is \bemph{weakly normalizing} if $a \mstep b$ for some $b \in \NF_R$.
+    \item[\bq \ule{$a \in \SN_R$}] $a$ is \bemph{strongly normalizing} if $a$ is accessible with respect to the converse relation $\bar{R} = \setof{(y,x) | (x,y) \in R}$.
     See Section \ref{sec:Well-foundedness} for the notion of accessibility.
@@
     \begin{description}
-        \item[\bq \ule{$a \in \WCR_R$}] \emph{$a$ is weakly Church-Rosser} (or \emph{weakly confluent}) if for all $b,c \in A$, \[c \bstep a \rstep b \implies \exists d.\, c \mstep d \bmstep b\]
-        \item[\bq \ule{$a \in \CR_R$}] \emph{$a$ is Church-Rosser} (or \emph{confluent}) if for all $b,c \in A$, \[c \bmstep a \mstep b \implies \exists d.\, c \mstep d \bmstep b\]
-        \item[\bq \ule{$a \in \CRs_R$}] \emph{$a$ is subcommutative} if for all $b, c \in A$,
+        \item[\bq \ule{$a \in \WCR_R$}] $a$ is \bemph{weakly Church-Rosser} (or \emph{weakly confluent}) if for all $b,c \in A$, \[c \bstep a \rstep b \implies \exists d.\, c \mstep d \bmstep b\]
+        \item[\bq \ule{$a \in \CR_R$}] $a$ is \bemph{Church-Rosser} (or \emph{confluent}) if for all $b,c \in A$, \[c \bmstep a \mstep b \implies \exists d.\, c \mstep d \bmstep b\]
+        \item[\bq \ule{$a \in \CRs_R$}] $a$ is \bemph{subcommutative} if for all $b, c \in A$,
         \[c \bmstep a \mstep b \implies \exists d. \, c \rrstep d \brstep b\]
-        \item[\bq \ule{$a \in \NPe_R$}] \emph{$a$ has the conversion normal form property} if for all $b \in \NF_R$, \[ a \estep b \implies a\mstep b\]
-        \item[\bq \ule{$a \in \NP_R$}] \emph{$a$ has the reduction normal form property} if for all $b \in \NF_R$,
+        \item[\bq \ule{$a \in \NPe_R$}] $a$ has the \bemph{conversion normal form property} if for all $b \in \NF_R$, \[ a \estep b \implies a\mstep b\]
+        \item[\bq \ule{$a \in \NP_R$}] $a$ has the \bemph{reduction normal form property} if for all $b \in \NF_R$,
         \[c \bmstep a \mstep b \implies c \mstep b\]
-        \item[\bq \ule{$a \in \UN_R$}] \emph{$a$ has the conversion unique normal form property} if for all $a, b \in \NF_R$, \[a \estep b \implies a \equiv b\]
-        \item[\bq \ule{$a \in \UNto_R$}] \emph{$a$ has the reduction unique normal form property} if for all $b, c \in \NF_R$,
+        \item[\bq \ule{$a \in \UN_R$}] $a$ has the \bemph{conversion unique normal form property} if for all $a, b \in \NF_R$, \[a \estep b \implies a \equiv b\]
+        \item[\bq \ule{$a \in \UNto_R$}] $a$ has the \bemph{reduction unique normal form property} if for all $b, c \in \NF_R$,
         \[c \bmstep a \mstep b  \implies b \equiv c\]
@@
 %     \begin{description}
-%         \item[\ule{$a \in \WCR_R$}] \emph{$a$ is weakly Church-Rosser (or weakly confluent)} if $c \bstep a \rstep b \implies c \mstep d \bmstep b$.
-%         \item[\ule{$a \in \CR_R$}] \emph{$a$ is Church-Rosser (or confluent)} if $c \bmstep a \mstep b \implies c \mstep d \bmstep b$.
-%         \item[\ule{$a \in \CRs_R$}] \emph{$a$ is subcommutative} if $c \bmstep a \mstep b \implies c \rrstep d \brstep b$.
-%         \item[\ule{$a \in \NPe_R$}] \emph{$a$ has the conversion normal form property} if $a \estep b \implies a\mstep b$ for any $b \in \NF$.
-%         \item[\ule{$a \in \NP_R$}] \emph{$a$ has the normal form property} if $c \bmstep a \mstep b \implies c \mstep b$ for any $b \in \NF$.
-%         \item[\ule{$a \in \UN_R$}] \emph{$a$ has the unique normal form property} if $a \estep b \implies a \equiv b$  for any $a, b \in \NF$.
-%         \item[\ule{$a \in \UNto_R$}] \emph{$a$ has the unique normal form property with respect to reduction} if $c \bmstep a \mstep b  \implies b \equiv c$  for any $b, c \in \NF$.
+%         \item[\ule{$a \in \WCR_R$}] \bemph{$a$ is weakly Church-Rosser (or weakly confluent)} if $c \bstep a \rstep b \implies c \mstep d \bmstep b$.
+%         \item[\ule{$a \in \CR_R$}] \bemph{$a$ is Church-Rosser (or confluent)} if $c \bmstep a \mstep b \implies c \mstep d \bmstep b$.
+%         \item[\ule{$a \in \CRs_R$}] \bemph{$a$ is subcommutative} if $c \bmstep a \mstep b \implies c \rrstep d \brstep b$.
+%         \item[\ule{$a \in \NPe_R$}] \bemph{$a$ has the conversion normal form property} if $a \estep b \implies a\mstep b$ for any $b \in \NF$.
+%         \item[\ule{$a \in \NP_R$}] \bemph{$a$ has the normal form property} if $c \bmstep a \mstep b \implies c \mstep b$ for any $b \in \NF$.
+%         \item[\ule{$a \in \UN_R$}] \bemph{$a$ has the unique normal form property} if $a \estep b \implies a \equiv b$  for any $a, b \in \NF$.
+%         \item[\ule{$a \in \UNto_R$}] \bemph{$a$ has the unique normal form property with respect to reduction} if $c \bmstep a \mstep b  \implies b \equiv c$  for any $b, c \in \NF$.
 %     \end{description}
@@
     For each of the predicates $\mathrm{X_R}$ defined above we write
-    $\mathbf{X}(R)$ if $\forall a.\; a \in \mathrm{X}_R$. When $R$ is clear from the context, we will write $\gNP$ for $\gNP(R)$, etc.
+    $\mathbf{X}(R)$ if $\forall a.\; a \in \mathrm{X}_R$. When $R$ is implied by the context, we will write $\gNP$ for $\gNP(R)$, etc.
 
@@
     \begin{enumerate}
-        \item $\gNP \iff \gNPe$
-        \item $\gUN \implies \gUNto$
+        \item $\gNPe \iff \gNP$
+        \item $\gUN \, \implies \gUNto$
     \end{enumerate}
 \end{proposition}
-\begin{proof} The majority of proofs in this work have been fully formalized in Agda and require no further elaboration.
+  All of the proofs in this work have been fully formalized in Agda, and many of them require no further elaboration.
 Throughout the paper, we refer to the relevant locations in the code base by giving the name of the Agda file, along with the names and types of the functions corresponding to each claim.
 
-  The following claims are formalized in \texttt{Implications.agda}.
+The proof of the above proposition is formalized in \texttt{ARS/Implications.agda} as follows.
     \begin{enumerate}
@@
     \end{enumerate}
-\end{proof}
 
@@
 
-\subsection{Sequences and Recurrence (\texttt{Seq.agda})}
+\subsection{Sequences and Recurrence (\texttt{Relations/Seq.agda}, \texttt{ARS/Properties.agda})}
 % The following definitions are key to formalizing Theorem 1.2.3 in \terese.
-The definitions in this subsections are key to formalizing Theorem 1.2.3 in \terese.
+The definitions in this subsection are key to formalizing Theorem 1.2.3 in \terese.
 
@@
   \begin{description}
-    \item \bq \ule{A {sequence}} is a function $s$ from the natural numbers to $A$.
-    \item \bq \ule{A sequence $s : \nat \to A$ is {$R$-decreasing}} if every element of the sequence is $R$-related to its preceding term.
-    \item \bq \ule{A sequence $s : \nat \to A$ is {$R$-increasing}} if every element of the sequence is $R$-related to its succeeding term.
+    \item \bq A \bemph{sequence} is a function $s$ from the natural numbers to $A$.
+    \item \bq A sequence $s : \nat \to A$ is \bemph{$R$-decreasing} if every element of the sequence is $R$-related to its preceding term: $\forall k. s(k+1) \rstep sk$.
+    \item \bq A sequence $s : \nat \to A$ is \bemph{$R$-increasing} if every element of the sequence is $R$-related to its succeeding term: $\forall k. sk \rstep s(k+1)$.
   \end{description}
@@
     \begin{description}
-        \item[\bq \ule{$x \in CP_R$}] \emph{$x$ has the cofinality property} if there exists an $R^r$-increasing sequence
+        \item[\bq \ule{$x \in CP_R$}] $x$ has the \bemph{cofinality property} if there exists an $R^r$-increasing sequence
         \mbox{$s : \nat {\to} A$} starting from $x$ such that every
@@
         \[ x \mstep y \implies \exists i. y \mstep s(i) \]
-        % \item[\ule{$x \in CP_R$}] \emph{$x$ has the cofinality property} if there exists an
+        % \item[\ule{$x \in CP_R$}] \bemph{$x$ has the cofinality property} if there exists an
         % (not necessarily strictly) increasing sequence starting from $x$ such that every
@@
 \begin{definition} \label{def:bound} \hfill
-  \begin{description}
-    \item[\bq \ule{$a \in A$ is an $s$-bound}] if for all $i \in \nat$, $s (i) \mstep a$.
-    \item[\bq \ule{$s : \nat \to A$ is bounded}] if there exists $a \in A$ that is an $s$-bound.
-  \end{description}
+  \begin{itemize}
+    \item $a \in A$ is an \bemph{$s$-bound} if for all $i \in \nat$, $s (i) \mstep a$.
+    \item $s : \nat \to A$ is \bemph{bounded} if there exists $a \in A$ that is an $s$-bound.
+  \end{itemize}
 \end{definition}
@@
     \begin{description}
-        \item[\bq \ule{$\gBP(R)$}] \emph{$R$ has the boundedness property} if every $R$-increasing sequence is bounded.
-        \item[\bq \ule{$\gRP(R)$}] \emph{$R$ has the recurrence property} if for every bounded, increasing sequence $s$ with an $s$-bound, there exists an $i \in \nat$ such that
+        \item[\bq \ule{$\gBP(R)$}] $R$ has the \bemph{boundedness property} if every $R$-increasing sequence is bounded.
+        \item[\bq \ule{$\gRP(R)$}] $R$ has the \bemph{recurrence property} if for every bounded, increasing sequence $s$ with an $s$-bound, there exists an $i \in \nat$ such that
         $s (i) \mstep x \implies x \mstep s (i)$ for all $x\in A$.
-        \item[\bq \ule{$\gRPm(R)$}] \emph{$R$ has the weak recurrence property} if for every increasing sequence $s$ with bound $b$ there exists an $i \in \nat$ such that $b \mstep s (i)$.
+        \item[\bq \ule{$\gRPm(R)$}] $R$ has the \bemph{weak recurrence property} if for every increasing sequence $s$ with bound $b$ there exists an $i \in \nat$ such that $b \mstep s (i)$.
     \end{description}
@@
 
-The property $\gBP$ is equivalent to the property called $\mathrm{\,Ind}$ in \terese.
-(Specifically, $\mathrm{\,Ind}$ asserts the exists of a bound for finite sequences as well, but that is automatic, since the last term of a finite reduction sequence is a bound for that sequence.)
+The property $\gBP$ is equivalent to the property called $\mathbf{Ind}$ in \terese.
+More precisely, $\mathbf{Ind}$ asserts the existence of a bound for finite sequences as well, but that is automatic, since the last term of a finite reduction sequence is a bound for that sequence.
 
@@
     \begin{description}
-        \item[\bq  \ule{$\gInc(R)$}] \emph{$R$ is increasing} if there exists a ``size function'' $|{-}| : A \to \nat$ satisfying, for all $a, b \in A$,
-        $(a \rstep b) \implies |a| < |b|$
+        \item[\bq  \ule{$\gInc(R)$}] $R$ is \bemph{increasing} if there exists a ``size function'' $|{-}| : A \to \nat$ satisfying, for all $a, b \in A$,
+        $(a \rstep b) \implies |a| < |b|$.
     \end{description}
@@
 Furthermore, it takes us outside of a purely relational theory.
-The weaker property $\gRP$ defined above will substitute $\gInc$ all places that require it.
-(For further discussion, see Subsection~\ref{subsec:def}.)
+The weaker property $\gRP$ defined above will substitute $\gInc$ in all places that require it.
+For further discussion, see Subsection~\ref{subsec:def}.
 
@@
         so $\gRP$ holds vacuously.
-        \item See \verb|RP-↔RP : R isRP- ↔ R isRP| in \texttt{Seq.agda}. \qedhere
+        \item See \verb|RP-↔RP : R isRP- ↔ R isRP| in \texttt{ARS/Implications.agda}. \qedhere
     \end{enumerate}
@@
 
-\subsection{Finitely branching (\texttt{FinitelyBranching.agda})}
+\subsection{Finitely branching (\texttt{Relations/FinitelyBranching.agda})}
 
@@
     \begin{description}
-        \item[\bq \ule{$a \in \FB$}] \emph{$a$ is finitely branching} if there are finitely many $b \in A$ such that $a \rstep b$.
+        \item[\bq \ule{$a \in \FB$}] $a$ is \bemph{finitely branching} if there are finitely many $b \in A$ such that $a \rstep b$.
     \end{description}

### 2025-11-13 Relations/Paper/Formalization-pldi.tex
Finalizing the paper

@@
 
-As outlined in the previous section, \texttt{Properties.agda}, \texttt{Seq.agda}, and \texttt{ClosureOperators.agda} define most standard termination and confluence properties.
+As presented in the previous section, the file \texttt{Properties.agda} defines most standard termination and confluence properties.
 The file \texttt{Base.agda} introduces additional definitions which are required for the formalization of the propositions found in Chapter 1 of \terese.
@@
 The differences are highlighted in Section~\ref{sec:Well-foundedness}.
-     See Section \ref{sec:Well-foundedness} for further discussion.
+%     See Section \ref{sec:Well-foundedness} for further discussion.
     \item $\NPe$ : We use the equivalent $\NP$ definition.
@@
 
-\begin{theorem}[Thm 1.2.2 in \terese]
+\begin{theorem}[Thm 1.2.2 in \terese] \hfill 
 \begin{enumerate}[label=\roman*.]
-  \item[]
+  % \item[]
   \item $\gCR \implies \gNPe \implies \gUN$
@@
 
-\begin{theorem}[Thm. 1.2.3 in \terese]
+\begin{theorem}[Thm. 1.2.3 in \terese] \hfill
   \begin{enumerate}[label=\roman*.]
-    \item[]
+    % \item[]
     \item $\gWN \land \gUN \implies \gBP$
@@
 For the closest constructive analogue to this proof we have written $\mathtt{iiSeq}$, where we replace $\gBP$ with the stronger properties $\gWN$ and $\gUN$ and we replace $\gInc$ with the weaker property $\gRP$.
-    With the original property $\gBP$ and $gRP$ we can imply the related property $gSM$ ($\gSM$ is defined in Section~\ref{sec:Hierarchy} and its relation to $gSN$ is expanded upon).
+    With the original property $\gBP$ and $\gRP$ we can imply the related property $\gSM$ ($\gSM$ is defined in Section~\ref{sec:Hierarchy} and its relation to $\gSN$ is expanded upon).
 The definition and further discussion of $\isWFseqm$ are provided in Section~\ref{sec:Well-foundedness}.
     \item[($iii$)] In $\mathtt{iii}$, we replace $\gInc$ with the more general property $\gRPm$.
-We also assume that $\gSN$ is decidable, as this allows the construction of a witness for whether an element possesses the property $\SN$, which is essential for our proof.
+We also assume that $\gSN$ is decidable, as this allows the construction of a witness for whether an element possesses the property $\SN$, which is essential for this proof.
   \end{description}

### 2025-11-13 Relations/Paper/Summer_2025_TODO.tex
todo update
External references file

@@
 \item [\done] In wfcounters we should have a system that is SN but not WN (WN implies excluded middle). 
-\item make an external bibliography file rather than inlining in main file.
 \end{todolist}
@@
   \item [\done] Work on the conclusion
-\item Need to fix how we put urls in for bibliography. Currently not quite working. \sacomment{Now all urls, if happy with how it looks we can tick it off. }
+  \item [\done] Need to fix how we put urls in for bibliography. Currently not quite working. \sacomment{Now all urls, if happy with how it looks we can tick it off. }
   \item Check the PLDI page for submission rules/requirements. In particular the bibliography style 
-\item Run through and compile everything, make sure we didn't introduce any bugs
+  \item [\done] Run through and compile everything, make sure we didn't introduce any bugs
   \item Check the layout of figures through the paper. Counterexamples for example is currently `off'. 
@@
   \item Final read through (wed?)
+  \item make an external bibliography file rather than inlining in main file. Make sure bibliography is up to standard (e.g. emph on book title).
 \item Submission deadline is Thursday 13th 
+\item MF and WN iff NF (see in hierarchy section) should be an intersection rather than logical and (change to be made in paper and agda code).
+Similarly it should be the double arrow iff.
+Check through paper for similar changes.
 \end{todolist}

### 2025-11-13 Relations/Paper/Introduction.tex

--- 2025-11-10 Relations/Paper/Introduction.tex
@@
 \section{Introduction}
+
+\newcommand{\inreview}[1]{[\textsc{university name}]}
+% \newcommand{\inreview}[1]{\sout{\phantom{#1}}}
+% \newcommand{\inreview}[1]{#1}
+
 \label{sec:Introduction}
@@
 This work is part of a larger effort to develop a library of formalized programming language theory (PL)
-at Appalachian State University.
+at \inreview{Appalachian State} University.
 Since Term Rewriting Systems (TRS) play a foundational role in programming languages,
@@
 pursue the broader project.  The present contribution can therefore be seen as
-``bootstrapping'' Appstate's new formalized PL repository.
+``bootstrapping'' \inreview{Appalachian State}'s new formalized PL repository.
 
@@
 The standard constructive definition does not even allow one to show that SN implies WN,
-as we discuss in Section \ref{sec:Well-foundedness} and formalize in \texttt{WFCounters.agda}.
-We therefore looked at a number of variations of this notion in the constructive context,
+as we discuss at the end of Section \ref{sec:Well-foundedness} and formalize in \texttt{ARS/Examples.agda}. We therefore looked at a number of variations of this notion in the constructive context,
 their classical counterparts all being logically equivalent. %This gave rise to a rich set of concepts, see Figure \ref{f:wf}.

### 2025-11-13 Relations/Paper/Well-foundedness.tex
Typo fix

@@
 %(and is equivalent to)
-that each subset $P$ it \emph{weakly} decidable,
+that each subset $P$ is \emph{weakly} decidable,
 satisfying $\lnot \lnot P(x) \lor \lnot P(X)$ for all $x$.
@@
 
-In \cite{Terese}, the $\WFseqm$ definition is used, as in the classical mathematics textbooks.
+In \terese, the $\WFseqm$ definition is used, as in the classical mathematics textbooks.
 Constructively, this is not a useful definition, as it does not provide any positive computational content and requires an explicit sequence to be defined.

### 2025-11-13 Relations/Paper/Summer_2025_TODO.tex
pre-submission todo changes

@@
 \item [\done] In wfcounters we should have a system that is SN but not WN (WN implies excluded middle).
+
 \end{todolist}
@@
   Use this to take this SNdec→WN to have a full proof from fb, isdec, sn -> wn. (issue in moving to fb file due to reversal of relation direction!) 
-  \item Make consistent how we display definitions.
-\sacomment{I've made a change which I think looks better (bullet point style.) If we're happy with this change we can apply it to the wellfoundedness section too unless we rely on the numbering/reference the numbers}
+  \item [\done] Make consistent how we display definitions. 
   \item [\done] Work on the conclusion
   \item [\done] Need to fix how we put urls in for bibliography. Currently not quite working. \sacomment{Now all urls, if happy with how it looks we can tick it off. }
-  \item Check the PLDI page for submission rules/requirements. In particular the bibliography style 
+  \item [\done] Check the PLDI page for submission rules/requirements. In particular the bibliography style 
   \item [\done] Run through and compile everything, make sure we didn't introduce any bugs
-  \item Check the layout of figures through the paper. Counterexamples for example is currently `off'. 
+  \item [\done] Check the layout of figures through the paper. Counterexamples for example is currently `off'.
+  \item talk about why we use agda in 1.2 Agda is the perfect system for formalizing programming language theory.  
   \item Submit 
@@
 
+\section*{Post pldi todos}
+\begin{todolist}
+  \item Make the well founded definitions conform to the style of the definitions in other sections.
+Namely, bring the symbols to the start of the sentence.
+Use bemph where appropriate.
+Do we want all definitions to be itemized?
+  \item Improve how we write P bar bar for the definitions in wellfounded (well founded minimality wise). Chat makes the following suggestion (see commented out line in tex file):
+  % \newcommand{\dneg}[1]{\overline{\smash{\overline{#1}}\vphantom{#1}}} % tight double overline
+  \item The sigma symbol was being rendered as a degree symbol. Why? Also, our solution is slightly too big, try and make it smaller (see well founded classical definitions).
+  \item We made a bodge fix for not right arrow in use in well founded. It is good enough for now but there should be a better way to express it in latex. (when defining isMinDec)
+  \item run through the table again and check the counterexamples line up.
+
+\end{todolist}
+
+notes to self:
+- Tell Dr. P to check out the trs pvs paper.
+
 \end{document}

### 2025-11-14 Relations/Paper/Summer_2025_TODO.tex
todoo update post submission

@@
   \item [\done] Check the layout of figures through the paper. Counterexamples for example is currently `off'.
-  \item talk about why we use agda in 1.2 Agda is the perfect system for formalizing programming language theory.  
+  \item [\done] talk about why we use agda in 1.2 Agda is the perfect system for formalizing programming language theory.  
   \item Submit 
-  \item Add a paragraph or two giving a short overview/summary of Agda.
-  \item Go through the code, make naming consistent and self-documenting
+  \item [\done] Add a paragraph or two giving a short overview/summary of Agda.
   \item Once we've got a current draft finished. Look in Teresa for first order term rewrite systems and see how many we can represent using our code.
@@
   \item Final read through (wed?)
-  \item make an external bibliography file rather than inlining in main file. Make sure bibliography is up to standard (e.g. emph on book title).
+  \item [\done] make an external bibliography file rather than inlining in main file. Make sure bibliography is up to standard (e.g. emph on book title).
   \item Submission deadline is Thursday 13th 
-\item MF and WN iff NF (see in hierarchy section) should be an intersection rather than logical and (change to be made in paper and agda code).
-Similarly it should be the double arrow iff.
-Check through paper for similar changes.
 \end{todolist}
@@
   \item We made a bodge fix for not right arrow in use in well founded. It is good enough for now but there should be a better way to express it in latex. (when defining isMinDec)
+  \item Go through the code, make naming consistent and self-documenting
   \item run through the table again and check the counterexamples line up. 
+  \item MF and WN iff NF (see in hierarchy section) should be an intersection rather than logical and (change to be made in paper and agda code).
+Similarly it should be the double arrow iff.
+Check through paper for similar changes.
 

### 2025-12-03 Relations/Paper/pldiSubmission/Implications.tex
Created a submission folder to make addressing potential reviewer comments easier.

--- 2025-11-12 Relations/Paper/Implications.tex
@@
 
+The developments of this section are formalized in the files 
+\texttt{Properties.agda} and
+\texttt{Implications.agda} inside the \texttt{ARS} folder.
+
 This section examines the hierarchy of ARS properties.
-In programming language theory, $\SN$ and $\CR$ constitute the essential properties that
+In programming language theory, $\gSN$ and $\gCR$ constitute the essential properties that
 jointly establish completeness.
@@
     \begin{description}
-        \item[\bq \ule{$a \in \MF_R$}] \emph{$a$ is a minimal form} if $a \mstep b \implies b \mstep a$ for any $b \in A$.
-        \item[\bq \ule{$a \in \WM_R$}] \emph{$a$ is weakly minimalizing} if $a \mstep b$ for some $b \in \MF_R$.
-        \item[\bq \ule{$a \in \SM_R$}]  \emph{$a$ is strongly minimalizing} if either $a \in MF_R$, or every element one $R$ step from $a$ is strongly minimalizing. (This
-        definition is to be understood inductively).
-        \item[\bq \ule{$a \in \SMseq_R$}] \emph{$a$ is sequentially strongly minimalizing} if for every $R$-increasing sequence $s$ starting at $a$, there exists
+        \item[\bq \ule{$a \in \MF_R$}] $a$ is a \bemph{minimal form} if $a \mstep b \implies b \mstep a$ for any $b \in A$.
+        \item[\bq \ule{$a \in \WM_R$}] $a$ is \bemph{weakly minimalizing} if $a \mstep b$ for some $b \in \MF_R$.
+        \item[\bq \ule{$a \in \SM_R$}]  $a$ is \bemph{strongly minimalizing} if either $a \in MF_R$, or every element one $R$-step from $a$ is strongly minimalizing. (This
+        definition is to be understood inductively.)
+        \item[\bq \ule{$a \in \SMseq_R$}] $a$ is \bemph{sequentially strongly minimalizing} if for every $R$-increasing sequence $s$ starting at $a$, there exists
         an $i \in \nat$ such that $s (i) \in \MF$.
-        \item[\bq \ule{$a \in \MP_R$}] \emph{$a$ has the minimal form property} if $c \bmstep a \mstep b \implies c \mstep b$ for any $b \in \MF$.
+        \item[\bq \ule{$a \in \MP_R$}] $a$ has the \bemph{minimal form property} if $c \bmstep a \mstep b \implies c \mstep b$ for any $b \in \MF$.
     \end{description}
@@
 The implication from $\SN$ to $\WN$ relies on the classical decidability of the property
-of being $R$-minimal, as demonstrated in our formalization:
+of being $R$-minimal, hence its formalization takes the form
 
@@
 
+The necessity of assuming a classical axiom for this implication is discussed 
+in Subsection \ref{sec:SNtoWN} and
+Section \ref{sec:Well-foundedness}.
 The same property is similarly required in order to show that $\SM$ implies $\WM$.
@@
 \begin{proof}
-    See \texttt{module Normalizing-Implications} in \texttt{Implications.agda},\\
+    See module \texttt{Normalizing-Implications} in \texttt{Implications.agda},\\
     \verb|MF∧WN↔NF : ∀ {x} → MF x × WN x ↔ NF x|\\
@@
 The following tables illustrate, for each property combination, whether confluence (left box) and strong normalization (right box) are obtained.
-Where properties cannot be derived, we provide counterexamples demonstrating the necessity of additional conditions.
+Where these properties cannot be derived, we provide counterexamples demonstrating the necessity of additional conditions; these are labeled as CE-X.
 
@@
         \item $\gWN \land \gUNto \implies \gCR$ only holds when the properties are global. Counterexample~\ref{CE:4} shows that $\WCR \land \WN \land \UNto \nRightarrow \CR$.
-        \item We have a generalization of Newman's Lemma as $\SM \land \gWCR \implies \CR$. This is explored in Subsection \ref{subsec:newnewman}.
-        \item Both $\SM$ and $\WN$ are required for $\SN$, this connection is explored in Subsection \ref{subsec:SMWNSN}.
+        \item Both $\SM$ and $\WN$ are required for $\SN$, see Subsection \ref{subsec:SMWNSN}.
+        \item We have a generalization of Newman's Lemma as $\SM \land \gWCR \implies \CR$.
     \end{enumerate}
@@
 obtain completeness when we have $\gWN$ and $\gSM$.
-To show that $\gSM \land \gWN \implies \gSN$ we built on our proof that $\SM \land \WN \land \NP \implies \SN$. If $\gWN$ holds
+To show that $\gSM \land \gWN \implies \gSN$ we build on our proof that $\SM \land \WN \land \NP \implies \SN$. If $\gWN$ holds
 then our proof no longer requires the property $\NP$. This progression of proofs can be seen in the functions:
@@
 normalization to weak normalization is actually not provable.
-A counterexample is furnished in the file \texttt{WFCounters.agda}.
+Indeed, the file \texttt{ARS/Examples.agda} shows that assuming this implication 
+for all relations on the natural numbers derives excluded middle.
 % This fact is related to the subtleties arising in constructive formulation of
@@
 1) decidable, and 2) finitely branching.
-This is formalized in file \apcomment{Need to fill this in.}
+This is formalized in the file \texttt{ARS/Implications.agda} as
+
+\verb|dec∧FB→SN⊆WN : R isDec → R isFB → SN ⊆ WN|
 
 Since these conditions are in fact satisfied by all of the standard
-term rewrite systems and lambda calculi, we see that for such ARSs the implication
-is automatically valid.
+term rewrite systems and lambda calculi, we see that for the ARSs they induce, the implication
+is valid.

### 2025-12-03 Relations/Paper/Summer_2025_TODO.tex
Todo update

@@
   \begin{todolist}
-    \item (Review 1) Elaborate on our motivations in the introduction (reviewer wasn't sure how relevant this is to ARS theory itself/ sees it as too minor a contribution.)
+    \item [\done] (Review 1) Elaborate on our motivations in the introduction (reviewer wasn't sure how relevant this is to ARS theory itself/ sees it as too minor a contribution.)
     \item [\done] (Review 1) Typo: incaranations $\to$ incarnations.
@@
     \item [\done] (Review 1) Citation expansion for program=proof.
-    \item (Review 2) Unconvinced by the motivations for the project, believes the same can be achieved in a classical framework. So maybe we should explain our motivations more clearly.
+    \item [\done] (Review 2) Unconvinced by the motivations for the project, believes the same can be achieved in a classical framework. So maybe we should explain our motivations more clearly.
     \item [\done] Not convinced by our definitions, as they are imprecise and lack quantifiers.

### 2025-12-03 Relations/Paper/Winter_2025_TODO.tex
Todo update

--- 2025-11-13 Relations/Paper/Summer_2025_TODO.tex
@@
 \begin{document}
-\title{Summer 2025 ToDo}
+\title{Winter 2025 ToDo}
 \maketitle
 
-\section*{September 2025}
-\subsection*{Notes from 7th September}
-Thoughts on the current state of the paper.
-\begin{description}
-\item[The status of wfCor]
-  \begin{itemize}
-    \item 
-      On the ``missing'' implication isWFCor$\lnot\lnot$ to isWFminDNE$\lnot\lnot$.
-
-      The wfCor hypothesis needs a ``choice function'' that will pick a successor $y$ of a given element $x$
-      (while still refuting the given predicate).
-
-      The property wfMinDNE$\lnot\lnot$ is equivalent to the statement that, if a $\lnot\lnot$-closed 
-      predicate $P$ has no minimal element, then its complement is universally true.
-
-      The ``no minimal element'' for not-not-closed $P$ is close to saying that its complement is coreductive; 
-      the difference is precisely that between the ``strong'' existential in the coreductive statement ---
-      and the weak one (with $\lnot\lnot$ applied to it) in the minimality one.
-
-      Assuming finite branchingness and weak decidability of $P$, we could get the strong existential 
-      from the weak one.  However, weak decidability and DNE are already equivalent with EM, so that 
-      will only apply to decidable predicates.  There may be a relationship to isWFminEM, but that 
-      would be a question for another paper.
-
-    \item 
-      On the ``strong side'' of the WF diagram, the situation is even worse.
-      Neither implication between isWFCor and isWFminDNE is provable, and similarly for isWFCor and isWFSeq.
-
-    \item 
-      At this point, there does not appear to be much more to say isWFCor, so we should consider removing it.
-
-      On Monday, we should quickly discuss the different versions of sequentially,
-      and move on to writing the text of the paper.
-    \end{itemize}
-\end{description}
-
-\section*{Week starting 21st April}
-\begin{itemize}
-  \item Items from review
-
+\section*{December 2025}
+\subsection*{Carry over from previous TODO}
 \begin{todolist}
-    \item (Review 1) Elaborate on our motivations in the introduction (reviewer wasn't sure how relevant this is to ARS theory itself/ sees it as too minor a contribution.)
-    \item [\done] (Review 1) Typo: incaranations $\to$ incarnations.
-    \item [\done] Improve fonts for constant and text (refering to a definition on line 258). General formatting imrpovement for how we set out defns.
-    \item [\done] (Review 1) Improve the layout on line 270 where we set out iiSeq.
-This should get fixed with an overall improvement in how we set out definitions.
-We should stop using itemize and verb combination.
-    \item [\done] (Review 1) Typo: we obtaining $\to$ we obtain (this is in the conclusion which we want to rewrite entirely).
-    \item [\done] (Review 1) Citation expansion for program=proof.
-    \item (Review 2) Unconvinced by the motivations for the project, believes the same can be achieved in a classical framework. So maybe we should explain our motivations more clearly.
-    \item [\done] Not convinced by our definitions, as they are imprecise and lack quantifiers.
-    \item [\done] Issue with definition of R|=RP on line 188. Use of bounded is ambiguous. We should clarify which use of bounded.
-    \item [\done] Improve proposition 11 on line 194, we want to make the clame that RP- $\to$ RP, and either have a one line proof or refer to the proof in Agda.
-    \item [\done] Section 3 is "full of repetitions and paraphrases between the statements in natural language and corresponding formalization".
-We can try and think of a way to get it to flow better, we do want to provide natural language summaries of what is in the code!
-    \item [\done] (Review 2) Struggled to understand the implications tables.
-We should add a reminder that bold font is global.
-We should rethink the tables generally to make them clearer.
-\apcomment{Don't comma seperate and don't denote counterexamples as CE-XX.
-?}
-    \item [\done] Struggled to find the relevant agda code for the various definitions. We should find a way to better link the two.
-    \item [\done] Clarify Notation 7 on line 159: "Choose a uniform notation, X or NP, but not both".
-    \item [\done] l 169: An annoying notational collision between the two arrows -> at different heights."I'm not too sure what they're referring to, though there could be some ambiguity with the arrows here, especially with use of $UN\to$.
-    \item [\done] (Review 2) "l 361: Swap s(k+1) and s(k) " We should clarify the definition here otherwise people (evidently) get confused.
-    \item [\done](Review 2) "l 422: $P_x$ has no arguments?"
-    \item [\done] (Review 3) Check out and include the following related work:
-    \begin{itemize}
-        \item Christian Sternagel and René Thieman formalized results on Abstract Rewriting in Isabelle https://www.isa-afp.org/entries/Abstract-Rewriting.html
-        \item André Galdino and Mauricio Ayala-Rincón also developed a theory in PVS regarding ARS and TRS  https://github.com/nasa/pvslib/tree/master/TRS
-        \item What are the differences and improvements of the formalization in this paper and the ones in the literature?
-        \item (Review 2) TeReSe is not state of the art. We need state of the art references. Try this: https://termination-portal.org/wiki/WScT
-    \end{itemize}
     \item (Review 3) * From the formalization, the authors could explain some features and syntax of Agda for readers unfamiliar with this proof assistant.
@@
 12.
-    \item [\done](Review 3) In line 270, isWFseq- is used in Section 3 but defined only in Section 5.
-    \item [\done] (Review 3) In line 192, the authors state that (in TeReSe) Ind denotes BP.
-However, in line 186, BP is defined from an R-increasing sequence, whereas this statement is not required in the definition of Ind by TeReSe.
-How does this difference impact the formalizations and generalizations pointed out in Section 3.3.3?
-(Maybe we should explicitly address all difference with TeReSe in one location.)
-  \end{todolist}
-
-  \item Other ToDo
-  \begin{todolist}
-    \item [\done] Make Latex version of WF implications (initial draft).
-    \item [\done] Verify which implications have and have not been formalized from the image.
-    \item [\done] $\lnot \lnot$ WFacc $\leftrightarrow$ $\lnot \lnot WFind$.
-    \apcomment{WFind to be removed, this is addressed in the Friday June 13th notes}
-    \item [\done] (Missing imp) WFmin- $\to$ WFDNE-
-    \item [\done] (Missing imp) All of the implicaions from the standard WF definition to the $\lnot \lnot$ definition.
-    \item [\done] Sam TODO: I still don't have a coherent understanding in my head as to how we relate the WF and ARS sections of the paper.
-I need to go through it and either understand it or come with questions to Friday's meeting.
-  \end{todolist}
-\end{itemize}
-
-\section*{Week starting April 28th}
-\begin{itemize}
-  \item Below notes from meeting on April 25th.
-  \begin{todolist}
-    \item [\done] Fix Wellfounded.agda after changes made during meeting.
-    \item [\done] Think about how to organize the Git repo going forward. For example, could be good to have a parent folder with ARS and WF, with a private dir for paper
-
-  \end{todolist}
-
-\end{itemize}
-\section*{Week starting 26th May}
-\begin{todolist}
-  \item [\done] Double check the counterexamples match in the table to the diagrams.
-  \item [\done] Make clear in proof references to agda code how it should be read (especially the first one). Make clear the module as well. After doing once, the others don't need to be as explicit.
-  \item [\done] find a seperate symbol for -> in the code sections in the paper for UN$\to$. Superscipt would be perfect. $UN^{\rightarrow}$
-  \item [\done] Mention theorem 123 ii and iii are inherently classical. For iii we require strong decidability.
-  \item [\done] Working on CR $\to$ CP. Low priority. \apcomment{This is mentioned as one of the research items above}
-\end{todolist}
-
-\section*{Week starting 2nd June}
-\begin{todolist}
-  \item [\done] Should we add quantification to each definition(I think quantification for $a$ is already implied)? E.g.\\
-  \item [\ule{$a \in \WCR_R$}] \emph{$a$ is weakly Church-Rosser (or weakly confluent)} if $c \bstep a \rstep b \implies c \mstep d \bmstep b$.\\
-   Transforms to
-  \item[\ule{$a \in \WCR_R$}] \emph{$a$ is weakly Church-Rosser (or weakly confluent)} if $c \bstep a \rstep b \implies c \mstep d \bmstep b$ for all $b, c, d \in A$.
-  \item [\done] For showing inc -> RP we're currently just saying "This is immediate". Is this sufficient? We did have a proof previously but I think we removed it for space reasons.
-  \item [\done] Remove "desired implications" and similar organizational issues in the code (general review)
-  \item [\done] Consider defining FB in terms of existing list library; especially in the rebooted repo,
-  we shouldn't use manual List type just for this.
-  \item [\done] Move all definitions and properties from Section 2.3 to Seq.agda, except Inc.
-  \item [\done] Revise section 3.1
-\end{todolist}
-\section*{Week starting 9th June (some of these items taken from Dr. Polonsky's email sent June 6th)}
-\begin{todolist}
-  \item [\done] Thm. 19(iv), i don't like that the parens are italicized.  maybe it would be okay if instead of CR => CP we just write "the forward implication"
-  \item [\done] Proof of (iii), line 296: do we really need () around SN?
-  \item [\done] Page 9, second half (the hierarchy): we should add a proof that $\MF \cap \SN \iff \NF$, say this in the text, and note that this does NOT hold for $\SM$ and $\WN$.
-Hence, the tables include a separate column for their combination.
-  \item [\done] In the par before 4.1 counterexamples, add that in the global table, the counterexample 3 satisfies the hypotheses globally.
-(I actually wonder whether we need example 9 at all, if we have a counterexample to the global one.
-Am I missing something?).
-\sacomment{I don't think we need to expand that CE:3 satisfies the global hypotheses.
-I'm hoping that we've done enough to show to the reader how to read the table at this point.
-If you disagree I'm happy to add it in though.
-As to why have local and global counterexamples, good point.
-Unless either of us can think of a reason we'll remove in the next meeting.}
-    \item [\done] the * and dagger in the table should be explained in the caption, or in the text.
-    \sacomment{I prefer to have this as a footnote. I have put it as a caption for now but I would revert it to what we had before.  }
-\end{todolist}
-
-\subsection*{Notes from meeting on Friday June 13th}
-
-\begin{itemize}
-  \item[\done] Perhaps we should not create variations and multiple implications of WFind,
-  but rather prove that it's equivalent to WFacc, but lands in a higher universe.
-  Mention this once at the beginning of section 5 then proceed to analyze
-  connections between WFacc and WFseq/WFmin.
-\end{itemize}
-
-\section*{July TODO}
-\begin{todolist}
-\item [\done] Carry on refactoring Wellfounded.agda once fixed, breaking it up if necessary.
-\item [\done] To finish the paper: We should do a final walk through and make sure we haven't introduced errors with our edits.
-In particular, do all the counterexamples line up.
-Do all the references to different sections and pieces of code in Agda line up.
-  \item [\done] Do we remove all our local counterexamples in favour of global ones?
-  \item [\done] Rework well-foundedness section 
-  \item[\done]  Rework conclusion 
-  \item [\done]  Rework introduction 
-  \item  [\done] Do we introduce a new section for discussing Agda? Talking about why we think there is an advantage to doing this work in Agda vs (say) Isabelle
-
-\end{todolist}
-
-\section*{Research items}
-\begin{todolist}
-\item[\done] (Research item) Go deeper in the related works and see which are most relevant.
-Make a list of works and give summaries to be used in future papers.
-* Look into the literature and related works.
-There should be an Agda formulation of rewrite systems (check agda standard library stuff on relations).
-  \item (Research item) Find a concrete application of generalized Newman's Lemma.
-* Finding a term rewrite system where it's eassier to see that it is weakly cr and that every term is SM (as opposed to being CR).
-  \item (Research item) Formalize a first order term rewriting system (I can't remember what the motivation for this was). Use TeReSe to create a list of rewrite systems.
-  \item (Research item) Carry out research on rewriting counterexamples like our own so we can try and put them into some sort of context. Have our counerexamples been shown before?
-  \item (Research item) Work on the missing implicaitons from the paper. So far we believe this is just CR $\to$ CP in the ARS section. - Will probably be quite a bit of work (low priority)
-  \item (Research item) Do we want to reincorporate Knaster Tarski? - Not this paper 
-  \item (Research item) How to go from WFseq to WFacc - possible that the Kleene Tree is a solution. - Not this paper
-  \item (Research item) Investigate: what we've done for natural numbers could be done for an arbitrary ARS (in the counter examples files), but for weak minimality and weak excluded middle. 
-  \end{todolist}
-
-\section*{Agda standard library}
-Some of the work we have explored is formalized in the Agda standard library.  
-% https://agda.github.io/agda-stdlib/v1.7.3/Relation.Binary.Rewriting.html#2096
-\begin{todolist}
-\item[\done] Write about the standard library formalization in our paper and talk about how ours differs. 
-\item[X]  Create an equivalences file showing that our formalization agrees with the ASL (specifically definitions such as confluet, wcr, nf, leading up to showing our formalizations of Newman's lemma agree).
+    \item  Create an equivalences file showing that our formalization agrees with the ASL (specifically definitions such as confluent, wcr, nf, leading up to showing our formalizations of Newman's lemma agree).
   \item Investigate contributing work to the ASL.
@@
 Theorem's 122 and 123.
-Alternative definitions of Wellfounded, the implications for the hierarchy.
-\end{todolist}
-
-\section*{20th August todos}
-\begin{todolist}
-  \item [\done] (Secondary) Find consistency with NP and UN with respect to reduction and conversion.
-Should the default be by reduction for both.
-Should we be explicit with $\to$ and = in each case.
-\sacomment{Main issue here is that we'll either introduce an inconsistency with our code or we'll have a hard to read symbol.
-We can do $\to$ as super or sub-script in Agda.
-If we're happy with $NP\to$ in agda but using a different script in the paper then I think we should go ahead and be explicit for both UN and NP as to whether it is WRT conversion or reduction.
-We already have this inconsistency in the code with $UN\to$} \apcomment{In the agda code let's not use arrow and have arrow implied as default but be explicit with '=' sign.}
-  \item [\done] Carry on modifying the names of wfXXX- to wfXXXnotnot with prefix underscore in agda and in latex.
-\sacomment{Done with the exception of WFseq-.
-This needs a bit more thought.
-Similarly for the relation between WFcor and WFminCor.}
-  \item [\done] Make a decision regarding WFcor.
-We use it to imply WFacc using AccCor.
-But otherwise it is sort of orphaned off.
-Does it help contribute to the overall story?
-\sacomment{We've now related it to WFmin by requiring that correductive predicates have double negation elimination.
-Is this too strong a requirement?
-Similarly we have linked WFacc to WFcor but this proof requires the same property as well as limiting ourselves to accessible predicates.
-Again, is this too much?}
-  \item [\done] Get the classical hypothesis and relations organized and see how they're used in the implications (organize implications by classical requirement.
-In the implications file we can import the classical implications.
-Basically, refactor the code.) \sacomment{Done but could be further refactored.}
-  \item [\done] Make a cheat sheet for the next meeting regarding to talk about coreductive.
-How it relates on the weak side and on the strong side.
-SEQ seq+- , how to present these.
-Try and clarify what the issues are here and what exactly are the differences between them in terms of definition and implication.
-Could one be removed and the overall story stay the same?
-\sacomment{Regarding seq+ (and seq+-) we currently only show that seq+ implies seq and seq+- implies seq- so could be removed without changing any of our other implictions.}
-\end{todolist}
-
-\section*{September 15th todo}
-\begin{todolist}
-\item[\done] (Minor) We want to have a sentence in our WF section making clear that we can consider local properties as well and maybe make an example from accessible to sequential. 
-  \item[\done] Sentence explaining that wfacc is equivalent to wfind and therefore isn't included in the diagram (wfind).
-\end{todolist}
-
-\section*{September 26th TODO}
-\begin{todolist}     
-\item[\done] Focus for next meeting on writing. 
-  \item [\done] Are not not closed predicates over natural numbers dedcidable: If not is this a counterexample for WFminDNE.
-\end{todolist}
-
-\section*{October 10th TODO}
-\begin{todolist}     
-\item[\done] Want to show that FB and weak decidability gives us accCor (think we may have shown this previously)
-  \item[\done] Add 'is' to wfcor macros.
-  \item[\done] make a decision on wfseq not not name. 
-  \item[\done] Keep on cleaning the WF section in paper. 
-\end{todolist}
-
-\section*{October 15th TODO / Oct 22nd}
-\begin{todolist}     
+Alternative definitions of Well-founded, the implications for the hierarchy.
   \item  It's possible to have a term rewrite system with good properties like FB and the relation being decidable.
@@
 Not sure if it can be done with strong normalization.)
-  \item [\done] Do a final read through of the information below the figure. Have we captured all the most important information / Are we repeating ourselves?
-  \item [\done] Do we want to keep anything in the old/delete section of WF?
-  \item [\done] Do we want to add anything about counter examples or positive examples? 
-  \item [\done] We may want to use words rather than macros in certain locations
-  \item [\done] Check through the comments in general in the section. 
-\item [\done]  CHange WFseq not not to WFseq- in the macro. We are sticking with this for now. If we have time we can investigate the relation between the two.
-\item [\done]  Make the diagram horizontal rather than vertical. Spoof it up and we can compare next week.
-\item [\done]  Use of macros in WF section. Double check the right one is being used. Don't use the "is'' macro at all in this section. Be consistent on whether we are using macros. 
-\item Does WFseq- with MP== imply WFseq? (W're thinking it will need rdec as well to give us the implication).
-\item [\done] make the WF macro bold font?
-\item add wfseq not not to the definitions?
-\item [\done] Go through the bibliography links. Not all of them are currently working!
+  \item Is there a path from WFseq- with MP== to WFseq? (W're thinking it will need rdec as well to give us the implication
+  ).
+ \item incorporate wfseq not not to the paper?
  \item We want to start looking at examples.
@@
 Can we prove is isn't satisfied?
-\item [\done] Make a connection in the final WF section talking about how SN doesn't imply WN constructively. (we've started writing this sentence). 
-\item [\done] We may need to add to the WFCounters file, if we have SN implies WN then every subset of the natural numbers is decidable.  
-\item [\done] Make sure we have a proof of the implication from SN to WN given FB and decidability of a relation (to back up our claim in our introduction).
  \item check TERESE and see first order term rewrite systems example which could be valid for showing classical and constructive formalization coincide.
 First order term rewrite systems are (always?) fb and R is dec.
-\item [\done] Change the macro for FB so that it is also boldface
-\item [\done, did SN to WN instead] update wfcounters to show that asserting wfmin implies the excluded middle (and wfmindne the weak excluded middle).
-\item [\done] In wfcounters we should have a system that is SN but not WN (WN implies excluded middle).
-
-\end{todolist}
-
-\section*{Plan for PLDI submission}
-\begin{todolist}
-  \item[X] Aim for first draft finished by the end of the 29th.
-  \item[\done] Make a main file at this point to conform to this conference's style. Possibly a sub-folder for each conference.
-  \item [\done] discussion env has qed boxes which shouldn't be there.
-  \item[\done] from wellfounded extra move the implication of fb -> isdec -> isMinDec. move to implications. 
-  Use this to take this SNdec→WN to have a full proof from fb, isdec, sn -> wn. (issue in moving to fb file due to reversal of relation direction!) 
-  \item [\done] Make consistent how we display definitions. 
-  \item [\done] Work on the conclusion
-  \item [\done] Need to fix how we put urls in for bibliography. Currently not quite working. \sacomment{Now all urls, if happy with how it looks we can tick it off. }
-  \item [\done] Check the PLDI page for submission rules/requirements. In particular the bibliography style 
-  \item [\done] Run through and compile everything, make sure we didn't introduce any bugs
-  \item [\done] Check the layout of figures through the paper. Counterexamples for example is currently `off'.
-  \item talk about why we use agda in 1.2 Agda is the perfect system for formalizing programming language theory.  
-  \item Submit 
-  \item Add a paragraph or two giving a short overview/summary of Agda.
-  \item Go through the code, make naming consistent and self-documenting
-  \item Once we've got a current draft finished. Look in Teresa for first order term rewrite systems and see how many we can represent using our code.
-  \item Consider adding some more motivations 
-  \item Look at the seq-minus vs. seq-not-not issue 
-  \item Final read through (wed?)
-  \item make an external bibliography file rather than inlining in main file. Make sure bibliography is up to standard (e.g. emph on book title).
-\item Submission deadline is Thursday 13th 
-\item MF and WN iff NF (see in hierarchy section) should be an intersection rather than logical and (change to be made in paper and agda code).
-Similarly it should be the double arrow iff.
-Check through paper for similar changes.
-\end{todolist}
-
-\section*{Post pldi todos}
-\begin{todolist}
   \item Make the well founded definitions conform to the style of the definitions in other sections.
@@
   \item We made a bodge fix for not right arrow in use in well founded. It is good enough for now but there should be a better way to express it in latex. (when defining isMinDec)
+  \item Go through the code, make naming consistent and self-documenting
   \item run through the table again and check the counterexamples line up. 
+  \item MF and WN iff NF (see in hierarchy section) should be an intersection rather than logical and (change to be made in paper and agda code).
+Similarly it should be the double arrow iff.
+Check through paper for similar changes.
 
 \end{todolist}
-
-notes to self:
-- Tell Dr. P to check out the trs pvs paper.
-
+\section*{Research items}
+\begin{todolist}
+  \item (Research item) Find a concrete application of generalized Newman's Lemma.
+* Finding a term rewrite system where it's easier to see that it is weakly cr and that every term is SM (as opposed to being CR).
+  \item (Research item) Formalize a first order term rewriting system. Use TeReSe to create a list of rewrite systems.
+  \item (Research item) Carry out research on rewriting counterexamples like our own so we can try and put them into some sort of context. Have our counterexamples been shown before?
+  \item (Research item) Work on the missing implications from the paper. So far we believe this is just CR $\to$ CP in the ARS section. - Will probably be quite a bit of work (low priority)
+  \item (Research item) Investigate: what we've done for natural numbers could be done for an arbitrary ARS (in the counter examples files), but for weak minimality and weak excluded middle. 
+  \end{todolist}
 \end{document}

### 2025-12-04 Relations/Paper/Well-foundedness.tex
Fixed minor macro issues

@@
 In this section, we will compare several definitions of well-foundedness.
-For ease of exposition, we will only consider local versions of these notions.
+For ease of exposition, we will only consider global versions of these notions.
 (There is no loss of generality in this; any global well-foundedness property $\gWF(A;R)$ 
-restricts to a predicate $WF_R$ on $A$ via $WF_R(x) = \gWF(\Sigma y : A. R^* x y;R')$, 
-where $R'((y,\rho),(z,\sigma)) = R(y,z)$.)
+restricts to a predicate $WF_R$ on $A$ via $WF_R(x) = \gWF(\Sigma y {:} A. R^* x y;R')$, 
+where $R'((y,\rho),(z,\sigma)) = R(y,z)$; now $\gWF(A;R) \leftrightarrow \forall x. WF_R(x)$.)
 %which depend on the basic notions given in Definition~\ref{def:WFnotions} below.
@@
 \begin{definition} \label{def:WFproperties} \hfill
-  \begin{enumerate}
+  \begin{itemize}
     \item $R$ is \emph{accessibly well-founded} ($\WFacc$) if every element is accessible:
@@
       \]
-    \item \label{def:WFind} $R$ is \emph{inductively well-founded} ($\WFind$) if every inductive predicate is universally true:
+    \item %\label{def:WFind}
+      $R$ is \emph{inductively well-founded} ($\WFind$) if every inductive predicate is universally true:
       \[
@@
       \]
-  \end{enumerate}
+  \end{itemize}
 \end{definition}
@@
 \begin{definition} \label{def:WFweakproperties} \hfill
-  \begin{enumerate}
+  \begin{itemize}
     \item $R$ is \emph{weakly accessibly well-founded} ($\WFaccm$) if accessibility holds for all elements up to double negation:
@@
     \]
-\end{enumerate}
+\end{itemize}
 \end{definition}
@@
 All of the implications in the figure have been
-formalized within the WellFounded subdirectory of the Agda repository.
+formalized within the \texttt{WellFounded} subdirectory of the Agda repository.
 An arrow from one node to another with no label indicates direct logical implication,
@@
 As can be seen from the figure, it is implied by
-Terese's definition $\WFseqm$ only when \emph{two}
+$\WFseqm$ (the definition used by \terese) only when \emph{two}
 strongly classical conditions are in place.
@@
 \small
+% \renewcommand{\Sigma}{{\scriptstyle{\sum}}}
+% \renewcommand{\Sigma}{{\sum}}
 \begin{tabular}{@{}l l l @{}}
@@
 $\FB$     & $R$ is finitely branching
-          & $\mathtt{\forall (a : A) \to \Sigma [ xs \in List A ] (\forall b \to R a b \to b \in{}List\, xs)}$ \\
+          & $\mathtt{\forall (a : A) \to}\Sigma\mathtt{[ xs \in List A ] (\forall b \to R a b \to b \in{}List\, xs)}$ \\
 $\mpe$    & Sequences are $\lnot\lnot$-closed
           & $\forall\ \mathtt{(f : \nat \to A) \to \lnot\lnot Closed
-          (\lambda x \to \Sigma [ k \in \nat ] (f\, k \equiv x))}$ \\
+        (\lambda x \to} \Sigma \mathtt{[ k \in \nat ] (f\, k \equiv x))}$ \\
 $\corDNE$ & Coreductives are $\lnot\lnot$-closed
@@
 % On the other hand, the reverse
-At the same time, the weak version of the sequential definition is unable to imply
-the (weak) accessible one without an additional hypothesis $\accCor$,
+At the same time, the implication from the weak version of the sequential definition 
+to the (weak) accessible one still requires the hypothesis $\accCor$,
 which may be described as the constructive contrapositive of the definition of accessibility.
@@
   has a least element.  This statement and its $\lnot\lnot$-version are both equivalent to $\WFcorm$
-  (see \texttt{CoreductiveImplications.agda}), so we have not included them in the figure.
+  (see \texttt{WFCoreductiveImplications.agda}), so we have not included them in the figure.
 
-We also did not include the inductive definition, Definition \ref{def:WFproperties}.\ref{def:WFind}.
+We also did not include $\WFind$ from Definition \ref{def:WFproperties}.
 Logically, it is trivially equivalent to the accessible one, but its Agda formalization has a defect:
@@
 Such distinctions have consequences for rewriting theory.
-For example, recall that $x\in \SN_R$ iff $x$ is $\bar{R}$-accessible, where $\bar{R}$
-is the converse of $R$.  Thus, if $\bar{R}$ is well-founded, $R \models \gSN$.
+For example, recall that $x\in \SN_R$ iff $x$ is $\tilde{R}$-accessible, where $\tilde{R}$
+is the converse of $R$.  Thus, if $\tilde{R}$ is well-founded, $R \models \gSN$.
 Yet actually computing the normal form of a given $x$ requires a
@@
 \[
-\tag{$\isMinDec$} \forall x. \left(\exists y. Ryx\right) \lor \left(\forall y. \lnot Ryx\right)
+  \tag{$\isMinDec$} \forall x. \left(\exists y. x \rstep y \right) \lor \left(\forall y. x \nrstep y\right)
 \]
@@
 % Note that deciding whether $x$ is a normal form constitutes the weaker disjunction
-$\lnot\lnot\left(\exists y. Ryx\right) \lor \left(\forall y. \lnot Ryx\right)$.
+$\lnot\lnot\left(\exists y. x \rstep y\right) \lor \left(\forall y. x \,\,\not \!\!\!\! \rstep y\right)$.
 Indeed, in the file \texttt{ARS/Examples.agda} the implication $\gSN \to \gWN$ for all relations $R$

### 2025-12-04 Relations/Paper/Winter_2025_TODO.tex
Fixed minor macro issues

@@
   % \newcommand{\dneg}[1]{\overline{\smash{\overline{#1}}\vphantom{#1}}} % tight double overline
+  (Have tried a number of solutions, none seem to quite get what we want. Putting this off for now as low priority.)
   \item The sigma symbol was being rendered as a degree symbol. Why? Also, our solution is slightly too big, try and make it smaller (see well founded classical definitions).
-  \item We made a bodge fix for not right arrow in use in well founded. It is good enough for now but there should be a better way to express it in latex. (when defining isMinDec)
+  \item [\done] We made a bodge fix for not right arrow in use in well founded.
+It is good enough for now but there should be a better way to express it in latex.
+(when defining isMinDec) (new macro nrstep fixes it).
   \item Go through the code, make naming consistent and self-documenting

### 2025-12-04 Relations/Paper/Winter_2025_TODO.tex
Work 4th December through

@@
 Can we prove is isn't satisfied?
- \item check TERESE and see first order term rewrite systems example which could be valid for showing classical and constructive formalization coincide.
+ \item Formalize perpetual strategy for untyped lambda calculus and conclude that the weak WF statements define the same subset of (untyped) lambda terms.  
+ \item check TERESE and see which first order term rewrite system examples which could be valid for showing classical and constructive formalization coincide.
 First order term rewrite systems are (always?) fb and R is dec.
+ \item If we formalize a first order rewrite system, this would allow other avenues of investigation.
+E.g.
+conjecture that in general first order rewrite system is FB and dec, and therefore SN implies WN.
+Because of the rewrite rule: "every variable occuring in the right hand side r occurs in l as well" we should be able to achieve this.
+And it will not be true in the absrtact context.
  \item Make the well founded definitions conform to the style of the definitions in other sections.
@@
 Do we want all definitions to be itemized?
-  \item Improve how we write P bar bar for the definitions in wellfounded (well founded minimality wise). Chat makes the following suggestion (see commented out line in tex file):
-  % \newcommand{\dneg}[1]{\overline{\smash{\overline{#1}}\vphantom{#1}}} % tight double overline
-  (Have tried a number of solutions, none seem to quite get what we want. Putting this off for now as low priority.)
-  \item The sigma symbol was being rendered as a degree symbol. Why? Also, our solution is slightly too big, try and make it smaller (see well founded classical definitions).
+(low priority, and probably not itemized).
+  \item [\done] Improve how we write P bar bar for the definitions in wellfounded (well founded minimality wise).
+there is probably a way to adjust the height of a character which may solve this problem.
+  \item [\done] The sigma symbol was being rendered as a degree symbol. Why? Also, our solution is slightly too big, try and make it smaller (see well founded classical definitions).
   \item [\done] We made a bodge fix for not right arrow in use in well founded.
@@
 Check through paper for similar changes.
+  \item Check if there is a first order term rewrite system formalization in ASL. If so, do they have a proof of SN $\to$ WN. If not, this is an interesting avenue to explore (see earlier TODO point).
 
@@
   \item (Research item) Investigate: what we've done for natural numbers could be done for an arbitrary ARS (in the counter examples files), but for weak minimality and weak excluded middle.
+(This is what we were working on end of day 4th December).
   \end{todolist}

### 2025-12-09 Relations/Paper/Winter_2025_TODO.tex
Todo update

@@
   \end{todolist}
+
+\section*{Week starting 8th December}
+\begin{todolist}
+  \item Is the new definition of wdec in Predicates correct?
+It corresponds to the definition in FBranching.
+(Do we want to go through and update all uses of Wdec with the new definition if it is correct?)
+  \item Go through the locations where we could use the wdec definition and replace it with our new wdec definition (search for wdec, previously we've manually defined it in each location)
+  \item $\lnot \lnot $closed C definition sometimes is a lambda term with three variables we can refactor this in those locations.  
+\end{todolist}
+
 \end{document}

### 2025-12-09 Relations/Paper/Winter_2025_TODO.tex
TODO update 9th December

@@
   \item $\lnot \lnot $closed C definition sometimes is a lambda term with three variables we can refactor this in those locations. 
+  \item can we show that  wfminDNE implies RisDec. We've shown that RisWFmin implies RisDec (in WFcounters). We've started the DNE proof in Wfimplications (commented out). 
+  \item [\done] We successfully proved that RisWFmin implies RisDec and RisMinDec!
+  \item We're trying to show that wfminDNE implies WEM (in WFcounters) (this is where we ended the session 9th December). Try using the commented out code to solve the goal on line 130. 
+  \item Ideal goal for next meeting is to formalize trs.
 \end{todolist}

### 2025-12-10 Relations/Paper/Winter_2025_TODO.tex
TODO update after 10th December session.

@@
   \item $\lnot \lnot $closed C definition sometimes is a lambda term with three variables we can refactor this in those locations. 
-  \item can we show that  wfminDNE implies RisDec. We've shown that RisWFmin implies RisDec (in WFcounters). We've started the DNE proof in Wfimplications (commented out). 
+  \item can we show that  wfminDNE implies RisDec. We've shown that WFmin implies RisDec (in WFcounters). We've started the DNE proof in Wfimplications (commented out). 
   \item [\done] We successfully proved that RisWFmin implies RisDec and RisMinDec!
-  \item We're trying to show that wfminDNE implies WEM (in WFcounters) (this is where we ended the session 9th December). Try using the commented out code to solve the goal on line 130. 
-  \item Ideal goal for next meeting is to formalize trs.
+  \item We're trying to show that wfminDNE implies WEM (in WFcounters) (this is where we ended the session 9th December). We currently think it is not possible.
+
+  \item [\done] We have made new discoveries as to what WFmin can imply.
+Can we use these developments to go from WFmin to WFacc?
+For example, with the addition of EM.
+Reminder that WFmin implies EM when R is non empty.
+  \item (high priority) Having shown that WFmin implies WFacc when R is non empty we need to update the paper.
+Specifically we should update the text in the WF section and the diagram to incorporate the new implication.
+Update the table too with R not empty?
+  \item [\done] Show that we can go from our weakest WF definition to our strongest
+  \item Do we want to make explicit on our table in the paper that we can go from our weakest definition (wfcornotnot) to our strongest (wfmin) via classical assumptions (EM).
+We think we already mention that all the definitions are classically equivalent in the paper (do we?).
+  \item We have moved the proof of wfmin implies EM to WFbasic implications. Can delete the old proof in WFcounters. 
+  \item can we show that wfminnotnot implies wfaccnotnot?
+That would give a nice equivalence between three definitions in the weak row of the diagram.
+One approach could be to see what predicates we can prove with just wfminnotnot (in the same way that we first explored what predicates could be proved with wfmin before finding out a path to wfacc).
+Perhaps wfminnotnot implies WEM?
+
+  \item We've started formalizing TRS in a new folder.
+This is our likely starting point for our next meeting.
+Before we meet it might be worth looking at the WF implications and see if we can add to it.
 \end{todolist}

### 2025-12-12 Relations/Paper/Winter_2025_TODO.tex
minor todo additions
Todo update end of Friday 12th December

@@
 \begin{todolist}
-  \item Is the new definition of wdec in Predicates correct?
+  \item [\done] Is the new definition of wdec in Predicates correct?
 It corresponds to the definition in FBranching.
 (Do we want to go through and update all uses of Wdec with the new definition if it is correct?)
-  \item Go through the locations where we could use the wdec definition and replace it with our new wdec definition (search for wdec, previously we've manually defined it in each location)
-  \item $\lnot \lnot $closed C definition sometimes is a lambda term with three variables we can refactor this in those locations. 
+  \item [\done] Go through the locations where we could use the wdec definition and replace it with our new wdec definition (search for wdec, previously we've manually defined it in each location)
+  \item $\lnot \lnot $closed C definition sometimes is a lambda term with three variables we can refactor this in those locations. (low priority) 
   \item can we show that  wfminDNE implies RisDec. We've shown that WFmin implies RisDec (in WFcounters). We've started the DNE proof in Wfimplications (commented out). 
@@
 Perhaps wfminnotnot implies WEM?
+  \item Work out what if any WF definition implies WEM (other than WFmin)?
+  \item Get rid of wfcor+ in our main development, substitute in the not not definition for consistency.
 
@@
 Before we meet it might be worth looking at the WF implications and see if we can add to it.
+
+  \item TRS: Complete our formalization. formalize some simple TRS to check our implementation works. 
+  \item TRS: Formalize orthogonality and show it is equivalent to our notion of confluence. 
+  \item [\done] We've shown that wfminDNE gives us decRmin is we have decidability of equality. 
+  \item [\done] We've shown that wfminDNE along with decidability of equality and not not closure of R gives us R is MinDec.
+  \item [\done] We show that R is weakly decidable with the assumption of wfminDNE and equality decidability.
+  \item Can we show that the not not closure of R emerges from WFminDNE?
+  \item Shown wfmindne not not implies wfacc not not with accDNE. Now need to update the paper/graph to reflect this.
+
+  \item [\done] We finished Friday's session by thinking we should be able to use our proofs from today to show wfmindne implies WEM (see wfcounters).
+If we have this, then we can show that wfacc implying wfminDNE would be absurd.
+This is probably a good launch for our next meeting.
+(We finished this quickly at the end of the session!
+We did require decidability of equality).
+  \item Tidy up wfcounters and consider whether any of the proofs want moving to wfbasic implications. 
+  \item What can we do with wfminDNE now that we have WEM? 
 \end{todolist}

### 2025-12-16 Relations/Paper/Winter_2025_TODO.tex
todo update prior to meeting Tue 16th Dec

@@
   \item [\done] We successfully proved that RisWFmin implies RisDec and RisMinDec!
-  \item We're trying to show that wfminDNE implies WEM (in WFcounters) (this is where we ended the session 9th December). We currently think it is not possible.
+  \item [\done] We're trying to show that wfminDNE implies WEM (in WFcounters) (this is where we ended the session 9th December). We currently think it is not possible.
 
@@
 We think we already mention that all the definitions are classically equivalent in the paper (do we?).
-  \item We have moved the proof of wfmin implies EM to WFbasic implications. Can delete the old proof in WFcounters. 
+  \item [\done] We have moved the proof of wfmin implies EM to WFbasic implications. Can delete the old proof in WFcounters. 
   \item can we show that wfminnotnot implies wfaccnotnot?
@@
 Perhaps wfminnotnot implies WEM?
-  \item Work out what if any WF definition implies WEM (other than WFmin)?
-  \item Get rid of wfcor+ in our main development, substitute in the not not definition for consistency.
+  \item [\done] Work out what if any WF definition implies WEM (other than WFmin)?
+  \item [\done] Get rid of wfcor+ in our main development, substitute in the not not definition for consistency.
 
@@
   \item Can we show that the not not closure of R emerges from WFminDNE?
-  \item Shown wfmindne not not implies wfacc not not with accDNE. Now need to update the paper/graph to reflect this.
+  \item We have shown wfmindne not not implies wfacc not not with accDNE. Now need to update the paper/graph to reflect this.
 

### 2025-12-17 Relations/Paper/Winter_2025_TODO.tex
todo updated and split into logical sections

@@
 \maketitle
+\section*{December 2025}
 
-\section*{December 2025}
-\subsection*{Carry over from previous TODO}
+\section*{Week starting 15th December}
 \begin{todolist}
+  \item [\done]Split the todo list into logical sections. Well foundedness. Paper updates. TRS. Research items. 
+  \item TRS: We've furthered the formalization and encoded a simple example. Would be worth encoding more examples and thinking about quality of life improvements we can make to the process. 
+\end{todolist}
+
+\subsection*{Well founded investigations}
+\begin{todolist}
+  \item Is there a path from WFseq- with MP== to WFseq? (W're thinking it will need rdec as well to give us the implication).
+  \item incorporate wfseq not not to the paper.
+  \item Can we show that the not not closure of R emerges from WFminDNE?
+  \item We know for wfminDNE every predicate that is not not closed with weak decidability of equality implies wem. What can we do from here. 
+  \item can we show that wfminnotnot implies wfaccnotnot?
+That would give a nice equivalence between three definitions in the weak row of the diagram.
+One approach could be to see what predicates we can prove with just wfminnotnot (in the same way that we first explored what predicates could be proved with wfmin before finding out a path to wfacc).
+Perhaps wfminnotnot implies WEM?
+
+\end{todolist}
+
+\subsection*{Paper updates and improvements}
+\begin{todolist}
+  \item (high priority) Having shown that WFmin implies WFacc when R is non empty we need to update the paper.
+Specifically we should update the text in the WF section and the diagram to incorporate the new implication.
+Update the table too with R not empty?
   \item (Review 3) * From the formalization, the authors could explain some features and syntax of Agda for readers unfamiliar with this proof assistant.
@@
 12.
-    \item  Create an equivalences file showing that our formalization agrees with the ASL (specifically definitions such as confluent, wcr, nf, leading up to showing our formalizations of Newman's lemma agree).
-  \item Investigate contributing work to the ASL.
-This may mean refactoring the work already done to conform with the ASL.
-Specific contributions would likely be: Generalized NL.
-Theorem's 122 and 123.
-Alternative definitions of Well-founded, the implications for the hierarchy.
-  \item  It's possible to have a term rewrite system with good properties like FB and the relation being decidable.
-But not satisfying accCor.
-That is something that can be added in a final touch of the paper.
-Either a remark or example, where a term rewrite system does not validate accCor.
-(In the lambda calculus, there are computable perpetual strategies.
-We think they're concerned with weak normalization.
-Not sure if it can be done with strong normalization.)
-  \item Is there a path from WFseq- with MP== to WFseq? (W're thinking it will need rdec as well to give us the implication
-  ).
- \item incorporate wfseq not not to the paper?
- \item We want to start looking at examples.
-What we want to know is whether a first order rewrite system with some minimal properties implies some of our classical properties.
-E.g.
-lambda calculus satisfies some of our classical properties.
-As does first order term rewrite system.
-Follow up question: how big of an issue is it that accCor is not provable?
-Can we prove is isn't satisfied?
- \item Formalize perpetual strategy for untyped lambda calculus and conclude that the weak WF statements define the same subset of (untyped) lambda terms.  
- \item check TERESE and see which first order term rewrite system examples which could be valid for showing classical and constructive formalization coincide.
-First order term rewrite systems are (always?) fb and R is dec.
- \item If we formalize a first order rewrite system, this would allow other avenues of investigation.
-E.g.
-conjecture that in general first order rewrite system is FB and dec, and therefore SN implies WN.
-Because of the rewrite rule: "every variable occuring in the right hand side r occurs in l as well" we should be able to achieve this.
-And it will not be true in the absrtact context.
      \item Make the well founded definitions conform to the style of the definitions in other sections.
@@
 (low priority, and probably not itemized).
+     \item run through the table again and check the counterexamples line up. 
+     \item MF and WN iff NF (see in hierarchy section) should be an intersection rather than logical and (change to be made in paper and agda code).
+Similarly it should be the double arrow iff.
+Check through paper for similar changes.
+     \item Make explicit on our table in the paper that we can go from our weakest definition (wfcornotnot) to our strongest (wfmin) via classical assumptions (EM).
+We think we already mention that all the definitions are classically equivalent in the paper (do we?).
+Also make explicit the implication from wfmin to wfacc.
+     \item We have shown wfmindne not not implies wfacc not not with accDNE. Now need to update the paper/graph to reflect this.
+
+    \end{todolist}
+    \subsection*{Formalizing TRS}
+    \begin{todolist}
+      \item  Create a TRS example that has FB and Rdec but not accCor. Follow up question: how big of an issue is it that accCor is not provable? Can we prove is isn't satisfied? 
+      \item In general first order rewrite system is FB and dec, and therefore SN implies WN.
+Because of the rewrite rule: "every variable occuring in the right hand side r occurs in l as well" we should be able to achieve this.
+And it will not be true in the absrtact context.
+      \item TRS: Formalize orthogonality and show it is equivalent to our notion of confluence.
+
+    \end{todolist}
+
+    \subsection*{Other research areas/work}
+    \begin{todolist}
+      \item Tidy up wfcounters and consider whether any of the proofs want moving to wfbasic implications. 
+      \item Investigate contributing work to the ASL.
+This means refactoring the work already done to conform with the ASL.
+Specific contributions would likely be: Generalized NL.
+Theorem's 122 and 123.
+Alternative definitions of Well-founded, the implications for the hierarchy.
+      \item Formalize perpetual strategy for untyped lambda calculus and conclude that the weak WF statements define the same subset of (untyped) lambda terms.  
+      \item Go through the code, make naming consistent and self-documenting
+      \item Check if there is a proof of SN $\to$ WN in first order term rewrite systems. If not, this is an interesting avenue to explore.
+      \item (Research item) Find a concrete application of generalized Newman's Lemma.
+* Finding a term rewrite system where it's easier to see that it is weakly cr and that every term is SM (as opposed to being CR).
+      \item (Research item) Carry out research on rewriting counterexamples like our own so we can try and put them into some sort of context. Have our counterexamples been shown before?
+      \item (Research item) Work on the missing implications from the paper. So far we believe this is just CR $\to$ CP in the ARS section. - Will probably be quite a bit of work (low priority)
+      \item $\lnot \lnot $closed C definition sometimes is a lambda term with three variables we can refactor this in those locations. (low priority)
+
+    \end{todolist}
+
+\subsection*{Complete}
+  \begin{todolist}
       \item [\done] Improve how we write P bar bar for the definitions in wellfounded (well founded minimality wise).
@@
 (when defining isMinDec) (new macro nrstep fixes it).
-  \item Go through the code, make naming consistent and self-documenting
-  \item run through the table again and check the counterexamples line up. 
-  \item MF and WN iff NF (see in hierarchy section) should be an intersection rather than logical and (change to be made in paper and agda code).
-Similarly it should be the double arrow iff.
-Check through paper for similar changes.
-  \item Check if there is a first order term rewrite system formalization in ASL. If so, do they have a proof of SN $\to$ WN. If not, this is an interesting avenue to explore (see earlier TODO point).
-
-\end{todolist}
-\section*{Research items}
-\begin{todolist}
-  \item (Research item) Find a concrete application of generalized Newman's Lemma.
-* Finding a term rewrite system where it's easier to see that it is weakly cr and that every term is SM (as opposed to being CR).
-  \item (Research item) Formalize a first order term rewriting system. Use TeReSe to create a list of rewrite systems.
-  \item (Research item) Carry out research on rewriting counterexamples like our own so we can try and put them into some sort of context. Have our counterexamples been shown before?
-  \item (Research item) Work on the missing implications from the paper. So far we believe this is just CR $\to$ CP in the ARS section. - Will probably be quite a bit of work (low priority)
-  \item (Research item) Investigate: what we've done for natural numbers could be done for an arbitrary ARS (in the counter examples files), but for weak minimality and weak excluded middle.
+      \item [\done] (Research item) Formalize a first order term rewriting system. Use TeReSe to create a list of rewrite systems.
+      \item [\done](Research item) Investigate: what we've done for natural numbers could be done for an arbitrary ARS (in the counter examples files), but for weak minimality and weak excluded middle.
 (This is what we were working on end of day 4th December).
-  \end{todolist}
-
-\section*{Week starting 8th December}
-\begin{todolist}
       \item [\done] Is the new definition of wdec in Predicates correct?
@@
       \item [\done] Go through the locations where we could use the wdec definition and replace it with our new wdec definition (search for wdec, previously we've manually defined it in each location)
-  \item $\lnot \lnot $closed C definition sometimes is a lambda term with three variables we can refactor this in those locations. (low priority) 
-  \item can we show that  wfminDNE implies RisDec. We've shown that WFmin implies RisDec (in WFcounters). We've started the DNE proof in Wfimplications (commented out). 
+  \item [\done] can we show that  wfminDNE implies RisDec (no but we've shown it implies RisminDec).
+We've shown that WFmin implies RisDec (in WFcounters).
+We've started the DNE proof in Wfimplications (commented out).
   \item [\done] We successfully proved that RisWFmin implies RisDec and RisMinDec!
@@
 Reminder that WFmin implies EM when R is non empty.
-  \item (high priority) Having shown that WFmin implies WFacc when R is non empty we need to update the paper.
-Specifically we should update the text in the WF section and the diagram to incorporate the new implication.
-Update the table too with R not empty?
   \item [\done] Show that we can go from our weakest WF definition to our strongest
-  \item Do we want to make explicit on our table in the paper that we can go from our weakest definition (wfcornotnot) to our strongest (wfmin) via classical assumptions (EM).
-We think we already mention that all the definitions are classically equivalent in the paper (do we?).
   \item [\done] We have moved the proof of wfmin implies EM to WFbasic implications. Can delete the old proof in WFcounters. 
-  \item can we show that wfminnotnot implies wfaccnotnot?
-That would give a nice equivalence between three definitions in the weak row of the diagram.
-One approach could be to see what predicates we can prove with just wfminnotnot (in the same way that we first explored what predicates could be proved with wfmin before finding out a path to wfacc).
-Perhaps wfminnotnot implies WEM?
   \item [\done] Work out what if any WF definition implies WEM (other than WFmin)?
   \item [\done] Get rid of wfcor+ in our main development, substitute in the not not definition for consistency. 
-
-  \item We've started formalizing TRS in a new folder.
-This is our likely starting point for our next meeting.
-Before we meet it might be worth looking at the WF implications and see if we can add to it.
-
-  \item TRS: Complete our formalization. formalize some simple TRS to check our implementation works. 
-  \item TRS: Formalize orthogonality and show it is equivalent to our notion of confluence. 
   \item [\done] We've shown that wfminDNE gives us decRmin is we have decidability of equality. 
@@
   \item [\done] We show that R is weakly decidable with the assumption of wfminDNE and equality decidability.
-  \item Can we show that the not not closure of R emerges from WFminDNE?
-  \item We have shown wfmindne not not implies wfacc not not with accDNE. Now need to update the paper/graph to reflect this.
 
@@
 We did require decidability of equality).
-  \item Tidy up wfcounters and consider whether any of the proofs want moving to wfbasic implications. 
-  \item What can we do with wfminDNE now that we have WEM? 
 \end{todolist}
